\documentclass[a4paper]{article}

\usepackage[welsh,english]{babel}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{textcomp}

%\usepackage[2012rules]{optional}

\usepackage[osf]{mathpazo}

\usepackage{perpage} %the perpage package
\MakePerPage{footnote} %the perpage package command
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\usepackage[perpage,para,symbol]{footmisc}

%\opt{newrules}{
\title{The Child Support (Maintenance Assessments and Special Cases) and Social Security (Claims and Payments) Amendment Regulations 1996}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I. 1996 No. 481}

\date{Made 28th February 1996\\Coming into force 8th April 1996
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead[L]{}
\fancyhead[C]{\itshape The Child Support (Maintenance Assessments and Special Cases) and Social Security (Claims and Payments) Amendment Regulations 1996 (S.I.~1996/481) \parthead%\phantom{...}% (\versionyear{} scheme version)
}
\fancyhead[R]{}
\fancyfoot[C]{\thepage}
\newcommand{\parthead}{}

\usepackage{array}
\usepackage{multirow}
\usepackage[debugshow]{tabulary}
\usepackage{longtable}
\usepackage{multicol}
\usepackage{lettrine}

\usepackage[colorlinks=true]{hyperref}
\usepackage{microtype}

\hyphenation{Aw-dur-dod}
\hyphenation{bank-rupt-cy}
\hyphenation{Ec-cles-ton}
\hyphenation{Eux-ton}
\hyphenation{Hogh-ton}
\hyphenation{Pres-ton}
\hyphenation{Pru-den-tial}
\hyphenation{Riv-ing-ton}

\newcolumntype{x}[1]
	{>{\raggedright}p{#1}}
\newcommand{\tn}{\tabularnewline}
\setlength\tymin{50pt}

\newcommand\amendment[1]{\subsubsection*{Notes}{\itshape\frenchspacing\footnotesize #1 \par}}

\setlength\headheight{34.87003pt}

\begin{document}

\maketitle

\noindent
Whereas a draft of this instrument was laid before Parliament in accordance with section 52(2) of the Child Support Act 1991\footnote{\frenchspacing 1991 c. 48.} and approved by resolution of each House of Parliament:

 Now, therefore, the Secretary of State for Social Security, in exercise of the powers conferred by sections 51, 52(4) and 54\footnote{\frenchspacing Section 54 is cited because of the meaning ascribed to the word “prescribed”.} of, and paragraphs 5 and 7 of Schedule 1 to, the Child Support Act 1991, section 5(1)($p$) of the Social Security Administration Act 1992\footnote{\frenchspacing 1992 c. 5.} as extended by section 43(2) of the Child Support Act 1991\footnote{\frenchspacing Section 43(2) was amended by Schedule 2, paragraph 113 of the Social Security (Consequential Provisons) Act 1992 (c. 6).} and section 189(1) and (4) of the Social Security Administration Act 1992, and of all other powers enabling him in that behalf, after agreement by the Social Security Advisory Committee that the proposals in respect of these Regulations should not be referred to it\footnote{\frenchspacing See section 173(1) of the Social Security Administration Act 1992.}, hereby makes the following Regulations:


{\sloppy

\tableofcontents

}

\setcounter{secnumdepth}{-2}

\subsection[1. Citation, commencement and interpretation]{Citation, commencement and interpretation}

1.—(1) These Regulations may be cited as the Child Support (Maintenance Assessments and Special Cases) and Social Security (Claims and Payments) Amendment Regulations 1996 and shall come into force on 8th April 1996.

(2) In these Regulations—
\begin{enumerate}\item[]
“the Act” means the Child Support Act 1991;

“Maintenance Assessments and Special Cases Regulations” means the Child Support (Maintenance Assessments and Special Cases) Regulations 1992\footnote{\frenchspacing S.I. 1992/1815.};

“Claims and Payments Regulations” means the Social Security (Claims and Payments) Regulations 1987\footnote{\frenchspacing S.I. 1987/1968; the relevant amending instruments are S.I. 1991/2284, 1992/1026, 1993/478, 495 and 2113 and 1994/2319.}.
\end{enumerate}

\subsection[2. Amendment of regulation 13 of the Maintenance Assessments and Special Cases Regulations]{Amendment of regulation 13 of the Maintenance Assessments and Special Cases Regulations}

2.—(1) Regulation 13 of the Maintenance Assessments and Special Cases Regulations shall be amended in accordance with the following provisions of this regulation.

(2) In paragraph (1) after the words “the minimum amount shall be” there shall be inserted the words “2 multiplied by”.

(3) In paragraph (2) for the words “an amount” there shall be substituted the words “the 5 per centum amount”.

\subsection[3. Amendment of Schedule 2 to the Maintenance Assessments and Special Cases Regulations]{Amendment of Schedule 2 to the Maintenance Assessments and Special Cases Regulations}

3.—(1) Schedule 2 to the Maintenance Assessments and Special Cases Regulations shall be amended in accordance with the following provisions of this regulation.

(2) In sub-paragraph (1) of paragraph 19, for “£10.00” there shall be substituted “up to £20.00”.

(3) In sub-paragraph (1) of paragraph 20, for “£10.00” in the three places in which it occurs there shall be substituted “£20.00”.

\subsection[4. Transitional provisions]{Transitional provisions}

4.  A maintenance assessment in force on 8th April 1996 shall not be reviewed solely to give effect to regulation 3 but, on a review of that assessment under section 16, 17 or 18 of the Act, the provisions of that regulation shall have effect from the effective date of any fresh maintenance assessment made following that review.

\subsection[5. Amendment of paragraph 7A of Schedule 9 to the Claims and Payments Regulations]{Amendment of paragraph 7A of Schedule 9 to the Claims and Payments Regulations}

5.—(1) Paragraph 7A of Schedule 9 to the Claims and Payments Regulations shall be amended in accordance with the following provisions of this regulation.

(2) In sub-paragraph (3)—
\begin{enumerate}\item[]
(a) at the beginning there shall be inserted the words “Subject to sub-paragraph (4),”;

(b) the words “(that is to say 5 per cent of the personal allowance for a single claimant aged not less than 25)” shall be omitted.
\end{enumerate}

(3) After sub-paragraph (3) there shall be added the following sub-\hspace{0pt}paragraph—
\begin{quotation}
“(4) Where, apart from the provisions of this sub-paragraph, the provisions of paragraphs 8(1) and 9 would result in the maximum aggregate amount payable equalling 2 times 5 per cent.\ of the personal allowance for a single claimant aged not less than 25 years, the amount of specified benefit to be paid under this paragraph shall be one half of the amount specified in sub-paragraph (3).”.
\end{quotation}

\subsection[6. Amendment of paragraph 8 of Schedule 9 to the Claims and Payments Regulations]{Amendment of paragraph 8 of Schedule 9 to the Claims and Payments Regulations}

6.  In sub-paragraph (1) of paragraph 8 of Schedule 9 to the Claims and Payments Regulations, for the word “sub-paragraphs” there shall be substituted the word “paragraphs” and for the word “sub-paragraph” there shall be substituted the word “paragraph”.

\bigskip

Signed by authority of the Secretary of State for Social Security.

{\raggedleft
\emph{A. J. B. Mitchell}\\*Parliamentary Under-Secretary of State,\\*Department of Social Security

}

29th February 1996

\part{Explanatory Note}

\renewcommand\parthead{--- Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations amend the Child Support (Maintenance Assessments and Special Cases) Regulations 1992 to provide for an increase in the minimum amount of child support maintenance payable, and accordingly, by virtue of regulation 28 of those Regulations, of the amount payable by an absent parent in receipt of income support or other prescribed benefit. The amount is increased to 2 times 5 per cent of the income support personal allowance for a single claimant aged not less than 25. Consequential amendments are made to paragraph 7A of Schedule 9 of the Social Security (Claims and Payments) Regulations 1987, which deals with deductions from benefit and direct payment to third parties. In particular, provision is made that, in certain circumstances, the amount to be deducted is one half of the amount otherwise deductible.

  Schedule 2 of the Child Support (Maintenance Assessments and Special Cases) Regulations is also amended so as to increase from £10.00 to £20.00 the disregard, when determining net income, in relation to charitable or voluntary payments.

  These Regulations impose no costs on business.

\end{document}