\documentclass[a4paper]{article}

\usepackage[welsh,english]{babel}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{textcomp}

%\usepackage[2012rules]{optional}

\usepackage[osf]{mathpazo}

\usepackage{perpage} %the perpage package
\MakePerPage{footnote} %the perpage package command
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\usepackage[perpage,para,symbol]{footmisc}

%\opt{newrules}{
\title{The Social Security and Child Support (Jobseeker’s Allowance) (Consequential Amendments) Regulations 1996}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I. 1996 No. 1345}

\date{Made 16th May 1996\\Laid before Parliament 24th May 1996\\Coming into force 7th October 1996
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead[L]{}
\fancyhead[C]{\itshape The Social Security and Child Support (Jobseeker’s Allowance) (Consequential Amendments) Regulations 1996 (S.I.~1996/1345) \parthead%\phantom{...}% (\versionyear{} scheme version)
}
\fancyhead[R]{}
\fancyfoot[C]{\thepage}
\newcommand{\parthead}{}

\usepackage{array}
\usepackage{multirow}
\usepackage[debugshow]{tabulary}
\usepackage{longtable}
\usepackage{multicol}
\usepackage{lettrine}

\usepackage[colorlinks=true]{hyperref}
\usepackage{microtype}

\hyphenation{Aw-dur-dod}
\hyphenation{bank-rupt-cy}
\hyphenation{Ec-cles-ton}
\hyphenation{Eux-ton}
\hyphenation{Hogh-ton}
\hyphenation{Pres-ton}
\hyphenation{Pru-den-tial}
\hyphenation{Riv-ing-ton}

\newcolumntype{x}[1]
	{>{\raggedright}p{#1}}
\newcommand{\tn}{\tabularnewline}
\setlength\tymin{50pt}

\newcommand\amendment[1]{\subsubsection*{Notes}{\itshape\frenchspacing\footnotesize #1 \par}}

\setlength\headheight{22.87003pt}

\begin{document}

\maketitle

\noindent
The Secretary of State for Social Security, in exercise of the powers conferred on him by sections 35(1), 36 and 40 of the Jobseekers Act 1995\footnote{\frenchspacing 1995 c. 18; section 35(1) is an interpretation provision and is cited because of the meaning assigned to the words “prescribed” and “regulations”.} and of all other powers enabling him in that behalf, by this instrument which is made before the end of the period of 6 months beginning with the coming into force of the enactment under which these Regulations are made\footnote{\frenchspacing See the Social Security Administration Act 1992 (c. 5), section 173(5)($a$).}, and with the consent of the Treasury to regulation 24\footnote{\frenchspacing See the Social Security Administration Act 1992, section 189(8).}, hereby makes the following Regulations:


{\sloppy

\tableofcontents

}

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and commencement]{Citation and commencement}

1.  These Regulations may be cited as the Social Security and Child Support (Jobseeker’s Allowance) (Consequential Amendments) Regulations 1996 and shall come into force on 7th October 1996.

\subsection[2. Amendment of the Child Benefit (General) Regulations 1976]{Amendment of the Child Benefit (General) Regulations 1976}

2.—(1) The Child Benefit (General) Regulations 1976\footnote{\frenchspacing S.I. 1976/965.} shall be amended in accordance with the following provisions of this regulation.

(2) For regulation 7C\footnote{\frenchspacing Regulation 7C was inserted by S.I. 1980/1045 and amended by S.I. 1988/521.} there shall be substituted the following regulation—
\begin{quotation}
\subsection*{“Child receiving income support or income-based jobseeker’s allowance}

7C.  Child benefit shall not be payable in respect of a child by virtue of section 142(1)($c$) of the Social Security Contributions and Benefits Act 1992\footnote{\frenchspacing 1992 c. 4.} for any week in respect of which that child receives income support or income-based jobseeker’s allowance within the meaning of section 1(4) of the Jobseekers Act 1995.”.
\end{quotation}

(3) In regulation 7D(3)($b$) (circumstances in which a person who has ceased to receive full-time education is to be treated as a child)\footnote{\frenchspacing Regulation 7D was inserted by S.I. 1988/1227.} after the words “income support” there shall be inserted the words “or income-based jobseeker’s allowance within the meaning of section 1(4) of the Jobseekers Act 1995”.

\subsection[3. Amendment of the Child Support (Arrears, Interest and Adjustment of Maintenance Assessments) Regulations 1992]{Amendment of the Child Support (Arrears, Interest and Adjustment of Maintenance Assessments) Regulations 1992}

3.—(1) In the provisions of the Child Support (Arrears, Interest and Adjustment of Maintenance Assessments) Regulations 1992\footnote{\frenchspacing S.I. 1992/1816.} listed in paragraph (2), after the words “income support” in each place where they occur there shall be inserted the words “or income-based jobseeker’s allowance”.

(2) The provisions referred to in paragraph (1) are—
\begin{enumerate}\item[]
($a$) regulation 7 (receipt and retention of interest paid);

($b$) regulation 8 (retention of recovered arrears of child support maintenance by the Secretary of State)\footnote{\frenchspacing Regulation 8 was substituted by S.I. 1995/3261.};

($c$) regulation 10A (reimbursement of a repayment of overpaid child maintenance)\footnote{\frenchspacing Regulation 10A was inserted by S.I. 1995/3261.}.
\end{enumerate}

\subsection[4. Amendment of the Child Support Fees Regulations 1992]{Amendment of the Child Support Fees Regulations 1992}

4.  In regulation 3(5)($a$) of the Child Support Fees Regulations 1992\footnote{\frenchspacing S.I. 1992/3094.} (liability to pay fees) after the words “Benefits Act 1992” there shall be inserted the words “,~or income-based jobseeker’s allowance under the Jobseekers Act 1995”.

\subsection[5. Amendment of the Child Support (Maintenance Assessment Procedure) Regulations 1992]{Amendment of the Child Support (Maintenance Assessment Procedure) Regulations 1992}

5.—(1) The Child Support (Maintenance Assessment Procedure) Regulations 1992\footnote{\frenchspacing S.I. 1992/1813.} shall be amended in accordance with the following provisions of this regulation.

(2) In regulation 1 (interpretation)—
\begin{enumerate}\item[]
($a$) in paragraph (2)—
\begin{enumerate}\item[]
(i) in the definition of “applicable amount” after the words “applicable amount” there shall be inserted the words “,~except in regulation 40ZA,”;

(ii) in the definition of “benefit week” after the words “Income Support Regulations,” there shall be inserted the words “in relation to jobseeker’s allowance has the same meaning as in the Jobseeker’s Allowance Regulations,”;

(iii) after the definition of “Information, Evidence and Disclosure Regulations” there shall be inserted the following definition—
\begin{quotation}
““the Jobseeker’s Allowance Regulations” means the Jobseeker’s Allowance Regulations 1996\footnote{\frenchspacing S.I. 1996/207.};”;
\end{quotation}

(iv) in the definition of “relevant benefit” after the words “income support,” there shall be inserted the words “income-based jobseeker’s allowance,”;
\end{enumerate}

($b$) in paragraph (3)\footnote{\frenchspacing Relevant amending instrument is S.I. 1995/3261.}—
\begin{enumerate}\item[]
(i) after the words “regulation 40(3)” in each place where they occur there shall be inserted the words “or, as the case may be, regulation 40ZA(4)”;

(ii) in sub-paragraph ($c$) after the words “income support” there shall be inserted the words “or income-based jobseeker’s allowance”.
\end{enumerate}
\end{enumerate}

(3) In regulation 8D(8)\footnote{\frenchspacing Regulations 8A to 8D were inserted by S.I. 1995/3261.} at the end there shall be added the words “or income-based jobseeker’s allowance”.

(4) In regulation 17(6) (intervals between periodical reviews and notice of a periodical review) after the words “income support” in each place where they occur there shall be inserted the words “or income-based jobseeker’s allowance”.

(5) In regulation 35A (circumstances in which a reduced benefit direction shall not be given)\footnote{\frenchspacing Regulation 35A was inserted by S.I. 1995/3261.} after paragraph ($a$) there shall be inserted the following paragraph—
\begin{quotation}
“($aa$) income-based jobseeker’s allowance is paid to or in respect of the parent in question and the applicable amount of the claimant for income-based jobseeker’s allowance includes one or more of the amounts set out in paragraph 20(4), (5) or (7) of Schedule 1 to the Jobseeker’s Allowance Regulations; or”.
\end{quotation}

(6) In regulation 36 (amount of and period of reduction of relevant benefit under a reduced benefit direction)\footnote{\frenchspacing Paragraphs (5A) to (5E) were inserted by S.I. 1995/1045.}—
\begin{enumerate}\item[]
($a$) in paragraphs (2) and (3) for the words “and 40” in each place where they occur there shall be substituted the words “,~40 and 40ZA”;

($b$) in paragraphs (5B), (6) and (7) after the words “income support” there shall be inserted the words “or income-based jobseeker’s allowance”;

($c$) in paragraph (5C)—
\begin{enumerate}\item[]
(i) after the words “income support” in the first place where they occur there shall be inserted the words “or income-based jobseeker’s allowance”;

(ii) for the words “or income support” in the second place where they occur there shall be substituted the words “, income support or income-based jobseeker’s allowance”;
\end{enumerate}

($d$) in paragraph (5D)($b$)—
\begin{enumerate}\item[]
(i) after the words “income support” in the first place where they occur there shall be inserted the words “or income-based jobseeker’s allowance”;

(ii) after the words “income support” in the second and third places where they occur there shall be inserted the words “or, as the case may be, income-based jobseeker’s allowance”.
\end{enumerate}
\end{enumerate}

(7) In regulation 37 (modification of reduction under a reduced benefit direction to preserve minimum entitlement to relevant benefit) after paragraph ($a$) there shall be inserted the following paragraph—
\begin{quotation}
“($aa$) in the case of income-based jobseeker’s allowance, by regulation 26A(10)\footnote{\frenchspacing Regulation 26A was inserted by S.I. 1996/207.} of those Regulations;”.
\end{quotation}

(8) In regulation 38(3) (suspension of a reduced benefit direction when relevant benefit ceases to be payable) after the word “40,” there shall be inserted the word “40ZA,”.

(9) In regulation 39(1) (reduced benefit direction where family credit or disability working allowance is payable and income support becomes payable)—
\begin{enumerate}\item[]
($a$) after the words “income support” in the first place where they occur there shall be inserted the words “or income-based jobseeker’s allowance”;

($b$) after the words “income support” in the second and third places where they occur there shall be inserted the words “or, as the case may be, income-based jobseeker’s allowance”.
\end{enumerate}

(10) After regulation 40 (suspension of a reduced benefit direction when a modified applicable amount is payable) there shall be inserted the following regulation—
\begin{quotation}
\subsection*{\sloppy “Suspension of a reduced benefit direction in the case of modified applicable amounts in jobseeker’s allowance}

40ZA.—(1) Where a direction is given or is in operation at a time when income-based jobseeker’s allowance is payable to or in respect of the parent concerned but her applicable amount falls to be calculated under the provisions mentioned in paragraph (4), that direction shall be suspended for so long as the applicable amount falls to be calculated under those provisions, or 52 weeks, whichever period is the shorter.

(2) Where a direction is given or is in operation at a time when income-based jobseeker’s allowance is payable to or in respect of the parent concerned, but her applicable amount includes a residential allowance under regulation 83($c$) of and paragraph 3 of Schedule 1 to the Jobseeker’s Allowance Regulations (persons in residential care or nursing homes), that direction shall be suspended for as long as her applicable amount includes such a residential allowance, or 52 weeks, whichever period is the shorter.

(3) Where a case falls within paragraph (1) or (2) and a direction has been suspended for a period of 52 weeks, it shall cease to be in force.

(4) The provisions of paragraph (1) shall apply where the applicable amount in relation to the parent concerned falls to be calculated under—
\begin{enumerate}\item[]
($a$) regulation 85 of and paragraph 1 or 2 of Schedule 5 to the Jobseeker’s Allowance Regulations (patients);

($b$) regulation 85 of and paragraph 8, 9 or 15 of Schedule 5 to the Jobseeker’s Allowance Regulations (persons in residential accommodation); or

($c$) regulation 86 of and Schedule 4 to the Jobseeker’s Allowance Regulations (applicable amounts for persons in residential care and nursing homes).”.
\end{enumerate}
\end{quotation}

(11) In regulation 47(1) (reduced benefit directions where there is an additional qualifying child) after the words “regulation 40” in each place where they occur there shall be inserted the words “or 40ZA”.

(12) In paragraph 1(3)($b$) of Schedule 1 (persons of 16 or 17 years of age who are not in full-time non-advanced education) after the words “income support” there shall be inserted the words “or income-based jobseeker’s allowance”.

\subsection[6. Amendment of the Child Support (Maintenance Assessments and Special Cases) Regulations 1992]{Amendment of the Child Support (Maintenance Assessments and Special Cases) Regulations 1992}

6.—(1) The Child Support (Maintenance Assessments and Special Cases) Regulations 1992\footnote{\frenchspacing S.I. 1992/1815.} shall be amended in accordance with the following provisions of this regulation.

(2) In regulation 1(2) (interpretation) after the definition of “Independent Living (Extension) Fund” there shall be inserted the following definition—
\begin{quotation}
““the Jobseekers Act” means the Jobseekers Act 1995\footnote{\frenchspacing 1995 c. 18.};”.
\end{quotation}

(3) In regulation 28(1) (amount payable where absent parent is in receipt of income support or other prescribed benefit)\footnote{\frenchspacing Relevant amending instrument is S.I. 1993/913.} after the words “income support” there shall be inserted the words “,~income-based jobseeker’s allowance”.

(4) In Schedule 1 (calculation of N and M)—
\begin{enumerate}\item[]
($a$) in paragraph 7 after sub-paragraph (1) there shall be inserted the following sub-paragraph—
\begin{quotation}
“(1A) For the purposes of sub-paragraph (1), an addition to a contribution-based jobseeker’s allowance under regulation 9(4) of the Jobseeker’s Allowance (Transitional Provisions) Regulations 1995\footnote{\frenchspacing S.I. 1995/3276.} shall be treated as a dependency increase included with a benefit under the Contributions and Benefits Act.”;
\end{quotation}

($b$) paragraph 22 shall be re-numbered sub-paragraph (1) of paragraph 22 and after sub-paragraph (1) there shall be added the following sub-paragraph—
\begin{quotation}
“(1A) For the purposes of sub-paragraph (1), an addition to a contribution-based jobseeker’s allowance under regulation 9(4) of the Jobseeker’s Allowance (Transitional Provisions) Regulations 1995 shall be treated as a dependency increase included with a benefit under the Contributions and Benefits Act.”;
\end{quotation}

($c$) in paragraph 28($b$) for the words “unemployment benefit” there shall be substituted the words “a contribution-based jobseeker’s allowance”.
\end{enumerate}

(5) In paragraph 15 of Schedule 2 (amounts to be disregarded when calculating or estimating N and M) after the words “income support,” there shall be inserted the words “income-based jobseeker’s allowance,”.

(6) In the provisions listed in paragraph (7), after the words “the Contributions and Benefits Act” in each place where they occur there shall be inserted the words “or the Jobseekers Act”.

(7) The provisions referred to in paragraph (6) are—
\begin{enumerate}\item[]
($a$) regulation 7(1)($b$) (net income: calculation or estimation of N);

($b$) paragraph 6(2) of Schedule 1 (calculation of N and M);

($c$) paragraphs 39 and 49 (when those words first occur) of Schedule 2 (amounts to be disregarded when calculating or estimating N or M).
\end{enumerate}

\subsection[7. Amendment of the Disability Working Allowance (General) Regulations 1991]{Amendment of the Disability Working Allowance (General) Regulations 1991}

7.—(1) The Disability Working Allowance (General) Regulations 1991\footnote{\frenchspacing S.I. 1991/2887.} shall be amended in accordance with the following provisions of this regulation.

(2) In regulation 2(1) (interpretation) after the definition of “attendance allowance” there shall be inserted the following definition—
\begin{quotation}
““the benefit Acts” means the Contributions and Benefits Act and the Jobseekers Act 1995\footnote{\frenchspacing 1995 c. 18.};”.
\end{quotation}

(3) In regulation 7 (income-related benefits) after paragraph ($a$) there shall be inserted the following paragraph—
\begin{quotation}
“($aa$) in the case of income-based jobseeker’s allowance, in accordance with paragraphs 12(1)($a$), ($b$)(ii) or ($c$) or 13, and 14 of Schedule 1 to the Jobseeker’s Allowance Regulations 1996\footnote{\frenchspacing S.I. 1996/207.} (applicable amounts).”.
\end{quotation}

(4) In regulation 8(2) (persons of a prescribed description) after sub-\hspace{0pt}paragraph ($a$) there shall be inserted the following sub-paragraph—
\begin{quotation}
“($aa$) who is entitled to income-based jobseeker’s allowance or would, but for section 3(1)($d$) of the Jobseekers Act 1995 (provision against dual entitlement of members of family), be so entitled;”.
\end{quotation}

(5) In regulation 55 (prevention of duplication of awards of family credit, disability working allowance and income support) after the words “family credit” there shall be inserted the words“, income-based jobseeker’s allowance”.

(6) In Schedule 3 (sums to be disregarded in the calculation of income other than earnings)—
\begin{enumerate}\item[]
($a$) in paragraph 3 after the words “housing benefit” there shall be inserted the words “, income-based jobseeker’s allowance”; and

($b$) in paragraph 5($b$) after the words “income support” there shall be inserted the words “or income-based jobseeker’s allowance”.
\end{enumerate}

(7) In Schedule 4 (capital to be disregarded)—
\begin{enumerate}\item[]
($a$) in paragraph 8($b$) after the words “income-related benefit” there shall be inserted the words“or income-based jobseeker’s allowance,”; and

($b$) at the end of the Schedule there shall be added the following paragraph—
\begin{quotation}
“49.  The amount of any back to work bonus payable by way of a jobseeker’s allowance or income support in accordance with section 26 of the Jobseekers Act 1995, or a corresponding payment under article 28 of the Jobseekers (Northern Ireland) Order 1995\footnote{\frenchspacing S.I. 1995/2705 (N.I.15).}, but only for a period of 52 weeks from the date of receipt.”.
\end{quotation}
\end{enumerate}

\subsection[8. Amendment of the Family Credit (General) Regulations 1987]{Amendment of the Family Credit (General) Regulations 1987}

8.—(1) The Family Credit (General) Regulations 1987\footnote{\frenchspacing S.I. 1987/1973.} shall be amended in accordance with the following provisions of this regulation.

(2) In regulation 2(1) (interpretation) after the definition of “assessment period” there shall be inserted the following definition—
\begin{quotation}
““the benefit Acts” means the Contributions and Benefits Act and the Jobseekers Act 1995\footnote{\frenchspacing 1995 c. 18.};”.
\end{quotation}

(3) In regulation 6(2) (persons of a prescribed description)\footnote{\frenchspacing Paragraph (2) was substituted by S.I. 1990/574.} after sub-paragraph ($a$) there shall be inserted the following sub-paragraph—
\begin{quotation}
“($aa$) who is entitled to income-based jobseeker’s allowance or would, but for section 3(1)($d$) of the Jobseekers Act 1995\footnote{\frenchspacing 1995 c. 18.} (provision against dual entitlement of members of family), be so entitled;”.
\end{quotation}

(4) In regulation 50 (prevention of duplication of awards of family credit and income support)\footnote{\frenchspacing Relevant amending instrument is S.I. 1991/2742.} after the words “income support” there shall be inserted the words “,~income-based jobseeker’s allowance”.

(5) In Schedule 2 (sums to be disregarded in the calculation of income other than earnings)—
\begin{enumerate}\item[]
($a$) in paragraph 3 after the words “housing benefit” there shall be inserted the words “,~income-based jobseeker’s allowance”; and

($b$) in paragraph 5($b$) after the words “income support” there shall be inserted the words “or income-based jobseeker’s allowance”.
\end{enumerate}

(6) In Schedule 3 (capital to be disregarded)—
\begin{enumerate}\item[]
($a$) in paragraph 8($b$) after the words “income-related benefit” there shall be inserted the words“or income-based jobseeker’s allowance,”; and

($b$) at the end of the Schedule there shall be added the following paragraph—
\begin{quotation}
“50.  The amount of any back to work bonus payable by way of a jobseeker’s allowance or income support in accordance with section 26 of the Jobseekers Act 1995, or a corresponding payment under article 28 of the Jobseekers (Northern Ireland) Order 1995, but only for a period of 52 weeks from the date of receipt.”.
\end{quotation}
\end{enumerate}

\subsection[9. Amendment of the Social Security (Airmen’s Benefits) Regulations 1975]{Amendment of the Social Security (Airmen’s Benefits) Regulations 1975}

9.  In regulation 3 of the Social Security (Airmen’s Benefits) Regulations 1975\footnote{\frenchspacing S.I. 1975/494.} (application of the Act and regulations) after the word “thereunder” there shall be inserted the words “,~and the Jobseekers Act 1995\footnote{\frenchspacing 1995 c. 18.} and regulations made thereunder”.

\subsection[10. Amendment of the Social Security (Attendance Allowance) Regulations 1991]{\sloppy Amendment of the Social Security (Attendance Allowance) Regulations 1991}

10.  In regulation 8(6)($a$) of the Social Security (Attendance Allowance) Regulations 1991 (exemption from regulations 6 and 7)\footnote{\frenchspacing S.I. 1991/2740; paragraph (6) of regulation 8 was added by S.I. 1992/3147; relevant amending instrument is S.I. 1993/518.} after the words “income support” in each place where they occur there shall be inserted the words “or income-based jobseeker’s allowance”.

\subsection[11. Amendment of the Social Security Benefit (Computation of Earnings) Regulations 1978]{Amendment of the Social Security Benefit (Computation of Earnings) Regulations 1978}

11.—(1) Regulation 3 of the Social Security Benefit (Computation of Earnings) Regulations 1978 (payments to be disregarded)\footnote{\frenchspacing S.I. 1978/1698; relevant amending instruments are S.I. 1987/606, 1989/2123, 1992/300 and 1995/829.} shall be amended in accordance with the following provisions of this regulation.

(2) In paragraph (3) the words from “and regulation 7(1)($g$)(i)” up to and including the words“lower earnings limit)” shall be omitted.

(3) Paragraphs (4A), (4B), (5) and (6) shall be omitted.

\subsection[12. Amendment of the Social Security Benefit (Dependency) Regulations 1977]{Amendment of the Social Security Benefit (Dependency) Regulations 1977}

12.—(1) The Social Security Benefit (Dependency) Regulations 1977\footnote{\frenchspacing S.I. 1977/343.} shall be amended in accordance with the following provisions of this regulation.

(2) In regulation 2(1)($a$) (provisions as to maintenance for the purposes of increase of benefit in respect of dependants)\footnote{\frenchspacing Relevant amending instrument is S.I. 1989/1642.} the words “unemployed, or” shall be omitted.

(3) In regulation 3 (allocation of contributions for spouse or children)\footnote{\frenchspacing Relevant amending instruments are S.I. 1983/1001, 1984/1699, 1985/1305 and 1994/2945.}—
\begin{enumerate}\item[]
($a$) in paragraph (1) the words “44(1)($a$),” shall be omitted;

($b$) in paragraph (5) for the words “sections 44(1)($a$) and” there shall be substituted the word “section”.
\end{enumerate}

(4) In regulation 8 in paragraph (2) for the words “the amount specified in paragraph 1 of Part I of Schedule 4 to the Contributions and Benefits Act” and in paragraphs (3) and (4) for the words“the amount specified in paragraph 1 of Part I of Schedule 4 to that Act” in each place in which those words occur, there shall be substituted, subject to paragraph (5), the words “the amount for the time being specified in regulation 79(1)($c$) of the Jobseeker’s Allowance Regulations 1996\footnote{\frenchspacing S.I. 1996/207.} (age related amount for a claimant who has attained the age of 25).”.

(5) Where the amount for the time being specified in regulation 79(1)($c$) of the Jobseeker’s Allowance Regulations 1996 is less than the amount specified in paragraph 1 of Part I of Schedule 4 to the Benefits Act as in force on 6th October 1996, paragraph (4) above shall have effect as if the words substituted by that paragraph were “£48.25”.

(6) Paragraph (4) above shall apply in a particular case only for so long as the amount substituted by that paragraph is greater than the amount specified in regulation 79(1)($c$) of the 1996 Regulations.

(7) In regulation 10 (increase of benefit for person having care of child)—
\begin{enumerate}\item[]
($a$) in paragraph (1)\footnote{\frenchspacing Relevant amending instruments are S.I. 1983/186, 1984/1698 and 1994/2945.} the words “of unemployment benefit or” shall be omitted, and

($b$) in paragraph (2)($b$)(ii)\footnote{\frenchspacing Relevant amending instruments are S.I. 1984/1698 and 1989/1642.} the words “unemployed or” shall be omitted.
\end{enumerate}

(8) In regulation 11 (contribution to maintenance of adult dependant)—
\begin{enumerate}\item[]
($a$) in paragraph (1)\footnote{\frenchspacing Relevant amending instruments are S.I. 1983/1001, 1984/1698 and 1994/2945.}—
\begin{enumerate}\item[]
(i) the words “(1) and” shall be omitted;

(ii) the words “unemployment benefit or” in each place where they occur shall be omitted;
\end{enumerate}

($b$) at the end of the regulation there shall be added the following paragraph—
\begin{quotation}
“(4) Where a person has been entitled to an addition to a contribution-based jobseeker’s allowance under regulation 9(4) of the Jobseeker’s Allowance (Transitional Provisions) Regulations 1995\footnote{\frenchspacing S.I. 1995/3276.} by virtue of having satisfied the requirements for an increase of unemployment benefit referred to in paragraphs (2), (2A) or (3), he shall be treated for the purposes of those paragraphs as if he had been entitled to an increase of unemployment benefit.”.
\end{quotation}
\end{enumerate}

\subsection[13. Amendment of the Social Security (Benefit) (Married Women and Widows Special Provisions) Regulations 1974]{Amendment of the Social Security (Benefit) (Married Women and Widows Special Provisions) Regulations 1974}

13.—(1) Regulation 3 of the Social Security (Benefit) (Married Women and Widows Special Provisions) Regulations 1974\footnote{\frenchspacing S.I. 1974/2010; relevant amending instruments are S.I. 1978/508 and 1995/829.} (modifications in relation to widows with respect to unemployment and other benefits) shall be amended in accordance with the following provisions of this regulation.

(2) In paragraph (1)—
\begin{enumerate}\item[]
($a$) in sub-paragraphs ($a$) and ($b$) the words “unemployment and” shall be omitted; and

($b$) sub-paragraph ($c$) shall be omitted.
\end{enumerate}

(3) In paragraph (5) the words “unemployment benefit or” in each place where they occur shall be omitted.

\subsection[14. Amendment of the Social Security (Benefit) (Members of the Forces) Regulations 1975]{Amendment of the Social Security (Benefit) (Members of the Forces) Regulations 1975}

14.—(1) The Social Security (Benefit) (Members of the Forces) Regulations 1975\footnote{\frenchspacing S.I. 1975/493.} shall be amended in accordance with the following provisions of this regulation.

(2) In regulation 2 (unemployment, sickness and invalidity benefit and severe disablement allowance)\footnote{\frenchspacing Relevant amending instrument is S.I. 1984/1303.} for the words “unemployment benefit” there shall be substituted the words“a jobseeker’s allowance”.

(3) In regulation 5 (application of the Act, the Northern Ireland Act and regulations) after the words “of the Act and regulations made under it,” there shall be inserted the words “or of the Jobseekers Act 1995\footnote{\frenchspacing 1995 c. 18.} and regulations made under it,”.

\subsection[15. Amendment of the Social Security Benefit (Persons Abroad) Regulations 1975]{Amendment of the Social Security Benefit (Persons Abroad) Regulations 1975}

15.—(1) The Social Security Benefit (Persons Abroad) Regulations 1975\footnote{\frenchspacing S.I. 1975/563.} shall be amended in accordance with the following provisions of this regulation.

(2) In regulation 12(1)($a$) (modification of the Act in relation to the Channel Islands) the words “(other than unemployment benefit)” shall be omitted.

(3) In regulation 14 (administrative arrangements about payment of benefits) after the words “under the Act” there shall be inserted the words “, or in connection with jobseeker’s allowance,”.

\subsection[16. Amendment of the Social Security Benefit (Persons Residing Together) Regulations 1977]{Amendment of the Social Security Benefit (Persons Residing Together) Regulations 1977}

16.  In regulation 2(2)($a$) of the Social Security Benefit (Persons Residing Together) Regulations 1977\footnote{\frenchspacing S.I. 1977/956; relevant amending instruments are S.I. 1983/186, 1984/1303 and 1995/829.} for the words “(increase of unemployment benefit),” there shall be substituted the words “(short-term benefits: increase for adult dependants)”.

\subsection[17. Amendment of the Social Security (Disability Living Allowance) Regulations 1991]{\sloppy Amendment of the Social Security (Disability Living Allow\-ance) Regulations 1991}

17.  In regulation 10(8)($a$) of the Social Security (Disability Living Allowance) Regulations 1991 (exemption from regulations 8 and 9)\footnote{\frenchspacing S.I. 1991/2890; paragraph (8) of regulation 10 was added by S.I. 1992/3147; relevant amending instrument is S.I. 1993/518.} after the words “income support” in each place where they occur there shall be inserted the words “or income-based jobseeker’s allowance”.

\subsection[18. Amendment of the Social Security (Graduated Retirement Benefit) (No. 2) Regulations 1978]{Amendment of the Social Security (Graduated Retirement Benefit) (No. 2) Regulations 1978}

18.  In section 36(9) of the National Insurance Act 1965\footnote{\frenchspacing 1965 c. 51.}, as continued in force by regulation 3(3) of, and Schedule 1 to, the Social Security (Graduated Retirement Benefit) (No.\ 2) Regulations 1978\footnote{\frenchspacing S.I. 1978/393; relevant amending instrument is S.I. 1995/829.}, for the words from “sections 25(5)” to the end of the subsection there shall be substituted the following words—
\begin{quotation}
“section 30B(3) of the Social Security Contributions and Benefits Act 1992\footnote{\frenchspacing 1992 c. 4; section 30B was inserted by section 2(1) of the Social Security (Incapacity for Work) Act 1994 (c. 18).}, regulations 11(1) and 18(7) of the Social Security (Incapacity Benefit) (Transitional) Regulations 1995\footnote{\frenchspacing S.I. 1995/310.} and regulation 9(5) of the Jobseeker’s Allowance (Transitional Provisions) Regulations 1995\footnote{\frenchspacing S.I. 1995/3276.} (rates of incapacity benefit and jobseeker’s allowance in transitional cases for persons over pensionable age).”.
\end{quotation}

\subsection[19. Amendment of the Social Security (Incapacity Benefit—Increases for Dependants) Regulations 1994]{\sloppy Amendment of the Social Security (Incapacity Benefit—\hspace{0pt}Increases for Dependants) Regulations 1994}

19.—(1) The Social Security (Incapacity Benefit—Increases for Dependants) Regulations 1994\footnote{\frenchspacing S.I. 1994/2945.} shall be amended in accordance with the following provisions of this regulation.

(2) In regulation 10, in paragraph (2) for the words “the amount specified in paragraph 1 of Part I of Schedule 4 to the Contributions and Benefits Act” there shall be substituted, subject to paragraph (3), the words “the amount for the time being specified in regulation 79(1)($c$) of the Jobseeker’s Allowance Regulations 1996 (age related amount for a claimant who has attained the age of 25).”.

(3) Where the amount for the time being specified in regulation 79(1)($c$) of the Jobseeker’s Allowance Regulations 1996\footnote{\frenchspacing S.I. 1996/207.} is less than the amount specified in paragraph 1 of Part I of Schedule 4 to the Benefits Act as in force on 6th October 1996 paragraph (2) above shall have effect as if the words substituted by that paragraph were “£48.25”.

(4) Paragraph (3) above shall apply in a particular case only for so long as the amount substituted by that paragraph is greater than the amount specified in regulation 79(1)($c$) of the 1996 Regulations.

\subsection[20. Amendment of the Social Security (Incapacity for Work) (General) Regulations 1995]{Amendment of the Social Security (Incapacity for Work) (General) Regulations 1995}

20.—(1) The Social Security (Incapacity for Work) (General) Regulations 1995\footnote{\frenchspacing S.I. 1995/311; relevant amending instrument is S.I. 1995/987.} shall be amended in accordance with the following provisions of this regulation.

(2) In regulation 6(3)($a$) (information required for determining capacity for work) for the words “unemployment benefit” there shall be substituted the words “jobseeker’s allowance”.

(3) In regulation 17A (person who claims unemployment benefit to be treated as capable of work) for the words “on each day in respect of which he claims unemployment benefit” there shall be substituted the words “throughout any period in respect of which he claims a jobseeker’s allowance”, and for the words “on that day” there shall be substituted the words “throughout that period”.

\subsection[21. Amendment of the Social Security (Mariners' Benefits) Regulations 1975]{Amendment of the Social Security (Mariners' Benefits) Regulations 1975}

21.—(1) The Social Security (Mariners' Benefits) Regulations 1975\footnote{\frenchspacing S.I. 1975/529.} shall be amended in accordance with the following provisions of this regulation.

(2) In regulation 4($b$) (removal of disqualification for receiving benefit by reason of absence from Great Britain)\footnote{\frenchspacing Relevant amending instruments are S.I. 1984/1303 and 1995/829.} the words “unemployment benefit” shall be omitted.

(3) In regulation 5 (evidence of unemployment or incapacity)\footnote{\frenchspacing Relevant amending instruments are S.I. 1984/1303 and 1995/829.} for the words “unemployment benefit” there shall be substituted the words “a jobseeker’s allowance”.

(4) In regulation 7 (modification of contribution conditions for receiving benefit in certain circumstances, in respect of mariners employed on board foreign-going ships) for all the words preceding the words “because the contributor concerned” there shall be substituted the following words—
\begin{quotation}
“Where, on a claim for benefit, a contribution condition that the contributor concerned must in respect of the relevant past year have—
\begin{enumerate}\item[]
($a$) either paid or been credited with contributions of a relevant class and the earnings factor derived from those contributions must not be less than a specified multiple of that year’s lower earnings limit; or

($b$) either paid contributions or been credited with earnings as specified in section 2 of the Jobseekers Act 1995\footnote{\frenchspacing 1995 c. 18.}, and the earnings factor derived from earnings upon which contributions have been paid or from earnings credited must not be less than a specified multiple of that year’s lower earnings limit,
\end{enumerate}
cannot apart from this regulation be satisfied”.
\end{quotation}

(5) In regulation 9 (application of the Act and regulations) after the words “relating to benefits” there shall be inserted the words “,~or of the Jobseekers Act 1995 and regulations made thereunder”.

\subsection[22. Amendment of the Social Security (Overlapping Benefits) Regulations 1979]{Amendment of the Social Security (Overlapping Benefits) Regulations 1979}

22.—(1) The Social Security (Overlapping Benefits) Regulations 1979\footnote{\frenchspacing S.I. 1979/597.} shall be amended in accordance with the following provisions of this regulation.

(2) In regulation 2(1) (interpretation)—
\begin{enumerate}\item[]
($a$) after the definition of “child benefit” there shall be inserted the following definition—
\begin{quotation}
““contributory benefit” means any benefit payable under Part II of the Contributions and Benefits Act, and a contribution-based jobseeker’s allowance;”;
\end{quotation}

($b$) after the definition of “disablement pension” there shall be inserted the following definition—
\begin{quotation}
““the Jobseekers Act” means the Jobseekers Act 1995\footnote{\frenchspacing 1995 c. 18.};”;
\end{quotation}

($c$) in the definition of “personal benefit”\footnote{\frenchspacing Relevant amending instrument is S.I. 1980/1927.} after the words “dependency benefit” there shall be inserted the words “, and includes a contribution-based jobseeker’s allowance but not an income-based jobseeker’s allowance,”.
\end{enumerate}

(3) In regulation 4(1)($a$) (adjustment of personal benefit)\footnote{\frenchspacing Paragraph (1) was substituted by S.I. 1992/3194.} after the words “injuries benefits)” there shall be inserted the words “or under the Jobseekers Act”.

(4) In regulation 10(1) (adjustment of dependency benefit)\footnote{\frenchspacing Relevant amending instruments are S.I. 1980/1927, 1982/1173, 1983/186, 1991/387 and 1992/3194 and the Employment Act 1989 (c. 38), Schedule 5, paragraphs 1 and 4.} after sub-paragraph ($i$) there shall be added the following sub-paragraph—
\begin{quotation}
“($j$) a contribution-based jobseeker’s allowance,”.
\end{quotation}

(5) In regulation 14 (provisions for adjusting benefit for part of a week)\footnote{\frenchspacing Relevant amending instrument is S.I. 1995/829.}—
\begin{enumerate}\item[]
($a$) in paragraph (1)($a$) the words “and unemployment benefit” shall be omitted;

($b$) in paragraph (1)($b$) for the words “where maternity benefit or unemployment benefit” there shall be substituted the words “where maternity benefit”; and

($c$) paragraph (2) shall be omitted.
\end{enumerate}

(6) In regulation 16 (persons to be treated as entitled to benefit for certain purposes)—
\begin{enumerate}\item[]
($a$) after the words “under the Act” in the first place where they occur there shall be inserted the words “or under the Jobseekers Act”; and

($b$) after the words “made under it” there shall be inserted the words “,~or under the Jobseekers Act and regulations made under it,”.
\end{enumerate}

(7) In regulation 17 (prevention of double adjustments) after the words “under the Act” in each place where they occur there shall be inserted the words “or under the Jobseekers Act”.

(8) In paragraph 1 of Schedule 1\footnote{\frenchspacing Relevant amending instrument is S.I. 1995/829.} for the words “Unemployment benefit” there shall be substituted the words “A contribution-based jobseeker’s allowance”.

\subsection[23. Amendment of the Social Security (Payments on account, Overpayments and Recovery) Regulations 1988]{Amendment of the Social Security (Payments on account, Overpayments and Recovery) Regulations 1988}

23.—(1) The Social Security (Payments on account, Overpayments and Recovery) Regulations 1988\footnote{\frenchspacing S.I. 1988/664.} shall be amended in accordance with the following provisions of this regulation.

(2) In regulation 1(2) (citation, commencement and interpretation)—
\begin{enumerate}\item[]
($a$) in the definition of “benefit”\footnote{\frenchspacing Relevant amending instruments are S.I. 1988/1725, 1989/136 and 1995/829.} after the word “means” there shall be inserted the words “a jobseeker’s allowance and”;

($b$) after the definition of “Income Support Regulations” there shall be inserted the following definition—
\begin{quotation}
\begin{sloppypar}
““Jobseeker’s Allowance Regulations” means the Jobseeker’s Allowance Regulations 1996\footnote{\frenchspacing S.I. 1996/207.};”.
\end{sloppypar}
\end{quotation}
\end{enumerate}

(3) In regulation 7(1) (duplication and prescribed income)\footnote{\frenchspacing Paragraph (1) was substituted by S.I. 1993/650.}—
\begin{enumerate}\item[]
($a$) after the words “income support” in the first place where they occur there shall be inserted the words “and income-based jobseeker’s allowance”;

($b$) in sub-paragraph ($a$) after the words “Income Support Regulations” there shall be inserted the words “or, as the case may be, Part VIII of the Jobseeker’s Allowance Regulations”;

($c$) in sub-paragraph ($b$) after the words “Income Support Regulations” there shall be inserted the words “or, as the case may be, Chapter VIII of Part VIII of the Jobseeker’s Allowance Regulations”.
\end{enumerate}

(4) In regulation 16 (limitations on deductions from prescribed benefits)—
\begin{enumerate}\item[]
($a$) in paragraph (4) after the words “income support” there shall be inserted the words “or income-based jobseeker’s allowance”;

($b$) in paragraph (6) for the words from the beginning of the paragraph up to and including the words “the weekly amount” there shall be substituted the following words—
\begin{quotation}
“Where—
\begin{enumerate}\item[]
($a$) in the calculation of the income of a person to whom income support is payable, the amount of earnings or other income falling to be taken into account is reduced by paragraphs 4 to 9 of Schedule 8 to the Income Support Regulations (sums to be disregarded in the calculation of earnings) or paragraphs 15 and 16 of Schedule 9 to those Regulations (sums to be disregarded in the calculation of income other than earnings); or

($b$) in the calculation of the income of a person to whom income-based jobseeker’s allowance is payable, the amount of earnings or other income falling to be taken into account is reduced by paragraphs 5 to 12 of Schedule 6 to the Jobseeker’s Allowance Regulations (sums to be disregarded in the calculation of earnings) or paragraphs 15 and 17 of Schedule 7 to those Regulations (sums to be disregarded in the calculation of income other than earnings),
\end{enumerate}
the weekly amount”;
\end{quotation}

($c$) in paragraph (8)—
\begin{enumerate}\item[]
(i) in the definition of “personal allowance for a single claimant aged not less than 25” at the end there shall be added the words “or, in the case of a person who is entitled to income-based jobseeker’s allowance, the amount for the time being specified in paragraph 1(1)($e$) of column (2) of Schedule 1 to the Jobseeker’s Allowance Regulations;”;

(ii) in the definition of “specified benefit” the word “unemployment,” shall be omitted, and at the end there shall be added the words “,~or income-based jobseeker’s allowance”.
\end{enumerate}
\end{enumerate}

(5) In the provisions listed in paragraph (6), after the words “income support” in each place where they occur there shall be inserted the words “,~or income-based jobseeker’s allowance”.

(6) The provisions referred to in paragraph (5) are—
\begin{enumerate}\item[]
($a$) regulation 5(3) (offsetting prior payment against subsequent award);

($b$) regulation 8(2) (duplication and prescribed payments);

($c$) regulation 13($b$) (sums to be deducted in calculating recoverable amounts);

($d$) regulation 14(1) (quarterly diminution of capital)\footnote{\frenchspacing Relevant amending instrument is S.I. 1991/2742.};

($e$) regulation 15(2)($d$) (recovery by deduction from prescribed benefits);

($f$) regulation 17 (recovery from couples)\footnote{\frenchspacing Relevant amending instrument is S.I. 1991/2742.}.
\end{enumerate}

\subsection[24. Amendment of the Social Security (Recoupment) Regulations 1990]{Amendment of the Social Security (Recoupment) Regulations 1990}

24.  In regulation 2(1) of the Social Security (Recoupment) Regulations 1990 (relevant benefits)\footnote{\frenchspacing S.I. 1990/322; relevant amending instruments are S.I. 1991/2742, 1994/730 and 1995/829.} at the end there shall be added the following sub-paragraph—
\begin{quotation}
“($o$) jobseeker’s allowance.”.
\end{quotation}

\subsection[25. Amendment of the Social Security (Unemployment, Sickness and Invalidity Benefit) Regulations 1983]{Amendment of the Social Security (Unemployment, Sickness and Invalidity Benefit) Regulations 1983}

25.  In regulation 20 of the Social Security (Unemployment, Sickness and Invalidity Benefit) Regulations 1983\footnote{\frenchspacing S.I. 1983/1598; relevant amending instrument is S.I. 1995/829.} for the words “unemployment benefit” there shall be substituted the words “contribution-based jobseeker’s allowance”.

\subsection[26. Amendment of the Social Security (Widow’s Benefit and Retirement Pensions) Regulations 1979]{Amendment of the Social Security (Widow’s Benefit and Retirement Pensions) Regulations 1979}

26.  In regulation 4(2)($b$)(ii) of the Social Security (Widow’s Benefit and Retirement Pensions) Regulations 1979\footnote{\frenchspacing S.I. 1979/642.} (days to be treated as days of increment) for the words “unemployment benefit” in the second place where they occur there shall be substituted the words “a contribution-based jobseeker’s allowance”.

\subsection[27. Revocations]{Revocations}

27.  The regulations listed in Column 2 of the Schedule to these Regulations are hereby revoked to the extent specified in Column 3 of the Schedule to these Regulations.

\bigskip

Signed by authority of the Secretary of State for Social Security.

{\raggedleft
\emph{Roger Evans}\\*Parliamentary Under-Secretary of State,\\*Department of Social Security

}

14th May 1996

\bigskip

We consent to the making of regulation 24,

{\raggedleft
\emph{Simon Burns}\\*\emph{Michael Bates}\\*Two of the Lords Commissioners of Her Majesty’s Treasury

}

16th May 1996

\clearpage

\part[Schedule --- Revocations]{S C H E D U L E\\*Revocations}

\renewcommand\parthead{--- Schedule}

\begin{longtable}{p{50.0pt}p{179.0888pt}p{79.90654pt}}
\hline
\itshape Column 1 & \itshape Column 2 & \itshape Column 3\\
\raggedright Statutory Instrument Number&Statutory Instrument&Provision revoked\\
\hline
\endhead
\hline
\endlastfoot
1975/529&The Social Security (Mariners' Benefits) Regulations 1975&Regulation 8.\\
1975/563&\textls[50]{The Social Security Benefit (Persons} Abroad) Regulations 1975&Regulation 13B.\\
1977/343&The Social Security Benefit (Dependency) Regulations 1977&Regulation 13.\\
1980/827&The Social Security Benefit (Dependency) Amendment (No.\ 2) Regulations 1980&The whole Regulations.\\
1983/1598&\textls[25]{The Social Security (Unemployment,} Sickness and Invalidity Benefit) Regulations 1983&Regulations 2, 4 to 7, 7B, 9 to 14, 16, 19 and 23 to 28.\\
1984/551&\textls[25]{The Social Security (Unemployment,} Sickness and Invalidity Benefit) Amendment Regulations 1984&The whole Regulations.\\
1986/486&\textls[50]{The Social Security Benefit (Persons} Abroad) Amendment Regulations 1986&The whole Regulations.\\
1986/1011&\textls[25]{The Social Security (Unemployment,} Sickness and Invalidity Benefit) Amendment (No.\ 2) Regulations 1986&The whole Regulations.\\
1986/1375&The Social Security (Unemployment Benefit) and Supplementary Benefit Amendment Regulations 1986&Regulation 2.\\
1987/317&\textls[25]{The Social Security (Unemployment,} Sickness and Invalidity Benefit) Amendment Regulations 1987&The whole Regulations.\\
1988/689&\textls[25]{The Social Security (Unemployment,} Sickness and Invalidity Benefit) Amendment Regulations 1988&The whole Regulations.\\
1988/1674&\textls[25]{The Social Security (Unemployment,} Sickness and Invalidity Benefit) Amendment (No.\ 2) Regulations 1988&The whole Regulations.\\
1988/2119&\textls[25]{The Social Security (Unemployment,} Sickness and Invalidity Benefit) Amendment (No.\ 3) Regulations 1988&The whole Regulations.\\
1989/872&\textls[25]{The Social Security (Unemployment,} Sickness and Invalidity Benefit) Amendment Regulations 1989&Regulation 2(3).\\
1989/1324&\textls[25]{The Social Security (Unemployment,} Sickness and Invalidity Benefit) Amendment No.\ 2 Regulations 1989&Regulations 3 to 7, 9 and 10.\\
1989/2122&\textls[25]{The Social Security (Unemployment,} Sickness and Invalidity Benefit) Amendment No.\ 3 Regulations 1989&The whole Regulations.\\
1990/1487&\textls[25]{The Social Security (Unemployment,} Sickness and Invalidity Benefit) Amendment Regulations 1990&The whole Regulations.\\
1990/1549&The Social Security Benefits (Student Loans Miscellaneous Amendments) Regulations 1990&Regulation 6.\\
1991/387&The Enterprise (Scotland) Consequential Amendments Order 1991&\textls[25]{Article 6($b$) and} ($c$).\\
1992/247&The Social Security (Miscellaneous Provisions) Amendment Regulations 1992&Regulation 4(3).\\
1992/2913&\textls[25]{The Social Security (Unemployment,} Sickness and Invalidity Benefit) Amendment Regulations 1992&The whole Regulations.\\
1993/1754&\textls[25]{The Social Security (Unemployment,} Sickness and Invalidity Benefit) Amendment Regulations 1993&Regulation 3.\\
1994/2945&The Social Security (Incapacity Benefit—Increases for Dependants) Regulations 1994&Regulation 15(8).\\
1995/829&The Social Security (Incapacity Benefit) (Consequential and Transitional Amendments and Savings) Regulations 1995&\textls[25]{Regulation 17(3),} (5) to (8) and (10).\\
1995/1742&The Social Security Benefits (Miscellaneous Amendments) Regulations 1995&Regulation 2($f$).\\
1995/2192&\textls[25]{The Social Security (Unemployment,} Sickness and Invalidity Benefit) Amendment Regulations 1995&The whole Regulations.\\
\end{longtable}

\part{Explanatory Note}

\renewcommand\parthead{--- Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations further amend the regulations listed below. The amendments are consequential on the coming into force of the Jobseekers Act 1995, which replaces income support for the unemployed and unemployment benefit with jobseeker’s allowance. The Regulations replace references to unemployment benefit with references to jobseeker’s allowance, and add references to jobseeker’s allowance where the existing regulations refer to income support.

  The regulations amended by this Instrument are:
\begin{itemize}
\item the Child Benefit (General) Regulations 1976 (S.I. 1976/965);
\item the Child Support (Arrears, Interest and Adjustment of Maintenance Assessments) Regulations 1992 (S.I. 1992/1816);
\item the Child Support Fees Regulations 1992 (S.I. 1992/3094);
\item the Child Support (Maintenance Assessment Procedure) Regulations 1992 (S.I. 1992/1813);
\item the Child Support (Maintenance Assessments and Special Cases) Regulations 1992 (S.I. 1992/1815);
\item the Disability Working Allowance (General) Regulations 1991 (S.I. 1991/\hspace{0pt}2887);
\item the Family Credit (General) Regulations 1987 (S.I. 1987/1973);
\item the Social Security (Airmen’s Benefits) Regulations 1975 (S.I. 1975/494);
\item the Social Security (Attendance Allowance) Regulations 1991 (S.I. 1991/\hspace{0pt}1740);
\item the Social Security Benefit (Computation of Earnings) Regulations 1978 (S.I. 1978/1698);
\item the Social Security Benefit (Dependency) Regulations 1977 (S.I. 1977/343);
\item the Social Security (Benefit) (Married Women and Widows Special Provisions) Regulations 1974 (S.I. 1974/2010);
\item the Social Security (Benefit) Members of the Forces Regulations 1975 (S.I. 1975/493);
\item the Social Security Benefit (Persons Abroad) Regulations 1975 (S.I. 1975/\hspace{0pt}563);
\item the Social Security Benefit (Persons Residing Together) Regulations 1977 (S.I. 1977/956);
\item the Social Security (Disability Living Allowance) Regulations 1991 (S.I. 1991/2890);
\item the Social Security (Graduated Retirement Benefit) (No.\ 2) Regulations 1978 (S.I. 1978/393);
\item the Social Security (Incapacity Benefit—Increases for Dependants) Regulations 1994 (S.I. 1994/2945);
\item the Social Security (Incapacity for Work) (General) Regulations 1995 (S.I. 1995/311);
\item the Social Security (Mariners' Benefits) Regulations 1975 (S.I. 1975/529);
\item the Social Security (Overlapping Benefits) Regulations 1979 (S.I. 1979/\hspace{0pt}597);
\item the Social Security (Payments on account, Overpayments and Recovery) Regulations 1988 (S.I. 1988/664);
\item the Social Security (Recoupment) Regulations 1990 (S.I. 1990/322);
\item the Social Security (Unemployment, Sickness and Invalidity Benefit) Regulations 1983 (S.I. 1983/1598);
\item the Social Security (Widow’s Benefit and Retirement Pensions) Regulations 1979 (S.I. 1979/642).
\end{itemize}

  A number of regulations are revoked by this instrument. In particular, most of the Social Security (Unemployment, Sickness and Invalidity Benefit) Regulations 1983 are revoked. The revocations are listed in the Schedule to these Regulations.

  These Regulations are made under section 40 of the Jobseekers Act 1995 and are made before the end of the period of six months beginning with the date that provision came into force. Accordingly they are exempted by section 173(5)($a$) of the Social Security Administration Act 1992 from reference to the Social Security Advisory Committee and have not been so referred.

  These Regulations do not impose a charge on business.

\end{document}