\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Maintenance Bonus (Northern Ireland Reciprocal Arrangements) Regulations 1997}

\newcommand\regsnumber{1997/645}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I. 1997 No. 645}

\date{Made 6th March 1997\\Laid before Parliament 12th March 1997\\Coming into force 7th April 1997}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\begin{document}

\maketitle

\noindent
The Secretary of State for Social Security, in exercise of the powers conferred on him by section 29(3) and (4) of the Child Support Act 1995\footnote{\frenchspacing 1995 c. 34.}, and of all other powers enabling him in that behalf, hereby makes the following Regulations:


{\sloppy

\tableofcontents

}

\setcounter{secnumdepth}{-2}

\subsection[1. Citation, commencement and interpretation]{Citation, commencement and interpretation}

1.—(1) These Regulations may be cited as the Child Maintenance Bonus (Northern Ireland Reciprocal Arrangements) Regulations 1997 and shall come into force on 7th April 1997.

(2) In these Regulations “the Child Support Act” means the Child Support Act 1995.

\subsection[2. Adaptation of section 10 of the Child Support Act and regulations made under it]{Adaptation of section 10 of the Child Support Act and regulations made under it}

2.—(1) The provisions contained in the Memorandum of Arrangements set out in the Schedule to these Regulations shall have effect so far as the same relate to Great Britain.

(2) In particular and without prejudice to paragraph (1) above, any act, omission, event or other matter which is relevant for the purposes of Article 4 of the Child Support (Northern Ireland) Order 1995\footnote{\frenchspacing S.I. 1995/2702 (N.I. 13).} and regulations made under it is deemed to be an act, omission, event or other matter which is relevant for the purposes of section 10 of the Child Support Act (the child maintenance bonus) and regulations made under it.

(3) In section 10 of the Child Support Act and regulations made under it the references to—
\begin{enumerate}\item[]
“a child maintenance bonus” shall be construed as including references to a child maintenance bonus within the meaning of Article 4 of the Child Support (Northern Ireland) Order 1995;

“income support” shall be construed as including references to income support within the meaning of Part VII of the Social Security Contributions and Benefits (Northern Ireland) Act 1992\footnote{\frenchspacing 1992 c. 7.};

“jobseeker’s allowance” shall be construed as including references to jobseeker’s allowance within the meaning of Article 3 of the Jobseekers (Northern Ireland) Order 1995\footnote{\frenchspacing S.I. 1995/2705 (N.I. 15).};

“the Secretary of State” shall be construed as including references to the Department of Health and Social Services for Northern Ireland.
\end{enumerate}

\bigskip

Signed by authority of the Secretary of State for Social Security.

{\raggedleft
\emph{Andrew Mitchell}\\*Parliamentary Under-Secretary of State,\\*Department of Social Security

}

6th March 1997

\small

\part[Schedule --- Memorandum of arrangements relating to the provision made for child maintenance bonus in the United Kingdom between the Secretary of State for Social Security of the one part and the Department of Health and Social Services for Northern Ireland of the other part]{S C H E D U L E\\*Memorandum of arrangements relating to the provision made for child maintenance bonus in the United Kingdom between the Secretary of State for Social Security of the one part and the Department of Health and Social Services for Northern Ireland of the other part}

\renewcommand\parthead{--- Schedule}

1.  In this Memorandum—
\begin{enumerate}\item[]
“the provision made for Great Britain” means section 10 of the Child Support Act 1995 and regulations made under it; and

“the provision made for Northern Ireland” means Article 4 of the Child Support (Northern Ireland) Order 1995 and regulations made under it.
\end{enumerate}

\medskip

2.—(1) The provision made for Great Britain and the provision made for Northern Ireland shall operate as a single system within the United Kingdom.

(2) For the purposes of paragraph (1), all acts, omissions, events and other matters and in particular any application, declaration, direction, decision or order having effect for the provision made for Great Britain and having effect in that territory or for the provision made for Northern Ireland and having effect in that territory, shall have a corresponding effect for the purposes of the provision made for child maintenance bonus in the other territory.

(3) The provisions of this Memorandum shall not confer a right to double benefit.

\medskip

3.  The Secretary of State and the Department of Health and Social Services for Northern Ireland may from time to time determine the administrative procedures appropriate for the purposes of giving effect to this Memorandum.

\medskip

4.  The arrangements in this Memorandum shall come into effect on 7th April 1997 but either Party may terminate them by giving not less than six months’ notice in writing to the other.

\bigskip

Signed by authority of the Secretary of State for Social Security on the 18th February 1997.

{\raggedleft
\emph{Andrew Mitchell}\\*Parliamentary Under-Secretary of State,\\*Department of Social Security

}


\bigskip


Sealed with the Official Seal of the Department of Health and Social Services for Northern Ireland on the 20th February 1997.

{\raggedleft
\emph{A. F. Elliott}\\*Permanent Secretary

}

\part{Explanatory Note}

\renewcommand\parthead{--- Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations give effect in Great Britain to reciprocal arrangements relating to matters for which provision is made in Great Britain under section 10 of the Child Support Act 1995; this section provides for a “child maintenance bonus” to be payable to persons who are or have been entitled to certain social security benefits and have also been in receipt of child maintenance payments.

  The reciprocal arrangements are contained in the Memorandum set out in the Schedule to the Regulations and have been made between the Secretary of State for Social Security and the Department of Health and Social Services for Northern Ireland. The Regulations provide that relevant matters under the Northern Ireland legislation have a corresponding effect in respect of the provisions of section 10 of the Child Support Act 1995 and regulations made under it.

  These Regulations do not impose any costs on business.



\end{document}