\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Social Security and Child Support (Tax Credits) Consequential Amendments Regulations 1999}

\newcommand\regsnumber{1999/2566}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 1999 No.\ 2566}

\date{Made
13th September 1999\\
Laid before Parliament
14th September 1999\\
Coming into force
5th October 1999
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.57402pt}

\begin{document}

\maketitle

\noindent
The Secretary of State for Social Security, in exercise of the powers set out in Schedule 1 to this Instrument and of all other powers enabling him in that behalf, by this Instrument, which contains only regulations consequential upon the Tax Credits Act 1999\footnote{1999 c.\ 10.} and which is made before the end of the period of six months beginning with the coming into force of that Act\footnote{\emph{See} section 173(5)($b$)  of the Social Security Administration Act 1992 (c.\ 5).} and, in so far as they relate to housing benefit and council tax benefit, with the agreement of such organisations appearing to him to be representative of the authorities concerned that consultations should not be undertaken\footnote{\emph{See} section 176(2)($b$) of the Social Security Administration Act 1992 (c.\ 5).}, hereby makes the following Regulations: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation, commencement and interpretation]{Citation, commencement and interpretation}

1.---(1)  These Regulations may be cited as the Social Security and Child Support (Tax Credits) Consequential Amendments Regulations 1999.

(2) These Regulations shall come into force on 5th October 1999.

(3) In these Regulations, unless the context otherwise requires, “working families' tax credit” and “disabled person’s tax credit” shall be construed in accordance with section 1(1) of the Tax Credits Act 1999.

(4) In these Regulations, unless the context otherwise requires, a reference—
\begin{enumerate}\item[]
($a$) to a numbered regulation or Schedule is to the regulation in, or the Schedule to, these Regulations bearing that number;

($b$) in a regulation or Schedule to a numbered paragraph is to the paragraph in that regulation or Schedule bearing that number.
\end{enumerate}

\subsection[2. Amendments consequential on the renaming of family credit as working families' tax credit and of disability working allowance as disabled person’s tax credit]{Amendments consequential on the renaming of family credit as working families' tax credit and of disability working allowance as disabled person’s tax credit}

2.---(1)  Subject to paragraph (3), in the provisions mentioned in Part I of Schedule 2, for the words “family credit” wherever they occur, except where they appear in a reference to the title of the Family Credit (General) Regulations 1987\footnote{S.I.\ 1987/1973.}, there shall be substituted the words “working families' tax credit”.

(2) Subject to paragraph (3), in the provisions mentioned in Part II of Schedule 2, for the words “disability working allowance” wherever they occur, except where they appear in a reference to the title of the Disability Working Allowance (General) Regulations 1991\footnote{S.I.\ 1991/2887.}, there shall be substituted the words “disabled person’s tax credit”.

(3) In the provisions mentioned in Part III of Schedule 2—
\begin{enumerate}\item[]
($a$) for the definition of “disability working allowance” there shall be substituted the following definition—
\begin{quotation}
““disabled person’s tax credit” means a disabled person’s tax credit under section 129 of the Contributions and Benefits Act\footnote{\emph{See} section 1 of, and paragraphs 1 and 2($h$)  of Schedule 1 to, the Tax Credits Act 1999.};”; and
\end{quotation}

($b$) the following definition shall be inserted in the appropriate place—
\begin{quotation}
““working families' tax credit” means a working families' tax credit under section 128 of the Contributions and Benefits Act\footnote{\emph{See} section 1 of, and paragraphs 1 and 2($g$)  of Schedule 1 to, the Tax Credits Act 1999.};”.
\end{quotation}
\end{enumerate}

(4) In the provisions mentioned in Part IV of Schedule 2 for the words “the allowance” there shall be substituted the words “the credit”.

\subsection[3. Amendment of regulation 3 of the Social Fund (Recovery by Deductions from Benefits) Regulations 1988]{Amendment of regulation 3 of the Social Fund (Recovery by Deductions from Benefits) Regulations 1988}

3.  In regulation 3 of the Social Fund (Recovery by Deductions from Benefits) Regulations 1988\footnote{S.I.\ 1988/35.}—
\begin{enumerate}\item[]
($a$) for paragraph ($b$)  there shall be substituted the following paragraph—
\begin{quotation}
“($b$) family credit awarded with effect from a date falling before 5th October 1999;”; and
\end{quotation}

($b$) for paragraph ($dd$)\footnote{Sub-paragraph ($dd$)  was inserted by regulation 14 of S.I.\ 1991/2742.} there shall be substituted the following paragraph—
\begin{quotation}
“($dd$) disability working allowance awarded with effect from a date falling before 5th October 1999;”.
\end{quotation}
\end{enumerate}

\subsection[4. Amendment of Schedule 8 to the Social Security (Claims and Payments) Regulations 1987]{Amendment of Schedule 8 to the Social Security (Claims and Payments) Regulations 1987}

4.  In paragraph 2($b$)  of Schedule 8 to the Social Security (Claims and Payments) Regulations 1987\footnote{S.I.\ 1987/1968. Paragraph 2($b$)  is amended by regulation 28 of S.I.\ 1991/2741 and regulation 2(25) of S.I.\ 1996/1460.}, for the words “family credit or disability working allowance” there shall be substituted the words—
\begin{quotation}
“or payment in accordance with an award of family credit or disability working allowance which was awarded with effect from a date falling before 5th October 1999”.
\end{quotation}

\subsection[5. Amendment of regulation 1 of the Child Support (Maintenance Assessment Procedure) Regulations 1992]{Amendment of regulation 1 of the Child Support (Maintenance Assessment Procedure) Regulations 1992}

5.---(1)  Regulation 1(2) of the Child Support (Maintenance Assessment Procedure) Regulations 1992\footnote{S.I.\ 1992/1813.} shall be amended in accordance with the following paragraphs of this regulation.

(2) For the definition of “disability working allowance” there shall be substituted the following definition—
\begin{quotation}
““disability working allowance” means an award of disability working allowance under section 129 of the Social Security Contributions and Benefits Act 1992\footnote{1992 c.\ 4.} which was awarded with effect from a date falling before 5th October 1999;”.
\end{quotation}

(3) The following definition shall be inserted in the appropriate place—
\begin{quotation}
““family credit” means an award of family credit under section 128 of the Social Security Contributions and Benefits Act 1992 which was awarded with effect from a date falling before 5th October 1999;”.
\end{quotation}

(4) In the definition of “relevant benefit” for the words “family credit or disability working allowance” there shall be substituted the following words—
\begin{quotation}
    “or an award of family credit or disability working allowance which was awarded with effect from a date falling before 5th October 1999”. 
\end{quotation}

\subsection[6. Revocation and Saving of the Child Support (Compensation for Recipients of Family Credit and Disability Working Allowance) Regulations 1995]{Revocation and Saving of the Child Support (Compensation for Recipients of Family Credit and Disability Working Allowance) Regulations 1995}

6.  The Child Support (Compensation for Recipients of Family Credit and Disability Working Allowance) Regulations 1995\footnote{S.I.\ 1995/3263.} are revoked except that they shall continue to have effect in the case of an award of family credit or disability working allowance awarded with effect from a date falling before 5th October 1999. 

\bigskip

Signed 
by authority of the Secretary of State for Work and Pensions.

{\raggedleft
\emph{Hugh Bayley}\\*Parliamentary Under-Secretary of State,\\*Department of Social Security

}

%St Andrew's House, Edinburgh

%Dated
13th September 1999

\small

\part[Schedule 1 --- Provisions conferring powers exercised in making these Regulations]{Schedule 1\\*Provisions conferring powers exercised in making these Regulations}

\renewcommand\parthead{--- Schedule 1}

%\begin{tabulary}{\linewidth}{JJ}
\begin{longtable}{p{221.45412pt}p{144.56973pt}}
\hline
\endhead
\hline
\endlastfoot
Child Support Act 1991\footnote{1991 c.\ 48. Sections 43 and 51 were amended by the Social Security Administration Act 1992 (c.\ 5) and paragraphs 40 and 46 of Schedule 7 to the Social Security Act 1998 (c.\ 14); section 28E and Schedule 4B were inserted by the Child Support Act 1995 (c.\ 34); and section 52 was amended by the Child Support Act 1995.}	&section 28E(5)\\
	&section 42\\
	&section 43\\
	&section 51\\
	&section 52\\
	&section 54\\
	&paragraphs 5 and 7 of Schedule 1\\
	&Schedule 4B\\
Social Security Administration Act 1992	&section 5(1)\\
	&section 78(2)\\
	&section 189(1), (4) and (5)\\
Social Security Contributions and Benefits Act 1992	&section 22(5)\newline
	section 45A\footnote{1992 c.\ 4. Section 45A was inserted by section 127(1) of the Pensions Act 1995 (c.\ 26).}\\
	&section 122(1)\footnote{Section 122(1) is cited because of the definition of “prescribe”.}\\
\pagebreak[4]
	&section 123(1)($a$), ($d$)  and ($e$) \\
	&section 135(1)\\
	&section 136(3), (4) and (5)\\
	&section 137(1)\\
	&section 138\\
	&section 145(1)\\
	&section 175(1), (3) and (4)\\
Jobseekers Act 1995\footnote{1995 c.\ 18.}	&section 4(5)\\
	&section 12(4)($a$) \\
	&section 26(4)($j$) \\
	&section 36\\
Child Support Act 1995\footnote{1995 c.\ 34.}	&section 10\\
	&section 24\\
	&section 26(3)\\
%\end{tabulary}
\end{longtable}

\part{Schedule 2}

\section[Part I --- Provisions in which the words “family credit” are substituted by the words “working families' tax credit”]{\sloppy Part I\\*Provisions in which the words “family credit” are substituted by the words “working families' tax credit”}

\renewcommand\parthead{--- Schedule 2 Part I}

\begin{longtable}{p{234.78296pt}p{131.2158pt}}
\hline
\endhead
\hline
\endlastfoot
The Social Security (Credits) Regulations 1975\footnote{S.I.\ 1975/556. The relevant amending instruments are S.I.\ 1995/2558 and S.I.\ 1996/2367.}	&regulation 7C and the heading which precedes it\\
The Social Fund Maternity and Funeral Expenses (General) Regulations 1987\footnote{S.I.\ 1987/481.}&	regulation 5(1)($a$) \newline 
	regulation 6($b$) \\
	&regulation 7(1)($a$)(i)\\
The Income Support (General) Regulations 1987\footnote{S.I.\ 1987/1967. The relevant amending instrument is S.I.\ 1992/468.}	&regulation 42(2)($e$)\\ 
The Housing Benefit (General) Regulations 1987\footnote{S.I.\ 1987/1971. The relevant amending instruments are S.I.\ 1995/1339 and S.I.\ 1996/462.}	&regulation 43A(3)($c$)\footnote{The relevant amending instrument is S.I.\ 1991/235.}\\
	&regulation 43A(4)($c$)\footnote{The relevant amending instrument is S.I.\ 1991/235.}\\
	&Schedule 4, paragraph 58\\
The Council Tax Benefit (General) Regulations 1992\footnote{S.I.\ 1992/1814.}	&regulation 35(3)($c$) \\
	&regulation 35(4)($c$) \\
\pagebreak[4]
	&Schedule 4, paragraph 57\\
The Child Support (Maintenance Assessments and Special Cases) Regulations 1992\footnote{S.I.\ 1992/1815.}	&regulation 10A\footnote{Regulation 10A was inserted by regulation 11 of S.I.\ 1996/3196.} and the heading which precedes it\\
	&Schedule 1, paragraphs 2(1A), 5(5) and 7(2) to (5)\\
The Social Security (Effect of Family Credit on Earnings Factors) Regulations 1995\footnote{S.I.\ 1995/2559.}	&regulation 2\\
The Jobseeker’s Allowance Regulations 1996\footnote{S.I.\ 1996/207.}	&regulation 105(2)($d$) \\
The Child Support Departure Direction and Consequential Amendments Regulations 1996\footnote{S.I.\ 1996/2907.}	&regulations 9 and 12\\
The Social Security (Back to Work Bonus) (No.\ 2) Regulations 1996\footnote{S.I.\ 1996/2570.}	&regulation 21($c$) \\
The Social Security (Child Maintenance Bonus) Regulations 1996\footnote{S.I.\ 1996/3195.}	&regulation 14($c$) \\
\end{longtable}

\section[Part II --- Provisions in which the words “disability working allowance” are substituted by the words “disabled person's tax credit”]{Part II\\*Provisions in which the words “disability working allowance” are substituted by the words “disabled person's tax credit”}

\renewcommand\parthead{--- Schedule 2 Part II}

\begin{longtable}{p{235.84389pt}p{130.1644pt}}
\hline
\endhead
\hline
\endlastfoot
The Social Security (Credits) Regulations 1975\footnote{S.I.\ 1975/556.}	&regulation 7B and the heading which precedes it\\
&	regulation 9($c$)(i)\\
The Social Fund Maternity and Funeral Expenses (General) Regulations 1987\footnote{S.I.\ 1987/481.}	&regulation 5(1)($a$) \newline
	regulation 6($c$) \\
	&regulation 7(1)($a$)(i)\\
The Income Support (General) Regulations 1987\footnote{S.I.\ 1987/1967. The relevant amending instruments are S.I.\ 1991/2742 and S.I.\ 1992/468.}	&regulation 42(2)($f$) \\
	&Schedule 2, paragraph 12(1)($a$)(i)\\
The Housing Benefit (General) Regulations 1987\footnote{S.I.\ 1987/1971. The relevant amending instruments are S.I.\ 1995/1339 and S.I.\ 1996/462.}	&regulation 43A(3)($e$)\footnote{The relevant amending instrument is S.I.\ 1992/2148.}\\
	&regulation 43A(4)($e$)\footnote{The relevant amending instrument is S.I.\ 1992/2148.}\\
	&Schedule 2, paragraph 12(1)($a$)(i)\footnote{The relevant amending instrument is S.I.\ 1991/2742.}\\
	&Schedule 4, paragraph 57\\
\pagebreak[4]
The Council Tax Benefit (General) Regulations 1992	&regulation 35(3)($e$) \\
	&regulation 35(4)($e$) \\
	&Schedule 1, paragraph 13(1)($a$)(i)\\
	&Schedule 4, paragraph 56\\
The Child Support (Maintenance Assessments and Special Cases) Regulations 1992\footnote{S.I.\ 1992/1815.}	&regulation 10A and the heading which precedes it\\
	&Schedule 1, paragraphs 2(1A), 5(5)\\
	&Schedule 4, paragraph ($a$)(xi)\\
The Social Security (Effect of Family Credit on Earnings Factors) Regulations 1995\footnote{S.I.\ 1995/2559.}	&regulation 2\\
The Jobseeker’s Allowance Regulations 1996	&regulation 105(2)($d$) \\
	&Schedule 1, paragraph 14(1)($a$) \\
The Child Support Departure Direction and Consequential Amendments Regulations 1996	&regulations 9 and 12\\
The Social Security (Back to Work Bonus) (No.\ 2) Regulations 1996	&regulation 21($d$) \\
The Social Security (Child Maintenance Bonus) Regulations 1996	&regulation 14($d$) \\
\end{longtable}

\section[Part III --- Provisions in which the definitions of “working families' tax credit” and “disabled person's tax credit” are substituted or inserted]{\sloppy Part III\\*Provisions in which the definitions of “working families' tax credit” and “disabled person's tax credit” are substituted or inserted}

\renewcommand\parthead{--- Schedule 2 Part III}

%\begin{tabulary}{\linewidth}{JJ}
\begin{longtable}{p{311.51366pt}p{54.49594pt}}
\hline
\endhead
\hline
\endlastfoot
The Social Security (Credits) Regulations 1975\footnote{S.I.\ 1975/556. The relevant amending instruments are S.I.\ 1995/829, S.I.\ 1995/2558 and S.I.\ 1996/2367.}&	regulation 2(1)\\
The Income Support (General) Regulations 1987	&regulation 2(1)\\
The Housing Benefit (General) Regulations 1987	&regulation 2(1)\\
The Council Tax Benefit (General) Regulations 1992	&regulation 2(1)\\
The Child Support (Maintenance Assessments and Special Cases) Regulations 1992	&regulation 1(2)\\
The Jobseeker’s Allowance Regulations 1996	&regulation 1(3)\\
%\end{tabulary}
\end{longtable}

\section[Part IV --- Provisions in which the words “the allowance” are substituted by the words “the credit”]{Part IV\\*Provisions in which the words “the allowance” are substituted by the words “the credit”}

\renewcommand\parthead{--- Schedule 2 Part IV}

\begin{longtable}{p{167.13934pt}p{198.86624pt}}
\hline
\endhead
\hline
\endlastfoot
The Housing Benefit (General) Regulations 1987	&Schedule 3, paragraph 16
	sub-paragraphs (1)($b$)  and (4)($c$)(ii)\footnote{Paragraph 16 of Schedule 3 was inserted by regulation 5 of S.I.\ 1999/920.}\\
	&Schedule 4, paragraph 57\\
The Council Tax Benefit (General) Regulations 1992	&Schedule 3, paragraph 16
	sub-paragraphs (1)($b$)  and (4)($c$)(ii)\footnote{Paragraph 16 of Schedule 3 was inserted by regulation 6 of S.I.\ 1999/920.}\\
&	Schedule 4, paragraph 56\\
\end{longtable}

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations are made in consequence of provisions in the Tax Credits Act 1999 (c.\ 10) (“the Act”) which transfer functions relating to family credit and disability working allowance from the Secretary of State for Social Security to the Treasury and the Inland Revenue on 5th October 1999. The Act also makes provision for the renaming of family credit and disability working allowance as working families' tax credit and disabled person’s tax credit respectively as from 5th October 1999.

The Regulations are made before the end of the period of six months beginning with the coming into force of the relevant provisions in the Act and are therefore exempted from the requirement in section 172(1) of the Social Security Administration Act 1992 (c.\ 5) to refer proposals to make these Regulations to the Social Security Advisory Committee and are made without reference to the Committee.

Regulation 1 provides for citation, commencement and interpretation.

Regulations 2 to 5 make amendments consequential on the renaming of family credit as working families' tax credit and of disability working allowance as disabled person’s tax credit and provide for transitional arrangements consequential on the transfer.

Regulation 6 provides for the revocation of the Child Support (Compensation for Recipients of Family Credit and Disability Working Allowance) Regulations 1995 with a saving for awards of family credit and disability working allowance made before the transfer.

These Regulations do not impose a charge on business. 

\end{document}