\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support (Miscellaneous Amendments) (No.\ 2) Regulations 1998}

\newcommand\regsnumber{1998/2799}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I. 1998 No. 2799}

\date{Made 16th November 1998\\Laid beford Parliament 16th November 1998\\Coming into force 7th December 1998}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.57402pt}

\begin{document}

\maketitle

\noindent
The Secretary of State for Social Security, in exercise of the powers conferred by sections 16, 21, 51, 52(4) and 54 of the Child Support Act 1991\footnote{\frenchspacing 1991 c. 48. Section 16 was substituted by section 40 of, and section 51 was amended by paragraph 46 of Schedule 7 to, the Social Security Act 1998 (c. 14). Section 54 is cited because of the meaning ascribed to the word “prescribed”. There are savings which are relevant to these Regulations in the Social Security Act 1998 (Commencement No. 2) Order 1998 (S.I. 1998/2780).} and of all other powers enabling him in that behalf, after consultation with the Council on Tribunals in accordance with section 8 of the Tribunals and Inquiries Act 1992\footnote{\frenchspacing 1992 c. 53.}, hereby makes the following Regulations:

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation, commencement and interpretation]{Citation, commencement and interpretation}

1.—(1) These Regulations may be cited as the Child Support (Miscellaneous Amendments) (No.\ 2) Regulations 1998 and shall come into force on 7th December 1998.

(2) In these Regulations—
\begin{enumerate}\item[]
“the Act” means the Child Support Act 1991; and

“the Maintenance Assessment Procedure Regulations” means the Child Support (Maintenance Assessment Procedure) Regulations 1992\footnote{\frenchspacing S.I. 1992 No. 1813. Relevant amending instruments are S.I. 1993/913, 1995/123, 1995/1045, 1995/3261, and 1996/1945.}.
\end{enumerate}

\subsection[2. Amendment of the Maintenance Assessment Procedure Regulations]{Amendment of the Maintenance Assessment Procedure Regulations}

2.—(1) The Maintenance Assessment Procedure Regulations shall be amended in accordance with the following paragraphs of this regulation.

(2) Parts III and IV of the Maintenance Assessment Procedure Regulations shall be amended as follows:—
\begin{enumerate}\item[]
($a$) in regulation 8B—
\begin{enumerate}\item[]
(i) in paragraph (1) there shall be inserted after “child support officer”, the words “in respect of a maintenance assessment the effective date of which is on or before 8th December 1996”, and

(ii) in paragraph (4) for “section 16 or” there shall be substituted—
\begin{quotation}
“section 16 of the Act of a maintenance assessment the effective date of which is on or before 8th December 1996 or a review under section”,
\end{quotation}
\end{enumerate}

($b$) in regulation 9 after “16” in sub-paragraph (iii) of paragraph (1) and in paragraphs (15) and (16) there shall be inserted—
\begin{quotation}
“of the Act of a maintenance assessment the effective date of which is on or before 8th December 1996 or a review under section”,
\end{quotation}

($c$) in paragraph (5) of regulation 9A for “sections 16 and” there shall be substituted “section”,

($d$) in regulation 10—
\begin{enumerate}\item[]
(i) in sub-paragraph ($a$) of paragraph (1) after “16” there shall be inserted “of the Act of a maintenance assessment the effective date of which is on or before 8th December 1996 or a review under section”,

(ii) the following shall be inserted after paragraph (1)—
\begin{quotation}
“(1A) Where the Secretary of State makes a fresh maintenance assessment on a revision under section 16 of the Act he shall immediately notify the relevant persons, so far as that is reasonably practicable, of the amount of the child support maintenance under that assessment.

(1B) Where a fresh Category A, Category C or Category D interim maintenance assessment is made, on a revision under section 16 of the Act, a notification under paragraph (1A) shall set out, in relation to that interim maintenance assessment, the maintenance requirement and the effective date and shall include information as to sections 16 to 19(1) of the Act.

(1C) Where a fresh maintenance assessment is made on a revision under section 16 of the Act, a notification under paragraph (1A) shall include information as to sections 16, 17 and 18 of the Act.”,
\end{quotation}

(iii) in paragraph (2A) for “section 16 or” there shall be substituted “section 16 of the Act of a maintenance assessment the effective date of which is on or before 8th December 1996 or a review under section”,

(iv) in sub-paragraph ($a$) of paragraph (4) for the words “sections 16, 17 and 18 of the Act” there shall be substituted “of a maintenance assessment the effective date of which is on or before 8th December 1996, sections 17 and 18 of the Act”,

(v) in sub-paragraph ($b$) of paragraph (4) for “sections 16 and” there shall be substituted “section”,

(vi) in sub-paragraphs ($d$) and ($e$) of paragraph (4) “16” shall be deleted,

(vii) in paragraph (5) for the words “section 16 or 19(1) of the Act” there shall be substituted “section 16 of the Act of a maintenance assessment the effective date of which is on or before 8th December 1996 or under section 19(1) of the Act”, and for “sections 16 and” there shall be substituted “section”, and

(viii) in paragraph (6) for “sections 16” there shall be substituted “section”,
\end{enumerate}

($e$) after paragraph (2) of regulation 11 there shall be inserted—
\begin{quotation}
“(2A) Where the Secretary of State refuses an application for a revision of a decision under section 16 of the Act, he shall immediately notify the applicant, so far as that is reasonably practicable, and shall give the reasons for his refusal in writing.”, and
\end{quotation}

($f$) after paragraph (7) of regulation 17 there shall be inserted—
\begin{quotation}
“(8) Nothing in this Part requires a review of a maintenance assessment which has not been in force for 104 weeks before 7th December 1998.”.
\end{quotation}
\end{enumerate}

(3) After Part V (periodical reviews) of the Maintenance Assessment Procedure Regulations there shall be inserted the following—
\begin{quotation}
\section*{“Part VA\\*Revision of decisions}

\subsection*{Circumstances in which decisions may be revised}

18A.—(1) An application may be made for a revision of, or the Secretary of State may decide on his own initiative to revise, a decision described in paragraph (2) and referred to in this part of these Regulations as a “relevant decision”.

(2) A decision for the purposes of paragraph (1) is a maintenance assessment made under section 11 (maintenance assessments) or 12 (interim maintenance assessments) of the Act in respect of which—
\begin{enumerate}\item[]
($a$) an application for a review has been made under section 18 (reviews of decisions of child support officers) of the Act, and

($b$) an appeal to a child support appeal tribunal has been made under section 20 (appeals) of the Act either on a review under section 18 of the Act or in respect of a refusal of such a review.
\end{enumerate}

\subsection*{Procedure}

18B.—(1) Where notice of an appeal referred to in regulation 18A(2)($b$) has been received by the Secretary of State in accordance with regulations made under section 21 (child support appeal tribunals) of the Act he shall acknowledge receipt in writing and notify the other relevant persons in writing of the receipt and such acknowledgement or notification shall include information as to the ability for the decision to be revised under section 16 of the Act, including any time limits for such a revision.

(2) An application under section 16(1)($b$) of the Act for revision of a relevant decision may be made by any party to the appeal referred to in regulation 18A(2)($b$) and shall be made in writing to the Secretary of State within the period of 28 days beginning with the date of receipt of the acknowledgement or notification, as the case may be, referred to in paragraph (1).

(3) Where an application is received by the Secretary of State under paragraph (2), or where he is on his own initiative considering whether to revise a relevant decision, he shall consider whether in his opinion the relevant decision was made in ignorance of a fact or based on a mistake as to a fact or was wrong in law.

(4) The Secretary of State shall give 14 days' notice of his intention to revise the decision to the relevant persons and invite representations, either in person or in writing, from the relevant persons on any matter relating to the relevant decision within 14 days of the date on which the notice of the intention to revise was given.

(5) Subject to paragraph (6), where the Secretary of State—
\begin{enumerate}\item[]
($a$) does not within 14 days of the date on which notice was given receive a request from the relevant person to make representations in person,

($b$) receives a request by the date referred to in paragraph ($a$) and arranges for an appointment but that appointment is not kept, or

($c$) does not receive written representations from a relevant person within 14 days of the date referred to in paragraph ($a$),
\end{enumerate}
he may revise the decision in the absence of such representations from that person.

(6) Where the Secretary of State is satisfied that there was good reason for failure to keep an appointment, he shall provide for a further opportunity for the making of representations by the relevant person concerned before he revises the relevant decision.

\subsection*{Effective date}

18C.  Where on a revision of a relevant decision in the opinion of the Secretary of State the effective date of that decision was based on ignorance of a fact or on a mistake as to a fact or was wrong in law, the effective date of that revised decision shall be a date determined by the Secretary of State as being the date which should have been the effective date of the relevant decision.

\subsection*{Lapse of appeals}

18D.—(1) In the circumstances described in paragraph (2) an appeal referred to in regulation 18A(2)($b$) shall not lapse if the relevant decision is revised under section 16 of the Act before the appeal is determined.

(2) The circumstances for the purposes of paragraph (1) are where—
\begin{enumerate}\item[]
($a$) in the case of an appeal brought by an absent parent, either the maintenance assessment under the revision is more than the maintenance assessment under the relevant decision or the effective date of the revision is prior to the effective date of the relevant decision; or

($b$) in the case of an appeal brought by a person with care, either the maintenance assessment under the revision is less than the maintenance assessment under the relevant decision or the effective date of the revision is later than the effective date of the relevant decision.”.
\end{enumerate}
\end{quotation}

(4) Part VIII of the Maintenance Assessment Procedure Regulations shall be amended as follows—
\begin{enumerate}\item[]
($a$) in paragraphs (1) and (2) of regulation 31 after “a review under section 16 of the Act” there shall be inserted “of a maintenance assessment the effective date of which is on or before 8th December 1996”,

($b$) in paragraph (1) of regulation 31C after “a review” there shall be inserted “by a child support officer of a maintenance assessment the effective date of which is on or before 8th December 1996, or a revision by the Secretary of State after 6th December 1998,” and

($c$) in paragraph (3) of regulation 33 after “a review under section 16” there shall be inserted “of the Act by a child support officer of a maintenance assessment the effective date of which is on or before 8th December 1996, or a revision by the Secretary of State under that section after 6th December 1998, or a review under section”.
\end{enumerate}

\subsection[3. Amendment of other Regulations]{Amendment of other Regulations}

3.—(1) The Child Support Departure Direction and Consequential Amendments Regulations 1996\footnote{\frenchspacing S.I. 1996 No. 2907. Regulation 11A was inserted by S.I. 1998/58, regulation 10.}, shall be amended as follows—
\begin{enumerate}\item[]
($a$) in paragraph ($b$) of regulation 11A for “reviewed under section 16” there shall be substituted “in the case of a maintenance assessment the effective date of which is on or before 8th December 1996, reviewed by a child support officer under section 16 of the Act, or, in the case of any assessment, revised by the Secretary of State under section 16 of the Act after 6th December 1998, or reviewed under section”, and

($b$) in paragraph (1) of regulation 33 and paragraph (6) of regulation 41 after “16” there shall be inserted “by a child support officer of a maintenance assessment the effective date of which is on or before 8th December 1996 or a revision by the Secretary of State under that section after 6th December 1998, or a review under section”.
\end{enumerate}

(2) In paragraph (2) of regulation 10 of the Child Support (Arrears, Interest and Adjustment of Maintenance Assessments) Regulations 1992\footnote{\frenchspacing S.I. 1992 No. 1816. Regulation 10(2) was amended by S.I. 1996/2907, regulation 62.} for “reviewed under section 16” there shall be substituted “in the case of a maintenance assessment the effective date of which is on or before 8th December 1996, reviewed by a child support officer under section 16 of the Act, or, in the case of any assessment, revised by the Secretary of State under section 16 of the Act after 6th December 1998, or reviewed under section”.

(3) In sub-paragraphs ($a$)(i) and (ii) of regulation 11(4) of the Child Support (Collection and Enforcement) Regulations 1992\footnote{\frenchspacing S.I. 1992 No. 1989.} after “16” there shall be inserted “by a child support officer of a maintenance assessment the effective date of which is on or before 8th December 1996 or a revision by the Secretary of State under that section after 6th December 1998, or a review under section”.

\bigskip

Signed 
by authority of the Secretary of State for Social Security.

{\raggedleft
\emph{P. Hallis}\\*Parliamentary Under-Secretary of State,\\*Department of Social Security

}

16th November 1998

\small

\part{Explanatory Note}

\renewcommand\parthead{--- Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations make provision for revision of decisions under section 16 of the Child Support Act 1991 (“the 1991 Act”). Section 16 was substituted by section 40 of the Social Security Act 1998.

  Decisions which can be revised by the Secretary of State are described in the new regulation 18A of the new Part VA which is inserted into the Child Support (Maintenance Assessment Procedure) Regulations (S.I. 1992 No.\ 1813) (“the Maintenance Assessment Procedure Regulations”). They are maintenance assessments under section 11 or 12 of the 1991 Act which have been reviewed under section 18 of that Act and are subject to appeal under section 20 of that Act. Revision under section 16 offers an alternative route to resolving a dispute in these cases. The new regulation 18B inserted into the Maintenance Assessment Procedure Regulations provides that an application for a revision must be made within 28 days of notification or acknowledgement from the Secretary of State of receipt of notice of the appeal; the application must be made to the Secretary of State. The Secretary of State may also revise a decision on his own initiative.

  The inserted regulation 18C sets out the circumstances in which a revised decision is to take effect from a date other than the date of the original decision. This is where the effective date of the original decision is considered to have been wrong.

  The inserted regulation 18D provides that the appeal against the decision of the child support officer is not to lapse under section 16(6) of the 1991 Act where the decision is revised under section 16 before the appeal is determined where the revised decision is a less advantageous decision so far as the appellant is concerned either as regards the amount of the assessment or its effective date.

  Regulations 2(2) and (4) make consequential amendments to the Maintenance Assessment Procedure Regulations and make savings for assessments the effective date of which is at least 104 weeks before the coming into force of these regulations. These are assessments in respect of which a review would have become due under section 16 of the 1991 Act before the new section 16 was introduced.

  Regulation 3 contains consequential amendments and savings in relation to the Child Support Departure Direction and Consequential Amendments Regulations 1996 (S.I. 1996 No.\ 2907), the Child Support (Arrears, Interest and Adjustment of Maintenance Assessments) Regulations 1992 (S.I. 1992 No.\ 1816) and the Child Support (Collection and Enforcement) Regulations 1992 (S.I. 1992 No.\ 1989).

  These Regulations do not impose any costs on business.

\end{document}