\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Tax Credits (Decisions and Appeals) (Amendment) Regulations 1999}

\newcommand\regsnumber{1999/2570}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I. 1999 No. 2570}

\date{Made
14th September 1999\\
Laid before Parliament
14th September 1999\\
Coming into force
5th October 1999
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.57402pt}

\begin{document}

\maketitle

\noindent
The Commissioners of Inland Revenue, in exercise of the powers set out in the Schedule to this instrument, and after consultation with the Council on Tribunals in accordance with section 8 of the Tribunals and Inquiries Act 1992\footnote{\frenchspacing 1992 c. 53; the Tribunals and Inquiries Act 1992 was relevantly amended by paragraph 121 of Schedule 7 to the Social Security Act 1998 (c. 14).}, hereby make the following Regulations: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation, commencement and effect]{Citation, commencement and effect}

1.---(1)  These Regulations may be cited as the Tax Credits (Decisions and Appeals) (Amendment) Regulations 1999 and shall come into force on 5th October 1999 immediately after the coming into force of section 2(1)($c$)  of the Tax Credits Act 1999.

(2) These Regulations have effect—
\begin{enumerate}\item[]
($a$) with respect only to tax credit, and

($b$) with respect to award periods of tax credit commencing on or after 5th October 1999.
\end{enumerate}

\subsection[2. Interpretation]{Interpretation}

2.  In these Regulations unless the context otherwise requires—
\begin{enumerate}\item[]
“the principal Regulations” means the Social Security and Child Support (Decisions and Appeals) Regulations 1999\footnote{\frenchspacing S.I. 1999/991; relevant amending instruments are S.I. 1999/1623 and 1999/1662 (C. 47).} and “regulation” means a regulation of the principal Regulations;

“tax credit” means working families' tax credit or disabled person’s tax credit, construing those terms in accordance with section 1(1) of the Tax Credits Act 1999.
\end{enumerate}

\subsection[3--27. Amendments to the principal Regulations]{Amendments to the principal Regulations}

3.  In regulation 1(2)($d$)  for the words “family credit and disability working allowance” there shall be substituted the words “working families' tax credit and disabled person’s tax credit”.

\medskip

4.  In regulation 1(3)—
\begin{enumerate}\item[]
($a$) in paragraph ($a$)  of the definition of “the date of notification” after the words “Secretary of State” there shall be inserted the words “or an officer of the Board”;

($b$) in the definition of “party to the proceedings” after the words “Secretary of State” there shall be inserted the words “or, as the case may be, the Board or an officer of the Board,”;

($c$) after the definition of “referral” there shall be inserted the following definition—
\begin{quotation}
““tax credit” means working families' tax credit or disabled person’s tax credit, construing those terms in accordance with section 1(1) of the Tax Credits Act 1999;”.
\end{quotation}
\end{enumerate}

\medskip

5.  In regulation 2—
\begin{enumerate}\item[]
($a$) in paragraph ($a$)—
\begin{enumerate}\item[]
(i) after the words “Secretary of State”, where those words first occur, there shall be inserted the words “or to an officer of the Board”;

(ii) after the words “Secretary of State”, where those words secondly occur, there shall be inserted the words “or by an officer of the Board”;
\end{enumerate}

($b$) in paragraph ($b$)—
\begin{enumerate}\item[]
% Reg 5(b)(i) inserted (14.2.00) by SI 2000/127 reg 2(a)
(i) after the words “Secretary of State”, where those words first occur, there shall be inserted the words “or of an officer of the Board”;

(ii) for the words “or to an officer”, there shall be substituted the words “or an officer”;

(iii) after the words “Secretary of State”, where those words secondly occur, there shall be inserted the words “or an officer of the Board”.
\end{enumerate}
\end{enumerate}

\amendment{
Reg. 5(b)(i) inserted (14.2.00) by the Tax Credits (Decisions and Appeals) (Amendment) Regulations 2000 reg. 2(a).}

\medskip

6.---(1)  Regulation 3 shall be amended as follows.

(2) In paragraphs (1), (2) and (7) to (9), after the words “Secretary of State”, wherever occurring, there shall be inserted the words “or the Board or an officer of the Board”.

(3) In paragraphs (1) and (2) after the word “he” there shall be inserted the words “or they”, and in paragraph (1) after the word “him” there shall be inserted the words “or them”.

(4) In paragraph (5)\footnote{\frenchspacing Regulation 3(5) was amended by regulation 2 of S.I. 1999/1623.}—
\begin{enumerate}\item[]
($a$) for the words “Secretary of State”, in the first place where they occur, there shall be substituted the words “Board or an officer of the Board”;

($b$) for sub-paragraph ($b$)  there shall be substituted the following sub-paragraph—
\begin{quotation}
“($b$) which was made in ignorance of, or was based on a mistake as to, some material 
fact,”;
\end{quotation}

($c$) for the words “at any time by the Secretary of State” there shall be substituted the words “by the Board or an officer of the Board at any time not later than the end of the period of six years immediately following the date of the decision or, where ignorance of the material fact referred to in sub-paragraph ($b$)  was caused by the fraudulent or negligent conduct of the claimant, not later than the end of the period of twenty years immediately following the date of the decision.”
\end{enumerate}

(5) In paragraph (10) after the words “Secretary of State” there shall be inserted the words “or the Board”.

(6) In paragraph (11)\footnote{\frenchspacing Regulation 3(11) was amended by regulation 3(3)($b$) of S.I. 1999/1662 (C. 47).} after sub-paragraph ($d$)  there shall be added
\begin{quotation}
“or

($e$) in the case of a person who has claimed working families' tax credit or disabled person’s tax credit, a Tax Credits Office, the address of which is indicated on the notification of the original decision.”
\end{quotation}

\medskip

7.  In regulation 4(4) and (5) after the words “Secretary of State” there shall be inserted the words “or the Board or an officer of the Board”.

\medskip

8.  In regulation 5 after the words “Secretary of State” there shall be inserted the words “or the Board or an officer of the Board”.

\medskip

9.---(1)  Regulation 6 shall be amended as follows.

(2) In paragraph (2)\footnote{\frenchspacing Paragraph (2) was amended by regulation 3 of S.I. 1999/1623.}—
\begin{enumerate}\item[]
($a$) after the words “Secretary of State's” there shall be inserted the words “or the Board's”;

($b$) in sub-paragraph ($b$)—
\begin{enumerate}\item[]
(i) after the words “Secretary of State”, in the first place where they occur, there shall be inserted the words “or the Board or an officer of the Board”;

(ii) after the words “Secretary of State” in paragraph (ii)  there shall be inserted, in each place where they occur, the words “or the Board”;

(iii) after the word “his” in paragraph (ii)  there shall be inserted the words “or their”;
\end{enumerate}

($c$) in sub-paragraph ($e$)  after the words “Secretary of State” there shall be inserted the words “or the Board or an officer of the Board”.
\end{enumerate}

(3) In paragraph (3) after the words “Secretary of State” there shall be inserted the words “or the Board or an officer of the Board”.

(4) In paragraph (4)—
\begin{enumerate}\item[]
($a$) after the words “Secretary of State requires” there shall be inserted the words “or the Board require”;

($b$) after the word “he” there shall be inserted the words “or they”;

($c$) in sub-paragraph ($a$)  after the words “Secretary of State” there shall be inserted the words “or the Board”.
\end{enumerate}

(5) In paragraph (5) after the words “Secretary of State” there shall be inserted the words “or the Board”.

\medskip

10.  In regulation 7(5) after the words “Secretary of State supersedes” there shall be inserted the words “or the Board supersede”.

\medskip

11.  In regulation 8—
\begin{enumerate}\item[]
($a$) in paragraph (4) after the words “Secretary of State is satisfied” there shall be inserted the words “or the Board are satisfied”;

($b$) in paragraph (5) after the words “Secretary of State” there shall be inserted the words “or the Board”.
\end{enumerate}

\medskip

12.---(1)  Regulation 16 shall be amended as follows.

(2) In paragraph (1) after the words “Secretary of State” there shall be inserted the words “or the Board”.

(3) In paragraph (3)—
\begin{enumerate}\item[]
($a$) in sub-paragraph ($a$)—
\begin{enumerate}\item[]
(i) after the words “Secretary of State” there shall be inserted the words “or the Board”;

(ii) in paragraph (iv) after the word “him” there shall be inserted the words “or them”;
\end{enumerate}

($b$) in sub-paragraph ($b$)  after the words “Secretary of State” there shall be inserted the words “or the Board”.
\end{enumerate}

(4) In paragraph (4)—
\begin{enumerate}\item[]
($a$) after the words “Secretary of State certifies” there shall be inserted the words “or the Board certify”;

($b$) after the words “he proposes” there shall be inserted the words “or they propose”.
\end{enumerate}

\medskip

13.  For regulations 17 and 18 there shall be substituted the following regulations—
\begin{quotation}
\subsection*{“Provision of information or evidence}

17.---(1)  This regulation applies where the Board require information or evidence for a determination whether a decision awarding tax credit should be—
\begin{enumerate}\item[]
($a$) revised under section 9; or

($b$) superseded under section 10.
\end{enumerate}

(2) The relevant person shall furnish such certificates, documents, information and evidence as may be required by the Board for the purposes of paragraph (1), and shall do so within one month of being required to do so or such longer period as the Board may consider reasonable.

(3) In paragraph (2) “the relevant person” means any of the following—
\begin{enumerate}\item[]
($a$) the claimant concerned;

($b$) where the tax credit could have been claimed by either of two partners or where entitlement to or the amount of the tax credit was affected or liable to be affected by the circumstances of either partner, the partner other than the claimant;

($c$) the employer of the claimant or, where sub-paragraph ($b$)  applies, the employer of the partner other than the claimant.
\end{enumerate}

(4) Where the claimant or any partner of the claimant is aged not less than 60 and is a member of, or a person deriving entitlement to a pension under, a personal pension scheme, or is a party to, or a person deriving entitlement to a pension under, a retirement annuity contract, the claimant shall, where the Board so require and within one month of being required to do so or such longer period as the Board may consider reasonable, furnish the following information—
\begin{enumerate}\item[]
($a$) the name and address of the pension fund holder;

($b$) such other information, including any reference number or policy number, as is needed to enable the personal pension scheme or retirement annuity contract to be identified.
\end{enumerate}

\pagebreak[3]

(5) A pension fund holder to whom paragraph (4) applies shall, where the Board so require and within one month of being required to do so or such longer period as the Board may consider reasonable, provide the Board with the information specified in paragraph (6).

(6) The information referred to in this paragraph is—
\begin{enumerate}\item[]
($a$) where the purchase of an annuity under a personal pension scheme has been deferred, the amount of any income which is being withdrawn from the personal pension scheme;

($b$) in the case of—
\begin{enumerate}\item[]
(i) a personal pension scheme where income withdrawal is available, the maximum amount of income which may be withdrawn from the scheme; or

(ii) a personal pension scheme where income withdrawal is not available, or a retirement annuity contract, the maximum amount of income which might be withdrawn from the fund if the fund were held under a personal pension scheme where income withdrawal was available,
\end{enumerate}
calculated by or on behalf of the pension fund holder by means of tables prepared from time to time by the Government Actuary which are appropriate for this purpose.
\end{enumerate}

(7) Every person providing childcare in respect of which a claimant to whom regulation 46A of the Family Credit (General) Regulations 1987\footnote{\frenchspacing S.I. 1987/1973; the regulation 13A inserted in S.I. 1987/1973 by S.I. 1994/1924 and amended by S.I. 1995/516, 1996/2545 and 1997/2793 was renumbered 46A and further amended by S.I. 1999/2487.} applies is incurring relevant childcare charges (within the meaning of that regulation), including a person providing childcare on behalf of a school, local authority, childcare scheme or establishment within paragraph (2)($b$), ($c$)  or ($d$)  of that regulation, shall furnish such certificates, documents, information and evidence as may be required by the Board for the purposes of paragraph (1), and shall do so within one month of being required to do so or such longer period as the Board may consider reasonable.

\subsection*{Suspension and termination in cases of failure to furnish information or evidence}

18.---(1)  Where a claimant—
\begin{enumerate}\item[]
($a$) is required by the Board under regulation 17 to furnish information, or evidence, and

($b$) fails to do so within the period specified by the Board in accordance with that regulation (“the suspension period”),
\end{enumerate}
the Board may, subject to paragraphs (3) and (4), decide to suspend payment of tax credit to or on behalf of the claimant in whole or in part.

(2) Where either—
\begin{enumerate}\item[]
($a$) a claimant whose benefit has been suspended in whole or in part in accordance with regulation 16 subsequently fails to comply with a requirement for information or evidence made under regulation 17, within the suspension period, or within the period of one month immediately following the suspension period; or

\begin{enumerate}\item[($b$)] (i) a claimant has been required by the Board under regulation 17 to furnish information or evidence,

(ii) the claimant has failed to do so within the suspension period and within the period of one month immediately following the suspension period, and

(iii) the Board have suspended payment of tax credit to or on behalf of the claimant in whole or in part in accordance with paragraph (1) of this regulation,
\end{enumerate}
\end{enumerate}
the Board may, subject to paragraphs (3) to (5), decide that the claimant shall cease to be entitled to payment of tax credit with effect from a date not earlier than the date on which payment of tax credit was suspended.

(3) No decision shall be taken by the Board pursuant to paragraph (1) or (2) where—
\begin{enumerate}\item[]
($a$) the failure to furnish information has been remedied; or

($b$) the Board have allowed a further period of time (in addition to the suspension period or the period of one month referred to in paragraph (2)($a$)  or ($b$)(ii)) within which the claimant is required to furnish the information and the claimant has furnished the information within that further period.
\end{enumerate}

(4) For the purposes of paragraphs (1) and (2), a claimant shall be deemed not to have failed to furnish information within the suspension period or within the period of one month referred to in paragraph (2)($a$)  or ($b$)(ii)  if he had a reasonable excuse and that excuse has not ceased; and, where that excuse has ceased, he shall be deemed not to have failed to furnish information within either of those periods for those purposes if he furnished the information without unreasonable delay after the excuse had ceased.

(5) No decision shall be taken by the Board pursuant to paragraph (2) unless payment of the whole of the relevant tax credit to or on behalf of the claimant has been suspended, under regulation 16 or 17 or both of those regulations.”
\end{quotation}

\medskip

14.---(1)  Regulation 19 shall be amended as follows.

(2) In paragraph (1)—
\begin{enumerate}\item[]
($a$) after the words “Secretary of State”, where those words first occur, there shall be inserted the words “or the Board”;

($b$) in sub-paragraph ($a$)—
\begin{enumerate}\item[]
(i) after the words “Secretary of State considers” there shall be inserted the words “or the Board consider”;

(ii) after the word “himself” there shall be inserted the words “or themselves”;
\end{enumerate}

($c$) in sub-paragraph ($b$)—
\begin{enumerate}\item[]
(i) after the words “Secretary of State considers” there shall be inserted the words “or the Board consider”;

(ii) after the word “his” there shall be inserted the words “or their”.
\end{enumerate}
\end{enumerate}

(3) In paragraphs (2) and (3) after the words “Secretary of State” there shall be inserted the words “or the Board”.

\medskip

15.---(1)  Regulation 20\footnote{\frenchspacing Paragraph (1) of regulation 20 was amended and sub-paragraph ($d$) was inserted by regulation 6($b$) of S.I. 1999/1623.} shall be amended as follows.

(2) In paragraphs (1)($a$)  and ($b$)  and (4) after the words “Secretary of State is satisfied” there shall be inserted the words “or the Board are satisfied”.

(3) In paragraph (1)($b$)  after the words “he has” there shall be inserted the words “or they have”.

(4) For paragraph (1)($d$)  there shall be substituted—
\begin{quotation}
“($d$) in a case to which regulation 18(1) applies, the Board are satisfied that the benefit suspended is properly payable and the requirements of regulation 17(2), (4), (5) or (7) have been satisfied.”
\end{quotation}

(5) In paragraph (2)—
\begin{enumerate}\item[]
($a$) after the words “which he” there shall be inserted the words “or they”;

($b$) after the words “Secretary of State has not” there shall be inserted the words “, or the Board have not,”;

($c$) after the words “he has” there shall be inserted the words “, or they have,”.
\end{enumerate}

(6) In paragraph (3)—
\begin{enumerate}\item[]
($a$) after the words “Secretary of State fails” there shall be inserted the words “or the Board fail”;

($b$) after the words “Secretary of State receives” there shall be inserted the words “or the Board receive”.
\end{enumerate}

\medskip

16.---(1)  Regulation 21 shall be amended as follows.

(2) In paragraph (3) after the words “Secretary of State” there shall be inserted the words “or the Board”.

(3) In paragraph (4)—
\begin{enumerate}\item[]
($a$) after the words “the Secretary of State” there shall be inserted the words “or the Board”;

($b$) in sub-paragraph ($a$)  after the words “certifies in writing that he is” there shall be inserted the words “, or certify in writing that they are,”;

($c$) in sub-paragraph ($b$)  after the word “considers” there shall be inserted the words “, or consider,”:
\end{enumerate}

\medskip

17.  In regulation 22—
\begin{enumerate}\item[]
($a$) after the words “Secretary of State” there shall be inserted the words “or the Board”;

($b$) in paragraph ($a$)  after the words “certifies in writing that he is” there shall be inserted the words “, or certify in writing that they are,”;

($c$) in paragraph ($b$)  after the word “considers” there shall be inserted the words “, or consider,”.
\end{enumerate}

\medskip

18.  In regulation 25($a$)  after the words “Secretary of State” there shall be inserted the words “or the Board”.

\medskip

19.  In regulation 26 after the words “Secretary of State”, there shall be inserted the words “or an officer of the Board”.

\medskip

20.  In regulation 28 after the words “Secretary of State”, in each place where they occur, there shall be inserted the words “or the Board or an officer of the Board”.

\medskip

21.---(1)  Regulation 30—
\begin{enumerate}\item[]
($a$) in paragraphs (1) and (5) after the words “Secretary of State” there shall be inserted the words “or the Board or an officer of the Board”;

($b$) in paragraph (5) after the words “revises his” there shall be inserted the words “, or revise their,”.
\end{enumerate}

\medskip

22.---(1)  Regulation 31 shall be amended as follows.

(2) In paragraph (1) after the words “Secretary of State”, where those words first occur, there shall be inserted the words “or the Board or an officer of the Board”.

(3) In paragraphs (2) and (3) after the words “Secretary of State”, wherever those words occur, there shall be inserted the words “or the Board or an officer of the Board”.

(4) In paragraph (2) after the words “he is” there shall be inserted the words “or they are”.

\medskip

23.---(1)  Regulation 33 shall be amended as follows.

(2) In paragraph (1)—
\begin{enumerate}\item[]
($a$) after the words “Secretary of State”, where those words first occur, there shall be inserted the words “or the Board”;

($b$) after the words “Secretary of State accepts” there shall be inserted the words “or the Board accept”.
\end{enumerate}

(3) In paragraph (2)—
\begin{enumerate}\item[]
($a$) the word “and” immediately following sub-paragraph ($d$)  shall be omitted;

($b$) after sub-paragraph ($d$)  there shall be inserted the following sub-paragraph—
\begin{quotation}
“($dd$) in the case of an appeal against a decision relating to working families' tax credit or disabled person’s tax credit, a Tax Credits Office of the Board, and”.
\end{quotation}
\end{enumerate}

(4) In paragraphs (3) and (5) to (9) after the words “Secretary of State” there shall be inserted the words “or the Board”.

(5) In paragraph (4)—
\begin{enumerate}\item[]
($a$) after the words “Secretary of State is satisfied” there shall be inserted the words “or the Board are satisfied”;

($b$) after the word “he” there shall be inserted the words “or they”.
\end{enumerate}

(6) In paragraph (7) after the words “Secretary of State's”, in both places where they occur, there shall be inserted the words “or the Board's”.

\medskip

24.  In regulation 34—
\begin{enumerate}\item[]
($a$) in paragraphs (1) and (3), after the words “Secretary of State”, wherever those words occur, there shall be inserted the words “or the Board”;

($b$) in paragraph (1) after the words “he thinks” there shall be inserted the words “or they think”.
\end{enumerate}

\medskip

25.  In regulation 40(1) for the words “Secretary of State” there shall be inserted the words “the Board or an officer of the Board,”.

\medskip

26.  In regulation 41($a$)(iv) for the words “disability working allowance” there shall be substituted the words “disabled person’s tax credit”.

\medskip

27.  In regulation 58(2) after the words “Secretary of State” there shall be inserted the words “or the Board”. 

\bigskip

%Signed 
%by authority of the Secretary of State for Social Security.

{\raggedleft
%\emph{Stephen C.\ Timms
%}\\*Minister of State,\\*Department of Social Security

\emph{G H Bush\\*Tim Flesher}\\*Two of the Commissioners of Inland Revenue

}

14th September 1999

\small

\part[Schedule --- Provisions conferring powers exercised in making these Regulations]{Schedule\\*Provisions conferring powers exercised in making these Regulations}

{\footnotesize

%\begin{tabulary}{\linewidth}{JJ}
\begin{longtable}{p{181.44629pt}p{162.9498pt}}
\hline
\endhead
\hline
\endlastfoot
Social Security Administration Act 1992\footnote{\frenchspacing 1992 c. 5; section 5(1) was amended by section 74 of the Social Security Act 1998 (c. 14).}	&Section 5(1)($hh$).\\
Social Security Act 1998	&Section 9(1), (4) and (6)\\
&	Section 10(3) and (6)\\
&	Section 11(1)\\
&	Section 12(3), (6) and (7)\\
&	Section 14(10)($a$)  and (11)\\
&	Section 16(1) and Schedule 5\\
&	Sections 20 to 24\\
&	Section 25(3)($b$)  and (5)($c$) \\
&	Section 26(6)($c$) \\
&	Section 79(4) to (7)\\
&	Section 84\\
&	Schedule 3 paragraph 9.\\
Tax Credits Act 1999\footnote{\frenchspacing 1999 c. 10.}	&Section 2(1)($c$) \\
&	Section 19(1)\\
&	Schedule 1 paragraph 3($a$) \\
&	Schedule 2 paragraphs 7($b$)  and 8($a$).\\
%\end{tabulary}
\end{longtable}

}

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations amend the Social Security and Child Support (Decisions and Appeals) Regulations 1999 (S.I.\ 1999/991) (“the principal Regulations”) in consequence of the transfer under the Tax Credits Act 1999 (c.\ 10) of functions relating to family credit and disability working allowance from the Department of Social Security to the Treasury and the Inland Revenue on 5th October 1999. Family credit and disability working allowance are to become known as working families' tax credit and disabled person’s tax credit respectively as from 5th October 1999.

The Regulations also substitute regulations in the principal Regulations relating to the furnishing of information to enable the Board of Inland Revenue to determine whether a decision awarding working families' tax credit or disabled person’s tax credit should be revised under section 9 of the Social Security Act 1998 (c.\ 14) or superseded under section 10 of that Act.

Regulation 1 provides for citation, commencement and effect and regulation 2 for interpretation.

Regulations 3 to 27 amend the principal Regulations and, in particular, regulation 13 substitutes new regulations 17 and 18 of the principal Regulations relating to the furnishing of information to determine whether an award of working families' tax credit or disabled person’s tax credit should be revised or superseded, with provision for suspension or termination of any such award in the event of failure to furnish the required information. 

\end{document}