\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 3) Order 2000}

\newcommand\regsnumber{2000/2994}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I. 2000 No. 2994 (C.94)}

\date{Made 7th November 2000}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.57402pt}

\begin{document}

\maketitle

\noindent
The Secretary of State for Social Security, in exercise of the powers conferred upon him by section 86(2) of the Child Support, Pensions and Social Security Act 2000\footnote{\frenchspacing 2000 c. 19.} and of all other powers enabling him in that behalf, hereby makes the following Order: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation]{Citation}

1.---(1)  This Order may be cited as the Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 3) Order 2000.

(2) In this Order references to “the Act” are references to the Child Support, Pensions and Social Security Act 2000 and, except where otherwise stated, references to sections and Schedules are references to sections of, and Schedules to, the Act.

\subsection[2. Appointed days]{Appointed days}

2.---(1)  The day appointed for the coming into force of the provisions of the Act specified in Part I of the Schedule to this Order for the purpose of the exercise of powers to make regulations and Acts of Sederunt is 10th November 2000.

(2) The day appointed for the coming into force of the provisions of the Act specified in Part II of the Schedule to this Order—
\begin{enumerate}\item[]
($a$) for the purpose of the exercise of the power to make regulations is 10th November 2000, and

($b$) for all other purposes is 1st January 2001.
\end{enumerate}

(3) The day appointed for the coming into force of paragraph 11(17) of Schedule 3 and section 26 so far as it relates to that paragraph is 1st January 2001.

(4) The day appointed for the coming into force of sections 57 and 58 of the Act—
\begin{enumerate}\item[]
($a$) for the purpose of the exercise of the power to make regulations is 15th November 2000, and

($b$) for all other purposes is 9th April 2001.
\end{enumerate}

(5) The day appointed for the coming into force of sections 59 and 61 of the Act is 1st January 2001.

(6) The day appointed for the coming into force of section 60 of the Act and Part IV of Schedule 9 to the Act is 9th April 2001. 

\bigskip

Signed 
by authority of the Secretary of State for Social Security.

{\raggedleft
\emph{P.~Hollis}\\*Parliamentary Under-Secretary of State,\\*Department of Social Security

}

7th November 2000

\small

\part{Schedule}

\section[Part I --- Provisions brought into force on 10th November 2000 for the purpose of making regulations and Acts of Sederunt]{Part I\\*Provisions brought into force on 10th November 2000 for the purpose of making regulations and Acts of Sederunt}

\renewcommand\parthead{--- Schedule Part I}

{\footnotesize\noindent
\begin{tabulary}{\linewidth}{JJ}
\hline
\itshape Provision of the Act	& \itshape Subject matter\\
\hline
Section 3	&Applications by persons claiming or receiving benefit\\
Section 4&	Default and interim maintenance decisions\\
Section 5&	Departure from usual rules for calculating maintenance\\
Section 7 except in so far as it relates to section 28G(2)	&Variations: revision and supersession\\
Section 9	&Decisions superseding earlier decisions\\
Section 10	&Appeals to appeal tribunals\\
Section 16	&Disqualification from driving\\
Section 17	&Civil imprisonment: Scotland\\
Section 18	&Financial penalties\\
Section 19	&Reduced benefit decisions\\
Section 20	&Voluntary payments\\
Section 21	&Recovery of child support maintenance by deduction from benefit\\
Section 22(3)	&Jurisdiction\\
Section 25	&Regulations\\
Section 29	&Interpretation, transitional provisions, savings etc\\
Schedule 1 and section 1(3)	&Substituted Part I of Schedule 1 to the Child Support Act 1991\\
Schedule 2 and section 6	&Substituted Schedules 4A and 4B to the Child Support Act 1991\\
Paragraph 11(18) of Schedule 3 and section 26 in so far as it relates to that paragraph	&Collection and enforcement of fees\\
\hline
\end{tabulary}

}

\section[Part II --- Provisions brought into force on 10th November 2000 for the purpose of making regulations and 1st January 2001 for all other purposes]{Part II\\*Provisions brought into force on 10th November 2000 for the purpose of making regulations and 1st January 2001 for all other purposes}

\renewcommand\parthead{--- Schedule Part I}

{\footnotesize\noindent
\begin{tabulary}{\linewidth}{JJ}
\hline
\itshape Provision of the Act	& \itshape Subject matter\\
\hline
Section 7 in so far as it relates to section 28G(2)	&Variation application when a maintenance calculation is in force\\
Section 27	&Temporary compensation payment scheme\\
\hline
\end{tabulary}

}

\part{Explanatory Note}

\renewcommand\parthead{--- Explanatory Note}

\subsection*{(This note is not part of the Order)}

This Order brings into force further provisions of the Child Support, Pensions and Social Security Act 2000 as follows.

Provisions relating to changes to the child support system are commenced for the purpose of making regulations and Acts of Sederunt on 10th November 2000 (article 2(1)).

Certain provisions relating to those changes which are to take effect in advance of the overall changes to the child support system are commenced from 1st January 2001 (article 2(2)). These concern the introduction of a statutory compensation scheme in relation to the current child support system, the ability to prescribe benefits for the purpose of Schedule 1 to the Act for flat rate cases and the ability to modify the provisions on variations for applications made when a maintenance calculation is in force.

Article 2(3) commences an amendment to section 33 of the Act to clarify what constitutes failure to make a payment when a court is considering a liability order.

Provisions relating to appeal rights and time limits for appeals in relation to war pensions are commenced for the purpose of making regulations on 15th November 2000 and fully on 9th April 2001 (article 2(4)).

Article 2(5) commences on 1st January 2001 provisions relating to the matters which are relevant for consideration on an appeal to the Pensions Appeal Tribunals and to enable the constitution of the Central Advisory Committee on war pensions to be amended.

Provisions concerning the constitution and procedure of the Pension Appeals Tribunal are commenced from 9th April 2001 (article 2(6)).

The impact on business of the commencement provisions in the Child Support, Pensions and Social Security Act 2000 is detailed in the Regulatory Impact Assessment (as revised) relating to the Child Support, Pensions and Social Security Bill (which was introduced in the House of Commons on 1st December 1999). A copy of that Assessment has been placed in the libraries of both Houses of Parliament and can be obtained from the Department of Social Security, Regulatory Impact Unit, 3rd Floor, the Adelphi, 1--11 John Adam Street, London \textsc{\lowercase{WC2N 6HT}}.

\part{Note as to earlier Commencement Orders}

\renewcommand\parthead{--- Note as to earlier Commencement Orders}

\subsection*{(This note is not part of the Order)}

The following provisions have been brought into force by the Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 1) Order 2000 (S.I.\ 2000/2666 (C.\ 74)) and the Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 2) Order 2000 (S.I.\ 2000/2950 (C.87)). 

{\footnotesize\noindent
%\begin{tabulary}{\linewidth}{JJJ}
\begin{longtable}{p{257.94028pt}p{50pt}p{46.06pt}}
\hline
\itshape Provision	&\itshape Date of commencement	&\itshape S.I. No.\\
\hline
\endhead
\footnote{\frenchspacing In this note an asterisk indicates that the provisions in the entry to which it relates has or have been commenced in part only.\label{fn:2}}Sections 30 to 35	&8 January 2001	&2000/2950\\
Section 36	&1 November 2000	&2000/2950\\
Section 41	&29 September 2000	&2000/2666\\
\footref{fn:2}Sections 62 to 65	&1 December 2000	&2000/2950\\
\footref{fn:2}Section 69&	1 November 2000	&2000/2950\\
\footref{fn:2}Section 71&	1 November 2000	&2000/2950\\
Section 72	&9 October 2000	&2000/2666\\
Section 73	&1 December 2000	&2000/2950\\
Schedule 4	&8 January 2001	&2000/2950\\
Schedule 5, paragraph 10 and section 56 in so far as it relates to that paragraph	&1 November 2000	&2000/2950\\
Schedule 6, paragraph 7 and paragraph 8 (partially) and paragraph 1 and section 67 in so far as they relate to those paragraphs	&1 November 2000	&2000/2950\\
\footref{fn:2}Schedule 7, paragraphs 3, 4, 6, 8 to 10, 12 to 16, 19, 20, 21 and 23 and paragraph 1 and section 68 in so far as they relate to those paragraphs	&1 November 2000	&2000/2950\\
\hline
\end{longtable}
%\end{tabulary}

}

\end{document}