\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support (Decisions and Appeals) (Amendment) Regulations 2003}

\newcommand\regsnumber{2003/129}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2003 No.\ 129}

\date{Made
27th January 2003\\
Laid before Parliament
31st January 2003\\
Coming into force
in accordance with regulation 1(1)
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.57402pt}

\begin{document}

\maketitle

\noindent
The Secretary of State for Work and Pensions, in exercise of the powers conferred upon him by sections 16(4), 52(1) and (4) and 54 of the Child Support Act 1991\footnote{1991 c.\ 48. Section 16 was substituted by section 40 of the Social Security Act 1998 (c.\ 14) and was amended by section 8 of the Child Support, Pensions and Social Security Act 2000 (c.\ 19). Section 54 is cited because of the meaning ascribed to the word “prescribed”.}, hereby makes the following Regulations: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation, commencement and interpretation]{Citation, commencement and interpretation}

1.---(1)  These Regulations may be cited as the Child Support (Decisions and Appeals) (Amendment) Regulations 2003 and shall come into force in relation to a particular case on the day on which section 16 of the Child Support Act 1991 as amended by the Child Support, Pensions and Social Security Act 2000\footnote{2000 c.\ 19.} comes into force in relation to that type of case.

(2) In these Regulations “the principal Regulations” means the Social Security and Child Support (Decisions and Appeals) Regulations 1999\footnote{S.I.\ 1999/991, relevant amending instruments are S.I.\ 2000/3185 and S.I.\ 2002/1204.}.

\subsection[2. Amendment of the principal Regulations]{Amendment of the principal Regulations}

2.  In regulation 5A of the principal Regulations (date from which a decision revised under section 16 of the Child Support Act takes effect)\footnote{Regulation 5A was inserted by S.I.\ 2000/3185.}—
\begin{enumerate}\item[]
($a$) for paragraph (2)($b$)  there shall be substituted—
\begin{quotation}
“($b$) the total amount of child support maintenance which would be fixed for the relevant period by the decision which is treated as a decision made under section 11 of the Child Support Act is greater than the total amount of child support maintenance which was fixed for that period by the decision made under section 12(1) of the Child Support Act (whether as originally made, or as revised or superseded under sections 16 or 17 of that Act respectively, or decided on appeal).”.
\end{quotation}

($b$) after paragraph (2)($b$)  there shall be added—
\begin{quotation}
“(3) For the purposes of paragraph (2)($b$), “the relevant period” means the period during which the decision under section 12(1) of the Child Support Act (whether as originally made, or as revised or superseded under sections 16 or 17 of that Act respectively, or decided on appeal) applied.”.
\end{quotation}
\end{enumerate}

\bigskip

Signed 
by authority of the Secretary of State for Work and Pensions.

{\raggedleft
\emph{P.~Hollis}\\*Parliamentary Under-Secretary of State,\\*Department of Work and Pensions

}

%St Andrew's House, Edinburgh

%Dated
27th January 2003

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations amend the Social Security and Child Support (Decisions and Appeals) Regulations 1999 (S.I.\ 1999/991) (“the principal Regulations”). The Regulations make an amendment to regulation 5A which provides the date from which a decision revised under section 16 of the Child Support Act 1991 (c.\ 48) takes effect.

Regulation 2 substitutes a new paragraph (2)($b$)  in regulation 5A of the principal Regulations to clarify the operation of that regulation. This regulation also adds a definition for the purposes of that paragraph.

These Regulations do not impose a charge on business.  

\end{document}