\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support (Consequential Provisions) Regulations 2008}

\newcommand\regsnumber{2008/2543}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2008 No.\ 2543}

\date{Made
26th September 2008\\
Laid before Parliament
1st October 2008\\
Coming into force
27th October 2008
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{42.11603pt}

%\hbadness=10000

\begin{document}

\maketitle

\noindent
The Secretary of State for Work and Pensions makes the following Regulations in exercise of the powers conferred by section 57(2) of the Child Maintenance and Other Payments Act 2008\footnote{2008 c.~6.}. 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and commencement]{Citation and commencement}

1.  These Regulations may be cited as the Child Support (Consequential Provisions) Regulations 2008 and shall come into force on 27th October 2008.

\subsection[2. Child Support (Maintenance Assessment Procedure) Regulations 1992]{\sloppy Child Support (Maintenance Assessment Procedure) Regulations 1992}

2.---(1)  The Child Support (Maintenance Assessment Procedure) Regulations 1992\footnote{S.I.~1992/1813, amended by S.I.~1999/1047; there are other amending instruments but none is relevant.} are amended as follows.

(2) In regulation 1—
\begin{enumerate}\item[]
($a$) in paragraph (2), omit the definition of “direction”; and

($b$) omit paragraph (3).
\end{enumerate}

(3) In regulation 2—
\begin{enumerate}\item[]
($a$) in the heading, omit “, 6”; and

($b$) in paragraph (2), omit “under section 6 of the Act or”.
\end{enumerate}

(4) In regulation 17(8)($a$), omit “a reduced benefit direction or”.

(5) In regulation 20(11)($a$), omit “a reduced benefit direction or”.

(6) In regulation 23, omit paragraphs (15) to (18).

(7) In regulation 30(1), omit “, 6”.

(8) In regulation 32, omit “or (3)”.

(9) Omit regulations 34 to 50.

(10) In paragraph 1 of Schedule 2—
\begin{enumerate}\item[]
($a$) in the heading, omit “or 6 or under sections 4 and 6”;

($b$) in sub-paragraph (1), omit “or 6”; and

($c$) omit sub-paragraph (2).
\end{enumerate}

(11) In paragraph 3 of Schedule 2—
\begin{enumerate}\item[]
($a$) in sub-paragraph (2), omit “or 6”;

($b$) omit sub-paragraph (8).
\end{enumerate}

(12) Omit paragraph 5 of Schedule 2.

\subsection[3. Child Support Departure Direction and Consequential Amendments Regulations 1996]{Child Support Departure Direction and Consequential Amendments Regulations 1996}

3.  In regulation 46(2)($b$)  of the Child Support Departure Direction and Consequential Amendments Regulations 1996\footnote{S.I.~1996/2907, to which there are amendments not relevant to these Regulations.}, omit “or treated as made”.

\subsection[4. Social Security and Child Support (Decisions and Appeals) Regulations 1999]{Social Security and Child Support (Decisions and Appeals) Regulations 1999}

4.---(1)  The Social Security and Child Support (Decisions and Appeals) Regulations 1999\footnote{S.I.~1999/991; relevant amending instruments are S.I.~2000/3185 and S.I.~2002/1204.} are amended as follows.

(2) In regulation 1(3) in the definition of “relevant person”, omit “, or has been treated as applied for under section 6(3) of that Act,”.

(3) In regulation 3A—
\begin{enumerate}\item[]
($a$) in paragraph (3), for “11, 12 or 46” substitute “11 or 12”; and

($b$) in paragraph (6), for “12, 17 or 46” substitute “12 or 17”.
\end{enumerate}

(4) In regulation 7B—
\begin{enumerate}\item[]
($a$) omit paragraphs (11) to (16); and

($b$) in paragraph (21)($a$), omit “, or treated as made under section 6(3) of that Act,”.
\end{enumerate}

\subsection[5. Child Support (Voluntary Payments) Regulations 2000]{Child Support (Voluntary Payments) Regulations 2000}

5.  In regulation 1(2) of the Child Support (Voluntary Payments) Regulations 2000\footnote{S.I.~2000/3177.}, in the definition of “relevant person”, omit “or has been treated as applied for, under section 6(3) of the Act,”.

\subsection[6. Child Support (Transitional Provisions) Regulations 2000]{\sloppy Child Support (Transitional Provisions) Regulations 2000}

6.  In the Child Support (Transitional Provisions) Regulations 2000\footnote{S.I.~2000/3186; relevant amending instruments are S.I.~2002/1204 and S.I.~2003/328.}, omit “or treated as made” in each place it occurs in regulations 3(1)($b$), 11(3)($a$), 15(3C)($b$), 25(2)($a$), 28(1), (2), (2A), (3), (5A), (7), (7A) and (9), and 30($a$).

\subsection[7. Child Support (Maintenance Calculations and Special Cases) Regulations 2000]{Child Support (Maintenance Calculations and Special Cases) Regulations 2000}

7.---(1)  The Child Support (Maintenance Calculations and Special Cases) Regulations 2000\footnote{S.I.~2001/155, amended by S.I.~2003/328; there are other amending instruments but none is relevant.} are amended as follows.

(2) In regulation 1(2), in sub-paragraph ($a$)(ii)  of the definition of “relevant week”, omit “, or treated as made, as the case may be,”.

(3) In regulation 8(1)($a$), omit “or treated as made”.

(4) In regulation 11(1)($a$), omit “or treated as made, as the case may be,”.

\subsection[8. Child Support (Variations) Regulations 2000]{Child Support (Variations) Regulations 2000}

8.---(1)  The Child Support (Variations) Regulations 2000\footnote{S.I.~2001/156, to which there are amendments not relevant to these Regulations.} are amended as follows.

(2) In regulation 19(1)($a$)  omit “or treated as applied for”.

(3) In regulation 20(1)($a$)  and (2), omit “or treated as applied for” in both places it occurs.

\subsection[9. Child Support (Maintenance Calculation Procedure) Regulations 2000]{\sloppy Child Support (Maintenance Calculation Procedure) Regulations 2000}

9.---(1)  The Child Support (Maintenance Calculation Procedure) Regulations 2000\footnote{S.I.~2001/157; relevant amending instruments are S.I.~2002/1204, S.I.~2003/328 and S.I.~2004/2415.} are amended as follows.

(2) In regulation 1—
\begin{enumerate}\item[]
($a$) in paragraph (2) in the definition of—
\begin{enumerate}\item[]
(i) “notice of a maintenance application”, omit “, or treated as made,”;

(ii) “relevant person”, omit “or has been treated as applied for under section 6(3) of the Act,”; and
\end{enumerate}

($b$) in paragraph (5), omit “6,” and “46,”.
\end{enumerate}

(3) In regulation 5(1), omit “or an application is treated as made under section 6(3) of the Act,” and “, or is treated as having made,”.

(4) In regulation 6(1), omit “or has been treated as made,”.

(5) Omit regulations 8 to 20.

(6) In regulation 25—
\begin{enumerate}\item[]
($a$) in paragraph (1), omit “or treated as made under section 6(3) of the Act,”; and

($b$) omit paragraph (3)($b$).
\end{enumerate}

(7) Omit regulation 27.

(8) In regulation 28($b$), omit “or 27 as the case may be”.

(9) In regulation 29—
\begin{enumerate}\item[]
($a$) in paragraph (1), omit “, or treated as made under section 6(3) of the Act”;

($b$) in paragraph (1)($a$), ($c$)  and ($d$), omit “except where the parent with care has made a request under section 6(5) of the Act,” in each place it occurs; and

($c$) omit paragraphs (2) and (3)($b$).
\end{enumerate}

(10) In regulation 31—
\begin{enumerate}\item[]
($a$) in the heading, omit “and reduced benefit decisions”;

($b$) in paragraph (1), omit “or is treated as made under section 6(3) of the Act,”;

($c$) in paragraph (1B)($b$), omit “or an application for a maintenance calculation is treated as made under the Act”; and

($d$) omit paragraphs (3) to (7) and (8)($b$).
\end{enumerate}

(11) In paragraph 1 of Schedule 2—
\begin{enumerate}\item[]
($a$) in the heading, omit “or 6 or under sections 4 and 6”;

($b$) in sub-paragraph (1), omit “or 6”; and

($c$) omit sub-paragraph (2).
\end{enumerate}

(12) In paragraph 3 of Schedule 2—
\begin{enumerate}\item[]
($a$) in sub-paragraph (2), omit “or is treated as made under section 6 of the Act,”; and

($b$) omit sub-paragraph (7).
\end{enumerate}

(13) In paragraph 4 of Schedule 2, omit “or treated as made, as the case may be,”.

(14) In paragraph 1 of Schedule 3—
\begin{enumerate}\item[]
($a$) in the heading, omit “or 6” and “and 6”;

($b$) in sub-paragraph (1), omit “or is treated as making, as the case may be,” and “or 6”; and

($c$) omit sub-paragraph (2).
\end{enumerate}

(15) In paragraph 3 of Schedule 3—
\begin{enumerate}\item[]
($a$) in sub-paragraph (2), omit “, or is made under section 6 of the former Act, or is treated as made under section 6 of the Act,”; and

($b$) omit sub-paragraph (7).
\end{enumerate}

(16) In paragraph 4 of Schedule 3, in sub-paragraph ($b$)  omit “or treated as made”. 

\bigskip

Signed 
by authority of the 
Secretary of State for Work and Pensions.
%I concur

{\raggedleft
\emph{Stephen C.~Timms}\\*
Minister
%Parliamentary Under-Secretary 
of State,\\*Department for Work and Pensions

}

26th September 2008

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations make provision consequential on the coming into force of section~15 of the Child Maintenance and Other Payments Act 2008 (c.~6), which repeals sections 6 and 46 of the Child Support Act 1991 (c.~48).

The Regulations remove references to sections 6 and 46, and related terms, in the following statutory instruments—
\begin{enumerate}\item[]
    the Child Support (Maintenance Assessment Procedure) Regulations 1992;

    the Child Support Departure Direction and Consequential Amendments Regulations 1996;

    the Social Security and Child Support (Decisions and Appeals) Regulations 1999;

    the Child Support (Voluntary Payments) Regulations 2000;

    the Child Support (Transitional Provisions) Regulations 2000;

    the Child Support (Maintenance Calculations and Special Cases) Regulations 2000;

    the Child Support (Variations) Regulations 2000; and

    the Child Support (Maintenance Calculation Procedure) Regulations 2000. 
\end{enumerate}

A full impact assessment has not been published for this instrument as it has no impact on the costs of business, charities and voluntary bodies. 

\end{document}