\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Employment and~Support Allowance (Consequential Provisions) (No.~2) Regulations 2008}

\newcommand\regsnumber{2008/1554}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and~Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2008 No.\ 1554}

\date{Made
12th June 2008\\
Laid before Parliament
19th June 2008\\
Coming into~force
in accordance with regulation~1
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{42.11603pt}

%\hbadness=10000

\begin{document}

\maketitle

\noindent
The Secretary of State for~Work and~Pensions makes the following Regulations in exercise of the powers conferred by section~28(2) of the Welfare Reform Act 2007\footnote{2007 c.~5.}.

This Instrument contains only regulations made consequential upon Part~I of the Welfare Reform Act 2007 and~is made before the end of the period of 6 months beginning with the coming into force of those provisions\footnote{\emph{See} section~173(5) of the Social Security Administration Act 1992. The requirement to refer Regulations to the Social Security Advisory Committee does not apply where Regulations are contained in a statutory instrument made before the end of the period of six months beginning with the coming into force of the enactment under which the regulations were made.}. 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\section[Part I --- General]{Part I\\*General}

\renewcommand\parthead{--- Part I}

\subsection[1. Citation and~commencement]{Citation and~commencement}

1.---(1)  These Regulations may be cited as the Employment and~Support Allowance (Consequential Provisions) (No.~2) Regulations 2008.

(2) These Regulations come into force—
\begin{enumerate}\item[]
($a$) for~the purposes of this Part~and~Part~IV, except for~regulation~21, on 27th July 2008; and

($b$) for~all other purposes on 27th October 2008.
\end{enumerate}

\section[Part II --- Income-related benefits]{Part II\\*Income-related benefits}

\renewcommand\parthead{--- Part II}

\subsection[2. Amendment of the Income Support (General) Regulations 1987]{Amendment of the Income Support (General) Regulations 1987}

2.---(1)  The Income Support (General) Regulations 1987\footnote{S.I.~1987/1967.} are amended as follows.

(2) In regulation~2(1) (interpretation)—
\begin{enumerate}\item[]
($a$) in the definition of “the benefit Acts”\footnote{Definition was inserted by S.I.~1996/206.} for~“and~the Jobseekers Act 1995”\footnote{1995 c.~18.} substitute “,~the Jobseekers Act 1995 and~Part~I of the Welfare Reform Act”;

($b$) after the definition of “the Contributions and~Benefits Act”\footnote{Definition was inserted by S.I.~1993/315.} insert—
\begin{quotation}
““contributory employment and~support allowance” means a contributory allowance under Part~I of the Welfare Reform Act (employment and~support allowance);”;
\end{quotation}

($c$) after the definition of “employment”\footnote{Definition inserted by S.I.~1988/1445.} insert—
\begin{quotation}
““the Employment and~Support Allowance Regulations” means the Employment and~Support Allowance Regulations 2008\footnote{S.I.~2008/794.};”;
\end{quotation}

($d$) after the definition of “Immigration and~Asylum Act”\footnote{Definition was inserted by S.I.~2000/636.} insert—
\begin{quotation}\sloppy
““income-related employment and~support allowance” means an income-related allowance under Part~I of the Welfare Reform Act (employment and~support allowance);”;
\end{quotation}

($e$) after the definition of “water charges”\footnote{Definition was inserted by S.I.~1990/547 and~amended by S.I.~1990/1776 and~1993/315.} insert—
\begin{quotation}
““the Welfare Reform Act” means the Welfare Reform Act 2007;”.
\end{quotation}
\end{enumerate}

(3) In regulation~6(5)\footnote{Paragraph~(5) was inserted by S.I.~2001/488 and~amended by S.I.~2007/3183.} (persons not treated as engaged in remunerative work)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($b$)  for~“or~an income-based jobseeker’s allowance” substitute “,~an income-based jobseeker’s allowance or~an income-related employment and~support allowance”; and

($b$) in sub-paragraph~($c$)—
\begin{enumerate}\item[]
(i) after (i)  omit “or”; and

(ii) after (ii)  for~“and” substitute—
\begin{quotation}
“or

(iii) an amount determined in accordance with Schedule~6 to the Employment and~Support Allowance Regulations (housing costs) as applicable to him in respect of housing costs which qualify under paragraphs~16 to 18 of that Schedule; and”.
\end{quotation}
\end{enumerate}
\end{enumerate}

(4) In regulation~14(2)\footnote{Paragraph~(2) was amended by S.I.~2001/3070 and~2006/718.} (persons of a prescribed description)—
\begin{enumerate}\item[]
($a$) after sub-paragraph~($b$)  omit “or”; and

($b$) after sub-paragraph~($c$)  add—
\begin{quotation}
“or

($d$) entitled to an employment and~support allowance or~would, but for~paragraph~6(1)($d$)  of Schedule~1 to the Welfare Reform Act (conditions of entitlement to income-related employment and~support allowance), be so entitled.”.
\end{quotation}
\end{enumerate}

(5) In regulation~31(2)\footnote{Paragraph~(2) was amended by S.I.~1988/663 and~1445, 1995/482 and~1996/206.} (date on which income is treated as paid) for~“or~severe disablement allowance” substitute “severe disablement allowance or~employment and~support allowance”.

(6) In regulation~32(4)($b$)\footnote{Paragraph~(4) was amended by S.I.~1988/663 and~1445, 1995/482, 1996/206.} (calculation of weekly amount of income) for~“or~jobseeker’s allowance” substitute “,~jobseeker’s allowance or~employment and~support allowance”.

(7) In regulation~40 (calculation of income other than earnings) after paragraph~(5)\footnote{Paragraph~(5) was inserted by S.I.~2000/636.} add—
\begin{quotation}
“(6) Where the claimant—
\begin{enumerate}\item[]
($a$) is a member of a couple;

($b$) his partner is receiving a contributory employment and support allowance; and

($c$) that benefit has been reduced under regulation~63 of the Employment and~Support Allowance Regulations,
\end{enumerate}
the amount of that benefit to be taken into account is the amount as if it had not been so reduced.”.
\end{quotation}

(8) In regulation~72 (assessment of income and~capital in urgent cases)—
\begin{enumerate}\item[]
($a$) in paragraph~(1)($a$)(ii)\footnote{Sub-paragraph~($a$) was substituted by S.I.~1998/563.} after “1996” insert “or~of employment and~support allowance under regulation~164 of the Employment and~Support Allowance Regulations”; and

($b$) in paragraph~(2)\footnote{Paragraph~(2) was amended by S.I.~1988/1445 and~2022 and~S.I.~2008/698.} after “these Regulations” insert “,~regulation~164 of the Employment and~Support Allowance Regulations”.
\end{enumerate}

(9) In regulation~73(3)\footnote{Regulation~73 was inserted by S.I.~1988/663 and~amended by S.I.~1988/1445, 1995/482, 1996/206 and~2001/3767.} (amount of income support payable) in the definition of “$B$” for~“or~severe disablement allowance” substitute “severe disablement allowance or~employment and~support allowance”.

(10) In regulation~75\footnote{Regulation~75 was inserted by S.I.~1988/663 and~amended by S.I.~1988/1445, 1995/482 and~1996/206.} (modifications in the calculation of income)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($b$)  for~“or~severe disablement allowance” substitute “severe disablement allowance or~employment and~support allowance”;

($b$) in sub-paragraph~($e$)  for~“or~severe disablement allowance” substitute “,~severe disablement allowance or~employment and~support allowance”; and

($c$) in sub-paragraph~($f$)  for~“or~severe disablement allowance” substitute “severe disablement allowance or~employment and~support allowance”.
\end{enumerate}

(11) In Schedule~3 (housing costs)—
\begin{enumerate}\item[]
($a$) in paragraph~1 (housing costs)—
\begin{enumerate}\item[]
(i) in sub-paragraph~(3)\footnote{Sub-paragraph~(3) was amended by S.I.~1995/2927 and~2006/2378.} after ($c$)  add—
\begin{quotation}
“($d$) who is in receipt of an employment and~support allowance which includes an amount under section~2(2) or~(3) or~4(4) or~(5) of the Welfare Reform Act (components).”; and
\end{quotation}

(ii) in sub-paragraph~(4) after “disqualification etc.)”\ add “or~disqualified for~receiving employment and~support allowance or~treated as not having limited capability for~work in accordance with regulations made under section~18 of the Welfare Reform Act (disqualification)”;
\end{enumerate}

($b$) in paragraph~1A\footnote{Paragraph~1A was inserted by S.I.~1997/2305 and~amended by S.I.~2007/3183.} (previous entitlement to income-based jobseeker’s allowance or~state pension credit)—
\begin{enumerate}\item[]
(i) in the heading after “allowance” insert “,~income-related employment and~support allowance”;

(ii) after “income-based jobseeker’s allowance” each time it occurs insert “or~income-related employment and~support allowance”; and

(iii) in sub-paragraph~(1)($a$)  after “1996” add “or~paragraphs~16 to 18 of Schedule~6 to the Employment and~Support Allowance Regulations”;
\end{enumerate}

($c$) in paragraph~4(4) (housing costs not met) after “income support” each time it occurs insert “or~income-related employment and~support allowance”;

($d$) in paragraph~6(1B)\footnote{Sub-paragraph~(1B) was inserted by S.I.~1997/2305 and~amended by S.I.~2002/3019.} (existing housing costs) for~“or~state pension credit” substitute “,~state pension credit or~income-related employment and~support allowance”;

($e$) in paragraph~8(1B)\footnote{Sub-paragraph~(1B) was inserted by S.I.~1997/2305 and~amended by S.I.~2002/3019.} (new housing costs) for~“or~state pension credit” substitute “,~state pension credit or~income-related employment and~support allowance”;

($f$) in paragraph~14 (linking rule)—
\begin{enumerate}\item[]
(i) in sub-paragraph~(5)($a$)  for~“or~incapacity benefit” substitute “,~incapacity benefit or~contributory employment and~support allowance”; and

(ii) after sub-paragraph~(14) add—
\begin{quotation}
“(15) For~the purpose of determining whether the linking rules set out in this paragraph~apply in a case where a claimant’s former partner was entitled to income-related employment and~support allowance, any reference to income support in this Schedule~shall be taken to include also a reference to income-related employment and~support allowance.”; and
\end{quotation}
\end{enumerate}

($g$) in paragraph~18(7) (non-dependant deductions) after paragraph~($h$)  add—
\begin{quotation}
“($i$) he is aged less than 25 and~is in receipt of employment and~support allowance which does not include an amount under section~2(2) or~(3) or~4(4) or~(5) of the Welfare Reform Act (components).”.
\end{quotation}
\end{enumerate}

(12) In Schedule~7 (applicable amounts in special cases) in paragraph~19A\footnote{Paragraph~19A was inserted by S.I.~2001/488 and~amended by S.I.~2001/3767 and~2002/398.} (persons who have commenced remunerative work) in column 2—
\begin{enumerate}\item[]
($a$) in sub-paragraph~(1)—
\begin{enumerate}\item[]
(i) in paragraph~($a$)—
\begin{enumerate}\item[]
($aa$) after (i)  omit “or”; and

($bb$) after (ii)  add—
\begin{quotation}
“or

(iii) as the case may be, Schedule~6 to the Employment and~Support Allowance Regulations (housing costs),”
\end{quotation}
\end{enumerate}

(ii) in paragraph~($b$)  after “income support” the first time it occurs, insert “,~income-related employment and~support allowance”.
\end{enumerate}
\end{enumerate}

(13) In paragraph~4(7)\footnote{Paragraph~4 was substituted by S.I.~1989/534 and~sub-paragraph~(7) was substituted by S.I.~1989/1678 and~amended by S.I.~1991/387 and~2002/3019.} of Schedule~8 (sums to be disregarded in the calculation of earnings) after “income support” each time it occurs insert “or~employment and~support allowance”.

(14) In Schedule~9 (sums to be disregarded in the calculation of income other than earnings)—
\begin{enumerate}\item[]
($a$) in paragraph~7($b$)\footnote{Paragraph~7($b$) was amended by S.I.~1998/563.} for~“or~jobseeker’s allowance” substitute “,~jobseeker’s allowance or~employment and~support allowance.”; and

($b$) in paragraph~13(1)($a$)\footnote{Paragraph~13 was substituted by S.I.~2004/565.} for~“or~severe disablement allowance” substitute “,~severe disablement allowance or~an employment and~support allowance”.
\end{enumerate}

(15) In paragraph~7\footnote{Paragraph~7 was amended by S.I.~1991/2742, 1996/206, 2001/2333, 2002/2380, 2003/455 and~2005/574.} of Schedule~10 (capital to be disregarded)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~(1)($b$)  after “income-related benefit” insert “,~an income-related employment and~support allowance”; and

($b$) in sub-paragraph~(3)—
\begin{enumerate}\item[]
(i) in paragraph~($a$)  after “income support” insert “,~an income-related employment and~support allowance”; and

(ii) in paragraph~($b$)  after “income support” insert “,~an income-related employment and~support allowance”.
\end{enumerate}
\end{enumerate}

\subsection[3. Amendment of the Jobseeker’s Allowance Regulations 1996]{Amendment of the Jobseeker’s Allowance Regulations 1996}

3.---(1)  The Jobseeker’s Allowance Regulations 1996\footnote{S.I.~1996/207.} are amended as follows.

(2) In regulation~1(3) (citation, commencement and~interpretation)—
\begin{enumerate}\item[]
($a$) after the definition of “the Eileen Trust” insert—
\begin{quotation}
““the Employment and~Support Allowance Regulations” means the Employment and~Support Allowance Regulations 2008;”; and
\end{quotation}

($b$) after the definition of “week”\footnote{Definition was amended by S.I.~1996/1517 and~1997/454.} insert—
\begin{quotation}
““the Welfare Reform Act” means the Welfare Reform Act 2007;”.
\end{quotation}
\end{enumerate}

(3) In regulation~11(2) (part-time students) for~“or~incapacity benefit” each time it occurs substitute “,~incapacity benefit or~employment and~support allowance”.

(4) In regulation~14(1) (circumstances in which a person is to be treated as available)—
\begin{enumerate}\item[]
($a$) in paragraphs~($l$)  and~($ll$)\footnote{Paragraphs ($l$)  and~($ll$)  were amended by S.I.~1996/1517, 1997/563, 1999/3087, 2000/3336, 2004/1869, 2006/1402 and~2008/698.} after “capable of work” insert “or~as not having limited capability for~work”; and

($b$) in paragraph~($o$)(ii)  after “incapacity benefit” insert “,~employment and~support allowance”.
\end{enumerate}

(5) In regulation~19(1)\footnote{Paragraph~(1) was amended by S.I.~1996/1517, 1997/563, 1998/1274, 1999/3087, 2000/3336, 2004/1869 and~2006/1402.} (circumstances in which a person is to be treated as actively seeking employment) in sub-paragraphs~($l$)  and~($ll$)  after “capable of work” insert “or~as not having limited capability for~work”.

(6) In regulation~46(1)\footnote{Paragraph~(1) was amended by S.I.~2000/1978 and~2003/511.} (waiting days)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($a$)  after “incapacity benefit” insert “,~employment and~support allowance”; and

($b$) in sub-paragraph~($d$)  after “incapacity benefit” insert “,~employment and~support allowance”.
\end{enumerate}

(7) In regulation~48(2)\footnote{Paragraph~2 was amended by S.I.~1996/2538, 1997/454 and~2863, 2000/724, 2001/1029, 2002/2314, and~2003/511.} (linking periods) after sub-paragraph~($b$)  insert—
\begin{quotation}
“($bb$) any period throughout which the claimant has, or~is treated as having, limited capability for~work for~the purposes of Part~I of the Welfare Reform Act;”.
\end{quotation}

(8) In regulation~49 (persons approaching retirement and~the jobseeking period)—
\begin{enumerate}\item[]
($a$) in paragraph~(2)\footnote{Paragraph~(2) substituted by S.I.~1996/1517.} for~“(3) and~(4)” substitute “(3), (4) and~(4A)”; and\looseness=-1

($b$) after paragraph~(4) insert—
\begin{quotation}
“(4A) Any day which, for~the purposes of Part~I of the Welfare Reform Act, is a day where the person has limited capability for~work falling within a period of limited capability for~work shall not be a day on which the person is treated as satisfying the conditions referred to in paragraph~(2).”.
\end{quotation}
\end{enumerate}

(9) In regulation~55 (short periods of sickness)—
\begin{enumerate}\item[]
($a$) in paragraph~(1)\footnote{Paragraph~(1) was amended by S.I.~1996/1517, 1999/2860 and~2000/1978.}—
\begin{enumerate}\item[]
(i) in sub-paragraph~($c$)  after “capable of work” insert “or~not having limited capability for~work”;

(ii) after “capable of work” the second time it occurs insert “or~as not having limited capability for~work”; and

(iii) after “incapacity benefit” insert “,~employment and~support allowance,”; and
\end{enumerate}

($b$) in paragraph~(4) after “within” insert “12 weeks of an entitlement of his to employment and~support allowance or”.
\end{enumerate}

(10) In regulation~55A(1)\footnote{Regulation was inserted by S.I.~2004/1869.} (periods of sickness and~persons receiving treatment outside Great Britain)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($d$)  after “capable of work” insert “or~not having limited capability for~work”;

($b$) after “capable of work” the second time it occurs insert “or~as not having limited capability for~work”; and

($c$) after “incapacity benefit” insert “,~employment and~support allowance”.
\end{enumerate}

(11) In regulation~61 (other young persons in prescribed circumstances)—
\begin{enumerate}\item[]
($a$) in paragraph~(1)\footnote{Paragraph~(1) was amended by S.I.~2000/1978 and~2001/652.} after sub-paragraph~($f$)  add—
\begin{quotation}
“($g$) who has limited capability for~work for~the purposes of Part~I of the Welfare Reform Act.”; and
\end{quotation}

($b$) in paragraph~(2)($b$)\footnote{Paragraph~(2) was amended by S.I.~2000/1978.} for~“1($b$)  or~($c$)” each time it occurs substitute “1($b$), ($c$)  or~($g$)”.
\end{enumerate}

(12) In regulation~76(2)\footnote{Paragraph~(2) was amended by S.I.~2001/3070 and~2006/718.} (persons of a prescribed description)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($d$)  after “applies” add—
\begin{quotation}
“or

($e$) entitled to an income-related employment and~support allowance or~would, but for~paragraph~6(1)($d$)  of Schedule~1 to the Welfare Reform Act (conditions of entitlement to income-related employment and~support allowance), be so entitled.”.\looseness=1
\end{quotation}
\end{enumerate}

(13) In regulation~78(6)\footnote{Paragraph~(6) was amended by S.I.~1996/1516.} (circumstances in which a person is to be treated as being or~not being a member of the household) after “income support” insert “or~an income-related employment and~support allowance”.

(14) In regulation~96(2) (date on which income is treated as paid) for~“or~jobseeker’s allowance” substitute “,~jobseeker’s allowance or~employment and~support allowance”.

(15) In regulation~97(4)($b$)  (calculation of weekly amount of income) for~“or~income support” substitute “,~income support or~employment and~support allowance”.\looseness=-1

(16) In regulation~103 (calculation of income other than earnings) after paragraph~(5A)\footnote{Paragraph~(5A) was inserted by S.I.~1997/65.} insert—
\begin{quotation}
“(5B) Where the claimant—
\begin{enumerate}\item[]
($a$) is a member of a couple;

($b$) his partner is receiving a contributory employment and support allowance; and

($c$) that benefit has been reduced under regulation~63 of the Employment and~Support Allowance Regulations,
\end{enumerate}
the amount of that benefit to be taken into account is the amount as if it had not been reduced.”.
\end{quotation}

(17) In regulation~140(3)\footnote{Paragraph~(3) was amended by S.I.~1996/1517.} (meaning of “person in hardship”) after “income support” insert “or~an income-related employment and~support allowance”.

(18) In regulation~146A(3)\footnote{Regulation~was inserted by S.I.~2000/1978.} (meaning of “couple in hardship”) after “income support” add “or~an employment and~support allowance”.

(19) In regulation~149(1)($a$)(ii)  (assessment of income and~capital in urgent cases) after “Income Support Regulations” insert “or~of employment and~support allowance under regulation~164 of the Employment and~Support Allowance Regulations”.

(20) In regulation~150(1)($b$)  (amount of jobseeker’s allowance payable) in the definition of “$B$” for~“or~severe disablement allowance” substitute “,~severe disablement allowance or~employment and~support allowance”.

(21) In regulation~153($b$)\footnote{Regulation~was amended by S.I.~2000/1978.} (modification in the calculation of income) after “Benefits Act” insert “or~employment and~support allowance”.

(22) In regulation~171($b$)\footnote{Regulation~was amended by S.I. 1996/1516.} (trade disputes: exemptions from section~15 of the Act)—
\begin{enumerate}\item[]
($a$) after paragraph~(i)  omit “or”; and

($b$) after paragraph~(ii)  add—
\begin{quotation}
“or

(iii) has limited capability for~work.”.
\end{quotation}
\end{enumerate}

(23) In Schedule~A1\footnote{Schedule~was inserted by S.I.~2000/1978 and~2001/518.} (categories of members of a joint-claim couple etc.)—
\begin{enumerate}\item[]
($a$) after paragraph~6 (member incapable of work) insert—
\begin{quotation}
\subsection*{\itshape “Member has limited capability for~work}

6A.  A person who—
\begin{enumerate}\item[]
($a$) has limited capability for~work under section~8 of the Welfare Reform Act; or

($b$) is treated as having limited capability for~work under regulations made under paragraph~1 of Schedule~2 to that Act; or

($c$) is treated as not having limited capability for~work under regulations made under section~18(1) of that Act (disqualification).”; and
\end{enumerate}
\end{quotation}

($b$) in paragraph~12 (pregnancy) after “incapable of work” insert “or~who has limited capability for~work”.
\end{enumerate}

(24) In Schedule~1 (applicable amounts) in paragraph~1(3)—
\begin{enumerate}\item[]
($a$) in paragraph~($a$)—
\begin{enumerate}\item[]
(i) in sub-paragraph~(iii)  after “income support” insert “or~an income-related employment and~support allowance”; and

(ii) in sub-paragraph~(vii)  after “income support” insert “or~an income-related employment and~support allowance”;
\end{enumerate}

($b$) in paragraph~($f$)(iii)  after “income support” insert “or~an income-related employment and~support allowance”;

($c$) in paragraph~($g$)(iii)  after “income support” insert “or~an income-related employment and~support allowance”;

($d$) in paragraph~($h$)(iii)  after “income support” insert “or~an income-related employment and~support allowance”; and

($e$) in paragraph~20H(1)\footnote{Paragraph~20H was inserted by S.I.~2000/1978 and~sub-paragraph~(1) was amended by S.I.~2003/455.} (additional conditions for~higher pensioner and~disability premium) after sub-paragraph~($e$)  insert—
\begin{quotation}
“($ee$) has had limited capability for~work or~has been treated as having limited capability for~work for~a continuous period of not less than—
\begin{enumerate}\item[]
(i) 196 days in the case of a member of a joint-claim couple who is terminally ill within the meaning of regulation~2(1) of the Employment and~Support Allowance Regulations; or

(ii) 364 days in any other case,
\end{enumerate}
and~for~these purposes any two or~more periods of limited capability for~work separated by a break of not more than 12 weeks is to be treated as one continuous period;”.
\end{quotation}
\end{enumerate}

(25) In Schedule~2 (housing costs)—
\begin{enumerate}\item[]
($a$) in paragraph~1 (housing costs)—
\begin{enumerate}\item[]
(i) in sub-paragraph~(3)—
\begin{enumerate}\item[]
($aa$) after ($c$)  omit “or”; and

($bb$) and~after ($d$)  add—
\begin{quotation}
“or

($e$) who is in receipt of an employment and~support allowance which includes an amount under section~2(2) or~(3) or~4(4) or~(5) of the Welfare Reform Act (components).”; and
\end{quotation}
\end{enumerate}

(ii) in sub-paragraph~(4) after “disqualification etc.)”\ add “or~disqualified for~receiving employment and~support allowance or~treated as not having limited capability for~work in accordance with regulations made under section~18 of the Welfare Reform Act (disqualification)”.
\end{enumerate}

($b$) in paragraph~1A\footnote{Paragraph~1A was inserted by S.I.~1997/2305 and~amended by S.I.~2007/3183.} (previous entitlement to income support and~state pension credit)—
\begin{enumerate}\item[]
(i) in the heading after “income support” insert “,~income-related employment and~support allowance”;

(ii) after “income support” each time it occurs insert “or~income-related employment and~support allowance”;

(iii) in sub-paragraph~(1)($a$)  after “Income Support Regulations” add “or~paragraphs~16 to 18 of Schedule~6 to the Employment and~Support Allowance Regulations”; and

(iv) in sub-paragraph~(1A)($a$)\footnote{Sub-paragraph~(1A) was inserted by S.I.~2000/1978.} after “Income Support Regulations” add “or~paragraphs~16 or~17 of Schedule~6 to the Employment and~Support Allowance Regulations”;
\end{enumerate}

($c$) in paragraph~6 (existing housing costs)—
\begin{enumerate}\item[]
(i) in sub-paragraph~(3) for~“or~state pension credit” substitute “,~state pension credit or~income-related employment and~support allowance”; and

(ii) in sub-paragraph~(4) after “income support” insert “or~income-related employment and~support allowance”;
\end{enumerate}

($d$) in paragraph~7 (new housing costs)—
\begin{enumerate}\item[]
(i) in sub-paragraph~(2A)\footnote{Sub-paragraph~(2A) was inserted by S.I.~1997/2305.} after “income support” insert “or income-related employment and~support allowance”; and

(ii) in sub-paragraph~(2B)\footnote{Sub-paragraph~(2B) was inserted by S.I.~2000/1978.} after “income support” insert “or income-related employment and~support allowance”;
\end{enumerate}

($e$) in paragraph~13(6)($a$)  (linking rule) for~“or~incapacity benefit” substitute “,~incapacity benefit or~contributory employment and~support allowance”;

($f$) in paragraph~17(7) (non-dependant deductions)—
\begin{enumerate}\item[]
(i) after paragraph~($g$)  omit “or”; and

(ii) after paragraph~($h$)  add—
\begin{quotation}
“or

($i$) he is aged less than 25 and~is in receipt of employment and~support allowance which does not include an amount under section~2(2) or~(3) or~4(4) or~(5) of the Welfare Reform Act (components)”; and
\end{quotation}
\end{enumerate}

($g$) in paragraph~18 (continuity with income support)—
\begin{enumerate}\item[]
(i) in the heading after “income support” add “or~income-related employment and~support allowance”; and

(ii) in sub-paragraph~(1)—
\begin{enumerate}\item[]
($aa$) after “income support” the first time it occurs insert “or~income-related employment and~support allowance”; and

($bb$) in paragraph~($c$)  after “income support” add “or~income-related employment and~support allowance”.
\end{enumerate}
\end{enumerate}
\end{enumerate}

(26) In paragraph~5(7) of Schedule~6 (sums to be disregarded in the calculation of earnings) for~“or~income support” each time it occurs substitute “,~income support or~an employment and~support allowance”.

(27) In paragraph~1(5) of Schedule~6A\footnote{Schedule~was inserted by S.I.~2000/1978.} (sums to be disregarded in the calculation of earnings of members of joint-claim couples) for~“income support” each time it occurs substitute “,~income support or~an employment and~support allowance”.

(28) In Schedule~7 (sums to be disregarded in the calculation of income other than earnings)—
\begin{enumerate}\item[]
($a$) in paragraph~8($b$)  for~“or~income support” substitute “,~income support or~employment and~support allowance”; and

($b$) in paragraph~14(1)($a$)\footnote{Paragraph~14(1)($a$) was amended by S.I.~2004/565.} for~“or~severe disablement allowance” substitute “,~severe disablement allowance or~employment and~support allowance”.
\end{enumerate}

(29) In paragraph~12\footnote{Paragraph~12 was amended by S.I.~1996/2538, 2001/2333, 2002/2380, 2003/455 and~2005/574.} of Schedule~8 (capital to be disregarded)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~(1)($b$)  after “working tax credit” add “or~an income-related employment and~support allowance”; and

($b$) in sub-paragraph~(3) for~“or~of income support” each time it occurs substitute “,~income support or~of an income-related employment and~support allowance”.
\end{enumerate}

\subsection[4. Amendment of the State Pension Credit Regulations 2002]{Amendment of the State Pension Credit Regulations 2002}

4.---(1)  The State Pension Credit Regulations 2002\footnote{S.I.~2002/1792.} are amended as follows.

(2) In regulation~1(2) (citation, commencement and~interpretation)—
\begin{enumerate}\item[]
($a$) after the definition of “close relative”\footnote{Definition was amended by S.I.~2005/2877.} insert—
\begin{quotation}
““contributory employment and~support allowance” means a contributory allowance under Part~I of the Welfare Reform Act (employment and~support allowance);”;
\end{quotation}

($b$) after the definition of “Eileen Trust” insert—
\begin{quotation}
““the Employment and~Support Allowance Regulations” means the Employment and~Support Allowance Regulations 2008;”;
\end{quotation}

($c$) after the definition of “a guaranteed income payment”\footnote{Definition was inserted by S.I.~2005/574.} insert—
\begin{quotation}\sloppy
““income-related employment and~support allowance” means an income-related allowance under Part~I of the Welfare Reform Act (employment and~support allowance);”; and
\end{quotation}

($d$) after the definition of “water charges” add—
\begin{quotation}
““the Welfare Reform Act” means the Welfare Reform Act 2007.”.
\end{quotation}
\end{enumerate}

(3) In regulation~9 (qualifying income for~the purposes of savings credit) after sub-paragraph~($f$)  add—
\begin{quotation}
“($g$) contributory employment and~support allowance.”.
\end{quotation}

(4) In regulation~13A(1)($a$)\footnote{Regulation~was inserted by S.I.~2002/3019.} (part-weeks) after “income support” insert “,~an income-related employment and~support allowance”.

(5) In regulation~13B(1)\footnote{Regulation~was inserted by S.I.~2002/3019.} (date on which benefits are treated as paid) after sub-paragraph~($d$)  add—
\begin{quotation}
“($e$) contributory employment and~support allowance.”.
\end{quotation}

(6) In regulation~15(4)\footnote{Paragraph~(4) was amended by S.I.~2005/3360.} (income for~the purposes of the Act) after sub-paragraph~($c$)  add—
\begin{quotation}
“($d$) section~3 of the Welfare Reform Act (deductions from contributory allowance).”.
\end{quotation}

(7) In paragraph~6\footnote{Paragraph~6 was amended by S.I.~2002/3197 and~2006/588.} of Schedule~1 (amount applicable for~former claimants of income support or~income-related jobseeker’s allowance)—
\begin{enumerate}\item[]
($a$) in the heading for~“or~income-related jobseeker’s allowance” substitute “,~income-based jobseeker’s allowance or~income-related employment and~support allowance”;

($b$) in sub-paragraph~(2) for~“or~an income-based jobseeker’s allowance” substitute “,~an income-based jobseeker’s allowance or~an income-related employment and~support allowance”;

($c$) in sub-paragraph~(5)—
\begin{enumerate}\item[]
(i) after paragraph~($a$)  omit “or”;

(ii) after paragraph~($b$)  insert—
\begin{quotation}
“or

($c$) for~the purposes of determining his entitlement to income-related employment and~support allowance,”; and
\end{quotation}

(iii) in sub-paragraph~(v)  after “Income Support Regulations” insert “,~paragraph~7 of Schedule~4 to the Employment and~Support Allowance Regulations”; and
\end{enumerate}

($d$) in sub-paragraph~(10)($a$)  after “Jobseeker’s Allowance Regulations” insert “or~paragraph~20(2) of Schedule~6 to the Employment and~Support Allowance Regulations”.
\end{enumerate}

(8) In Schedule~2 (housing costs)—
\begin{enumerate}\item[]
($a$) in paragraph~1 (housing costs)—
\begin{enumerate}\item[]
(i) in sub-paragraph~(2)($a$)(iii)  after paragraph~($cc$)  add—
\begin{quotation}
“or

($dd$) is in receipt of an employment and~support allowance which includes an amount under section~2(2) or~(3) or~4(4) or~(5) of the Welfare Reform Act (components).”; and
\end{quotation}

(ii) in sub-paragraph~(3) after “disqualification etc.)”\ add “or~disqualified for~receiving employment and~support allowance or~treated as not having limited capability for~work in accordance with regulations made under section~18 of the Welfare Reform Act (disqualification)”;
\end{enumerate}

($b$) in paragraph~5 (housing costs not met)—
\begin{enumerate}\item[]
(i) in sub-paragraph~(4) after “income-based jobseeker’s allowance” each time it occurs insert “,~income-related employment and~support allowance”; and

(ii) in sub-paragraph~(5) for~“or~state pension credit” substitute “,~state pension credit or~income-related employment and~support allowance”;
\end{enumerate}

($c$) in paragraph~7 (the calculation for~loans)—
\begin{enumerate}\item[]
(i) in sub-paragraph~(4A)($a$)  after “income support” insert “,~income\hspace{0pt}-related employment and~support allowance”;

(ii) in sub-paragraph~(4B)—
\begin{enumerate}\item[]
($aa$) after paragraph~($a$)  omit “or”; and

($bb$) after paragraph~($b$)  for~“and” substitute—
\begin{quotation}
“or

($c$) where the earlier entitlement was to an income-related employment and~support allowance, if their applicable amount included an amount determined in accordance with Schedule~6 to the Employment and~Support Allowance Regulations as applicable to them in respect of a loan which qualifies under paragraph~16 to 18 of that Schedule, and”;
\end{quotation}
\end{enumerate}
\end{enumerate}

($d$) in paragraph~10(10) (excessive housing costs) for~“and~income-based jobseeker’s allowance” substitute “,~income-based jobseeker’s allowance and~income-related employment and~support allowance”; and

($e$) in paragraph~14(7) (persons residing with the claimant) after ($f$)  add—
\begin{quotation}
“($g$) if he is aged less than 25 and~is in receipt of employment and~support allowance which does not include an amount under section~2(2) or~(3) or~4(4) or~(5) of the Welfare Reform Act (components).”.
\end{quotation}
\end{enumerate}

(9) In Schedule~5 (income from capital)—
\begin{enumerate}\item[]
($a$) in paragraph~20(2)\footnote{Sub-paragraph~(2) was substituted by S.I.~2003/2274.} after paragraph~($n$)  add—
\begin{quotation}
“($o$) income-related employment and~support allowance.”;
\end{quotation}

($b$) in paragraph~20A(2)\footnote{Sub-paragraph~(2) was substituted by S.I.~2003/2274 and~amended by S.I.~2002/3197.}—
\begin{enumerate}\item[]
(i) after sub-paragraph~($c$)  omit “or”; and

(ii) after paragraph~($d$)  add—
\begin{quotation}
“or

($e$) paragraph~11(2) of Schedule~9 to the Employment and~Support Allowance Regulations,”.
\end{quotation}
\end{enumerate}
\end{enumerate}

(10) In paragraph~4\footnote{Paragraph~4 was amended by S.I.~2002/3197.} of Schedule~6 (sums disregarded from claimant’s earnings)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~(1)($a$)—
\begin{enumerate}\item[]
(i) after paragraph~(v)  omit “or”; and

(ii) after paragraph~(vi)  add—
\begin{quotation}
“(vii) employment and~support allowance; or”;
\end{quotation}
\end{enumerate}

($b$) in sub-paragraph~(2) for~“or~income-based jobseeker’s allowance” substitute “,~income-based jobseeker’s allowance or~income-related employment and~support allowance”.
\end{enumerate}

\section[Part III --- The Social Fund]{Part III\\*The Social Fund}

\renewcommand\parthead{--- Part III}

\subsection[5. Amendment of the Social Fund (Recovery by Deductions from Benefits) Regulations 1988]{Amendment of the Social Fund (Recovery by Deductions from Benefits) Regulations 1988}

5.  In regulation~3 of the Social Fund (Recovery by Deductions from Benefits) Regulations 1988\footnote{S.I.~1988/35.} (benefits from which an award may be recovered) after sub-paragraph~($d$)  insert—
\begin{quotation}
“($dd$) an employment and~support allowance under section~1 of the Welfare Reform Act 2007;”.
\end{quotation}

\subsection[6. Amendment of the Social Fund Cold Weather Payments (General) Regulations 1988]{Amendment of the Social Fund Cold Weather Payments (General) Regulations 1988}

6.---(1)  The Social Fund Cold Weather Payments (General) Regulations 1988\footnote{S.I.~1988/1724.} are amended as follows.

(2) In regulation~1(2) (citation, commencement and~interpretation)—
\begin{enumerate}\item[]
($a$) after the definition of “the Act” insert—
\begin{quotation}
““the Welfare Reform Act” means the Welfare Reform Act 2007;”;
\end{quotation}

($b$) in the definition of “claimant”\footnote{Definition was substituted by S.I.~1991/2238.} for~“or~income-based jobseeker’s allowance” substitute “,~income-based jobseeker’s allowance or~income-related employment and~support allowance”; and

($c$) after the definition of “income-based jobseeker’s allowance” insert—
\begin{quotation}\sloppy
““income-related employment and~support allowance” means an income-related allowance under Part~I of the Welfare Reform Act (employment and~support allowance);”.
\end{quotation}
\end{enumerate}

(3) In regulation~1A(1)\footnote{Regulation~1A was inserted by S.I.~1991/2448 and~paragraph~(1) was amended by S.I.~2002/3019, 2003/1121 and~2005/2687.} (prescribed description of persons)—
\begin{enumerate}\item[]
($a$) for~“or~income-based jobseeker’s allowance” substitute “,~income-based jobseeker’s allowance or~income-related employment and~support allowance”; and

($b$) after sub-paragraph~(ic) insert—
\begin{quotation}
“(id) whose applicable amount includes one or~more of the premiums specified in paragraphs~5 to 8 of Schedule~4 to the Employment and~Support Allowance Regulations 2008; or

(ie) whose applicable amount includes an amount under section~4(2)($b$)  of the Welfare Reform Act; or”.
\end{quotation}
\end{enumerate}

\subsection[7. Amendment of the Social Fund Winter Fuel Payment Regulations 2000]{Amendment of the Social Fund Winter Fuel Payment Regulations 2000}

7.---(1)  The Social Fund Winter Fuel Payment Regulations 2000\footnote{S.I.~2000/729.} are amended as follows.

(2) In regulation~1(2) (citation, commencement and~interpretation) after the definition of “free in-patient treatment” insert—
\begin{quotation}
““income-related employment and~support allowance” means an income-related allowance under Part~I of the Welfare Reform Act 2007 (employment and~support allowance);”.
\end{quotation}

(3) In regulation~2(1)($b$)(ii)\footnote{Regulation~2 was substituted by S.I.~2003/1737.} (social fund winter fuel payments) for~“or~an income-based jobseeker’s allowance” substitute “,~an income-based jobseeker’s allowance or~an income-related employment and~support allowance”.

(4) In regulation~3(1)($a$)(i)  (persons not entitled to a social fund winter fuel payment) for~“or~an income-based jobseeker’s allowance” substitute “,~an income-based jobseeker’s allowance or~an income-related employment and~support allowance”.

(5) In regulation~4(2) (making a winter fuel payment without a claim) for~“or~state pension credit” substitute “,~state pension credit or~an income-related employment and~support allowance”.

\subsection[8. Amendment of the Social Fund Maternity and~Funeral Expenses (General) Regulations 2005]{Amendment of the Social Fund Maternity and~Funeral Expenses (General) Regulations 2005}

8.---(1)  The Social Fund Maternity and~Funeral Expenses (General) Regulations 2005\footnote{S.I.~2005/3061.} are amended as follows.

(2) In regulation~3 (interpretation)—
\begin{enumerate}\item[]
($a$) in paragraph~(1)—
\begin{enumerate}\item[]
(i) after the definition of “the Act” insert—
\begin{quotation}
““the Employment and~Support Allowance Regulations” means the Employment and~Support Allowance Regulations 2008;”; and
\end{quotation}

(ii) after the definition of “income-based jobseeker’s allowance” insert—
\begin{quotation}
““income-related employment and~support allowance” means an income-related allowance under Part~I of the Welfare Reform Act 2007 (employment and~support allowance);”;
\end{quotation}
\end{enumerate}

($b$) in paragraph~(3) after “Regulations” add “or~regulation~2(1) of the Employment and~Support Allowance Regulations”; and

($c$) in paragraph~(4)($a$)  after “Income Support Regulations” insert “,~in regulation~156 of the Employment and~Support Allowance Regulations”.
\end{enumerate}

(3) In regulation~5(1)($a$)  (entitlement)—
\begin{enumerate}\item[]
($a$) after paragraph~(iv)  omit “or”; and

($b$) after paragraph~(v)  for~“; and” substitute—
\begin{quotation}
“or

(vi) income-related employment and~support allowance; and”.
\end{quotation}
\end{enumerate}

(4) In regulation~7(4)($a$)  (funeral payments: entitlement)—
\begin{enumerate}\item[]
($a$) after paragraph~(vi)  omit “or”; and

($b$) after paragraph~(vii)  insert—
\begin{quotation}
“(viii) income-related employment and~support allowance; or”.
\end{quotation}
\end{enumerate}

\section[Part IV --- Administrative provisions]{Part IV\\*Administrative provisions}

\subsection[Chapter I --- The Social Security (Claims and~Payments) Regulations 1987]{Chapter I\\*The Social Security (Claims and~Payments) Regulations 1987}

\renewcommand\parthead{--- Part IV Chapter I}

\subsubsection[9. Amendment of the Social Security (Claims and~Payments) Regulations 1987]{Amendment of the Social Security (Claims and~Payments) Regulations 1987}

9.  The Social Security (Claims and~Payments) Regulations 1987\footnote{S.I.~1987/1968.} are amended in accordance with this Chapter.

\subsubsection[10. Amendment of regulation~2]{Amendment of regulation~2}

10.  In regulation~2 (interpretation)—
\begin{enumerate}\item[]
($a$) in paragraph~(1)—
\begin{enumerate}\item[]
(i) after the definition of “electronic communication”\footnote{Definition inserted by S.I.~2003/2800.} insert—
\begin{quotation}
““the Employment and~Support Allowance Regulations” means the Employment and~Support Allowance Regulations 2008;”;
\end{quotation}

(ii) after the definition of “joint-claim couple”\footnote{Definition was inserted by S.I.~2000/1892.} insert—
\begin{quotation}
““limited capability for~work” has the same meaning as in section~1(4) of the Welfare Reform Act”; and
\end{quotation}

(iii) after the definition of “week” insert—
\begin{quotation}
““the Welfare Reform Act” means the Welfare Reform Act 2007;”; and
\end{quotation}
\end{enumerate}

($b$) in paragraph~(2)($b$)\footnote{Paragraph~(2)($b$) was amended by S.I.~1988/1725, 1996/1360, 1999/2572, 2002/3019 and~2005/1551.} for~“and~a shared additional pension” substitute “,~a shared additional pension or~an employment and~support allowance under Part~I of the Welfare Reform Act”.
\end{enumerate}

\subsubsection[11. Amendment of regulation~3]{Amendment of regulation~3}

11.  In regulation~3 (claims not required for~entitlement to benefit in certain cases)—
\begin{enumerate}\item[]
($a$) in paragraph~($h$)(ii)\footnote{Sub-paragraph~($h$) was added by S.I.~1999/2556 and~(ii) was amended by S.I.~2001/488.} after “allowance” insert “or~an income-related employment and~support allowance”; and

($b$) after paragraph~($i$)\footnote{Paragraph~($i$) was added by S.I.~2005/1551.} add—
\begin{quotation}
“($j$) in the case of an employment and~support allowance where the beneficiary has made and~is pursuing an appeal against the decision of the Secretary of State that he does not have limited capability for~work.”.
\end{quotation}
\end{enumerate}

\subsubsection[12. Amendment of regulation~4]{Amendment of regulation~4}

12.  In regulation~4(10)\footnote{Paragraph~(10) was inserted by S.I.~2002/3019.} (making a claim for~benefit), after “state pension credit” insert “or~an employment and~support allowance”.

\subsubsection[13. Claims for~employment and~support allowance]{Claims for~employment and~support allowance}

13.  After regulation~4F\footnote{Regulation~4F was inserted by S.I.~2002/3019.} (making a claim after attaining the qualifying age: date of claim) insert—
\begin{quotation}
\subsection*{“Making a claim for~employment and~support allowance by telephone}

4G.---(1)  A claim (“a telephone claim”) for~an employment and~support allowance may be made by telephone call to the telephone number specified by the Secretary of State.

(2) Where the Secretary of State, in any particular case, directs that the person making the claim approves a written statement of his circumstances, provided for~the purpose by the Secretary of State, a telephone claim is not a valid claim unless the person complies with the direction.

(3) A telephone claim is defective unless the Secretary of State is provided, during that telephone call, with all the information he requires to determine the claim.

(4) Where a telephone claim is defective, the Secretary of State is to advise the person making it of the defect and~of the relevant provisions of regulation~6(1F) relating to the date of claim.

(5) If the person corrects the defect within one month, or~such longer period as the Secretary of State considers reasonable, of the date the Secretary of State last drew attention to the defect, the Secretary of State must treat the claim as if it had been properly made in the first instance.

\subsection*{Making a claim for~employment and~support allowance in writing}

4H.---(1)  A claim (“a written claim”) for~employment and~support allowance need only be made in writing if the Secretary of State so directs in any particular case but a written claim may be made whether or~not a direction is issued.

(2) A written claim must be made on a form approved for~the purpose by the Secretary of State and~be made in accordance with the instructions on the form.

(3) A claim in writing may also be made at the offices of—
\begin{enumerate}\item[]
($a$) a local authority administering housing benefit or~council tax benefit;

($b$) a person providing to such an authority services relating to housing benefit or~council tax benefit; or

($c$) a person authorised to exercise the function of a local authority relating to housing benefit or~council tax benefit,
\end{enumerate}
if the Secretary of State has arranged with the local authority or~person specified in sub-paragraph~($b$)  or~($c$)  for~them to receive claims in accordance with this paragraph.

(4) Where a written claim is made in accordance with paragraph~(3), on receipt of that claim the local authority or~other person specified in that paragraph—
\begin{enumerate}\item[]
($a$) must forward the claim to the Secretary of State as soon as reasonably practicable;

($b$) may receive information or~evidence relating to the claim supplied by—
\begin{enumerate}\item[]
(i) the person making, or~who has made, the claim; or

(ii) other persons in connection with the claim,
\end{enumerate}
and~shall forward it to the Secretary of State as soon as reasonably practicable;

($c$) may obtain information or~evidence relating to the claim from the person who has made the claim, but not any medical information or~evidence except for~that which the claimant must provide in accordance with instructions on the form, and~must forward the information or~evidence to the Secretary of State as soon as reasonably practicable;

($d$) may record information or~evidence relating to the claim supplied or~obtained in accordance with sub-paragraph~($b$)  or~($c$)  and~may hold the information or~evidence (whether as supplied or~obtained or~as recorded) for~the purpose of forwarding it to the Secretary of State; and

($e$) may give information and~advice with respect to the claim to the person who makes, or~who has made, the claim.
\end{enumerate}

(5) Paragraphs (4)($b$)  to ($e$)  apply in respect of information, evidence and~advice relating to any claim whether the claim is made in accordance with paragraph~(3) or~otherwise.

(6) If a written claim is defective when first received, the Secretary of State is to advise the person making it of the defect and~of the provisions of regulation~6(1F) relating to the date of claim.

(7) If that person corrects the defect so that the claim then satisfies the requirements of paragraph~(2) and~does so within one month, or~such longer period as the Secretary of State considers reasonable, of the date the Secretary of State last drew attention to the defect, the claim must be treated as having been properly made in the first instance.

\subsection*{Claims for~employment and~support allowance: supplemental}

4I.---(1)  Where a person who is a member of a couple may be entitled to an income-related employment and~support allowance the claim for~an employment and~support allowance must be made by whichever member of the couple they agree should claim or, in default of agreement, by such one of them as the Secretary of State may choose.

(2) Where one member of a couple (“the former claimant”) is entitled to an income-related employment and~support allowance under an award but a claim for~an employment and~support allowance is made by the other member of the couple and~the Secretary of State considers that the other member is entitled to an income-related employment and~support allowance, then, if both members of the couple confirm in writing that they wish the claimant to be the other member, the former claimant’s entitlement terminates on the day the partner’s claim is actually made or, if earlier, is treated as made.

(3) In calculating any period of one month for~the purposes of regulations 4G and~4H, any period commencing on a day on which a person is first notified of a decision in connection with his failure to take part in a work-focused interview and~ending on a day on which he was notified that that decision has been revised so that the decision as revised is that he did take part is to be disregarded.

(4) Employment and~support allowance is a relevant benefit for~the purposes of section~7A of the 1992 Act.”.
\end{quotation}

\subsubsection[14. Amendment of regulation~6]{Amendment of regulation~6}

14.  In regulation~6 (date of claim) after paragraph~(1E)\footnote{Paragraph~(1E) was inserted by S.I.~2006/832 and~amended by S.I.~2007/2911.} insert—
\begin{quotation}
“(1F) For~employment and~support allowance—
\begin{enumerate}\item[]
($a$) in the case of a telephone claim made in accordance with regulation~4G(1) the date of claim is the date of the telephone call or~the first day in respect of which the claim is made, if later;

($b$) subject to sub-paragraph~($c$)  in the case of a written claim which meets the requirements of regulation~4H(2) the date of claim is the date the claim form was received in an appropriate office or~office mentioned in regulation~4H(3) or~the first day in respect of which the claim is made, if later;

($c$) where the claimant notifies the Secretary of State (by whatever means) of his intention of making a claim and, within one month or~such longer period as the Secretary of State considers reasonable of first notification, a claim mentioned in sub-paragraph~($b$)  is received, in an office mentioned in that sub-paragraph, the date of claim is the date notification was made or~the first day in respect of which the claim is made, if later.”.
\end{enumerate}
\end{quotation}

\subsubsection[15. Amendment of regulation~7]{Amendment of regulation~7}

15.  In regulation~7(4)\footnote{Paragraph~(4) was added by S.I.~1995/2303 and~amended by S.I.~1996/1460, 1999/2572 and~2002/3019.} (evidence and~information) for~“or~state pension credit” substitute “,~state pension credit or~employment and~support allowance”.

\subsubsection[16. Amendment of regulation~10]{Amendment of regulation~10}

16.  In regulation~10 (claim for~incapacity benefit or~severe disablement allowance where no entitlement to statutory sick pay or~statutory maternity pay)—
\begin{enumerate}\item[]
($a$) in the heading for~“or~severe disablement allowance” substitute “,~severe disablement allowance or~employment and~support allowance”; and

($b$) after paragraph~(1)\footnote{Paragraph~(1) was amended by S.I.~1994/2943.} insert—
\begin{quotation}
“(1A) Paragraph~(2) also applies to a claim for~an employment and~support allowance for~a period of limited capability for~work in relation to which the claimant gave his employer a notice of incapacity under regulation~7 of the Statutory Sick Pay (General) Regulations 1982\footnote{S.I.~1982/894.}, and~for~which he has been informed in writing by his employer that there is no entitlement to statutory sick pay.”.
\end{quotation}
\end{enumerate}

\subsubsection[17. Amendment of regulation~11]{Amendment of regulation~11}

17.  In regulation~11\footnote{Regulation~11 was amended by S.I.~1994/2943 and~1997/793.} (special provisions where it is certified that a woman is expected to be confined or~where she has been confined)—
\begin{enumerate}\item[]
($a$) in paragraph~(1) for~“or~severe disablement allowance” substitute “,~severe disablement allowance or~an employment and~support allowance,”; and

($b$) in paragraph~(2) for~“or~severe disablement allowance” substitute “,~severe disablement allowance or~an employment and~support allowance,”.
\end{enumerate}

\subsubsection[18. Amendment of regulation~13]{Amendment of regulation~13}

18.  In regulation~13(9)\footnote{Paragraph~(9) was added by S.I.~2007/1331.} (advance claims and~awards)—
\begin{enumerate}\item[]
($a$) after sub-paragraph~($a$)  omit “or”; and

($b$) after sub-paragraph~($b$)  add—
\begin{quotation}
“and

($c$) a claim for~an employment and~support allowance made by a person from abroad as defined in regulation~70 of the Employment and~Support Allowance Regulations (special cases: supplemental---persons from abroad).”.
\end{quotation}
\end{enumerate}

\subsubsection[19. Amendment of regulation~16]{Amendment of regulation~16}

19.  In regulation~16(4)\footnote{Paragraph~(4) was amended by S.I.~1988/522, 1994/2943, 1996/1460 and~2002/3019.} (date of entitlement under an award for~the purpose of payability of benefit and~effective date of change of rate) after “incapacity benefit” insert “,~employment and~support allowance”.

\subsubsection[20. Amendment of regulation~16A]{Amendment of regulation~16A}

20.  In regulation~16A(2)($a$)\footnote{Regulation~16A was inserted by S.I.~2002/3019.} (date of entitlement under an award of state pension credit for~the purpose of payability and~effective date of change of rate) for~“or~income-based jobseeker’s allowance” substitute “,~income-based jobseeker’s allowance or~income-related employment and~support allowance”.

\subsubsection[21. Payment]{Payment}

21.  After regulation~26B\footnote{Regulation~26B was inserted by S.I.~2002/3019.} (state pension credit) insert—
\begin{quotation}
\subsection*{“Employment and~support allowance}

26C.---(1)  Subject to paragraphs~(3) to (7), employment and~support allowance is to be paid fortnightly in arrears on the day of the week determined in accordance with paragraph~(2).

(2) The day specified for~the purposes of paragraph~(1) is the day in column (2) which corresponds to the series of numbers in column (1) which includes the last 2 digits of the claimant’s national insurance number—

{\noindent
\begin{longtable}{ll}
\hline
(1)	&(2)\\
\hline
\endhead
\hline
\endlastfoot
00 to 19	&Monday\\
20 to 39	&Tuesday\\
40 to 59	&Wednesday\\
60 to 79	&Thursday\\
80 to 99	&Friday\\
\end{longtable}

}

(3) The Secretary of State may, in any particular case or~class of case, arrange that the claimant be paid otherwise than fortnightly.

(4) The Secretary of State may, in any particular case or~class of case, arrange that employment and~support allowance be paid on any day of the week and~where it is in payment to any person and~the day on which it is payable is changed, it must be paid at a daily rate of \nicefrac{1}{7}th of the weekly rate in respect of any of the days for~which payment would have been made but for~that change.\looseness=1

(5) Where the weekly amount of employment and~support allowance is less than £1$.$00 it may be paid in arrears at intervals of not more than 13 weeks.

(6) Where the weekly amount of an employment and~support allowance is less than 10 pence that allowance is not payable.

(7) The provisions of paragraph~2A of Schedule~7 (payment of income support at time of office closure) apply for~the purposes of payment of employment and~support allowance as they apply for~the purposes of payment of income support.”.
\end{quotation}

\subsubsection[22. Amendment of regulation~32]{Amendment of regulation~32}

22.  In regulation~32(3)\footnote{Paragraph~(3) was added by S.I.~1995/2303 and~amended by S.I.~1996/1460, and~2002/3019.} (information to be given and~changes to be notified) for~“or~a jobseeker’s allowance” substitute “,~a jobseeker’s allowance or~an employment and~support allowance”.

\subsubsection[23. Amendment of regulation~36]{Amendment of regulation~36}

23.  In regulation~36(2)($b$)\footnote{Paragraph~(2) was added by S.I.~2002/2660 and~amended by S.I.~2005/2877.} (payment to a partner as alternative payee) for~“or~an income-based jobseeker’s allowance” substitute “,~an income-based jobseeker’s allowance or~an income-related employment and~support allowance”.

\subsubsection[24. Amendment of Schedule~1]{Amendment of Schedule~1}

24.  In Schedule~1 (benefit claimed and~other benefit which may be treated as if claimed in addition or~in the alternative)—
\begin{enumerate}\item[]
($a$) in column (1) (benefit claimed) after the entry “Severe disablement allowance for~a woman” insert “Employment and~support allowance for~a woman” and~in the corresponding place in column (2) (alternative benefit) insert “Maternity allowance.”; and

($b$) in column (2) in the entry corresponding to “Maternity allowance”\footnote{Entry was amended by S.I.~1994/2943.} for~“or~severe disablement allowance” substitute “,~severe disablement allowance or~employment and~support allowance”.
\end{enumerate}

\subsubsection[25. Amendment of Schedule~4]{Amendment of Schedule~4}

25.  In Schedule~4 (prescribed times for~claiming benefit)—
\begin{enumerate}\item[]
($a$) in column (1) (description of benefit) after the entry “15. Shared additional pension”\footnote{Paragraph~15 was added by S.I.~2005/1551.} add “16. Employment and~support allowance”; and

($b$) in column (2) (prescribed time for~claiming benefit) in the corresponding place insert “The day in respect of which the claim is made and~the period of three months immediately following it.”.
\end{enumerate}

\subsubsection[26. Amendment of Schedule~9]{Amendment of Schedule~9}

26.---(1)  Schedule~9 (deductions from benefit and~direct payment to third parties) is amended as follows.

(2) In paragraph~1 (interpretation)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~(1)—
\begin{enumerate}\item[]
(i) after the definition of “contribution-based jobseeker’s allowance” insert—
\begin{quotation}\sloppy
““contributory employment and support allowance” means any contributory employment and support allowance which does not fall within the definition of “specified benefit””;
\end{quotation}

(ii) in the definition of “housing costs”\footnote{Definition was substituted by S.I.~1996/1460 and~amended by S.I.~2002/3019 and~2005/777.} after paragraph~($c$)  add—
\begin{quotation}
“or

($d$) Schedule~6 to the Employment and~Support Allowance Regulations but—
\begin{enumerate}\item[]
(i) excludes costs under paragraph~18(1)($f$)  of that Schedule~(tents and~tent sites); and

\begin{sloppypar}
(ii) includes costs under paragraph~18(1)($a$)  (ground rent) and~18(1)($c$)  (rent charges) of that Schedule~but only where they are paid with costs under paragraph~18(1)($b$)  of that Schedule~(service charges);”;
\end{sloppypar}
\end{enumerate}
\end{quotation}

(iii) in the definition of “mortgage payment”\footnote{Definition was substituted by S.I.~1996/1460 and~amended by S.I.~2002/3019.} after paragraph~($b$)  omit “or” and~after paragraph~($c$)  add—
\begin{quotation}
“or

($d$) Schedule~6 to the Employment and~Support Allowance Regulations in accordance with paragraphs~8 to 11 of that Schedule~(housing costs to be met in employment and~support allowance) on a loan which qualifies under paragraph~16 or~17 of that Schedule, but less any amount deducted under paragraph~19 of that Schedule~(non-dependant deductions),”;
\end{quotation}

(iv) in the definition of “personal allowance for~a single claimant aged not less than 25 years”\footnote{Definition was amended by S.I.~1991/2284, 1996/1460 and~2002/3019.} after “Jobseeker’s Allowance Regulations” add “or, in connection with employment and~support allowance, paragraph~1(1)($b$)  of Schedule~4 to the Employment and~Support Allowance Regulations”; and

(v) in the definition of “specified benefit”\footnote{Definition was substituted by S.I.~1996/672 and~amended by S.I.~1996/1460 and~3195, 2002/2441 and~3019 and~2005/777.} after paragraph~($d$)  add—
\begin{quotation}
“($e$) subject to sub-paragraph~(3), employment and support allowance;”;
\end{quotation}
\end{enumerate}

($b$) after sub-paragraph~(2) add—
\begin{enumerate}\item[]
“(3) For~the purposes of the definition of “specified benefit” in sub-paragraph~(1) “employment and~support allowance” means—
\begin{enumerate}\item[]
($a$) income-related employment and~support allowance; and

($b$) in a case where, if there was no entitlement to a contributory employment and~support allowance, there would be entitlement to income-related employment and~support allowance at the same rate, contributory employment and~support allowance.”.
\end{enumerate}
\end{enumerate}
\end{enumerate}

(3) In paragraph~3(2A)\footnote{Sub-paragraph~(2A) was inserted by S.I.~1992/1026 and~amended by S.I.~1995/1613 and~2927, 1996/1460 and~2002/3019.} (housing costs)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($b$)  after “State Pension Credit Regulations” insert “or~paragraph~6(10) or~(13) or~paragraph~19 of Schedule~6 to the Employment and~Support Allowance Regulations”; and

($b$) in the description of “$C$” after “State Pension Credit Regulations” add “or~paragraph~6(10) or~(13) or~paragraph~19 of Schedule~6 to the Employment and~Support Allowance Regulations”.
\end{enumerate}

(4) In paragraph~4 (miscellaneous accommodation costs)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~(1)\footnote{Sub-paragraph~(1) was amended by S.I.~1989/136, 1992/3147, 1996/1460, 1999/3178, 2002/398, 2003/2325 and~2005/2687.}—
\begin{enumerate}\item[]
(i) for~“or~state pension credit” substitute “,~state pension credit or~employment and~support allowance”; and

(ii) in paragraph~($a$)  after “Jobseeker’s Allowance Regulations” insert “or~in the case of employment and~support allowance, regulation~2(1) of the Employment and~Support Allowance Regulations”;
\end{enumerate}

($b$) in sub-paragraph~(2)\footnote{Sub-paragraph~(2) was substituted by S.I.~2003/2325 and~amended by S.I.~2005/2687.}—
\begin{enumerate}\item[]
(i) for~“or~state pension credit” substitute “,~state pension credit or~employment and~support allowance”;

(ii) in paragraph~($a$)—
\begin{enumerate}\item[]
($aa$) for~“or~guarantee credit” substitute “,~guarantee credit or~employment and~support allowance”; and

($bb$) after “Jobseeker’s Allowance Regulations” insert “,~regulation~90 of the Employment and~Support Allowance Regulations”; and
\end{enumerate}

(iii) in paragraph~($b$)  for~“or~guarantee credit” substitute “,~guarantee credit or~employment and~support allowance”; and
\end{enumerate}

($c$) in sub-paragraph~(3)—
\begin{enumerate}\item[]
(i) after paragraph~($b$)  omit “or”; and

(ii) after paragraph~($c$)  add—
\begin{quotation}
“or

($d$) employment and~support allowance for~a period of less than a week calculated in accordance with Part~XIV of the Employment and~Support Allowance Regulations (periods of less than a week).”.
\end{quotation}
\end{enumerate}
\end{enumerate}

(5) In paragraph~4A(6)\footnote{Paragraph~4A was inserted by S.I.~1991/2284 and~sub-paragraph~(6) was substituted by S.I.~1996/1460.} (hostel payments)—
\begin{enumerate}\item[]
($a$) after paragraph~($a$)—
\begin{enumerate}\item[]
(i) omit “or”; and

(ii) after paragraph~($b$)  insert—
\begin{quotation}
“or

($c$) an award of employment and~support allowance is calculated in accordance with regulation~165 of the Employment and~Support Allowance Regulations (entitlement of less than a week etc.),”; and
\end{quotation}
\end{enumerate}

($b$) after “jobseeker’s allowance” the third time it occurs insert “or~employment and~support allowance”.
\end{enumerate}

(6) In paragraph~7B\footnote{Paragraph~7B was inserted by S.I.~1996/2344 and~amended by S.I.~1999/3178.} (arrears of child support maintenance)—
\begin{enumerate}\item[]
($a$) after “jobseeker’s allowance” each time it occurs insert “or~contributory employment and~support allowance”; and

($b$) after sub-paragraph~(3) insert—
\begin{quotation}
“(3A) Subject to sub-paragraphs~(4) and~(5), the amount to be deducted from the beneficiary’s employment and~support allowance under sub-paragraph~(2) is the weekly amount requested from the beneficiary’s employment and~support allowance by the Secretary of State, subject to a maximum of one-third of the amount applicable to the beneficiary under regulation~67(2) of the Employment and~Support Allowance Regulations (prescribed amounts).”.
\end{quotation}
\end{enumerate}

(7) In paragraph~7C(2)($c$)\footnote{Paragraph~7C was inserted by S.I.~2006/3188.} (eligible loans) after sub-paragraph~(iii)  add—
\begin{quotation}
“(iv) employment and~support allowance.”.
\end{quotation}

(8) In paragraph~8(4)($a$)\footnote{Sub-paragraph~(4) was inserted by S.I.~2006/2377.} (maximum amount of payment to third parties)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~(ii)  omit “or”; and

($b$) after sub-paragraph~(iii)  add—
\begin{quotation}
“(iv) in the case of employment and~support allowance, the applicable amount for~the family as is awarded under paragraphs~($a$)  to ($d$)  of regulation~67 (prescribed amounts) or~regulation~68 (polygamous marriages) of the Employment and~Support Allowance Regulations; or”.
\end{quotation}
\end{enumerate}

\subsubsection[27. Amendment of Schedule~9A]{Amendment of Schedule~9A}

27.---(1)  Schedule~9A\footnote{Schedule~9A was inserted by S.I.~1992/1026.} (deductions of mortgage interest from benefit and~payment to qualifying lenders) is amended as follows.

(2) In paragraph~1 (interpretation) in the definition of “relevant benefits”\footnote{Definition was substituted by S.I.~1996/672 and~amended by S.I.~1996/1460 and~3195, 2002/2441 and~3019 and~2005/777.}—
\begin{enumerate}\item[]
($a$) after paragraph~($c$)  omit “and”; and

($b$) after paragraph~($d$)  add—
\begin{quotation}
“and

($e$) income-related employment and~support allowance;”.
\end{quotation}
\end{enumerate}

(3) In paragraph~2($a$)\footnote{Paragraph~2 was substituted by S.I.~1995/1613 and~amended by S.I.~1996/1460, 2002/3019 and~3197 and~2004/2825.} (specified circumstances for~the purposes of regulation~34A) after sub-paragraph~(iii)  add—
\begin{quotation}
“or

(iv) Schedule~6 to the Employment and~Support Allowance Regulations,”.
\end{quotation}

(4) In paragraph~3 (specified part of relevant benefit)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~(1)\footnote{Sub-paragraph~(1) was substituted by S.I.~1995/1613 and~amended by S.I.~1996/1460 and~1999/3178.} after “Jobseeker’s Allowance Regulations” add “or, in the case of employment and~support allowance, a sum equal to the amount of mortgage interest to be met in accordance with paragraphs~8 to 11 of Schedule~6 to the Employment and~Support Allowance Regulations”; and

($b$) in sub-paragraph~(3)\footnote{Sub-paragraph~(3) was amended by S.I.~1995/1613, 1996/1460 and~2002/3019.}—
\begin{enumerate}\item[]
(i) for~“or~income-based jobseeker’s allowance” substitute “income-based jobseeker’s allowance or~income-related employment and~support allowance”;

(ii) in paragraph~($b$)  after “Jobseeker’s Allowance Regulations” insert “or~paragraph~6(10) or~(13) or~19 of Schedule~6 to the Employment and~Support Allowance Regulations”;

(iii) in the definition of “$A$” after “Jobseeker’s Allowance Regulations” add “or~paragraph~1 of Schedule~6 to the Employment and~Support Allowance Regulations”;

(iv) in the definition of “$B$” after “Jobseeker’s Allowance Regulations” add “or~paragraphs~8 to 11 of Schedule~6 to the Employment and~Support Allowance Regulations”; and

(v) in the definition of “$C$” after “Jobseeker’s Allowance Regulations” add “or~paragraph~19 of Schedule~6 to the Employment and~Support Allowance Regulations”.
\end{enumerate}
\end{enumerate}

(5) In paragraph~4(2)($a$)\footnote{Paragraph~4 was amended by S.I.~1995/1613, 1996/1460, 1997/827 and~2002/3019.} (direct payment: more than one loan) after “Jobseeker’s Allowance Regulations” insert “or~paragraph~13 of Schedule~6 to the Employment and~Support Allowance Regulations”.

(6) In paragraph~10\footnote{Paragraph~10 was amended by S.I.~1996/1460, 1997/2305 and~2002/3019.} (provision of information)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~(2)($a$)  after “income support” insert “,~employment and~support allowance”:

($b$) in sub-paragraph~(3)($a$)  after “income support” insert “,~employment and~support allowance”; and

($c$) in sub-paragraph~(4) after “(housing costs)” the first time it occurs insert “,~paragraph~3 of Schedule~6 to the Employment and~Support Allowance Regulations (housing costs)”.
\end{enumerate}

(7) In paragraph~11(2)($a$)(i)\footnote{Paragraph 11 was amended by S.I.~1995/1613, 1996/1460, 2002/3197 and~2004/2825.} (recovery of sums wrongly paid) after “Jobseeker’s Allowance Regulations” insert “,~or~paragraph~13 of Schedule~6 to the Employment and~Support Allowance Regulations”.

\subsubsection[28. Amendment of Schedule~9B]{Amendment of Schedule~9B}

28.---(1)  Schedule~9B\footnote{Schedule~9B was inserted by S.I.~2001/18.} (deductions from benefit in respect of child support maintenance etc.)\ is amended as follows.

(2) In paragraph~2(1)\footnote{Sub-paragraph~(1) was amended by S.I.~2002/3019.} (deductions) for~“or~income-based jobseeker’s allowance” substitute “,~income-based jobseeker’s allowance or~income-related employment and~support allowance”.

(3) In paragraph~3(1)\footnote{Sub-paragraph~(1) was amended by S.I.~2002/3019.} (arrears) for~“or~income-based jobseeker’s allowance” substitute “,~income-based jobseeker’s allowance or~income-related employment and~support allowance”.

(4) In paragraph~5(1)\footnote{Sub-\hspace{0pt}paragraph~(1) was amended by S.I.~2002/3019.} (flat rate maintenance) for~“or~income-based jobseeker’s allowance” substitute “,~income-based jobseeker’s allowance or~income-related employment and~support allowance”.

(5) In paragraph~6(1)\footnote{Sub-paragraph~(1) was amended by S.I.~2002/3019.} (flat rate maintenance (polygamous marriage)) for~“or~income-based jobseeker’s allowance” substitute “,~income-based jobseeker’s allowance or~income-related employment and~support allowance”.

(6) In paragraph~8 (general) after “1987” insert “,~regulation~104(3) of the Employment and~Support Allowance Regulations”.

\subsection[Chapter II --- The Social Security and~Child Support (Decisions and~Appeals) Regulations 1999]{Chapter II\\*The Social Security and~Child Support (Decisions and Appeals) Regulations 1999}

\renewcommand\parthead{--- Part IV Chapter II}

\subsubsection[29. Amendment of the Social Security and~Child Support (Decisions and~Appeals) Regulations 1999]{Amendment of the Social Security and~Child Support (Decisions and~Appeals) Regulations 1999}

29.  The Social Security and~Child Support (Decisions and~Appeals) Regulations 1999\footnote{S.I.~1999/991.} are amended in accordance with this Chapter.

\subsubsection[30. Amendment of regulation~1]{Amendment of regulation~1}

30.  In regulation~1(3) (citation, commencement and~interpretation)—
\begin{enumerate}\item[]
($a$) in paragraph~($a$)  of the definition of “claimant”\footnote{Definition amended by S.I.~1999/1662 and~2002/3019.} for~“or~section~17(1) of the State Pension Credit Act” substitute “,~section~17(1) of the State Pension Credit Act or~section~24(1) of the Welfare Reform Act”;

($b$) after the definition of “clerk to the appeal tribunal” insert—
\begin{quotation}
““contributory employment and~support allowance” means a contributory allowance under Part~I of the Welfare Reform Act;”;
\end{quotation}

($c$) after the definition of “designated authority”\footnote{Definition substituted by S.I.~2002/1703.} insert—
\begin{quotation}
““the Employment and~Support Allowance Regulations” means the Employment and~Support Allowance Regulations 2008\footnote{S.I.~2008/794.};

“failure determination” means a determination by the Secretary of State under regulation~63(1) of the Employment and~Support Allowance Regulations that a claimant has failed to satisfy the requirement of regulation~47 or~54 of those Regulations (requirement to take part in a work-focused health related assessment or~a work-focused interview);”;
\end{quotation}

($d$) after the definition of “the Graduated Retirement Benefit Regulations”\footnote{Definition was inserted by S.I.~2005/2677.} insert—
\begin{quotation}\sloppy
““income-related employment and~support allowance” means an income-related allowance under Part~I of the Welfare Reform Act;”;
\end{quotation}

($e$) after the definition of “legally qualified panel member” insert—
\begin{quotation}
““limited capability for~work” has the same meaning as in section~1(4) of the Welfare Reform Act”; and
\end{quotation}

($f$) after the definition of “the Variations Regulations”\footnote{Definition inserted by S.I.~2000/3185.} insert—
\begin{quotation}
““the Welfare Reform Act” means the Welfare Reform Act 2007;”.
\end{quotation}
\end{enumerate}

\subsubsection[31. Amendment of regulation~3]{Amendment of regulation~3}

31.---(1)  Regulation~3 (revision of decisions) is amended as follows.

(2) In paragraph~(5)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($c$)\footnote{Sub-paragraph~($c$) was inserted by S.I.~1999/1623 and~amended by S.I.~2007/2470.}—
\begin{enumerate}\item[]
(i) after “incapacity determination” the first time it occurs insert “or~is an employment and~support allowance decision where there has been a limited capability for~work determination”; and

(ii) for~“or~the incapacity determination” substitute “,~the incapacity determination or~the limited capability for~work determination”; and
\end{enumerate}

($b$) in sub-paragraph~($d$)\footnote{Sub-paragraph~($d$) was inserted by S.I.~2007/2470.}—
\begin{enumerate}\item[]
(i) after “where the decision” insert “is an employment and~support allowance decision,”;

(ii) after “not in relation to the” insert “limited capability for~work determination,”; and

(iii) after “in or~necessary to” insert “the employment and~support allowance decision,”.
\end{enumerate}
\end{enumerate}

(3) In paragraph~(5ZB)\footnote{Paragraph~(5ZB) was inserted by S.I.~2007/2582.}—
\begin{enumerate}\item[]
($a$) after sub-paragraph~($f$)  omit “and”; and

($b$) after sub-paragraph~($g$)  add—
\begin{quotation}
“and

($h$) contributory employment and~support allowance.”
\end{quotation}
\end{enumerate}

(4) After paragraph~(5B)\footnote{Paragraph~(5B) was inserted by S.I.~2007/2470.} insert—
\begin{quotation}
“(5C) A decision of the Secretary of State under section~10 made in consequence of a failure determination may be revised at any time if it contained an error~to which the claimant did not materially contribute.

(5D) A decision by the Secretary of State under section~8 or~10 awarding employment and~support allowance may be revised at any time if—
\begin{enumerate}\item[]
($a$) it incorporates a determination that the condition in regulation~30 of the Employment and~Support Allowance Regulations is satisfied;

($b$) the condition referred to in sub-paragraph~($a$)  was not satisfied at the time when the claim was first determined; and

($c$) there is a period before the award which falls to be decided.”.
\end{enumerate}
\end{quotation}

(5) In paragraph~(7ZA)\footnote{Paragraph~(7ZA) was inserted by S.I.~2005/337.}—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($a$)  for~“or~state pension credit” substitute “,~state pension credit or~an income-related employment and~support allowance”;

($b$) in sub-paragraph~($b$)  after “Income Support Regulations” insert “or~regulation~71 of the Employment and~Support Allowance Regulations”;

($c$) in sub-paragraph~($c$)(i)  after “Income Support Regulations” insert “or~regulation~67 of the Employment and~Support Allowance Regulations”; and

($d$) in sub-paragraph~($d$)(ii)  after “Income Support Regulations” insert “,~paragraph~6(4)($a$)  of Schedule~4 to the Employment and~Support Allowance Regulations”.
\end{enumerate}

(6) In paragraph~(9)\footnote{Paragraph~(9) was substituted by S.I.~1999/2677 and~amended by S.I.~1999/2570, 2003/1050 and~2005/337.}—
\begin{enumerate}\item[]
($a$) after sub-paragraph~($a$)  omit “nor”; and

($b$) after sub-paragraph~($b$)  insert—
\begin{quotation}
“nor

($c$) a decision which relates to an employment and~support allowance where the claimant is terminally ill, within the meaning of regulation~2(1) of the Employment and~Support Allowance Regulations unless the claimant makes an application which contains an express statement that he is terminally ill and~where such an application is made, the decision may be revised.”.
\end{quotation}
\end{enumerate}

\subsubsection[32. Amendment of regulation~6]{Amendment of regulation~6}

32.---(1)  Regulation~6 (supersession of decisions) is amended as follows.

(2) In paragraph~(2)\footnote{Paragraph~(2) was amended by S.I.~1999/1623, 1999/2570 and~1999/2677, 2000/1596, 2001/1711 and~2000/1982, 2002/428, 2002/490, 2000/897 and~2002/3019, 2003/1050, 2003/1886 and~2003/2274, 2004/959, 2005/337 and~2005/2677.}—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($a$)(i)  after “Regulations” insert “or~regulation~146 of the Employment and~Support Allowance Regulations”;

($b$) in sub-paragraph~($i$)  for~“or~income support” substitute “,~income support or~an employment and~support allowance”; and

($c$) after sub-paragraph~($o$)  add—
\begin{quotation}
“($p$) is a decision awarding employment and~support allowance where there has been a failure determination;

($q$) is a decision made in consequence of a failure determination where the reduction ceases to have effect under of regulation~64 of the Employment and~Support Allowance Regulations;

($r$) is an employment and~support allowance decision where, since the decision was made, the Secretary of State has received medical evidence from a health care professional approved by the Secretary of State for~the purposes of regulation~23 or~38 of the Employment and~Support Allowance Regulations.”.
\end{quotation}
\end{enumerate}

(3) In paragraph~(6)($a$)\footnote{Paragraph~(6) was amended by S.I.~1999/2677 and~2005/337.} after “Income Support Regulations” insert “,~regulation~137 of the Employment and~Support Allowance Regulations”.

\subsubsection[33. Amendment of regulation~7]{Amendment of regulation~7}

33.---(1)  Regulation~7 (date from which a decision superseded under section~10 takes effect) is amended as follows.

(2) In paragraph~(1)($a$)\footnote{Paragraph~(1) was substituted by S.I.~1999/3178 and~sub-paragraph~($a$) was substituted by S.I.~2002/3019 and~amended by S.I.~2003/1050.}—
\begin{enumerate}\item[]
($a$) after “(2)($b$)” insert “or~($be$)”; and

($b$) for~“and~3B” substitute “,~3B and~3C”.
\end{enumerate}

(3) In paragraph~(2)\footnote{Paragraph~(2) was amended by S.I.~1999/3178, 2000/1596, 2002/3019, 2003/1050, 2005/337, 2006/832 and~2006/2377 and~2007/2470.}—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($b$)(i)  for~“or~state pension credit” substitute “,~state pension credit or~an employment and~support allowance”; and

($b$) after paragraph~($bc$)\footnote{Sub-paragraph~($bc$)  was inserted by S.I.~2006/2377. Sub-paragraph~($bd$)  was inserted by S.I.~2007/2470 and~omitted by S.I.~2008/1042.} insert—
\begin{quotation}
“($be$) in the case of a claimant who is in receipt of an employment and~support allowance and~the claimant makes an application which contains an express statement that he is terminally ill within the meaning of regulation~2(1) of the Employment and~Support Allowance Regulations, from the date the claimant became terminally ill;”.
\end{quotation}
\end{enumerate}

(4) For~paragraph~(3)\footnote{Paragraph~(3) was amended by S.I.~2002/3019.} substitute—
\begin{quotation}
“(3) For~the purposes of paragraphs~(2) and~(8) “benefit week” has the same meaning, as the case may be, as in—
\begin{enumerate}\item[]
($a$) regulation~2(1) of the Income Support Regulations;

($b$) regulation~1(3) of the Jobseeker’s Allowance Regulations;

($c$) regulation~1(2) of the State Pension Credit Regulations; or

($d$) regulation~2(1) of the Employment and~Support Allowance Regulations.”.
\end{enumerate}
\end{quotation}

(5) In paragraph~(7)($b$)\footnote{Paragraph~(7) was substituted by S.I.~2006/832.}—
\begin{enumerate}\item[]
($a$) in paragraph~(i)  after “(guarantee credit)” add “or~paragraph~6 of Schedule~4 to the Employment and~Support Allowance Regulations;”; and

($b$) in paragraph~(ii)($aa$)  after “Income Support Regulations” add “or~regulation~71 of the Employment and~Support Allowance Regulations”.
\end{enumerate}

(6) In paragraph~(13)($a$)\footnote{Paragraph~(3)($a$) was amended by S.I.~2002/3019.}—
\begin{enumerate}\item[]
($a$) in paragraph~(iii)  for~“and” substitute “or”; and

($b$) after paragraph~(iii)  insert—
\begin{quotation}
“(iv) paragraph~16 or~17 of Schedule~6 to the Employment and~Support Allowance Regulations; and”.
\end{quotation}
\end{enumerate}

(7) After paragraph~(17C)\footnote{Paragraph~(17C) was inserted by S.I.~2002/3197 and~substituted by S.I.~2004/647.} insert—
\begin{quotation}
“(17D) Except in a case where paragraph~(23) applies, where a claimant is in receipt of an employment and~support allowance and~his applicable amount includes an amount determined in accordance with Schedule~6 to the Employment and~Support Allowance Regulations (housing costs), and~there is a reduction in the amount of eligible capital owing in connection with a loan which qualifies under paragraph~16 or~17 of that Schedule, a decision made under section~10 shall take effect—
\begin{enumerate}\item[]
($a$) on the first anniversary of the date on which the claimant’s housing costs were first met under that Schedule; or

($b$) where the reduction in eligible capital occurred after the first anniversary of the date referred to in sub-paragraph~($a$), on the next anniversary of that date following the date of the reduction.
\end{enumerate}

(17E) Where a claimant is in receipt of an employment and~support allowance and~payments made to that claimant which fall within paragraph~31 or~32(1)($a$)  to ($c$)  of Schedule~8 to the Employment and~Support Allowance Regulations have been disregarded in relation to any decision under section~8 or~10 and~there is a change in the amount of interest payable—
\begin{enumerate}\item[]
($a$) on a loan qualifying under paragraph~16 or~17 of Schedule~6 to those Regulations to which those payments relate; or

($b$) on a loan not so qualifying which is secured on the dwelling occupied as the home to which those payments relate,
\end{enumerate}
a decision under section~10 which is made as a result of that change in the amount of interest payable shall take effect on whichever of the dates referred to in paragraph~(17F) is appropriate in the claimant’s case.

(17F) The date on which a decision under section~10 takes effect for~the purposes of paragraph~(17E) is—
\begin{enumerate}\item[]
($a$) the date on which the claimant’s housing costs are first met under paragraph~8(1)($a$), 9(1)($a$)  or~10(2)($a$)  of Schedule~6 to the Employment and~Support Allowance Regulations; or

($b$) where the change in the amount of interest payable occurred after the date referred to in sub-paragraph~($a$), on the date of the next alteration in the standard rate following the date of that change.
\end{enumerate}

(17G) In paragraph~(17F) “standard rate” has the same meaning as it has in paragraph~13(2) of Schedule~6 to the Employment and~Support Allowance Regulations.

(17H) Where the decision is superseded in accordance with regulation~6(2)($a$)(i)  and~the relevant circumstances are that the claimant has a non-dependant who has become entitled to main phase employment and~support allowance, the superseding decision shall take effect from the date the main phase employment and~support allowance is first paid to the non-dependant.”.
\end{quotation}

(8) In paragraph~(23)\footnote{Paragraph~(23) was substituted by S.I.~2002/3197 and~amended by S.I.~2004/647.}—
\begin{enumerate}\item[]
($a$) after “(17A)” insert “,~(17D)”;

($b$) after “a jobseeker’s allowance” the first time it occurs insert “,~an employment and~support allowance”; and

($c$) in sub-paragraph~($a$)  for~“or~jobseeker’s allowance” substitute “,~jobseeker’s allowance or~employment and~support allowance”.
\end{enumerate}

(9) After paragraph~(34)\footnote{Paragraph~(34) was inserted by S.I.~2005/337.} add—
\begin{quotation}
“(35) A decision made in accordance with regulation~6(2)($p$), where the failure determination was made before the 13th week of entitlement, shall take effect from the first day of the benefit week following that week.

(36) A decision made in accordance with regulation~6(2)($p$)  where paragraph~(35) does not apply shall take effect from the first day of the benefit week in which the failure determination was made.

(37) A decision made in accordance with regulation~6(2)($q$)  shall take effect from the first day of the benefit week in which the reduction mentioned in that sub-paragraph~ceased to have effect.

(38) A decision made in accordance with regulation~6(2)($r$)  that embodies a determination that the claimant has limited capability for~work which is the first such determination shall take effect from the beginning of the 14th week of entitlement.

(39) A decision made in accordance with regulation~6(2)($r$), following an application by the claimant, that embodies a determination that the claimant has limited capability for~work-related activity shall take effect from the date of the application.”.
\end{quotation}

\subsubsection[34. Amendment of regulation~7A]{Amendment of regulation~7A}

34.---(1)  Regulation~7A\footnote{Regulation~7A was inserted by S.I.~1999/1623 and~amended by 2000/1596.} (definitions etc.)\ is amended as follows.

(2) For~the heading substitute “Definitions for~the purposes of Chapters I and~II”.

(3) In paragraph~(1)—
\begin{enumerate}\item[]
($a$) after the definition of “disability determination” insert—
\begin{quotation}
““employment and~support allowance decision” means a decision to award a relevant benefit or~relevant credit embodied in or~necessary to which is a determination that a person has or~is to be treated as having limited capability for~work under Part~I of the Welfare Reform Act;”
\end{quotation}

($b$) after the definition of “incapacity determination” insert—
\begin{quotation}
““limited capability for~work determination” means a determination whether a person has limited capability for~work by applying the test of limited capability for~work or~whether a person is to be treated as having limited capability for~work in accordance with regulation~20 of the Employment and~Support Allowance Regulations;”; and
\end{quotation}

($c$) in the definition of “payee” after “incapacity benefit decision” insert “or~“employment and~support allowance decision””.
\end{enumerate}

\subsubsection[35. Amendment of regulation~7B]{Amendment of regulation~7B}

35.  In regulation~7B(23)\footnote{Regulation~7B was inserted by S.I.~2000/3185.} (date from which a decision superseded under section~17 of the Child Support Act takes effect) in the definition of “benefit week” after “Income Support Regulations” insert “,~in relation to employment and~support allowance has the same meaning as in regulation~2(1) of the Employment and~Support Allowance Regulations”.

\subsubsection[36. Amendment of regulation~10]{Amendment of regulation~10}

36.  For~regulation~10 (effect of a determination as to capacity for~work) substitute—
\begin{quotation}
\subsection*{“Effect of determination as to capacity or~capability for~work}

10.---(1)  This regulation~applies to a determination whether a person—
\begin{enumerate}\item[]
($a$) is capable or~incapable of work;

($b$) is to be treated as capable or~incapable of work;

($c$) has or~does not have limited capability for~work; or

($d$) is to be treated as having or~not having limited capability for~work.
\end{enumerate}

(2) A determination (including a determination made following a change of circumstances) as set out in paragraph~(1) which is embodied in or~necessary to a decision under Chapter II of Part~I of the Act or~on which such a decision is based shall be conclusive for~the purposes of any further decision.”.
\end{quotation}

\subsubsection[37. Amendment of regulation~11]{Amendment of regulation~11}

37.  In regulation~11 (Secretary of State to determine certain matters)—
\begin{enumerate}\item[]
($a$) after “Act” insert “or~Part~I of the Welfare Reform Act”; and

($b$) after sub-paragraph~($a$)  insert—
\begin{quotation}
“($aa$) whether a person is, or~is to be treated as, having or~not having limited capability for~work; or”.
\end{quotation}
\end{enumerate}

\subsubsection[38. Amendment of regulation~13]{Amendment of regulation~13}

38.  In regulation~13\footnote{Regulation~13 was amended by S.I.~2002/3019.} (income support and~social fund determinations on incomplete evidence)—
\begin{enumerate}\item[]
($a$) in paragraph~(1)($a$)—
\begin{enumerate}\item[]
(i) after paragraph~(i)  omit “or”; and

(ii) after paragraph~(ii)  for~“and” substitute—
\begin{quotation}\sloppy
“or

(iii) a claimant’s applicable amount under regulation~67(1)($c$)  or~68(1)($d$)  of the Employment and~Support Allowance Regulations; and” and
\end{quotation}
\end{enumerate}

($b$) in paragraph~(2)($a$)—
\begin{enumerate}\item[]
(i) in paragraph~(ii)  omit “or”;

(ii) after paragraph~(iii)  for~“and” substitute—
\begin{quotation}
“or

(iv) in relation to any claimant, the applicable amount includes the severe disability premium by virtue of regulation~67(1) or~68(1) of, and~paragraph~6 of Schedule~4 to, the Employment and~Support Allowance Regulations; and”.
\end{quotation}
\end{enumerate}
\end{enumerate}

\subsubsection[39. Amendment of regulation~14A]{Amendment of regulation~14A}

39.---(1)  Regulation~14A\footnote{Regulation~14A was inserted by S.I.~2002/1379.} (termination of award of income support or~jobseeker’s allowance) is amended as follows.

(2) In the heading for~“or~jobseeker’s allowance” substitute “,~jobseeker’s allowance or~employment and~support allowance”.

(3) In paragraph~(1)—
\begin{enumerate}\item[]
($a$) for~“or~a jobseeker’s allowance” substitute “,~a jobseeker’s allowance or~an employment and~support allowance”; and

($b$) after “partner for” insert “an employment and~support allowance,”.
\end{enumerate}

(4) After paragraph~(4) add—
\begin{quotation}
“(5) Where an award of an employment and~support allowance is made in accordance with the provisions of this regulation, paragraph~2 of Schedule~2 to the Welfare Reform Act (waiting days) shall not apply.”.
\end{quotation}

\subsubsection[40. Amendment of regulation~17]{Amendment of regulation~17}

40.  In regulation~17(2) (provision of information or~evidence) after sub-paragraph~($e$)  add—
\begin{quotation}
“($f$) a person whose entitlement to an employment and~support allowance is conditional on his having, or~being treated as having, limited capability for~work.”.
\end{quotation}

\subsubsection[41. Amendment of regulation~19]{Amendment of regulation~19}

41.  In regulation~19(1)\footnote{Regulation~19 was amended by S.I.~1999/2570 and~2007/1626.} (suspension and~termination for~failure to submit to medical examination)—
\begin{enumerate}\item[]
($a$) omit “applies”; and

($b$) after “capable of work)” insert “or~regulation~23 of the Employment and~Support Allowance Regulations (where a question arises whether a person has limited capability for~work) applies”.
\end{enumerate}

\subsubsection[42. Amendment of Schedule~2]{Amendment of Schedule~2}

42.  In paragraph~5 of Schedule~2 (decisions against which no appeal lies)—
\begin{enumerate}\item[]
($a$) after paragraph~($a$)  insert—
\begin{quotation}
“($aa$) regulation~4I (which partner should make a claim for~an employment and~support allowance);”;
\end{quotation}

($b$) in sub-paragraph~($h$)  after “benefit” add “or~employment and~support allowance”; and

($c$) after paragraph~($mm$)  insert—
\begin{quotation}
“($mn$) regulation~26C (manner and~time of payment of employment and~support allowance);”.
\end{quotation}
\end{enumerate}

\subsubsection[43. Schedule~3C]{Schedule~3C}

43.  After Schedule~3B\footnote{Schedule~3B was inserted by S.I.~2002/3019.} (date on which change of circumstances takes effect where claimant entitled to state pension credit) insert—
\begin{quotation}
\part*{\noindent ``Schedule~3C\\*Date from which change of circumstances takes effect where claimant entitled to employment and~support allowance}

1.  Subject to paragraphs~2 to 7, where the amount of an employment and~support allowance payable under an award is changed by a superseding decision made on the ground of a change of circumstances, that superseding decision shall take effect from the first day of the benefit week in which the relevant change of circumstances occurs or~is expected to occur.

\medskip

2.  In the cases set out in paragraph~3, the superseding decision shall take effect from the day on which the relevant change of circumstances occurs or~is expected to occur.

\medskip

3.  The cases referred to in paragraph~2 are where—
\begin{enumerate}\item[]
($a$) entitlement ends, or~is expected to end, for~a reason other than that the claimant no longer satisfies the provisions of paragraph~6(1)($a$)  of Schedule~1 to the Welfare Reform Act;

($b$) a child or~young person referred to in regulation~156(6)($d$)  or~($h$)  of the Employment and~Support Allowance Regulations (child in care of local authority or~detained in custody) lives, or~is expected to live, with the claimant for~part only of the benefit week;

($c$) a person referred to in paragraph~12 of Schedule~5 to the Employment and~Support Allowance Regulations—
\begin{enumerate}\item[]
(i) ceases, or~is expected to cease, to be a patient; or

(ii) a member of the person’s family ceases, or~is expected to cease, to be a patient,
\end{enumerate}
in either case for~a period of less than a week;

($d$) a person referred to in paragraph~3 of Schedule~5 to the Employment and~Support Allowance Regulations—
\begin{enumerate}\item[]
(i) ceases to be a prisoner; or

(ii) becomes a prisoner;
\end{enumerate}

($e$) during the currency of the claim a claimant makes a claim for~a relevant social security benefit—
\begin{enumerate}\item[]
(i) the result of which is that his benefit week changes; or\looseness=-1

(ii) in accordance with regulation~13 of the Claims and~Payments Regulations and~an award of that benefit on the relevant day for~the purposes of that regulation~means that his benefit week is expected to change.
\end{enumerate}
\end{enumerate}

\medskip

4.  A superseding decision made in consequence of a payment of income being treated as paid on a particular day under regulation~93 of the Employment and~Support Allowance Regulations (date on which income is treated as paid) shall take effect from the day on which that payment is treated as paid.

\medskip

5.  Where—
\begin{enumerate}\item[]
($a$) it is decided upon supersession on the ground of a relevant change of circumstances or~change specified in paragraphs~9 and~10 that the amount of an employment and~support allowance is, or~is to be, reduced; and

($b$) the Secretary of State certifies that it is impracticable for~a superseding decision to take effect from the day prescribed in paragraph~9 or~the preceding paragraphs~of this Schedule~(other than where paragraph~3($e$)  or~4 applies),
\end{enumerate}
that superseding decision shall take effect—
\begin{enumerate}\item[]
(i) where the relevant change has occurred, from the first day of the benefit week following that in which that superseding decision is made; or

(ii) where the relevant change is expected to occur, from the first day of the benefit week following that in which that change of circumstances is expected to occur.
\end{enumerate}

\medskip

6.  Where—
\begin{enumerate}\item[]
($a$) a superseding decision (“the former supersession”) was made on the ground of a relevant change of circumstances in the cases set out in paragraph~3($b$)  to ($e$); and

($b$) that superseding decision is itself superseded by a subsequent decision because the circumstances which gave rise to the former supersession cease to apply (“the second change”),
\end{enumerate}
that subsequent decision shall take effect from the date of the second change.

\medskip

7.  In the case of an employment and~support allowance decision where there has been a limited capability for~work determination, where—
\begin{enumerate}\item[]
($a$) the Secretary of State is satisfied that, in relation to a limited capability for~work determination, the claimant or~payee failed to notify an appropriate office of a change of circumstances which regulations under the Administration Act required him to notify; and

($b$) the claimant or~payee, as the case may be, could reasonably have been expected to know that the change of circumstances should have been notified,
\end{enumerate}
the superseding decision shall take effect—
\begin{enumerate}\item[]
(i) from the date on which the claimant or~payee, as the case may be, ought to have notified the change of circumstances; or\looseness=-1

\enlargethispage{-6\baselineskip}

(ii) if more than one change has taken place between the date from which the decision to be superseded took effect and~the date of the superseding decision, from the date on which the first change ought to have been notified.
\end{enumerate}

\section*{\itshape Changes other than changes of circumstances}

8.  Where—
\begin{enumerate}\item[]
($a$) the Secretary of State supersedes a decision made by an appeal tribunal or~a Commissioner on the grounds specified in regulation~6(2)($c$)(i)  (ignorance of, or~mistake as to, a material fact);\looseness=-1

($b$) the decision to be superseded was more advantageous to the claimant because of the ignorance or~mistake than it would otherwise have been; and

($c$) the material fact—
\begin{enumerate}\item[]
(i) does not relate to the limited capability for~work determination embodied in or~necessary to the decision; or\looseness=-1

(ii) relates to a limited capability for~work determination embodied in or~necessary to the decision and~the Secretary of State is satisfied that at the time the decision was made the claimant or~payee, as the case may be, knew or~could reasonably have been expected to know of it and~that it was relevant,
\end{enumerate}
\end{enumerate}
the superseding decision shall take effect from the first day of the benefit week in which the decision of the appeal tribunal or~the Commissioner took effect or~was to take effect.

\medskip

9.  Where an amount of an employment and~support allowance payable under an award is changed by a superseding decision specified in paragraph~10 the superseding decision shall take effect from the day specified in paragraph~1 for~a change of circumstances.

\medskip

10.  The following are superseding decisions for~the purposes of paragraph~9—
\begin{enumerate}\item[]
($a$) a decision which supersedes a decision specified in regulation~6(2)($b$)  and~($d$)  to ($ee$); and

\enlargethispage{-6\baselineskip}

\begin{sloppypar}
($b$) a superseding decision which would, but for~paragraph~9, take effect from a date specified in regulation~7(6), (7), (12), (13), (17D) to (17F), and~(33).”.
\end{sloppypar}
\end{enumerate}
\end{quotation}

\section[Part V --- Miscellaneous amendments]{Part V\\*Miscellaneous amendments}

\subsection[Chapter I --- Statutory payments]{Chapter I\\*Statutory payments}

\renewcommand\parthead{--- Part V Chapter I}

\subsubsection[44. Amendment of the Social Security Contributions and~Benefits Act 1992]{Amendment of the Social Security Contributions and~Benefits Act 1992}

44.  After paragraph~2($d$)\footnote{1992 c.~4. Paragraph~(2) was amended by Social Security (Incapacity for Work) Act 1994 (c.~18) and~the relevant amending Instruments are S.I.~2002/2034 and~2006/1031.} of Schedule~11 to the Social Security Contributions and~Benefits Act 1992 (circumstances in which periods of entitlement to statutory sick pay do not arise) insert—
\begin{quotation}
“($dd$) in the period of 85 days ending immediately before the relevant date the employee had at least one day on which he was entitled to an employment and~support allowance (or~would have been so entitled had he satisfied the requirements in section~1(2) of the Welfare Reform Act 2007.”.
\end{quotation}

\subsubsection[45. Amendment of the Statutory Sick Pay (General) Regulations 1982]{Amendment of the Statutory Sick Pay (General) Regulations 1982}

45.---(1)  In regulation~3 of the Statutory Sick Pay (General) Regulations 1982\footnote{S.I.~1982/894. Paragraph~(2B) was inserted by S.I.~2007/825.} (period of entitlement ending or~not arising) after paragraph~(2B) insert—
\begin{quotation}
“(2C) A period of entitlement in respect of an employee who was entitled to employment and~support allowance shall not arise in relation to any day within a period of limited capability for~work beginning with the first day on which paragraph~2($dd$)  of Schedule~11 to the Contributions and~Benefits Act ceases to have effect where the employee in question is a person to whom regulation~148 of the Employment and~Support Allowance Regulations 2008 (work and~training beneficiaries) applies.”.
\end{quotation}

\subsubsection[46. Amendment of the Statutory Maternity Pay (General) Regulations 1986]{Amendment of the Statutory Maternity Pay (General) Regulations 1986}

46.  In regulation~25A(1) of the Statutory Maternity Pay (General) Regulations 1986\footnote{S.I.~1986/1960. Regulation~25A was inserted by S.I.~1990/622 and~amended by S.I.~1995/829 and~2002/2690.} (provision of information relating to claims for~certain other benefits) for~“or~incapacity benefit”, substitute “,~incapacity benefit or~an employment and~support allowance”.

\subsection[Chapter II --- National insurance]{Chapter II\\*National insurance}

\renewcommand\parthead{--- Part V Chapter II}

\subsubsection[47. Amendment of the Social Security Contributions and~Benefits Act 1992]{Amendment of the Social Security Contributions and~Benefits Act 1992}

47.---(1)  Section 44A\footnote{Section 44A was inserted by section 30(3) of the Child Support, Pensions and~Social Security Act 2000 (c.~19).} of the Social Security Contributions and~Benefits Act 1992 (deemed earnings factors) is amended as follows.

(2) In subsection~(2)($d$)—
\begin{enumerate}\item[]
($a$) after “incapacity benefit” insert “or~qualifying employment and~support allowance”; and

($b$) in sub-paragraph~(i)  after “Schedule~3” add “or, as the case may be, paragraph~1 of Schedule~1 to the Welfare Reform Act”.
\end{enumerate}

(3) After subsection~(6) add—
\begin{quotation}
“(7) In subsection~(2)($d$)  “qualifying employment and~support allowance” means contributory employment and~support allowance where—
\begin{enumerate}\item[]
($a$) that allowance was payable for~a continuous period of 52 weeks;

($b$) that allowance included the support component under section~2(2) of the Welfare Reform Act; or

($c$) in the case of—
\begin{enumerate}\item[]
(i) a man born between 6th April 1944 and~5th April 1947; or

(ii) a woman born between 6th April 1949 and~5th April 1951,
\end{enumerate}
that allowance was payable for~a continuous period of 13 weeks immediately following a period throughout which statutory sick pay was payable.”.
\end{enumerate}
\end{quotation}

\subsubsection[48. Amendment of the Social Security (Credits) Regulations 1975]{Amendment of the Social Security (Credits) Regulations 1975}

48.---(1)  The Social Security (Credits) Regulations 1975\footnote{S.I.~1975/556.} are amended as follows.

(2) In regulation~2(1) (interpretation)—
\begin{enumerate}\item[]
($a$) in the definition of “benefit”\footnote{Definition inserted by S.I.~1996/2367 and~amended by S.I.~2000/1483.} after “income-based jobseeker’s allowance” insert “and~includes a contributory employment and~support allowance but not an income-related employment and~support allowance”;

($b$) after the definition of “contribution-based jobseeker’s allowance”\footnote{Definition inserted by S.I.~1996/2367.} insert—
\begin{quotation}
““contributory employment and~support allowance” means a contributory allowance under Part~I of the Welfare Reform Act (employment and~support allowance);”;
\end{quotation}

($c$) after the definition of “income-based jobseeker’s allowance” insert—
\begin{quotation}\sloppy
““income-related employment and~support allowance” means an income-related allowance under Part~I of the Welfare Reform Act (employment and~support allowance);”;
\end{quotation}

($d$) in the definition of “reckonable year”\footnote{Definition was substituted by S.I.~1996/2367 and~amended by S.I.~2007/1749.}—
\begin{enumerate}\item[]
(i) after sub-paragraph~($a$)  omit “or”; and

(ii) after sub-paragraph~($b$)  add—
\begin{quotation}
“or

($c$) in relation to a contributory employment and~support allowance, the condition specified in paragraph~2(1) of Schedule~1 to the Welfare Reform Act (conditions relating to national insurance).”;
\end{quotation}
\end{enumerate}

($e$) in the definition of “relevant benefit year”\footnote{Definition was substituted by S.I.~1996/2367.}—
\begin{enumerate}\item[]
(i) after sub-paragraph~($a$)  omit “and”; and

(ii) after sub-paragraph~($b$)  add—
\begin{quotation}
“and

($c$) in relation to a contributory employment and~support allowance, in paragraph~3(1)($f$)  of Schedule~1 to the Welfare Reform Act (conditions relating to national insurance);”; and
\end{quotation}
\end{enumerate}

($f$) after the definition of “relevant past year”\footnote{Definition was amended by S.I.~1988/1545.} insert—
\begin{quotation}
““the Welfare Reform Act” means the Welfare Reform Act 2007;”.
\end{quotation}
\end{enumerate}

(3) In regulation~3(1)\footnote{Paragraph~(1) was substituted by S.I.~1996/2367 and~amended by S.I.~2000/1483.} (general provisions relating to the crediting of contributions and~earnings)—
\begin{enumerate}\item[]
($a$) after sub-paragraph~($a$)  omit “or”; and

($b$) after sub-paragraph~($b$)  add—
\begin{quotation}
“or

($c$) in relation to a contributory employment and~support allowance, the condition specified in paragraph~2(1) of Schedule~1 to the Welfare Reform Act,”.
\end{quotation}
\end{enumerate}

(4) In regulation~8(1)\footnote{Paragraph~(1) was substituted by S.I.~1989/1627 and~amended by S.I.~1991/387, 1995/829 and~1996/2367.} (credits on termination of full-time education, training or~apprenticeship) for~“or~short-term incapacity benefit” substitute “,~short-term incapacity benefit or~a contributory employment and~support allowance”.

(5) In regulation~8A(2)($c$)\footnote{Regulation~8A was inserted by S.I.~1996/2367 and~paragraph (2) was amended by S.I.~2002/490.} (credits for~unemployment) after “incapable of work” insert “or~had limited capability for~work”.

(6) In regulation~8B\footnote{Regulation~8B was inserted by S.I.~1996/2367 and~amended by S.I.~2003/521, 2007/1749.} (credits for~incapacity for~work)—
\begin{enumerate}\item[]
($a$) in the heading, after “incapacity for~work” insert “or~limited capability for~work”; and

($b$) in paragraph~(2) after sub-paragraph~($a$)  omit “or” and~substitute—
\begin{quotation}
“($aa$) a week in which, in relation to the person concerned, each of the days—
\begin{enumerate}\item[]
(i) was a day of limited capability for~work for~the purposes of Part~I of the Welfare Reform Act (limited capability for~work) or~would have been such a day had that person been entitled to an employment and~support allowance by virtue of section~1 of the Welfare Reform Act; or

(ii) would have been such a day had the person concerned claimed an employment and~support allowance or~maternity allowance within the prescribed time; or”.
\end{enumerate}
\end{quotation}
\end{enumerate}

(7) In regulation~8C(1)\footnote{Regulation~8C was inserted by S.I.~2000/1483.} (credits on termination of bereavement benefits)—
\begin{enumerate}\item[]
($a$) after sub-paragraph~($a$)  omit “or”; and

($b$) after sub-paragraph~($b$)  add—

%($c$) after sub-paragraph~($b$)  add—
\begin{quotation}
“or

($c$) paragraph~2(1) of Schedule~1 to the Welfare Reform Act in relation to a contributory employment and~support allowance.”.
\end{quotation}
\end{enumerate}

\subsubsection[49. Amendment of the Social Security (Crediting and~Treatment of Contributions, and~National Insurance Numbers) Regulations 2001]{Amendment of the Social Security (Crediting and~Treatment of Contributions, and~National Insurance Numbers) Regulations 2001}

49.---(1)  The Social Security (Crediting and~Treatment of Contributions, and~National Insurance Numbers) Regulations 2001\footnote{S.I.~2001/769.} are amended as follows.

(2) In regulation~1(2) (citation, commencement and~interpretation)—
\begin{enumerate}\item[]
($a$) in the definition of “contributory benefit” after “income-based jobseeker’s allowance” insert “and~includes a contributory employment and~support allowance but not an income-related employment and~support allowance”;

($b$) after the definition of “contributory benefit” insert—
\begin{quotation}
““contributory employment and~support allowance” means a contributory allowance under Part~I of the Welfare Reform Act (employment and~support allowance);”;
\end{quotation}

($c$) after the definition of “earnings factor” insert—
\begin{quotation}\sloppy
““income-related employment and~support allowance” means an income-related allowance under Part~I of the Welfare Reform Act (employment and~support allowance);”;
\end{quotation}

($d$) in the definition of “relevant benefit year” after sub-paragraph~($b$)  add—
\begin{quotation}
“($c$) paragraph~3(1)($f$)  of Schedule~1 to the Welfare Reform Act (conditions relating to national insurance), in relation to a contributory employment and~support allowance.”; and
\end{quotation}

($e$) after the definition of “relevant time” insert—
\begin{quotation}
““the Welfare Reform Act” means the Welfare Reform Act 2007;”.
\end{quotation}
\end{enumerate}

(3) In regulation~4 (treatment for~the purpose of any contributory benefit of late paid contributions)—
\begin{enumerate}\item[]
($a$) in paragraph~(8) for~“or~short-term incapacity benefit” substitute “,~short-term incapacity benefit or~a contributory employment and~support allowance”; and

($b$) after paragraph~(9)($b$)  insert—
\begin{quotation}
“($c$) a contributory employment and~support allowance is a reference to the condition specified in paragraph~2(1) of Schedule~1 to the Welfare Reform Act”.
\end{quotation}
\end{enumerate}

(4) In regulation~5\footnote{Regulation~5 was amended by S.I.~2002/2366.} (treatment~\dots\ of late paid primary Class 1 contributions etc.)—
\begin{enumerate}\item[]
($a$) in paragraph~(1)($b$)—
\begin{enumerate}\item[]
(i) after paragraph~(i)  omit “or”; and

(ii) after paragraph~(ii)  add—
\begin{quotation}
“or

(iii) a contributory employment and~support allowance, is not paid before the beginning of the relevant benefit year,”;
\end{quotation}
\end{enumerate}

($b$) in paragraph~(2)($a$)  for~“or~short-term incapacity benefit” substitute “,~short-term incapacity benefit or~a contributory employment and~support allowance”; and

($c$) in paragraph~(3)($a$)\footnote{Paragraph~(3)($a$) was modified by S.I.~1996/207 and~paragraph 2(2) of Schedule~3 to the Act was amended by the Welfare Reform and~Pensions Act 1999 (c.~30).} after (ii)  add—
\begin{quotation}
“(iii) a contributory employment and~support allowance is a reference to the condition specified in paragraph~1(1) of Schedule~1 to the Welfare Reform Act;”.
\end{quotation}
\end{enumerate}

(5) In regulation~5A($a$)\footnote{Regulation~5A was inserted by S.I.~2007/1154.} (treatment for~the purpose of any contributory benefit of duly paid primary Class 1 contributions in respect of retrospective earnings) for~“or~short-term incapacity benefit” substitute “,~short-term incapacity benefit or~a contributory employment and~support allowance”.

\subsection[Chapter III --- Adjustments and~deductions]{Chapter III\\*Adjustments and~deductions}

\renewcommand\parthead{--- Part V Chapter III}

\subsubsection[50. Amendment of the Social Security (Recovery of Benefits) Act 1997]{Amendment of the Social Security (Recovery of Benefits) Act 1997}

50.---(1)  The Social Security (Recovery of Benefits) Act 1997\footnote{1997 c.~27.} is amended as follows.

(2) In section~29\footnote{Section 29 was amended by the Social Security Act 1998 (c.~14).} (general interpretation) in the definition of “benefit” after “a jobseeker’s allowance” insert “,~an employment and~support allowance”.\looseness=-1

(3) In Schedule~2\footnote{Schedule~2 was amended by the Tax Credits Act 1999 (c.~10).} (calculation of compensation payment) in column (2) (benefit) after the entry “Disablement pension payable under section~103 of the 1992 Act” insert the entry “Employment and~support allowance”.

\subsubsection[51. Amendment of the Social Security (Overlapping Benefits) Regulations 1979]{Amendment of the Social Security (Overlapping Benefits) Regulations 1979}

51.---(1)  The Social Security (Overlapping Benefits) Regulations 1979\footnote{S.I.~1979/597.} are amended as follows.

(2) In regulation~2(1) (interpretation)—
\begin{enumerate}\item[]
($a$) in the definition of “contributory benefit”\footnote{Definition was inserted by S.I.~1996/1345.} for~“and~a contribution-based jobseeker’s allowance” substitute “a contribution-based jobseeker’s allowance and~a contributory employment and~support allowance”;

($b$) in the definition of “personal benefit”\footnote{Definition was amended by S.I.~2005/1551.} after “includes” insert “a contributory employment and~support allowance but not an income-related employment and~support allowance and~includes”; and

($c$) after the definition of “1914--1918 War Injuries Scheme” insert—
\begin{quotation}
““the Welfare Reform Act” means the Welfare Reform Act 2007.”.
\end{quotation}
\end{enumerate}

(3) In regulation~4(1)($a$)\footnote{Paragraph~(1) was substituted by S.I.~1992/3194 and~amended by S.I.~1996/1345} (adjustment of personal benefit etc.)\ after “industrial injuries benefits)” insert “,~Part~I of the Welfare Reform Act”.

(4) In regulation~10(1)\footnote{Paragraph~(1) was amended by S.I.~1980/1927, 1982/1173, 1983/186, 1991/387, 1992/3194, 1996/1345 and~by virtue of the Employment Act 1998 (c.~38).} (adjustment of dependency benefit where certain personal benefit is payable) after sub-paragraph~($j$)  add—
\begin{quotation}
“($k$) a contributory employment and~support allowance,”.
\end{quotation}

(5) In regulation~16\footnote{Regulation~16 was amended by S.I.~1996/1345.} (persons to be treated as entitled to benefit for~certain purposes)—
\begin{enumerate}\item[]
($a$) after “the Act” the first time it occurs insert “,~Part~I of the Welfare Reform Act”; and

($b$) after “under it,” the first time it occurs insert “Part~I of the Welfare Reform Act and~regulations made under it”.
\end{enumerate}

(6) In regulation~17\footnote{Regulation~17 was amended by S.I.~1996/1345} (prevention of double adjustments) for~“or~under the Jobseekers Act” each time it occurs substitute “,~the Jobseekers Act or~Part~I of the Welfare Reform Act”.

(7) In Schedule~1\footnote{Schedule~1 was amended by S.I.~1983/186, 1984/1303, 1995/829, 1996/1345, 2000/1483 and~2005/2877.} (personal benefits which are required to be adjusted etc.)\ in column (1) (personal benefit under the Act) in paragraph~4, after “severe disablement allowance” insert “,~contributory employment and~support allowance”.

\subsubsection[52. Amendment of the Social Security (Payments on Account, Overpayments and~Recovery) Regulations 1988]{Amendment of the Social Security (Payments on Account, Overpayments and~Recovery) Regulations 1988}

52.---(1)  The Social Security (Payments on Account, Overpayments and~Recovery) Regulations 1988\footnote{S.I.~1988/664.} are amended as follows.

(2) In regulation~1(2) (citation, commencement and~interpretation)—
\begin{enumerate}\item[]
($a$) in the definition of “benefit”\footnote{Definition was amended by S.I.~1988/1725, 1989/136, 1995/829, 1996/1345 and~2002/3019.} after “state pension credit” insert “,~an employment and~support allowance”;

($b$) after the definition of “disabled person’s tax credit”\footnote{Definition was substituted by S.I.~1999/2571.} insert—
\begin{quotation}
““the Employment and~Support Allowance Regulations” means the Employment and~Support Allowance Regulations 2008;”; and
\end{quotation}

($c$) after the definition of “tax credit” insert—
\begin{quotation}
““the Welfare Reform Act” means the Welfare Reform Act 2007;”.
\end{quotation}
\end{enumerate}

(3) In regulation~2(4)\footnote{Regulation~2 was amended by S.I.~1991/2742, 1993/650, 1996/30, 1999/3178 and~2005/337.} (making of interim payments) after “income support” insert “or~income-related employment and~support allowance”.

(4) In regulation~4(3)($c$)\footnote{Paragraph~(3) was amended by S.I.~1996/650.} (recovery of overpaid interim payments) after “income support” insert “or~income-related employment and~support allowance”.

(5) In regulation~5(3)\footnote{Regulation~5 was amended by S.I.~1996/1345, 1999/2571 and~1999/3178, 2000/3120, 2002/3019, 2005/1551 and~2006/516.} (offsetting prior~payment against subsequent award) after “income-based jobseeker’s allowance” insert “or~an income-related employment and~support allowance”.

(6) In regulation~7 (duplication and~prescribed income)—
\begin{enumerate}\item[]
($a$) in paragraph~(1)($a$)\footnote{Paragraph~(1) was amended by S.I.~1993/650, 1996/1345 and~2002/3019.} after “Part~III of the State Pension Credit Regulations” insert “or~Part~X of the Employment and~Support Allowance Regulations”; and

($b$) in paragraph~(1)($b$)  after “(child support maintenance)” insert “or~Chapter IX of Part~X to the Employment and~Support Allowance Regulations (child support)”.
\end{enumerate}

(7) In regulation~8 (duplication and~prescribed payments)—
\begin{enumerate}\item[]
($a$) in paragraph~(1)\footnote{Paragraph~(1) was amended by S.I.~1991/387 and~1999/2571, 2742 and~3178, 2000/1483, 2005/337 and~3476 and~by virtue of the Employment Act 1988.}, after sub-paragraph~($k$)  add—
\begin{quotation}
“($l$) a contributory employment and~support allowance.”; and
\end{quotation}

($b$) in paragraph~(2)\footnote{Paragraph~(2) was amended by S.I.~1996/1345, 1999/3178 and~2002/3019.} after “income-based jobseekers allowance” add “or~income-related employment and~support allowance”.
\end{enumerate}

(8) In regulation~13(1)($b$)\footnote{Paragraph~(1) was amended by S.I.~1996/1345, 1999/2571 and~2002/3019.} (sums to be deducted in calculating recoverable amounts) after “income-based jobseeker’s allowance” insert “or~income-related employment and~support allowance”.

(9) In regulation~14\footnote{Regulation 14 was amended by S.I.~1996/1345 and~1996/2519, 1999/2571 and~2002/3019.} (quarterly diminution of capital) after “or~an income-based jobseeker’s allowance” each time it occurs insert “,~or~income-related employment and~support allowance”.

(10) In regulation~15(2)($d$)\footnote{Sub-paragraph (2)($d$) was amended by S.I.~1996/2519 and~2002/3019.} (recovery by deduction from prescribed benefits) after “income support,” insert “an employment and~support allowance,”.

(11) In regulation~16 (limitations on deductions from prescribed benefits)—
\begin{enumerate}\item[]
($a$) in paragraph~(4A)\footnote{Paragraph~(4A) was inserted by S.I.~1996/2519 and~amended by S.I.~2002/3019.} after sub-paragraph~($d$)  add—
\begin{quotation}
“($e$) an income-related employment and~support allowance;

($f$) where, if there was no entitlement to a contributory employment and~support allowance, there would be entitlement to an income-related employment and~support allowance at the same rate, a contributory employment and~support allowance.”;
\end{quotation}

($b$) in paragraph~(6)\footnote{Paragraph~(6) was amended by S.I.~1996/1345 and~2002/3019.} after sub-paragraph~($c$)  add—
\begin{quotation}
“or

($d$) in the calculation of the income of a person to whom income-related employment and~support allowance is payable, the amount of earnings or~other income falling to be taken into account is reduced by paragraph~7 of Schedule~7 to the Employment and~Support Allowance Regulations (sums to be disregarded in the calculation of earnings) or~paragraphs~16 and~17 of Schedule~8 to those Regulations (sums to be disregarded in the calculation of income other than earnings),”; and
\end{quotation}

($c$) in paragraph~(8)\footnote{Paragraph~(8) was amended by S.I.~2000/2336 and~2002/3019.}—
\begin{enumerate}\item[]
(i) in the definition of “personal allowance for~a single claimant aged not less than 25” for~“either” substitute “an employment and~support allowance,”; and

(ii) in the definition of “specified benefit”—
\begin{enumerate}\item[]
($aa$) after paragraph~($d$)  omit “and”; and

($bb$) after paragraph~($e$)  add—
\begin{quotation}
“and

($f$) an employment and~support allowance,”.
\end{quotation}
\end{enumerate}
\end{enumerate}
\end{enumerate}

(12) In regulation~17\footnote{Regulation~17 was amended by S.I.~1996/1345, 1999/2571, 2002/3019, 2003/492 and~2005/2877.} (recovery from couples) after “income-based jobseeker’s allowance” each time it occurs insert “or~income-related employment and~support allowance”.

\subsubsection[53. Amendment of the Community Charges (Deductions from Income Support) (No.~2) Regulations 1990]{Amendment of the Community Charges (Deductions from Income Support) (No.~2) Regulations 1990}

53.---(1)  The Community Charges (Deductions from Income Support) (No.~2) Regulations 1990\footnote{S.I.~1990/545.} are amended as follows.

(2) In regulation~2 (applications for~deductions etc.)—
\begin{enumerate}\item[]
($a$) in the heading for~“or~jobseeker’s allowance” substitute “,~jobseeker’s allowance or~employment and~support allowance”;

($b$) in paragraph~(1) for~“or~jobseeker’s allowance” substitute “,~jobseeker’s allowance or~employment and~support allowance”; and

($c$) in paragraph~(2)($e$)  for~“or~jobseeker’s allowance” substitute “,~jobseeker’s allowance or~employment and~support allowance”.
\end{enumerate}

(3) In regulation~3—
\begin{enumerate}\item[]
($a$) in the heading for~“or~jobseeker’s allowance” substitute “,~jobseeker’s allowance or~employment and~support allowance”; and

($b$) in paragraph~(1) for~“or~income-based jobseeker’s allowance” substitute “,~income-based jobseeker’s allowance or~income-related employment and~support allowance”.
\end{enumerate}

(4) In regulation~4 (circumstances, time of making and~termination of deductions) for~“or~jobseeker’s allowance” substitute “,~jobseeker’s allowance or~employment and~support allowance”.

\subsubsection[54. Amendment of the Fines (Deductions from Income Support) Regulations 1992]{Amendment of the Fines (Deductions from Income Support) Regulations 1992}

54.---(1)  The Fines (Deductions from Income Support) Regulations 1992\footnote{S.I.~1992/2182.} are amended as follows.

(2) In regulation~1(2) (citation, commencement and~interpretation)—
\begin{enumerate}\item[]
($a$) in the definition of “benefit week”\footnote{Definition was amended by S.I.~1996/2344 and~2002/3019.} after “1996” add “or~regulation~2(1) of the Employment and~Support Allowance Regulations”;

($b$) after the definition of “contribution-based jobseeker’s allowance”\footnote{Definition inserted by S.I.~1996/563.} insert—
\begin{quotation}
““contributory employment and~support allowance” means a contributory allowance under Part~I of the Welfare Reform Act;”;
\end{quotation}

($c$) after the definition of “court” insert—
\begin{quotation}
““the Employment and~Support Allowance Regulations” means the Employment and~Support Allowance Regulations 2008;”;
\end{quotation}

($d$) after the definition of “income-based jobseeker’s allowance”\footnote{Definition inserted by S.I.~1996/563.} insert—
\begin{quotation}
\begin{sloppypar}
““income-related employment and~support allowance” means—
\end{sloppypar}
\begin{enumerate}\item[]
($a$) 
an income-related allowance under Part~I of the Welfare Reform Act; and

($b$) 
in a case where, if there was no entitlement to contributory employment and~support allowance, there would be entitlement to income-related employment and~support allowance at the same rate, contributory employment and~support allowance;”;
\end{enumerate}
\end{quotation}

($e$) in the definition of “personal allowance for~a single claimant aged not less than 25”, after sub-paragraph~($b$), insert—
\begin{quotation}
“($c$) in the case of a person who is entitled to an income-related employment and~support allowance, the amount specified for~the time being in paragraph~1(1)($b$)  of column 2 of Schedule~4 to the Employment and~Support Allowance Regulations;”;
\end{quotation}

($f$) in the definition of “social security office”\footnote{Definition was amended by S.I.~2002/1397.} for~“or~a jobseeker’s allowance” substitute “,~a jobseekers allowance or~an employment and~support allowance”; and

($g$) after the definition of “tribunal”\footnote{Definition substituted by S.I.~1999/3178.} insert—
\begin{quotation}
““the Welfare Reform Act” means the Welfare Reform Act 2007;”.
\end{quotation}
\end{enumerate}

(3) In regulation~2\footnote{Regulation was amended by S.I.~1996/2344, 2002/3019.} (application for~deductions) for~“jobseeker’s allowance” each time it occurs substitute “,~jobseeker’s allowance or~employment and~support allowance”.

(4) In regulation~2A(2)\footnote{Regulation was inserted in relation to England and Wales by S.I.~2004/2889.} (information that the court or~fines officer may require) for~“or~a jobseeker’s allowance” substitute “,~a jobseeker’s allowance or~an employment and~support allowance”.

(5) In regulation~4\footnote{Regulation was substituted by S.I.~1999/3178 and amended by S.I.~2002/3019 and 2004/2889.} (deductions from offender’s income support etc.)—
\begin{enumerate}\item[]
($a$) in paragraph~(1)($a$)  for~“or~income-based jobseeker’s allowance” substitute “,~income-based jobseeker’s allowance or~income-related employment and~support allowance”;

($b$) in paragraph~(2)—
\begin{enumerate}\item[]
(i) in sub-paragraph~($a$)  after “jobseeker’s allowance” insert “or~contributory employment and~support allowance”; and

(ii) for~sub paragraph~($b$)  substitute—
\begin{quotation}
“($b$) the amount payable, before any deductions under this paragraph, of—
\begin{enumerate}\item[]
(i) contribution-based jobseeker’s allowance is equal to or~more than one-third of the age related amount applicable to the offender under section~4(1)($a$)  of the Jobseekers Act; or

(ii) contributory employment and~support allowance is equal to or~more than one third of the amount applicable to the offender under section~2(1)($a$)  of the Welfare Reform Act,
\end{enumerate}
as the case may be,”, and
\end{quotation}

(iii) after “Jobseekers Act” the second time it occurs insert “or~under section~2(1)($a$)  of the Welfare Reform Act”.
\end{enumerate}
\end{enumerate}

(6) In regulation~7\footnote{Regulation was amended by S.I.~1996/2344, 1999/3178 and 2002/3019.} (circumstances, time of making and~making of deductions) for~“or~jobseeker’s allowance” each time it occurs substitute “,~jobseeker’s allowance or~employment and~support allowance”.

\subsubsection[55. Amendment of the Council Tax (Deductions from Income Support) Regulations 1993]{Amendment of the Council Tax (Deductions from Income Support) Regulations 1993}

55.---(1)  The Council Tax (Deductions from Income Support) Regulations 1993\footnote{S.I.~1993/494.} are amended as follows.

(2) In regulation~1(2) (citation, commencement and~interpretation)—
\begin{enumerate}\item[]
($a$) in the definition of “benefit week” after “State Pension Credit Regulations 2002” insert “,~regulation~2(1) of the Employment and~Support Allowance Regulations 2008”;

($b$) after the definition of “contribution-based jobseeker’s allowance” insert—
\begin{quotation}
““contributory employment and~support allowance” means a contributory allowance under Part~I of the Welfare Reform Act (employment and~support allowance);”;
\end{quotation}

($c$) after the definition of “income-based jobseeker’s allowance” insert—
\begin{quotation}
\begin{sloppypar}
““income-related employment and~support allowance” means—
\end{sloppypar}
\begin{enumerate}\item[]
($a$) 
an income-related allowance under Part~I of the Welfare Reform Act; and

($b$) 
in a case where, if there was no entitlement to contributory employment and~support allowance, there would be entitlement to income-related employment and~support allowance at the same rate, contributory employment and~support allowance;”;
\end{enumerate}
\end{quotation}

($d$) in the definition of “personal allowance for~a single claimant aged not less than 25”—
\begin{enumerate}\item[]
(i) after sub-paragraph~($a$)  omit “or”;

(ii) after sub-paragraph~($b$)  add—
\begin{quotation}
“or

($c$) in the case of a person who is entitled to income-related employment and~support allowance, the amount specified for~the time being in paragraph~1 of column 2 of Schedule~4 to the Employment and~Support Allowance Regulations 2008;”;
\end{quotation}
\end{enumerate}

($e$) in the definition of “social security office” for~“or~a jobseeker’s allowance” substitute “,~a jobseeker’s allowance or~an employment and~support allowance”;

($f$) after the definition of “tribunal” insert—
\begin{quotation}
““the Welfare Reform Act” means the Welfare Reform Act 2007.”.
\end{quotation}
\end{enumerate}

(3) In regulation~2 (application for~deductions~\dots\ England~and~Wales)—
\begin{enumerate}\item[]
($a$) in the heading for~“or~jobseeker’s allowance” substitute “,~jobseeker’s allowance or~employment and~support allowance”; and

($b$) for~“or~jobseeker’s allowance” each time it occurs substitute “,~a jobseeker’s allowance or~an employment and~support allowance”;
\end{enumerate}

(4) In regulation~3 (application for~deductions~\dots\ Scotland)—
\begin{enumerate}\item[]
($a$) in the heading for~“or~jobseeker’s allowance” substitute “,~jobseeker’s allowance or~employment and~support allowance”;

($b$) for~“or~jobseeker’s allowance” each time it occurs substitute “,~a jobseeker’s allowance or~an employment and~support allowance”.
\end{enumerate}

(5) In regulation~4(1)($f$)  (contents of application) for~“or~jobseeker’s allowance” substitute “,~a jobseeker’s allowance or~an employment and~support allowance”.

(6) In regulation~5 (deductions from debtor’s income support etc.)—
\begin{enumerate}\item[]
($a$) in the heading for~“or~jobseeker’s allowance” substitute “,~jobseeker’s allowance or~employment and~support allowance”;

($b$) in paragraph~(1)($a$)  for~“or~income-based jobseeker’s allowance” substitute “,~an income-based jobseeker’s allowance or~an income-related employment and~support allowance”; and

($c$) in paragraph~(2)—
\begin{enumerate}\item[]
(i) in sub-paragraph~($a$)  after “allowance” insert “or~contributory employment and~support allowance”; and

(ii) for~sub-paragraph~($b$)  substitute—
\begin{quotation}
“($b$) the amount payable, before any deductions under this paragraph, of—
\begin{enumerate}\item[]
(i) contribution-based jobseeker’s allowance is equal to or~more than one-third of the age-related amount applicable to the debtor~under section~4(1)($a$)  of the Jobseekers Act; or

(ii) contributory employment and~support allowance is equal to or~more than one-third of the amount applicable to the debtor~under section~2(1)($a$)  of the Welfare Reform Act,
\end{enumerate}
as the case may be,”; and
\end{quotation}

(iii) after “Jobseekers Act” the second time it occurs insert “or~under section~2(1)($a$)  of the Welfare Reform Act”.
\end{enumerate}
\end{enumerate}

(7) In regulation~8 (circumstances, time of making and~termination of deductions)—
\begin{enumerate}\item[]
($a$) in paragraph~(1)—
\begin{enumerate}\item[]
(i) for~“or~jobseeker’s allowance” substitute “,~jobseeker’s allowance or~employment and~support allowance”;

(ii) for~“regulation~7 or~7A” substitute “regulation~5”; and

(iii) in sub-paragraph~($a$)  for~“or~jobseeker’s allowance” substitute “,~jobseeker’s allowance or~employment and~support allowance”;
\end{enumerate}

($b$) in paragraph~(2) for~“or~jobseeker’s allowance” each time it occurs substitute “,~jobseeker’s allowance or~employment and~support allowance”;

($c$) in paragraph~(3) for~“or~jobseeker’s allowance” each time it occurs substitute “,~jobseeker’s allowance or~employment and~support allowance”; and

($d$) in paragraph~(5) for~“or~jobseeker’s allowance” substitute “,~jobseeker’s allowance or~employment and~support allowance”.
\end{enumerate}

\subsubsection[56. Amendment of the Social Security (Loss of Benefit) Regulations 2001]{Amendment of the Social Security (Loss of Benefit) Regulations 2001}

56.---(1)  The Social Security (Loss of Benefit) Regulations 2001\footnote{S.I.~2001/4022.} are amended as follows.

(2) In regulation~2 (disqualification period)—
\begin{enumerate}\item[]
($a$) in paragraph~(1)\footnote{Paragraph (1) was amended by S.I.~2002/486 and 1792.}—
\begin{enumerate}\item[]
(i) in sub-paragraph~($a$)(iii)  after “state pension credit” insert “,~employment and~support allowance”; and

(ii) in sub-paragraph~($b$)(iii)  for~“or~state pension credit” substitute “,~state pension credit or~employment and~support allowance”; and
\end{enumerate}

($b$) in paragraph~(3)($c$)\footnote{Paragraph (3) was amended by S.I.~2002/1792.} after “state pension credit” insert “,~employment and~support allowance”.
\end{enumerate}

(3) In regulation~3 (reduction of income support)—
\begin{enumerate}\item[]
($a$) in the heading after “income support” add “and~income-related employment and~support allowance”;

($b$) in paragraph~(1) after “income support” the first time it occurs insert “or~an income-related employment and~support allowance”;

($c$) in paragraph~(4) after “income support” each time it occurs insert “or~an income-related employment and~support allowance”;

($d$) in paragraph~(5) after “income support” insert “or~an income-related employment and~support allowance”; and

($e$) in paragraph~(6) after “Regulations” add “or, as the case may be, regulation~2(1) of the Employment and~Support Allowance Regulations 2008”.
\end{enumerate}

\addtocontents{toc}{\protect\pagebreak[3]}

\subsection[Chapter IV --- Child support]{Chapter IV\\*Child support}

\renewcommand\parthead{--- Part V Chapter IV}

\subsubsection[57. Amendment of the Child Support (Maintenance Assessment Procedure) Regulations 1992]{Amendment of the Child Support (Maintenance Assessment Procedure) Regulations 1992}

57.---(1)  The Child Support (Maintenance Assessment Procedure) Regulations 1992\footnote{S.I.~1992/1813 which was revoked with savings by S.I.~2000/157.} are amended as follows.

(2) In regulation~1(2) (citation, commencement and~interpretation)—
\begin{enumerate}\item[]
($a$) in the definition of “benefit week” after “Jobseeker’s Allowance Regulations,” insert “in relation to employment and~support allowance has the same meaning as in the Employment and~Support Allowance Regulations 2008,”;

($b$) after the definition of “family credit” insert—
\begin{quotation}\sloppy
““income-related employment and~support allowance” means an income-related allowance under Part~I of the Welfare Reform Act 2007;”; and
\end{quotation}

($c$) in the definition of “relevant benefit” after “income-based jobseeker’s allowance,” insert “income-related employment and~support allowance”.
\end{enumerate}

(3) In paragraph~(3)($c$)  for~“or~income-based jobseeker’s allowance” substitute “,~income-based jobseeker’s allowance or~income-related employment and~support allowance”.

(4) In regulation~8D(8)\footnote{Regulation 8D was inserted by S.I.~1995/3261 and paragraph (8) was amended by S.I.~1996/3196 and 2003/2779.} (miscellaneous provisions in relation to interim maintenance assessments) “income support” each time it occurs insert “,~an income-related employment and~support allowance”.

(5) In regulation~30A(5)\footnote{Regulation 30A was inserted by S.I.~1995/3261 and paragraph (5) was inserted by S.I.~1996/3196 and amended by S.I.~1996/3196, 1999/1047 and 2003/2779.} (effective dates of new maintenance assessments in particular cases) for~“or~an income-based jobseeker’s allowance” each time it occurs substitute “,~an income-based jobseeker’s allowance or~an income-related employment and~support allowance”.

\subsubsection[58. Amendment of the Child Support (Maintenance Assessments and Special Cases) Regulations 1992]{Amendment of the Child Support (Maintenance Assessments and Special Cases) Regulations 1992}

58.---(1)  The Child Support (Maintenance Assessments and~Special Cases) Regulations 1992\footnote{S.I.~1992/1815 which is revoked with savings by S.I.~2001/155.} are amended as follows.

(2) In regulation~1(2) (citation, commencement and~interpretation) after the definition of “weekly council tax” insert—
\begin{quotation}
““the Welfare Reform Act” means the Welfare Reform Act 2007;”.
\end{quotation}

(3) In regulation~7(1)($b$)  (net income: calculation or~estimation of $N$) for~“or~the Jobseekers Act” substitute “,~the Jobseekers Act or~the Welfare Reform Act”.

(4) In regulation~28(1) (amount payable where absent parent is in receipt of income support or~other prescribed benefit) after “income-based jobseeker’s allowance” insert “,~income-related employment and~support allowance under Part~I of the Welfare Reform Act,”.

(5) In Schedule~1 (calculation of $N$ and~$M$) in paragraph~6(2) of Part~II (benefit payments) for~“or~the Jobseekers Act” substitute “,~the Jobseekers Act or~the Welfare Reform Act”.

\subsubsection[59. Amendment of the Social Security Benefits (Maintenance Payments and~Consequential Amendments) Regulations 1996]{\sloppy Amendment of the Social Security Benefits (Maintenance Payments and Consequential Amendments) Regulations 1996}

59.---(1)  The Social Security Benefits (Maintenance Payments and~Consequential Amendments) Regulations 1996\footnote{S.I.~1996/940.} are amended as follows.

(2) In regulation~1 (citation, commencement and~interpretation) after the definition of “the Act” insert—
\begin{quotation}
““the Employment and~Support Allowance Regulations” means the Employment and~Support Allowance Regulations 2008;”.
\end{quotation}

(3) In regulation~2($c$)  (interpretation for~the purposes of section~74A of the Act) after (ii)  add—
\begin{quotation}
“or

(iii) any income which is taken into account under Part~X of the Employment and~Support Allowance Regulations for~the purposes of calculating the amount of employment and~support allowance to which the claimant is entitled.”.
\end{quotation}

(4) In regulation~3 (persons of a prescribed description) after sub-\hspace{0pt}paragraph~($b$)  add—
\begin{quotation}
“or

($c$) is referred to as a “young person” in the Employment and~Support Allowance Regulations by virtue of regulation~2(1) of those Regulations.”;
\end{quotation}

(5) In regulation~5 (circumstances in which persons are to be treated as being members of the same household)—
\begin{enumerate}\item[]
($a$) omit “either”; and

($b$) after “Jobseeker’s Allowance Regulations” insert “or~regulation~156 of the Employment and~Support Allowance Regulations”.
\end{enumerate}

\subsubsection[60. Amendment of the Child Support Departure Direction and~Consequential Amendments Regulations 1996]{Amendment of the Child Support Departure Direction and~Consequential Amendments Regulations 1996}

60.---(1)  The Child Support Departure Direction and~Consequential Amendments Regulations 1996\footnote{S.I.~1996/2907 which is revoked with savings by S.I.~2001/156..} are amended as follows.

(2) In regulation~1(2) (citation, commencement and~interpretation) after the definition of “effective date” insert—
\begin{quotation}
““income-related employment and~support allowance” means an income-related allowance under Part~I of the Welfare Reform Act 2007 (employment and~support allowance);”.
\end{quotation}

(3) In regulation~9\footnote{Regulation 9 was substituted by S.I.~1998/58.} (departure directions and~persons in receipt of income support, state pension credit, income-based jobseeker’s allowance, or~working tax credit)—
\begin{enumerate}\item[]
($a$) in the heading after “state pension credit” insert “,~income-related employment and~support allowance,”; and

($b$) after “state pension credit” each time it occurs insert “,~income-related employment and~support allowance”.
\end{enumerate}

(4) In regulation~12 (meaning of “benefit” for~the purposes of section~28E of the Act) after “income-based jobseeker’s allowance” insert “,~income-related employment and~support allowance,”.

\subsubsection[61. Amendment of the Child Support (Maintenance Calculations and~Special Cases) Regulations 2000]{Amendment of the Child Support (Maintenance Calculations and Special Cases) Regulations 2000}

61.---(1)  The Child Support (Maintenance Calculations and~Special Cases) Regulations 2000\footnote{S.I.~2001/155.} are amended as follows.

(2) In regulation~1(2) (citation, commencement and~interpretation) after the definition of “war widower’s pension”\footnote{Definition was inserted by S.I.~2003/2779 and amended by S.I.~2005/2877.} insert—
\begin{quotation}
““the Welfare Reform Act” means the Welfare Reform Act 2007;”.
\end{quotation}

(3) In regulation~4 (flat rate)—
\begin{enumerate}\item[]
($a$) in paragraph~(1)\footnote{Paragraph (1) was amended by S.I.~2002/2497, 2003/2779, 2005/785 and 2005/2877.}—
\begin{enumerate}\item[]
(i) after sub-paragraph~($f$)  omit “and”; and

(ii) after sub-paragraph~($g$)  add—
\begin{quotation}
“and

($h$) contributory employment and~support allowance under section~2 of the Welfare Reform Act.”;
\end{quotation}
\end{enumerate}

($b$) in paragraph~(2)\footnote{Paragraph (2) was amended by S.I.~2002/3019.} after sub-paragraph~($c$)  add—
\begin{quotation}
“and

($d$) income-related employment and~support allowance under section~4 of the Welfare Reform Act.”.
\end{quotation}
\end{enumerate}

(4) In regulation~5($d$)\footnote{Regulation 5($d$) was amended by S.I.~2002/3019, 2003/1195, 2003/2779, 2004/2415 and 2005/785.} (nil rate) for~“or~income-based jobseeker’s allowance” each time it occurs substitute “,~income-based jobseeker’s allowance or~income-related employment and~support allowance”.

\subsubsection[62. Amendment of the Child Support (Variations) Regulations 2000]{Amendment of the Child Support (Variations) Regulations 2000}

62.  In regulation~32 of the Child Support (Variations) Regulations 2000\footnote{S.I.~2001/156.} (meaning of “benefit” for~the purposes of section~28E\footnote{Section 28E of the Child Support Act 1991 was substituted by the Child Support, Pensions and Social Security Act 2000 (c.~19).} of the Act) after “income-based jobseeker’s allowance,” insert “income-related employment and~support allowance under Part~I of the Welfare Reform Act 2007”.

\subsubsection[63. Amendment of the Child Support (Maintenance Calculation Procedure) Regulations 2000]{Amendment of the Child Support (Maintenance Calculation Procedure) Regulations 2000}

63.  In Schedule~1 (meaning of “child” for~the purposes of the Act) in paragraph~1(3)($b$)  (persons of 16 or~17 years of age who are not in full-time non-advanced education) of the Child Support (Maintenance Calculation Procedure) Regulations 2000\footnote{S.I.~2001/157.} for~“or~an income-based jobseeker’s allowance” substitute “,~an income-based jobseeker’s allowance or~income-related employment and~support allowance”.

\subsection[Chapter V --- Miscellaneous amendments]{Chapter V\\*Miscellaneous amendments}

\renewcommand\parthead{--- Part V Chapter V}

\subsubsection[64. Amendment of the Social Security (Benefit) (Married Women and~Widows Special Provisions) Regulations 1974]{Amendment of the Social Security (Benefit) (Married Women and Widows Special Provisions) Regulations 1974}

64.---(1)  The Social Security (Benefit) (Married Women and~Widows Special Provisions) Regulations 1974\footnote{S.I.~1974/2010.} are amended as follows.

(2) In regulation~1(2) (citation, commencement and~interpretation)—
\begin{enumerate}\item[]
($a$) after the definition of “the Industrial Injuries Act” insert—
\begin{quotation}
““the Welfare Reform Act” means the Welfare Reform Act 2007;”; and
\end{quotation}

($b$) after the definition of “appropriate weekly rate” insert—
\begin{quotation}
““contributory employment and~support allowance” means a contributory allowance under Part~I of the Welfare Reform Act;”.
\end{quotation}
\end{enumerate}

(3) In regulation~3\footnote{Regulation 3 was amended by S.I.~1978/508, 1989/893, 1995/829 and 1996/1345.} (modifications, etc.)—
\begin{enumerate}\item[]
($a$) in the heading after “short-term incapacity benefit” insert “,~contributory employment and~support allowance”;

($b$) in paragraph~(1)—
\begin{enumerate}\item[]
(i) in sub-paragraph~($a$)  after “the Act” add “or, in relation to contributory employment and~support allowance, she shall be deemed to have satisfied the first condition referred to in paragraph~1(1) of Schedule~1 to the Welfare Reform Act”; and

(ii) in sub-paragraph~($b$)  after “the Act” insert “or, in relation to contributory employment and~support allowance, she shall be deemed to have satisfied the second condition referred to in paragraph~2(1) of Schedule~1 to the Welfare Reform Act”; and
\end{enumerate}

($c$) in paragraph~(5) after “short-term incapacity benefit” each time it appears insert “,~contributory employment and~support allowance”.
\end{enumerate}

\subsubsection[65. Amendment of the Social Security (Airmen’s Benefits) Regulations 1975]{Amendment of the Social Security (Airmen’s Benefits) Regulations 1975}

65.---(1)  The Social Security (Airmen’s Benefits) Regulations 1975\footnote{S.I.~1975/494.} are amended as follows.

(2) In regulation~1(2) (citation, commencement and~interpretation) after the definition of “the Act” insert—
\begin{quotation}
““the Welfare Reform Act” means the Welfare Reform Act 2007;”.
\end{quotation}

(3) In regulation~2\footnote{Regulation 2 was amended by S.I.~1984/1303 and 1995/829.} (removal of disqualification etc.)---
\begin{enumerate}\item[]
($a$) in paragraph~(1)—
\begin{enumerate}\item[]
(i) after “of the Act” insert “or~section~18(1) of the Welfare Reform Act”; and

(ii) after “incapacity benefit” insert “,~employment and~support allowance”.
\end{enumerate}

($b$) in paragraph~(2)—
\begin{enumerate}\item[]
(i) after “incapacity benefit” insert “,~employment and~support allowance”; and

(ii) after “incapable of work” insert “or~to have limited capability for~work as defined in section~1(4) of the Welfare Reform Act”.
\end{enumerate}
\end{enumerate}

(4) In regulation~3\footnote{Regulation 3 was amended by S.I.~1996/1345.} (application of the Act and~regulations) after “thereunder” the second time it occurs insert “and~Part~I of the Welfare Reform Act and~regulations made under it”.

\subsubsection[66. Amendment of the Social Security (Benefit) (Members of the Forces) Regulations 1975]{\sloppy Amendment of the Social Security (Benefit) (Members of the Forces) Regulations 1975}

66.  In regulation~2 (unemployment etc.)\ of the Social Security (Benefit) (Members of the Forces) Regulations 1975\footnote{S.I.~1975/493. Regulation 2 was amended by S.I.~1984/1303 and 1996/1345.} after “jobseeker’s allowance” insert “,~an employment and~support allowance”.

\subsubsection[67. Amendment of the Social Security (Mariners’ Benefits) Regulations 1975]{Amendment of the Social Security (Mariners’ Benefits) Regulations 1975}

67.---(1)  The Social Security (Mariners’ Benefits) Regulations 1975\footnote{S.I.~1975/529.} are amended as follows.

(2) In regulation~1(2) (citation, commencement and~interpretation)——
\begin{enumerate}\item[]
($a$) after the definition of “Contributions Regulations” insert—
\begin{quotation}
““contributory employment and~support allowance” means a contributory allowance under Part~I of the Welfare Reform Act;”; and
\end{quotation}

($b$) after the definition of “on-shore share fisherman” insert—
\begin{quotation}
““the Welfare Reform Act” means the Welfare Reform Act 2007;”.
\end{quotation}
\end{enumerate}

(3) In regulation~4 (removal of disqualification etc.)—
\begin{enumerate}\item[]
($a$) after “of the Act” insert “or~section~18(1) of the Welfare Reform Act 2007,”; and

($b$) after “incapacity benefit” each time it occurs insert “,~contributory employment and~support allowance”;
\end{enumerate}

(4) In regulation~5 (evidence of unemployment or~incapacity)—
\begin{enumerate}\item[]
($a$) in the heading for~“or~incapacity” substitute “,~incapacity for~work or~limited capability for~work”; and

($b$) after “incapacity benefit” insert “,~contributory employment and~support allowance”.
\end{enumerate}

(5) In regulation~6 (special provisions etc.)—
\begin{enumerate}\item[]
($a$) in the heading for~“or~incapacity for~work” substitute “,~incapacity for~work or~limited capability for~work”;

($b$) in paragraph~(2)—
\begin{enumerate}\item[]
(i) after “incapacity benefit” insert “,~contributory employment and~support allowance”; and

(ii) after “incapable of work” insert “or~as having limited capability for~work as defined in section~1(4) of the Welfare Reform Act”.
\end{enumerate}
\end{enumerate}

\subsubsection[68. Amendment of the Social Security (Medical Evidence) Regulations 1976]{Amendment of the Social Security (Medical Evidence) Regulations 1976}

68.---(1)  The Social Security (Medical Evidence) Regulations 1976\footnote{S.I.~1976/615.} are amended as follows.

(2) In regulation~1 (citation, commencement and~interpretation) after the definition of “the Contributions and~Benefits Act”\footnote{Definition was inserted by S.I.~1994/2975.} insert—
\begin{quotation}
““the Employment and~Support Allowance Regulations” means the Employment and~Support Allowance Regulations 2008;

“limited capability for~work” has the meaning given in section~1(4) of the Welfare Reform Act 2007;

“limited capability for~work assessment” means the assessment of whether a person has limited capability for~work as set out in regulation~19(2) of, and~in Schedule~2 to, the Employment and~Support Allowance Regulations;”.
\end{quotation}

(3) In regulation~2 (evidence of incapacity for~work and~confinement)—
\begin{enumerate}\item[]
($a$) in the heading, after “incapacity for~work” insert “,~limited capability for~work”;

($b$) in paragraph~(1)\footnote{Paragraph (1) was amended by S.I.~1982/699, 1992/247, 1994/2975, 1995/987 and 2000/590.}—
\begin{enumerate}\item[]
(i) after “incapable of work” insert “or~having limited capability for~work”;

(ii) after “personal capability assessment” each time it occurs insert “or~the limited capability for~work assessment”;

(iii) after “evidence of such incapacity” insert “or~limited capability for~work”; and

(iv) in sub-paragraph~($c$)  after “incapable of work” insert “or whether a person has or~does not have limited capability for~work”; and
\end{enumerate}

($c$) in paragraph~(2)\footnote{Paragraph (2) was amended by S.I.~1994/2975 and 1999/3190.} after “personal capability assessment” insert “or~the limited capability for~work assessment”.
\end{enumerate}

(4) In regulation~5\footnote{Regulation 5 was inserted by S.I.~1982/699 and amended by S.I.~1994/2975.} (self-certificate for~first 7 days of a spell of incapacity for~work)—
\begin{enumerate}\item[]
($a$) in the heading after “incapacity for~work” insert “or~limited capability for~work”;

($b$) in paragraph~(1)—
\begin{enumerate}\item[]
(i) after “incapacity” insert “or~limited capability for~work”;

(ii) after sub-paragraph~($a$)  omit “or”;

(iii) after sub-paragraph~($b$)  insert—
\begin{quotation}
“($c$) for~a period of limited capability for~work which lasts less than 8 days; or

($d$) in respect of any of the first 7 days of a longer period of limited capability for~work,”; and
\end{quotation}
\end{enumerate}

($c$) in paragraph~(2) for~the definition of “self-certificate” substitute—
\begin{quotation}
““self-certificate” means either—
\begin{enumerate}\item[]
(i) 
a declaration made by the claimant in writing, on a form approved for~the purpose by the Secretary of State; or

(ii) 
where the claimant has made a claim for~employment and~support allowance in accordance with regulation~4G of the Social Security (Claims and~Payments) Regulations 1987, an oral declaration by the claimant,
\end{enumerate}
that the claimant has been unfit for~work from a date or~for~a period specified in the declaration and~may include a statement that the claimant expects to continue to be unfit for~work on days subsequent to the date on which it is made;.”.
\end{quotation}
\end{enumerate}

\subsubsection[69. Amendment of the Social Security (Immigration and~Asylum) Consequential Amendments Regulations 2000]{Amendment of the Social Security (Immigration and~Asylum) Consequential Amendments Regulations 2000}

69.---(1)  The Social Security (Immigration and~Asylum) Consequential Amendments Regulations 2000\footnote{S.I.~2000/636.} are amended as follows.

(2) In regulation~1(3) (citation, commencement and~interpretation)—
\begin{enumerate}\item[]
($a$) after the definition of “the Disability Living Allowance Regulations” insert—
\begin{quotation}
““the Employment and~Support Allowance Regulations” means the Employment and~Support Allowance Regulations 2008;”; and
\end{quotation}

($b$) after the definition of “the Severe Disablement Allowance Regulations” add—
\begin{quotation}\sloppy
““income-related employment and~support allowance” means an income-related allowance under Part~I of the Welfare Reform Act 2007 (employment and~support allowance).”
\end{quotation}
\end{enumerate}

(3) In regulation~2 (persons not excluded from specified benefits under section~115 of the Immigration and~Asylum Act 1999\footnote{1999 c.~33.})—
\begin{enumerate}\item[]
($a$) in paragraph~(1) after “Benefits Acts” insert “income-related employment and~support allowance,”;

($b$) in paragraph~(4)($a$)  after “Benefits Act,” insert “or~income-related employment and~support allowance,”; and

($c$) in paragraph~(5) after “Jobseeker’s Allowance Regulations (urgent cases) insert “,~to employment and~support allowance by virtue of regulation~162 of the Employment and~Support Allowance Regulations (urgent cases)”;
\end{enumerate}

(4) In regulation~12 (transitional arrangements and~savings) in paragraph~(3) after “Income Support Regulations” insert “,~regulation~162 of the Employment and~Support Allowance Regulations”.

(5) In the heading to Part~I of the Schedule~(persons not excluded from certain benefits etc.)\ after “Income Support,” insert “Income-Related Employment and~Support Allowance,”.

\subsubsection[70. Amendment of the Children (Leaving Care) Social Security Benefits Regulations 2001]{Amendment of the Children (Leaving Care) Social Security Benefits Regulations 2001}

70.  In regulation~2(1) of the Children (Leaving Care) Social Security Benefits Regulations 2001\footnote{S.I.~2001/3074.} (entitlement to benefits) for~“or~income-based jobseeker’s allowance” substitute “,~income-based jobseeker’s allowance or~income-related employment and~support allowance”.

\subsubsection[71. Amendment of the Social Security (Jobcentre Plus Interviews for Partners) Regulations 2003]{Amendment of the Social Security (Jobcentre Plus Interviews for Partners) Regulations 2003}

71.---(1)  In regulation~11(4) of the Social Security (Jobcentre Plus Interviews for~Partners) Regulations 2003\footnote{S.I.~2003/1886.} (failure to take part in an interview) after sub-paragraph~($a$)  insert—
\begin{quotation}
“($aa$) an income-related employment and~support allowance under Part~I of the Welfare Reform Act 2007 (employment and~support allowance);”.
\end{quotation}

\subsubsection[72. Amendment of the Age-Related Payments Regulations 2005]{Amendment of the Age-Related Payments Regulations 2005}

72.  In regulation~2(3)($a$)  of the Age-Related Payments Regulations 2005\footnote{S.I.~2005/1983.} (entitlement: basic cases) for~“or~income support” substitute “,~income support or~income-related employment and~support allowance under Part~I of the Welfare Reform Act 2007”. 

\bigskip

Signed 
by authority of the 
Secretary of State for~Work and~Pensions.
%I concur
%By authority of the Lord Chancellor

{\raggedleft
\emph{Stephen C.~Timms}\\*
%Secretary
Minister
%Parliamentary Under-Secretary 
of State,\\*Department 
for~Work and~Pensions

}

12th June 2008

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

The Regulations contained in this Instrument are either made by virtue of, or~are consequential upon, provisions in Part~I of the Welfare Reform Act 2007 (c.~5). This Instrument is made before the expiry of the period of 6 months beginning with the coming into force of those provisions; the regulations in it are therefore exempt in accordance with section~173(5) of the Social Security Administration Act 1992 from the requirement in section~172(1) of that Act to refer proposals to make Regulations to the Social Security Advisory Committee and~are made without reference to that Committee.

Part~II makes consequential amendments to income-related benefits. Regulation~2 makes consequential changes to the Income Support (General) Regulations 1987. Regulation~3 makes consequential amendments to the Jobseeker’s Allowance Regulations 1996. Regulation~4 makes consequential amendments to the State Pension Credit Regulations 2002.

Part~III makes changes to the Social Fund scheme so as to extend entitlement to certain payments to applicants who are entitled to an employment and~support allowance.

Part~IV makes consequential changes in relation to administrative provisions.

Chapter I makes changes to the Social Security (Claims and~Payments) Regulations 1987 so as to make separate provision for~claims for, and~payment of, state pension credit.

Regulation~13 provides for~the manner of making a claim for~employment and~support allowance which may be by telephone or~by written claim.

Regulations 14 to 20 and~regulations 22 and~23 apply provisions currently in the Social Security (Claims and~Payments) Regulations 1987 to employment and~support allowance.

Regulation~21 provides for~the day on which employment and~support allowance is to be paid to the claimant.

Regulation~24 provides that a claim for~employment and~support allowance may be made in addition to or~in the alternative to other benefits.

Regulation~25 provides that a claim for~employment and~support allowance may be made within 3 months of the date for~which the claim is made.

Regulations 26, 27 and~28 provide that deductions may be made from employment and~support allowance and~paid direct to third parties.

Chapter II applies the Social Security and~Child Support (Decisions and~Appeals) Regulations 1999 to employment and~support allowance.

Regulation~31 provides additional circumstances in which a decision relating to employment and~support allowance may be revised.

Regulations 32, 33 and~34 provide additional circumstances in which a decision relating to employment and~support allowance may be superseded and~for~the effective date of that supersession.

Part~V makes miscellaneous amendments.

Chapter I makes consequential amendments in relation to statutory sick pay and~statutory maternity pay to prevent duplication of payments.

Chapter II makes consequential amendments in relation to national insurance contributions and~credits.

Chapter III adds references to employment and~support allowance to—
\begin{enumerate}\item[]
    the Social Security (Recovery of Benefits) Act 1997;

    the Social Security (Payments on Account, Overpayments and~Recovery) Regulations 1988;

    the Community Charges (Deductions From Income Support) (No.~2) Regulations 1990;

    the Fines (Deductions From Income Support) Regulations 1992;

    the Council Tax (Deductions From Income Support) Regulations 1993;

    the Social Security (Loss of Benefit) Regulations 2001. 
\end{enumerate}

Chapter IV makes consequential amendments in relation to child support by adding references to employment and~support allowance to—
\begin{enumerate}\item[]
    the Child Support (Maintenance Assessment Procedure) Regulations 1992;

    the Child Support (Maintenance Assessment and~Special Cases) Regulations 1992;

    the Social Security Benefits (Maintenance Payments and~Consequential Amendments) Regulations 1996;

    the Child Support Departure Directions and~Consequential Amendments Regulations 1996;

    the Child Support (Maintenance Calculations and~Special Cases) Regulations 2000;

    the Child Support (Variations) Regulations 2000;

    the Child Support (Maintenance Calculation Procedure) Regulations 2000. 
\end{enumerate}

Chapter V makes miscellaneous amendments by adding the references to employment and~support allowance to—
\begin{enumerate}\item[]
    the Social Security (Benefit) (Married Women and~Widows Special Provisions) Regulations 1974;

    the Social Security (Airmen’s Benefits) Regulations 1975;

    the Social Security (Benefit) (Members of the Forces) Regulations 1975;

    the Social Security (Mariner’s Benefits) Regulations 1975;

    the Social Security (Medical Evidence) Regulations 1976;

    the Social Security (Immigration and~Asylum) Consequential Amendments Regulations 2000;

    the Children (Leaving Care) Social Security Benefits Regulations 2001;

    the Social Security (Jobcentre Plus Interviews For~Partners) Regulations 2003;

    the Age-Related Payments Regulations 2005. 
\end{enumerate}

These Regulations have no impact on the cost of business, charities or~the voluntary sector~and~an Impact Assessment has not been published. 

\end{document}