\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 5) Order 2000}

\newcommand\regsnumber{2000/3354}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I. 2000 No. 3354 (C.112)}

\date{Made 18th December 2000%\\Laid before Parliament 6th December 2000\\Coming into force as provided in regulation 1(1)
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.57402pt}

\begin{document}

\maketitle

\noindent
The Secretary of State for Social Security, in exercise of the powers conferred upon him by section 86(2) of the Child Support, Pensions and Social Security Act 2000\footnote{\frenchspacing 2000 c. 19.} and of all other powers enabling him in that behalf, hereby makes the following Order: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation]{Citation}

1.---(1)  This Order may be cited as the Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 5) Order 2000.

(2) In this Order—
\begin{enumerate}\item[]
($a$) “the Act” means the Child Support, Pensions and Social Security Act 2000 and, except where otherwise stated, references to sections and Schedules are references to sections of and Schedules to the Act; and

($b$) “the 1991 Act” means the Child Support Act 1991\footnote{\frenchspacing 1991 c. 48.}.
\end{enumerate}

\subsection[2. Appointed days]{Appointed days}

2.---(1)  31st January 2001 is the day appointed for the coming into force of the following provisions:—
\begin{enumerate}\item[]
($a$) sections 13, 14, 15 and 22(1) to (3); and

($b$) paragraph 11(2) of Schedule 3, and section 26 in so far as it relates to that paragraph, in so far as that paragraph affects section 3(2) of the 1991 Act (change of terminology from “absent parent” to “non-resident parent”) for the purposes of sections 15(4A) and 44(2A) of the 1991 Act, inserted respectively by sections 14 and 22(3), and section 44(1) of the 1991 Act amended by section 22(2).
\end{enumerate}

(2) The day appointed for the coming into force of section 11 is 15th February 2001.

(3) The day appointed for the coming into force of sections 16 and 17 is 2nd April 2001. 

\bigskip

Signed 
by authority of the Secretary of State for Social Security.

{\raggedleft
\emph{P.~Hollis}\\*Parliamentary Under-Sercretary of State,\\*Department of Social Security

}

18th December 2000

\small

\part{Explanatory Note}

\renewcommand\parthead{--- Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

This Order brings into force further provisions of the Child Support, Pensions and Social Security Act 2000 which brings into force the Child Support Act 1991 (“the 1991 Act”) as follows.

Article 2(1) commences provisions relating to changes to the child support system in sections 13, 14, 15 and 22(1) to (3) on 31st January 2001. Section 13 inserts a new section 14A into the 1991 Act which makes it a criminal offence to fail to provide information for child support purposes or to provide false information. Section 14 amends section 15 of the 1991 Act with regard to the powers of inspectors.

Section 15 adds to section 26(2) of the 1991 Act further cases where parentage may be presumed, including where the alleged parent refuses to take a scientific test or such a test shows there is no reasonable doubt he is the parent. Section 22(1) to (3) amends section 44 of the 1991 Act to extend the jurisdiction of that Act to non-resident parents who are not habitually resident in the United Kingdom but are in certain types of employment.

Article 2(2) commences section 11 on 15th February 2001. Section 11 inserts a new section 23A into the 1991 Act (“the 1991 Act”) to enable the appeal tribunal to redetermine cases in certain circumstances.

Article 2(3) commences sections 16 and 17 on 2nd April 2001. These sections insert new sections 39A, 40A and 40B into the 1991 Act and amend section 40 of that Act. The provisions give power to magistrates courts in England and Wales, and the sheriff in Scotland, where there has been wilful refusal or culpable neglect to pay child support maintenance, to commit the liable person to prison, or make an order for him to be disqualified from holding or obtaining a driving licence, as they consider appropriate.

The impact on business of the commencement provisions in the Child Support, Pensions and Social Security Act 2000 is detailed in the Regulatory Impact Assessment (as revised) relating to the Child Support, Pensions and Social Security Bill (which was introduced in the House of Commons on 1st December 1999). A copy of that Assessment has been placed in the libraries of both Houses of Parliament and can be obtained from the Department of Social Security, Regulatory Impact Unit, 3rd Floor, Adelphi, 1--11 John Adam Street, London \textsc{\lowercase{WC2N 6HT}}. 

\end{document}