\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 11) Order 2002}

\newcommand\regsnumber{2002/437}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2002 No.\ 437 (C.\ 12)}

\date{Made
27th February 2002\\
%Laid before Parliament
%10th May 2001\\
%Coming into force
%31st May 2001
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.57402pt}

\begin{document}

\maketitle

\noindent
The Secretary of State for Work and Pensions, in exercise of the powers conferred by section 86(2) and (3)($a$)  of the Child Support, Pensions and Social Security Act 2000\footnote{2000 c.\ 19.} and of all other powers enabling him in that behalf, hereby makes the following Order:  

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and interpretation]{Citation and interpretation}

1.---(1)  This Order may be cited as the Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 11) Order 2002.

(2) In this Order, unless the context otherwise requires, any reference to a numbered section or Schedule is a reference to the section or, as the case may be, the Schedule bearing that number in the Child Support, Pensions and Social Security Act 2000.

\subsection[2. Amendment of earlier Order]{Amendment of earlier Order}

2.  Article 2($b$)  of the Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 9) Order 2001\footnote{S.I.\ 2001/2295 (C.\ 76).} (which brings Part II of Schedule 5 into force on 6th April 2002 for all purposes other than that of authorising the making of regulations and orders) shall be omitted.

\subsection[3. Appointed days]{Appointed days}

3.---(1)  The day appointed for the coming into force of
\begin{enumerate}\item[]
($a$) sections 47 (information to be given to the Authority) and 48 (modification by Authority to secure winding-up);

($b$) section 49(1) (reports about winding-up) in so far as it inserts section 72A(1) and (2) into the Pensions Act 1995\footnote{1995 c.\ 26.};

($c$) section 49(1) in so far as it inserts section 72A(3) into that Act, except for the words “Subject to subsection (4),” and “(apart from any postponement under subsection (4))”;

($d$) section 49(1) in so far as it inserts section 72A(7), (8)($a$)  and (9) into that Act;

($e$) section 49(2) and (3);

($f$) section 50 (directions for facilitating winding-up);

($g$) section 54 (investigations by the Pensions Ombudsman);

($h$) section (2) of Part III of Schedule 9 (repeals: information to be given to the Authority)
\end{enumerate}
is 1st March 2002 for the purposes of making regulations and rules.

(2) The day appointed for the coming into force of the provisions mentioned in paragraph (1) of this article, except section 54, is 1st April 2002 for all purposes other than the purposes of making regulations.

(3) The day appointed for the coming into force of section (11) of Part III of Schedule 9 (spent provisions) is 6th April 2002. 

\bigskip

Signed 
by authority of the Secretary of State for Work and Pensions.

{\raggedleft
\emph{Ian McCartney}\\*Minister of State,\\*Department of Work and Pensions

}

%Dated
27th February 2002

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Order)}

This Order brings into force further provisions of the Child Support, Pensions and Social Security Act 2000 (“the Act”). It also amends an earlier commencement order.

Article 1 is about citation and interpretation.

Article 2 amends the Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 9) Order 2001 with the effect of revoking the coming into force date for Part II of Schedule 5 to the Act (alternative to anti-franking rules).

Article 3 appoints 1st March 2002 as the date for the coming into force of sections 47, 48 and 50 and part of section 49 of the Act, and a related repeal in Part III of Schedule 9, for the purposes of making regulations. Article 3 also appoints 1st April 2002 as the date for the coming into force of those provisions for all other purposes. These provisions relate to the winding-up of schemes.

Article 3 appoints 1st March 2002 as the date for the coming into force of section 54 for the purposes of making regulations and rules. Section 54 relates to investigations by the Pensions Ombudsman.

The impact on business of the commencement of provisions in the Act is detailed in the Regulatory Impact Assessment (as revised) relating to the Child Support, Pensions and Social Security Bill (which was introduced in the House of Commons on 1st December 1999). A copy of that Assessment has been placed in the libraries of both Houses of Parliament and can be obtained from the Department for Work and Pensions, Regulatory Impact Unit, 3rd floor, the Adelphi, 1--11 John Adam Street, London \textsc{\lowercase{WC2N 6HT}}. 

\end{document}