\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support (Consequential and Miscellaneous Amendments) (No.~2) Regulations 2014}

\newcommand\regsnumber{2014/1621}

\title{\regstitle}

\author{S.I.\ 2014 No.\ 1621}

\date{Made
23rd June 2014\\
Laid before Parliament
23rd June 2014\\
Coming into force
in accordance with regulation 1
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.61603pt}

%\hbadness=10000

\begin{document}

\maketitle

\begin{center}
\itshape This Statutory Instrument has been printed to correct errors in S.I.~2014/1386 and is being issued free of charge to all known recipients of that Statutory Instrument. 
\end{center}

\enlargethispage{\baselineskip}

\noindent
The Secretary of State for Work and Pensions, in exercise of the powers conferred by sections 43A, 51(1) and 52(4) of the Child Support Act 1991\footnote{1991 c.~48. Section 43A was inserted by section 38 of the Child Maintenance and Other Payments Act 2008 (c.~6) and amended by S.I.~2012/2007.}, makes the following Regulations: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and commencement]{Citation and commencement}

1.—(1) These Regulations may be cited as the Child Support (Consequential and Miscellaneous Amendments) (No.~2) Regulations 2014.

(2) This regulation and regulation 3 come into force on 24th June 2014.

(3) Regulation 2 comes into force on 11th August 2014.

\subsection[2. Modification of the Child Support (Management of Payments and Arrears) Regulations 2009]{Modification of the Child Support (Management of Payments and Arrears) Regulations 2009}

2.—(1) The Child Support (Management of Payments and Arrears) Regulations 2009\footnote{S.I.~2009/3151, which was amended by S.I.~2012/2007; there are other amending instruments but none is relevant.} are modified, in relation to a case in which liability to pay child support maintenance is calculated in accordance with Part I of Schedule 1 to the Child Support Act 1991 as amended by paragraph 2 of Schedule 4 to the Child Maintenance and Other Payments Act 2008, as if they had been amended as follows.

(2) In regulation 11 (recovery of arrears from a deceased person’s estate), after “maintenance” insert “and collection fees (payable under regulation 7 (the collection fee) of the Child Support Fees Regulations 2014\footnote{S.I.~2014/612.})”.

\subsection[3. Variations to the Child Support (Consequential and Miscellaneous Amendments) Regulations 2014]{Variations to the Child Support (Consequential and Miscellaneous Amendments) Regulations 2014}

3.—(1) The Child Support (Consequential and Miscellaneous Amendments) Regulations 2014\footnote{S.I.~2014/1386.} are varied as follows.

(2) Any provision that came into force at the making of those Regulations is revoked and any legislation varied by such a provision is restored as if the variation had not been made.

(3) Regulation 1 (citation and commencement) is amended by substitution of the following for paragraphs (2) to (6)—
\begin{quotation}
“(2) These Regulations come into force on 30th June 2014.”.
\end{quotation}

(4) In regulation 2(1), for “are amended” substitute “are modified, in relation to a case in which liability to pay child support maintenance is calculated in accordance with Part I of Schedule 1 to the Child Support Act 1991 as amended by paragraph 2 of Schedule 4 to the Child Maintenance and Other Payments Act 2008, as if they had been amended”.

(5) In regulation 6(1), for “are amended” substitute “are modified, in relation to a case in which liability to pay child support maintenance is calculated in accordance with Part I of Schedule 1 to the Child Support Act 1991 as amended by paragraph 2 of Schedule 4 to the Child Maintenance and Other Payments Act 2008, as if they had been amended”.

(6) Regulation 6(5) is revoked. 

\bigskip

\pagebreak[3]

Signed 
by authority of the 
Secretary of State for~Work and~Pensions.
%I concur
%By authority of the Lord Chancellor

{\raggedleft
\emph{Steve Webb}\\*
%Secretary
Minister
%Parliamentary Under Secretary 
of State\\*Department 
for~Work and~Pensions

}

23rd June 2014

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations make amendments to the Child Support (Management of Payments and Arrears) Regulations 2009 (S.I.~2009/3151) (“the 2009 Regulations”) and the Child Support (Consequential and Miscellaneous Amendments) Regulations 2014 (S.I.~2014/1386) (“the 2014 Regulations”).

Regulation 2 modifies regulation 11 of the 2009 Regulations in relation to cases administered under the 2012 scheme of child support. The modification is consequential on the introduction of charging collection fees (a fee payable in a case where the Secretary of State arranges for collection of child maintenance) under the Child Support Fees Regulations 2014 (S.I.~2014/612) and enables the Secretary of State to recover collection fees from a deceased person’s estate.

Regulation 3 varies the 2014 Regulations. In so far as any provision came into force when the 2014 Regulations were made, paragraph (2) revokes it and restores any legislation varied by such provision. Paragraph (3) amends the commencement provisions in the 2014 Regulations so that those Regulations will be commenced on 30th June 2014. Paragraphs (4) and (5) vary regulations 2(1) and 6(1) of the 2014 Regulations so that the modifications made by regulations 2 and 6 apply only to cases administered under the 2012 scheme of child support. There is no commencement provision in the 2014 Regulations for paragraph (5) of regulation 6. Paragraph (6) revokes that paragraph. The amendment made by that paragraph is made by regulation 2 of these Regulations.

A full impact assessment has not been produced for this instrument as it has no impact on the private sector and civil society organisations. 

\end{document}