\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Social Security, Child Support, Vaccine Damage and Other Payments (Decisions and Appeals) (Amendment) Regulations 2013}

\newcommand\regsnumber{2013/2380}

\title{\regstitle}

\author{S.I.\ 2013 No.\ 2380}

\date{Made
10th September 2013\\
%%Laid before Parliament
%%27th June 2013\\
Coming into force
28th October 2013
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{41.57603pt}

%\hbadness=10000

\begin{document}

\maketitle

\enlargethispage{\baselineskip}

\noindent
The Secretary of State for Work and Pensions makes the following Regulations in exercise of the powers conferred by—
\begin{enumerate}\item[]
    sections 3A(3), 4(1B) and (2) and 8(1), (2)($b$)  and (5) of the Vaccine Damage Payments Act 1979\footnote{1979 c.~17 (“the 1979 Act”). Section 3A was inserted by section 45 of the Social Security Act 1998 (c.~14) (“the 1998 Act”). It was amended by S.I.~2008/2833, by section 67 of, and Schedule 8 to, the Welfare Reform Act 2007 (c.~5) (“the 2007 Act”) from a date to be appointed and by paragraph 108 of the Schedule to S.I.~2012/2007. Section 4 was substituted by section 46 of the 1998 Act and was amended by sections 57 and 63 of, and Schedule 7 to, the 2007 Act (date in force to be appointed), by S.I.~2008/2833 and by section 102(6) of, and Schedule 11 to, the Welfare Reform Act 2012 (c.~5) (“the 2012 Act”). Section 8 was substituted by Schedule 7 of the 1998 Act for the purpose of making regulations and for the purposes specified in article 1and Schedule 1 of S.I.~1999/2866.},

    sections 20(3A) and (5) (as it has effect apart from section 10 of the Child Support, Pensions and Social Security Act 2000)\footnote{2000 c.~19 (“the 2000 Act”).} and 52(4) of the Child Support Act 1991\footnote{1991 c.~48. Section 20(3A) was inserted by section 102 of, and Schedule 11 to, the 2012 Act. Section 52 was repealed by Schedule 4 to the Constitutional Reform Act 2005 (c.~4) (“the 2005 Act”) and by Schedule 8 of the Child Maintenance and Other Payments Act 2008 (c.~6) (“the 2008 Act”). It was substituted by Part~I section 25 of the 2000 Act in relation to cases specified in article 3 of S.I.~2003/192 and by Schedule 7 of the 2008 Act.},

    sections 20(2A) and (4) (as substituted by section 10 of the Child Support, Pensions and Social Security Act 2000) and 52(4) of the Child Support Act 1991\footnote{Section 20(2A) of the 2000 Act was inserted by section 102 of, and Schedule 11 to, the 2012 Act.},

    sections 1A(3)($e$), 11(2A), (5) and 30(4) of the Social Security (Recovery of Benefits) Act 1997\footnote{1997 c.~27 (“the 1997 Act”). Section 1A was inserted by section 54 of the 2008 Act. Section 11 was amended by section 86 of, and Schedule 7 to, the 1998 Act, section 59 of, and Schedule 11 to, the Constitutional Reform Act 2005 (c.~4) and by S.I.~2008/2833. Section 11(2A) was inserted, and 30 was amended, by section 102 of, and Schedule 11 to, the 2012 Act. Section 11(2A) was also amended by paragraph 108 of the Schedule to S.I.~2012/2007.}, and

    sections 9(1), 12(3A) and (7), 79(4), (6) and (7) and 84 of the Social Security Act 1998\footnote{1998 c.~14. Section 9 was amended by section 147 of, and Schedule 14 to the 2012 Act. Section 12(3A) was inserted, and section 12(7) was amended by, section 102 of the 2012 Act. Section 84 is cited for the meaning of “prescribe”.},

    sections 49(2), 50(1A) and (4) and 53(1), (2) and (2A) of the Child Maintenance and Other Payments Act 2008\footnote{2008 c.~6. Sections 49(2) was amended by, and sections 50(1A) and 53(2A) were inserted by section 102 of, and Schedule 11 to, the 2012 Act.}. 
\end{enumerate}

In so far as these Regulations are made under the Social Security (Recovery of Benefits) Act 1997 and the Social Security Act 1998, the Social Security Advisory Committee has agreed that the proposals in respect of these Regulations should not be referred to it\footnote{\emph{See} section 173(1) of the Social Security Administration Act 1992 (c.~5).}.

A draft of this instrument was laid before Parliament in accordance with section 8(2A)($b$)  of the Vaccine Damage Payments Act 1979\footnote{Section 8(2A) of the 1979 Act was inserted by section 102 of, and Schedule 11 to, the 2012 Act.}, section 52(2)($a$)  of the Child Support Act 1991\footnote{Section 52(2) of the 1991 Act was substituted by section 25 of the 2000 Act and was amended by section 102 of, and Schedule 11 to, the 2012 Act.}, section 30(2A) of the Social Security (Recovery of Benefits) Act 1997\footnote{Section 30(2A) of the 1997 Act was inserted by section 102 of, and Schedule 11 to, the 2012 Act.}, section 80(1) of the Social Security Act 1998\footnote{Section 80(1) of the 1998 Act was amended by S.I.~2008/2833 any by section 102 of, and Schedule 11 to, the 2012 Act.} and section 53(3) of the Child Maintenance and Other Payments Act 2008\footnote{Section 53(3) of the 2008 Act was amended by section 102 of, and Schedule 11 to, the 2012 Act.} and approved by resolution of each House of Parliament. 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and commencement]{Citation and commencement}

1.---(1)  These Regulations may be cited as the Social Security, Child Support, Vaccine Damage and Other Payments (Decisions and Appeals) (Amendment) Regulations 2013.

(2) These Regulations come into force on 28th October 2013.

\subsection[2. Amendment of the Vaccine Damage Payments Regulations 1979]{Amendment of the Vaccine Damage Payments Regulations 1979}

2.---(1)  The Vaccine Damage Payments Regulations 1979\footnote{S.I.~1979/432.} are amended as follows.

(2) In regulation 11(2)($b$)  (decisions reversing earlier decisions made by the Secretary of State or appeals tribunals)\footnote{Regulation 11 was substituted by S.I.~1999/2677.}, for “within six years of the date on which notification of that decision was given” substitute “at any time after notification of that decision was given but before a decision of an appeal tribunal has been made”.

(3) After regulation 11 (decisions reversing earlier decisions), insert—
\begin{quotation}
\subsection*{“Consideration of reversal before appeal}

11A.---(1)  This regulation applies in a case where—
\begin{enumerate}\item[]
($a$) the claimant’s address is not in Northern Ireland;

($b$) the Secretary of State gives a person written notice of a decision; and

($c$) that notice includes a statement to the effect that there is a right of appeal to the First-tier Tribunal in relation to the decision only if the Secretary of State has considered an application for a reversal of the decision.
\end{enumerate}

(2) In a case to which this regulation applies, a person has a right of appeal under section 4 of the Act in relation to the decision only if the Secretary of State has considered whether to reverse the decision under section 3A of the Act.

(3) The notice referred to in paragraph (1) must inform the person that, where the notice does not include a statement of the reasons for the decision, he may, within one month of the date of the notice, request that the Secretary of State provide him with written reasons.

(4) Where written reasons are requested under paragraph (3), the Secretary of State must provide them within 14 days of receipt of the request or as soon as practicable afterwards.

(5) Where, as the result of paragraph (2), there is no right of appeal against a decision, the Secretary of State may treat any purported appeal as an application for a reversal of the decision under section 3A of the Act.”.
\end{quotation}

\subsection[3. Amendment of the Child Support (Maintenance Assessment Procedure) Regulations 1992]{Amendment of the Child Support (Maintenance Assessment Procedure) Regulations 1992}

3.---(1)  The Child Support (Maintenance Assessment Procedure) Regulations 1992\footnote{S.I.~1992/1813.} are amended as follows.

(2) At the end of regulation 10 (notification of a new or a fresh maintenance assessment)\footnote{Regulation 10 was revoked (with savings) by S.I.~2001/157, S.I.~2003/328 and by S.I.~2012/2785.}, insert—
\begin{quotation}
“(5) Paragraphs (2) to (4) of this regulation apply in the case of a decision in respect of which there is no right of appeal as the result of regulation 17A (consideration of revision before appeal) as they apply in the case of a decision which may be appealed under section 20 of the Act (as it has effect apart from section 10 of the Child Support, Pensions and Social Security Act 2000).”.
\end{quotation}

(3) After regulation 17 (revision of decision)\footnote{Regulation 17 was substituted by S.I.~1999/1047. It was revoked (with savings) by S.I.~2001/157 and 2003/328 and was amended by S.I.~2000/1596, 2004/2415 and by S.I.~2008/2543.}, insert—
\begin{quotation}
\subsection*{“Consideration of revision before appeal}

17A.---(1)  This regulation applies in a case where—
\begin{enumerate}\item[]
($a$) the Secretary of State gives a person written notice of a decision; and

($b$) that notice includes a statement to the effect that there is a right of appeal to the First-tier Tribunal against the decision only if the Secretary of State has considered an application for a revision of the decision.
\end{enumerate}

(2) In a case to which this regulation applies, a person has a right of appeal under section 20 of the Act against the decision only if the Secretary of State has considered on an application whether to revise the decision under section 16 of the Act.

(3) The notice referred to in paragraph (1) must inform the person of the time limit specified in regulation 17(1) for making an application for a revision.

(4) Where, as the result of paragraph (2), there is no right of appeal against a decision, the Secretary of State may treat any purported appeal as an application for a revision under section 16 of the Act.

(5) In this regulation, “decision” means a decision mentioned in section 20 of the Act (as it has effect apart from section 10 of the Child Support, Pensions and Social Security Act 2000).”.
\end{quotation}

(4) Subject to regulation 8(1) (transitional and savings provisions) of these Regulations, in regulation 17(1)($f$)\footnote{Sub-paragraph ($f$)  of regulation 17(1) was inserted by S.I.~2004/2415.}, for “in regulation 31 of the Social Security and Child Support (Decisions and Appeals) Regulations 1999, or in a case to which regulation 32 of those Regulations applies within the time prescribed in that regulation” substitute “by the Tribunal Procedure Rules”.

(5) In regulation 18 (late application for a revision)\footnote{Regulation 18 was substituted by S.I.~1999/1407, was revoked (with savings) by S.I.~2001/157 and was amended by S.I.~2008/2683.}—
\begin{enumerate}\item[]
($a$) at the end of paragraph (4)($b$), insert “except in a case to which regulation 17A applies”;

($b$) in paragraph (6), after “extension of time”, insert “except in a case to which regulation 17A applies,”.
\end{enumerate}

\subsection[4. Amendment of the Social Security and Child Support (Decisions and Appeals) Regulations 1999]{Amendment of the Social Security and Child Support (Decisions and Appeals) Regulations 1999}

4.---(1)  The Social Security and Child Support (Decisions and Appeals) Regulations 1999\footnote{S.I.~1999/991.} are amended as follows.

(2) In regulation 3(1)($b$)  (revision of decisions)\footnote{Relevant instruments are S.I.~1999/2570 and S.I.~2002/1379. Regulation 3 was revoked, in so far as it relates to child benefit and guardian’s allowance, by S.I.~2003/916.} before “paragraph (1)($b$)” in both places it occurs, insert “paragraph (3)($b$)  of regulation 3ZA or”.

(3) After regulation 3 (revision), insert—
\begin{quotation}
\subsection*{“Consideration of revision before appeal}

3ZA.---(1)  This regulation applies in a case where—
\begin{enumerate}\item[]
($a$) the Secretary of State gives a person written notice of a decision under section 8 or 10 of the Act (whether as originally made or as revised under section 9 of that Act); and

($b$) that notice includes a statement to the effect that there is a right of appeal in relation to the decision only if the Secretary of State has considered an application for a revision of the decision.
\end{enumerate}

(2) In a case to which this regulation applies, a person has a right of appeal under section 12(2) of the Act in relation to the decision only if the Secretary of State has considered on an application whether to revise the decision under section 9 of the Act.

(3) The notice referred to in paragraph (1) must inform the person—
\begin{enumerate}\item[]
($a$) of the time limit specified in regulation 3(1) or (3) for making an application for a revision; and

($b$) that, where the notice does not include a statement of the reasons for the decision (“written reasons”), he may, within one month of the date of notification of the decision, request that the Secretary of State provide him with written reasons.
\end{enumerate}

(4) Where written reasons are requested under paragraph (3)($b$), the Secretary of State must provide them within 14 days of receipt of the request or as soon as practicable afterwards.

(5) Where, as the result of paragraph (2), there is no right of appeal against a decision, the Secretary of State may treat any purported appeal as an application for a revision under section 9 of the Act.”.
\end{quotation}

(4) After regulation 3A (revision of chlild support decisions)\footnote{Regulation 3A was inserted by S.I.~2000/3185 and was revoked, in so far as it relates to child benefit and guardian’s allowance, by S.I.~2003/916.}, insert—
\begin{quotation}
\subsection*{“Consideration of revision before appeal in relation to certain child support decisions}

3B.---(1)  This regulation applies in a case where—
\begin{enumerate}\item[]
($a$) the Secretary of State gives a person written notice of a decision; and

($b$) that notice includes a statement to the effect that there is a right of appeal against the decision only if the Secretary of State has considered an application for a revision of the decision.
\end{enumerate}

(2) In a case to which this regulation applies, a person has a right of appeal under section 20 of the Child Support Act 1991 (as substituted by section 10 of the Child Support, Pensions and Social Security Act 2000) against the decision only if the Secretary of State has considered on an application whether to revise the decision under section 16 of that Act.

(3) The notice referred to in paragraph (1) must inform the person of the time limit specified in regulation 3A(1)($a$)  for making an application for a revision.

(4) Where, as the result of paragraph (2), there is no right of appeal against a decision, the Secretary of State may treat any purported appeal as an application for a revision under section 16 of that Act.

(5) In this regulation “decision” means a decision mentioned in section 20(1)($a$)  or ($b$)  of the Child Support Act 1991 (as substituted by section 10 of the Child Support, Pensions and Social Security Act 2000).”.
\end{quotation}

(5) In regulation 4 (late application for a revision)\footnote{Regulation 4(3) was amended by S.I.~2005/337. Regulation 4(4) was amended by S.I.~1999/2570. Regulation 4(6) was amended by S.I.~2008/2683.}—
\begin{enumerate}\item[]
($a$) in paragraph (3)($b$), after “in accordance with” insert “regulation~3ZA(3)($b$)  or”;

($b$) at the end of paragraph (4)($b$)  insert “, except in a case to which regulation 3ZA or 3B applies.”;

($c$) in paragraph (6), after “extension of time” insert “, except in a case to which regulation 3ZA or 3B applies,”.
\end{enumerate}

(6) After regulation 9ZA (review of certificates)\footnote{Regulation 9ZA was inserted by S.I.~2008/1596 and was amended by S.I.~2008/2365 and S.I.~2008/2683.}, insert—
\begin{quotation}
\subsection*{“Consideration of review before appeal}

9ZB.---(1)  This regulation applies in a case where—
\begin{enumerate}\item[]
($a$) the Secretary of State has issued a certificate of recoverable benefits or certificate of recoverable lump sum payments; and

($b$) that certificate is accompanied by a notice to the effect that there is a right of appeal in relation to the certificate only if the Secretary of State has considered an application for review of the certificate.
\end{enumerate}

(2) In a case to which this regulation applies, a person has a right of appeal under section 11 of the 1997 Act against the certificate only if the Secretary of State has considered an application for review of the certificate under section 10 of that Act.”.
\end{quotation}

(7) In regulation 25 (other persons with a right of appeal)\footnote{Regulation 25 was amended by S.I.~1999/2570, 2002/1379, 2004/3368 and by S.I.~2008/2683 and was revoked, in so far as it relates to child benefit and guardian’s allowance, by S.I.~2003/916.}, after “section~12(2)” insert “, but subject to regulation 3ZA,”.

(8) In regulation 26 (decisions against which an appeal lies)\footnote{Regulation 26 was amended by S.I.~1999/2570, 2000/1596, 2001/518, 2008/2683 and by S.I 2009/2715. Regulation 26 was revoked, in so far as it relates to child benefit and guardian’s allowance, by S.I.~2003/916.}, at the beginning insert “Subject to regulation 3ZA,”.

(9) For regulation 29(6) (further particulars required relating to certificate of recoverable benefits or, as the case may be, recoverable lump sum payments appeals)\footnote{Regulation 29(6) was amended by S.I.~2008/1596 was revoked, in so far as it relates to child benefit and guardian’s allowance, by S.I.~2003/916.}, substitute—
\begin{quotation}
“(6) The Secretary of State may treat any—
\begin{enumerate}\item[]
\begin{sloppypar}
($a$) purported appeal (where, as the result of regulation~9ZB(2) (consideration of review before appeal), there is no right of appeal);
\end{sloppypar}

($b$) appeal relating to the certificate of recoverable benefits; or

($c$) appeal relating to the certificate of recoverable lump sum payments,
\end{enumerate}
as an application for review under section 10 of the 1997 Act.”
\end{quotation}

(10) Subject to regulation 8 (transitional and savings provisions) of these Regulations, omit the following—
\begin{enumerate}\item[]
($a$) “and 33” in regulation 9ZA(2) (review of certificates);

($b$) regulation 29(3) to (5) (further particulars required relating to certificate of recoverable benefits or, as the case may be, recoverable lump sum payments appeals);

($c$) regulation 32 (late appeals);

($d$) regulation 33 (notice of appeal); and

($e$) regulation 34 (death of a party to an appeal).
\end{enumerate}

\subsection[5. Amendment of the Mesothelioma Lump Sum Payments (Claims and Reconsiderations) Regulations 2008]{Amendment of the Mesothelioma Lump Sum Payments (Claims and Reconsiderations) Regulations 2008}

5.---(1)  The Mesothelioma Lump Sum Payments (Claims and Reconsiderations) Regulations 2008\footnote{S.I.~2008/1595.} are amended as follows.

(2) At the end of regulation 4(1)($a$)  (reconsideration), omit “and”.

(3) After that sub-paragraph, insert—
\begin{quotation}
“($aa$) where a written statement is requested under regulation~4B(3) (reconsideration before appeal) and is provided within the period specified in sub-paragraph ($a$)  above, be made within 14 days of the expiry of that period,

($ab$) where a written statement is requested under regulation~4B(3) (reconsideration before appeal) and is provided after the period specified in sub-paragraph ($a$)  above, be made within 14 days of the date on which the statement is provided, or

($ac$) be made within such longer period as may be allowed under regulation 4A (late application for reconsideration), and”.
\end{quotation}

(4) After regulation 4 (reconsideration), insert—
\begin{quotation}
\subsection*{“Late application for reconsideration}

4A.  Where, in a case to which regulation 4B (reconsideration before appeal) applies, the Secretary of State considers there was good cause for not applying for reconsideration of a determination within the time limit specified in regulation 4(1) (reconsideration), he may extend the time limit for such period as he considers appropriate in the circumstances.

\subsection*{Reconsideration before appeal}

4B.---(1)  This regulation applies in a case where—
\begin{enumerate}\item[]
($a$) the Secretary of State gives a person written notice of a determination made on a claim; and

($b$) that notice includes a statement to the effect that there is a right of appeal to the First-tier Tribunal in relation to the determination only if the Secretary of State has, on an application, decided whether to reconsider the determination.
\end{enumerate}

(2) In a case to which this regulation applies, a person may appeal against the determination only if the Secretary of State has decided on an application whether to reconsider the determination under section 49 of the Child Maintenance and Other Payments Act 2008 (“the 2008 Act”).

(3) The notice referred to in paragraph (1) must inform the person—
\begin{enumerate}\item[]
($a$) of the time limit specified in regulation 4(1) for making an application for reconsideration of the determination; and\looseness=1

($b$) that, where the notice does not include a statement of the reasons for the determination (“written reasons”), he may, within one month of the date of notification of the determination, request that the Secretary of State provide him with written reasons.
\end{enumerate}

(4) Where written reasons are requested under paragraph (3)($b$), the Secretary of State must provide them within 14 days of receipt of the request or as soon as practicable afterwards.

(5) Where, as the result of paragraph (2), there is no right of appeal against a determination made on a claim, the Secretary of State may treat any purported appeal as an application for reconsideration of the determination under section 49 of the 2008 Act.”.\end{quotation}

(5) Subject to regulation 8(1) (transitional and savings provisions) of these Regulations, omit regulation 5(2) and (3) (appeal treated as a reconsideration) and regulation 6 (appeals).

\subsection[6. Amendment of the Child Support Maintenance Calculation Regulations 2012]{Amendment of the Child Support Maintenance Calculation Regulations 2012}

6.---(1)  The Child Support Maintenance Calculation Regulations 2012\footnote{S.I.~2012/2677.} are amended as follows.

(2) After regulation 14 (grounds for revision), insert—
\begin{quotation}
\subsection*{“Consideration of revision before appeal}

14A.---(1)  This regulation applies in a case where—
\begin{enumerate}\item[]
($a$) the Secretary of State gives a person written notice of a decision; and

($b$) that notice includes a statement to the effect that there is a right of appeal to the First-tier Tribunal against the decision only if the Secretary of State has considered an application for a revision of the decision.
\end{enumerate}

(2) In a case to which this regulation applies, a person has a right of appeal against the decision only if the Secretary of State has considered on an application whether to revise the decision under section 16 of the 1991 Act.

(3) The notice referred to in paragraph (1) must inform the person of the time limit specified in regulation 14(1) for making an application for a revision.

(4) Where, as the result of paragraph (2), there is no right of appeal against a decision, the Secretary of State may treat any purported appeal as an application for a revision under section 16 of that Act.

(5) In this regulation, “decision” means a decision mentioned in section 20(1)($a$)  or ($b$)  of the 1991 Act (as substituted by section~10 of the Child Support, Pensions and Social Security Act 2000).”.
\end{quotation}

(3) In regulation 15 (late application for a revision)—
\begin{enumerate}\item[]
($a$) at the end of paragraph (4)($b$)  insert “, except in a case to which regulation 14A applies”;

($b$) in paragraph (6), after “extension of time” insert “, except in a case to which regulation 14A applies,”.
\end{enumerate}

(4) Subject to regulation 8(1) (transitional and savings provisions) of these Regulations, in the Schedule, omit paragraph 2 (late appeals), 3 (notice of appeal) and 4 (death of a party to an appeal).

\subsection[7. Other consequential amendments relating to appeals]{Other consequential amendments relating to appeals}

7.---(1)  Subject to regulation 8(1) (transitional and savings provisions), the Regulations mentioned below are amended as follows.

(2) In regulation 147A(5A) (claimants appealing a decision) of the Employment and Support Allowance Regulations 2008\footnote{S.I.~2008/794. Regulation 147A was inserted by S.I.~2010/840. Paragraph (5A) was inserted by S.I.~2011/2425.} omit—
\begin{enumerate}\item[]
($a$) “either”; and

($b$) sub-paragraph ($b$)  and the word “or” immediately preceding it.
\end{enumerate}

(3) Omit regulation 13(2)($c$)  (disclosure of information to other persons) of the Child Support Information Regulations 2008\footnote{S.I.~2008/2551.}.

(4) Omit regulation 12(2) (appeals and other proceedings) of the Child Support (Management of Payments and Arrears) Regulations 2009\footnote{S.I.~2009/3151.}.

\subsection[8. Transitional and savings provisions]{Transitional and savings provisions}

8.---(1)  The amendments made by regulations 3(4), 4(10), 5(5), 6(4) and 7 do not apply in any case where the notice of the decision to which the appeal relates was posted to the appellant’s last known address before 28th October 2013.\looseness=-1

(2) Notwithstanding regulation 4(10)($e$)  of these Regulations, regulation~34 (death of a party to an appeal) of the Social Security and Child Support (Decisions and Appeals) Regulations 1999 continues to have effect for the purposes of regulation 8 (general provision relating to the procedure for appeals) of the Personal Injuries (NHS Charges) (Reviews and Appeals) (Scotland) Regulations 2006\footnote{S.I.~2006/593.}.%\looseness=-1

(3) In paragraph (1), “decision” includes—
\begin{enumerate}\item[]
($a$) a determination given under the Child Maintenance and Other Payments Act 2008\footnote{2008 c.~6.}; and

($b$) a certificate of recoverable benefits or recoverable lump sum payments given under
 the Social Security (Recovery of Benefits) Act 1997\footnote{1997 c.~27.}.
\end{enumerate}

\bigskip

\pagebreak[3]

Signed 
by authority of the 
Secretary of State for~Work and~Pensions.
%I concur
%By authority of the Lord Chancellor

{\raggedleft
\emph{Esther McVey}\\*
%Secretary
%Minister
Parliamentary Under Secretary 
of State\\*Department 
for~Work and~Pensions

}

10th September 2013

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations amend the Social Security and Child Support (Decisions and Appeals) Regulations 1999 (S.I.1999/991) (“the Decisions and Appeals Regulations”) to enable the Secretary of State to require a person to apply for a social security decision to be revised pursuant to section 9 of the Social Security Act 1998 before the person is permitted to appeal to the First-tier Tribunal (see new regulation 3ZA of the Decisions and Appeals Regulations, as inserted by regulation 4(3) of these Regulations).

The restriction applies where the Secretary of State gives a person written notice to that effect. In such cases, a person has a right of appeal only if the Secretary of State has considered on an application whether to revise the decision.

New regulation 3ZA(5) also makes provision for the Secretary of State to treat a purported appeal as an application for a revision.

These Regulations also make similar changes to regulations relating to certain other appeals. These are appeals relating to:
\begin{itemize}\item
    vaccine damage payments (regulation 2);
\item
    certain child support decisions (regulations 3 and 6);
\item
    certificates of recoverable benefits and certificates of recoverable lump sum payments (regulation 4(6));
\item
    payments in respect of mesothelioma (regulation 5). 
\end{itemize}

These Regulations also make related amendments to enable a person who must apply for a decision to be revised before they are permitted to appeal to request a written statement of reasons for the decision, specifying the time within which that statement is to be provided and for extending the time in which a person is able to make an application for a decision to be revised (see, for example, new regulation 3ZA(3) and (4) of the Decisions and Appeals Regulations).

Regulation 2(2) amends the Vaccine Damage Payments Regulations 1979 (S.I.~1979/432) to enable an application for a decision to be reversed to be made at any time instead of within 6 years of the date of notification of the decision in all cases.

Regulation 5 also amends the Mesothelioma Lump Sum Payments (Claims and Reconsiderations) Regulations 2008 (S.I.~2008/1595) (“the Mesothelioma Regulations”) by inserting new regulation 4A which enables the Secretary of State to extend the time by which a person must apply for reconsideration of a determination.

These Regulations also revoke provisions in the Decisions and Appeals Regulations which require a notice of appeal to be sent or delivered to the decision maker and for connected purposes (regulation 4(10)). The procedure for appeals in such cases will instead be set out in the Tribunal Procedure (First-tier Tribunal) (Social Entitlement Chamber) Rules 2008 (S.I.~2008/2835). There are similar revocations in regulation 5(5) in relation to the Mesothelioma Regulations and in regulation 6(4) in the case of the Child Support Maintenance Calculation Regulations 2012 (S.I.~2012/2677).

Regulation 7 contains consequential amendments to other regulations relevant to appeals.

Regulation 8 contains a saving in relation to appeals where the notification of the decision to which the appeal relates is sent before the date on which these Regulations come into force in that person’s case.

It also ensures that regulation 34 (death of a party to an appeal) of the Decisions and Appeals Regulations continues in effect in so far as it is applies to appeals concerning the recovery of NHS charges in Scotland.

A full impact assessment has not been produced for this instrument as it has no impact on the private sector or civil society organisations. 

\end{document}