\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support (Transitional Provision) (Miscellaneous Amendments) Regulations 2003}

\newcommand\regsnumber{2003/347}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2003 No.\ 347}

\date{Made
22nd February 2003\\
Laid before Parliament
26th February 2003\\
Coming into force
3rd March 2003
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.57402pt}

\begin{document}

\maketitle

\noindent
The Secretary of State for Work and Pensions, in exercise of the powers conferred upon him by section 29(2) of the Child Support, Pensions and Social Security Act 2000\footnote{2000 c.\ 19.}, and of all other powers enabling him in that behalf, hereby makes the following Regulations: 

\enlargethispage{\baselineskip}

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and commencement]{Citation and commencement}

1.  These Regulations may be cited as the Child Support (Transitional Provision) (Miscellaneous Amendments) Regulations 2003 and shall come into force on 3rd March 2003.

\subsection[2. Amendment of revocation, saving and transitional provisions]{Amendment of revocation, saving and transitional provisions}

2.---(1)  In each of the provisions specified in paragraph (2), after “Subject to” there shall be inserted “the Child Support (Transitional Provisions) Regulations 2000 and”\footnote{S.I.\ 2000/3186. Relevant amending instruments are S.I.\ 2002/1204 and 2003/328.}.

(2) The provisions referred to in paragraph (1) are—
\begin{enumerate}\item[]
($a$) regulation 14(1) of the Child Support (Decisions and Appeals) (Amendment) Regulations 2000 (revocation and savings)\footnote{S.I.\ 2000/3185.};

($b$) regulation 30(1) of the Child Support (Maintenance Calculation Procedure) Regulations 2000 (revocation and savings)\footnote{S.I.\ 2001/157.}; and

($c$) regulation 15(1) of the Child Support (Maintenance Calculations and Special Cases) Regulations 2000 (revocation and savings)\footnote{S.I.\ 2001/155.}.
\end{enumerate}

(3) At the beginning of each of the provisions specified in paragraph (4), the following paragraph shall be inserted—
\begin{quotation}
“(Z1) This regulation is subject to the Child Support (Transitional Provisions) Regulations 2000.”.
\end{quotation}

(4) The provisions referred to in paragraph (3) are—
\begin{enumerate}\item[]
($a$) regulation 6 of the Child Support (Collection and Enforcement and Miscellaneous Amendments) Regulations 2000 (savings)\footnote{S.I.\ 2001/162.};

($b$) regulation 10 of the Child Support (Consequential Amendments and Transitional Provisions) Regulations 2001 (savings for particular cases)\footnote{S.I.\ 2001/158.};

($c$) regulation 15 of the Child Support (Decisions and Appeals) (Amendment) Regulations 2000 (revocation and savings); and

($d$) regulation 10 of the Child Support (Information, Evidence and Disclosure and Maintenance Arrangements and Jurisdiction) (Amendment) Regulations 2000 (transitional provisions and savings)\footnote{S.I.\ 2001/161.}.
\end{enumerate}

(5) In regulation 33(1) of the Child Support (Variations) Regulations 2000 (revocation and savings)\footnote{S.I.\ 2001/156.}, after “Subject to” there shall be inserted “the Transitional Regulations and”.

\subsection[3. Amendment of the Child Support (Transitional Provisions) Regulations 2000]{Amendment of the Child Support (Transitional Provisions) Regulations 2000}

3.  In regulation 16 of the Child Support (Transitional Provisions) Regulations 2000 (conversion calculation and conversion decision)\footnote{Relevant amending instrument is S.I.\ 2003/328.}, after paragraph (2A) there shall be inserted—
\begin{quotation}
“(2B) For the purposes of regulation 2 of the Social Security Benefits (Maintenance Payments and Consequential Amendments) Regulations 1996 (interpretation for the purposes of section 74A of the Social Security Administration Act 1992\footnote{1992 c.\ 5. Section 74A was inserted by section 25 of the Child Support Act 1995 (c.\ 34).})\footnote{S.I.\ 1996/940. Relevant amending instrument is S.I.\ 2001/158.}, a conversion decision shall be treated on or after the case conversion date as if it were a maintenance calculation.”.
\end{quotation}

\bigskip

Signed 
by authority of the Secretary of State for Work and Pensions.

{\raggedleft
\emph{P.~Hollis}\\*Parliamentary Under-Secretary of State,\\*Department of Work and Pensions

}

%St Andrew's House, Edinburgh

%Dated
22nd February 2003

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

Regulation 2 of these Regulations amends regulations which concern revocations and savings consequent upon the introduction of changes to the child support scheme under the Child Support Act 1991 (c.\ 48) made by Part I of the Child Support, Pensions and Social Security Act 2000 (c.\ 19). The amendments made by regulation 2 ensure that those revocations or savings are to have effect subject to the provisions of the Child Support (Transitional Provisions) Regulations 2000 (“the Transitional Regulations”).

Regulation 3 amends the Transitional Regulations to provide that for the purposes of the Social Security Benefits (Maintenance Payments and Consequential Amendments) Regulations 1996, which provide for the interpretation of the term “child maintenance” for the purposes of section 74A of the Social Security Administration Act 1992 (c.\ 5), a conversion decision made under the Transitional Regulations is to be treated, on or after the case conversion date, as if it were a maintenance calculation.

These Regulations do not impose any cost on business. 

\end{document}