\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Public Bodies (Child Maintenance and Enforcement Commission: Abolition and Transfer of Functions) Order 2012}

\newcommand\regsnumber{2012/2007}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and~Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2012 No.\ 2007}

\date{Made
31st July 2012\\
%Laid before Parliament
%14th May 2012\\
Coming into~force
in accordance with article 1
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{42.11603pt}

%\hbadness=10000

\begin{document}

\maketitle

\noindent
The Secretary of State for Work and Pensions makes the following Order in exercise of the powers conferred by sections 1(1) and (2), 6(1) and (5), 23(1)($a$)  and 35(2) of the Public Bodies Act 2011\footnote{2011 c.~24.} (“the Act”).

In accordance with section 8 of that Act, the Secretary of State considers that this Order—
\begin{enumerate}\item[]
($a$) serves the purpose of improving the exercise of public functions, having had regard to the factors set out in section 8(1) of the Act; and

($b$) does not remove any necessary protection or prevent any person from continuing to exercise any right or freedom which that person might reasonably expect to continue to exercise.
\end{enumerate}

The Secretary of State has consulted in accordance with section~10 of the Act.

A draft of this Order and an explanatory document containing the information required in section~11(2) of the Act have been laid before Parliament in accordance with section~11(1) after the end of the period of twelve weeks mentioned in section~11(3). In accordance with section~11(4) of the Act, the draft of this Order has been approved by a resolution of each House of Parliament after the expiry of the 40-day period referred to in that provision. 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation, commencement and interpretation]{Citation, commencement and interpretation}

1.---(1)  This Order may be cited as the Public Bodies (Child Maintenance and Enforcement Commission: Abolition and Transfer of Functions) Order 2012.

(2) Subject to paragraph (3), this Order comes into force on the day after the day on which it is made.

(3) Paragraph 109($f$)  of the Schedule comes into force on the day after that on which the other provisions of this Order come into force.

(4) In this Order—
\begin{enumerate}\item[]
“the 1991 Act” means the Child Support Act 1991\footnote{1991 c.~48.};

“the 2008 Act” means the Child Maintenance and Other Payments Act 2008\footnote{2008 c.~6.};

“the Commission” means the Child Maintenance and Enforcement Commission established by section~1 of the 2008 Act;

“the commencement date” means the date on which this Order (other than paragraph 109($f$)  of the Schedule) comes into force.
\end{enumerate}

\subsection[2. Abolition of the Commission]{Abolition of the Commission}

2.  The Commission is abolished.

\subsection[3. Transfer of functions of the Commission to the Secretary of State]{Transfer of functions of the Commission to the Secretary of State}

3.---(1)  The functions of the Commission that were transferred to it by section~13 of the 2008 Act (transfer of child support functions) are transferred back to the Secretary of State.

(2) The Schedule, making consequential, incidental and supplementary amendments, has effect.

(3) All property, rights and liabilities to which the Commission was entitled or subject immediately before the commencement date are transferred to and vested in the Secretary of State.

\subsection[4. Accounts and audit]{Accounts and audit}

4.---(1)  It is the duty of the Secretary of State to take such action as may be necessary for the winding up of the affairs of the Commission, including the preparation of a statement of accounts for the period beginning on 1st April 2012 and ending on the commencement date.

(2) The Secretary of State must send a copy of the statement of accounts referred to in paragraph (1) to the Comptroller and Auditor General before the end of the period of five months beginning with the commencement date.

(3) The Comptroller and Auditor General must—
\begin{enumerate}\item[]
($a$) examine, certify and report on the statement of accounts received under paragraph (2); and

($b$) send a copy of that report and certified statement to the Secretary of State.
\end{enumerate}

(4) The Secretary of State must lay before Parliament a copy of the report and statement sent under paragraph (3)($b$).

\subsection[5. Provision for the continuity of the exercise of functions]{Provision for the continuity of the exercise of functions}

5.---(1)  Anything which—
\begin{enumerate}\item[]
($a$) relates to any function transferred to the Secretary of State by virtue of article~3, and

($b$) immediately before the commencement date, is in the process of being done by or in relation to the Commission,
\end{enumerate}
may be continued by or in relation to the Secretary of State.

(2) Anything done (or having effect as if done) by or in relation to the Commission before the commencement date for the purpose of, or in connection with, any function transferred by virtue of article~3 shall, so far as is required for continuing its effect from that date, have effect as if done by or in relation to the Secretary of State.

(3) Any enactment, instrument or other document has effect, so far as necessary for the purposes of or in consequence of the transfer effected by article~3, as if any reference to the Commission were a reference to the Secretary of State.

(4) Nothing in article~3 shall affect the validity of anything done (or having effect as if done) by or in relation to the Commission before the commencement date.

(5) Where, on or after the commencement date, any document or notice relating to a function transferred to the Secretary of State by virtue of article~3 is given or sent to any person by the Secretary of State which contains a reference to the Commission, that document or notice is not to be invalidated by virtue of that reference. 

\bigskip

\pagebreak[3]

Signed 
by authority of the 
Secretary of State for~Work and~Pensions.
%I concur
%By authority of the Lord Chancellor

{\raggedleft
\emph{Maria Miller}\\*
%Secretary
%Minister
Parliamentary Under-Secretary 
of State\\*Department 
for~Work and~Pensions

}

31st July 2012

\small

\part[Schedule --- Consequential, supplementary and incidental amendments]{Schedule\\*Consequential, supplementary and incidental amendments}

\section[Part I --- Amendments to Acts]{Part I\\*Amendments to Acts}

\renewcommand\parthead{--- Schedule Part I}

\subsection*{\itshape The Child Support Act 1991}

1.  The 1991 Act is amended as follows.

\medskip

2.  In section 2 (welfare of children: the general principle)\footnote{Section 2 was amended by the Child Maintenance and Other Payments Act 2008 (c.~6) (“the 2008 Act”).}—
\begin{enumerate}\item[]
($a$) for “Commission” substitute “Secretary of State”;

($b$) for “it” substitute “the Secretary of State”; and

($c$) for “its” substitute “the”.
\end{enumerate}

\medskip

3.  In section 4 (child support maintenance)\footnote{Relevant amendments were made by the Social Security Act 1998 (c.~14) (“the 1998 Act”), the Child Support, Pensions and Social Security Act 2000 (c.~19) (“the 2000 Act”) and the 2008 Act.}—
\begin{enumerate}\item[]
($a$) in subsection (1), for “Commission” substitute “Secretary of State”;

($b$) in subsection (2), for “Commission” substitute “Secretary of State” and for “it” substitute “the Secretary of State”;

($c$) in subsection (3), for “Commission” (in both places) substitute “Secretary of State” and for “it” substitute “the Secretary of State”;

($d$) in subsection (4), for “Commission” (in both places) substitute “Secretary of State”;

($e$) in subsection (5), for “Commission” substitute “Secretary of State” and for “it” substitute “the Secretary of State”; and

($f$) in subsections (6) and (7)($b$), for “Commission” substitute “Secretary of State”.
\end{enumerate}

\medskip

4.  In section 7 (right of child in Scotland to apply for calculation)\footnote{Relevant amendments were made to sections 7 and 8 by the 1998 Act, the 2000 Act and the 2008 Act.}—
\begin{enumerate}\item[]
($a$) in subsections (1) and (2), for “Commission” substitute “Secretary of State”;

($b$) in subsection (3), for “Commission” substitute “Secretary of State” and for “it” substitute “the Secretary of State”;

($c$) in subsection (4), for “Commission” (in both places) substitute “Secretary of State” and for “it” substitute “the Secretary of State”;

($d$) in subsection (5), for “Commission” (in both places) substitute “Secretary of State”; and

($e$) in subsections (6), (7) and (8)($b$), for “Commission” substitute “Secretary of State”.
\end{enumerate}

\medskip

5.  In section 8 (role of the courts with respect to maintenance for children), in subsections (1) and (2), for “Commission” substitute “Secretary of State”.

\medskip

6.  In section~10 (relationship between maintenance calculations and certain court orders etc)\footnote{Relevant amendments were made by the 1998 Act, the 2000 Act and the 2008 Act.}—
\begin{enumerate}\item[]
($a$) in subsection (4)($a$), for “Commission” substitute “Secretary of State” and for “it” substitute “the Secretary of State”; and

($b$) in subsections (4)($b$)  and (5), for “Commission” substitute “Secretary of State”.
\end{enumerate}

\medskip

7.  In section~11 (as substituted by the Child Support, Pensions and Social Security Act 2000) (maintenance calculations)\footnote{Section 11 was substituted by section~1 of the 2000 Act and amended by the 2008 Act.}—
\begin{enumerate}\item[]
($a$) in subsections (1) and (2), for “Commission” substitute “Secretary of State” and for “it” substitute “the Secretary of State”; and

($b$) in subsection (7), for “Commission” substitute “Secretary of State” and for “it determines” substitute “determined”.
\end{enumerate}

\medskip

8.---(1)  Section 12 (as substituted by the Child Support, Pensions and Social Security Act 2000) (default and interim maintenance decisions)\footnote{Section 12 was substituted by section 4 of the 2000 Act and amended by the 2008 Act.} is amended as follows.

(2) In subsection (1)—
\begin{enumerate}\item[]
($a$) for “Commission” (in both places) substitute “Secretary of State”;

($b$) for the second “it” substitute “the Secretary of State”;

($c$) for “it to do so” substitute “such a decision to be made”; and

($d$) for the final “it” substitute “the Secretary of State”.
\end{enumerate}

(3) In subsection (2), for “Commission” substitute “Secretary of State”.

\medskip

9.  In section~14 (information required by Commission)\footnote{Relevant amendments were made by the 1998 Act and the 2008 Act.}, in the title and in subsections (3) and (4) for “Commission” (in each place) substitute “Secretary of State”.

\medskip

10.  In section~15 (powers of inspectors)\footnote{Relevant amendments were made by the 2000 Act and the 2008 Act.}—
\begin{enumerate}\item[]
($a$) in subsection (1), for “Commission” substitute “Secretary of State” and for “it” substitute “the Secretary of State”; and

($b$) in subsection (2), for “Commission” substitute “the Secretary of State”.
\end{enumerate}

\medskip

11.---(1)  Section 16 (revision of decisions)\footnote{Section 16 was substituted by section 40 of the 1998 Act and amended by the 2000 Act, the 2008 Act and S.I.~2008/2833.} is amended as follows.

(2) In subsection (1), for “Commission” (in both places) substitute “Secretary of State” and for “its” substitute “the Secretary of State’s”.

(3) In subsection (1A), for “Commission” substitute “Secretary of State”.

(4) In subsection (1B)—
\begin{enumerate}\item[]
($a$) for “Commission” substitute “Secretary of State”;

($b$) in paragraph ($a$), for the first “it” substitute “the Secretary of State” and omit “it were”; and

($c$) in paragraph ($b$), for the first “it” substitute “the Secretary of State” and for “its” substitute “the”.
\end{enumerate}

(5) In subsection (2)—
\begin{enumerate}\item[]
($a$) for “Commission” substitute “Secretary of State”;

($b$) for “it” substitute “the Secretary of State”; and

($c$) for “its” substitute “the Secretary of State’s”.
\end{enumerate}

(6) In subsection (6), for “Commission” substitute “Secretary of State”.

\medskip

12.---(1)  Section 17 (decisions superseding earlier decisions)\footnote{Section 17 was inserted by section 41 of the 1998 Act and amended by the 2000 Act, the 2008 Act and S.I.~2008/2833.} is amended as follows.

(2) In subsection (1), for “Commission” (in both places) substitute “Secretary of State” and for “its” substitute “the Secretary of State’s”.

(3) In subsection (2) (as it has effect before the coming into force of section~17 of the 2008 Act)—
\begin{enumerate}\item[]
($a$) for “Commission” substitute “Secretary of State”;

($b$) for “it” substitute “the Secretary of State”; and

($c$) for “its” substitute “the Secretary of State’s”.
\end{enumerate}

(4) In subsection (4A), for “Commission” substitute “Secretary of State” and for “its” substitute “the Secretary of State’s”.

\medskip

13.  In section 20 (appeals to First-tier Tribunals) (as substituted by the Child Support, Pensions and Social Security Act 2000)\footnote{Section 20 was substituted by section 2 of the 2000 Act and amended by the 2008 Act and S.I.~2008/2833.}, in subsections (1)($a$)  and~($b$),~(2)($a$)(i), (7)($b$)  and (8)($b$), for “Commission” substitute “Secretary of State”.

\medskip

14.  In section 23A (redetermination of appeals)\footnote{Section 23A was inserted by section~11 of the 2000 Act and amended by the 2008 Act and S.I.~2008/2833.}, omit subsection (4)($za$).

\medskip

15.  In section 24 (appeals to Upper Tribunal)\footnote{Section 24 was amended by the 2008 Act and S.I.~2008/2833.}—
\begin{enumerate}\item[]
($a$) omit subsection (1)($a$); and

($b$) in subsection (2), omit “the Commission or” (in both places).
\end{enumerate}

\medskip

16.  In section 26 (disputes about parentage)\footnote{Section 26 was amended by the 1998 Act, the 2000 Act, the Adoption and Children Act 2002 (c.~38), the 2008 Act, the Human Fertilisation and Embryology Act 2008 (c.~22), the Welfare Reform Act 2009 (c.~24) and S.I.~1995/756.}, in subsection (1) and in Cases A1 and E in subsection (2), for “Commission” substitute “Secretary of State”.

\medskip

17.  In section 27 (applications for declaration of parentage under Family Law Act 1986)\footnote{Section 27 was substituted by section 85(3) of, and Schedule 8 to, the 2000 Act and amended by the 2008 Act.}, in subsections (1)($b$)  and ($c$)  and (2)($b$), for “Commission” substitute “Secretary of State”.

\medskip

18.  In section 27A (recovery of fees for scientific tests)\footnote{Section 27A was inserted by section 21 of the Child Support Act 1995 (c.~34) (“the 1995 Act”) and amended by the 2000 Act and 2008 Act.}—
\begin{enumerate}\item[]
($a$) in subsection (2)($c$), for “Commission” substitute “Secretary of State”; and

($b$) in subsections (3) and (5), for “Commission” substitute “Secretary of State” and for “it” substitute “the Secretary of State”.
\end{enumerate}

\medskip

19.  In section 28 (power to initiate or defend actions of declarator)\footnote{Section 28 was amended by the 1995 Act, the Social Security Act 1998 (c.~14) (“the 1998 Act”), the Child Support, Pensions and Social Security Act 2000 (c.~19) (“the 2000 Act”) and the Child Maintenance and Other Payments Act 2008 (c.~6) (“the 2008 Act”).}, in the title and in subsections (1)($b$), (1A) and (2), for “Commission” substitute “Secretary of State”.

\medskip

20.  In section 28ZA (decisions involving issues that arise on appeal in other cases)\footnote{Sections 28ZA to 28ZD were inserted by sections 43 and 44 of the 1998 Act and amended by the 2000 Act, the 2008 Act and S.I.~2008/2833.}—
\begin{enumerate}\item[]
($a$) in subsection (1)($a$), for “Commission” substitute “Secretary of State”;

($b$) in subsection (2), for “Commission” substitute “Secretary of State” and, in paragraphs ($a$)  and ($b$), for “it” substitute “the Secretary of State”; and

($c$) in subsection (3), for “Commission” substitute “Secretary of State”, for “it” substitute “the Secretary of State” and for “its” substitute “the”.
\end{enumerate}

\medskip

21.  In section 28ZB (appeals involving issues that arise on appeal in other cases)—
\begin{enumerate}\item[]
($a$) in subsection (2), for “Commission” (in each place) substitute “Secretary of State”;

($b$) in subsection (3), for “Commission” (in both places) substitute “Secretary of State” and for “its” substitute “the”; and

($c$) in subsection (5), for “Commission” substitute “Secretary of State”.
\end{enumerate}

\medskip

22.  In section 28ZC (restrictions on liability in certain cases of error), in subsections (1)($b$), (2) and (6), for “Commission” substitute “Secretary of State”.

\medskip

23.  In section 28A (as substituted by the Child Support, Pensions and Social Security Act 2000) (application for variation of usual rules for calculating maintenance)\footnote{Sections 28A to 28C were substituted by section 5 of the 2000 Act and amended by the 2008 Act.}, in subsections (1), (3) and (4)($a$), for “Commission” substitute “Secretary of State”.

\medskip

24.---(1)  Section 28B (as substituted by the Child Support, Pensions and Social Security Act 2000) (preliminary consideration of applications) is amended as follows.

(2) In subsection (1), for “Commission” substitute “Secretary of State” and for the first “it” substitute “the Secretary of State”.

(3) In subsection (2)—
\begin{enumerate}\item[]
($a$) for the words from “Where” to “completing the” substitute “The Secretary of State may on completing such a”;

($b$) for “its” substitute “a”;

($c$) for the second “Commission” substitute “Secretary of State”;

($d$) in paragraph ($a$), for “it could agree to a variation” substitute “a variation could be agreed to”; and

($e$) in paragraph ($b$), for “it” substitute “the Secretary of State” and for “its” substitute “the Secretary of State’s”.
\end{enumerate}

\medskip

25.  In section 28C (as substituted by the Child Support, Pensions and Social Security Act 2000) (imposition of regular payments condition)—
\begin{enumerate}\item[]
($a$) in subsection (1), for “Commission” (in both places) substitute “Secretary of State”, for the first “it” substitute “the Secretary of State” and for “its” substitute “a”;

($b$) in subsection (3), for “Commission” substitute “Secretary of State” and for the first “it” substitute “the Secretary of State”;

($c$) in subsection (4), for “Commission” substitute “Secretary of State” and for “it” substitute “the Secretary of State”;

($d$) in subsection (5), for “Commission” substitute “Secretary of State” and for “its” substitute “a”;

($e$) in subsection (6), for “Commission” substitute “Secretary of State”; and

($f$) in subsection (7), for “Commission” substitute “Secretary of State”, for “it” substitute “the Secretary of State” and for “its” substitute “the”.
\end{enumerate}

\medskip

26.  In section 28D (determination of applications)\footnote{Sections 28D and 28E were inserted by sections 4 and 5 of the 1995 Act and amended by the 2000 Act, the 2008 Act and S.I.~2008/2833.}—
\begin{enumerate}\item[]
($a$) in subsection (1) (as substituted by the Child Support, Pensions and Social Security Act 2000), for “Commission” substitute “Secretary of State”;

($b$) in subsection (2), for “Commission” (in both places) substitute “Secretary of State”; and

($c$) in subsection (3), for “Commission if it were” substitute “Secretary of State in”.
\end{enumerate}

\medskip

27.  In section 28E (matters to be taken into account)—
\begin{enumerate}\item[]
($a$) in subsection (1), for “Commission” substitute “Secretary of State”;

($b$) in subsection (3), for “Commission” substitute “Secretary of State” and for “it” substitute “the Secretary of State”; and

($c$) in subsection (4)($a$), for “Commission” substitute “Secretary of State”.
\end{enumerate}

\medskip

28.---(1)  Section 28F (as substituted by the Child Support, Pensions and Social Security Act 2000) (agreement to a variation)\footnote{Section 28F was substituted by section 5 of the 2000 Act and amended by the 2008 Act.} is amended as follows.

(2) In subsection (1)—
\begin{enumerate}\item[]
($a$) for “Commission” substitute “Secretary of State”;

($b$) in paragraph ($a$), for “it” substitute “the Secretary of State”; and

($c$) in paragraph ($b$), for “its” substitute “the Secretary of State’s”.
\end{enumerate}

(3) In subsection (2)—
\begin{enumerate}\item[]
($a$) for “Commission” substitute “Secretary of State”; and

($b$) in paragraph ($a$), for “it” substitute “the Secretary of State”.
\end{enumerate}

(4) In subsection (3)—
\begin{enumerate}\item[]
($a$) for “Commission” substitute “Secretary of State”;

($b$) for the first “its” substitute “a”;

($c$) omit “it is”; and

($d$) in paragraph ($a$), for “it” substitute “the Secretary of State” and for “its” substitute “the”.
\end{enumerate}

(5) In subsection (4), for “Commission” substitute “Secretary of State” and for “it” substitute “the Secretary of State”.

(6) In subsection (5), for “Commission” substitute “Secretary of State” and for “its” substitute “the Secretary of State’s”.

(7) In subsection (6), for “Commission” substitute “Secretary of State”.

\medskip

29.  In section 28J (voluntary payments)\footnote{Section 28J was inserted by section 20(1) of the 2000 Act and amended by the 2008 Act.}—
\begin{enumerate}\item[]
($a$) in subsection (1)($b$), for “Commission” substitute “Secretary of State”;

($b$) in subsection (2), for “Commission” (in both places) substitute “Secretary of State” and for “it” substitute “the Secretary of State”; and

($c$) in subsection (4), for “Commission” substitute “Secretary of State” and for “it” in the first two places substitute “the Secretary of State”.
\end{enumerate}

\medskip

30.  In section 29 (collection of child support maintenance)\footnote{Sections 29 to 32 were amended by the 2000 Act and the 2008 Act.}—
\begin{enumerate}\item[]
($a$) in subsection (1), for “Commission” (in both places) substitute “Secretary of State” and for “it” substitute “the Secretary of State”; and

($b$) in subsection (3), for “Commission” (in each place) substitute “Secretary of State”.
\end{enumerate}

\medskip

31.  In section 30 (collection and enforcement of other forms of maintenance)—
\begin{enumerate}\item[]
($a$) in subsections (1) and (2), for “Commission” substitute “Secretary of State” and for “it” substitute “the Secretary of State”;

($b$) in subsection (3), for “Commission” (in each place) substitute “Secretary of State” and for “it” substitute “the Secretary of State”;

($c$) in subsections (4) and (5), for the words from “enabling” to “arrangements” substitute “enabling the Secretary of State to enforce any obligation to pay any amount for the collection of which the Secretary of State is authorised under this section to make arrangements”; and

($d$) in subsection (5)($a$), for “Commission” substitute “Secretary of State”.
\end{enumerate}

\medskip

32.  In section 31 (deduction from earnings orders)—
\begin{enumerate}\item[]
($a$) in subsections (2) and (5)($b$), for “Commission” substitute “Secretary of State”; and

($b$) in subsection (6), for “Commission” (in both places) substitute “Secretary of State” and for “which it makes” substitute “made”.
\end{enumerate}

\medskip

33.  In section 32 (regulations about deduction from earnings orders), in subsections (2) and (3), for “Commission” (in each place) substitute “Secretary of State”.

\medskip

34.  In section 32A (orders for regular deductions from accounts)\footnote{Sections 32A to 32D were inserted by section 22 of the 2008 Act.}—
\begin{enumerate}\item[]
($a$) in subsection (1), for “Commission” substitute “Secretary of State” and for the second “it” substitute “the Secretary of State”; and

($b$) in subsections (3), (6)($b$)  and (7), for “Commission” substitute “Secretary of State”.
\end{enumerate}

\medskip

35.  In section 32B (orders under section 32A: joint accounts), for “Commission” (in each place) substitute “Secretary of State”.

\medskip

36.  In section 32C (regulations about orders under section 32A)—
\begin{enumerate}\item[]
($a$) in subsection (2), for “Commission” (in each place) substitute “Secretary of State” and, in paragraph ($k$), for “it” substitute “the Secretary of State”; and

($b$) in subsection (4), for “Commission” substitute “Secretary of State”.
\end{enumerate}

\medskip

\begin{sloppypar}
37.  In section 32E (lump sum deductions: interim orders)\footnote{Sections 32E to 32K were inserted by section 23 of the 2008 Act.}, in subsections~(1),~(4)($c$),~(5) and (6), for “Commission” (in each place) substitute “Secretary of State”.
\end{sloppypar}

\medskip

38.  In section 32F (lump sum deductions: final orders)—
\begin{enumerate}\item[]
($a$) in subsection (1), for “Commission” (in each place) substitute “Secretary of State” and for “it” substitute “the Secretary of State”; and

($b$) in subsections (4), (5) and (6), for “Commission” substitute “Secretary of State”.
\end{enumerate}

\medskip

39.  In section 32H (orders under section 32F: deductions and payments), in subsections (1) to (4), for “Commission” (in each place) substitute “Secretary of State”.

\medskip

40.  In section 32I (power to disapply sections 32G(1) and (2) and 32H(2)($b$)  and (4)($b$)), in subsections (2) to (4), for “Commission’s” substitute “Secretary of State’s”.

\medskip

41.  In section 32J (regulations about orders under section 32E or 32F), in subsection (2), for “Commission” (in each place) substitute “Secretary of State”.

\medskip

42.  In section 32L (orders preventing avoidance)\footnote{Section 32L was inserted by section 24 of the Child Maintenance and Other Payments Act 2008 (c.~6) (“the 2008 Act”).}, in subsections (1) and (2), for “Commission” substitute “Secretary of State”.

\medskip

43.  In section 33 (liability orders), in subsections (1)($b$), (2), (3) and (5), for “Commission” substitute “Secretary of State”.

\medskip

44.  In section 34 (regulations about liability orders), in subsections (1)($a$)  and~($c$)  and (2), for “Commission” substitute “Secretary of State”.

\medskip

45.  In section 35 (enforcement of liability orders by taking control of goods)—
\begin{enumerate}\item[]
($a$) in subsection (1), for “Commission” substitute “Secretary of State”; and

($b$) in subsection (3), for “Commission” substitute “Secretary of State” and for “its” substitute “the”.
\end{enumerate}

\medskip

46.  In section 37(2) (regulations about liability orders: Scotland), for “Commission” substitute “Secretary of State”.

\medskip

47.  In section 38 (enforcement of liability orders by diligence), in subsection~(1)($a$), for “Commission” substitute “Secretary of State”.

\medskip

48.  In section 39A (commitment to prison and disqualification from driving)\footnote{Sections 39A and 40B were inserted by section~16 of the Child Support, Pensions and Social Security Act 2000 (c.~19) (“the 2000 Act”) and amended by the 2008 Act.}—
\begin{enumerate}\item[]
($a$) in subsection (1), for “Commission” substitute “Secretary of State” and for the second “it” substitute “the Secretary of State”; and

($b$) in subsection (4), for “Commission” substitute “Secretary of State” and for the first “it” substitute “the Secretary of State”.
\end{enumerate}

\medskip

49.  In section 40B (disqualification from driving: further provision)—
\begin{enumerate}\item[]
($a$) in subsections (5), (6), (7) and (8), for “Commission” (in each place) substitute “Secretary of State”; and

($b$) in subsection (9), for “Commission” substitute “Secretary of State” and for the second “it” substitute “the Secretary of State”.
\end{enumerate}

\medskip

50.  In section 41 (arrears of child support maintenance)—
\begin{enumerate}\item[]
($a$) in subsection (1), for “Commission” substitute “Secretary of State”;

($b$) in subsection (2), for “Commission” substitute “Secretary of State” and for “it” (in both places) substitute “the Secretary of State”; and

($c$) in subsection (6), for “Commission” substitute “Secretary of State” and for “it” substitute “the Secretary of State”.
\end{enumerate}

\medskip

51.  In section 41A (as substituted by the Child Support, Pensions and Social Security Act 2000) (penalty payments)\footnote{Section 41A was substituted by section~18 of the 2000 Act and amended by the 2008 Act.\looseness=-1
}—
\begin{enumerate}\item[]
($a$) in subsections (1), (2) and (4)($b$), for “Commission” substitute “Secretary of State”; and

($b$) in subsection (6), for “Commission” substitute “Secretary of State” and for “it” substitute “the Secretary of State”.
\end{enumerate}

\medskip

52.  In section 41B (repayment of overpaid child support maintenance)\footnote{Section 41B was inserted by section 23 of the Child Support Act 1995 (c.~34) (“the 1995 Act”) and amended by the 2000 Act and the 2008 Act.}—
\begin{enumerate}\item[]
($a$) in subsection (1), for “Commission” substitute “Secretary of State”;

($b$) in subsection (1A), for “Commission” substitute “Secretary of State” and for the third “it” substitute “the Secretary of State”;

($c$) in subsection (2), for “Commission” (in both places) substitute “Secretary of State”;

($d$) in subsection (3), for “Commission” substitute “Secretary of State” and for “it” (in both places) substitute “the Secretary of State”;

($e$) in subsections (4), (5) and (6)($a$), for “Commission” (in each place) substitute “Secretary of State”; and

($f$) in subsection (9), for “Commission” substitute “Secretary of State” and for “it” substitute “the Secretary of State”.
\end{enumerate}

\medskip

53.  In section 41C (power to treat liability as satisfied)\footnote{Section 41C was inserted by section 31 of the 2008 Act.}, in subsections (1)($a$)  and ($b$)  and (3), for “Commission” substitute “Secretary of State”.

\medskip

54.  In section 43A(2)($a$)  (recovery of arrears from deceased’s estate)\footnote{Section 43A was inserted by section 38 of the 2008 Act.}, for “Commission” substitute “Secretary of State”.

\medskip

55.  In section 44 (jurisdiction), in subsections (1) and (4), for “Commission” substitute “Secretary of State”.

\medskip

56.  In section 46A(1) (finality of decisions)\footnote{Sections 46A and 46B were inserted by section 86(1) of, and Schedule 7 to, the Social Security Act 1998 (c.~14) (“the 1998 Act”) and amended by the 2000 Act and the 2008 Act.}, omit “the Commission,”.

\medskip

57.  In section 46B(1)($a$)  (matters arising as respects decisions), for “Commission” substitute “Secretary of State”.

\medskip

58.  In section 48(1) (right of audience)\footnote{Section 48(1) was amended by the 1995 Act and the 2008 Act.}, for “Commission” (in both places) substitute “Secretary of State”.

\medskip

59.  In section 50 (unauthorised disclosure of information)\footnote{Subsections (1A) to (1C) were inserted by section 57(1) of, and Schedule 7 to, the 2008 Act.}—
\begin{enumerate}\item[]
($a$) omit subsection (1A)($d$);

($b$) in subsection (1A)($e$), for “Commission” substitute “Secretary of State”;

($c$) omit subsection (7)($ba$); and

($d$) in subsection (7)($c$), for “, the Secretary of State or the person appointed to chair the Commission” substitute “or the Secretary of State”.
\end{enumerate}

60.  In section 50A (use of computers)\footnote{Section 50A was inserted by section~13(4) of, and Schedule 3 to, the 2008 Act.}—
\begin{enumerate}\item[]
($a$) for “Commission” substitute “Secretary of State”; and

($b$) for “Commission’s” substitute “Secretary of State’s”.
\end{enumerate}

\medskip

61.  In section 54 (interpretation), in subsection (1), omit the definition of “Commission”.

\medskip

62.---(1)  Schedule 1 (calculations) is amended as follows.

(2) In Part~I (as substituted by Schedule 1 to the Child Support, Pensions and Social Security Act 2000) (calculation of weekly amount of child support maintenance)\footnote{Part~I was substituted by section~1(3) of, and Schedule 1 to, the 2000 Act and amended by the 2008 Act.}—
\looseness=-1
\begin{enumerate}\item[]
($a$) in paragraph 7(3), for “Commission” substitute “Secretary of State”;

($b$) in paragraph 10 (as it has effect before the coming into force of paragraph~9 of Schedule 4 to the 2008 Act), in sub-paragraph (2)—
\begin{enumerate}\item[]
(i)  for “Commission” substitute “Secretary of State”; and

(ii) for “its” (in both places) substitute “the Secretary of State’s”; and
\end{enumerate}

($c$) in paragraph 10B($a$), for “Commission” (in both places) substitute “Secretary of State”.
\end{enumerate}

(3) In Part~II (maintenance calculations)\footnote{Part~II was amended by the 1998 Act, the 2000 Act and the 2008 Act.}—
\begin{enumerate}\item[]
($a$) in paragraphs 12 and 13, for “Commission” substitute “Secretary of State”;\looseness=-1

($b$) in paragraph 15—
\begin{enumerate}\item[]
(i)  for “Commission” substitute “Secretary of State”; and

(ii) for “it” substitute “the Secretary of State”; and
\end{enumerate}

($c$) in paragraph 16(10), for “Commission” (in both places) substitute “Secretary of State”.
\end{enumerate}

\medskip

63.  In Schedule 4A (as substituted by Schedule 2 to the Child Support, Pensions and Social Security Act 2000) (applications for a variation)\footnote{Schedule 4A was substituted by section 6(1) of, and Schedule 2 to, the 2000 Act and amended by the 2008 Act.}, in paragraph 4, for “Commission” (in both places) substitute “Secretary of State”.

\subsection*{\itshape Social Security Act 1998}

64.  In the Social Security Act 1998\footnote{1998 c.~14. Subsection 3(1A) was inserted by section 236 of, and Schedule 10 to, the Pensions Act 2004 (c.~35) and amended by the 2008 Act. Section 15A was inserted by S.I.~2008/2833.}—
\begin{enumerate}\item[]
($a$) in section 3(1A)($aa$)  (use of information), omit “in Northern Ireland”; and
\looseness=-1

($b$) in section~15A(2) (functions of senior president of tribunals), omit “and the Child Maintenance and Enforcement Commission” (in both places).
\end{enumerate}

\subsection*{\itshape Regulation of Investigatory Powers Act 2000}

65.  In the Regulation of Investigatory Powers Act 2000\footnote{2000 c.~23. Paragraph 28A was inserted by S.I.~2010/521.}, omit paragraph 28A (and the preceding heading) of Part II of Schedule 1 (relevant authorities for the purposes only of section 28).

\subsection*{\itshape Employment Act 2002}

66.  In section~13 of the Employment Act 2002\footnote{2002 c.~22.} (supply of information held by the Board), in subsection (2)—
\begin{enumerate}\item[]
($a$) in paragraphs ($a$)  and ($b$), omit “the Child Maintenance and Enforcement Commission”; and

($b$) in the final words, omit “and in relation to the Child Maintenance and Enforcement Commission, any function of that Commission”.
\end{enumerate}

\subsection*{\itshape Sexual Offences Act 2003}

67.  The Sexual Offences Act 2003\footnote{2003 c.42. Sections 94 and 95 were amended by S.I.~2008/2656.} is amended as follows.

\medskip

68.  In section 94 (supply of information to Secretary of State etc for verification)—
\looseness=-1
\begin{enumerate}\item[]
($a$) in subsection (2), omit paragraph ($aa$);

($b$) in subsection (2)($c$), omit “, the Child Maintenance and Enforcement Commission”;

($c$) in subsection (4)($a$)(i), omit “, the Child Maintenance and Enforcement Commission”; and

($d$) in the definition of “relevant function” in subsection (8), omit paragraph~($aa$).
\end{enumerate}

\medskip

69.  In section 95 (supply of information by Secretary of State etc)—
\begin{enumerate}\item[]
($a$) in subsection (1), omit paragraph ($aa$); and

($b$) in subsection (3)($a$), omit “, the Child Maintenance and Enforcement Commission”.
\looseness=-1
\end{enumerate}

\subsection*{\itshape Child Maintenance and Other Payments Act 2008}

70.  The 2008 Act is amended as follows.

\medskip

71.  Omit sections 1 to 5 and Schedule 1 (the Commission).

\medskip

72.---(1)  Section 6 (fees) is amended as follows.

(2) In subsections (1) and (5), for “Commission” substitute “Secretary of State”.

(3) In subsection (7), for “Commission” substitute “Secretary of State” and for “it” (in both places) substitute “the Secretary of State”.

\medskip

73.  Omit section 7 (agency arrangements and provision of services).

\medskip

74.---(1)  Section 8 (contracting out) is amended as follows.

(2) In subsection (1)—
\begin{enumerate}\item[]
($a$) for the first “Commission” substitute “Secretary of State relating to child support”; and

($b$) for the second “Commission” substitute “Secretary of State”.
\end{enumerate}

(3) In subsections (3)($b$)  and ($c$), (4), (5)($a$), (6) and (7), for “Commission” substitute “Secretary of State”.

\medskip

75.  Omit sections 9 to 12 (the Commission).

\medskip

76.  Omit sections 13 and 14 and Schedule 2 (transfer of child support functions to the Commission).

\medskip

77.  In section~17 (power to regulate supersession), in subsection (3)($b$)  to be substituted in section~17 of the 1991 Act, for “Commission” substitute “Secretary of State” and for “its” substitute “the Secretary of State’s”.

\medskip

78.---(1)  Section 18(2) (determination of applications for a variation) is amended as follows.

(2) In subsection (2A)($b$)  to be inserted into section 28D of the 1991 Act, for “Commission” substitute “Secretary of State” and for “its” substitute “the”.

(3) In subsection (2B) to be so inserted, for “Commission” (in both places) substitute “Secretary of State” and for “it” substitute “the Secretary of State”.

\medskip

79.---(1)  In section 25 (administrative liability orders), section 32M to be inserted into the 1991 Act is amended as follows.

(2) In subsection (1), for “Commission” substitute “Secretary of State” and for the second “it” substitute “the Secretary of State”.

(3) In subsection (2), for “Commission” substitute “Secretary of State”.

\medskip

80.---(1)  Section 27 (disqualification for holding or obtaining travel authorisation) is amended as follows.

(2) In section 39B to be inserted into the 1991 Act—
\begin{enumerate}\item[]
($a$) in subsection (1), for “Commission” (in both places) substitute “Secretary of State” and for “it” substitute “the Secretary of State”; and

($b$) in subsections (2), (7)($a$)  and (11), for “Commission” (in each place) substitute “Secretary of State”.
\end{enumerate}

(3) In section 39C to be so inserted, in subsection (5), for “Commission” substitute “Secretary of State”.

(4) In section 39E to be so inserted, in subsections (1), (2), (3) and (5), for “Commission” (in each place) substitute “Secretary of State”.

\medskip

81.---(1)  Section 28 (curfew orders) is amended as follows.

(2) In section 39H to be inserted into the 1991 Act—
\begin{enumerate}\item[]
($a$) in subsection (1), for “Commission” (in both places) substitute “Secretary of State” and for “it” substitute “the Secretary of State”; and

($b$) in subsections (2) to (5), for “Commission” substitute “Secretary of State”.
\looseness=-1
\end{enumerate}

(3) In section 39K to be so inserted, in subsections (2), (4), (5) and (6), for “Commission” substitute “Secretary of State”.

(4) In section 39M to be so inserted, in subsection (2)($a$), for “Commission” substitute “Secretary of State”.

(5) In section 39N to be so inserted, in subsections (1), (7) and (8), for “Commission” substitute “Secretary of State”.

(6) In section 39P to be so inserted, in subsection (2)($g$), for “Commission” substitute “Secretary of State”.

(7) In section 39Q to be so inserted, in subsection (2)($c$), for “Commission” substitute “Secretary of State”.

\medskip

82.---(1)  Section 29 (commitment to prison) is amended as follows.

(2) In subsection (1), in the provisions to be inserted into section 40 of the 1991 Act—
\looseness=-1
\begin{enumerate}\item[]
($a$) in subsection (2A), for “Commission” (in both places) substitute “Secretary of State” and for “it” (in both places) substitute “the Secretary of State”; and

($b$) in subsections (2B) and (2D)($a$), for “Commission” substitute “Secretary of State”.
\end{enumerate}

(3) In subsection (3), in the provisions to be inserted into section 40A of the 1991 Act—
\begin{enumerate}\item[]
($a$) in subsection (A1), for “Commission” (in both places) substitute “Secretary of State” and for “it” (in both places) substitute “the Secretary of State”; and

($b$) in subsections (A2) and (A4)($a$), for “Commission” substitute “Secretary of State”.
\end{enumerate}

\medskip

83.---(1)  In section 30(1) (disqualification for driving), the provisions to be substituted in section 40B of the 1991 Act are amended as follows.

(2) In subsection (A1), for “Commission” (in both places) substitute “Secretary of State” and for “it” (in both places) substitute “the Secretary of State”.

(3) In subsections (A3) and (A5)($a$), for “Commission” substitute “Secretary of State”.

\medskip

84.---(1)  In section 32 (power to accept part payment of arrears in full and final satisfaction), section 41D to be inserted into the 1991 Act is amended as follows.

(2) In subsections (1) and (3), for “Commission” substitute “Secretary of State”.

(3) In subsection (4), for “Commission” (in each place) substitute “Secretary of State” and for “it” (in both places) substitute “Secretary of State”.

\medskip

85.  In section 33 (power to write off arrears), in section 41E to be inserted into the 1991 Act, in subsection (1), for “Commission” substitute “Secretary of State” and for the second “it” substitute “the Secretary of State”.

\medskip

86.---(1)  In section 34 (transfer of arrears), section 49A to be inserted into the 1991 Act is amended as follows.

(2) In subsection (1), for “Commission” substitute “Secretary of State”.

(3) In subsection (2)($a$), for “Commission’s” substitute “Secretary of State’s”.

(4) In subsection (3), for “Commission” substitute “Secretary of State”.

(5) In subsection (4), for “Commission” (in each place) substitute “Secretary of State” and for “it” (in both places) substitute “the Secretary of State”.

(6) In subsections (5)($a$), (9)($d$)  and (10)($b$)  and ($c$), for “Commission” substitute “Secretary of State”.

\medskip

87.---(1)  In section 39 (disclosure of information relating to family proceedings), section 49B to be inserted into the 1991 Act is amended as follows.

(2) In subsection (1)—
\begin{enumerate}\item[]
($a$) for “Commission” (in the first place) substitute “Secretary of State for the purposes of the Secretary of State’s functions relating to child support”; and
\looseness=-1

($b$) for “Commission” (in the second place) substitute “Secretary of State for those purposes”.
\end{enumerate}

(3) In subsections (2)($c$)  and (3)($b$), for “Commission’s” substitute “Secretary of State’s”.

\medskip

88.  In section 40 (disclosure of information to credit reference agencies), in section 49D to be inserted into the 1991 Act, in subsections (1), (2)($a$)  and (4), for “Commission” substitute “Secretary of State”.

\medskip

89.  Omit section 44 and Schedule 6 (use of information).

\medskip

90.  In section 55 (regulations and orders: general), in subsection (5)—
\begin{enumerate}\item[]
($a$) insert “or” at the end of paragraph ($a$); and

($b$) omit subsection (5)($c$)  and the preceding “or”.
\end{enumerate}

\medskip

91.  In section 56 (general interpretation), omit subsection (1).

\medskip

92.  In section 59 (transition), omit subsection (1).

\medskip

93.  In section 61 (extent), omit subsection (2)($b$).

\medskip

94.  In Schedule 3—
\begin{enumerate}\item[]
($a$) omit paragraphs 40($b$)  and ($c$)  (amendment and temporary modification of section 38(1) of the 1991 Act);

($b$) omit paragraph 55 (transitional).
\end{enumerate}

\medskip

95.---(1)  Schedule 4 (changes to the calculation of maintenance) is amended as follows.
\looseness=-1

(2) In paragraph 8(4), in the inserted paragraph 9(2), for “Commission” substitute “Secretary of State”.

(3) In paragraph 9, in the substituted paragraph 10(2), for “Commission” substitute “Secretary of State” and for “its” (in both places) substitute “Secretary of State’s”.
\looseness=-1

\medskip

96.---(1)  Schedule 5 (maintenance calculations: transfer of cases to new rules) is amended as follows.

(2) In paragraph 1(1), for “Commission” substitute “Secretary of State”.

(3) In paragraph 2(2)($e$)—
\begin{enumerate}\item[]
($a$) for “Commission” substitute “Secretary of State”; and

($b$) omit “and approved by the Secretary of State”.
\end{enumerate}

(4) In paragraphs 3(2)($b$)  and 6(3), for “Commission” substitute “Secretary of State”.
\looseness=-1

\medskip

97.---(1)  In Schedule 7 (minor and consequential amendments), paragraph 1 is amended as follows.

(2) In sub-paragraph (3), in the inserted paragraph ($ba$), for “Commission” substitute “Secretary of State”.

(3) In sub-paragraph (6), in the inserted subsection (7A), for “Commission” substitute “Secretary of State”.

\subsection*{\itshape Welfare Reform Act 2009}

98.  The Welfare Reform Act 2009\footnote{2009 c.~24.} is amended as follows.

\medskip

99.---(1)  Section 51 (disqualification for holding etc driving licence or travel authorisation) is amended as follows.

(2) In subsection (2)($a$), for “Commission” (in both places) substitute “Secretary of State”.

(3) In subsection (2)($b$), in subsections (4) and (7) of the provisions to be substituted in section 39B of the 1991 Act, for “Commission” substitute “Secretary of State”.

(4) In subsection (4), in section 39CB to be inserted into the 1991 Act—
\begin{enumerate}\item[]
($a$) in subsection (5)($a$), for “Commission” substitute “Secretary of State” and for “its” substitute “the”; and

($b$) in subsection (6)($a$), for “Commission” substitute “Secretary of State”.
\end{enumerate}

(5) In subsection (5), in section 39DA to be inserted into the 1991 Act—
\begin{enumerate}\item[]
($a$) in the title, for “Commission’s” substitute “Secretary of State’s”;

($b$) in subsection (1), for “Commission” (in both places) substitute “Secretary of State” and omit “its”;

($c$) in subsection (2), for “Commission” substitute “Secretary of State” and for “Commission’s” substitute “Secretary of State’s”; and

($d$) in subsection (3), for “Commission’s” substitute “Secretary of State’s”.
\end{enumerate}

\medskip

100.---(1)  Schedule 5 (consequential amendments etc.) is amended as follows.

(2) In paragraph 3(2)($a$)  and ($b$), (3)($a$)  and ($b$)  and (4)($a$), for “Commission” substitute “Secretary of State”.

(3) In paragraph 5—
\begin{enumerate}\item[]
($a$) in sub-paragraph (2)($b$)  and ($c$), for “Commission” substitute “Secretary of State”;

($b$) in sub-paragraph (3), in the inserted subsection (1A), for “Commission” substitute “Secretary of State”; and

($c$) in sub-paragraph (4)($b$)  and ($c$), for “Commission” substitute “Secretary of State”.
\end{enumerate}

(4) In paragraph 6, in the substituted section 39F of the 1991 Act, in subsection~(2)($e$)  and ($f$), for “Commission” substitute “Secretary of State”.

\subsection*{\itshape Welfare Reform Act 2012}

101.  The Welfare Reform Act 2012\footnote{2012 c.~5.} is amended as follows.

\medskip

102.  In section~127 (information-sharing between Secretary of State and HMRC), in subsection (7), in the definition of “departmental functions”—
\begin{enumerate}\item[]
($a$) omit the “or” at the end of paragraph ($b$); and

($b$) after paragraph ($c$)  insert—
\begin{quotation}
“or

($d$) child support;”.
\end{quotation}
\end{enumerate}

\medskip

103.---(1)  Section 128 (information-sharing between Secretary of State and DPP) is amended as follows.

(2) In subsection (1), after “information” insert “or child support information”.

(3) In subsection (3), in paragraphs ($a$), ($b$)  and ($c$), after “matters” insert “or child support”.

(4) In subsection (6), insert the following definition at the appropriate place—
\begin{quotation}
““child support information” means information held for the purposes of any of the Secretary of State’s functions relating to child support;”.
\looseness=-1
\end{quotation}

\medskip

104.  In section~129 (unlawful disclosure of information supplied under section~128), in subsection (2)($c$), after “section~128)” insert “or child support”.

\enlargethispage{-2\baselineskip}

\medskip

105.---(1)  Section 136 (supporting maintenance agreements) is amended as follows.
\looseness=-1

(2) In subsection (1), in subsection (2A) to be inserted into section 9 of the 1991 Act—
\looseness=-1
\begin{enumerate}\item[]
($a$) for “Commission” (in the first place) substitute “Secretary of State”;

($b$) in paragraph ($a$), for “it” substitute “the Secretary of State”; and

($c$) in paragraph ($b$), for “Commission” substitute “Secretary of State”.
\end{enumerate}

(3) In subsection (2), in sub-paragraph (3) to be inserted into paragraph 3 of Schedule 5 to the 2008 Act, for “Commission” (in both places) substitute “Secretary of State”.
\looseness=-1

\medskip

106.---(1)  Section 137 (collection of child support maintenance) is amended as follows.
\looseness=-1

(2) In subsection (2)($b$), in subsection (2A) to be inserted into section 4 of the 1991 Act, for “Commission” (in both places) substitute “Secretary of State”.

(3) In subsection (3)($b$), in subsection (3A) to be inserted into section 7 of the 1991 Act, for “Commission” (in both places) substitute “Secretary of State”.

\medskip

107.---(1)  In section~138 (indicative maintenance calculations), section 9A to be inserted into the 1991 Act is amended as follows.

(2) In subsections (1), (2) and (3), for “Commission” substitute “Secretary of State”.\looseness=-1

(3) In subsection (5), for “Commission” substitute “Secretary of State” and for “it” (in both places) substitute “the Secretary of State”.

(4) In subsection (6), for “Commission” substitute “Secretary of State”.

\medskip

108.---(1)  Schedule 11 (power to require consideration of revision before appeal) is amended as follows.

(2) In paragraph 5(2), in the inserted subsections (2A) and (2B), for “Commission” (in each place) substitute “Secretary of State”.

(3) In paragraph 6(2), in the inserted subsections (3A) and (3B), for “Commission” (in each place) substitute “Secretary of State”.

\subsection*{\itshape Other Acts}

109.  In each of the following, omit the entry relating to the Child Maintenance and Enforcement Commission—
\begin{enumerate}\item[]
($a$) Schedule 2 to the Parliamentary Commissioner Act 1967\footnote{1967 c.~13.} (departments etc subject to investigation);

\enlargethispage{-2\baselineskip}

($b$) Part~II of Schedule 1 to the House of Commons Disqualification Act 1975\footnote{1975 c.~24.} (bodies of which all members are disqualified);

($c$) Part~II of Schedule 1 to the Northern Ireland Assembly Disqualification Act 1975\footnote{1975 c.~25.} (bodies of which all members are disqualified);

($d$) Part~VI of Schedule 1 to the Freedom of Information Act 2000\footnote{2000 c.~36.} (other public bodies and offices---general);

($e$) Part~I of Schedule 19 to the Equality Act 2010\footnote{2010 c.~15.} (public authorities: general); and

($f$) Schedule 1 to the Public Bodies Act 2011\footnote{2011 c.~24.} (power to abolish: bodies and offices).\looseness=-1
\end{enumerate}

\section[Part II --- Amendments to Statutory Instruments]{Part II\\*Amendments to Statutory Instruments}

\renewcommand\parthead{--- Schedule Part II}

\subsection*{\itshape Child Support (Maintenance Assessments and Special Cases) Regulations 1992}

110.  In paragraph 5B of Schedule 1 to the Child Support (Maintenance Assessments and Special Cases) Regulations 1992\footnote{S.I.~1992/1815. Paragraph 5B was inserted by S.I.~2012/712.} (estimate of earnings where insufficient information available), in sub-paragraphs (1) and (2), for “Commission” (in each place) substitute “Secretary of State”.

\subsection*{\itshape Child Support (Collection and Enforcement) Regulations 1992}

111.---(1)  The Child Support (Collection and Enforcement) Regulations 1992\footnote{S.I.~1992/1989. Relevant amendments were made by S.I.~2009/1815.} are amended as follows.

(2) In regulation 25A (interpretation)—
\begin{enumerate}\item[]
($a$) in paragraph (1), in the definition of “working day” for “Commission” substitute “Secretary of State”; and

($b$) in paragraphs (2), (3), (4) and (7), for “Commission” (in each place) substitute “Secretary of State”.
\end{enumerate}

(3) In regulation 25E (notification by the deposit-taker to the Commission), in paragraphs (1), (3), (4) and (5) and in the heading to that regulation, for “Commission” (in each place) substitute “Secretary of State”.

(4) In regulation 25F (notification by the Commission to the deposit-taker) and the heading to that regulation, for “Commission” substitute “Secretary of State”.

(5) In regulation 25G (review of a regular deduction order)—
\begin{enumerate}\item[]
($a$) in paragraphs (1) and (2)($a$), for “Commission” substitute “Secretary of State”; and

($b$) in paragraph (3), for “Commission” (in both places) substitute “Secretary of State” and for “it” (in both places) substitute “the Secretary of State”.
\end{enumerate}

\begin{sloppypar}
(6) In regulation 25I (variation of a regular deduction order), in paragraphs~(1),~(2) and (3), for “Commission” (in each place) substitute “Secretary of State”.
\end{sloppypar}

(7) In regulation 25J (lapse of a regular deduction order), in paragraphs (2),~(3) and (4), for “Commission” (in each place) substitute “Secretary of State”.

(8) In regulation 25K (revival of a regular deduction order), for “Commission” (in each place) substitute “Secretary of State”.

(9) In regulation 25L (discharge of a regular deduction order)—
\begin{enumerate}\item[]
($a$) in paragraph (1), for “Commission” (in each place) substitute “Secretary of State” and in sub-paragraph ($d$)  of that paragraph, for “it” substitute “the Secretary of State”; and

($b$) in paragraph (2), for “Commission” substitute “Secretary of State”.
\end{enumerate}

(10) In regulation 25M (period in which representations may be made), for “Commission” substitute “Secretary of State”.

(11) In regulation 25N (disapplication of sections 32G(1) and 32H(2)($b$)  of the Act), in paragraphs (1), (2), (3), (4) and (6), for “Commission” (in each place) substitute “Secretary of State”.

(12) In regulation 25O (information), in paragraphs (1), (3), (4) and (5), for “Commission” (in each place) substitute “Secretary of State”.

(13) In regulation 25R (variation of a lump sum deduction order), in paragraphs~(1) and (2), for “Commission” (in each place) substitute “Secretary of State”.

(14) In regulation 25S (lapse of a lump sum deduction order), in paragraphs~(2) and (3), for “Commission” (in each place) substitute “Secretary of State”.

(15) In regulation 25T (revival of a lump sum deduction order), for “Commission” (in each place) substitute “Secretary of State”.

(16) In regulation 25U (discharge of a lump sum deduction order)—
\begin{enumerate}\item[]
($a$) in paragraphs (1) and (2), for “Commission” (in each place) substitute “Secretary of State”; and

($b$) in paragraph (1)($d$), for “it” substitute “the Secretary of State”.
\end{enumerate}

(17) In regulation 25V($a$)(ii)  (time at which a lump sum deduction order under section 32E of the Act ceases to be in force), for “Commission” substitute “Secretary of State”.

(18) In regulation 25X(2) (accounts of a prescribed description), for “Commission” substitute “Secretary of State”.

(19) In regulation 25Z (administrative costs), for “Commission” substitute “Secretary of State”.

(20) In regulation 25AA (payment by deposit-taker to the Commission), in paragraphs (1) and (2) and in the heading to that regulation, for “Commission” (in each place) substitute “Secretary of State”.

(21) In regulation 25AB(1)($b$)  (appeals), for “Commission” substitute “Secretary of State”.

(22) In regulation 25AC (offences), in paragraphs ($a$)  and ($e$), for “Commission” substitute “Secretary of State”.

(23) In regulation 25AD (Commission to warn of consequences of failing to comply with an order or to provide information) and in the heading to that regulation, for “Commission” substitute “Secretary of State”.

\subsection*{\itshape Child Support Departure Direction and Consequential Amendments Regulations 1996}

112.  In the Child Support Departure Direction and Consequential Amendments Regulations 1996\footnote{S.I.~1996/2907.}—
\begin{enumerate}\item[]
($a$) in regulation 1(2) (interpretation), omit ““the Commission” means the Child Maintenance and Enforcement Commission;”; and

($b$) in regulation 24(1)($b$)  (diversion of income) for “Commission” substitute “Secretary of State”.
\end{enumerate}

\subsection*{\itshape Social Security and Child Support (Decisions and Appeals) Regulations 1999}

113.---(1)  The Social Security and Child Support (Decisions and Appeals) Regulations 1999\footnote{S.I.~1999/991. Relevant amendments were made by S.I.~2000/3185, 2001/158, 2002/1204, 2004/2415, 2008/2544 and 2683 and 2009/396.} are amended as follows.

(2) In regulation 1 (interpretation)—
\begin{enumerate}\item[]
($a$) in paragraph (3), omit ““the Commission” means the Child Maintenance and Enforcement Commission;”;

($b$) in paragraph ($a$)  of the definition of “official error” omit “, the Commission” (in each place); and

($c$) in the definition of “party to the proceedings” omit “or where the proceedings relate to child support, the Commission”.
\end{enumerate}

(3) In regulation 3A (revision of child support decisions)—
\begin{enumerate}\item[]
($a$) in paragraph (1)—
\begin{enumerate}\item[]
(i)  for “Commission” (in each place) substitute “Secretary of State”;

(ii) for the first, second and third “it” substitute “the Secretary of State”; and

(iii) for the final “it” substitute “the Secretary of State”;
\end{enumerate}

($b$) in paragraphs (2)($b$), (3) and (5), for “Commission” substitute “Secretary of State”;

($c$) in paragraph (5A)—
\begin{enumerate}\item[]
(i)  for “Commission” (in both places) substitute “Secretary of State”; and

(ii) in sub-paragraph ($c$), omit “it had been” and for “it made” substitute “of making”; and
\end{enumerate}

($d$) in paragraphs (8) and (9), for “Commission” (in each place) substitute “Secretary of State”.
\end{enumerate}

(4) In regulation 6A (supersession of child support decisions)—
\begin{enumerate}\item[]
($a$) in paragraph (1), for “Commission” substitute “Secretary of State”;

($b$) in paragraph (2), for “Commission” substitute “Secretary of State” and for “its” substitute “the Secretary of State’s”; and

($c$) in paragraphs (3) and (4), for “Commission” (in each place) substitute “Secretary of State”.
\end{enumerate}

(5) In regulation 6B (circumstances in which a child support decision may not be superseded), in paragraphs (1) and (5), for “Commission” substitute “Secretary of State”.

(6) In regulation 7C (procedure where the Secretary of State proposes to supersede a decision under section~17 of the Child Support Act on his own initiative), for “Commission” substitute “Secretary of State”, for “its” substitute “the Secretary of State’s” and for “it” substitute “the Secretary of State”.

(7) In regulation 15A (provision of information), for “Commission” (in each place) substitute “Secretary of State” and for “it” (in each place) substitute “the Secretary of State”.

(8) In regulation 15B (procedure in relation to an application made under section~16 or 17 of the Child Support Act in connection with a previously determined variation)—
\begin{enumerate}\item[]
($a$) in paragraph (1), for “Commission” (in each place) substitute “Secretary of State” and for “it” (in each place) substitute “the Secretary of State”;

($b$) in paragraph (2), for “Commission” (in each place) substitute “Secretary of State”;

($c$) in paragraph (3)—
\begin{enumerate}\item[]
(i)  for “Commission” substitute “Secretary of State”; and

(ii) in sub-paragraph ($a$)—
\begin{enumerate}\item[]
($aa$) for the words from “it is satisfied” to “force” substitute “satisfied on the information or evidence available that a variation of the maintenance calculation in force will not be agreed”; and

($bb$) for “it” (in both remaining places) substitute “the Secretary of State”;
\end{enumerate}
\end{enumerate}

($d$) in paragraph (4)—
\begin{enumerate}\item[]
(i)  for “Commission” (in each place) substitute “Secretary of State”;

(ii) for the first “it” substitute “the Secretary of State”; and

(iii) in sub-paragraph ($a$)—
\begin{enumerate}\item[]
($aa$) for the first “it” substitute “the Secretary of State”; and

($bb$) for “it may have” substitute “to be provided”; and
\end{enumerate}

(iv) in sub-paragraph ($b$), for “it” substitute “the Secretary of State”;
\end{enumerate}

($e$) in paragraphs (5) and (6), for “Commission” substitute “Secretary of State” and for “it” substitute “the Secretary of State”;

($f$) in paragraph (7), for “Commission” (in each place) substitute “Secretary of State” and for the first and second “it” substitute “the Secretary of State”; and

($g$) in paragraph (8), for “Commission” substitute “Secretary of State” and for “it” substitute “the Secretary of State”.
\end{enumerate}

(9) In regulation 15C (notification of a decision made under section~16 or 17 of the Child Support Act)—
\begin{enumerate}\item[]
($a$) in paragraph (3), for “Commission” (in both places) substitute “Secretary of State”;

($b$) in paragraphs (5), (9) and (11), for “Commission” (in each place) substitute “Secretary of State” and for “it” (in each place) substitute “the Secretary of State”; and

($c$) in paragraph (12), for “Commission” substitute “Secretary of State”.
\end{enumerate}

(10) In regulation 23 (child support decisions involving issues that arise on appeal in other cases)—
\begin{enumerate}\item[]
($a$) in paragraph (3), for “Commission” substitute “Secretary of State”; and

($b$) in paragraph (4), for “Commission” substitute “Secretary of State” and for “it” (in both places) substitute “the Secretary of State”.
\end{enumerate}

(11) In regulation 24 (child support appeals involving issues that arise in other cases)—
\begin{enumerate}\item[]
($a$) for “Commission” substitute “Secretary of State”; and

($b$) in paragraph ($a$), for “it” substitute “the Secretary of State”.
\end{enumerate}

(12) In regulation 30 (appeal against a decision which has been replaced or revised), in paragraphs (1) and (5) omit “, the Commission”.

(13) In regulation 32 (late appeals), in paragraphs (2) and (4), omit “, the Commission”.

(14) In regulation 33 (notice of appeal), in paragraphs (2) and (3), omit “, the Commission” (in each place).

(15) In Schedule 3D (effective dates for supersession of child support decisions), in paragraphs 9, 10 and 11, for “Commission” (in each place) substitute “Secretary of State”.

\subsection*{\itshape Child Support (Maintenance Calculations and Special Cases) Regulations 2000}

114.---(1)  The Schedule to the Child Support (Maintenance Calculations and Special Cases) Regulations 2000\footnote{S.I.~2001/155. Paragraphs 6A and 9A were inserted into the Schedule by S.I.~2012/712.} is amended as follows.

(2) In paragraph 6A (estimate of net weekly income of employed earner where insufficient information available), in sub-paragraphs (1) and (2), for “Commission” (in each place) substitute “Secretary of State”.

(3) In paragraph 9A (estimate of net weekly income of self-employed earner where insufficient information available), in sub-paragraphs (1) and (2), for “Commission” (in each place) substitute “Secretary of State”.

\subsection*{\itshape Child Support (Variations) Regulations 2000}

115.  In the Child Support (Variations) Regulations 2000\footnote{S.I.~2001/156. Relevant amendments made by S.I.~2009/736.}—
\begin{enumerate}\item[]
($a$) in regulation 1(2) (interpretation), omit ““the Commission” means the Child Maintenance and Enforcement Commission;”; and

($b$) in regulation 19(4)($b$)  (income not taken into account and diversion of income), for “Commission” substitute “Secretary of State”.
\end{enumerate}

\subsection*{\itshape Child Support Information Regulations 2008}

116.---(1)  The Child Support Information Regulations 2008\footnote{S.I.~2008/2551.} are amended as follows.

(2) In regulation 3 (information from the applicant), for “Commission” (in each place) substitute “Secretary of State”.

(3) In regulation 4(1) (information from other persons), for “Commission” substitute “Secretary of State”.

(4) In regulation 5 (information from persons denying parentage), for “Commission” substitute “Secretary of State”.

(5) In regulation 6(1) (information from a court), for “Commission” substitute “Secretary of State”.

(6) In regulation 8 (Commission to warn of consequences of failing to provide information or providing false information) and in the heading to that regulation, for “Commission” substitute “Secretary of State”.

(7) In regulation 9 (duty to notify change of address), for “Commission” substitute “Secretary of State”.

(8) In regulation 10 (continuing duty of person with care), for “Commission” (in each place) substitute “Secretary of State”.

(9) In regulation 12 (disclosure of information to a court or tribunal), in paragraphs (1) and (3), for “Commission” substitute “Secretary of State”.

(10) In regulation 13 (disclosure of information to other persons)—
\begin{enumerate}\item[]
($a$) in paragraph (1), for “Commission” (in both places) substitute “Secretary of State” and in sub-paragraph ($a$)  of that paragraph, for “it” substitute “the Secretary of State”; and

($b$) in paragraphs (3) and (4), for “Commission” (in each place) substitute “Secretary of State”.
\end{enumerate}

(11) Regulation 16 (transitional provisions in relation to transfer of child support functions) is revoked.

\subsection*{\itshape Tribunal Procedure (First Tier Tribunal) (Social Entitlement Chamber) Rules 2008}

117.  In rule 19 of the Tribunal Procedure (First Tier Tribunal) (Social Entitlement Chamber) Rules 2008\footnote{S.I.~2008/2685.} (confidentiality in child support or child trust fund cases)—
\begin{enumerate}\item[]
($a$) in paragraph (2)($a$), omit “or the Child Maintenance and Enforcement Commission”;

($b$) in paragraph (2)($b$), omit “or the Child Maintenance and Enforcement Commission, whichever has made enquiry,”; and

($c$) in paragraph (3), omit “, the Child Maintenance and Enforcement Commission”.
\end{enumerate}

\subsection*{\itshape Tribunal Procedure (Upper Tribunal) Rules 2008}

118.  In rule 19 of the Tribunal Procedure (Upper Tribunal) Rules 2008\footnote{S.I.~2008/2698.} (confidentiality in child support or child trust fund cases)—
\begin{enumerate}\item[]
($a$) in paragraph (2)($b$)(iii), omit “, the Child Maintenance and Enforcement Commission”; and

($b$) in paragraph (3), omit “, the Child Maintenance and Enforcement Commission”.
\end{enumerate}

\subsection*{\itshape\sloppy
Company, Limited Liability Partnership and Business Names (Sensitive Words and Expressions) Regulations 2009}

119.  In Column (2) of Part~I of Schedule 2 to the Company, Limited Liability Partnership and Business Names (Sensitive Words and Expressions) Regulations 2009\footnote{S.I.~2009/2615.} (list of government departments and other bodies whose views must be sought), for “Child Maintenance and Enforcement Commission” (in both places) substitute “Department for Work and Pensions”.

\subsection*{\itshape
Company, Limited Liability Partnership and Business Names (Public Authorities) Regulations 2009
}

120.  In Columns (1) and (2) of the Schedule to the Company, Limited Liability Partnership and Business Names (Public Authorities) Regulations 2009\footnote{S.I.~2009/2982.} (specified “Public Authorities” and list of government departments and other bodies whose views must be sought), omit “Child Maintenance and Enforcement Commission” (in both places).

\subsection*{\itshape\sloppy
Child Support (Management of Payments and Arrears) Regulations 2009
}

121.---(1)  The Child Support (Management of Payments and Arrears) Regulations 2009\footnote{S.I.~2009/3151.} are amended as follows.

(2) In regulation 3 (arrears notices)—
\begin{enumerate}\item[]
($a$) in paragraph (1)($a$), for “Commission” substitute “Secretary of State”; and

($b$) in paragraph (2), for “Commission” substitute “Secretary of State” and for “it” substitute “the Secretary of State”.
\end{enumerate}

(3) In regulation 4 (attribution of payments), for “Commission” substitute “Secretary of State” and for “it” substitute “the Secretary of State”.

(4) In regulation 5 (set off of liabilities to pay child support maintenance), in paragraphs (1) and (2), for “Commission” substitute “Secretary of State”.

(5) In regulation 6 (set off of payments against child support maintenance liability), in paragraphs (1) and (2), for “Commission” substitute “Secretary of State”.

(6) In regulation 7 (application to set off)—
\begin{enumerate}\item[]
($a$) in paragraph (1), for “Commission” substitute “Secretary of State”; and

($b$) in paragraph (2), for “Commission” substitute “Secretary of State” and for the first “it” substitute “the Secretary of State”.
\end{enumerate}

(7) In regulation 8 (application of overpayments)—
\begin{enumerate}\item[]
($a$) in paragraph (1), for “Commission” substitute “Secretary of State”; and

($b$) in paragraph (2), for “Commission” substitute “Secretary of State” and for the first “it” substitute “the Secretary of State”.
\end{enumerate}

(8) In regulation 9 (application of voluntary payments)—
\begin{enumerate}\item[]
($a$) in paragraph (1), for “Commission” substitute “Secretary of State”; and

($b$) in paragraph (2), for “Commission” substitute “Secretary of State” and for the first “it” substitute “the Secretary of State”.
\end{enumerate}

(9) In regulation 10 (application and interpretation of Part~IV), in paragraph~(2), for “Commission” substitute “Secretary of State”.

(10) In regulation 11 (recovery of arrears from a deceased person’s estate), for “Commission” substitute “Secretary of State”.

(11) In regulation 12(2) (appeals and other proceedings), in the paragraph substituting paragraphs (1) and (2) of regulation 34 of the Social Security and Child Support (Decisions and Appeals) Regulations 1999\footnote{S.I.~1999/991.}, for “Commission” substitute “Secretary of State” and for “it” (in both places) substitute “the Secretary of State”.

(12) In regulation 13 (disclosure of information), for “Commission” (in each place) substitute “Secretary of State”.

\subsection*{\itshape
Regulation of Investigatory Powers (Communications Data) Order 2010
}

122.---(1)  Part~II of Schedule 2 to the Regulation of Investigatory Powers (Communications Data) Order 2010\footnote{S.I.~2010/480.} (individuals in additional relevant public authorities that may acquire communications data falling within section 21(4)($b$)  and ($c$)) is amended as follows.

(2) In the entry for the Child Maintenance and Enforcement Commission—
\begin{enumerate}\item[]
($a$) in column (1), for “Child Maintenance and Enforcement Commission” substitute “Department for Work and Pensions”; and

($b$) in column (2), after “grade” insert “carrying out functions in relation to child support”.
\end{enumerate}

\subsection*{\itshape
Regulation of Investigatory Powers (Directed Surveillance and Covert Human Intelligence Sources) Order 2010
}

123.---(1)  Part~II of the Schedule to the Regulation of Investigatory Powers (Directed Surveillance and Covert Human Intelligence Sources) Order 2010\footnote{S.I.~2010/521.} (offices, etc and restrictions in respect of relevant public authorities specified in Part~II of Schedule~1 to the Act) is amended as follows.

(2) In the entry for the Child Maintenance and Enforcement Commission—
\begin{enumerate}\item[]
($a$) in column (1), omit “The Child Maintenance and Enforcement Commission”;

($b$) in column (2), omit “Senior Executive Officer or equivalent grade”;

($c$) in column (3), omit “Higher Executive Officer or equivalent grade”; and

($d$) in column (4), omit “Paragraph ($b$)”.
\end{enumerate}

(3) In the entry for the Department for Work and Pensions—
\begin{enumerate}\item[]
($a$) in column (2), insert “Senior Executive Officer or equivalent grade carrying out functions in relation to child support”;

($b$) in column (3), insert “Higher Executive Office or equivalent grade carrying out functions in relation to child support”; and

($c$) in column (4), insert “Paragraph ($b$)”.
\end{enumerate}

\subsection*{\itshape
Management of Offenders etc.\ (Scotland) Act 2005 (Disclosure of Information) Order 2010
}

124.---(1)  The Management of Offenders etc.\ (Scotland) Act 2005 (Disclosure of Information) Order 2010\footnote{S.I.~2010/912.} is amended as follows.

(2) In article 2 (interpretation), omit ““the Commission” means the Child Maintenance and Enforcement Commission;”.

(3) In article~3 (disclosure of information to the Secretary of State and the Commission)—
\begin{enumerate}\item[]
($a$) in the heading, omit “and the Commission”;

($b$) omit “or” at the end of paragraph (1)($a$);

($c$) omit sub-paragraph (1)($b$);

($d$) omit “or” at the end of paragraph (2)($a$);

($e$) after paragraph (2)($b$)  insert—
\begin{quotation}
“or

($c$) child support.”; and
\end{quotation}

($f$) omit paragraph (3).
\end{enumerate}

(4) In article 4 (disclosure of information to responsible authorities)—
\begin{enumerate}\item[]
($a$) omit “or” at the end of paragraph (1)($a$);

($b$) after paragraph (1)($b$)  insert—
\begin{quotation}
“or

($c$) child support.”; and
\end{quotation}

($c$) omit paragraph (2).
\end{enumerate}

\subsection*{\itshape
Family Procedure Rules 2010
}

125.  In the Family Procedure Rules 2010\footnote{S.I.~2010/2955.}—
\begin{enumerate}\item[]
($a$) in rule 2.3(1) (interpretation), omit ““Commission” means the Child Maintenance and Enforcement Commission;”;

($b$) in rule 8.38 (who the parties are), for “Commission” substitute “Secretary of State”; and

($c$) in rule 29.2 (disclosure of information under the Child Support Act 1991), for “Commission”, substitute “Secretary of State”. 
\end{enumerate}

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Order)}

The Public Bodies Act 2011 provides for the abolition, and associated transfer of functions, by order of any body specified in Schedule 1 to that Act. The Child Maintenance and Enforcement Commission (“the Commission”) is a body listed in that Schedule.

Article 2 abolishes the Commission.

Article 3(1) transfers the functions of the Commission to the Secretary of State. Article 3(2) and the Schedule make consequential, incidental and supplementary amendments. Article 3(3) transfers the property, rights and liabilities of the Commission to the Secretary of State.

Article 4 makes provision in relation to the winding up of the Commission’s affairs by the Secretary of State, including the preparation of final accounts.

Article 5 makes provision for the continuity of the exercise of functions on the transfer of functions from the Commission to the Secretary of State. Paragraph (1) ensures that anything which relates to the transferring functions which has been done, or is in the process of being done, by or in relation to Commission, immediately before its abolition can be continued by, or in relation to the Secretary of State. Paragraph (2) provides that anything done by or in relation to the Commission before its abolition for the purposes of, or in connection with, the transferring functions shall continue to have effect as if done by or in relation to the Secretary of State. Paragraph (3) ensures that, as far as necessary, documents have effect as if any reference to the Commission is a reference to the Secretary of State. Paragraph (4) prevents the transfer of functions, property, rights and liabilities from the Commission to the Secretary of State affecting the validity of anything done by or in relation to the Commission prior to the transfer. Paragraph (5) prevents a reference to the Commission in any document or notice issued by the Secretary of the State, following the transfer, invalidating that document or notice.

A full impact assessment has not been published for this instrument as it has no impact on the private sector or civil society organisations. 

\end{document}