\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support (Information, Evidence and Disclosure and Maintenance Arrangements and Jurisdiction) (Amendment) Regulations 2000}

\newcommand\regsnumber{2001/161}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2001 No.\ 161}

\date{Made
18th January 2001\\
%Laid before Parliament
%25th January 2001\\
Coming into force
as provided in regulation 1(3)
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{42.07402pt}

\begin{document}

\maketitle

\noindent
Whereas a draft of this Instrument was laid before Parliament in accordance with section 52(2) of the Child Support Act 1991\footnote{1991 c.\ 48. Section 52 is amended by section 25 of the Child Support, Pensions and Social Security Act 2000 (c.\ 19).} and approved by a resolution of each House of Parliament:

Now, therefore, the Secretary of State for Social Security, in exercise of the powers conferred upon him by sections 4(4), 6(7), 7(5), 10(1), (2) and (4), 14(1), (1A) and (3), 44(2A), 51, 52(1) and (4), 54 and 57 of the Child Support Act 1991\footnote{The Act is amended by Part I of the Child Support, Pensions and Social Security Act 2000. Section 4(4) is amended by paragraph 11(3) of Schedule 3 to that Act, section 14(1) is amended by section 12 of, and paragraph 11(7) of Schedule 3 to, that Act, section 6(9) is substituted by section 3 of that Act, sections 51 and 54 are amended by paragraph 11(19) and (20) respectively of Schedule 3 to that Act and section 44(2A) is inserted by section 22(3) of that Act. Section 54 is cited because of the meaning ascribed to the word “prescribed”.}, and of all other powers enabling him in that behalf, hereby makes the following Regulations: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation, commencement and interpretation]{Citation, commencement and interpretation}

1.---(1)  These Regulations may be cited as the Child Support (Information, Evidence and Disclosure and Maintenance Arrangements and Jurisdiction) (Amendment) Regulations 2000.

(2) In these Regulations—
\begin{enumerate}\item[]
($a$) “the Information Regulations” means the Child Support (Information, Evidence and Disclosure) Regulations 1992\footnote{S.I.\ 1992/1812. Amending instruments are S.I.\ 1995/123, 1995/1045, 1995/3261, 1996/1945, 1996/2907, 1998/58, 1999/977 and 1999/1510.};

($b$) “the Jurisdiction Regulations” means the Child Support (Maintenance Arrangements and Jurisdiction) Regulations 1992\footnote{S.I.\ 1992/2645. Amending instruments are S.I.\ 1993/913, 1995/123, 1995/1045, 1995/3261 and 1999/1510.}; and

($c$) “the Act” means the Child Support Act 1991.
\end{enumerate}

(3) These Regulations shall come into force as follows—
\begin{enumerate}\item[]
($a$) regulations 5(2)($b$), ($d$)  and ($e$), 6(3) and 7(1) and, for the purposes of those provisions, this regulation, shall come into force in relation to a particular case on the day on which section 13 of the Child Support, Pensions and Social Security Act 2000 comes into force for the purposes of that type of case;

($b$) regulation 8(3) and, for the purposes of that provision, this regulation, shall come into force in relation to a particular case on the day on which section 22(3) of the Child Support, Pensions and Social Security Act 2000 comes into force for the purposes of that type of case;

($c$) regulation 4 and, for the purposes of that provision, this regulation, shall come into force on 1st April 2001\footnote{This is the day on which section 90 (transfer of clerks' functions to the chief executives) of the Access to Justice Act 1999 (c.\ 22) comes into force.}; and

($d$) the remainder of these Regulations shall come into force in relation to a particular case on the day on which sub-paragraphs (19) and (20) of paragraph 11 of Schedule 3 to the Child Support, Pensions and Social Security Act 2000, which respectively amend sections 51 and 54 of the Act, come into force for the purposes of that type of case.
\end{enumerate}

\subsection[2. References to “absent parent”, “assessment” and “departure direction”]{References to “absent parent”, “assessment” and “departure direction”}

2.---(1)  For the words “absent parent” wherever they appear in the Information Regulations and the Jurisdiction Regulations there shall be substituted the words “non-resident parent”.

(2) For the word “assessment” wherever it appears in the Information Regulations and the Jurisdiction Regulations there shall be substituted the word “calculation”.

(3) In regulation 3(1)($f$)  of the Information Regulations for the word “assessed” there shall be substituted the word “calculated”.

(4) In regulation 9A(2)($c$)(ii)  of the Information Regulations for the words “departure direction” there shall be substituted the word “variation”.

\subsection[3. References to regulations]{References to regulations}

3.---(1)  In regulation 1(2) of the Information Regulations and regulation 1(2) of the Jurisdiction Regulations—
\begin{enumerate}\item[]
($a$) for the definition of the Maintenance Assessments and Special Cases Regulations there shall be substituted ““Maintenance Calculations and Special Cases Regulations” means the Child Support (Maintenance Calculations and Special Cases) Regulations 2000\footnote{S.I.\ 2001/155.};”; and

($b$) for the definition of the Maintenance Assessment Procedure Regulations there shall be substituted ““Maintenance Calculation Procedure Regulations” means the Child Support (Maintenance Calculation Procedure) Regulations 2000\footnote{S.I.\ 2001/157.};”.
\end{enumerate}

(2) In regulation 1(2), in the definition of “relevant person”, of the Information Regulations and regulation 5(3)($c$)  of the Jurisdiction Regulations for the words “regulation 20 of the Maintenance Assessments and Special Cases Regulations” there shall be substituted the words “regulation 8 of the Maintenance Calculations and Special Cases Regulations”.

(3) In the Information Regulations—
\begin{enumerate}\item[]
($a$) in regulation 5(1) for the words “regulations 2(5) and 6(1) of the Maintenance Assessment Procedure Regulations” there shall be substituted the words “regulation 3(4) of the Maintenance Calculation Procedure Regulations”; and

($b$) in regulation 9A(1)($d$)  for the words “regulation 10 of the Maintenance Assessment Procedure Regulations” there shall be substituted the words “regulation 23 of the Maintenance Calculation Procedure Regulations”.
\end{enumerate}

\subsection[4. References to “clerk to the justices”]{References to “clerk to the justices”}

4.  In regulation 2(3)($a$)(iii)  of the Information Regulations and regulations 5(4)($a$)(iii)  and 6(2)($a$)(iii)  of the Jurisdiction Regulations for the words “clerk to the justices of” there shall be substituted the words “justices' chief executive for”.

\subsection[5. Amendment of regulations 1 and 2 of the Information Regulations]{Amendment of regulations 1 and 2 of the Information Regulations}

5.---(1)  In regulation 1(2) of the Information Regulations—
\begin{enumerate}\item[]
($a$) for the definition of “local authority” there shall be substituted ““local authority” means, in relation to England, a county council, a district council, a London borough council, the Common Council of the City of London or the Council of the Isles of Scilly and, in relation to Wales, a county council or a county borough council and, in relation to Scotland, a council constituted under section 2 of the Local Government etc (Scotland) Act 1994\footnote{1994 c.\ 39.};”; and

($b$) in the definition of “relevant person” after the words “in respect of whom” there shall be substituted the words “a maintenance calculation has been applied for, or has been treated as applied for under section 6(3) of the Act, or is or has been in force.”.
\end{enumerate}

(2) In regulation 2(2) of the Information Regulations—
\begin{enumerate}\item[]
($a$) in sub-paragraphs ($c$)  and ($cc$)  the words “or the parent with care” shall be omitted;

($b$) in sub-paragraphs ($c$)  and ($cc$)  after “($d$), ($e$), ($f$), ($h$)” there shall be inserted “, ($hh$)”;

($c$) in sub-paragraphs ($b$), ($c$)  and ($cc$)  for the words “assessment has been made” there shall be substituted the words “calculation has been made, or has been treated as made,”;

($d$) in sub-paragraph ($d$)—
\begin{enumerate}\item[]
(i) for the word “matter” there shall be substituted the word “matters”; and

(ii) after the words “sub-paragraph ($a$)” there shall be inserted “,~($d$), ($e$), ($f$), ($h$)  and ($hh$)”; and
\end{enumerate}

($e$) after sub-paragraph ($e$)  there shall be inserted—
\begin{quotation}
“($f$) a person who acts or has acted as an accountant for the absent parent, including where that person is self-employed, in relation to any business accounts of that parent with respect to the matters listed in sub-paragraphs ($e$), ($f$), ($h$)  and ($hh$)  of regulation 3(1);

($g$) a company or partnership for whom the absent parent is providing or has provided services under a contract for services with respect to the matters listed in sub-paragraphs ($e$)  and ($f$)  of regulation 3(1); and

($h$) persons employed in the service of the Crown or otherwise in the discharge of Crown functions—
\begin{enumerate}\item[]
(i) under sections 97 to 99A of the Road Traffic Act 1988\footnote{1988 c.\ 52. Sections 97 to 99A were amended by the Road Traffic (Driver Licensing and Information Systems) Act 1989 (c.\ 22), the Road Traffic Act 1991 (c.\ 40), the Driving Licence (Community Driving Licence) Regulations 1990 S.I.\ 1990/144, the Driving Licence (Community Driving Licence) Regulations 1996 S.I.\ 1996/1974 and the Driving Licence (Community Driving Licence) Regulations 1998 S.I.\ 1998/1420.} or Part II of the Vehicle Excise and Registration Act 1994\footnote{1994 c.\ 22. Part II was amended by the Finance Act 1995 (c.\ 4), the Finance Act 1996 (c.\ 8), the Finance Act 1997 (c.\ 16), the Finance (No.\ 2) Act 1997 (c.\ 58) and the Finance Act 1998 (c.\ 36).} with respect to the matter listed in sub-paragraph ($e$)  of regulation 3(1); or

(ii) under the Prison Act 1952\footnote{15 \& 16 Geo.\ 6 \& 1 Eliz. 2 c.\ 52.} with respect to the matter listed in sub-paragraph ($e$)  of regulation 3(1).”.
\end{enumerate}
\end{quotation}
\end{enumerate}

\subsection[6. Amendment of regulations 3 and 3A of the Information Regulations]{Amendment of regulations 3 and 3A of the Information Regulations}

6.---(1)  In regulation 3(1) of the Information Regulations—
\begin{enumerate}\item[]
($a$) in sub-paragraph ($aa$)  after “maintenance order” there shall be inserted “made on or after the date prescribed for the purposes of section 4(10)($a$)  of the Act\footnote{Section 4(10) was amended by section 2 of the Child Support, Pensions and Social Security Act 2000.} which has been in force for at least a year from the date it was made”; and

($b$) after sub-paragraph ($k$)  there shall be inserted—
\begin{quotation}
“($l$) a determination as to who is in receipt of child benefit, payable under Part IX of the Social Security Contributions and Benefits Act 1992\footnote{1992 c.\ 4.}, either for a child who may be a relevant other child for the purposes of Schedule 1 to the Act, or for the qualifying child where a parent may fall to be treated as a non-resident parent under the Maintenance Calculations and Special Cases Regulations.”.
\end{quotation}
\end{enumerate}

(2) In regulation 3(2) of the Information Regulations—
\begin{enumerate}\item[]
($a$) in sub-paragraphs ($a$)  and ($e$)  for the words from “an application” to “made” and in sub-paragraph ($b$)  for the words from “the application” to “made” there shall be substituted the words “the maintenance calculation has been applied for, or has been treated as applied for”;

($b$) the following words shall be omitted—
\begin{enumerate}\item[]
(i) in sub-paragraph ($g$)  “or a parent with care”;

(ii) in sub-paragraph ($h$)  “or parent with care”;

(iii) in sub-paragraph ($i$)  “and a parent with care”;

(iv) in sub-paragraph ($l$)  “or living in the same household as the parent with care” and “or the parent with care, as the case may be”;

(v) in sub-paragraph ($q$)  “or the person with care”; and

(vi) in sub-paragraph ($r$)(i)  “or should be cancelled”; and
\end{enumerate}

($c$) sub-paragraphs ($j$), ($m$), ($n$), ($o$), ($p$)  and ($s$)  shall be omitted.
\end{enumerate}

(3) At the end of regulation 3A of the Information Regulations there shall be inserted “including details of the offences provided for in section 14A of the Act\footnote{Section 14A is inserted into the Act by section 13 of the Child Support, Pensions and Social Security Act 2000.} for failing to provide, or providing false, information.”.

\subsection[7. Amendment of regulations 6 and 9A and omission of regulation 4 of the Information Regulations]{Amendment of regulations 6 and 9A and omission of regulation 4 of the Information Regulations}

7.---(1)  Regulation 4 of the Information Regulations shall be omitted.

(2) In regulation 6 of the Information Regulations the words “or should be cancelled” shall be omitted in both places where they appear.

(3) In regulation 9A(1) of the Information Regulations—
\begin{enumerate}\item[]
($a$) in sub-paragraph ($a$)  for the words from “why” to “Act”, in the first place where it appears, there shall be substituted “why he has decided not to make a maintenance calculation in response to an application made under section 4 or 7 of the Act or treated as made under section 6 of the Act”; and

($b$) in sub-paragraph ($c$)  the words “or has been cancelled” shall be omitted.
\end{enumerate}

\subsection[8. Amendment of regulation 3, omission of regulation 7 and insertion of regulation 7A of the Jurisdiction Regulations]{Amendment of regulation 3, omission of regulation 7 and insertion of regulation 7A of the Jurisdiction Regulations}

8.---(1)  In regulation 3 of the Jurisdiction Regulations—
\begin{enumerate}\item[]
($a$) in paragraph (2) after the words “cease to have effect” there shall be added the words “on the effective date of the maintenance calculation.”; and

($b$) paragraphs (5) to (8) shall be omitted.
\end{enumerate}

(2) Regulation 7 of the Jurisdiction Regulations shall be omitted.

(3) After regulation 7 of the Jurisdiction Regulations there shall be inserted—
\begin{quotation}
\subsection*{“Prescription for the purposes of jurisdiction}

7A.---(1)  The companies prescribed for the purposes of section 44(2A)($c$)  of the Act (non-resident parents not habitually resident in the United Kingdom but employed by prescribed companies) are companies which employ employees to work outside the United Kingdom but make calculations and payment arrangements in relation to the earnings of those employees in the United Kingdom so that a deduction from earnings order may be made under section 31 of the Act in respect of the earnings of any such employee who is a liable person for the purposes of that section.

(2) The following bodies are prescribed for the purposes of section 44(2A)($d$)  of the Act (non-resident parents not habitually resident in the United Kingdom but employed by a prescribed body)—
\begin{enumerate}\item[]
($a$) a National Health Service Trust established by order made under section 5 of the National Health Service and Community Care Act 1990\footnote{1990 c.\ 19. Section 5 was amended by paragraph 69 of Schedule 1 to the Health Authorities Act 1995 (c.\ 17), by paragraph 65(2) of Schedule 2 to the National Health Service (Primary Care) Act 1997 (c.\ 46) and by sections 13(1) and 14 of the Health Act 1999 (c.\ 8).} (“the 1990 Act”) or under section 12A of the National Health Service (Scotland) Act 1978\footnote{1978 c.\ 29. Section 12A was inserted by section 31 of the 1990 Act and amended by section 46(1) of the Health Act 1999.} (“the 1978 Act”);

($b$) a Primary Care Trust established by order made under section 16A of the National Health Service Act 1977\footnote{1977 c.\ 49. Section 16A was inserted by section 2(1) of the Health Act 1999. Section 16A was commenced in England on 4th January 2000. Section 16A has not been commenced in Wales.};

($c$) a Health Authority established under section 8 of the National Health Service Act 1977\footnote{Section 8 was substituted by section 1 of the Health Authorities Act 1995 and amended by paragraph 5 of Schedule 4 to the Health Act 1999.} (“the 1977 Act”);

($d$) a Special Health Authority established under section 11 of the 1977 Act\footnote{Section 11 was amended by paragraph 3 of Schedule 1 to the Health Authorities Act 1995 and by paragraph 6 of Schedule 4 to the Health Act 1999.};

($e$) a local authority, and for this purpose “local authority” means, in relation to England, a county council, a district council, a London borough council, the Common Council of the City of London or the Council of the Isles of Scilly and, in relation to Wales, a county council or a county borough council and, in relation to Scotland, a council constituted under section 2 of the Local Government etc (Scotland) Act 1994\footnote{1994 c.\ 39.};

($f$) a Health and Social Service Trust established by order made under Article 10 of the Health and Personal Social Services (Northern Ireland) Order 1991\footnote{S.I.\ 1991/194 (N.I.1). Article 10 was amended by Article 3(8) of the Health and Personal Social Services (Northern Ireland) Order 1994 S.I.\ 1994/429 (N.I.2).};

($g$) a Health and Social Services Board established by order made under Article 16 of the Health and Personal Social Services (Northern Ireland) Order 1972\footnote{S.I.\ 1972/1265 (N.I.14).} (“the 1972 Order”);

($h$) the Central Services Agency established by order made under Article 26 of the 1972 Order;

($i$) a Special Agency established by order made under Article 3 of the Health and Personal Social Services (Special Agencies) (Northern Ireland) Order 1990\footnote{S.I.\ 1990/247 (N.I.3).};

($j$) a Health Board constituted under section 2 of the 1978 Act; and

($k$) a Special Health Board constituted under section 2 of the 1978 Act.”.
\end{enumerate}
\end{quotation}

\subsection[9. Amendment of regulation 8 of the Jurisdiction Regulations]{Amendment of regulation 8 of the Jurisdiction Regulations}

9.  In regulation 8 of the Jurisdiction Regulations—
\begin{enumerate}\item[]
($a$) for paragraph (1)($c$)  there shall be substituted “the Secretary of State revises the decision as to the maintenance calculation under section 16 of the Act and decides that no child support maintenance was payable on the ground that the previous decision was made in error,”;

($b$) in paragraph (2)($aa$)  the words “is cancelled or” shall be omitted; and

($c$) in paragraph (2) the words “as not having been cancelled or, as the case may be,” shall be omitted.
\end{enumerate}

\subsection[10. Transitional provisions and savings]{Transitional provisions and savings}

10.---%
% Reg 10(Z1) inserted (3.3.03) by SI 2001/162 reg 2(3), (4)(d)
(Z1) This regulation is subject to the Child Support (Transitional Provisions) Regulations 2000.

(1)  Where in respect of a particular case before the date that these Regulations come into force with respect to that type of case (“the commencement date”)—
\begin{enumerate}\item[]
($a$) an application was made and not determined for—
\begin{enumerate}\item[]
(i) a maintenance assessment;

(ii) a departure direction; or

(iii) a revision or supersession of a decision;
\end{enumerate}

($b$) the Secretary of State had begun but not completed a revision or supersession of a decision on his own initiative;

($c$) any time limit provided for in Regulations for making an application for a revision or a departure direction had not expired; or

($d$) any appeal was made but not decided or any time limit for making an appeal had not expired,
\end{enumerate}
regulations 2, 3, 5 (except for sub-paragraphs (2)($b$), ($d$)  and ($e$)), 6(1) and (2), 7(2) and (3), 8(1) and (2) and 9 shall not apply for the purposes of—
\begin{enumerate}\item[]
($aa$) the decision on the application referred to in sub-paragraph ($a$);

($bb$) the revision or supersession referred to in sub-paragraph ($b$);

($cc$) the ability to apply for the revision or the departure direction referred to in sub-paragraph ($c$)  and the decision whether to revise or to give a departure direction following any such application;

($dd$) any appeal outstanding or made during the time limit referred to in sub-paragraph ($d$); or

($ee$) any revision, supersession or appeal or application for a departure direction in relation to a decision, ability to apply or appeal referred to in sub-paragraphs ($aa$)  to ($dd$)  above.
\end{enumerate}

(2) Where after the commencement date a maintenance assessment falls to be cancelled on grounds of lack of jurisdiction with effect from before the commencement date, regulation 8(2) shall not apply for that purpose.

(3) For the purposes of this regulation—
\begin{enumerate}\item[]
($a$) “departure direction” and “maintenance assessment” have the same meaning as in section 54 of the Act before its amendment by the 2000 Act;

($b$) “revision or supersession” means a revision or supersession of a decision under section 16 or 17 of the Act before its amendment by the 2000 Act; and

($c$) “2000 Act” means the Child Support, Pensions and Social Security Act 2000.
\end{enumerate}

\amendment{
Reg. 10(Z1) inserted (3.3.03) by the Child Support (Transitional Provision) (Miscellaneous Amendments) Regulations 2003 reg. 2(3), (4)(d).
}

\bigskip

Signed 
by authority of the Secretary of State for Social Security.

{\raggedleft
\emph{P.~Hollis}\\*Parliamentary Under-Secretary of State,\\*Department of Social Security

}

18th January 2001

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations amend the Child Support (Information, Evidence and Disclosure) Regulations 1992, S.I.\ 1992/1812 (“the Information Regulations”) and the Child Support (Maintenance Arrangements and Jurisdiction) Regulations 1992, S.I.\ 1992/2645 (“the Jurisdiction Regulations”) mainly consequent upon the introduction of the changes to the child support system made by the Child Support, Pensions and Social Security Act 2000 c.\ 19 (“the 2000 Act”).

Apart from regulation 4 which comes into force on 1st April 2001, these Regulations come into force at different times for different cases according to the dates on which provisions of the Child Support, Pensions and Social Security Act 2000 which are relevant to these Regulations are commenced for different types of cases.

Regulation 2 changes the terminology in the Information Regulations and the Jurisdiction Regulations.

Regulation 3 amends references in the Information Regulations and the Jurisdiction Regulations to the Child Support (Maintenance Assessments and Special Cases) Regulations 1992 and the Child Support (Maintenance Assessment Procedure) Regulations 1992 as these have been revoked and replaced respectively by the Child Support (Maintenance Calculations and Special Cases) Regulations 2000 and the Child Support (Maintenance Calculation Procedure) Regulations 2000.

Regulation 4 transfers the administrative functions of justices' clerks to justices' chief executives in accordance with section 90 (transfer of clerks' functions to chief executives) and 91 (accounting etc functions of chief executives) of, and Schedule 13 to, the Access to Justice Act 1999 c.\ 22.

Regulation 5 amends regulations 1 and 2 of the Information Regulations mainly to adjust the information that can be required so that this is relevant to the changes to the child support system.

Regulations 6 and 7 make amendments consequential on the changes to the child support system to regulations 3, 6 and 9A and omit regulation 4 of the Information Regulations. In particular regulation 6(3) amends regulation 3A of the Information Regulations so that notices will include reference to the information offences created by section 14A of the Child Support Act 1991 c.\ 48 (“the Act”).

Regulation 8 prescribes the companies and bodies based in the United Kingdom that employ someone not habitually resident for the purposes of section 44(2A) of the Act in the United Kingdom. Regulation 8 also makes omissions in regulation 3 of the Jurisdiction Regulations as references to the “effective date” are now contained in the Child Support (Maintenance Calculation Procedure) Regulations 2000.

Regulation 9 amends references in the Jurisdiction Regulations to “cancelling” a maintenance calculation.

Regulation 10 allows the Information Regulations and Jurisdiction Regulations to apply as they were before they were amended in certain cases for transitional purposes.

The impact on business of these Regulations was covered in the Regulatory Impact Assessment (RIA) for the Child Support, Pensions and Social Security Act 2000, in accordance with which, and in consequence of which, these Regulations are made. A copy of that RIA has been placed in the libraries of both Houses of Parliament and can be obtained from the Department of Social Security, Regulatory Impact Unit, Adelphi, 1--11 John Adam Street, London \textsc{\lowercase{WC2N 6HT}}. 

\end{document}