\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 1) Order 2000}

\newcommand\regsnumber{2000/2666}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I. 2000 No. 2666 (C.74)}

\date{Made 27th September 2000}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.57402pt}

\begin{document}

\maketitle

\noindent
The Secretary of State for Social Security, in exercise of the powers conferred upon him by section 86(2) of the Child Support, Pensions and Social Security Act 2000\footnote{\frenchspacing 2000 c. 19.} and of all other powers enabling him in that behalf, hereby makes the following Order: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and interpretation]{Citation and interpretation}

1.---(1)  This Order may be cited as the Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 1) Order 2000.

(2) In this Order, references to “the Act” are references to the Child Support, Pensions and Social Security Act 2000.

\subsection[2. Appointed days]{Appointed days}

2.---(1)  The day appointed for the coming into force of section 41 of the Act (sharing of state scheme rights) is 29th September 2000.

(2) The day appointed for the coming into force of section 72 of the Act (child benefit disregards) is 9th October 2000. 

\bigskip

Signed 
by authority of the Secretary of State for Social Security.

{\raggedleft
\emph{Patricia Hollis}\\*Parliamentary Under-Secretary of State,\\*Department of Social Security

}

27th September 2000

\small

\part{Explanatory Note}

\renewcommand\parthead{--- Explanatory Note}

\subsection*{(This note is not part of the Order)}

This Order provides for the coming into force of sections 41 and 72 of the Child Support, Pensions and Social Security Act 2000 (c. 19).

Section 41 makes further provision for the sharing, on divorce or nullity of marriage, of rights to the additional pension component of a state retirement pension.

Section 72 adds to the list of enactments under which days when a child is absent from his home in residential accommodation are to be disregarded for the purpose of determining entitlement to child benefit.

This Order does not impose any costs on business. 

\end{document}