\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 6) Order 2001}

\newcommand\regsnumber{2001/153}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I. 2001 No. 153 (C.8)}

\date{Made 24th January 2001%\\Laid before Parliament 6th December 2000\\Coming into force as provided in regulation 1(1)
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.57402pt}

\begin{document}

\maketitle

\noindent
The Secretary of State for Social Security, in exercise of the powers conferred upon him by section 86(2) and (3)($a$) of the Child Support, Pensions and Social Security Act 2000\footnote{\frenchspacing 2000 c. 19.} and of all other powers enabling him in that behalf, hereby makes the following Order: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation]{Citation}

1.---(1)  This Order may be cited as the Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 6) Order 2001.

(2) In this Order references to sections and Schedules are references to sections of and Schedules to the Child Support, Pensions and Social Security Act 2000.

\subsection[2. Appointed days]{Appointed days}

2.  The day appointed for the coming into force of—
\begin{enumerate}\item[]
($a$) sections 30, 31, 34 and 35 (and Schedule 4) (state second pension)—
\begin{enumerate}\item[]
(i) for the purposes of making reports and orders under sections 42, 42B and 45A of the Pension Schemes Act 1993\footnote{1993 c.\ 48. Section 42B was inserted by section 137(5) of the Pensions Act 1995 (c.\ 26). Section 45A was inserted by section 138(5) of the Pensions Act 1995 (c.\ 26) and amended by section 34 of the Child Support, Pensions and Social Security Act 2000.} (review, determination and alteration of rebates and rates of contributions and minimum contributions applicable under sections 41, 42 and 45 of that Act), is 25th January 2001,

(ii) for all remaining purposes, is 6th April 2002;
\end{enumerate}

($b$) section 32 (calculation of Category B retirement pension), for all remaining purposes, is 9th April 2001;

($c$) section 33(1) and (2) (revaluation)—
\begin{enumerate}\item[]
(i) for the purposes of an order under section 148A of the Social Security Administration Act 1992\footnote{\frenchspacing 1992 c. 5.} as inserted by section 33(1), is 25th January 2001,

(ii) for all remaining purposes, 6th April 2002;
\end{enumerate}

($d$) section 33(3) and (4), for all remaining purposes, is 25th January 2001;

($e$) Part II of Schedule 9 (repeals), is 8th April 2001.
\end{enumerate}

\bigskip

Signed 
by authority of the Secretary of State for Social Security.

{\raggedleft
\emph{Jeff Rooker}\\*Minister of State,\\*Department of Social Security

}

24th January 2001

\small

\part{Explanatory Note}

\renewcommand\parthead{--- Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

This Order makes further provision for the coming into force of provisions of the Child Support, Pensions and Social Security Act 2000 as follows.

Provisions relating to—
\begin{itemize}
\item    state second pension (sections 30, 31, 34 and 35 and Schedule 4) are brought into force on 25th January 2001 for the purposes of making reports and orders in relation to the review, determination and alteration of rebates and rates of contributions and minimum contributions applicable under Part III of the Pension Schemes Act 1993, and on 6th April 2002 for all remaining purposes;

\item    calculations of Category B retirement pension (section 32) are brought into force on 9th April 2001 for all remaining purposes and related repeal is brought into force on 8th April 2001;

\item    revaluation of earnings threshold and earnings factors—
\begin{itemize}
\item        (section 33(1) and (2)) are brought into force on 25th January 2001 for the purposes of an order under section 148A of the Social Security Administration Act 1992, and on 6th April 2002 for all remaining purposes;

\item        (section 33(3) and (4)) is brought into force on 25th January 2001 for all remaining purposes. 
\end{itemize}
\end{itemize}

The impact on business of the commencement of provisions in the Child Support, Pensions and Social Security Act 2000 is detailed in the Regulatory Impact Assessment (as revised) relating to the Child Support, Pensions and Social Security Bill (which was introduced in the House of Commons on 1st December 1999). A copy of that Assessment has been placed in the libraries of both Houses of Parliament and can be obtained from the Department of Social Security, Regulatory Impact Unit, 3rd Floor, Adelphi, 1--11 John Adam Street, London \textsc{\lowercase{WC2N 6HT}}. 

\end{document}