\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Maintenance and Other Payments Act 2008 (Commencement No.~15) Order 2015}

\newcommand\regsnumber{2015/176}

\title{\regstitle}

\author{S.I.\ 2015 No.\ 176 (C.~10)}

\date{Made
%23rd June 2014\\
%Laid before Parliament
%23rd June 2014\\
%Coming into force
9th February 2015
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.61603pt}

%\hbadness=10000

\begin{document}

\maketitle

%\enlargethispage{\baselineskip}

\noindent
The Secretary of State for Work and Pensions makes the following Order in exercise of the power conferred by section 62(3) of the Child Maintenance and Other Payments Act 2008\footnote{2008 c.~6.}: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation]{Citation}

1.  This Order may be cited as the Child Maintenance and Other Payments Act 2008 (Commencement No.~15) Order 2015.

\subsection[2. Appointed Day]{Appointed Day}

2.  Section 40 of the Child Maintenance and Other Payments Act 2008 (disclosure of information to credit reference agencies)\footnote{Section 40 was amended by S.I.~2012/2007.} comes into force on—
\begin{enumerate}\item[]
($a$) the day after the day on which this Order is made for the purpose only of making regulations; and

($b$) 23rd March 2015 for all other purposes.
\end{enumerate}

\bigskip

\pagebreak[3]

Signed 
by authority of the 
Secretary of State for~Work and~Pensions.
%I concur
%By authority of the Lord Chancellor

{\raggedleft
\emph{Steve Webb}\\*
%Secretary
Minister
%Parliamentary Under Secretary 
of State\\*Department 
for~Work and~Pensions

}

9th February 2015

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Order)}

This Order brings into force section 40 of the Child Maintenance and Other Payments Act 2008 (c.~6) on the day after the day on which this Order is made for the purpose of making regulations and on 23rd March 2015 for all other purposes. Section 40 inserts new section 49D into the Child Support Act 1991 (c.~48). Section 49D allows the Secretary of State to disclose information relating to persons who are liable to pay Child Support Maintenance to credit reference agencies. It will only allow the Secretary of State to disclose information relating to such a person where that person has given their consent to the disclosure or is subject to a liability order. Section 49D enables the Secretary of State to make regulations prescribing the information that may be disclosed. 

\end{document}