\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support Information Regulations 2008}

\newcommand\regsnumber{2008/2551}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2008 No.\ 2551}

\date{Made
26th September 2008\\
Laid before Parliament
2nd October 2008\\
Coming into force
27th October 2008
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{42.11603pt}

%\hbadness=10000

\begin{document}

\maketitle

\noindent
The Secretary of State, in exercise of the powers conferred by sections 4(4), 7(5), 14(1) and (3), 50(5), 51(1), 52(4), 54 and 57(1) and (2) of, and paragraph~16(10) of Schedule~1 to, the Child Support Act 1991\footnote{1991 c.~48. Section 54 is cited because of the meaning given to the word “prescribed”.} makes the following Regulations: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\section[Part~I --- General]{Part~I\\*General}

\renewcommand\parthead{--- Part~I}

\subsection[1. Citation and commencement]{Citation and commencement}

1.  These Regulations may be cited as the Child Support Information Regulations 2008 and come into force on 27th October 2008.

\bigskip

\subsection[2. Interpretation]{Interpretation}

2.---(1)  In these Regulations—
\begin{enumerate}\item[]
“the 1991 Act” means the Child Support Act 1991;

“local authority” means, in relation to England, a county council, a district council, a London borough council, the Common Council of the City of London or the Council of the Isles of Scilly and, in relation to Wales, a county council or a county borough council and, in relation to Scotland, a council constituted under section~2 of the Local Government etc.\ (Scotland) Act 1994\footnote{1994 c.~39.};

\begin{sloppypar}
[\emph{2003 scheme}] “Maintenance Calculation Procedure Regulations” means the Child Support (Maintenance Calculation Procedure) Regulations 2000\footnote{S.I.~2001/157.}.
\end{sloppypar}

% Definition substituted (10.12.12 for 2012 scheme cases only) by SI 2012/2785 reg 8(2)(a)
[\emph{2012 scheme}] “the Maintenance Calculation Regulations” means the Child Support Maintenance Calculation Regulations 2012\footnote{S.I.~2012/2677.}.
\end{enumerate}

% Reg 2(2), (3) omitted (10.12.12 for 2012 scheme cases only) by SI 2012/2785 reg 8(2)(b)
(2) [\emph{not 2012 scheme}] These Regulations apply to a 1993 scheme case in the same way as they apply to a 2003 scheme case and any references to expressions in the 1991 Act (including “non-resident parent” and “maintenance calculation”) or to regulations~made under that Act are to be read, in relation to a 1993 scheme case, with the necessary modifications.

(3) [\emph{not 2012 scheme}] In paragraph~(2)—
\begin{enumerate}\item[]
($a$) “2003 scheme case” means a case in respect of which the provisions of the Child Support, Pensions and Social Security Act 2000\footnote{2000 c.~19.} have been brought into force in accordance with article~3 of the Child Support, Pensions, and Social Security Act 2000 (Commencement No.~12) Order 2003\footnote{S.I.~2003/192.}; and

($b$) “1993 scheme case” means a case in respect of which those provisions have not been brought into force.
\end{enumerate}

(4) References in these Regulations to a non-resident parent are to a person who is the non-resident parent in relation to an application for a maintenance calculation or in relation to a maintenance calculation that is or has been in force and includes a person treated as a non-resident parent by virtue of regulations~made under section~42 of the 1991 Act.

\amendment{
Definition of ``Maintenance Calculation Procedure Regulations'' in reg.~2(1) substituted and reg.~2(2), (3) omitted (10.12.12 for 2012 scheme cases only) by the Child Support (Meaning of Child and New Calculation Rules) (Consequential and Miscellaneous Amendment) Regulations 2012 reg.~8(2).
}

\section[Part~II --- Duty to provide information]{Part~II\\*Duty to provide information}

\renewcommand\parthead{--- Part~II}

\subsection[3. Information from the applicant]{Information from the applicant}

3.---(1)  A person who has made an application for a maintenance calculation under section~4 of the 1991 Act must furnish such information as the 
%Commission 
Secretary of State  % Words substituted (1.8.12) by SI 2012/2007 Sch para 116(s)
requires to enable—
\begin{enumerate}\item[]
($a$) the non-resident parent to be identified or traced (where that is necessary);

($b$) the amount of child support maintenance payable by the non-resident parent to be calculated; or

($c$) that amount to be recovered from the non-resident parent.
\end{enumerate}

(2) A qualifying child who has made an application for a maintenance calculation under section~7 of the 1991 Act (right of a child in Scotland to apply for a calculation) must furnish such information as the 
%Commission 
Secretary of State  % Words substituted (1.8.12) by SI 2012/2007 Sch para 116(s)
requires for any of the purposes, except enabling the non-resident parent to be identified, set out in paragraph~(1).

\amendment{
Words substituted in reg.~3 (1.8.12) by the Public Bodies (Child Maintenance and Enforcement Commission: Abolition and Transfer of Functions) Order 2012 Sch. para.~116(2).
}

\subsection[4. Information from other persons]{Information from other persons}

4.---(1)  The persons listed in paragraph~(2) must furnish such information or evidence as is required by the 
%Commission 
Secretary of State  % Words substituted (1.8.12) by SI 2012/2007 Sch para 116(3)
and is needed—
\begin{enumerate}\item[]
($a$) for the determination of any application made under the 1991 Act or any question arising in connection with such an application;

($b$) for the making of any decision, or in connection with the imposition of any condition or requirement, under that Act; or

($c$) in connection with the collection or enforcement of child support or other maintenance under that Act.
\end{enumerate}

(2) The persons required to furnish information or evidence are—
\begin{enumerate}\item[]
($a$) subject to regulation~5, the non-resident parent;

($b$) a current or previous employer of the non-resident parent;

($c$) a person for whom the non-resident parent is providing or has provided services under a contract for services;

($d$) a person who acts or has acted as an accountant for the non-resident parent;

($e$) a person, other than the applicant, who provides day to day care for a child in respect of whom an application for a maintenance calculation has been made or in respect of whom a maintenance calculation is or has been in force;

($f$) a credit reference agency within the meaning given by the Consumer Credit Act 1974\footnote{1974 c.~39.};

($g$) a local authority in whose area the non-resident parent or the person with care resides or has resided;

($h$) persons employed in the service of the Crown or otherwise in the discharge of Crown functions—
\begin{enumerate}\item[]
(i) under the Road Traffic (Northern Ireland) Order 1981\footnote{S.I.~1981/154 (N.I.~1).}, sections~97 to 99A of the Road Traffic Act 1988\footnote{1988 c.~52. Sections~97 to 99A were amended by the Road Traffic (Driver Licensing and Information Systems) Act 1989 (c.~22), the Road Traffic Act 1991 (c.~40), the Driving Licence (Community Driving Licence) Regulations 1990 S.I.~1990/144, the Driving Licence (Community Driving Licence) Regulations 1996 S.I.~1996/1974, the Driving Licence (Community Driving Licence) Regulations 1998 S.I.~1998/1420 and the Transport Act 2000 (c.~38).} or Part~II of the Vehicle Excise and Registration Act 1994\footnote{1994 c.~22. Part~II was amended by the Finance Act 1995 (c.~4), the Finance Act 1996 (c.~8), the Finance Act 1997 (c.~16), the Finance (No.~2) Act 1997 (c.~58), the Finance Act 1998 (c.~36), the Vehicles (Crime) Act 2001 (c.~3), the Finance Act 2002 (c.~23), the Finance Act 2003 (c.~14) and the Serious Organised Crime and Police Act 2005 (c.~15).}; or

(ii) under the Prison Act 1952\footnote{15 \& 16 Geo.~6 \& 1 Eliz.~2 c.~52.}, the Prison Act (Northern Ireland) 1953\footnote{1953 c.~18 (N.I.).} or the Prisons (Scotland) Act 1989\footnote{1989 c.~45.};
\end{enumerate}

($i$) a person who, in the course of business, may lawfully accept deposits in the United Kingdom;

($j$) a person who, within the meaning of the Electricity Act 1989\footnote{1989 c.~29.}, distributes or supplies electricity;

($k$) a person who is the holder of a licence under section~7 of the Gas Act 1986\footnote{1986 c.~44.} to convey gas through pipes or the holder of a licence under section~7A(1) of that Act to supply gas through pipes.
\end{enumerate}

(3) The persons mentioned in paragraph~(2)($b$)  and ($c$)  include persons employed in the service of the Crown or otherwise in the discharge of Crown functions.

\amendment{
Words substituted in reg.~4(1) (1.8.12) by the Public Bodies (Child Maintenance and Enforcement Commission: Abolition and Transfer of Functions) Order 2012 Sch. para.~116(3).
}

\subsection[5. Information from persons denying parentage]{Information from persons denying parentage}

5.  Where a person is alleged to be, but denies being, the parent of a child in respect of whom an application for a maintenance calculation has been made, unless the case falls within one of those set out in section~26(2) of the 1991 Act (disputes about parentage), the information or evidence which that person may be required to furnish is limited to what is needed for the purposes of enabling the non-resident parent to be identified or to enable a decision to be made as to whether the 
%Commission 
Secretary of State  % Words substituted (1.8.12) by SI 2012/2007 Sch para 116(4)
has jurisdiction under section~44 to make a maintenance calculation.

\amendment{
Words substituted in reg.~5 (1.8.12) by the Public Bodies (Child Maintenance and Enforcement Commission: Abolition and Transfer of Functions) Order 2012 Sch. para.~116(4).
}

\subsection[6. Information from a court]{Information from a court}

6.---(1)  Where there is or has been a relevant court order, or there have been proceedings in which such an order was sought or where such proceedings are pending, the persons mentioned in paragraph~(2) must furnish such information or evidence in relation to that order or those proceedings as is required by the 
%Commission 
Secretary of State  % Words substituted (1.8.12) by SI 2012/2007 Sch para 116(5)
and is needed for any of the purposes mentioned in regulation~4(1).

(2) The persons who are required to furnish information or evidence are—
\begin{enumerate}\item[]
($a$) in England and Wales—
\begin{enumerate}\item[]
(i) in relation to the High Court, the senior district judge of the principal registry of the Family Division or, where proceedings were instituted in a district registry, the district judge;

%(ii) in relation to a county court, the proper officer of that court within the meaning of Order 1, Rule 3 of the County Courts Rules 1981\footnote{S.I.~1981/1687, to which there are amendments not relevant to these Regulations.};
%
%(iii) in relation to a magistrates’ court, the designated officer for that court;

% Reg 6(2)(a)(ii) substituted for reg 6(2)(a)(ii), (iii) by SI 2014/879 art 121
(ii) in relation to the family court, a judge of that court;
\end{enumerate}

($b$) in Scotland—
\begin{enumerate}\item[]
(i) in relation to the Court of Session, the Deputy Principal Clerk of Session;

(ii) in relation to a sheriff court, the sheriff clerk.
\end{enumerate}
\end{enumerate}

(3) In paragraph~(1) “relevant court order” means—
\begin{enumerate}\item[]
($a$) an order as to periodical or capital provision or as to variation of property rights made under an enactment specified in paragraphs~($a$)  to ($ea$)  of section~8(11) of the 1991 Act or prescribed under section~8(11) of that Act in relation to a person who has made an application for a maintenance calculation or a qualifying child, person with care or non-resident parent in relation to such an application;

($b$) an order under Part~II of the Children Act 1989\footnote{1989 c.~41.} (orders with respect to children in family proceedings) in relation to a qualifying child or, in Scotland, an order under section~3 of the Law Reform (Parent and Child) (Scotland) Act 1986\footnote{1986 c.~9.} or a decree of declarator under section~7 of that Act in relation to a qualifying child.
\end{enumerate}

\amendment{
Words substituted in reg.~6(1) (1.8.12) by the Public Bodies (Child Maintenance and Enforcement Commission: Abolition and Transfer of Functions) Order 2012 Sch. para.~116(5).

Reg. 6(2)(a)(ii) substituted for reg. 6(2)(a)(ii), (iii) (22.4.14) by the Crime and Courts Act 2013 (Family Court: Consequential Provision) (No. 2) Order 2014 art. 121.
}

\subsection[7. Duty of persons from whom information requested]{Duty of persons from whom information requested}

7.---(1)  Persons required to furnish information or evidence under regulations~3 to 6 must furnish the information or evidence requested if it is in their possession or they can reasonably be expected to acquire it.

(2) The information must be furnished as soon as is reasonably practicable in the particular circumstances of the case.

% Reg 7(3) omitted (10.12.12 for 2012 scheme cases only) by SI 2012/2785 reg 8(3)
(3) [\emph{not 2012 scheme}] Paragraph (2) is subject to regulation~3(4) of the Maintenance Calculation Procedure Regulations (which provides for a time limit where additional information is requested in relation to an ineffective application).

\amendment{
Reg.~7(3) omitted (10.12.12 for 2012 scheme cases only) by the Child Support (Meaning of Child and New Calculation Rules) (Consequential and Miscellaneous Amendment) Regulations 2012 reg.~8(3).
}

\subsection[8. 
%Commission 
Secretary of State  % Words substituted (1.8.12) by SI 2012/2007 Sch para 116(6)
to warn of consequences of failing to provide information or providing false information]{%
%Commission 
Secretary of State  % Words substituted (1.8.12) by SI 2012/2007 Sch para 116(6)
to warn of consequences of failing to provide information or providing false information}

8.  A request by the 
%Commission 
Secretary of State  % Words substituted (1.8.12) by SI 2012/2007 Sch para 116(6)
under regulations~3 to 6 must set out the possible consequences of failure to provide the information or evidence, including details of the offences provided for in section~14A of the 1991 Act\footnote{Section 14A is inserted in to the Act by section~13 of the Child Support, Pensions and Social Security Act 2000.} for failing to provide, or providing false, information.

\amendment{
Words substituted in reg.~8 and heading (1.8.12) by the Public Bodies (Child Maintenance and Enforcement Commission: Abolition and Transfer of Functions) Order 2012 Sch. para. 116(6).
}

\subsection[9. Duty to notify change of address]{Duty to notify change of address}

9.  Persons who are liable to make payments of child support maintenance must, if they change their address, notify the 
%Commission 
Secretary of State  % Words substituted (1.8.12) by SI 2012/2007 Sch para 116(7)
of their new address within 7 days of the change.

\amendment{
Words substituted in reg.~9 (1.8.12) by the Public Bodies (Child Maintenance and Enforcement Commission: Abolition and Transfer of Functions) Order 2012 Sch. para.~116(7).
}

% Reg 9A inserted (10.12.12 for 2012 scheme cases only) by SI 2012/2785 reg 8(4)
\subsection[9A. Duty to notify increase in current income]{Duty to notify increase in current income\\*\emph{2012 scheme only}}

9A.---(1)  In a case falling within paragraphs (2) or (3), the Secretary of State may notify the non-resident parent that that parent is required to notify the Secretary of State of any relevant change of circumstances in relation to that income.

(2) A case falls within this paragraph if, in relation to a maintenance calculation in force—
\begin{enumerate}\item[]
($a$) gross weekly income is determined by reference to the non-resident parent’s current income as an employee or officeholder (in accordance with regulation 38 of the Maintenance Calculation Regulations); and

($b$) paragraph 5($b$)  of Schedule 1 to the 1991 Act (nil rate) does not apply.
\end{enumerate}

(3) A case falls within this paragraph if, in relation to a maintenance calculation in force—
\begin{enumerate}\item[]
($a$) gross weekly income is determined by reference to the non-resident parent’s current income (in accordance with regulation 37 of the Maintenance Calculation Regulations); and

($b$) paragraph 5($b$)  of Schedule 1 to the 1991 Act applies (nil rate).
\end{enumerate}

(4) A notification by the Secretary of State under paragraph~(1) must be in writing.

(5) Where a relevant change of circumstances occurs after the non-resident parent has been notified of a requirement under paragraph~(1), the non-resident parent must notify the Secretary of State of that change—
\begin{enumerate}\item[]
($a$) within fourteen days beginning with the day on which the change occurs; or

($b$) within such other period as the Secretary of State has specified in the notification.
\end{enumerate}

(6) For the purposes of a case falling within paragraph (2), a relevant change of circumstances occurs where—
\begin{enumerate}\item[]
($a$) the non-resident parent—
\begin{enumerate}\item[]
(i) commences a new employment or office; or

(ii) in relation to an existing employment or office, commences a new rate of remuneration or a new working pattern,
\end{enumerate}
and could reasonably be expected to know that would result in an increased liability under the maintenance calculation in force if reported to the Secretary of State; or

($b$) the non-resident parent receives from their employment or office the following number of consecutive payments, each of which (if it were taken as a weekly average) exceeds the gross weekly income taken into account in the maintenance calculation in force by 25\% or more—
\begin{enumerate}\item[]
(i) five payments, in the case of a non-resident parent paid weekly;

(ii) three payments, in the case of a non-resident parent paid fortnightly;

(iii) two payments, in the case of a non-resident parent paid four weekly or monthly.
\end{enumerate}
\end{enumerate}

(7) The payments referred to in paragraph (6)($b$)  are the gross remuneration from the employment or office in question less any pension contributions deducted under net pay arrangements.

(8) In paragraph (7) “net pay arrangements” means arrangements for relief in respect of pension contributions under section~193 of the Finance Act 2004\footnote{2004 c. 12.}.

(9) For the purposes of a case falling within paragraph (3), a relevant change of circumstances occurs where the non-resident parent’s income increases to a gross weekly income of 
£5 
%£7  % Figure substituted (prosp for 2012 scheme cases only) by SI 2013/1654 reg 4
or more.

(10) For the purposes of paragraph (9), gross weekly income is to be calculated in accordance with regulation 45(2) of the Maintenance Calculation Regulations.

\amendment{
Reg.~9A inserted (10.12.12 for 2012 scheme cases only) by the Child Support (Meaning of Child and New Calculation Rules) (Consequential and Miscellaneous Amendment) Regulations 2012 reg.~8(4).

Figure substituted in reg.~9A(9) (prosp. for 2012 scheme case only) by the Child Support and Claims and Payments (Miscellaneous Amendments and Change to the Minimum Amount of Liability) Regulations 2013 reg.~4.
}

\subsection[10. Continuing duty of person with care]{Continuing duty of person with care}

\looseness=1
10.  Where a person with care with respect to whom a maintenance calculation has been made believes that, by virtue of section~44 or 55 of, or paragraph~16 of Schedule~1 to, the 1991 Act, the calculation has ceased to have effect, that person must, as soon as is reasonably practicable, inform the 
%Commission 
Secretary of State  % Words substituted (1.8.12) by SI 2012/2007 Sch para 116(8)
of that belief, and of the reasons for it, and must provide such other information as the 
%Commission 
Secretary of State  % Words substituted (1.8.12) by SI 2012/2007 Sch para 116(8)
may reasonably require, with a view to assisting the 
%Commission 
Secretary of State  % Words substituted (1.8.12) by SI 2012/2007 Sch para 116(8)
in determining whether the calculation has ceased to have effect.

\amendment{
Words substituted in reg.~10 (1.8.12) by the Public Bodies (Child Maintenance and Enforcement Commission: Abolition and Transfer of Functions) Order 2012 Sch. para.~116(8).
}

\subsection[11. Powers of inspectors in relation to Crown premises]{Powers of inspectors in relation to Crown premises}

11.  Subject to Her Majesty not being in residence, an inspector appointed under section~15 of the 1991 Act may enter any Crown premises for the purposes of exercising any powers conferred by that section.

\section[Part III --- Disclosure of information]{Part III\\*Disclosure of information}

\renewcommand\parthead{--- Part~III}

\subsection[12. Disclosure of information to a court or tribunal]{Disclosure of information to a court or tribunal}

12.---(1)  The 
%Commission 
Secretary of State  % Words substituted (1.8.12) by SI 2012/2007 Sch para 116(9)
may disclose any information held for the purposes of the 1991 Act to—
\begin{enumerate}\item[]
($a$) a court;

($b$) any tribunal or other body or person mentioned in the 1991 Act;

($c$) a person with a right of appeal under the 1991 Act to 
%an appeal tribunal
the First-tier Tribunal%  % Words substituted (3.11.08) by SI 2008/2683 Sch 1 para 346
,
\end{enumerate}
where such disclosure is made for the purposes of any proceedings before any of those bodies relating to the 1991 Act, the benefit Acts, the Jobseekers Act 1995\footnote{1995 c.~18.} or Part~I of the Welfare Reform Act 2007\footnote{2007 c.~5.}.

(2) For the purposes of this regulation~“proceedings” includes the determination of an application referred to 
%an appeal tribunal
the First-tier Tribunal  % Words substituted (3.11.08) by SI 2008/2683 Sch 1 para 346
under section~28D(1)($b$)  of the 1991 Act.

(3) The 
%Commission 
Secretary of State  % Words substituted (1.8.12) by SI 2012/2007 Sch para 116(9)
may disclose information held for the purposes of the 1991 Act to a court in any case where—
\begin{enumerate}\item[]
($a$) that court has exercised any power it has to make, vary or revive a maintenance order or to vary a maintenance agreement; and

($b$) such disclosure is made for the purposes of any proceedings before that court in relation to that maintenance order or that maintenance agreement or for the purposes of any matters arising out of those proceedings.
\end{enumerate}

\amendment{
Words substituted in reg.~12(1)(c), (2) (3.11.08) by the Tribunals, Courts and Enforcement Act 2007 (Transitional and Consequential Provisions) Order 2008 Sch.~1 para.~346.

Words substituted in reg.~12(1), (3) (1.8.12) by the Public Bodies (Child Maintenance and Enforcement Commission: Abolition and Transfer of Functions) Order 2012 Sch. para.~116(9).
}

\subsection[13. Disclosure of information to other persons]{Disclosure of information to other persons}

13.---(1)  The 
%Commission 
Secretary of State  % Words substituted (1.8.12) by SI 2012/2007 Sch para 116(10)(a)
may disclose information held for the purposes of the 1991 Act relating to one party to a maintenance calculation to another party to that calculation where, in the opinion of the 
%Commission 
Secretary of State%  % Words substituted (1.8.12) by SI 2012/2007 Sch para 116(10)(a)
, such information is essential to inform the party to whom it would be given as to—
\begin{enumerate}\item[]
($a$) why 
%it 
the Secretary of State  % Words substituted (1.8.12) by SI 2012/2007 Sch para 116(10)(a)
has decided not to make a maintenance calculation in response to an application made under section~4 or 7 of the 1991 Act, or an application for a revision under section~16 of that Act or a decision under section~17 of that Act superseding an earlier decision has been rejected;

($b$) why, although an application for a maintenance calculation referred to in sub-paragraph~($a$)  has been made, that calculation cannot, at the time in question, be proceeded with;

($c$) why a maintenance calculation has ceased to have effect;

($d$) [\emph{2003 scheme}] how a maintenance calculation has been calculated, in so far as the matter has not been dealt with by the notification given under regulation~23 of the Maintenance Calculation Procedure Regulations;

($d$) [\emph{2012 scheme}] how a maintenance calculation has been calculated, in so far as the matter has not been dealt with by the notification given under 
%regulation~23 of the Maintenance Calculation Procedure Regulations
regulation 25 of the Maintenance Calculation Regulations (notification of a maintenance calculation)%  % Words substituted (10.12.12 for 2012 scheme cases only) by SI 2012/2785 reg 8(5)(a)
;

($e$) why a decision has been made not to arrange for, or to cease, collection of any child support maintenance under section~29 of the 1991 Act;

($f$) why a particular method of enforcement under the 1991 Act of an amount due under a maintenance calculation has been adopted in a particular case; 
%or  % Word omitted (10.12.12) by SI 2012/3002 reg 3(2)

($g$) why a decision has been made not to enforce, or to cease to enforce, under the 1991 Act the amount due under a maintenance calculation;

% Reg 30(1)(h), (i) inserted (10.12.12) by SI 2012/3002 reg 3(3)
($h$) why it was decided, in relation to any arrears of child support maintenance, not to accept payment in part in satisfaction of liability for the whole under section 41D(1) of the 1991 Act; or

($i$) why it was decided not to extinguish liability in respect of arrears of child support maintenance under section 41E(1) of the 1991 Act.
\end{enumerate}

(2) For the purposes of this regulation, “party to a maintenance calculation” means—
\begin{enumerate}\item[]
($a$) a person who has made an application for a maintenance calculation;

($b$) a qualifying child, person with care or non-resident parent in respect of whom an application for a maintenance calculation has been made;

% Reg 13(2)(c) omitted (28.10.13) by SI 2013/2380 reg 7(3)
%($c$) [\emph{2003 scheme}] a person appointed under regulation~34 of the Social Security and Child Support (Decisions and Appeals) Regulations 1999\footnote{S.I.~1999/991.} (death of party to an appeal);

%($c$) [\emph{2012 scheme}] a person appointed under 
%%regulation~34 of the Social Security and Child Support (Decisions and Appeals) Regulations 1999\footnote{S.I.~1999/991.} 
%paragraph 4 of the Schedule to the Maintenance Calculation Regulations  % Words substituted (10.12.12 for 2012 scheme cases only) by SI 2012/2785 reg 8(5)(b)
%(death of party to an appeal);

($d$) the personal representative of a person mentioned in sub-\hspace{0pt}paragraph~($a$)  or ($b$)  where—
\begin{enumerate}\item[]
(i) a revision, supersession or appeal was pending at the date of death of that person and the personal representative is dealing with that revision, supersession or appeal on behalf of that person; or

(ii) an application for a variation has been made but not determined at the date of death of that person and the personal representative is dealing on behalf of that person with any matters arising in connection with such an application.
\end{enumerate}
\end{enumerate}

(3) Any application for information under this regulation~shall be made to the 
%Commission 
Secretary of State  % Words substituted (1.8.12) by SI 2012/2007 Sch para 116(10)(b)
in writing setting out the reasons for the application.

\looseness=1
(4) Except where a person gives written permission to the 
%Commission 
Secretary of State  % Words substituted (1.8.12) by SI 2012/2007 Sch para 116(10)(b)
that the information mentioned in sub-paragraphs~($a$)  and ($b$)  below in relation to that person may be conveyed to other persons, any information given under the provisions of paragraph~(1) shall not contain—
\begin{enumerate}\item[]
\looseness=1
($a$) the address of any person other than the recipient of the information in question (other than the address of the office of the officer concerned who is exercising functions of the 
%Commission 
Secretary of State  % Words substituted (1.8.12) by SI 2012/2007 Sch para 116(10)(b)
under the 1991 Act) or any other information the use of which could reasonably be expected to lead to any such person being located;

($b$) any other information the use of which could reasonably be expected to lead to any person, other than a party to the maintenance calculation, being identified.
\end{enumerate}

\amendment{
Words substituted in reg.~13(1), (3), (4) (1.8.12) by the Public Bodies (Child Maintenance and Enforcement Commission: Abolition and Transfer of Functions) Order 2012 Sch. para.~116(10).

Words substituted in reg.~13(1)(d), (2)(c) (10.12.12 for 2012 scheme cases only) by the Child Support (Meaning of Child and New Calculation Rules) (Consequential and Miscellaneous Amendment) Regulations 2012 reg.~8(5).

Reg.~13(1)(h), (i) inserted (10.12.12) by the Child Support Management of Payments and Arrears (Amendment) Regulations 2012 reg.~3.

Reg. 13(2)(c) omitted (28.10.13) by the Social Security, Child Support, Vaccine Damage and Other Payments (Decisions and Appeals) (Amendment) Regulations 2013 reg.~7(3) (subject to transitional provisions in reg.~8(1)).
}

%\subsection[14. Employment to which section~50 of the 1991 Act applies]{Employment to which section~50 of the 1991 Act applies}
%
%14.  Section 50 of the 1991 Act (unauthorised disclosure of information) applies to the following kinds of employment, in addition to those specified in subsection~(5) of that section—
%\begin{enumerate}\item[]
%($a$) the Comptroller and Auditor General;
%
%($b$) any member of staff of the National Audit Office or any other person who carries out administrative work of that Office, or who provides or is employed in the provision of, services to it;
%
%($c$) the Parliamentary Commissioner for Administration;
%
%($d$) the Health Service Commissioner for Wales;
%
%($e$) the Health Service Commissioner for Scotland;
%
%($f$) any officer of any of the Commissioners referred to in paragraphs~($c$)  to ($e$)  above.
%\end{enumerate}

% Reg 14 substituted (6.4.09) by SI 2009/396 reg 6
\subsection[14. Employment to which section~50 of the 1991 Act applies]{Employment to which section~50 of the 1991 Act applies}

\looseness=1
14.---(1)  For~the purposes of section~50(1A) of the 1991 Act, employment as any member of a committee or~sub-committee established under paragraph~11 of Schedule~1 to the Child Maintenance and Other Payments Act 2008 is prescribed as a kind of employment to which section~50(1) of that Act applies.

(2) For~the purposes of section~50(1C) of the 1991 Act, the following kinds of employment are prescribed as kinds of employment to which section~50(1B) of that Act applies—
\begin{enumerate}\item[]
($a$) the Comptroller and Auditor~General;

% Reg 14(2)(aa) inserted by SI 2012/725 art 2(10)(a)
\looseness=1
($aa$) a member or employee of the National Audit Office or any other person who carries out administrative work of the Office, or who provides, or is employed in the provision of, services to it;

%($b$) any member of staff of the National Audit Office or~any other person who carries out administrative work of that Office or~who provides, or~is employed in the provision of, services to it;

% Reg 14(2)(b) substituted by SI 2012/725 art 2(10)(b)
\looseness=1
($b$) any member of the staff of the National Audit Office that was established by section 3 of the National Audit Act 1983 or any other person who carried out administrative work of the Office, or who provided, or was employed in the provision of, services to it;

($c$) the Parliamentary Commissioner for~Administration;

($d$) the Health Service Commissioner for~Wales;

($e$) the Health Service Commissioner for~Scotland;

($f$) any officer of any of the Commissioners referred to in paragraphs~($c$)  to ($e$)    above.
\end{enumerate}

\amendment{
Reg.~14 substituted (6.4.09) by the Child Support (Miscellaneous Amendments) Regulations 2009 reg.~6.

Reg. 14(2)(aa) inserted and reg. 14(2)(b) substituted (1.4.12) by the Budget Responsibility and National Audit Act 2011 (Consequential Amendments) Order 2012 art. 2(10).
}

% Reg 14A inserted by SI 2015/338 reg 7
\subsection[14A. Disclosure of information to credit reference agencies]{Disclosure of information to credit reference agencies}

14A.—(1) The information prescribed for the purposes of section~49D(2)($c$)  of the 1991 Act (disclosure of information to credit reference agencies) is, in relation to the person referred to in section 49D(2)($b$)  of that Act—
\begin{enumerate}\item[]
($a$) the person’s name, last known or notified address and date of birth;

($b$) the reference number used by the Secretary of State to identify the person’s case;

($c$) the date on which any liability order in force against the person was made;

($d$) the amount in respect of which that liability order was made;

($e$) the address stated in that liability order, if different from the person’s last known or notified address;

($f$) that the amount referred to in sub-paragraph ($d$)  has been paid and the date on which that amount was paid;

($g$) that a liability order made against the person has been set aside or quashed.
\end{enumerate}

(2) The Secretary of State must send a written notice by post to the person’s last known or notified address at least twenty-one days prior to supplying the information in paragraph (1)($a$)  to ($e$)  to a credit reference agency.

(3) The requirement in paragraph (2) does not apply where the person cannot be traced.

\looseness=-1
(4) The written notice must state that the Secretary of State intends to supply information in relation to the non-resident parent to a credit reference agency.

\amendment{
Reg. 14A inserted (23.3.15) by the Child Support (Miscellaneous and Consequential Amendments) Regulations 2015 reg. 7.
}

\section[Part IV --- Miscellaneous]{Part IV\\*Miscellaneous}

\renewcommand\parthead{--- Part~IV}

\subsection[15. Revocation and saving]{Revocation and saving}

15.---(1)  The Child Support (Information, Evidence and Disclosure) Regulations 1992\footnote{S.I.~1992/1812.} are revoked.

(2) The revocation of those Regulations shall not affect any request for information made before 27th October 2008 and those Regulations shall remain in force for the purposes of any proceedings under section~14A of the 1991 Act (information offences) in relation to any such request.

\amendment{
Reg.~16 revoked (1.8.12) by the Public Bodies (Child Maintenance and Enforcement Commission: Abolition and Transfer of Functions) Order 2012 Sch. para.~116(11).
}

% Reg  16 revoked (1.8.12) by SI 2012/2007 Sch para 116(11)
%\subsection[16. Transitional provisions in relation to transfer of child support functions]{Transitional provisions in relation to transfer of child support functions}
%
%16.  During the period from the coming into force of these Regulations to the date on which section~13 of the Child Maintenance and Other Payments Act 2008\footnote{2008 c.~6.} (transfer of child support functions to the Commission) comes into force, any reference in these Regulations to the Commission is to be read as a reference to the Secretary of State. 

\bigskip

Signed 
by authority of the 
Secretary of State for~Work and Pensions.
%I concur

{\raggedleft
\emph{Stephen C.~Timms}\\*
Minister
%Parliamentary Under-Secretary 
of State,\\*Department for~Work and Pensions

}

26th September 2008

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations provide for the furnishing of information or evidence required by the Child Maintenance and Enforcement Commission for the purpose of their functions under the Child Support Act 1991 (“the 1991 Act”). They also provide for the disclosure by the Commission of information held for the purpose of the 1991 Act. These Regulations replace the Child Support (Information, Evidence and Disclosure) Regulations 1992.

Part~II relates to the duty to furnish information or evidence:
\begin{enumerate}\item[]
Regulations 3 to 6 impose a duty to furnish information required by the Commission on the applicant, on other persons (including the non-resident parent and a person alleged to be a non-resident parent) and on the courts. Regulation~7 deals with the obligation of persons from whom information is requested. Regulation~8 requires a request under regulations~3 to 6 to contain a warning as to the consequences of failure to comply.

Regulations 9 and 10 impose obligations to report matters to the Commission. Regulation~9 requires persons liable to pay child support maintenance to notify a change of address. Regulation~10 requires persons with care to inform the Commission where they believe that the maintenance calculation has ceased to have effect.

Regulation~11 gives inspectors appointed under the 1991 Act a right of entry to Crown premises.
\end{enumerate}

Part~III deals with disclosure of information:
\begin{enumerate}\item[]
Regulation~12 provides for disclosure of information by the Commission to a court or tribunal and regulation~13 provides for disclosure of information to the parties to a maintenance calculation.

Regulation~14 extends the application of section~50 of the 1991 Act, which creates an offence for unauthorised disclosure of information, to the employments listed in that regulation.
\end{enumerate}

Part~IV contains miscellaneous provisions.
\begin{enumerate}\item[]
Regulation~15 revokes the Child Support (Information, Evidence and Disclosure) Regulations 1992 with a saving provision in relation to outstanding requests for information.

Regulation~16 is a transitional provision which enables references to the Commission to be read as references to the Secretary of State pending the transfer of child support functions to the Commission.
\end{enumerate}

An assessment of the impact of these Regulations on the private and voluntary sectors has been made. Copies of this impact assessment are available in the libraries of both Houses of Parliament. Copies may also be obtained from the Better Regulation~Unit of the Department for Work and Pensions, level 4, The Adelphi, 1--11 John Adam Street, London \textsc{\lowercase{WC2N 6HT}}, or from the DWP website: \url{http://www.dwp.gov.uk/resourcecentre/ria.asp}. 

\end{document}