\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Social Security (Miscellaneous Amendments) (No.~4) Regulations 2007}

\newcommand\regsnumber{2007/2470}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and~Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2007 No.\ 2470}

\date{Made
22nd August 2007\\
Laid before Parliament
28th August 2007\\
Coming into~force
24th September 2007
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.61603pt}

%\hbadness=10000

\begin{document}

\maketitle

\noindent
The Secretary of State for~Work and~Pensions makes the following Regulations in exercise of the powers conferred by sections 1(1), 5(1)($a$), ($b$), ($i$),~($p$)  and~($q$),~189(1), (3), (4) and~(6) and~191 of the Social Security Administration Act 1992\footnote{1992 c.~5. Section 189(1) was amended by the Social Security Act 1998 (c.~14), Schedule~7, paragraph~109($a$)  and Schedule~8, by the Social Security Contributions (Transfer of functions, etc.)\ Act 1999 (c.~2), Schedule~3, paragraph~57(1) and (2) and by the Tax Credits Act 2002 (c.~21), Schedule~6. Section 191 is cited for~the meaning ascribed to~the word “prescribe”.}, sections 9(1)($a$)  and~(4), 10(3) and~(6), 79(1), (3), (4) and~(7) and~84 of the Social Security Act 1998\footnote{1998 c.~14. Section 79(1) was amended by the Tax Credits Act 2002 (c.~21), Schedule 4, paragraphs 12, 13(1) and (2). Section 84 is cited for~the meaning ascribed to~the word “prescribe”.} and~paragraphs 4(6), 20(1)($b$)  and~23(1) of Schedule~7 to~the Child Support, Pensions and~Social Security Act 2000\footnote{2000 c.~19. Schedule 7, paragraph~23(1) is cited for~the meaning ascribed to~the word “prescribed”.}.

In accordance with section 173(1)($b$)  of the Social Security Administration Act 1992 he has obtained the agreement of the Social Security Advisory Committee that proposals to~make these Regulations should not be referred to~it. \looseness=-1

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and~commencement]{Citation and~commencement}

1.  These Regulations may be cited as the Social Security (Miscellaneous Amendments) (No.~4) Regulations 2007 and~shall come into~force on 24th September 2007.

\subsection[2. Amendment of the Social Security (Claims and~Payments) Regulations 1987]{Amendment of the Social Security (Claims and~Payments) Regulations 1987}

2.---(1)  The Social Security (Claims and~Payments) Regulations 1987\footnote{S.I.~1987/1968.} are amended as follows.

(2) In regulation~3\footnote{Regulation~3 was amended by S.I.~1989/136, S.I.~1994/2943, S.I.~1999/2556, S.I.~1999/3178, S.I.~2000/1483, S.I.~2001/488, S.I.~2003/1589 and S.I.~2005/1551.} (claims not required for~entitlement to~benefit in certain cases)—
\begin{enumerate}\item[]
($a$) after sub-paragraph~($c$)  insert—
\begin{quotation}
“($ca$) in the case of a Category A retirement pension where the beneficiary—
\begin{enumerate}\item[]
(i) is entitled to~any category of retirement pension other than a Category A retirement pension; and

(ii) becomes divorced or~the beneficiary’s civil partnership is dissolved;
\end{enumerate}

($cb$) in the case of a Category B retirement pension where the beneficiary—
\begin{enumerate}\item[]
(i) is entitled to~either a Category A retirement pension or~to~a graduated retirement benefit or~to~both; and

(ii) marries or~enters into~a civil partnership;”;
\end{enumerate}
\end{quotation}

($b$) after sub-paragraph~($d$)  insert—
\begin{quotation}
“($da$) in the case of a bereavement payment where the beneficiary is over pensionable age and~satisfies the conditions of entitlement under section 36(1) of the Contributions and~Benefits Act\footnote{1992 c.~4. Section 36 was substituted by the Welfare Reform and Pensions Act 1999 (c.~30), section 54(1) and amended by the Civil Partnership Act 2004 (c.~33), Schedule 24, paragraph~16.};”.
\end{quotation}
\end{enumerate}

(3) After regulation~6(15) insert—
\begin{quotation}
“(15A) Paragraphs (16) to~(34) shall not apply in any case where it would be advantageous to~the claimant to~apply the provisions of regulation~19 (time for~claiming benefit.”.
\end{quotation}

(4) In regulation~6(19)\footnote{Regulation~6(19) was amended by S.I.~2002/428 and S.I.~2006/2377.} (date of claim) for~the words from “original award”)” to~“the circumstances”, substitute “original award”) has been terminated or~reduced or~payment under that award ceases in the circumstances” and~in sub-paragraph~($b$)  for~“re-awarded,” substitute “re-awarded or~becomes payable again”.

(5) In regulation~6(20)\footnote{Regulation~6(20) was substituted by S.I.~2006/2377.}—
\begin{enumerate}\item[]
($a$) after sub-paragraph~($a$)  omit “or”;

($b$) at the end of sub-paragraph~($b$)  add “or”; and

($c$) after sub-paragraph~($b$)  add—
\begin{quotation}
“($c$) that the qualifying benefit has ceased to~be payable in accordance with—
\begin{enumerate}\item[]
(i) regulation~6(1) of the Social Security (Attendance Allowance) Regulations 1991\footnote{S.I.~1991/2740. Regulation~6(1) was substituted by S.I.~1992/2869. Regulation~7 was amended by S.I.~1992/2869, S.I.~1992/3147, S.I.~1993/518, S.I.~2001/3767, S.I.~2002/208, S.I.~2002/1406, S.I.~2003/2259, S.I.~2005/445, S.I.~2005/2078 and S.I.~2005/2687.} or~regulation~8(1) of the Social Security (Disability Living Allowance) Regulations 1991\footnote{S.I.\ 1991/2890. Regulation~8 was substituted by S.I.\ 1992/2869 and amended by S.I.\ 2000/1401. Regulation~9 was amended by S.I.\ 1992/633, S.I.\ 1992/2869, S.I.\ 1992/3147, S.I.\ 1993/518, S.I.\ 1995/2162, S.I.\ 2000/3181, S.I.\ 2001/3767, S.I.\ 2002/208, S.I.\ 2002/1406, S.I.\ 2003/2259, S.I.\ 2005/445, S.I.\ 2005/2078 and S.I.\ 2005/2687.} because the claimant is undergoing treatment as an in-patient in a hospital or~similar institution, or

(ii) regulation~7 of the Social Security (Attendance Allowance) Regulations 1991 or~regulation~9 of the Social Security (Disability Living Allowance) Regulations 1991 because the claimant is resident in certain accommodation other than a hospital.”.
\end{enumerate}
\end{quotation}
\end{enumerate}

(6) In regulation~6(21)\footnote{Regulation~6(21)($b$) was amended by S.I.~2002/428 and S.I.~2006/2377.}—
\begin{enumerate}\item[]
($a$) for~“The additional” substitute “Subject to~paragraph~(21A), the additional” and~in sub-paragraph~($a$), for~“and” substitute “or”; and

($b$) for~sub-paragraph~($b$)  substitute—
\begin{quotation}
\begin{enumerate}\item[]
“($b$) the qualifying benefit is re-awarded following revision, supersession or~appeal; or

($c$) the qualifying benefit is re-awarded on a renewal claim when an award for~a fixed period expires; or

($d$) the cessation of payment ends when the claimant leaves the hospital or~similar institution or~accommodation referred to~in paragraph~(20)($c$); and
\end{enumerate}
the further claim referred to~in paragraph~(19), is made within three months of the date on which the additional circumstances apply.”.
\end{quotation}
\end{enumerate}

(7) After regulation~6(21), insert—
\begin{quotation}
\begin{sloppypar}
“(21A) Paragraph (21) applies whether the benefit is re-\hspace{0pt}awarded when the further claim is decided or~following a revision of, or~an appeal against, such a decision.”.
\end{sloppypar}
\end{quotation}

(8) In regulation~6(30)($b$)\footnote{Regulation~6(30) was inserted by S.I.~2002/428.} omit “not later than 10 working days after the termination,”.

\begin{sloppypar}
(9) In regulation~6(33)\footnote{Regulation~6(33) was inserted by S.I.~2006/832.}, for~“Where” substitute “Subject to~paragraph~(34), where”.
\end{sloppypar}

(10) After regulation~6(33) add—
\begin{quotation}
“(34) Paragraph (33) shall not apply where the decision awarding a qualifying benefit is made in respect of a renewal claim where a fixed period award of that benefit has expired, or~is due to~expire.”.
\end{quotation}

(11) In regulation~19\footnote{Regulation~19 was substituted by S.I.~1997/793 and paragraph (3B) was inserted by S.I.~1997/793.} (time for~claiming benefit), after paragraph~(3B) insert—
\begin{quotation}
“(3C) In any case where the application of paragraphs (16) to~(34) of regulation~6 would be advantageous to~the claimant, this regulation~shall apply subject to~those provisions.”.
\end{quotation}

(12) In regulation~30(4)\footnote{Regulation~30(4) was amended by S.I.~1999/2572.} (payments on death), for~“Paragraphs” substitute “Subject to~paragraph~(4B), paragraphs”.

(13) After regulation~30(4A)\footnote{Regulation~30(4A) was inserted by S.I.~2000/1982.} insert—
\begin{quotation}
“(4B) A written application is not required where—
\begin{enumerate}\item[]
($a$) an executor~or~administrator~has not been appointed;

($b$) the deceased was in receipt of a retirement pension of any category or~state pension credit including where any other benefit was combined for~payment purposes with either of those benefits at the time of death;

($c$) the sum payable by way of benefit to~the deceased is payable to~a person who was the spouse or~civil partner of the deceased at the time of death; and

($d$) either—
\begin{enumerate}\item[]
(i) the spouse or~civil partner and~the deceased were living together at the time of death; or

(ii) they would have been living together at the time of death but for~the fact that either or~both of them were in a residential care or~a nursing home or~in a hospital.”.
\end{enumerate}
\end{enumerate}
\end{quotation}

(14) In regulation~33(1)($c$)\footnote{Regulation~33(1) was amended by S.I.~1999/2572 and S.I.~2005/337.} (persons unable to~act) for~“receiver” substitute “deputy” and~after “Court of Protection” insert “under Part I of the Mental Capacity Act 2005\footnote{2005 c.~9.} or~receiver appointed under Part VII of the Mental Health Act 1983\footnote{1983 c.~20.} but treated as a deputy by virtue of the Mental Capacity Act 2005”.\looseness=-1

\subsection[3. Amendment of the Social Security and~Child Support (Decisions and~Appeals) Regulations 1999]{Amendment of the Social Security and~Child Support (Decisions and~Appeals) Regulations 1999}

3.---(1)  The Social Security and~Child Support (Decisions and~Appeals) Regulations 1999\footnote{S.I.~1999/991.} are amended as follows.

(2) In regulation~3(5)($b$)\footnote{Regulation~3(5)($b$) was amended by S.I.~1999/1623.} (revision of decisions), for~“except in the case of a disability decision or~an incapacity benefit decision where there has been an incapacity determination (whether before or~after the decision)”, substitute “except in a case to~which sub-paragraph~($c$)  or~($d$)  applies,”.

(3) In regulation~3(5)($c$)\footnote{Regulation 3(5)($c$) was inserted by S.I.~1999/1623.}, at the beginning, insert “subject to~sub-paragraph~($d$),”.

(4) After regulation~3(5)($c$), add—
\begin{quotation}
“($d$) where the decision is a disability benefit decision, or~is an incapacity benefit decision, which was made in ignorance of, or~was based upon a mistake as to, some material fact not in relation to~the incapacity or~disability determination embodied in or~necessary to~the incapacity benefit decision or~disability benefit decision, and~as a result of that ignorance of, or~mistake as to~that fact, the decision was more advantageous to~the claimant than it would otherwise have been but for~the ignorance or~mistake,”.
\end{quotation}

(5) After regulation~3(5A)\footnote{Regulation~3(5A) was inserted by S.I.\ 2002/1379.} insert—
\begin{quotation}
“(5B) A decision by the Secretary of State under section 8 or~10 awarding incapacity benefit may be revised at any time if—
\begin{enumerate}\item[]
($a$) it incorporates a determination that the condition in regulation~28(2)($b$)  of the Social Security (Incapacity for~Work) (General) Regulations 1995\footnote{S.I.~1995/311. Regulation~28(2)($b$) was amended by S.I.~1995/987 and S.I.~1996/3207.} (conditions for~treating a person as incapable of work until the personal capability assessment is carried out) is satisfied;

($b$) the condition referred to~in sub-paragraph~($a$)  was not satisfied at the time when the further claim was first determined; and\looseness=-1

($c$) there is a period before the award which falls to~be decided.”.\looseness=-1
\end{enumerate}
\end{quotation}

(6) In regulation~7(2)($bc$)\footnote{Regulation~7(2)($bc$)  was inserted by S.I.~2006/2377.} (date from which a decision superseded under section 10 takes effect), at the beginning, insert “subject to~sub-\hspace{0pt}paragraph~($bd$),”.

(7) After regulation~7(2)($bc$)  add—
\begin{quotation}
“($bd$) sub-paragraph~($bc$)  shall only apply to~the disabled person whose benefit is affected by the cessation of payment of carer’s allowance;”.
\end{quotation}

%\begin{sloppypar}
(8) In regulation~7A(1)\footnote{Regulation~7A was inserted by S.I.~1999/1623 and amended by S.I.~2000/1596.} (definitions for~the purposes of regulations~3(5)($c$), 6(2)($g$), 7(2)($c$)  and~(5) and~ancillary provisions), in the definition of “incapacity benefit decision”, at the end, add “or~an award of long term incapacity benefit under regulation~17(1) (transitional awards of long-term incapacity benefit) of the Social Security (Incapacity Benefit) (Transitional) Regulations 1995\footnote{S.I.~1995/310.}”.
%\end{sloppypar}

(9) In Schedule~3B, paragraph~6\footnote{Schedule 3B was inserted by S.I.~2002/3019.}, (date on which change of circumstances takes effect where claimant entitled to~state pension credit) for~“Social Security (Hospital In-Patients) Regulations 1975\footnote{S.I.~1975/555. These Regulations were revoked by S.I.~2005/3360.}” substitute “Social Security (Hospital In-Patients) Regulations 2005\footnote{S.I.~2005/3360.}”.

\subsection[4. Amendment of the Housing Benefit Regulations 2006]{Amendment of the Housing Benefit Regulations 2006}

4.---(1)  The Housing Benefit Regulations 2006\footnote{S.I.~2006/213.} are amended as follows.

(2) In regulation~79(1) (date on which change of circumstances is to~take effect) for~the words from “either regulation~34” to~“subject to” substitute “regulation~34 (disregard of changes in tax, contributions, etc.)\ applies, and~subject to~regulation~8(3) of the Decisions and~Appeals Regulations and”.

(3) In regulation~79(2)\footnote{Regulation~79(2) was substituted by S.I.~2005/2502 and amended by S.I.~2006/217.} for~“, except in a case where regulation~8(3) of the Decisions and~Appeals Regulations applies,” substitute “and~regulation~8(3) of the Decisions and~Appeals Regulations”.

\subsection[5. Amendment of the Housing Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations 2006]{Amendment of the Housing Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations 2006}

5.---(1)  The Housing Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations 2006\footnote{S.I.~2006/214.} are amended as follows.

(2) In regulation~59(1) (date on which change of circumstances is to~take effect) for~the words from “of these Regulations” to~“subject to” substitute “applies, and~subject to~regulation~8(3) of the Decisions and~Appeals Regulations and”.

(3) In regulation~59(2)\footnote{Regulation~59(2) was substituted by S.I.~2005/2502 and amended by S.I.~2006/217.} for~“, except in a case where regulation~8(3) of the Decisions and~Appeals Regulations applies,” substitute “and~regulation~8(3) of the Decisions and~Appeals Regulations”.

\subsection[6. Amendment of the Council Tax Benefit Regulations 2006]{\sloppy Amendment of the Council Tax Benefit Regulations 2006}

6.---(1)  The Council Tax Benefit Regulations 2006\footnote{S.I.~2006/215.} are amended as follows.

(2) In regulation~67(1) (date on which change of circumstances is to~take effect) for~the words from “, or~regulation” to~“subject to” substitute “applies, and~subject to~regulation~8(3) of the Decisions and~Appeals Regulations, and”.

\subsection[7. Amendment of the Council Tax Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations 2006]{Amendment of the Council Tax Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations 2006}

7.---(1)  The Council Tax Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations 2006\footnote{S.I.~2006/216.} are amended as follows.

(2) In regulation~50(1) (date on which change of circumstances is to~take effect) for~the words from “, or~regulation” to~“subject to” substitute “applies, and~subject to~regulation~8(3) of the Decisions and~Appeals Regulations, and”.

\subsection[8. Revocations]{Revocations}

8.  Regulations 7(2A) (decisions superseding earlier decisions) and~8(12) and~(13) (date from which a decision superseding an earlier decision takes effect) of the Housing Benefit and~Council Tax Benefit (Decisions and~Appeals) Regulations 2001\footnote{S.I.~2001/1002. Regulation~7(2A) was inserted by S.I.~2003/1338 and amended by S.I.~2006/217. Regulations 8(12) and (13) were inserted by S.I.~2003/1338 and Regulation~8(12) was amended by S.I.~2006/217.} are revoked. 

\pagebreak[3]

\bigskip

Signed 
by authority of the 
Secretary of State for~Work and~Pensions.
%I concur
%By authority of the Lord Chancellor

{\raggedleft
\emph{Mike O'Brien}\\*
%Secretary
Minister
%Parliamentary Under-Secretary 
of State,\\*Department 
for~Work and~Pensions

}

22nd August 2007

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations amend the Social Security (Claims and~Payments) Regulations 1987, (“the 1987 Regulations”), the Social Security and~Child Support (Decisions and~Appeals) Regulations 1999 (“the 1999 Regulations”), the Housing Benefit Regulations 2006 (“the 2006 Regulations”), the Housing Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations 2006, the Council Tax Benefit Regulations 2006 and~the Council Tax Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations 2006.

Regulation~2 amends the 1987 Regulations. Paragraph (2) extends the list of exceptions to~the general rule of the necessity to~make a claim to~be entitled to~benefit.

Paragraphs (3) and~(11) insert provisions which enable a claimant to~benefit from either the linking rules in the circumstances described in regulation~6 or~the rules relating to~the prescribed time for~claiming benefit in regulation~19 and~not both at the same time.

Paragraphs (4) to~(7) have the effect that the transitional protection which applies for~payment of child dependency increases is not lost where a disabled person goes into~hospital or~other accommodation.

Paragraph (8) enables a further claim for~income support to~be treated as made on the first day of an award of a linked benefit.

Paragraphs (9) and~(10) enable carer’s allowance to~be paid from the date that entitlement first arises in the circumstances described in regulation~6(33) of the 1987 Regulations.

Paragraphs (12) and~(13) enable arrears of benefit to~be paid to~a spouse or~civil partner of a deceased claimant without the need for~a written application to~be made for~such payment.

Paragraph (14) amends regulation~33(1)($c$)  by substituting the word “deputy” for~“receiver” to~enable the appointee process to~reflect changes introduced by the Mental Capacity Act 2005.

Regulation~3 amends the 1999 Regulations. Paragraphs (2) to~(4) enable the Secretary of State to~revise a decision at any time where there is a non-medical change of circumstances relating to~a disability or~incapacity benefit decision.

Paragraph (5) enables the Secretary of State to~revise a decision which awarded incapacity benefit from a date later than the first day of claim because of the rule contained in regulation~28(2)($b$)  of the Social Security (Incapacity for~Work) (General) Regulations 1995, when the claimant subsequently passes the personal capability assessment.

Paragraphs (6) and~(7) have the effect of adding a further sub-paragraph~to~regulation~7(2) of the 1999 Regulations. The amendment enables the existing provision to~apply only to~the person being cared for~and~not the carer.

Paragraph (8) amends regulation~7A(1) of the 1999 Regulations to~extend the definition of an “incapacity benefit decision” to~cover an award of long term incapacity benefit under regulation~17(1) of the Social Security (Incapacity Benefit) (Transitional) Regulations 1995.

Paragraph (9) amends the definition of “patient” in paragraph~6 of Schedule~3B to~the 1999 Regulations to~refer to~the Social Security (Hospital In-Patient) Regulations 2005.

Regulation~4 amends the 2006 Regulations. Paragraphs (2) and~(3) provide that regulation~79(1) and~(2) apply subject to~the provisions contained in regulation~8(3) of the Housing Benefit and~Council Tax Benefit (Decisions and~Appeals) Regulations 2001.

Regulation~5 amends the Housing Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations 2006. Paragraphs (2) and~(3) provide that regulation~59(1) and~(2) apply subject to~the provisions contained in regulation~8(3) of the Housing Benefit and~Council Tax Benefit (Decisions and~Appeals) Regulations 2001.

Regulation~6 amends the Council Tax Benefit Regulations 2006. Paragraph (2) provides that regulation~67 applies subject to~the provisions contained in regulation~8(3) of the Housing Benefit and~Council Tax Benefit (Decisions and~Appeals) Regulations 2001.

Regulation~7 amends the Council Tax Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations 2006. Paragraph (2) provides that regulation~50(1) applies subject to~the provisions contained in regulation~8(3) of the Housing Benefit and~Council Tax Benefit (Decisions and~Appeals) Regulations 2001.

Regulation~8 revokes regulations~7(2A) and~8(12) and~(13) of the Housing Benefit and~Council Tax (Decisions and~Appeals) Regulations 2001. These provisions are revoked given that they are now redundant.

A full regulatory impact assessment has not been carried out in respect of these Regulations as they do not impose a cost on business, charities or~the voluntary sector. 

\end{document}