\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Maintenance and Other Payments Act 2008 (Commencement) Order 2008}

\newcommand\regsnumber{2008/1476}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2008 No.\ 1476 (C.~67)}

\date{Made
%17th March 2008\\
%Laid before Parliament
%4th March 2008\\
%Coming into force
9th June 2008
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{42.11603pt}

%\hbadness=10000

\begin{document}

\maketitle

\noindent
The Secretary of State, in exercise of the powers conferred by section~62(3) and (4) of the Child Maintenance and Other Payments Act 2008\footnote{2008 c.~6.}, makes the following Order: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and interpretation]{Citation and interpretation}

1.---(1)  This Order may be cited as the Child Maintenance and Other Payments Act 2008 (Commencement) Order 2008.

(2) In this Order—
\begin{enumerate}\item[]
“the 1991 Act” means the Child Support Act 1991\footnote{1991 c.~48.};

“the 2000 Act” means the Child Support, Pensions and Social Security Act 2000\footnote{2000 c.~19.}.
\end{enumerate}

(3) In this Order, unless the context requires otherwise, any reference to a numbered section, Part or Schedule is a reference to a section, Part or Schedule of the Child Maintenance and Other Payments Act 2008.

\subsection[2. Appointed days for provisions in Parts I, III and V]{Appointed days for provisions in Parts I, III and V}

2.---(1)  10th June 2008 is the day appointed for the coming into force of section 1 (the Child Maintenance and Enforcement Commission), except in relation to paragraph 1($c$)  of Schedule 1, for the purpose only of conferring power to appoint the members of the Commission.

(2) 14th July 2008 is the day appointed for the coming into force of—
\begin{enumerate}\item[]
($a$) section 15($b$)  (repeal of section 46 of the 1991 Act),

($b$) section 45 (liable relative provision: exclusion of parental duty to maintain),

($c$) Schedule 8 (repeals) so far as it relates to repeals in—
\begin{enumerate}\item[]
(i) sections 16, 17, 20, 28ZA, 28ZC and 46 of the 1991 Act,

(ii) section 106(7) of the Social Security Administration Act 1992\footnote{1992 c.~5.},

(iii) section 19 of and sub-paragraphs (11)($a$)  and (13)($d$)  of paragraph 11 of Schedule 3 to the 2000 Act.
\end{enumerate}
\end{enumerate}

(3) Subject to paragraph (4), 14th July 2008 is the day appointed for the coming into force of—
\begin{enumerate}\item[]
($a$) Section 15($a$)  (repeal of section~6 of the 1991 Act),

($b$) paragraph 1(34) of Schedule 7,

($c$) Schedule 8 so far as it relates to the repeals in section 4(10), section~6 and section 7(1) of the 1991 Act.
\end{enumerate}

(4) Paragraph (3) does not apply in relation to existing cases as defined in paragraph (5) and, insofar as section~6 of the 1991 Act remains in force for such cases, it shall have effect as if the reference to section 46 in subsection (4) were omitted.

(5) In paragraph (4) an existing case is one in which, immediately before 14th July 2008, section~6 of the 1991 Act applies in relation to a parent with care and—
\begin{enumerate}\item[]
($a$) a maintenance calculation or maintenance assessment is in force as a result of the Secretary of State acting under that section, or

($b$) no maintenance calculation or maintenance assessment has been made but the Secretary of State has given notice in accordance with regulation 5 of the Child Support (Maintenance Calculation Procedure) Regulations 2000\footnote{S.I.~2001/157.} or regulation 5 of the Child Support (Maintenance Assessment Procedure) Regulations 1992\footnote{S.I.~1992/1813.}.
\end{enumerate}

(6) 10th June 2008 is the day appointed for the coming into force of section 56 (general interpretation), section 57(2) (power to make consequential amendments), section 59 (transition) and section~60(1) (financial provisions).

\subsection[3. Appointed days for provisions in Part IV]{Appointed days for provisions in Part IV}

3.---(1)  10th June 2008 is the day appointed for the coming into force of—
\begin{enumerate}\item[]
($a$) the provisions specified in the Schedule, for the purpose only of conferring power to make regulations,

($b$) section 54 (amendment of Social Security (Recovery of Benefits) Act 1997\footnote{1997 c.~27.}) for the purpose only of conferring power to make regulations under section 1A of the Social Security (Recovery of Benefits) Act 1997 (Lump sum payments: regulation-making power).
\end{enumerate}

(2) 1st October 2008 is the day appointed for the coming into force of—
\begin{enumerate}\item[]
($a$) sections 46 to 50, 53 and 54 insofar as they are not already in force,

($b$) sections 51 and 52.
\end{enumerate}

\bigskip

Signed 
by authority of the 
Secretary of State for Work and Pensions.

{\raggedleft
\emph{William D.\ McKenzie}\\*
%Minister
Parliamentary Under-Secretary 
of State,\\*Department for Work and Pensions

}

9th June 2008

\small

\part[Schedule --- Provisions brought into force on 10th June 2008 for regulation-making purposes]{Schedule\\*Provisions brought into force on 10th June 2008 for regulation-making purposes}

\renewcommand\parthead{— Schedule}

%\begin{tabulary}{\linewidth}{JJ}
\begin{longtable}{p{101.10304pt}p{264.90263pt}}
\hline
\itshape Provision of the Act	& \itshape Subject-matter\\
\hline
\endhead
\hline
\endlastfoot
Section 46(3)	&Prescribing the amounts of payments\\
Section 47(1)($b$)  and ($c$), (2)($b$)  and~($c$), (3)($e$)  and (4)($d$) 	&Prescribing conditions of entitlement\\
Section 48(1) to (3)	&Prescribing the manner and time limit for making claims\\
Section 49(2)	&Prescribing the manner and the period within which applications may be made for, or the Secretary of State may institute, a reconsideration\\
Section 50(4)($c$) 	&Enabling an appeal to be treated as an application for reconsideration\\
Section 53	&Regulations\\
%\end{tabulary}
\end{longtable}

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Order)}

This Order brings into force provisions of the Child Maintenance and Other Payments Act 2008 as follows:

Article 2 brings into force certain provision in Part I (Child Maintenance and Enforcement Commission), Part III (child support) and Part V (general).

Section 1 is brought into force on 10th June for the purpose only of conferring power to make appointments to the Commission. The requirement for the Commission to comprise one or more executive directors is excluded for that purpose.

Section 15($b$)  (which repeals section 46 of the Child Support Act 1991) and associated repeals come into force on 14th July 2008. Section 15($a$)  (which repeals section~6 of the Child Support Act 1991) and associated repeals also come into force on 14th July 2008 except for existing cases.

Section 45 (which amends provisions relating to liable relatives in the Social Security Administration Act 1992 so that they do not apply in relation to children), together with the repeal of s.106(7) of that Act, come into force on 14th July 2008.

Certain provisions in Part V (General) come into force on 10th June 2008.

Article 3 brings into force the provisions in Part IV (Lump sum payments: mesothelioma etc.).

10th June 2008 is the day appointed for the coming into force of the powers listed in the Schedule to the Order, for the purposes of conferring power to make regulations. The Regulations relate to lump sum payments for mesothelioma and enable provision to be made for making claims and applications for reconsideration of decisions. 10th June 2008 is also the day appointed for the coming into force of section 54 of the Act which amends the Social Security (Recovery of Benefits) Act 1997, so that Regulations may provide for the recovery of lump sum payments.

1st October 2008 is the day appointed for the coming into force of sections 46 to 54 of the Act (lump sum payments: mesothelioma etc) insofar as they have not already been commenced. 

\end{document}