\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support (Miscellaneous and Consequential Amendments) Regulations 2015}

\newcommand\regsnumber{2015/338}

\title{\regstitle}

\author{S.I.\ 2015 No.\ 338}

\date{Made
19th February 2015\\
Laid before Parliament
26th February 2015\\
Coming into force
in accordance with regulation 1
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.61603pt}

%\hbadness=10000

\begin{document}

\maketitle

%\enlargethispage{\baselineskip}

\noindent
The Secretary of State for Work and Pensions, in exercise of the powers conferred by sections 28ZD(1), 34(1)($b$), 41B(3), 49D(2)($c$), 51(1) and (2)($i$), 52(4) and 54(1) of, and paragraph 5(1) and (2) of Schedule 1 (as it has effect apart from section 1 of the Child Support, Pensions and Social Security Act 2000\footnote{2000 c.~19.}) to, the Child Support Act 1991\footnote{1991 c.~48. Section 28ZD was inserted by section 44 of the Social Security Act 1998 (c.~14) and subsection (1) was amended by S.I.~2008/2833. Section 41B was inserted by section 23 of the Child Support Act 1995 (c.~34) and subsection (3) was amended by section 13 of, and paragraph 45 of Schedule 3 to, the Child Maintenance and other Payments Act 2008 (c.~6) (“the 2008 Act”) and S.I.~2012/2007. Section 49D was inserted by section 40 of the 2008 Act and subsection (2) was amended by S.I.~2012/2007. Section 54 is cited for the meaning given to the word “prescribed”. Subsection (1) of section 54 was inserted by Schedule 7 to the 2008 Act. Paragraph 5(1) of Schedule 1 was amended by the Child Support, Pensions and Social Security Act 2000, section 1(2)($b$).}, makes the following Regulations: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and commencement]{Citation and commencement}

1.—(1) These Regulations may be cited as the Child Support (Miscellaneous and Consequential Amendments) Regulations 2015.

(2) Subject to paragraph (3), these Regulations come into force on 23rd March 2015.

(3) Regulation 3 comes into force on the date on which section 1 of the Childcare Payments Act 2014 (entitlement to receive money towards costs of childcare)\footnote{2014 c.~28.} comes into force for all purposes.

\subsection[2. Amendments to the Child Support (Maintenance Assessment Procedure) Regulations 1992]{Amendments to the Child Support (Maintenance Assessment Procedure) Regulations 1992}

2.—(1) The Child Support (Maintenance Assessment Procedure) Regulations 1992\footnote{S.I.~1992/1813, which was revoked with savings by S.I.~2001/157 and 2012/2785.} are amended as follows.

(2) In regulation 17 (revision of decisions)\footnote{Regulation 17 was inserted by S.I.~1999/1047 and amended by S.I.~2000/1596, 2004/2415, 2008/2543, 2011/1464 and 2013/2380.}—
\begin{enumerate}\item[]
($a$) in paragraph (1)($a$)  omit “within one month of the date of notification of the decision or within such longer time as may be allowed by regulation~18”;

($b$) after “section 16 of the Act” insert—
\begin{quotation}
“either—
\begin{enumerate}\item[]
(i) within one month of the date of notification of the decision;

(ii) within one month of the date on which notice of the correction is given under regulation 53A(3) (correction of accidental errors); or

(iii) within such longer time as may be allowed by regulation 18;”.
\end{enumerate}
\end{quotation}
\end{enumerate}

(3) After regulation 53 (authorisation of representative) insert—
\begin{quotation}
\subsection*{“Correction of accidental errors}

53A.—(1) An accidental error in a decision of the Secretary of State made under the Act, or in any record of such a decision, may be corrected by the Secretary of State at any time.

(2) Such a correction is to be treated as part of that decision or of that record.

(3) The Secretary of State must give written notice of the correction as soon as practicable to the persons to whom notice of the decision was required to be given.

(4) In calculating the time within which an application may be made under regulation 17(1)($a$)  (revision of decisions) for a decision to be revised, no account is to be taken of any day falling before the day on which notice of any correction was given.”.
\end{quotation}

\subsection[3. Amendment to the Child Support (Maintenance Assessments and Special Cases) Regulations 1992]{Amendment to the Child Support (Maintenance Assessments and Special Cases) Regulations 1992}

3.  After paragraph 48F of Schedule 2 to the Child Support (Maintenance Assessments and Special Cases) Regulations 1992 (amounts to be disregarded when calculating or estimating $N$ and $M$)\footnote{S.I.~1992/1815, which was revoked with savings by S.I.~2001/155 and 2012/2785. Paragraph 48F was inserted by S.I.~2003/2779 and amended by S.I.~2005/2877.} insert—
\begin{quotation}
“48G.  Any top-up payment made under the Childcare Payments Act 2014 (“top-up payment” is to be read in accordance with section 1 of that Act).”.
\end{quotation}

\subsection[4. Amendments to the Child Support (Arrears, Interest and Adjustment of Maintenance Assessments) Regulations 1992]{Amendments to the Child Support (Arrears, Interest and Adjustment of Maintenance Assessments) Regulations 1992}

4.  In regulations 10A(1)($a$)  (reimbursement of a repayment of overpaid child maintenance) and 10B (repayment of a reimbursement of a voluntary payment) of the Child Support (Arrears, Interest and Adjustment of Maintenance Assessments) Regulations 1992\footnote{S.I.~1992/1816. Regulation 10A(1) was inserted by S.I.~1995/3261 and amended by S.I.~1996/1345, 2001/162 and 2002/3019. Regulation 10B was inserted by S.I.~2001/162 and amended by S.I.~2002/3019.}, after “income support” insert “, income-related employment and support allowance”.

\subsection[5. Amendments to the Child Support (Collection and Enforcement) Regulations 1992]{Amendments to the Child Support (Collection and Enforcement) Regulations 1992}

5.  Schedule 1 to the Child Support (Collection and Enforcement) Regulations 1992 (liability order prescribed form)\footnote{S.I.~1992/1989; relevant amending instruments are S.I.~2001/162 and 2014/1386.} is amended as follows—
\begin{enumerate}\item[]
($a$) omit “for Social Security”;

($b$) for “are due from the defendant” substitute “have become payable by the liable person (the defendant)”;

($c$) for “are outstanding” substitute “have not been paid”;

($d$) for “collected by virtue of” substitute “that the Secretary of State has arranged to collect under”.
\end{enumerate}

\subsection[6. Modification of the Social Security and Child Support (Decisions and Appeals) Regulations 1999]{Modification of the Social Security and Child Support (Decisions and Appeals) Regulations 1999}

6.—(1) The Social Security and Child Support (Decisions and Appeals) Regulations 1999\footnote{S.I.~1999/991; relevant amending instruments are S.I.~2000/3185, 2002/1204, 2002/1379, 2003/916, 2008/2543, 2008/2544, 2008/2683, 2009/396 and 2012/2007.} are modified, in relation to a case in which liability to pay child support maintenance is calculated in accordance with Part I of Schedule~1 to the Child Support Act 1991 as substituted by Schedule 1 to the Child Support, Pensions and Social Security Act 2000, before its amendment by paragraph 2 of Schedule 4 to the Child Maintenance and Other Payments Act 2008\footnote{2008 c.~6.}, as if they had been amended as follows.

(2) In regulation 3A(1) (revision of child support decisions)\footnote{Regulation 3A was inserted by S.I.~2000/3185 and amended by S.I.~2002/1204, 2008/2543, 2008/2544, 2008/2683, 2009/396 and 2012/2007.}, for sub-paragraph ($a$)  substitute—
\begin{quotation}
“($a$) if the Secretary of State receives an application for the revision of a decision under either section 16 or section 28G of the Child Support Act—
\begin{enumerate}\item[]
(i) within one month of the date of notification of the decision;

(ii) within one month of the date on which notice of the correction is given under regulation 9B(3) (correction of accidental errors in child support decisions); or

(iii) within such longer time as may be allowed under regulation 4;”.
\end{enumerate}
\end{quotation}

(3) After regulation 9A (correction of accidental errors)\footnote{Regulation 9A was inserted by S.I.~2002/1379, revoked in relation to certain cases by S.I.~2003/916 and amended by S.I.~2008/2683.} insert—
 \begin{quotation}
\subsection*{“Correction of accidental errors in Child Support Decisions}

9B.—(1) An accidental error in a decision of the Secretary of State made under the Child Support Act 1991, or in any record of such a decision, may be corrected by the Secretary of State at any time.

(2) Such a correction is to be treated as part of that decision or of that record.

(3) The Secretary of State must give written notice of the correction as soon as practicable to the persons to whom notice of the decision was required to be given.

(4) In calculating the time within which an application may be made under regulation 3A(1)($a$)  (revision of child support decisions) for a decision to be revised, no account is to be taken of any day falling before the day on which notice of any correction was given.”.
\end{quotation}

\subsection[7. Amendment to the Child Support Information Regulations 2008]{Amendment to the Child Support Information Regulations 2008}

7.  After regulation 14 of the Child Support Information Regulations 2008 (employment to which section 50 of the 1991 Act applies)\footnote{S.I.~2008/2551. Regulation 14 was amended by S.I.~2009/396 and 2012/725.} insert—
\begin{quotation}
\subsection*{“Disclosure of information to credit reference agencies}

14A.—(1) The information prescribed for the purposes of section~49D(2)($c$)  of the 1991 Act (disclosure of information to credit reference agencies) is, in relation to the person referred to in section 49D(2)($b$)  of that Act—
\begin{enumerate}\item[]
($a$) the person’s name, last known or notified address and date of birth;

($b$) the reference number used by the Secretary of State to identify the person’s case;

($c$) the date on which any liability order in force against the person was made;

($d$) the amount in respect of which that liability order was made;

($e$) the address stated in that liability order, if different from the person’s last known or notified address;

($f$) that the amount referred to in sub-paragraph ($d$)  has been paid and the date on which that amount was paid;

($g$) that a liability order made against the person has been set aside or quashed.
\end{enumerate}

(2) The Secretary of State must send a written notice by post to the person’s last known or notified address at least twenty-one days prior to supplying the information in paragraph (1)($a$)  to ($e$)  to a credit reference agency.

(3) The requirement in paragraph (2) does not apply where the person cannot be traced.

(4) The written notice must state that the Secretary of State intends to supply information in relation to the non-resident parent to a credit reference agency.”.
\end{quotation}

\subsection[8. Amendments to the Child Support Maintenance Calculation Regulations 2012]{Amendments to the Child Support Maintenance Calculation Regulations 2012}

8.—(1) The Child Support Maintenance Calculation Regulations 2012\footnote{S.I.~2012/2677, to which there are amendments not relevant to these Regulations.} are amended as follows.

(2) In regulation 14(1) (grounds for revision), for sub-paragraph ($a$)  substitute—
\begin{quotation}
“($a$) if the Secretary of State receives an application for the revision of a decision under either section 16 or section 28G (application for a variation where a maintenance calculation is in force) of that Act—
\begin{enumerate}\item[]
\looseness=1
(i) within 30 days after the date of notification of the decision;

(ii) within 30 days after the date on which notice of the correction is given under regulation 27A(3) (correction of accidental errors); or

(iii) within such longer time as may be allowed under regulation 15;”.
\end{enumerate}
\end{quotation}

(3) After Chapter V (notification of decisions) insert—
\begin{quotation}
\section*{“Chapter VA\\*Accidental errors}

\subsection*{Correction of accidental errors}

27A.—(1) An accidental error in a decision of the Secretary of State made under the 1991 Act, or in any record of such a decision, may be corrected by the Secretary of State at any time.

(2) Such a correction is to be treated as part of that decision or of that record.

(3) The Secretary of State must give written notice of the correction as soon as practicable to the persons to whom notice of the decision was required to be given.

\looseness=1
(4) In calculating the time within which an application may be made under regulation 14(1)($a$)  (grounds for revision) for a decision to be revised, no account is to be taken of any day falling before the day on which notice of any correction was given.”.
\end{quotation}

\bigskip

\pagebreak[3]

Signed 
by authority of the 
Secretary of State for~Work and~Pensions.
%I concur
%By authority of the Lord Chancellor

{\raggedleft
\emph{Steve Webb}\\*
%Secretary
Minister
%Parliamentary Under Secretary 
of State\\*Department 
for~Work and~Pensions

}

19th February 2015

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations make miscellaneous and consequential amendments to various Child Support Regulations.

\looseness=-1
Regulations 2, 6 and 8 amend, respectively, the Child Support (Maintenance Assessment Procedure) Regulations 1992 (S.I.~1992/1813), the Social Security and Child Support (Decisions and Appeals) Regulations 1999 (S.I.~1999/991) and the Child Support Maintenance Calculation Regulations 2012 (S.I.~2012/2677). These Regulations relate, respectively, to the 1993 scheme for administering child support maintenance, the 2003 scheme and the 2012 scheme. A regulation is inserted into each set of Regulations which allows the Secretary of State to correct accidental errors in decisions and records of decisions made by the Secretary of State under the Child Support Act 1991 (c.~48) (“the 1991 Act”). The corrected decision or record will be treated as part of the original decision or record. Notice of the corrected decision or record must be given as soon as is practicable to those persons who were required to be notified of the original decision. Paragraph (4) of each regulation means that the period within which such a person may make an application for revision begins on the day the notice of the correction is given. Paragraph (2) of each of regulations 2, 6 and 8 makes a consequential amendment to the revision provision in each set of regulations.

\looseness=-1
Regulation 3 amends Schedule 2 to the Child Support (Maintenance Assessments and Special Cases) Regulations 1992 (S.I.~1992/1815), which applies to the 1993 scheme of child support. The amendment is consequential on the Childcare Payments Act 2014 (c.~28) and means that a top-up payment made under that Act will not be taken into account when calculating a parent’s income for the purposes of assessing the amount of child support maintenance payable.

\looseness=-1
Regulation 4 amends regulations 10A(1)($a$)  and 10B of the Child Support (Arrears, Interest and Adjustment of Maintenance Assessments) Regulations 1992 (S.I.~1992/1816). Regulation 10A(1)($a$)  allows the Secretary of State to pursue reimbursements of repayments of overpaid child maintenance. Regulation 10B allows the Secretary of State to pursue reimbursements of repayments of voluntary payments. If a person liable to make payments of child support (the “liable person”) has made an overpayment or voluntary payment of child maintenance, and the Secretary of State has made a payment by way of reimbursement of this overpayment or voluntary payment to the liable person, the Secretary of State may require the person who received that payment to repay the whole or a part of the payment. Regulations 10A(1)($a$)  and 10B are both amended so that the Secretary of State may not require a person who received such a payment to repay it where that person was in receipt of income-related employment and support allowance when the overpayment or voluntary payment occurred or when the reimbursement was made.

Regulation 5 makes technical amendments to Schedule 1 to the Child Support (Collection and Enforcement) Regulations 1992 (S.I.~1992/1989).

Regulation 7 inserts a new regulation into the Child Support Information Regulations 2008 (S.I.~2008/2551) which prescribes information for the purposes of section 49D(2)($c$)  of the 1991 Act. Section 49D allows the Secretary of State to disclose prescribed information relating to liable persons to credit reference agencies in certain circumstances. This new regulation prescribes the information that may be disclosed. This new regulation also makes provision for notifying the liable person that the Secretary of State intends to disclose information to a credit reference agency.

An impact assessment has not been published for this instrument as it has no impact on the private sector and civil society organisations. 

\end{document}