\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support, Pensions and Social Security Act 2000 (Commencement No.~14) Order 2008}

\newcommand\regsnumber{2008/2545}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and~Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2008 No.\ 2545 (C.~109)}

\date{Made
%26th September 2008\\
%Laid before Parliament
%1st October 2008\\
%Coming into force
25th September 2008
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{42.11603pt}

%\hbadness=10000

\begin{document}

\maketitle

\noindent
The Secretary of State, in exercise of the powers conferred by section~86(2) of the Child Support, Pensions and Social Security Act 2000\footnote{2000 c.~19.}, makes the following Order: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and interpretation]{Citation and interpretation}

1.---(1)  This Order may be cited as the Child Support, Pensions and Social Security Act 2000 (Commencement No.~14) Order 2008.

(2) In this Order any reference to a numbered section~or Schedule~is a reference to a section~of, or Schedule~to, the Child Support, Pensions and Social Security Act 2000.

\subsection[2. Appointed day for section~12]{Appointed day for section~12}

2.  26th September 2008 is the day appointed for the coming into force of section~12 (information required by the Secretary of State) in so far as it is not already in force.

\subsection[3. Appointed day for Schedule~3, paragraph~11(16)]{Appointed day for Schedule~3, paragraph~11(16)}

3.  The day appointed for the coming into force of paragraph~11(16) of Schedule~3 (amendment of enactments relating to child support), and section~26 so far as it relates to that sub-paragraph, in so far as they are not already in force is—
\begin{enumerate}\item[]
($a$) 26th September 2008 for the purpose of making regulations; and

($b$) 27th October 2008 for all other purposes.
\end{enumerate}

\subsection[4. Appointed day for section~23]{Appointed day for section~23}

4.  27th October 2008 is the day appointed for the coming into force of section~23 (abolition of the child maintenance bonus) in so far as it is not already in force. 

\bigskip

Signed 
by authority of the 
Secretary of State for~Work and~Pensions.
%I concur

{\raggedleft
\emph{Stephen C.~Timms}\\*
Minister
%Parliamentary Under-Secretary 
of State,\\*Department for~Work and~Pensions

}

25th September 2008

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Order)}

This Order brings into force provisions of the Child Support, Pensions and Social Security Act 2000 (c.~19) as follows:

Article 2 brings fully into force section~12, which amends section~14 of the Child Support Act 1991 (“the 1991 Act”) (c.~48), on 26th September 2008.

Article 3 brings into force paragraph~11(16) of Schedule~3, which amends section~32 of the 1991 Act, on 26th September 2008 for regulation making purposes and on 27th October 2008 for all other purposes.

Article 4 brings fully into force section~23, which abolishes the child maintenance bonus, on 27th October 2008.

A full impact assessment has not been produced for this instrument as it has no impact on the private or voluntary sectors. 

\end{document}