\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support, Pensions and Social Security Act 2000 (Commencement No.~15) Order 2014}

\newcommand\regsnumber{2014/1263}

\title{\regstitle}

\author{S.I.\ 2014 No.\ 1263 (C.~51)}

\date{Made
%12th March 2014\\
%%%Laid before Parliament
%%%27th June 2013\\
%Coming into force
15th May 2014
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

%\setlength\headheight{27.61603pt}

%\hbadness=10000

\begin{document}

\maketitle

\enlargethispage{\baselineskip}

\noindent
The Secretary of State for Work and Pensions, in exercise of the powers conferred by section 86(2) of the Child Support, Pensions and Social Security Act 2000\footnote{2000 c.~19.}, makes the following Order: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation]{Citation}

1.  This Order may be cited as the Child Support, Pensions and Social Security Act 2000 (Commencement No.~15) Order 2014.

\subsection[2. Appointed day for section 25]{Appointed day for section 25}

2.  Section 25 of the Child Support, Pensions and Social Security Act 2000 comes into force on the day after the day on which this Order is made, in so far as it is not already in force.  

\bigskip

\pagebreak[3]

Signed 
by authority of the 
Secretary of State for~Work and~Pensions.
%I concur
%By authority of the Lord Chancellor

{\raggedleft
\emph{Steve Webb}\\*
%Secretary
Minister
%Parliamentary Under Secretary 
of State\\*Department 
for~Work and~Pensions

}

15th May 2014

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Order)}

This Order brings into force section 25 of the Child Support, Pensions and Social Security Act 2000 (c.~19) (“the 2000 Act”) in respect of the purposes for which it is not already in force.

Section 25 of the 2000 Act amended section 52 of the Child Support Act 1991 (c.~48).

Section 25 of the 2000 Act was brought into force for the purpose of making regulations on 10th November 2000 by the Child Support, Pensions and Social Security Act 2000 (Commencement No.~3 Order 2000 (S.I.~2000/2994).

Section 25 of the 2000 Act was brought into force for certain purposes on 3rd March 2003 by the Child Support, Pensions and Social Security Act 2000 (Commencement No.~12) Order 2003 (S.I.~2003/192). These purposes related to applications under the 2003 and 2012 schemes of child support maintenance.

This Order brings section 25 of the 2000 Act into force for remaining purposes, namely applications for child support maintenance made under the 1992 scheme.

A full impact assessment has not been produced for this instrument as it has no impact on the private or voluntary sectors. 

\end{document}