\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support (Miscellaneous Amendments) Regulations 2006}

\newcommand\regsnumber{2006/1520}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2006 No.\ 1520}

\date{Made
13th June 2006\\
Laid before Parliament
16th June 2006\\
Coming into force
in accordance with regulation 1
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{42.11603pt}

\hbadness=10000

\begin{document}

\maketitle

\noindent
The Secretary of State for Work and Pensions makes the following Regulations in exercise of the powers conferred on him by sections 14(1), 16(4), 29(2) and (3), 32, 34, 40B(3), 52(4) and 54 of, and paragraph 11 of Part II of Schedule 1 to, the Child Support Act 1991\footnote{1991 c.\ 48. Section 16 was substituted by section 40 of the Social Security Act 1998 (c.\ 14). Section 29(2) and (3) and paragraph 11 of Part II of Schedule 1 were amended by section 1(2)($a$)  and ($b$)  of the Child Support, Pensions and Social Security Act 2000 (c.\ 19); section 14(1) was amended by section 12 of, and paragraph 11(7) of Schedule 3 to, that Act; section 32 was amended by paragraph 16 of Schedule 3 to that Act and section 40B was inserted by section 16(3) of that Act. Section 54 is cited for the meaning given to the word “prescribed”.}: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and commencement]{Citation and commencement}

1.---(1)  These Regulations may be cited as the Child Support (Miscellaneous Amendments) Regulations 2006 and, subject to paragraph (2), come into force on 12th July 2006.

(2) Where, in relation to a particular case, paragraph 11(16) of Schedule 3 to the Child Support, Pensions and Social Security Act 2000\footnote{2000 c.\ 19. See article 3 of S.I.\ 2003/192 for the commencement of paragraph 11(16) of Schedule 3 to that Act.} has not come into force before 12th July 2006, regulation 3(3) shall come into force for the purposes of that case on the day on which that paragraph comes into force.

\subsection[2. Amendment of the Child Support (Information, Evidence and Disclosure) Regulations 1992]{Amendment of the Child Support (Information, Evidence and Disclosure) Regulations 1992}

2.---(1)  The Child Support (Information, Evidence and Disclosure) Regulations 1992\footnote{S.I.\ 1992/1812. Relevant amendments were made by S.I.\ 2001/161 and 2002/1204.} are amended as follows.

(2) In regulation 2 (persons under a duty to furnish information or evidence)—
\begin{enumerate}\item[]
($a$) at the end of paragraph (2)($g$)  omit “and”;

($b$) at the end of paragraph (2)($h$)  insert “and”;

($c$) after sub-paragraph (2)($h$)  insert—
\begin{quotation}
“($i$) a credit reference agency within the meaning given by section 145(8) of the Consumer Credit Act 1974\footnote{1974 c.\ 39.} with respect to the matters listed in sub-paragraphs ($d$), ($e$), ($m$)  and ($n$)  of regulation 3(1).”.
\end{quotation}
\end{enumerate}

(3) In regulation 3 (purposes for which information or evidence may be required) after paragraph (1)($l$)  insert—
\begin{quotation}
“($m$)  an assessment of the financial standing of the non-resident parent;

($n$) an amount of, or an amount treated as, overpaid child support maintenance, to be recovered in accordance with section 41B of the Act\footnote{Section 41B was inserted by section 23 of the Child Support Act 1995 (c.\ 34).} (repayment of overpaid child support maintenance) and regulations made under or by virtue of that section, from a relevant person.”.
\end{quotation}

\subsection[3. Amendment of the Child Support (Collection and Enforcement) Regulations 1992]{Amendment of the Child Support (Collection and Enforcement) Regulations 1992}

3.---(1)  The Child Support (Collection and Enforcement) Regulations 1992\footnote{S.I.\ 1992/1989. Relevant amendments were made by S.I.\ 2001/162.} are amended as follows.

(2) In regulation 3 (method of payment)—
\begin{enumerate}\item[]
($a$) after paragraph (1)($f$)  add—
\begin{quotation}
“($g$) by credit card;

($h$) by a voluntary deduction from earnings arrangement.”;
\end{quotation}

($b$) for paragraph (1A) substitute—
\begin{quotation}
“(1A) In paragraph (1)—
\begin{enumerate}\item[]
($a$) “debit card” means a card, operating as a substitute for a cheque, that can be used to obtain cash or to make a payment at a point of sale whereby the card holder’s bank or building society account is debited without deferment of payment;

($b$) “credit card” means a card which is a credit-token within the meaning of section 14(1)($b$)  of the Consumer Credit Act 1974\footnote{1974 c.\ 39.};

($c$) “voluntary deduction from earnings arrangement” means an arrangement under which the liable person and his employer agree that payments of child support maintenance are to be deducted from the liable person’s earnings and paid to the Secretary of State.”.
\end{enumerate}
\end{quotation}
\end{enumerate}

(3) In regulation 11(2) (protected earnings proportion) for the words from “as calculated” to the end substitute—
\begin{quotation}
    “as calculated—
\begin{enumerate}\item[]
    ($a$) 
    at the date of the current maintenance calculation; or

    ($b$) 
    if the deduction from earnings order relates only to arrears of child support maintenance, at the date on which the order is made or varied.”. 
\end{enumerate}
\end{quotation}

(4) In regulation 26 (liability orders – extent of Part IV) for “regulation 29(2)” substitute “regulations 29(2) and 35(5)”.

(5) In regulation 28 (application for a liability order)—
\begin{enumerate}\item[]
($a$) for paragraph (2) substitute—
\begin{quotation}
“(2) Subject to paragraph (2A), there is no period of limitation in relation to an application under paragraph (1).”;
\end{quotation}

($b$) after paragraph (2) insert—
\begin{quotation}
“(2A) An application under paragraph (1) may not be instituted in respect of an amount payment of which became due on or before 12th July 2000.”.
\end{quotation}
\end{enumerate}

\subsection[4. Amendment of the Social Security and Child Support (Decisions and Appeals) Regulations 1999]{Amendment of the Social Security and Child Support (Decisions and Appeals) Regulations 1999}

4.---(1)  The Social Security and Child Support (Decisions and Appeals) Regulations 1999\footnote{S.I.\ 1999/991. Regulation 5A was inserted by S.I.\ 2000/3185 and amended by S.I.\ 2003/129.} are amended in accordance with paragraph (2).

(2) In regulation 5A (date from which a decision revised under section 16 of the Child Support Act takes effect) omit paragraphs (2) and (3).

\subsection[5. Amendment of the Child Support (Maintenance Calculation Procedure) Regulations 2000]{Amendment of the Child Support (Maintenance Calculation Procedure) Regulations 2000}

5.  After regulation 29 of the Child Support (Maintenance Calculation Procedure) Regulations 2000\footnote{S.I.\ 2001/157. Regulation 25 was amended by S.I.\ 2003/328, regulation 28 was amended by S.I.\ 2002/1204 and regulation 29 was amended by S.I.\ 2002/1204, 2003/328 and 2004/2415.} (effective dates of maintenance calculations in specified cases) insert—
\begin{quotation}
\subsection*{“Interim effective date where regulation 25, 28 or 29 applies}

29A.---(1)  Where the Secretary of State has sufficient information to enable him to make a maintenance calculation, but only in respect of a period beginning after the date which would have been the effective date under regulation 25, 28 or 29 (“the original effective date”), the effective date of that calculation (“the interim effective date”) shall, instead, be the first day of the maintenance period after the Secretary of State receives that information.

(2) Where the information referred to in paragraph (1) is that the non-resident parent or his partner has been awarded any benefit, pension or allowance prescribed for the purposes of paragraph 4 of Schedule 1 to the Act\footnote{Paragraph 4 of Schedule 1 was substituted by section 1(3) of the Child Support, Pensions and Social Security Act 2000 (c.\ 19).} (flat rate), the Secretary of State shall be treated as having received the information on the first day in respect of which that benefit, pension or allowance was payable under that award.

(3) If the Secretary of State subsequently receives sufficient information to enable him to make a maintenance calculation for the period from the original effective date to the interim effective date, that calculation shall have effect for that period.”.
\end{quotation}

\subsection[6. Amendment of the Child Support (Collection and Enforcement and Miscellaneous Amendments) Regulations 2000]{Amendment of the Child Support (Collection and Enforcement and Miscellaneous Amendments) Regulations 2000}

6.---(1)  The Child Support (Collection and Enforcement and Miscellaneous Amendments) Regulations 2000\footnote{S.I.\ 2001/162. Regulation 1(2A) was inserted by S.I.\ 2001/1775.} are amended as follows.

(2) In regulation 1 (citation, commencement and interpretation) after paragraph (2A) insert—
\begin{quotation}
“(2B) Regulation 2(3)($b$)(ii) and ($c$)  shall, to the extent that those provisions are not already in force on 12th July 2006, come into force on that date.”.
\end{quotation}

(3) In regulation 6(1) (savings)—
\begin{enumerate}\item[]
($a$) insert “or” at the end of sub-paragraph ($a$)  and head (i);

($b$) omit “or” at the end of sub-paragraph ($b$)  and head (ii); and

($c$) omit sub-paragraph ($c$)  and head (iii).
\end{enumerate}

\bigskip

Signed 
by authority of the 
Secretary of State for Work and Pensions.

{\raggedleft
\emph{Philip Hunt}\\*Parliamentary Under Secretary of State,\\*Department for Work and Pensions

}

13th June 2006

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations make miscellaneous amendments to regulations relating to child support.

The powers exercised to make these Regulations are those contained in the Child Support Act 1991 (“the 1991 Act”), as amended by the Child Support, Pensions and Social Security Act 2000 (“the 2000 Act”). Some of the amendments made by the 2000 Act are only in force for the purposes of specified categories of case (see the Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 12) Order 2003) (“the new scheme”). In all other cases the 1991 Act prior to those amendments continues to apply (“the old scheme”).

Regulation 1 deals with citation and commencement. The Regulations come into force on 12th July 2006, save that regulation 3(3) (which relates to deduction from earnings orders) only comes into force for cases under the new scheme.

Regulation 2 amends the Child Support (Information, Evidence and Disclosure) Regulations 1992 (S.I.\ 1992/1812) by making provision for credit reference agencies to be required to furnish information to the Secretary of State.

Regulation 3 makes a number of amendments to the Child Support (Collection and Enforcement) Regulations 1992 (S.I.\ 1992/1989). First, it extends the range of arrangements for collection of child support by adding payment by credit card and voluntary deduction from earnings arrangements (paragraph (2)). Secondly, it provides a basis for calculating the protected earnings proportion in relation to a deduction from earnings order which relates only to arrears of child support maintenance (paragraph (3)). Thirdly, it extends to Scotland the provision for determining the costs in relation to a disqualification from driving order (paragraph (4)). Lastly, it removes the 6 year limitation period for an application for a liability order, but only in relation to amounts that became due after 12th July 2000 (that is amounts which were not already time barred at the commencement of these Regulations) (paragraph (5)).

Regulation 4 amends the Social Security and Child Support (Decisions and Appeals) Regulations 1999 (S.I.\ 1999/991) by revoking the provision which specifies an effective date in a case where a default maintenance decision is revised as if it were a maintenance calculation under section 11 of the Act.

Regulation 5 amends the Child Support (Maintenance Calculation Procedure) Regulations 2000 (S.I.\ 2001/157) by providing for an interim effective date for the initial calculation of child support maintenance in cases where the available information does not cover the whole of the relevant period.

Regulation 6 amends the Child Support (Collection and Enforcement and Miscellaneous Amendments) Regulations 2000 (S.I.\ 2001/162) in two respects. First, it amends the commencement provisions so as to bring fully into force (that is for both old and new scheme cases) the amendments in those Regulations which make provision for collection of child support maintenance by debit card (paragraph (2)). Secondly, it amends the savings provision in regulation 6 so that, in cases which have been converted from the old scheme to the new scheme, all arrears of child support maintenance, whenever they accrued, are treated the same for collection and enforcement purposes (paragraph (3)).

These Regulations do not impose any costs on business, charities or the voluntary sector. 

\end{document}