\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support (Information, Evidence and Disclosure) Amendment Regulations 2003}

\newcommand\regsnumber{2003/3206}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2003 No.\ 3206}

\date{Made
9th December 2003\\
Laid before Parliament
15th December 2003\\
Coming into force
7th January 2004
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.57402pt}

\begin{document}

\maketitle

\noindent
The Secretary of State for Work and Pensions, in exercise of the powers conferred upon him by sections 14(1), 51(1) and (2)($g$), 52(4), 54 and 57(1) of the Child Support Act 1991\footnote{1991 c.\ 48. Section 14(1) is amended by section 12 of, and paragraph 11(7) of Schedule 3 to, the Child Support, Pensions and Social Security Act 2000 (c.\ 19); those amendments are not in force for the purposes of the cases to which the amendments made by these Regulations apply. Section 54 is cited for the definition of “prescribed”.} and of all other powers enabling him in that behalf, hereby makes the following Regulations: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation, commencement and effect]{Citation, commencement and effect}

1.---(1)  These Regulations may be cited as the Child Support (Information, Evidence and Disclosure) Amendment Regulations 2003.

(2) Subject to paragraph (3), these Regulations shall come into force on 7th January 2004.

(3) These Regulations shall have effect only for the purposes of any case in respect of which section 12 of the Child Support, Pensions and Social Security Act 2000 (information required by the Secretary of State)\footnote{2000 c.\ 19. \emph{See} S.I.\ 2003/192 (C.11).} has not come into force and for so long as that section is not in force for the purposes of such a case.

\subsection[2. Amendment of the Child Support (Information, Evidence and Disclosure) Regulations 1992]{Amendment of the Child Support (Information, Evidence and Disclosure) Regulations 1992}

2.---(1)  The Child Support (Information, Evidence and Disclosure) Regulations 1992\footnote{S.I.\ 1992/1812; relevant amendments have been made by S.I.\ 1995/123, 1045 and 3261, 1996/1945 and 1999/1510 (C.43); further amendments are made by S.I.\ 2001/161 and S.I.\ 2002/1204 but those amendments are not in force for the purposes of the cases to which the amendments made by these Regulations apply.} shall be amended in accordance with the following paragraphs.

(2) In regulation 2 (persons under a duty to furnish information or evidence)—
\begin{enumerate}\item[]
($a$) in paragraph (1), for “to enable a decision to be made under section 11, 12, 16 or 17 of the Act” substitute “and is needed for any of the purposes specified in regulation 3(1)”; and

($b$) for paragraph (1A), substitute—
\begin{quotation}
“(1A) In such cases as the Secretary of State may determine, a person falling within a category listed in paragraph (2) shall furnish such information or evidence as the Secretary of State may determine which is information or evidence—
\begin{enumerate}\item[]
($a$) with respect to the matter or matters specified in that paragraph in relation to that category;

($b$) needed by the Secretary of State for the purpose specified in regulation 3(1A); and

($c$) in that person’s possession or which that person can reasonably be expected to acquire.”.
\end{enumerate}
\end{quotation}
\end{enumerate}

(3) In regulation 3 (purposes for which information or evidence may be required), after paragraph (1) insert—
\begin{quotation}
“(1A) The Secretary of State may require information or evidence to be provided under the provisions of regulation 2(1A) only for the purpose of verifying whether information or evidence which he holds, or has held, is correct.”.
\end{quotation}

\bigskip

Signed 
by authority of the Secretary of State for Work and Pensions.

{\raggedleft
\emph{P.~Hollis}\\*Parliamentary Under-Secretary of State,\\*Department of Work and Pensions

}

%St Andrew's House, Edinburgh

%Dated
9th December 2003

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations further amend the Child Support (Information, Evidence and Disclosure) Regulations 1992, which provide for information or evidence to be furnished in connection with the determination of any application under the Child Support Act 1991. The amendments made by these Regulations apply to cases in respect of which section 12 of the Child Support, Pensions and Social Security Act 2000 has not come into force. The amendments made by regulation 2 enable information or evidence to be required for the purposes of verifying, in such cases as the Secretary of State may determine, such information or evidence that he holds, or has held, as he may determine.

A full regulatory impact assessment has not been produced for this instrument as it has no impact on the costs of business. 

\end{document}