\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support (Consequential Provisions) (No.~2) Regulations 2008}

\newcommand\regsnumber{2008/2656}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and~Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2008 No.\ 2656}

\date{Made
7th October 2008\\
Laid before Parliament
10th October 2008\\
Coming into~force
1st November 2008
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{42.11603pt}

%\hbadness=10000

\begin{document}

\maketitle

\noindent
The Secretary of State makes the following Regulations in exercise of the powers conferred by section~57(2) of the Child Maintenance and Other Payments Act 2008\footnote{2008 c.~6.}: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and commencement]{Citation and commencement}

1.  These Regulations may be cited as the Child Support (Consequential Provisions) (No.~2) Regulations 2008 and shall come into force on 1st November 2008.

\subsection[2. The Employment Act 2002]{The Employment Act 2002}

2.  In section~13(2) of the Employment Act 2002\footnote{2002 c.~22.} (supply of information held by the Board)—
\begin{enumerate}\item[]
($a$) in paragraphs ($a$)  and ($b$), after “Secretary of State” in each place it occurs, insert “, the Child Maintenance and Enforcement Commission”; and

($b$) after “war pensions” add “and in relation to the Child Maintenance and Enforcement Commission, any function of that Commission”.
\end{enumerate}

\subsection[3. The Sexual Offences Act 2003]{The Sexual Offences Act 2003}

3.---(1)  The Sexual Offences Act 2003\footnote{2003 c.~42.} is amended as follows.

(2) In section~94 (Part~II: supply of information to Secretary of State etc for verification)—
\begin{enumerate}\item[]
($a$) in subsection~(2)—
\begin{enumerate}\item[]
(i) after paragraph ($a$)  insert—
\begin{quotation}
“($aa$) the Child Maintenance and Enforcement Commission,”; and
\end{quotation}

(ii) in paragraph ($c$), after “Secretary of State” insert “, the Child Maintenance and Enforcement Commission”;
\end{enumerate}

($b$) in subsection~(4), in paragraph ($a$)(i)  after “Secretary of State” insert “, the Child Maintenance and Enforcement Commission”; and

($c$) in subsection~(8), in the definition of “relevant function” after paragraph ($a$)  insert—
\begin{quotation}
“($aa$) in relation to the Child Maintenance and Enforcement Commission, any function of that Commission,”.
\end{quotation}
\end{enumerate}

(3) In section~95 (Part~II: supply of information by Secretary of State etc)—
\begin{enumerate}\item[]
($a$) in subsection~(1), after paragraph ($a$)  insert—
\begin{quotation}
“($aa$) the Child Maintenance and Enforcement Commission,”; and
\end{quotation}

($b$) in subsection~(3)($a$), after “Secretary of State” insert “, the Child Maintenance and Enforcement Commission”.
\end{enumerate}

\subsection[4. The Social Security and Child Support (Decisions and Appeals) Regulations 1999]{The Social Security and Child Support (Decisions and Appeals) Regulations 1999}

4.---(1)  Regulation 1(3) of the Social Security and Child Support (Decisions and Appeals) Regulations 1999\footnote{S.I.~1999/991, amended by S.I.~2002/1379, S.I.~1999/2570 and S.I.~2008/2544; there are other amending instruments but none is relevant.} (interpretation) is amended as follows.

(2) After the definition of “clerk to the appeal tribunal” insert—
\begin{quotation}
““the Commission” means the Child Maintenance and Enforcement Commission;”.
\end{quotation}

(3) In paragraph ($a$)  of the definition of “official error”—
\begin{enumerate}\item[]
($a$) after the words “Work and Pensions” insert “, the Commission”; and

($b$) after the words “the Department” insert “, the Commission” in each place it occurs.
\end{enumerate}

(4) In the definition of “party to the proceedings” after “the Secretary of State” insert “or where the proceedings relate to child support, the Commission”. 

\bigskip

%Signed 
%by authority of the 
%Secretary of State for~Work and~Pensions.
%I concur

{\raggedleft
\emph{James Purnell}\\*
Secretary
%Minister
%Parliamentary Under-Secretary 
of State %,\\*Department 
for~Work and~Pensions

}

7th October 2008

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations make provision consequential on the coming into force of section~13 of the Child Maintenance and Other Payments Act 2008 (c.~6).

The Regulations insert references to the Child Maintenance and Enforcement Commission in, and make other related amendments to, the following legislation:
\begin{itemize}
\item    the Employment Act 2002
\item
    the Sexual Offences Act 2003
\item
    the Social Security and Child Support (Decisions and Appeals) Regulations 1999. 
\end{itemize}

A full impact assessment has not been published for this instrument as it has no impact on the costs of business, charities and the voluntary sector. 

\end{document}