\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support (Miscellaneous Amendments) Regulations 2008}

\newcommand\regsnumber{2008/536}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2008 No.\ 536}

\date{Made
27th February 2008\\
Laid before Parliament
4th March 2008\\
Coming into force
6th April 2008
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{42.11603pt}

\hbadness=10000

\begin{document}

\maketitle

\noindent
The Secretary of State for Work and Pensions, in exercise of the powers conferred by sections 14(1), 32(1), (3)($a$), (8) and (9) and 54 of the Child Support Act 1991\footnote{1991 c.\ 48. Section 14(1) was amended by section 12 of, and paragraph 11(7) of Schedule 3 to, the Child Support, Pensions and Social Security Act 2000 (c.\ 19). Section 54 is cited for the meaning given to the word “prescribed”.}, makes the following Regulations: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and commencement]{Citation and commencement}

1.  These Regulations may be cited as the Child Support (Miscellaneous Amendments) Regulations 2008 and shall come into force on 6th April 2008.

\subsection[2. Amendment of the Child Support (Information, Evidence and Disclosure) Regulations 1992]{Amendment of the Child Support (Information, Evidence and Disclosure) Regulations 1992}

2.---(1)  The Child Support (Information, Evidence and Disclosure) Regulations 1992\footnote{S.I.\ 1992/1812. Relevant amendments were made by S.I.\ 1996/1945, 2001/161, 2002/1204, 2006/1520 and 2007/1979.} are amended as follows.

(2) In regulation 1(2) (citation, commencement and interpretation), after the definition of “appropriate authority”, insert the following definition:
\begin{quotation}
““deposit-taker” means a person who, in the course of a business, may lawfully accept deposits in the United Kingdom;”.
\end{quotation}

(3) In regulation 2(2) (persons under a duty to furnish information or evidence)—
\begin{enumerate}\item[]
($a$) in sub-paragraph ($h$)(i), for “($e$)” substitute “($d$), ($e$)  and ($o$)”;

($b$) at the end of sub-paragraph ($h$)(ii) omit “and”;

($c$) in sub-paragraph ($i$), for “and ($n$)” substitute “, ($n$)  and ($o$)”;

($d$) after sub-paragraph ($i$) insert—
\begin{quotation}
“($j$) a deposit-taker with respect to the matters listed in sub-paragraphs ($d$), ($e$), ($f$)  and ($o$)  of regulation 3(1).”.
\end{quotation}
\end{enumerate}

(4) In regulation 3(1) (purposes for which information or evidence may be required) after sub-paragraph ($n$)  insert—
\begin{quotation}
“($o$) the collection and enforcement of child support maintenance payable and amounts payable under a relevant court order.”.
\end{quotation}

\subsection[3. Amendment of the Child Support (Collection and Enforcement) Regulations 1992]{Amendment of the Child Support (Collection and Enforcement) Regulations 1992}

3.---(1)  The Child Support (Collection and Enforcement) Regulations 1992\footnote{S.I.\ 1992/1989.} are amended as follows.

(2) For regulation 15 (information to be provided by liable person), substitute—
\begin{quotation}
“15.---(1)  A liable person in respect of whom a deduction from earnings order is in force must notify the Secretary of State in writing within 7 days of each occasion on which he leaves employment or becomes employed, or re-employed.

(2) If a liable person becomes employed or re-employed, such notification must include the following details—
\begin{enumerate}\item[]
($a$) the name and address of his employer;

($b$) the amount of his earnings and expected earnings; and

($c$) his place of work, nature of his work and any works or pay number.”
\end{enumerate}
\end{quotation}

\bigskip

Signed 
by authority of the 
Secretary of State for Work and Pensions.

{\raggedleft
\emph{James Plaskitt}\\*Parliamentary Under-Secretary of State,\\*Department for Work and Pensions

}

27th February 2008

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations make miscellaneous amendments to regulations relating to child support.

Regulation 1 deals with citation and commencement. These Regulations come into force on 6th April 2008.

Regulation 2 makes a number of amendments to the Child Support (Information, Evidence and Disclosure) Regulations 1992 (S.I.\ 1992/1812). It extends the purposes for which the DVLA and credit reference agencies may be required to furnish information to the Secretary of State. It makes provision for deposit-takers, for example, banks and building societies, to be required to furnish information to the Secretary of State for various purposes. It extends the purposes for which information or evidence may be required to include information or evidence needed to enable the collection and enforcement of child support maintenance payable or amounts payable under a relevant court order.

Regulation 3 amends the Child Support (Collection and Enforcement) Regulations 1992 (S.I.\ 1992/1989). It sets out the information which a liable person subject to a deduction from earnings order must provide on leaving employment or becoming employed, or re-employed. It is an offence if a liable person does not provide such information.

An Impact Assessment of the effect of this instrument on the costs of business has been prepared and may be obtained from the CSA Policy Team, Department for Work and Pensions, 5th Floor Caxton House, Tothill Street, London \textsc{\lowercase{SW1H 9NA}}. It is also available on the Department for Work and Pensions’ website \url{http://www.dwp.gov.uk/resourcecentre/ria.asp}. A copy has been placed in the library of both Houses of Parliament. 

\end{document}