\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support (Consequential Amendments and Transitional Provisions) Regulations 2001}

\newcommand\regsnumber{2001/158}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2001 No.\ 158}

\date{Made
24th January 2001\\
Laid before Parliament
25th January 2001\\
Coming into force
as provided in regulation 1(2) and (3)
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.57402pt}

\begin{document}

\maketitle

\noindent
The Secretary of State for Social Security, in exercise of the powers conferred upon him by section 29(2) of the Child Support, Pensions and Social Security Act 2000\footnote{2000 c.\ 19.}, and of all other powers enabling him in that behalf, hereby makes the following Regulations: 

\enlargethispage{\baselineskip}

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\section[Part I --- General]{Part I\\*General}

\renewcommand\parthead{--- Part I}

\subsection[1. Citation and commencement]{Citation and commencement}

1.---(1)  These Regulations may be cited as the Child Support (Consequential Amendments and Transitional Provisions) Regulations 2001.

(2) Regulation 11 and, for the purposes of that provision, this regulation and regulation 2, shall come into force on 15th February 2001.

(3) The remainder of these Regulations shall come into force in relation to a particular case on the date on which section 1 of the 2000 Act comes into force in relation to that type of case.

\subsection[2. Interpretation]{Interpretation}

2.  In these Regulations—
\begin{enumerate}\item[]
“the 2000 Act” means the Child Support, Pensions and Social Security Act 2000;

“the Act” means the Child Support Act 1991\footnote{1991 c.\ 48.};

\enlargethispage{-\baselineskip}

“the Community Action (Miscellaneous Provisions) Order” means the Community Action (Miscellaneous Provisions) Order 1993\footnote{S.I.\ 1993/1621.};

“the Decisions and Appeals Regulations” means the Social Security and Child Support (Decisions and Appeals) Regulations 1999\footnote{S.I.\ 1999/991. Relevant amending instruments are S.I.\ 1999/2570 and 2677.};

“the former Act” means the Act prior to its amendment by the 2000 Act;

“the Guardian’s Allowances Regulations” means the Social Security (Guardian’s Allowances) Regulations 1975\footnote{S.I.\ 1975/515. Relevant amending instrument is S.I.\ 1998/811.};

“the Income Support Regulations” means the Income Support (General) Regulations 1987\footnote{S.I.\ 1987/1967. Relevant amending instruments are S.I.\ 1993/846 and 1999/3178.};

“the Jobseeker’s Allowance Regulations” means the Jobseeker’s Allowance Regulations 1996\footnote{S.I.\ 1996/207. Relevant amending instrument is S.I.\ 1999/2860.};

“the Maintenance Payments Regulations” means the Social Security Benefits (Maintenance Payments and Consequential Amendments) Regulations 1996\footnote{S.I.\ 1996/940.};

“the New Deal (25 plus) (Miscellaneous Provisions) Order” means the New Deal (25 plus) (Miscellaneous Provisions) Order 1999\footnote{S.I.\ 1999/779.};

“the New Deal (Miscellaneous Provisions) Order” means the New Deal (Miscellaneous Provisions) Order 1998\footnote{S.I. 1998/217.\ Relevant amending instrument is S.I.\ 1998/1425.};

“the North Norfolk Action (Miscellaneous Provisions) Order” means the North Norfolk Action (Miscellaneous Provisions) Order 1993\footnote{S.I.\ 1993/1065.};

“the Project Work (Miscellaneous Provisions) Order” means the Project Work (Miscellaneous Provisions) Order 1996\footnote{S.I.\ 1996/1623.}; and

“the Training for Work (Miscellaneous Provisions) Order” means the Training for Work (Miscellaneous Provisions) Order 1995\footnote{S.I.\ 1995/1780. Relevant amending instrument is S.I.\ 1998/1426.}.
\end{enumerate}

\section[Part II --- Consequential amendments]{Part II\\*Consequential amendments}

\renewcommand\parthead{--- Part II}

\subsection[3. Amendment of the Community Action (Miscellaneous Provisions) Order and the North Norfolk Action (Miscellaneous Provisions) Order]{\sloppy Amendment of the Community Action (Miscellaneous Provisions) Order and the North Norfolk Action (Miscellaneous Provisions) Order}

3.  To the list of subordinate legislation specified respectively in the Schedule to the Community Action (Miscellaneous Provisions) Order and the Schedule to the North Norfolk Action (Miscellaneous Provisions) Order, there shall be added “The Child Support (Maintenance Calculations and Special Cases) Regulations 2000\footnote{S.I.\ 2001/155.}”.

\subsection[4. Amendment of the Decisions and Appeals Regulations]{Amendment of the Decisions and Appeals Regulations}

4.---(1)  The Decisions and Appeals Regulations shall be amended as provided in the following paragraphs.

(2) In regulations 23(2)($b$)  and (5) and 44(1)($a$), (2) and (3), for the words “absent parent” wherever they appear there shall be substituted the words “non-resident parent”.

(3) In regulation 23(3)($a$)  for the word “assessment” there shall be substituted the word “calculation”.

(4) In regulation 33(1)($a$)(i) and (2)($d$)  the words “as extended by paragraph 3 of Schedule 4C to that Act” shall be omitted.

(5) In regulation 44(2), for the word “direction” there shall be substituted the word “decision” and for the words “section 46(11)” there shall be substituted the words “section 46(10)($b$)”.

\subsection[5. Amendment of the Guardian’s Allowances Regulations]{Amendment of the Guardian’s Allowances Regulations}

5.  In regulation 4(1)($b$)  of the Guardian’s Allowances Regulations, for the word “assessment” there shall be substituted “calculation”.

\subsection[6. Amendment of the Income Support Regulations]{Amendment of the Income Support Regulations}

6.---(1)  The Income Support Regulations shall be amended as provided in the following paragraphs.

(2) In regulations 60A and 60C(6)($a$), for the word “assessment” there shall be substituted “calculation”.

(3) In paragraph 14(2) of Schedule 3—
\begin{enumerate}\item[]
($a$) subject to sub-paragraph ($b$), for the word “assessment” wherever it appears there shall be substituted “calculation”; and

($b$) in sub-paragraph ($b$), for the words “interim maintenance assessment” wherever they appear there shall be substituted “interim maintenance decision or default maintenance decision”.
\end{enumerate}

\subsection[7. Amendment of the Jobseeker’s Allowance Regulations]{Amendment of the Jobseeker’s Allowance Regulations}

7.---(1)  The Jobseeker’s Allowance Regulations shall be amended as provided in the following paragraphs.

(2) In regulations 125 and 128(6)($a$), for the word “assessment” there shall be substituted “calculation”.

(3) In paragraph 13(2) of Schedule 2—
\begin{enumerate}\item[]
($a$) subject to sub-paragraph ($b$), for the word “assessment” wherever it appears there shall be substituted “calculation”; and

($b$) in sub-paragraph ($b$), for the words “interim maintenance assessment” wherever they appear there shall be substituted “interim maintenance decision or default maintenance decision”.
\end{enumerate}

\subsection[8. Amendment of the Maintenance Payments Regulations]{Amendment of the Maintenance Payments Regulations}

8.  In regulation 2($a$)(ii) of the Maintenance Payments Regulations, for the word “assessment” there shall be substituted “calculation”.

\subsection[9. Amendment of the New Deal (25 plus) (Miscellaneous Provisions) Order, the New Deal (Miscellaneous Provisions) Order, the Project Work (Miscellaneous Provisions) Order and the Training for Work (Miscellaneous Provisions) Order]{Amendment of the New Deal (25 plus) (Miscellaneous Provisions) Order, the New Deal (Miscellaneous Provisions) Order, the Project Work (Miscellaneous Provisions) Order and the Training for Work (Miscellaneous Provisions) Order}

\enlargethispage{\baselineskip}

9.  To the list of subordinate legislation specified respectively in the Schedule to the New Deal (25 plus) (Miscellaneous Provisions) Order, the Schedule to the New Deal (Miscellaneous Provisions) Order, the Schedule to the Project Work (Miscellaneous Provisions) Order and the Schedule to the Training for Work (Miscellaneous Provisions) Order there shall be added “The Child Support (Maintenance Calculations and Special Cases) Regulations 2000\footnote{S.I.\ 2001/155.}” and “The Child Support (Maintenance Calculation Procedure) Regulations 2000\footnote{S.I.\ 2001/157.}”.

\section[Part III --- Savings]{Part III\\*Savings}

\renewcommand\parthead{--- Part III}

\subsection[10. Savings for particular cases]{Savings for particular cases}

10.---%
% Reg 6(Z1) inserted (3.3.03) by SI 2001/162 reg 2(3), (4)(a)
(Z1) This regulation is subject to the Child Support (Transitional Provisions) Regulations 2000.

(1)  Where, in respect of a particular case there is a maintenance assessment the effective date of which is before the date that these Regulations come into force with respect to that type of case (“the commencement date”), these Regulations shall not apply for the purposes of—
\begin{enumerate}\item[]
($a$) the Guardian’s Allowances Regulations, in relation to a parent who died on or before the commencement date;

($b$) the Income Support Regulations, in relation to a person who is entitled to income support for a period beginning on or before the day before the commencement date;

($c$) the Jobseeker’s Allowance Regulations, in relation to a person who is entitled to a jobseeker’s allowance for a period beginning on or before the day before the commencement date; and

($d$) the Maintenance Payments Regulations, in relation to payment of child support maintenance under a maintenance assessment in a period beginning on or before the day before the commencement date.
\end{enumerate}

(2) These Regulations shall not apply with respect to the Income Support Regulations and the Jobseeker’s Allowance Regulations in relation to a person who is entitled to income support or a jobseeker’s allowance, as the case may be, for a period beginning on or before the day before the commencement date.

\amendment{
Reg. 10(Z1) inserted (3.3.03) by the Child Support (Transitional Provision) (Miscellaneous Amendments) Regulations 2003 reg. 2(3), (4)(b).
}

\section[Part IV --- Transitional provision]{Part IV\\*Transitional provision}

\renewcommand\parthead{--- Part IV}

\subsection[11. Transitional provision—redetermination of appeals]{Transitional provision—redetermination of appeals}

11.  In relation to any particular case, before the date on which these Regulations, except for this regulation, come into force for the purposes of that case, in section 23A(4)($b$)  of the Act\footnote{Section 23A was inserted by section 11 of the Child Support, Pensions and Social Security Act 2000.} the reference to “qualifying persons” shall be treated as a reference to any person referred to in section 20 of the former Act with a right of appeal under that section and the reference in section 23A(3) to “the principal parties” shall be construed accordingly. 

\bigskip

Signed 
by authority of the Secretary of State for Social Security.

{\raggedleft
\emph{P.~Hollis}\\*Parliamentary Under-Secretary of State,\\*Department of Social Security

}

24th January 2001

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations provide for the amendment of various Regulations and Orders and make savings and transitional provisions.

Part I (regulations 1 and 2) makes provision for citation, commencement and interpretation.

Part II (regulations 3 to 9) contains amendments to various provisions. Regulations 4 to 7 amend the Social Security and Child Support (Decisions and Appeals) Regulations 1999, the Social Security (Guardian’s Allowances) Regulations 1975, the Income Support (General) Regulations 1987, the Jobseeker’s Allowance Regulations 1996 and the Social Security Benefits (Maintenance Payments and Consequential Amendments) Regulations 1996. The amendments in regulations 4 to 8 reflect changes in terminology in the Child Support Act 1991 (c.\ 48) (“the Act”) in consequence of the amendment of the Act by the Child Support, Pensions and Social Security Act 2000 (c.\ 19) (“the 2000 Act”).

Regulations 3 and 9 amend the Community Action (Miscellaneous Provisions) Order 1993, the New Deal (25 plus) (Miscellaneous Provisions) Order 1999, the New Deal (Miscellaneous Provisions) Order 1998, the North Norfolk Action (Miscellaneous Provisions) Order 1993, the Project Work (Miscellaneous Provisions) Order 1996 and the Training for Work (Miscellaneous Provisions) Order 1995. Amendments are made to these Orders to include within the Schedules to the Orders references to the Child Support (Maintenance Calculations and Special Cases) Regulations 2000 and, where appropriate, the Child Support (Maintenance Calculation Procedure) Regulations 2000, to reflect the making of these new Regulations.

Part IV (regulation 10) contains savings provisions.

Part V (regulation 11) contains transitional provision for the redetermination of appeals under section 23A(4)($b$)  of the Act.

The impact on business of these Regulations was covered in the Regulatory Impact Assessment (RIA) for the 2000 Act, in accordance with which, and in consequence of which, these Regulations are made. A copy of that RIA has been placed in the libraries of both Houses of Parliament and can be obtained from the Department of Social Security, Regulatory Impact Unit, Adelphi, 1–11 John Adam Street, London \textsc{\lowercase{WC2N 6HT}}. 

\end{document}