\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Maintenance and~Other Payments Act 2008 (Commencement No.~4 and~Transitional Provision) Order 2008}

\newcommand\regsnumber{2008/2675}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and~Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2008 No.\ 2675 (C.~116)}

\date{Made
%7th October 2008\\
%Laid before Parliament
%10th October 2008\\
%Coming into~force
7th October 2008
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{42.11603pt}

%\hbadness=10000

\begin{document}

\maketitle

\noindent
The Secretary of State, in exercise of the powers conferred by sections 62(3) and~(4) of the Child Maintenance and~Other Payments Act 2008\footnote{2008 c.~6.}, makes the following Order: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and~interpretation]{Citation and~interpretation}

1.---(1)  This Order may be cited as the Child Maintenance and~Other Payments Act 2008 (Commencement No.~4 and~Transitional Provision) Order 2008.

(2) In this Order “the relevant date” means 1st November 2008.

(3) In this Order, except where otherwise stated, any reference to a numbered section or Schedule is a reference to a section of, or Schedule to, the Child Maintenance and~Other Payments Act 2008.

\subsection[2. Appointed day for paragraph~40($b$)  of Schedule 3]{Appointed day for paragraph~40(\textbf{\itshape b})  of Schedule 3}

2.  Paragraph 40($b$)  of Schedule 3 (transfer of child support functions) and~section 13, in so far as it relates to that sub-paragraph, come into force—
\begin{enumerate}\item[]
($a$) in relation to Scotland, immediately after paragraph~18($a$)(i)  of Schedule 5 to the Bankruptcy and~Diligence etc.\ (Scotland) Act 2007\footnote{2007 asp~3.} comes into force; and

\begin{sloppypar}
($b$) in relation to England~and~Wales, immediately after paragraph 18($a$)(i)  of Schedule 5 to the Bankruptcy and~Diligence etc.\ (Scotland) Act 2007 extends to England~and~Wales.
\end{sloppypar}
\end{enumerate}

\subsection[3. Appointed day for other provisions]{Appointed day for other provisions}

3.  The following provisions come into force on the relevant date—
\begin{enumerate}\item[]
($a$) section 3(1)($a$)  (functions of the Commission: general);

($b$) section 13 (transfer of child support functions) and~Schedules~2 and~3, except in relation to paragraph~40($b$)  of Schedule 3;

($c$) section 14 (transfer of property, rights and~liabilities);

($d$) section 44 and~Schedule 6 (use of information);

($e$) sections 57(1) and~58, so far as relating to the paragraphs and~entries referred to in sub-paragraphs ($f$)  and~($g$)  below;

($f$) paragraph~1(19), (20), (21) and~(33) of Schedule 7 (minor and~consequential amendments); and

($g$) in Schedule 8 (repeals), the entries relating to the repeals in—
\begin{enumerate}\item[]
(i) section 50(5) of, and~Schedule 2 to, the Child Support Act 1991\footnote{1991 c.~48.}; and

(ii) section 80 of the Welfare Reform and~Pensions Act 1999\footnote{1999 c.~30.}.
\end{enumerate}
\end{enumerate}

\subsection[4. Transitional provision]{Transitional provision}

4.  Where, on or after the relevant date, any document or notice relating to a function transferred to the Commission by virtue of section 13 is given or sent to any person by the Commission which contains a reference to the Secretary of State, that document or notice is not to be invalidated by virtue of that reference. 

\bigskip

%Signed 
%by authority of the 
%Secretary of State for~Work and~Pensions.
%I concur

{\raggedleft
\emph{James Purnell}\\*
Secretary
%Minister
%Parliamentary Under-Secretary 
of State %,\\*Department 
for~Work and~Pensions

}

7th October 2008

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

This Order brings into force provisions of the Child Maintenance and~Other Payments Act 2008 (“the Act”) (c.~6) as follows:

Article 2 commences paragraph~40($b$)  of Schedule 3 to the Act on different dates in relation to Scotland, and~England~and~Wales.

Article 3 brings various other provisions of the Act into force on 1st November 2008. These include sections 3(1)($a$)  and~13, which transfer child support functions from the Secretary of State to the Child Maintenance and~Enforcement Commission (“the Commission”), section 14, which enables the Secretary of State to make schemes for the transfer of property, rights and~liabilities to the Commission; Schedule 6 which provides for the use of information by the Commission, and~Schedules~7 and~8, which contain consequential provisions and~repeals.

Article 4 provides that, where any document or notice that relates to a function transferred to the Commission is sent to a person by the Commission on or after 1st November 2008, any reference in that document or notice to the Secretary of State is not to invalidate that document or notice.

A full impact assessment has not been published for this instrument as it has no impact on the costs of business, charities and~voluntary bodies. 

\end{document}