\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support (Miscellaneous Amendments) Regulations 2005}

\newcommand\regsnumber{2005/785}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2005 No.\ 785}

\date{Made
15th March 2005\\
%Laid before Parliament
%18th February 2005\\
Coming into force
in accordance with regulation 1(2)
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.61603pt}

\begin{document}

\maketitle

\noindent
Whereas a draft of this instrument was laid before Parliament in accordance with section 52(2) of the Child Support Act 1991\footnote{1991 c.\ 48. Section 52(2) was amended by section 30(5) of, and paragraph 15 of Schedule 3 to, the Child Support Act 1995 (c. 34) and is substituted by section 25 of the Child Support, Pensions and Social Security Act 2000 (c. 19) (“the 2000 Act”).} and approved by resolution of each House of Parliament:

Now, therefore, the Secretary of State for Work and Pensions, in exercise of the powers conferred upon him by sections 10(1), 17(3) and (5), 28B(2)($c$), 42(1), 51, 52(4) and 54 of, and paragraphs 4(1)($b$), 5, 6(2), (4) and (6), 7(3), 9($d$)  and 10(1) of Schedule 1, and paragraphs 2 and 4(1) of Schedule 4B to, the Child Support Act 1991\footnote{Section 10(1) was amended by section 1(2)($a$) of the 2000 Act. Section 17(3) and (5) was substituted by section 41 of the Social Security Act 1998 (c.\ 14). Section 28B was inserted by section 2 of the Child Support Act 1995, is substituted by section 5(2) of the 2000 Act and is modified by regulations made under section 28G(2)($b$), as substituted by section 7 of the 2000 Act. Section 51 was amended by section 86(1) of, and paragraph 46 of Schedule 7 to, the Social Security Act 1998 and is amended by section 1(2) of, and paragraph 11(19) of Schedule 3 to, the 2000 Act. Paragraph 4(1)($b$) of Schedule 1 is substituted by section 1(3) of, and Schedule 1 to, the 2000 Act. Paragraph 5 of Schedule 1 was amended by section 41(4) of, and paragraph 20(7) of Schedule 2 to, the Jobseekers Act 1995 (c.\ 18) and is substituted by section 1(3) of, and Schedule 1 to, the 2000 Act. Paragraph 10(1) of Schedule 1 is substituted by section 1(3) of, and Schedule 1 to, the 2000 Act. Schedule 4B was inserted by section 6(2) of, and Schedule 2 to, the Child Support Act 1995 and is substituted by section 6(2) of, and Part II of Schedule 2 to, the 2000 Act. Section 54 is cited for the meaning ascribed to the word “prescribed”. \emph{See} also S.I.\ 2003/192 (C.\ 11).} and section 29 of the Child Support, Pensions and Social Security Act 2000\footnote{2000 c.\ 19.}, and of all other powers enabling him in that behalf, hereby makes the following Regulations:  

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and commencement]{Citation and commencement}

1.---(1)  These Regulations may be cited as the Child Support (Miscellaneous Amendments) Regulations 2005.

(2) These Regulations shall come into force as follows—
\begin{enumerate}\item[]
($a$) subject to sub-paragraphs ($b$)  and ($c$), on the day after the day that they are made;

($b$) regulation 2 shall come into force—
\begin{enumerate}\item[]
(i) except for the purposes of any type of case referred to in head (ii), on the day after the day that they are made; and

(ii) for the purposes of any type of case which is not one in relation to which 3rd March 2003 is the day appointed for the coming into force of section 1(2)($a$)  of the Child Support, Pensions and Social Security Act 2000\footnote{S.I.\ 2003/192 (C.\ 11).}, on the day on which that provision comes into force in relation to that type of case;
\end{enumerate}

($c$) regulation 8(2), (4), (5) and (6), on 6th April 2005.
\end{enumerate}

\subsection[2. Amendment of the Child Support (Maintenance Arrangements and Jurisdiction) Regulations 1992]{\sloppy Amendment of the Child Support (Maintenance Arrangements and Jurisdiction) Regulations 1992}

2.  After regulation 8 of the Child Support (Maintenance Arrangements and Jurisdiction) Regulations 1992\footnote{S.I.\ 1992/2645.} (maintenance assessments and maintenance orders made in error), insert—
\begin{quotation}
\subsection*{“Maintenance calculations and maintenance orders --- payments}

8A.  Where—
\begin{enumerate}\item[]
($a$) a maintenance calculation has been made with respect to a qualifying child in response to an application made under section 4 or 7 of the Act\footnote{Sections 4 and 7 were amended by section 18 of the Child Support Act 1995, respectively by paragraphs 19 and 21 of Schedule 7 to the Social Security Act 1998 and by section 1(2) of, and paragraph 11 of Schedule 3 to, the 2000 Act. Section 4 was amended by section 2(2) and (3) of the 2000 Act.};

($b$) at the time that maintenance calculation was made a maintenance order was in force with respect to that child;

($c$) the maintenance order has ceased to have effect by virtue of the provisions of regulation 3\footnote{Regulation 3 was amended by S.I.\ 1995/1045, S.I.\ 1999/1510 (C.43) and S.I.\ 2001/161.}; and

($d$) the non-resident parent has made payments of maintenance due under that order after the date on which the maintenance calculation took effect in accordance with regulation 26 of the Maintenance Calculation Procedure Regulations\footnote{Regulation 26 was amended by S.I.\ 2002/1204.},
\end{enumerate}
the payments made under the maintenance order shall be treated as payments of child support maintenance.”.
\end{quotation}

\subsection[3. Amendment of the Child Support (Maintenance Assessment Procedure) Regulations 1992]{Amendment of the Child Support (Maintenance Assessment Procedure) Regulations 1992}

3.---(1)  The Child Support (Maintenance Assessment Procedure) Regulations 1992\footnote{S.I.\ 1992/1813. The relevant amending instruments are S.I.\ 1995/3261, S.I.\ 1999/1047, S.I.\ 2000/1596 and S.I.\ 2003/1050.} shall be amended in accordance with the following paragraphs.

(2) In regulation 1(2) (commencement, citation and interpretation), insert in the appropriate place—
\begin{quotation}
““family” has the same meaning as in the Maintenance Assessments and Special Cases Regulations\footnote{The definition of “family” in the Maintenance Assessments and Special Cases Regulations was substituted by S.I.\ 1996/1945.};”; and

““partner” has the same meaning as in the Maintenance Assessments and Special Cases Regulations;”.
\end{quotation}

(3) In regulation 8\footnote{Regulation 8 was substituted by S.I. 1995/3261 and amended by S.I.\ 1999/1047.} (categories of interim maintenance assessment), omit paragraph (4).

(4) In regulation 20(3)\footnote{Regulation 20 was substituted by S.I.\ 1999/1047. Paragraph (3) was amended by S.I.\ 2000/1596.} (supersession of decisions), after “where paragraph (8) applies,” insert “but subject to regulation 23(22)”.

(5) In regulation 23\footnote{Regulation 23 was substituted by S.I.\ 1999/1047 and amended by S.I.\ 2000/1596 and S.I.\ 2003/1050.} (date from which a decision is superseded), after paragraph (20) add—
\begin{quotation}
“(21) Where a superseding decision is made in a case to which regulation 20(2)($a$)  or (3) applies, and the relevant circumstance is that a person has ceased to be a person with care in relation to a qualifying child in respect of whom the maintenance assessment was made, the decision shall take effect from the first day of the maintenance period in which that person ceased to be that person with care in relation to that qualifying child.

(22) Regulation 21 shall not apply where a superseding decision is made under regulation 20(3) in the circumstances set out in paragraph (19) or (21).”.
\end{quotation}

\subsection[4. Amendment of the Child Support (Maintenance Assessments and Special Cases) Regulations 1992]{Amendment of the Child Support (Maintenance Assessments and Special Cases) Regulations 1992}

4.---(1)  The Child Support (Maintenance Assessments and Special Cases) Regulations 1992\footnote{S.I.\ 1992/1815. The relevant amending instruments are S.I.\ 1993/913, S.I.\ 1995/1045, S.I.\ 1996/481, S.I.\ 1996/3196, S.I.\ 1998/58, S.I.\ 1999/997 and S.I.\ 2003/2779.} shall be amended in accordance with the following paragraphs.

(2) In Schedule 1 (calculation of N and M)—
\begin{enumerate}\item[]
($a$) in paragraph 2A(3)($a$)\footnote{Paragraph 2A was inserted by S.I.\ 1999/997.}, for “equivalent to any personal allowance” substitute “calculated as if it were equivalent to any personal allowance which would be”;

($b$) in paragraph 3(5)($a$)\footnote{Paragraph 3(5) was substituted by S.I.\ 1996/3196 and amended by S.I.\ 1998/58.}, for “equivalent to any personal allowance” substitute “calculated as if it were equivalent to any personal allowance which would be”.
\end{enumerate}

(3) In Schedule 2 (amounts to be disregarded when calculating or estimating N and M)—
\begin{enumerate}\item[]
($a$) after paragraph 18, insert—
\begin{quotation}
“18A.  Subject to paragraph 20\footnote{Paragraph 20 was amended by S.I.\ 1996/481.}, and to the extent that it does not exceed £10$.$00, a payment made in respect of a parent under a scheme mentioned in section 1(2) of the Armed Forces (Pensions and Compensation) Act 2004\footnote{2004 c.\ 32.} (compensation schemes for armed and reserve forces).”;
\end{quotation}

($b$) in paragraph 20 for the words “18 and 19(1)” wherever they appear, substitute “18 to 19(1)”;

($c$) in paragraph 25\footnote{Paragraph 25 was amended by S.I.\ 1993/913, S.I.\ 1998/58 and S.I.\ 1999/997.} after the words “(permitted allowances)”, insert “or paragraph 3 of Schedule 4 to the Adoption and Children Act 2002\footnote{2002 c.\ 38.}”;

($d$) after paragraph 25, insert—
\begin{quotation}
“25A.  Any payment made to a person in accordance with regulations made pursuant to section 14F of the Children Act 1989\footnote{1989 c.\ 41. Section 14F was inserted by section 115 of the Adoption and Children Act 2002 (c.\ 38).} (special guardianship support services) in respect of a child who is a member of his family.”.
\end{quotation}
\end{enumerate}

(4) In paragraph ($b$)  of Schedule 4 (cases where child support maintenance is not to be payable)—
\begin{enumerate}\item[]
($a$) at the end of sub-paragraph (ix), omit “and”;

($b$) after sub-paragraph (ix), add—
\begin{quotation}
“(x) the Armed Forces (Pensions and Compensation) Act 2004; and”.
\end{quotation}
\end{enumerate}

\subsection[5. Amendment of the Child Support (Maintenance Calculation Procedure) Regulations 2000]{Amendment of the Child Support (Maintenance Calculation Procedure) Regulations 2000}

5.---(1)  Regulation 10 of the Child Support (Maintenance Calculation Procedure) Regulations 2000\footnote{S.I.\ 2001/157. The relevant amending instrument is S.I.\ 2003/328.} (circumstances in which a reduced benefit decision shall not be given) shall be renumbered as paragraph (1) of that regulation.

(2) After that paragraph add—
\begin{quotation}
“(2) In paragraph (1)($c$), “family” has the same meaning as in the Maintenance Calculations and Special Cases Regulations.”.
\end{quotation}

\subsection[6. Amendment of the Child Support (Maintenance Calculations and Special Cases) Regulations 2000]{Amendment of the Child Support (Maintenance Calculations and Special Cases) Regulations 2000}

6.---(1)  The Child Support (Maintenance Calculations and Special Cases) Regulations 2000\footnote{S.I.\ 2001/155. The relevant amending instruments are S.I.\ 2002/2497, S.I.\ 2002/3019, S.I.\ 2003/1195, S.I.\ 2003/2779 and S.I.\ 2004/2415.} shall be amended in accordance with the following paragraphs.

(2) In regulation 4(1) (flat rate)—
\begin{enumerate}\item[]
($a$) after sub-paragraphs ($d$)  and ($e$), omit “and”;

($b$) after sub-paragraph ($f$), add—
\begin{quotation}
“; and

($g$) a payment under a scheme mentioned in section 1(2) of the Armed Forces (Pensions and Compensation) Act 2004\footnote{2004 c.\ 32.} (compensation schemes for armed and reserve forces).”.
\end{quotation}
\end{enumerate}

(3) In regulation 5 (nil rate)—
\begin{enumerate}\item[]
($a$) after paragraph ($gg$), insert “or”;

($b$) after paragraph ($h$), omit “; or”.
\end{enumerate}

(4) In regulation 11 (non-resident parent liable to pay maintenance under a maintenance order), in paragraph (1), for the words after “pay maintenance” substitute—
\begin{quotation}
    “for that child—
\begin{enumerate}\item[]
    (i) 
    under a maintenance order;

    (ii) 
    in accordance with the terms of an order made by a court outside Great Britain; or

    (iii)
    under the legislation of a jurisdiction outside the United Kingdom,
\end{enumerate}
    that case shall be treated as a special case for the purpose of the Act.”; 
\end{quotation}

(5) In paragraph 7(4)($a$)  of the Schedule (net weekly income) for “equivalent to any personal allowance” substitute “calculated as if it were equivalent to any personal allowance which would be”.

\subsection[7. Amendment of the Child Support (Transitional Provisions) Regulations 2000]{Amendment of the Child Support (Transitional Provisions) Regulations 2000}

7.---(1)  The Child Support (Transitional Provisions) Regulations 2000\footnote{S.I.\ 2000/3186. The relevant amending instruments are S.I.\ 2002/1204, S.I.\ 2003/328, S.I.\ 2003/2779 and S.I.\ 2004/2415.} shall be amended in accordance with the following paragraphs.

(2) In regulation 3(2)($b$)(ii)\footnote{Paragraph (2) was substituted by S.I.\ 2004/2415.} (decision and notice of decision), for “paragraph” substitute “sub-paragraph”.

(3) In regulation 27 (subsequent decision with effect in transitional period---amount payable)—
\begin{enumerate}\item[]
($a$) after paragraph (7)\footnote{Paragraph (7) was added by S.I.\ 2003/328.}, insert—
\begin{quotation}
“(7A) This paragraph applies where—
\begin{enumerate}\item[]
($a$) paragraph (1) applies and at the date of the subsequent decision there is more than one person with care in relation to the same non-resident parent; and

($b$) as a result of the subsequent decision there is one person with care in relation to that non-resident parent.
\end{enumerate}

(7B) Where paragraph (7A) applies, the amount payable to a person with care in respect of whom the amount payable is calculated by reference to a phasing amount shall be determined by applying paragraphs (1) to (5) as if references to—
\begin{enumerate}\item[]
($a$) the new amount and the transitional amount were to the apportioned part of the amount in question which had been payable immediately prior to the subsequent decision to the person with care in respect of whom the subsequent decision is made; and

($b$) the subsequent decision amount were to the full amount payable under the subsequent decision.”;
\end{enumerate}
\end{quotation}

($b$) in paragraph (8), after “paragraph (7)” insert “and (7B)”.
\end{enumerate}

\subsection[8. Amendment of the Child Support (Variations) Regulations 2000]{Amendment of the Child Support (Variations) Regulations 2000}

8.---(1)  The Child Support (Variations) Regulations 2000\footnote{S.I.\ 2001/156. The relevant amending instrument is S.I.\ 2002/1204.} shall be amended in accordance with the following paragraphs.

(2) In regulation 6(2)($b$)(iii) (rejection of an application following preliminary consideration), after “regulation 19(1)” insert “or (1A)”.

(3) For regulation 11(3) (special expenses—illness or disability of relevant other child), substitute—
\begin{quotation}
“(3) Where, at the date on which the non-resident parent makes the variation application—
\begin{enumerate}\item[]
($a$) he or a member of his household has received, or at that date is in receipt of, or where he or the member of his household will receive any financial assistance from any source in respect of the long-term illness or disability of the relevant other child; or

($b$) a disability living allowance is received by the non-resident parent or the member of his household on behalf of the relevant other child,
\end{enumerate}
only the net amount of the costs incurred in respect of the items listed in paragraph (1), after the deduction of the financial assistance or the amount of the allowance, shall constitute special expenses for the purposes of paragraph 2(2) of Schedule 4B to the Act.”.
\end{quotation}

(4) For regulation 18(3)($a$)  (assets), substitute—
\begin{quotation}
“($a$) where the total value of the assets referred to in that paragraph does not exceed £65,000 after deduction of—
\begin{enumerate}\item[]
(i) the amount owing under any mortgage or charge on those assets;

(ii) the value of any asset in respect of which income has been taken into account under regulation 19(1A);”.
\end{enumerate}
\end{quotation}

(5) In regulation 19 (income not taken into account and diversion of income)—
\begin{enumerate}\item[]
($a$) after paragraph (1), insert—
\begin{quotation}
“(1A) Subject to paragraph (2), a case shall constitute a case for the purposes of paragraph 4(1) of Schedule 4B to the Act where—
\begin{enumerate}\item[]
($a$) the non-resident parent has the ability to control the amount of income he receives from a company or business, including earnings from employment or self-employment; and

($b$) the Secretary of State is satisfied that the non-resident parent is receiving income from that company or business which would not otherwise fall to be taken into account under the Maintenance Calculations and Special Cases Regulations.”;
\end{enumerate}
\end{quotation}

($b$) for paragraph (2), substitute—
\begin{quotation}
“(2) Paragraphs (1) and (1A) shall apply where—
\begin{enumerate}\item[]
($a$) the income referred to in paragraph (1)($b$)  is net weekly income of over £100; or

($b$) the income referred to in paragraph (1A)($b$)  is over £100; or

($c$) the aggregate of the net weekly income referred to in sub-paragraph ($a$)  and the income referred to in sub-paragraph ($b$)  is over £100,
\end{enumerate}
as the case may be.”;
\end{quotation}

($c$) in paragraph (4)($b$)—
\begin{enumerate}\item[]
(i) after “Regulations” insert “or paragraph (1A)”;

(ii) omit “in order to reduce his liability to pay child support maintenance”;
\end{enumerate}

($d$) in paragraph (5), after sub-paragraph ($b$)  add—
\begin{quotation}
“; and

($c$) in a case to which paragraph (1A) applies, the additional income taken into account under regulation 25 shall be the whole of the income referred to in paragraph (1A)($b$).”.\end{quotation}
\end{enumerate}

(6) In regulation 20(3) (lifestyle inconsistent with declared income), after sub-paragraph ($a$)  insert—
\begin{quotation}
“($aa$) income which falls to be considered under regulation 19(1A) (income not taken into account);”. 
\end{quotation}

\bigskip

Signed 
by authority of the 
Secretary of State for Work and Pensions.

{\raggedleft
\emph{Patricia Hollis}\\*Parliamentary Under-Secretary of State,\\*Department for Work and Pensions

}

15th March 2005

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations provide for the amendment of regulations relating to child support.\looseness=-1

The powers exercised to make these Regulations are those contained in the Child Support Act 1991 (“the 1991 Act”). Some of those powers are conferred by provisions of the 1991 Act prior to the amendments made to that Act by the Child Support, Pensions and Social Security Act 2000 (“the 2000 Act”), which amendments are not fully in force, and relate to the child support scheme which was in force prior to 3rd March 2003 and which remains in force for the purposes of certain cases (“the old scheme”). Other powers are conferred by provisions of the 1991 Act as amended by the 2000 Act, which relate to the child support scheme provided for by those amendments and which came into force for the purposes of specified categories of cases on 3rd March 2003 (see the Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 12) Order 2003) (“the new scheme”).

Regulation 2 amends the Child Support (Maintenance Arrangements and Jurisdiction) Regulations 1992, which are old and new scheme regulations, to insert a new regulation 8A (which only applies to the new scheme), which provides for payments due and made under a maintenance order to be treated as child support maintenance where those payments have been made under that order after the date on which a maintenance calculation took effect and the maintenance order has ceased to have effect under regulation 3 of those Regulations.

Regulation 3 amends the Child Support (Maintenance Assessment Procedure) Regulations 1992, which are old scheme regulations. Paragraph (2) inserts definitions of “family” and “partner” into regulation 1(2) of those Regulations. Paragraph (3) makes a consequential amendment to regulation 8(3) of those Regulations. Paragraph (4) makes a consequential amendment to regulation 20(3) of those Regulations. Paragraph (5) inserts new paragraphs (21) and (22) into regulation 23 of those Regulations. That paragraph (21) makes provision for the effective date of a decision where a person with care has ceased to be the person with care in relation to a qualifying child in respect of whom the maintenance assessment was made, being the date that person so ceased to be the person with care in relation to that child and that paragraph (22) disapplies the provisions of regulation 21 of those Regulations where a superseding decision is made and the circumstances set out in regulation 23(19) and (21) of those Regulations apply.%\looseness=1

Regulation 4 amends the Child Support (Maintenance Assessments and Special Cases) Regulations 1992, which are old scheme regulations. Paragraph (2) makes clarifying amendments. Paragraph (3)($a$)  inserts a new paragraph 18A of Schedule 2 to those Regulations providing for a new disregarded amount where a payment is made in respect of a parent under a scheme mentioned in section 1(2) of the Armed Forces (Pensions and Compensation) Act 2004. Paragraph (3)($b$)  makes a consequential amendment. Paragraph (3)($c$)  extends the disregard in paragraph 25 of Schedule 2 to those Regulations to apply to payments made under paragraph 3 of Schedule 4 to the Adoption and Children Act 2002 and sub-paragraph ($d$)  inserts a new paragraph 25A for the disregard of payments made under section 14F of the Children Act 1989 where a special guardianship order has been made. Paragraph (4) adds the Armed Forces (Pensions and Compensation) Act 2004 to the list of enactments under which awards made in respect of disablement are cases where child support maintenance is not to be payable.%\looseness=1

Regulation 5 amends the Child Support (Maintenance Calculation Procedure) Regulations 2000, which are new scheme regulations, to make a clarifying amendment.

Regulation 6 amends the Child Support (Maintenance Calculations and Special Cases) Regulations 2000, which are new scheme regulations. Other than paragraph (4) all the amendments made by this regulation either mirror those made to the Child Support (Maintenance Assessments and Special Cases) Regulations 1992 or make clarifying or consequential amendments. Paragraph (4) amends regulation 11(1) of those Regulations extending that special case where the circumstances are that an application for child support maintenance has been made (or treated as made) and the non-resident parent in respect of whom the application was made is liable for payments of maintenance for a different child under the terms of an order of a court outside Great Britain, or under the legislation of a jurisdiction outside the United Kingdom.%\looseness=1

Regulation 7 amends the Child Support (Transitional Provisions) Regulations 2000 which make provision for the conversion of cases from the old to the new scheme. Paragraph (2) makes a clarifying amendment and paragraph (3) amends regulation 27 of those Regulations making provision for the amount payable where there is a “subsequent decision” made during the transitional period and the consequence of that decision is that there is only one person with care in relation to the non-resident parent where previously there had been more than one.

Regulation 8 amends the Child Support (Variations) Regulations 2000 (“the Variations Regulations”), which are new scheme regulations. Paragraph (3) substitutes regulation 11(3) of those Regulations to make provision to take into account financial assistance paid in respect of the long-term illness or disability of a relevant other child or disability living allowance paid on behalf of that child, to a member of the non-resident parent’s household where there is an application for a variation for special expenses for that relevant other child. Paragraph (5) extends the ground in regulation 19 of those Regulations for a variation for income not taken into account to a case where the non-resident parent has the ability to control the amount of income he receives from a company or business and the Secretary of State is satisfied he is receiving income which would not otherwise fall to be taken into account under the Child Support (Maintenance Calculations and Special Cases) Regulations 2000. Paragraph (5)($b$)  makes provision for a threshold for a variation in relation to each specified case under regulation 19(1) and (1A) of those Variations Regulations, or an aggregated amount where both cases apply. Paragraph (5)($c$)  makes a consequential amendment to, and omits words from, regulation 19(4) of those Regulations. Paragraph (5)($d$)  sets out the amount of income to be taken into account where a variation is made under regulation 19(1A) of those Regulations. Paragraphs (2), (4) and (6) make consequential amendments.

A full regulatory impact assessment has not been produced for this instrument as it has no impact on the cost of business. 

\end{document}