\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 8) Order 2001}

\newcommand\regsnumber{2001/1252}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2001 No.\ 1252 (C.\ 45)}

\date{Made
28th March 2001\\
%Laid before Parliament
%3rd April 2001\\
%Coming into force
%24th April 2001
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.57402pt}

\begin{document}

\maketitle

\noindent
The Secretary of State for Social Security, in exercise of the powers conferred on him by section 86(2) and (3)($a$)  of the Child Support, Pensions and Social Security Act 2000\footnote{2000 c.\ 19.} and of all other powers enabling him in that behalf, hereby makes the following Order:— 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and interpretation]{Citation and interpretation}

1.---(1)  This Order may be cited as the Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 8) Order 2001.

(2) In this Order, unless the context otherwise requires, any reference to a numbered section or Schedule is a reference to the section or, as the case may be, the Schedule bearing that number in the Child Support, Pensions and Social Security Act 2000.

\subsection[2. Appointed days]{Appointed days}

2.---(1)  2nd April 2001 is the day appointed for the coming into force of—
\begin{enumerate}\item[]
($a$) section 67 and Schedule 6 (social security investigation powers), so far as not already in force;

($b$) sub-paragraphs (1) and (3) of paragraph 13 of Schedule 3 (by virtue of which section 24 of the Child Support Act 1995\footnote{1995 c.\ 34.}, which is now spent, ceases to have effect), and section 26 so far as it relates to those sub-paragraphs;

($c$) paragraph 11 of Schedule 5 (conditions of payment of surplus out of funds of an occupational pension scheme to employer), and section 56 so far as it relates to that paragraph;

($d$) Part I of Schedule 9 (repeals and revocations—child support provisions) so far as it relates to—
\begin{enumerate}\item[]
(i) the repeals in section 15(10) of the Child Support Act 1991\footnote{1991 c.\ 48.},

(ii) the repeal of section 40(1) and (2) of that Act, of section 24 of the Child Support Act 1995 and of paragraph 28 of Schedule 7 to the Social Security Act 1998\footnote{1998 c.\ 14.}, and

(iii) the revocation in the Social Security Act 1998 (Commencement No.\ 2) Order 1998\footnote{S.I.\ 1998/2780 (C.66).}; and
\end{enumerate}

($e$) Part VI of Schedule 9 (repeals—investigation powers).
\end{enumerate}

(2) 2nd July 2001 is the day appointed for the coming into force of the following provisions so far as not already in force:—
\begin{enumerate}\item[]
($a$) in Schedule 7 (housing benefit and council tax benefit: revisions and appeals)—
\begin{enumerate}\item[]
(i) paragraphs 1 to 16,

(ii) paragraph 18, except for sub-paragraph (2)($b$),

(iii) paragraphs 19 to 21,

(iv) except for the purposes specified in paragraph (3) below, paragraph 22(1), and

(v) paragraphs 22(2) and (3) and 23,
\end{enumerate}
and section 68 so far as it relates thereto;

($b$) section 69 (discretionary financial assistance with housing); and

($c$) except for the purposes specified in paragraph (3) below, Part VII of Schedule 9 (repeals—housing benefit and council tax benefit).
\end{enumerate}

(3) The purposes referred to in paragraph (2)($a$)(iv) and ($c$)  above are where, pursuant to a request for a further review of a determination under section 34 of the Social Security Act 1998 relating to housing benefit or council tax benefit—
\begin{enumerate}\item[]
($a$) an oral hearing by a Review Board constituted under the Housing Benefit (General) Regulations 1987\footnote{S.I.\ 1987/1971; relevant amendments were made by S.I. 1993/317, 1994/2137 and 2000/897.} or, as the case may be, the Council Tax Benefit (General) Regulations 1992\footnote{S.I.\ 1992/1814; relevant amendments were made by S.I. 1993/688, 1994/2137 and 2000/897.} has been held and completed before 2nd July 2001, the purpose of enabling the Review Board on or after that date to record its decision, or to give or send its decision to persons likely to be affected by it; or

($b$) a decision on the further review has been given by such a Review Board, whether before, on or after that date—
\begin{enumerate}\item[]
(i) the purpose of enabling the Review Board to correct any accidental error in the record of its decision,

(ii) where proceedings are brought by way of judicial review in connection with that decision, the purpose of enabling the Review Board to participate in those proceedings or in any appeal arising out of those proceedings, or

(iii) the purpose of giving effect to the Review Board’s decision.
\end{enumerate}
\end{enumerate}

\subsection[3. Amendment of earlier Order]{Amendment of earlier Order}

3.  In article 2(5) of the Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 4) Order 2000\footnote{S.I.\ 2000/3166 (C.101).} sub-paragraph ($b$)  (which brings Part II of Schedule 5 into force on 1st June 2001 for all purposes other than that of authorising the making of regulations and orders) shall be omitted. 

\bigskip

Signed 
by authority of the Secretary of State for Social Security.

{\raggedleft
\emph{Jeff Rooker}\\*Minister of State,\\*Department of Social Security

}

%Dated
28th March 2001

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Order)}

This Order brings into force further provisions of the Child Support, Pensions and Social Security Act 2000 as follows.

Section 67 and Schedule 6 (which amend the provisions governing powers of investigation for social security purposes) are brought fully into force, along with associated repeals in Part VI of Schedule 9, on 2nd April 2001 (article 2(1)($a$)  and ($e$)). Paragraph 11 of Schedule 5 (concerning the payment to an employer of any surplus out of the funds of an occupational pension scheme) is also brought into force on 2nd April 2001 (article 2(1)($c$)), as are a number of miscellaneous repeals and revocations of child support provisions (article 2(1)($b$)  and ($d$)).

Section 68 and Schedule 7 except so far as relating to paragraphs 17 and 18(2)($b$)  of that Schedule, (which make provision for revisions and appeals in connection with housing benefit and council tax benefit), and section 69 (which provides for discretionary assistance with housing) are brought into force on 2nd July 2001, as are the associated repeals in Part VII of Schedule 9, except for certain purposes relating to further reviews of determinations (article 2(2) and (3)).

An amendment is made in an earlier commencement order to revoke the day previously appointed for the coming fully into force of Part II of Schedule 5 (which provides for an alternative to the anti-franking rules relating to salary related contracted-out pension schemes) (article 3).

The impact on business of provisions in the Child Support, Pensions and Social Security Act 2000 is detailed in the Regulatory Impact Assessment relating to the Child Support, Pensions and Social Security Bill (which was introduced in the House of Commons on 1st December 1999). A copy of that Assessment has been placed in the libraries of both Houses of Parliament and can be obtained from the Department of Social Security, Regulatory Impact Unit, 3rd Floor, The Adelphi, 1–11 John Adam Street, London \textsc{\lowercase{WC2N 6HT}}. 

\end{document}