\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Pensions Act 2007 (Supplementary Provision) Order 2009}

\newcommand\regsnumber{2009/2715}

\title{\regstitle}

\author{S.I.\ 2009 No.\ 2715}

\date{Made
7th October 2009\\
Laid before Parliament
12th October 2009\\
Coming into force
6th April 2010
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

%\setlength\headheight{27.61603pt}

%\hbadness=10000

\begin{document}

\maketitle

\enlargethispage{\baselineskip}

\noindent
The Secretary of State makes the following Order in exercise of the powers conferred on him by section 27(1)($a$)  of the Pensions Act 2007\footnote{2007 c.~22.}. 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and commencement]{Citation and commencement}

1.  This Order may be cited as the Pensions Act 2007 (Supplementary Provision) Order 2009 and shall come into force on 6th April 2010.

\subsection[2. Amendment of the Social Security and Child Support (Decisions and Appeals) Regulations 1999]{Amendment of the Social Security and Child Support (Decisions and Appeals) Regulations 1999}

2.  In regulation 26 (decisions against which an appeal lies) of the Social Security and Child Support (Decisions and Appeals) Regulations 1999\footnote{S.I.~1991/991. Relevant amending instruments are S.I.~1999/2570, S.I.~2000/1596, S.I.~2001/518 and S.I.~2008/2683.}, at the end of paragraph ($d$)  add—
\begin{quotation}
“; or

($e$) under, or by virtue of regulations made under, section~23A (contributions credits for relevant parents and carers) of the Contributions and Benefits Act.”\footnote{1992 c.~4. Section 23A was inserted into the Social Security Contributions and Benefits Act 1992 (c.~4) by section 3 of the Pensions Act 2007 (c.~22).}.
\end{quotation}

\bigskip

\pagebreak[3]

Signed 
by authority of the 
Secretary of State for~Work and~Pensions.
%I concur
%By authority of the Lord Chancellor

{\raggedleft
\emph{Angela Eagle}\\*
%Secretary
Minister
%Parliamentary Under-Secretary 
of State\\*Department 
for~Work and~Pensions

}

7th October 2009

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Order)}

This Order makes provision supplementary to section 3 (contributions credits for relevant parents and carers) of the Pensions Act 2007 (c.~22), which inserts section 23A (contributions credits for relevant parents and carers) of the Social Security Contributions and Benefits Act 1992 (c.~4) (“the 1992 Act”).

This Order amends the Social Security and Child Support (Decisions and Appeals) Regulations 1999 (S.I.~1999/991) to provide that an appeal lies to the First-tier Tribunal established under Chapter II (First-tier Tribunal and Upper Tribunal) of Part I (tribunals and inquiries) of the Tribunals, Courts and Enforcement Act 2007 (c.~15) against decisions of the Secretary of State under, or by virtue of regulations made under, section 23A of the 1992 Act.

A full impact assessment has not been produced for this instrument as it has no impact on the private or voluntary sectors. 

\end{document}