\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Maintenance and Other Payments Act 2008 (Commencement No.~9) and the Welfare Reform Act 2009 (Commencement No.~9) Order 2012}

\newcommand\regsnumber{2012/2523}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and~Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2012 No.\ 2523 (C.~101)}

\date{Made
%17th September 2012\\
%Laid before the House of Commons
%17th September 2012\\
%Coming into force
4th October 2012
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{42.11603pt}

%\hbadness=10000

\begin{document}

\maketitle

\noindent
The Secretary of State for Work and Pensions, in exercise of the powers conferred by section 62(3) of the Child Maintenance and Other Payments Act 2008\footnote{2008 c.~6.} and section 61(3) of the Welfare Reform Act 2009\footnote{2009 c.~24.}, makes the following Order: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and interpretation]{Citation and interpretation}

1.---(1)  This Order may be cited as the Child Maintenance and Other Payments Act 2008 (Commencement No.~9) and the Welfare Reform Act 2009 (Commencement No.~9) Order 2012.

(2) In this Order, except where otherwise stated, any reference to a numbered section or Schedule is a reference to a section of, or Schedule to, the Child Maintenance and Other Payments Act 2008.

\subsection[2. Commencement date]{Commencement date}

2.---(1)  The following provisions come into force on 8th October 2012—
\begin{enumerate}\item[]
($a$) section 37 (additional special case);

($b$) section 41 (pilot schemes);

($c$) section 57(1) and paragraph 1(1) of Schedule 7, so far as relating to the paragraph referred to in sub-paragraph ($d$);

($d$) paragraph 1(24), (30) and (31) of Schedule 7 (minor and consequential amendments); and

($e$) sections 54 (payments of child support maintenance) and 55(1) and~(2) (offences relating to information) of the Welfare Reform Act 2009, in so far as they are not already in force.
\end{enumerate}

(2) The following provisions come into force, for the purpose only of making regulations, on 8th October 2012—
\begin{enumerate}\item[]
($a$) section 16 (changes to the calculation of maintenance) and paragraph~1 of Schedule 4 (introductory), so far as relating to the paragraphs referred to in sub-paragraph ($b$);

($b$) paragraphs 2, 5(2) and 7 to 9 of Schedule 4 (changes to the calculation of maintenance);

($c$) section 17 (power to regulate supersession);

($d$) sections 32 (power to accept part payment of arrears in full and final satisfaction) and 33 (power to write off arrears);

($e$) section 42 (meaning of child);

($f$) section 58, so far as relating to the entry referred to in sub-paragraph~($g$); and

($g$) the entry in Schedule 8 (repeals) relating to Schedule 1 to the Child Support Act 1991\footnote{1991 c.~48.}.
\end{enumerate}

\bigskip

\pagebreak[3]

Signed 
by authority of the 
Secretary of State for~Work and~Pensions.
%I concur
%By authority of the Lord Chancellor

{\raggedleft
\emph{Steve Webb}\\*
%Secretary
Minister
%Parliamentary Under-Secretary 
of State\\*Department 
for~Work and~Pensions

}

4th October 2012

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

This Order brings into force provisions of the Child Maintenance and Other Payments Act 2008 (c.~6) and the Welfare Reform Act 2009 (c.~24).

Article 2(1) brings into force the provisions listed, in so far as they are not already in force, on 8th October 2012. Article 2(2) brings into force the provisions listed on 8th October 2012 for the purpose only of making regulations. 

\end{document}