\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support (Miscellaneous Amendments) Regulations 2004}

\newcommand\regsnumber{2004/2415}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2004 No.\ 2415}

\date{Made
15th September 2004\\
%Laid before Parliament
%15th December 2003\\
Coming into force
in accordance with regulation 1(2)
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.57402pt}

\begin{document}

\maketitle

\noindent
Whereas a draft of this instrument was laid before Parliament in accordance with section 52(2) of the Child Support Act 1991\footnote{1991 c.\ 48. Section 52(2) was amended by section 30(5) of, and paragraph 15 of Schedule 3 to, the Child Support Act 1995 (c.\ 34) and is substituted by section 25 of the Child Support, Pensions and Social Security Act 2000 (c.\ 19) (“the 2000 Act”).} and approved by resolution of each House of Parliament:

Now, therefore, the Secretary of State for Work and Pensions, in exercise of the powers conferred upon him by sections 14(3), 16(1)($a$), 17(3), 28B(2)($c$), 51, 52(4) and 54 of, and paragraphs 5, 6(2), (4) and (6), 9($d$), 10(1) and 11 of Schedule 1, paragraphs 1 and 2($a$)  of Schedule 4A and paragraphs 5(1) and 6 of Schedule 4B to the Child Support Act 1991\footnote{Section 14(3) was amended by section 86(1) of, and paragraph 27($b$)  of Schedule 7 to, the Social Security Act 1998 (c.\ 14). Section 16(1) was substituted by section 40 of the Social Security Act 1998 and is amended by section 8(2) of the 2000 Act. Section 17(3) was substituted by section 41 of the Social Security Act 1998. Section 28B was inserted by section 2 of the Child Support Act 1995 and is substituted by section 5(2) of the 2000 Act. Section 51 was amended by section 86(1) of, and paragraph 46 of Schedule 7 to, the Social Security Act 1998 and is amended by section 1(2) of, and paragraph 11(19) of Schedule 3 to, the 2000 Act. Paragraph 5 of Schedule 1 was amended by section 41(4) of, and paragraph 20(7) of Schedule 2 to, the Jobseekers Act 1995 (c.\ 18) and is substituted by section 1(3) of, and Schedule 1 to, the 2000 Act. Paragraph 10(1) of Schedule 1 is substituted by section 1(3) of, and Schedule 1 to, the 2000 Act. Paragraph 11 of Schedule 1 was amended by section 1(2) of the 2000 Act. Schedule 4A was inserted by section 1(2) of, and Schedule 1 to, the Child Support Act 1995 (c.\ 34), amended by section 86(1) of, and paragraph 53 of Schedule 7 to, the Social Security Act 1998 and is substituted by section 6(1) of, and Part I of Schedule 2 to, the 2000 Act. Schedule 4B was inserted by section 6(2) of, and Schedule 2 to, the Child Support Act 1995 and is substituted by section 6(2) of, and Part II of Schedule 2 to, the 2000 Act. Section 54 is cited for the meaning ascribed to the word “prescribed”. \emph{See} also S.I.\ 2003/192 (C.\ 11).} and section 29 of the Child Support, Pensions and Social Security Act 2000\footnote{2000 c.\ 19.}, and of all other powers enabling him in that behalf, hereby makes the following Regulations: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and commencement]{Citation and commencement}

1.---(1)  These Regulations may be cited as the Child Support (Miscellaneous Amendments) Regulations 2004.

(2) These Regulations shall come into force as follows—
\begin{enumerate}\item[]
($a$) subject to sub-paragraph ($b$), these Regulations shall come into force on the day after the day that they are made;

($b$) regulations 2 and 3 shall come into force—
\begin{enumerate}\item[]
(i) except for the purposes of any type of case referred to in head (ii), on the day after the day that they are made; and

(ii) for the purposes of any type of case which is not one in relation to which 3rd March 2003 is the day appointed for the coming into force of sections 1(2), 8 and 9 of, and paragraph 11(2) and (7) of Schedule 3 to, the Child Support, Pensions and Social Security Act 2000\footnote{S.I.\ 2003/192 (C.\ 11), the relevant amending instrument is S.I.\ 2003/346 (C.\ 21).}, on the day on which those provisions come into force in relation to that type of case.
\end{enumerate}
\end{enumerate}

\subsection[2. Amendment of the Social Security and Child Support (Decisions and Appeals) Regulations 1999]{Amendment of the Social Security and Child Support (Decisions and Appeals) Regulations 1999}

2.---(1)  The Social Security and Child Support (Decisions and Appeals) Regulations 1999\footnote{S.I.\ 1999/991.} shall be amended in accordance with the following paragraph.

(2) In regulation 6B (circumstances in which a child support decision may not be superseded)\footnote{Regulation 6B was inserted by regulation 8 of S.I.\ 2000/3185.}—
\begin{enumerate}\item[]
($a$) for paragraph (3) substitute—
\begin{quotation}
“(3) Where the application for a supersession is made on more than one ground, if those grounds which do not relate to the net income of the non-resident parent lead to a superseding decision this regulation shall not apply to the ground relating to the net income of that parent.”;
\end{quotation}

($b$) after paragraph (4) add—
\begin{quotation}
“(5) Where an application has been made to which paragraph (1) applied (“application A”) and a further application (“application B”) is made for a supersession on a ground other than one relating to the net income of the non-resident parent, the Secretary of State may make a superseding decision on the basis that application A was made at the same time as application B.”.
\end{quotation}
\end{enumerate}

\subsection[3. Amendment of the Child Support (Information, Evidence and Disclosure) Regulations 1992]{Amendment of the Child Support (Information, Evidence and Disclosure) Regulations 1992}

3.  In regulation 8 of the Child Support (Information, Evidence and Disclosure) Regulations 1992\footnote{S.I.\ 1992/1812, relevant amending instruments are S.I.\ 1996/2907, S.I.\ 1998/58 and S.I.\ 1999/1510.} (disclosure of information to a court or tribunal) in paragraph (1), after sub-paragraph ($b$)  insert—
\begin{quotation}
“($cc$) a person with a right of appeal under the Act to an appeal tribunal,”.
\end{quotation}

\enlargethispage{-\baselineskip}

\subsection[4. Amendment of the Child Support (Maintenance Assessment Procedure) Regulations 1992]{Amendment of the Child Support (Maintenance Assessment Procedure) Regulations 1992}

4.  In regulation 17(1) of the Child Support (Maintenance Assessment Procedure) Regulations 1992\footnote{S.I.\ 1992/1813, which is revoked, with savings, by S.I.\ 2001/157. The relevant amending instrument is S.I.\ 1999/1047.} (revision of decisions)—
\begin{enumerate}\item[]
($a$) after sub-paragraph ($d$)  omit “or”;

($b$) after sub-paragraph ($e$)  add—
\begin{quotation}
    “or

    ($f$) 
    if an appeal is made under section 20 of the Act against a decision within the time prescribed in regulation 31 of the Social Security and Child Support (Decisions and Appeals) Regulations 1999\footnote{S.I.\ 1999/991, relevant amending instruments are S.I.\ 1999/2570, S.I.\ 2002/1204 and S.I.\ 2002/1379.}, or in a case to which regulation 32 of those Regulations applies within the time prescribed in that regulation, but the appeal has not been determined.”. 
\end{quotation}
\end{enumerate}

\subsection[5. Amendment of the Child Support (Maintenance Assessments and Special Cases) Regulations 1992]{Amendment of the Child Support (Maintenance Assessments and Special Cases) Regulations 1992}

5.---(1)  The Child Support (Maintenance Assessments and Special Cases) Regulations 1992\footnote{S.I.\ 1992/1815, which is revoked, with savings, by S.I.\ 2001/155. The relevant amending instruments are S.I.\ 1995/1045, S.I.\ 1996/1945, S.I.\ 1996/3196, S.I.\ 1999/977 and S.I.\ 1999/1510 (C.\ 43).} shall be amended in accordance with the following paragraphs.

(2) In Schedule 1 (calculation of N and M), in paragraph 1(1), after head ($g$)  insert—
\begin{quotation}
“($gg$) any statutory paternity pay under Part XIIZA of the Contributions and Benefits Act or any statutory adoption pay under Part XIIZB of that Act\footnote{Part XIIZA was inserted by section 2 of the Employment Act 2002 (c.\ 22) and Part XIIZB was inserted by section 4 of that Act.};”;
\end{quotation}

(3) After paragraph 36 of Schedule 2 (amounts to be disregarded when calculating or estimating N and M) insert—
\begin{quotation}
“36A.  Any sum in respect of financial assistance given, or given under arrangements made, by the Secretary of State (in relation to England) or the National Assembly for Wales (in relation to Wales) under section 14 of the Education Act 2002\footnote{2002 c.\ 32.} (power of Secretary of State and National Assembly for Wales to give financial assistance for purposes related to education), to a child.”.
\end{quotation}

(4) In Schedule 3B (amount to be allowed in respect of travelling costs)\footnote{Schedule 3B was inserted by regulation 57 of, and Schedule 2 to, S.I.\ 1995/1045.}—
\begin{enumerate}\item[]
($a$) in paragraph 1 for the definition of “straight-line distance” substitute—
\begin{quotation}
““straight-line distance” means the straight-line distance measured in kilometres and calculated to 2 decimal places, and, where that distance is not a whole number of kilometres, rounded to the nearest whole number of kilometres, a distance which exceeds a whole number of kilometres by 0$.$50 of a kilometre being rounded up;”;
\end{quotation}

($b$) in paragraphs 7, 14 and 20—
\begin{enumerate}\item[]
(i) for “150”, wherever it appears, substitute “240”; and

(ii) for “10 pence”, wherever it appears, substitute “6 pence”;
\end{enumerate}

($c$) in paragraph 8(1) and (2) for “13”, wherever it appears, substitute “14”.
\end{enumerate}

\subsection[6. Amendment of the Child Support (Maintenance Calculation Procedure) Regulations 2000]{Amendment of the Child Support (Maintenance Calculation Procedure) Regulations 2000}

6.---(1)  The Child Support (Maintenance Calculation Procedure) Regulations 2000\footnote{S.I.\ 2001/157, relevant amending instruments are S.I.\ 2002/1204 and S.I.\ 2003/328.} shall be amended in accordance with the following paragraphs.

(2) In regulation 29(1) (effective dates of maintenance calculations in specified cases), after sub-paragraph ($c$)  add—
\begin{quotation}
“($d$) except where the parent with care has made a request under section 6(5) of the Act, where on the date the application is made, or treated as made under regulation 3, there is in force a maintenance calculation in relation to the same non-resident parent and a different person with care, and the maintenance calculation in force when the application was made has ceased to have effect before a decision has been made in respect of that application, the effective date of the maintenance calculation made in response to the application shall be—
\begin{enumerate}\item[]
(i) where the date of notification to the non-resident parent is before the date on which the maintenance calculation in force has ceased to have effect, the day following the day on which that maintenance calculation ceases to have effect;

\pagebreak[3]

(ii) where the date of notification to the non-resident parent is after the date on which the maintenance calculation in force has ceased to have effect, the date of notification to the non-resident parent.”.
\end{enumerate}
\end{quotation}

(3) In regulation 31(1)($c$)  (transitional provision – effective dates and reduced benefit decisions) for “and in sub-paragraph ($c$)(iii)” substitute “, in sub-paragraph ($c$)(iii) and the first time it occurs in sub-paragraph ($d$)”.

\subsection[7. Amendment of the Child Support (Maintenance Calculations and Special Cases) Regulations 2000]{Amendment of the Child Support (Maintenance Calculations and Special Cases) Regulations 2000}

7.---(1)  The Child Support (Maintenance Calculations and Special Cases) Regulations 2000\footnote{S.I.\ 2001/155, relevant amending instruments are S.I.\ 2002/3019, S.I.\ 2003/1195 and S.I.\ 2003/2779.} shall be amended in accordance with the following paragraphs.

(2) In regulation 5 (nil rate) omit paragraph ($i$).

(3) In paragraph 4(1) of the Schedule (net weekly income) after head ($d$)  insert—
\begin{quotation}
“($dd$) any statutory paternity pay under Part XIIZA of the Contributions and Benefits Act or any statutory adoption pay under Part XIIZB of that Act\footnote{Part XIIZA was inserted by section 2 of the Employment Act 2002 (c.\ 22) and Part XIIZB was inserted by section 4 of that Act.};”.
\end{quotation}

(4) After paragraph 16 of the Schedule add—
\begin{quotation}
\section*{“Part VI\\*Benefits, pensions and allowances}

17.---(1)  Subject to paragraph (2), the net weekly income of a non-resident parent shall include payments made by way of benefits, pensions and allowances prescribed in regulation 4 for the purposes of paragraph 4(1)($b$)  and ($c$)  of Schedule 1 to the Act, to a non-resident parent or his partner at the rate payable at the effective date.

(2) Paragraph (1) applies only for the purpose of establishing whether the non-resident parent is a person to whom paragraph 5($b$)  of Schedule 1 to the Act applies.”.
\end{quotation}

\subsection[8. Amendment of the Child Support (Transitional Provisions) Regulations 2000]{Amendment of the Child Support (Transitional Provisions) Regulations 2000}

8.---(1)  The Child Support (Transitional Provisions) Regulations 2000\footnote{S.I.\ 2000/3186, relevant amending instruments are S.I.\ 2002/1204, S.I.\ 2003/328, S.I.\ 2003/347 and S.I.\ 2003/2779.} shall be amended in accordance with the following paragraphs.

(2) In regulation 2(1) (interpretation)—
\begin{enumerate}\item[]
($a$) after the definition of “the Act” insert—
\begin{quotation}
““the Arrears, Interest and Adjustment Regulations” means the Child Support (Arrears, Interest and Adjustment of Maintenance Assessments) Regulations 1992\footnote{S.I.\ 1992/1816, relevant amending instruments are S.I.\ 1995/1045, S.I.\ 1999/1510 (C.\ 43), S.I.\ 2001/162 and S.I.\ 2000/3185.};”;
\end{quotation}

($b$) in the definition of “new amount” for “in accordance with the conversion decision” substitute “from the case conversion date”.
\end{enumerate}

(3) In regulation 3 (decision and notice of decision), for paragraph (2) substitute—
\begin{quotation}
“(2) Where the Secretary of State acts in accordance with paragraph (1), the information used for the purposes of that supersession will be—
\begin{enumerate}\item[]
($a$) that held by the Secretary of State on the calculation date; or

($b$) where—
\begin{enumerate}\item[]
(i) regulation 5($b$)  applies; and

(ii) the Secretary of State is unable to make the decision required to be made in accordance with that regulation on the basis of the information referred to in paragraph ($a$),
\end{enumerate}
that which was used or considered to make the maintenance assessment to be superseded in accordance with regulation 3(1)($a$)  or ($b$).”.
\end{enumerate}
\end{quotation}

(4) After regulation 4 (revision, supersession and appeal of conversion decisions) insert—
\begin{quotation}
\subsection*{“Revision and supersession of an adjustment}

4A.  Where, on or after the calculation date, an application is made to the Secretary of State or he acts on his own initiative to revise or supersede an adjustment of the amounts payable under a maintenance assessment, he may revise or supersede that adjustment in accordance with the Decisions and Appeals Regulations.”.
\end{quotation}

(5) After regulation 5 (outstanding applications at calculation date) insert—
\begin{quotation}
\subsection*{“Outstanding revisions and supersessions at calculation date}

5A.  Regulation 5 shall apply in the same way to a decision of the Secretary of State acting on his own initiative under section 16 or 17 of the former Act to revise or supersede a maintenance assessment, an interim maintenance assessment or a departure direction as it does to an application made for the same purpose.”.
\end{quotation}

(6) In regulation 9(1) (amount of child support maintenance payable) for “Where” substitute “Subject to regulation 9A, where”.

(7) After regulation 9 insert—
\begin{quotation}
\subsection*{“Adjustment of the amount of child support maintenance payable}

9A.---(1)  Subject to paragraph (2), where—
\begin{enumerate}\item[]
($a$) there has been an overpayment of child support maintenance under a maintenance assessment; and

($b$) the amount payable under that maintenance assessment has been adjusted under regulation 10 of the Arrears, Interest and Adjustment Regulations as it applies to a maintenance assessment,
\end{enumerate}
that adjustment shall apply to the new amount or the transitional amount in the conversion decision, as the case may be, if—
\begin{enumerate}\item[]
(i) the overpayment remains on the case conversion date; and

(ii) the Secretary of State considers it appropriate in all the circumstances of the case having regard to the matters set out in regulation 10(1)($b$)  of the Arrears, Interest and Adjustment Regulations as it applies to a conversion decision.
\end{enumerate}

(2) Where the conversion decision relates to more than one parent with care, the adjustment of the amount payable under a maintenance assessment which applies to the new amount or the transitional amount, as the case may be, in accordance with paragraph (1) shall only apply in respect of the apportioned amount payable to the parent with care in relation to whom the maintenance assessment subject to the adjustment was made.

(3) In paragraph (2) the “apportioned amount” shall have the meaning given in regulation 11(4).

\subsection*{Attribution of payments}

9B.---(1)  Where—
\begin{enumerate}\item[]
($a$) there are arrears of child support maintenance under a maintenance assessment; and

($b$) the Secretary of State has attributed any payment of child support maintenance made by an absent parent to child support maintenance due as he thinks fit, in accordance with regulation 9 of the Arrears, Interest and Adjustment Regulations as it applies to a maintenance assessment,
\end{enumerate}
that attribution of payments shall apply to the new amount or the transitional amount in the conversion decision, as the case may be, if—
\begin{enumerate}\item[]
(i) the arrears remain on the case conversion date; and

(ii) the Secretary of State has made that attribution of payments as he thought fit, in accordance with regulation 9 of the Arrears, Interest and Adjustment Regulations as it applies to a conversion decision.”.
\end{enumerate}
\end{quotation}

(8) In regulation 16 (conversion calculation and conversion decision)—
\begin{enumerate}\item[]
($a$) for paragraph (1)($b$)  substitute—
\begin{quotation}
“($b$) taking into account the information used in accordance with regulation 3(2); and”;
\end{quotation}

($b$) after paragraph (2B)\footnote{Sub-paragraph (2B) was inserted by S.I.\ 2003/347.} add—
\begin{quotation}
“(2C) For the purposes of regulations 9 and 10 of the Arrears, Interest and Adjustment Regulations, a conversion decision shall be treated on or after the case conversion date as if it were a maintenance calculation.”.
\end{quotation}
\end{enumerate}

(9) In regulation 27 (subsequent decision with effect in transitional period---amount payable)—
\begin{enumerate}\item[]
($a$) in paragraph (9)\footnote{Sub-paragraph (9) was added by S.I.\ 2003/328 and amended by S.I.\ 2003/2779.}, for “Subject to paragraph (10), where” substitute “Where”;

($b$) in paragraph (10)\footnote{Sub-paragraph (10) was added by S.I.\ 2003/2779.}—
\begin{enumerate}\item[]
(i) for “Where” substitute “Subject to paragraph (11), where”;

(ii) for the words from “so that the subsequent decision” to “before decision A was made” substitute “as if decision A had not been made.”;
\end{enumerate}

($c$) after paragraph (10) add—
\begin{quotation}
“(11) In the circumstances set out in paragraph (10), paragraph (9) shall not apply where the decision in place before decision A was made was the decision which took effect from the case conversion date.”.
\end{quotation}
\end{enumerate}

\subsection[9. Amendment of the Child Support (Variations) Regulations 2000]{Amendment of the Child Support (Variations) Regulations 2000}

9.---(1)  The Child Support (Variations) Regulations 2000\footnote{S.I.\ 2001/156, relevant amending instruments are S.I.\ 2002/1204 and S.I.\ 2003/328.} shall be amended in accordance with the following paragraphs.

(2) In regulation 1(2) (citation, commencement and interpretation) after the definition of “Maintenance Calculations and Special Cases Regulations”, insert—
\begin{quotation}
““partner” has the same meaning as in paragraph 10C(4) of Schedule 1 to the Act;”.
\end{quotation}

(3) In regulation 7(5)($b$)  (prescribed circumstances) omit the words from “and for this purpose” to “the Act”.

(4) In regulation 27(5) (effect on maintenance calculation—general) for “paragraph 4(1)($b$)” substitute “paragraph 4(1)”. 

\bigskip

Signed 
by authority of the Secretary of State for Work and Pensions.

{\raggedleft
\emph{P.~Hollis}\\*Parliamentary Under-Secretary of State,\\*Department of Work and Pensions

}

%St Andrew's House, Edinburgh

%Dated
15th September 2004

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations provide for the amendment of regulations relating to child support.

The powers exercised to make these Regulations are those contained in the Child Support Act 1991 (“the 1991 Act”). Some of those powers are conferred by provisions of the 1991 Act prior to the amendments made to that Act by the Child Support, Pensions and Social Security Act 2000 (“the 2000 Act”), which amendments are not fully in force, and relate to the child support scheme which was in force prior to 3rd March 2003 and which remains in force for the purposes of certain cases (“the old scheme”). Other powers are conferred by provisions of the 1991 Act as amended by the 2000 Act, which relate to the child support scheme provided for by those amendments, which came into force for the purposes of specified categories of cases on 3rd March 2003 (\emph{see} the Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 12) Order 2003) (“the new scheme”).

Regulation 2 amends regulation 6B of the Social Security and Child Support (Decisions and Appeals) Regulations 1999 (“the Decisions and Appeals Regulations”). Regulation 2(2)($a$)  amends regulation 6B(3) of the Decisions and Appeals Regulations to provide that where the application for supersession is made on more than one ground, if one of the grounds which does not relate to the net income of the non-resident parent leads to a supersession, regulation 6B of those Regulations shall not apply to the ground which relates to the net income of the non-resident parent.

Regulation 2(2)($b$)  adds a new paragraph (5) to regulation 6B of the Decisions and Appeals Regulations. This paragraph provides that where there has been an earlier application for a supersession to which paragraph (1) of that regulation 6B applied, and there is a later application for supersession on a ground other than that relating to the net income of the non-resident parent, the superseding decision may be made on the basis that the earlier application was made at the same time as the later application. This amendment applies to the new scheme.

Regulation 3 amends the Child Support (Information, Evidence and Disclosure) Regulations 1992 to clarify that the Secretary of State may disclose information to all the parties to an appeal for the purposes of an appeal to an appeal tribunal. This amendment applies to the old scheme and the new scheme.

Regulation 4 amends regulation 17 of the Child Support (Maintenance Assessment Procedure) Regulations 1992 which relate to the old scheme. This regulation adds a new sub-paragraph ($f$)  to regulation 17(1) of those Regulations to provide a new ground for revision in a case where an appeal is made within the time limits provided for in regulations 31 and 32 of those Regulations and that appeal has not been determined.

Regulation 5 amends the Child Support (Maintenance Assessments and Special Cases) Regulations 1992 which relate to the old scheme. Regulation 5(2) inserts a new head ($gg$)  into paragraph 1(1) of Schedule 1 to those Regulations to provide that any statutory paternity pay or any statutory adoption pay (under Parts XIIZA and XIIZB of the Social Security Contributions and Benefits Act 1992 (c.\ 4), respectively) are brought within the definition of “earnings” in the case of employment as an employed earner for the purposes of calculating “net income” of an absent parent and a parent with care.

Regulation 5(3) inserts a new paragraph 36A into Schedule 2 to those Regulations to provide for sums payable to a child in respect of financial assistance given, or given under arrangements made, by the Secretary of State or the National Assembly for Wales under section 14 of the Education Act 2002 (c.\ 32), to be disregarded when calculating the net income of the absent parent or the parent with care. Regulation 5(4)($a$)  and ($b$)  makes amendments to paragraphs 1, 7, 14 and 20 of Schedule 3B to those Regulations to provide for the calculation of costs in respect of travelling between home and work to be made in metric equivalents. Regulation 5(4)($c$)  makes minor technical amendments.

Regulation 6 amends the Child Support (Maintenance Calculation Procedure) Regulations 2000 which relate to the new scheme. Regulation 6(2) adds a new sub-paragraph ($d$)  to regulation 29(1) of those Regulations to provide effective dates for a maintenance calculation which is made in response to an application where there is at the time of that application a maintenance calculation in force in relation to the same non-resident parent and a different person with care and that maintenance calculation ceases to have effect. Regulation 6(3) makes an amendment consequent upon the amendment made by regulation 6(2), to regulation 31(1)($c$)  of those Regulations.

Regulation 7 amends the Child Support (Maintenance Calculations and Special Cases) Regulations 2000 which relate to the new scheme. Regulation 7(2) omits paragraph ($i$)  from regulation 5 of those Regulations consequent upon the amendment made by regulation 7(5). Regulation 7(3) inserts a head ($dd$)  into paragraph 4(1) of the Schedule to those Regulations to provide that any statutory paternity pay or any statutory adoption pay are brought within the definition of “earnings” in the case of employment as an employed earner for the purposes of calculating the “net weekly income” of a non-resident parent. Regulation 7(4) adds a new Part VI to the Schedule to those Regulations to include benefits, pensions and allowances prescribed under paragraph 4(1)($b$)  and ($c$)  of Schedule 1 to the 1991 Act, paid to a non-resident parent or his partner, in the list of payments which are aggregated to calculate the net weekly income of the non-resident parent, for the purposes of establishing whether that non-resident parent is a person to whom paragraph 5($b$)  of Schedule 1 to the 1991 Act applies.

Regulation 8 amends the Child Support (Transitional Provisions) Regulations 2000 (“the Transitional Regulations”). Regulation 8(2) amends the interpretation provision of those Regulations. Regulation 8(3) amends regulation 3(2) of those Regulations to provide that where the Secretary of State supersedes under regulation 3(1)($a$)  or ($b$)  in a case to which regulation 5($b$)  applies he will (where he is unable to make the decision on the basis of the information held at the calculation date) use the information used or considered to make the maintenance assessment to be superseded. Regulation 8(4) inserts a new regulation 4A into those Regulations to provide that where an adjustment has been made to a maintenance assessment it may be revised or superseded under the Decisions and Appeals Regulations. Regulation 8(5) inserts a new regulation 5A into the Transitional Regulations to provide that regulation 5 applies in the same way to a decision of the Secretary of State acting on his own initiative to revise or supersede a maintenance assessment, an interim maintenance assessment or a departure direction.

Regulation 8(8)($a$)  makes an amendment to regulation 16(1)($b$)  of those Regulations consequent upon that made by regulation 8(2). Regulation 8(6) makes an amendment consequent upon that made by regulation 8(7). Regulation 8(7) inserts new regulations 9A and 9B into those Regulations. Regulation 9A provides that where there has been an adjustment made to a maintenance assessment, it may be applied to the new amount or transitional amount payable under a conversion decision, where the overpayment remains on the case conversion date and the Secretary of State considers it appropriate in all the circumstances. In a case where there is more than one parent with care the adjustment to the conversion decision shall only apply to the parent with care in respect of whom the maintenance assessment was made. Regulation 9B provides that where there are arrears of child support maintenance payable under a maintenance assessment and the Secretary of State has attributed a payment of that maintenance, it may be applied to the new amount or transitional amount payable under a conversion decision where the arrears are outstanding on the case conversion date. Regulation 8(8)($b$)  makes a minor technical amendment to regulation 16. Regulation 8(9) amends regulation 27 to make provision for specific cases where a subsequent decision is made.

Regulation 9 makes amendments to the Child Support (Variations) Regulations 2000. Regulation 9(2) inserts a new definition of “partner” into regulation 1(2) of those Regulations. Regulation 9(3) makes an amendment consequent upon that made by regulation 9(2). Regulation 9(4) makes a minor technical amendment.

A full regulatory impact assessment has not been produced for this instrument as it has no impact on the cost of business. 

\end{document}