\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Social Security (Claims and Payments and Miscellaneous Amendments) Regulations 2002}

\newcommand\regsnumber{2002/428}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2002 No.\ 428}

\date{Made
26th February 2002\\
Laid before Parliament
5th March 2002\\
Coming into force
2nd April 2002
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.57402pt}

\begin{document}

\maketitle

\noindent
The Secretary of State for Work and Pensions, except in relation to working families' tax credit and disabled person’s tax credit, and the Commissioners of Inland Revenue, in relation to those credits and to regulations 1, 3 and 4 only, in exercise of the powers conferred by sections 5(1)($a$)  and ($b$)  and 191 of the Social Security Administration Act 1992\footnote{1992 c.\ 5. Section 191 is cited because of the meaning ascribed to the word “prescribe”.} and sections 9(1), 10(3) and (6) and 84 of the Social Security Act 1998\footnote{1998 c.\ 14. Section 84 is cited because of the meaning ascribed to the word “prescribe”.}, and now vested in them\footnote{\emph{See} section 2(1)($c$) of, and paragraphs 7($b$) and 8($a$) of Schedule 2 to, the Tax Credits Act 1999 (c.\ 10), by which functions concerning certain benefits were transferred to the Commissioners of Inland Revenue.}, and of all other powers enabling them in that behalf, and after agreement by the Social Security Advisory Committee that proposals in respect of the Regulations should not be referred to it\footnote{\emph{See} section 173(1)($b$) of the Social Security Administration Act 1992.}, hereby make the following Regulations: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation, commencement and interpretation]{Citation, commencement and interpretation}

1.---(1)  These Regulations may be cited as the Social Security (Claims and Payments and Miscellaneous Amendments) Regulations 2002 and shall come into force on 2nd April 2002.

(2) In these Regulations “the Claims and Payments Regulations” means the Social Security (Claims and Payments) Regulations 1987\footnote{S.I.\ 1987/1968; relevant amending instruments are S.I.\ 1997/793 and 2290, 1999/2572 and 3108 and 2000/636, 1483, 1596 and 1982.}.

\subsection[2. Amendment of regulation 6 of the Claims and Payments Regulations]{Amendment of regulation 6 of the Claims and Payments Regulations}

2.---(1)  Regulation 6 of the Claims and Payments Regulations\footnote{Paragraphs (16) to (19), (21) and (22) were substituted by S.I.\ 2000/1596 and paragraph (29) was added by S.I.\ 1997/2290 and amended by S.I.\ 2000/1596.} (date of claim) shall be amended in accordance with the following paragraphs.

(2) In paragraph (16)($b$)  for the word “payable” there shall be substituted the word “awarded”.

(3) In paragraph (17)($c$)  after the words “the claimant” there shall be inserted the words “, a member of his family or the disabled person”.

(4) In paragraph (18) for sub-paragraphs ($a$)  and ($b$)  there shall be substituted the following sub-paragraphs—
\begin{quotation}
“($a$) a claim for the qualifying benefit was made not later than 10 working days after the date of the original claim and the claim for the qualifying benefit had not been decided;

($b$) after the original claim had been decided the claim for the qualifying benefit had been decided in favour of the claimant, a member of his family or the disabled person; and”.
\end{quotation}

(5) In paragraph (19)($b$)  for the words “again becomes payable” there shall be substituted the words “is re-awarded”.

(6) In paragraph (21)($a$)  for the words “the claimant’s or the disabled person’s favour” there shall be substituted the words “favour of the claimant, a member of his family or the disabled person”.

(7) In paragraph (22)—
\begin{enumerate}\item[]
($a$) after the words “paragraphs (16) to (21)” there shall be inserted the words “and (30)”;

($b$) in the definition of “qualifying benefit”, in paragraph ($d$), after the words “any other relevant benefit which” there shall be inserted the words “, when it is awarded or re-awarded,”; and

($c$) after the definition of “the disabled person” there shall be added the following definition—
\begin{quotation}
    ““family” has the same meaning as in section 137(1) of the Contributions and Benefits Act\footnote{1992 c.\ 4.} or, as the case may be, section 35(1) of the Jobseekers Act\footnote{1995 c.\ 18.}.”. 
\end{quotation}
\end{enumerate}

(8) After paragraph (29) there shall be added the following paragraph—
\begin{quotation}
“(30) Where—
\begin{enumerate}\item[]
($a$) a claimant was awarded income support or income-based jobseeker’s allowance (“the original award”);

($b$) the original award was terminated and not later than 10 working days after the termination, the claimant, a member of his family or the disabled person claimed a qualifying benefit; and

($c$) the claimant makes a further claim for income support or income-based jobseeker’s allowance within 3 months of the date on which the claim for the qualifying benefit was decided,
\end{enumerate}
the further claim shall be treated as made on the date of termination of the original award or the first date in respect of which the qualifying benefit is awarded, whichever is the later.”.
\end{quotation}

\subsection[3. Amendment of regulation 19 of the Claims and Payments Regulations]{Amendment of regulation 19 of the Claims and Payments Regulations}

3.---(1)  Regulation 19 of the Claims and Payments Regulations\footnote{Regulation 19 was substituted by S.I.\ 1997/793 and amended by S.I.\ 1997/2290, 1999/2572 and 2000/1982.} (time for claiming benefit) shall be amended in accordance with the following paragraphs.

(2) In paragraph (4)($a$)  after the word “any” there shall be inserted the words “one or more”.

(3) In paragraph (6) for the words from “where---” to the end of the paragraph there shall be substituted the words—
\begin{quotation}
    “where the claim is not made within the time specified for that benefit in Schedule 4, the prescribed time for claiming the benefit shall be extended, subject to a maximum extension of one month, to the date on which the claim is made, where—
\begin{enumerate}\item[]
    ($a$) 
    any one or more of the circumstances specified in paragraph (7) applies or has applied to the claimant; and

    ($b$) 
    as a result of that circumstance or those circumstances the claimant could not reasonably have been expected to make the claim earlier.”. 
\end{enumerate}
\end{quotation}

(4) In paragraph (7)($d$)—
\begin{enumerate}\item[]
($a$) after the words “the claimant” in the first place where they occur, there shall be inserted the words “or, in the case of income support or jobseeker’s allowance, the claimant or his partner”; and

($b$) after the words “the claimant” in the second place where they occur, there shall be inserted the words “or his partner, as the case may be,”.
\end{enumerate}

\subsection[4. Amendment of the Decisions and Appeals Regulations]{Amendment of the Decisions and Appeals Regulations}

4.---(1)  The Social Security and Child Support (Decisions and Appeals) Regulations 1999\footnote{S.I.\ 1999/991; the relevant amending instrument is S.I.\ 2000/1596.} shall be amended in accordance with the following paragraphs.

(2) For regulation 3(7)\footnote{Paragraph (7) was substituted by S.I.\ 2000/1596.} (revision of decisions) there shall be substituted the following paragraph—
\begin{quotation}
“(7) Where—
\begin{enumerate}\item[]
($a$) the Secretary of State or an officer of the Board makes a decision under section 8 or 10 awarding a relevant benefit to a claimant (“the original award”); and

($b$) an award of another relevant benefit or of an increase in the rate of another relevant benefit is made to the claimant or a member of his family for a period which includes the date on which the original award took effect,
\end{enumerate}
the Secretary of State or an officer of the Board, as the case may require, may revise the original award.”.
\end{quotation}

(3) In regulation 6(2)($e$)(ii)\footnote{Sub-paragraph ($e$) was substituted by S.I.\ 2000/1596.} (supersession of decisions)—
\begin{enumerate}\item[]
($a$) for the words “on a date after that entitlement arises” there shall be substituted the words “subsequent to the first day of the period to which that entitlement relates”; and

($b$) the words “, and is paid,” shall be omitted.
\end{enumerate}

(4) For regulation 7(7)\footnote{Paragraph (7) was substituted by S.I.\ 2000/1596.} (date from which a decision superseded under section 10 takes effect) there shall be substituted the following paragraph—
\begin{quotation}
“(7) A decision which is superseded in accordance with regulation 6(2)($e$)  shall be superseded from the date on which entitlement arises to the other relevant benefit referred to in regulation 6(2)($e$)(ii) or to an increase in the rate of that other relevant benefit.”.
\end{quotation}

\bigskip

 Signed 
by authority of the Secretary of State for Work and Pensions. 

{\raggedleft
\emph{Malcolm Wicks}\\*Parliamentary Under-Secretary of State,\\*Department for Work and Pensions

}

%St Andrew's House, Edinburgh

%Dated
24th February 2002

\bigskip

% Signed 
%by authority of the Secretary of State for Work and Pensions. 

{\raggedleft
\emph{Dave Hartnett}\\*\emph{Ann Chant}\\*Two of the Commissioners of Inland Revenue

}

%St Andrew's House, Edinburgh

%Dated
26th February 2002


\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations amend the Social Security (Claims and Payments) Regulations 1987 (“the Claims and Payments Regulations”) and the Social Security and Child Support (Decisions and Appeals) Regulations 1999 (“the Decisions and Appeals Regulations”).

Regulation 2 amends regulation 6 of the Claims and Payments Regulations to provide for certain claims to take effect earlier when entitlement is affected by benefit awarded to a partner or child or where entitlement to income support or jobseeker’s allowance is affected by a qualifying benefit, and makes minor amendments relating certain provisions in regulation 6 to the award rather than the payability of a benefit.

Regulation 3 amends regulation 19 to provide for an extension of the time for claiming income support, jobseeker’s allowance, working families' tax credit and disabled person’s tax credit in specified circumstances.

Regulation 4 amends the Decisions and Appeals Regulations. The power to revise or supersede a decision under regulation 3(7) or 6(2)($e$)  is amended. The date certain decisions are superseded under regulation 7(7) is amended.

These Regulations do not impose a charge on business. 

\end{document}