\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support (Temporary Compensation Payment Scheme) (Modification and Amendment) Regulations 2002}

\newcommand\regsnumber{2002/1854}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2002 No.\ 1854}

\date{Made
16th July 2002\\
%Laid before Parliament
%26th March 2002\\
Coming into force
17th July 2002
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.57402pt}

\begin{document}

\maketitle

\noindent
Whereas a draft of this instrument was laid before Parliament in accordance with section 27(12) of the Child Support, Pensions and Social Security Act 2000\footnote{2000 c.\ 19.} and approved by resolution of each House of Parliament:

Now, therefore, the Secretary of State for Work and Pensions, in exercise of the powers conferred upon him by section 27(1), (9) and (10) of the Child Support, Pensions and Social Security Act 2000, and of all other powers enabling him in that behalf, hereby makes the following Regulations: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and commencement]{Citation and commencement}

1.  These Regulations may be cited as the Child Support (Temporary Compensation Payment Scheme) (Modification and Amendment) Regulations 2002 and shall come into force on the day after the day that they are made.

\subsection[2. Modification of section 27(5) of the Child Support, Pensions and Social Security Act 2000]{Modification of section 27(5) of the Child Support, Pensions and Social Security Act 2000}

2.  Section 27 of the Child Support, Pensions and Social Security Act 2000 (temporary compensation payment scheme) shall have effect as if in subsection (5)—
\begin{enumerate}\item[]
($a$) for “2002” there were substituted “2005”; and

($b$) for “2003” there were substituted “2006”.
\end{enumerate}

\subsection[3. Amendment of Regulations]{Amendment of Regulations}

3.  In regulation 3 of the Child Support (Temporary Compensation Payment Scheme) Regulations 2000 (prescribed date)\footnote{S.I.\ 2000/3174.}, for “2002”, there shall be substituted “2005”. 

\bigskip

Signed 
by authority of the Secretary of State for Work and Pensions.

{\raggedleft
\emph{P.~Hollis}\\*Parliamentary Under-Secretary of State,\\*Department of Work and Pensions

}

%Dated
16th July 2002

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations provide for modifications and amendments in relation to the temporary compensation payment scheme (“the scheme”) under section 27 of the Child Support, Pensions and Social Security Act 2000 (“the Act”). The scheme makes provision for certain cases where there has been a delay in the making of a maintenance assessment under the Child Support Act 1991 (c.\ 48) leading to arrears of child support maintenance.

Regulation 1 makes provision for citation and commencement.

Regulation 2 modifies section 27 of the Act, so that it has effect as if later dates were substituted in subsection (5) of that section as the dates before which an agreement must be entered into and expire.

Regulation 3 amends regulation 3 of the Child Support (Temporary Compensation Payment Scheme) Regulations 2000, substituting a later prescribed date for the purposes of section 27(1)($a$)  of the Act, being the date before which a maintenance assessment must be made for the scheme to apply.

These Regulations do not impose costs on business. 

\end{document}