\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Social Security (Miscellaneous Amendments) (No.~2) Regulations 2008}

\newcommand\regsnumber{2008/1042}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and~Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2008 No.\ 1042}

\date{Made
7th April 2008\\
Laid before Parliament
11th April 2008\\
Coming into~force
in accordance with regulation~1
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.61603pt}

%\hbadness=10000

\begin{document}

\maketitle

\noindent
The Secretary of State for~Work and~Pensions makes the following Regulations in exercise of the powers conferred by sections 123(1)($d$)  and~($e$),~135(1),~136(3) to (5), 136A(3), 137(1) and~(2)($f$), ($h$)  and~(i), 175(1), (3) and~(4) of the Social Security Contributions and~Benefits Act 1992\footnote{1992 c.~4. Section 123(1)($e$)  was substituted by paragraph~1(1) of Schedule 9 to the Local Government Finance Act 1992 (c.~14). Section 136A was inserted by paragraph~3 of Schedule 2 to the State Pension Credit Act 2002 (c.~16). Section 137(1) is an interpretation provision and~is cited because of the meaning of the word “prescribed”. Section 175(1) and~(4) was amended by section 2 of, and~paragraph~29(1), (2) and~(4) of Schedule 3 to the Social Security Contributions (Transfer of Functions, etc.)\ Act 1999 (c.~2).}, sections 5(1)($h$)  and~($j$),~6(1)($h$)  and~($k$), 75(1), (2) and~(4), 134, 189(1) and~(3) to (6) and~191 of the Social Security Administration Act 1992\footnote{1992 c.~5. Section 189(1) was amended by paragraph~57(1) and~(2) of Schedule 3 to the Social Security Contributions (Transfer of Functions, etc.)\ Act 1999 (c.~2), paragraph~109 of Schedule 7 to the Social Security Act 1998 (c.~14) and~Schedule 6 to the Tax Credits Act 2002 (c.~21). Section 189(4), (5) and~(6) was amended by paragraph~109 of Schedule 7 to the Social Security Act 1998. Section 191 is cited for~the meaning of the word “prescribed”.} and~sections 10(6), 34(1) and~(2), 79(1), (3) and~(4) and~84 of the Social Security Act 1998\footnote{1998 c.~14. Section 79(1) was amended by paragraphs 12 and~13(1) and~(2) of Schedule 4 to the Tax Credits Act 2002 (c.~21). Section 84 is cited for~the meaning of “prescribed”.}.

The Social Security Advisory Committee has agreed that the proposals in respect of these Regulations should not be referred to it\footnote{\emph{See} sections 172(1) and~173(1)($b$)  of the Social Security Administration Act 1992.}.

\enlargethispage{-\baselineskip}

In accordance with section 176(1) of the Social Security Administration Act 1992, the Secretary of State has consulted with organisations which appear to him to be representative of the authorities concerned\footnote{Section 176(1) was amended by paragraph~23 of Schedule 9 to the Local Government Finance Act 1992 (c.~14), section 69(6) of the Child Support, Pensions and~Social Security Act 2000 (c.~19) and~paragraph~3(4) of Schedule 13 to the Housing Act 1996 (c.~52).}. 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation, commencement and~interpretation]{Citation, commencement and~interpretation}

1.---(1)  These Regulations may be cited as the Social Security (Miscellaneous Amendments) (No.~2) Regulations 2008.

(2) Subject to paragraph~(3), these Regulations shall come into force on 19th May 2008.

(3) Regulations 3(12)($h$)  and~5(12)($d$)  shall come into force on 27th October 2008.

(4) In these Regulations—
\begin{enumerate}\item[]
“the Decisions and~Appeals Regulations” means the Social Security and~Child Support (Decisions and~Appeals) Regulations 1999\footnote{S.I.~1999/991.};

“the Housing Benefit Regulations” means the Housing Benefit Regulations 2006\footnote{S.I.~2006/213.};

“the Housing Benefit (State Pension Credit) Regulations” means the Housing Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations 2006\footnote{S.I.~2006/214.};

“the Council Tax Benefit Regulations” means the Council Tax Benefit Regulations 2006\footnote{S.I.~2006/215.};

“the Council Tax Benefit (State Pension Credit) Regulations” means the Council Tax Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations 2006\footnote{S.I.~2006/216.}; and

“the Housing Benefit and~Council Tax Benefit (Consequential Provisions) Regulations” means the Housing Benefit and~Council Tax Benefit (Consequential Provisions) Regulations 2006\footnote{S.I.~2006/217.}.
\end{enumerate}

\subsection[2. Amendments to the Decisions and~Appeals Regulations]{Amendments to the Decisions and~Appeals Regulations}

2.  Regulation 7 of the Decisions and~Appeals Regulations shall be amended as follows—
\begin{enumerate}\item[]
($a$) in sub-paragraph~(2)($bc$)\footnote{Sub-paragraph~(2)($bc$)  was inserted by S.I.~2006/2377 and~amended by S.I.~2007/2470.} (date from which a decision superseded under section 10 takes effect), for~“sub-paragraph~($bd$)” substitute “paragraph~(2A)”;

($b$) omit sub-paragraph~(2)($bd$)\footnote{Sub-paragraph~(2)($bd$)  was inserted by S.I.~2007/2470.} (date from which a decision superseded under section 10 takes effect); and

($c$) after paragraph~(2) (date from which a decision superseded under section 10 takes effect), insert—
\begin{quotation}
“(2A) Paragraph (2)($bc$)  shall only apply to the disabled person whose benefit is affected by the cessation of payment of carer’s allowance.”
\end{quotation}
\end{enumerate}

\subsection[3. Amendments to the Housing Benefit Regulations]{Amendments to the Housing Benefit Regulations}

3.---(1)  The Housing Benefit Regulations shall be amended as follows.

(2) In regulation~2(1) (interpretation)—
\begin{enumerate}\item[]
($a$) in the definition of “concessionary payment”, omit “or~the Child Benefit Act 1975”; and

($b$) omit the definition of “person on state pension credit”.
\end{enumerate}

(3) In regulation~7(8)($c$)(ii)\footnote{Regulation 7(8) was amended by S.I.~2007/2618.} (circumstances in which a person is or~is not to be treated as occupying a dwelling as his home)—
\begin{enumerate}\item[]
($a$) for~“Part III”, substitute “Part VIII”; and

($b$) omit “9, 10, 11,”.
\end{enumerate}

(4) In regulation~28 (treatment of child care charges)—
\begin{enumerate}\item[]
($a$) for~paragraph~(11)($a$), substitute “the claimant’s applicable amount includes a disability premium on account of the other member’s incapacity;”;

($b$) in paragraph~(11)($b$), omit “or~a higher pensioner premium”; and

($c$) in paragraph~(11)($g$), for~“Department of Health and~Social Services for~Northern Ireland”, substitute “Department of Health, Social Services and~Public Safety in Northern Ireland”.
\end{enumerate}

(5) In regulation~42\footnote{A relevant amending instrument is S.I.~2007/1749.} (notional income), omit paragraphs (3) to (5).

(6) In regulation~53(1) (students---interpretation)—
\begin{enumerate}\item[]
($a$) in the definition of “grant” for~“paragraph~54”, substitute “paragraph~51”;

($b$) for~the definition of “sandwich course” substitute—
\begin{quotation}
““sandwich course” has the meaning prescribed in regulation~2(9) of the Education (Student Support) Regulations 2008\footnote{S.I.~2008/529.}, regulation~4(2) of the Education (Student Loans) (Scotland) Regulations 2007\footnote{S.S.I.~2007/154.} or~regulation~2(8) of the Education (Student Support) Regulations (Northern Ireland) 2007\footnote{S.R.~(NI) 2007 No.~195.}, as the case may be;”; and
\end{quotation}

($c$) in the definition of “student loan” for~“Students’ Allowances (Scotland) Regulations 1999”, substitute “Students’ Allowances (Scotland) Regulations 2007\footnote{S.S.I.~2007/153.}”.
\end{enumerate}

(7) In regulation~56 (full-time students to be treated as not liable to make payments in respect of a dwelling)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~(2)($c$)  omit “pensioner premium for~persons under 75 or, as the case may be, persons 75 or~over, higher pensioner premium,”;

($b$) for~sub-paragraph~(2)($i$)(ii), substitute—
\begin{quotation}
“(ii) an allowance or, as the case may be, bursary has been granted which includes a sum under paragraph~(1)($d$)  of regulation~4 of the Students’ Allowances (Scotland) Regulations 2007 or, as the case may be, under paragraph~(1)($d$)  of regulation~4 of the Education Authority Bursaries (Scotland) Regulations 2007\footnote{S.S.I.~2007/149.}, in respect of expenses incurred; or”;
\end{quotation}

($c$) in sub-paragraph~(2)($i$)(iv) for~“regulation~13 of the Education (Student Support) Regulations 2005”, substitute “regulation~37 of the Education (Student Support) Regulations 2008”, and~for~“regulation~13 of the Education (Student Support) Regulations (Northern Ireland) 2000”, substitute “regulation~39 of the Education (Student Support) Regulations (Northern Ireland) 2007”;

($d$) in sub-paragraph~(2)($i$)(v) for~“Student Awards Regulations (Northern Ireland) 1999”, substitute “Students Awards Regulations (Northern Ireland) 2003\footnote{S.R.(NI) 2003 No.~459.}”; and

($e$) in paragraph~(4), omit “refers”.
\end{enumerate}

(8) In regulation~63(2) (other amounts to be disregarded) for~“Students’ Allowance (Scotland) Regulations 1999”, substitute “Students’ Allowances (Scotland) Regulations 2007”.

(9) In regulation~88(3)($d$)  (duty to notify changes of circumstances), after “income support” where it first occurs, insert “or~income-based jobseeker’s allowance”.

(10) In Schedule 3\footnote{Relevant amending instruments are S.I.~2006/2378, S.I.~2007/688 and~S.I.~2008/632.} (applicable amounts)—
\begin{enumerate}\item[]
($a$) in paragraph~3(3)($a$)  and~($b$), for~“sub-paragraph~($a$)  of this paragraph”, substitute “sub-paragraph~(1)($a$)”;

($b$) in paragraph~3(4)($e$), omit “9, 10, 11 or”;

($c$) for~paragraph~6, substitute—
\begin{quotation}
“6. The following premiums, namely—
\begin{enumerate}\item[]
($a$) a severe disability premium to which paragraph~14 applies;

($b$) an enhanced disability premium to which paragraph~15 applies;

($c$) a disabled child premium to which paragraph~16 applies; and

($d$) a carer premium to which paragraph~17 applies,
\end{enumerate}
may be applicable in addition to any other premium which may apply under this     Schedule.”;
\end{quotation}

($d$) omit paragraphs 9, 10 and~11;

($e$) in paragraph~13 omit from the heading “Higher Pensioner and~Disability Premiums” and~substitute “Disability Premium”;

($f$) in paragraph~13(3), omit “the higher pensioner premium or”;

($g$) omit paragraph~13(4);

($h$) in paragraph~13(8) for~“within the meaning of paragraph~11(5)”, substitute “(a person to whom regulation~13A(1) of the Social Security (Incapacity for~Work) (General) Regulations 1995 applies, and~who again becomes incapable of work for~the purposes of Part XIIA of the Act)”; and

($i$) in paragraph~20, omit sub-paragraphs (2), (3) and~(4).
\end{enumerate}

(11) In Schedule 4 (sums to be disregarded in the calculation of earnings)—
\begin{enumerate}\item[]
($a$) for~paragraph~3(3)($a$), substitute “the claimant is a member of a couple and~his applicable amount includes an amount by way of the disability premium under Schedule 3; and”;

($b$) omit paragraph~3(4) and~(5);

($c$) in paragraph~9—
\begin{enumerate}\item[]
(i) for~“one of more employments”, substitute “one or~more employments”; and

(ii) for~“paragraph~6”, substitute “paragraph~8”;
\end{enumerate}

($d$) in paragraph~17(2)($b$)(iv)($aa$)  omit “a higher pensioner premium or”, “11 or” and~“respectively”;

($e$) in paragraph~17(2)($b$)(iv)($bb$)  omit “higher pensioner premium or”; and

($f$) in paragraph~17(3)($b$)  for~“regulation~28(1)($c$)”, substitute “regulation~27(1)($c$)”.
\end{enumerate}

(12) In Schedule 5 (sums to be disregarded in the calculation of income other than earnings)—
\begin{enumerate}\item[]
($a$) for~paragraph~15($b$), substitute “a war widow’s pension or~any corresponding pension payable to a widower or~surviving civil partner;”;

($b$) omit paragraph~18;

($c$) in paragraph~25(1)($a$)  before “with a scheme”, insert “in accordance”;

($d$) in paragraph~44(1)($a$)  for~“or~12” substitute “or~11” and~after “Regulations”, insert “2003”;

($e$) in paragraph~44(1)($b$)  for~“3, 5 and~8” substitute “5, 6 and~10” and~for~“National Health Service (Travelling Expenses and~Remission of Charges) Regulations 1988” substitute “National Health Service (Travelling Expenses and~Remission of Charges) (Wales) Regulations 2007”;

($f$) in paragraph~44(1)($c$)  for~“or~8” substitute “or~11” and~after “(Scotland)” insert “(No.~2)”;

($g$) in paragraph~45 omit “8,”; and

($h$) for~paragraph~47, substitute—
\begin{quotation}
“47.---(1)  Where a claimant’s applicable amount includes an amount by way of family premium, £15 of any payment of maintenance, other than child maintenance, whether under a court order or~not, which is made or~due to be made by the claimant’s former partner, or~the claimant’s partner’s former partner.

(2) For~the purpose of sub-paragraph~(1) where more than one maintenance payment falls to be taken into account in any week, all such payments shall be aggregated and~treated as if they were a single payment.

(3) A payment made by the Secretary of State in lieu of maintenance shall, for~the purposes of sub-paragraph~(1), be treated as a payment of maintenance made by a person specified in sub-paragraph~(1).

\medskip

47A.---(1)  Any payment of child maintenance which is made by the parent of the child or~young person except where the person making the payment is the claimant or~the claimant’s partner.

(2) In this paragraph, “child maintenance” means any payment towards the maintenance of a child or~young person, including any payment made voluntarily and~payments made through or~under—
\begin{enumerate}\item[]
($a$) the Child Support Act 1991\footnote{1991 c.~48.};

($b$) the Child Support (Northern Ireland) Order 1991\footnote{S.R.~(NI) 1991 No.~23.};

($c$) a court order (including a consent order);

($d$) a minute of agreement as registered for~execution in the Books of Council and~Session or~the sheriff court books;
\end{enumerate}
and~for~this purpose a “young person” is a person referred to in regulation~19 (persons of a prescribed description).

(3) For~the purpose of sub-paragraph~(1) where more than one maintenance payment falls to be taken into account in any week, all such payments shall be aggregated and~treated as if they were a single payment.

(4) A payment made by the Secretary of State in lieu of maintenance shall, for~the purposes of sub-paragraph~(1), be treated as a payment of maintenance made by a person specified in sub-paragraph~(1).”.
\end{quotation}
\end{enumerate}

(13) In Schedule 6 (capital to be disregarded)—
\begin{enumerate}\item[]
($a$) in paragraph~16 for~“paragraph~11 of Schedule 4”, substitute “paragraph~13 of Schedule 4”;

($b$) in paragraph~40(1)($a$)  for~“or~12” substitute “or~11” and~after “Regulations”, insert “2003”;

($c$) in paragraph~40(1)($b$)  for~“3, 5 or~8” substitute “5, 6 or~10” and~for~“National Health Service (Travelling Expenses and~Remission of Charges) Regulations 1988” substitute “National Health Service (Travelling Expenses and~Remission of Charges) (Wales) Regulations 2007”;\looseness=-1

($d$) in paragraph~40(1)($c$)  for~“or~8” substitute “or~11”, and~after “(Scotland)” insert “(No.~2)”;

($e$) in paragraph~41 omit “8,”;

($f$) in paragraph~43 after “Disabled Persons (Employment) Act 1944” omit “or”; and

($g$) in paragraph~55(1)($b$)  for~“time”, substitute “date”.
\end{enumerate}

\subsection[4. Amendments to the Housing Benefit (State Pension Credit) Regulations]{\sloppy Amendments to the Housing Benefit (State Pension Credit) Regulations}

4.---(1)  The Housing Benefit (State Pension Credit) Regulations shall be amended as follows.

(2) In regulation~2 (interpretation)—
\begin{enumerate}\item[]
($a$) in the definition of “concessionary payment”, for~“or~the Social Security Act 1975” substitute “are charged”.

($b$) omit the definition of “the former regulations”;

($c$) for~the definition of “sandwich course”, substitute—
\begin{quotation}
““sandwich course” has the meaning prescribed in regulation~2(9) of the Education (Student Support) Regulations 2008, regulation~4(2) of the Education (Student Loans) (Scotland) Regulations 2007 or~regulation~2(8) of the Education (Student Support) Regulations (Northern Ireland) 2007, as the case may be;”.
\end{quotation}
\end{enumerate}

(3) In regulation~7(8)($c$)(ii)  (circumstances in which a person is or~is not to be treated as occupying a dwelling as his home) for~“Part III”, substitute “Part VIII”.

(4) In regulation~22(5)\footnote{A relevant amending instrument is S.I.~2005/2502 (as amended by S.I.~2006/217).} (applicable amounts) for~“Schedule 2A”, substitute “Schedule 3”.

(5) In regulation~31(11)($f$)  (treatment of child care charges), for~“sub-paragraph~($c$)  or~($d$)”, substitute “sub-paragraph~($d$)  or~($e$)”.

(6) In regulation~67(4)($a$)(ii)  (evidence and~information) for~“London Bombings Charitable Relief Fund”, substitute “London Bombings Relief Charitable Fund”.

(7) In regulation~83(4) (method of recovery) for~“paragraphs 3 to 8”, substitute “paragraphs 2 to 5 and~7”.

(8) In Schedule 5 (amounts to be disregarded in the calculation of income other than earnings)—
\begin{enumerate}\item[]
($a$) for~paragraph~1($b$), substitute “a war widow’s pension or~any corresponding pension payable to a widower or~surviving civil partner;”;

($b$) in paragraph~12(4) for~“ordinary clothing and~footwear”, substitute “ordinary clothing or~footwear”.
\end{enumerate}

(9) In paragraph~22(2)($c$)  of Schedule 6 (capital to be disregarded generally) for~“Schedule 5”, substitute “Schedule 6”.

(10) In paragraph~9(1)($e$)  of Schedule 8 (matters to be included in decision notice) for~“rate rebate”, substitute “rent rebate”.

\subsection[5. Amendments to the Council Tax Benefit Regulations]{Amendments to the Council Tax Benefit Regulations}

5.---(1)  The Council Tax Benefit Regulations shall be amended as follows.

(2) In regulation~2(1) (interpretation) omit the definition of “person on state pension credit”.

(3) In regulation~18 (treatment of child care charges)—
\begin{enumerate}\item[]
($a$) for~paragraph~(11)($a$)  substitute “the claimant’s applicable amount includes a disability premium on account of the other member’s incapacity”;\looseness=-1

($b$) in paragraph~(11)($b$), omit “or~a higher pensioner premium”; and

($c$) in paragraph~(11)($g$), for~“Department of Health and~Social Services for~Northern Ireland”, substitute “Department of Health, Social Services and~Public Safety in Northern Ireland”.
\end{enumerate}

(4) In regulation~32\footnote{A relevant amending instrument is S.I.~2007/1749.} (notional income), omit paragraphs (3) to (5).

(5) In regulation~43 (students---interpretation)—
\begin{enumerate}\item[]
($a$) for~the definition of “sandwich course” substitute—
\begin{quotation}
““sandwich course” has the meaning prescribed in regulation~2(9) of the Education (Student Support) Regulations 2008, regulation~4(2) of the Education (Student Loans) (Scotland) Regulations 2007\footnote{S.S.I.~2007/154.} or~regulation~2(8) of the Education (Student Support) Regulations (Northern Ireland) 2007\footnote{S.R.~(NI) 2007 No.~195.}, as the case may be;”; and\looseness=-1
\end{quotation}

($b$) in the definition of “student loan” for~“Students’ Allowances (Scotland) Regulations 1999”, substitute “Students’ Allowances (Scotland) Regulations 2007\footnote{S.S.I.~2007/153.}”.
\end{enumerate}

(6) In regulation~50(2) (other amounts to be disregarded) for~“Students’ Allowance (Scotland) Regulations 1999”, substitute “Students’ Allowances (Scotland) Regulations 2007”.

(7) In regulation~70 (date of claim where claim sent or~delivered to a gateway office) in sub-paragraph~(1)($a$)(ii)  and~sub-paragraph~(1)($c$)(iii)  for~“4 weeks”, substitute “one month”.

(8) In regulation~71(1) (date of claim where claim sent or~delivered to an office of a designated authority) for~“4 weeks”, substitute “one month”.

(9) In regulation~72(1) (evidence and~information) for~“4 weeks”, substitute “one month”.

(10) In Schedule 1\footnote{Relevant amending instruments are S.I.~2006/378, 2007/688, 2007/2618 and~S.I.~2008/632.} (applicable amounts)—
\begin{enumerate}\item[]
($a$) in paragraph~3(4)($e$), omit “9, 10, 11 or”;

($b$) for~paragraph~6, substitute—
\begin{quotation}
“6.  The following premiums, namely—
\begin{enumerate}\item[]
($a$) a severe disability premium to which paragraph~14 applies;

($b$) an enhanced disability premium to which paragraph~15 applies;

($c$) a disabled child premium to which paragraph~16 applies; and

($d$) a carer premium to which paragraph~17 applies,
\end{enumerate}
may be applicable in addition to any other premium which may apply under this     Schedule.”;
\end{quotation}

($c$) omit paragraphs 9, 10 and~11;

($d$) in paragraph~13 omit from the heading “Higher Pensioner and~Disability Premiums” and~substitute “Disability Premium”;

($e$) in paragraph~13(3), omit “the higher pensioner premium or”;

($f$) omit paragraph~13(4);

($g$) in paragraph~13(9) for~“within the meaning of paragraph~11(5)”, substitute “(a person to whom regulation~13A(1) of the Social Security (Incapacity for~Work) (General) Regulations 1995 applies, and~who again becomes incapable of work for~the purposes of Part XIIA of the Act)”; and

($h$) in paragraph~20—
\begin{enumerate}\item[]
(i) omit sub-paragraphs (2), (3) and~(4); and

(ii) in sub-paragraph~(5)($a$), omit “or~($b$)”.
\end{enumerate}
\end{enumerate}

(11) In Schedule 3 (sums to be disregarded in the calculation of earnings)—
\begin{enumerate}\item[]
($a$) for~paragraph~3(3)($a$)  substitute “the claimant is a member of a couple and~his applicable amount includes an amount by way of the disability premium under Schedule 1; and”;

($b$) omit paragraph~3(4) and~(5);

($c$) in paragraph~9 for~“one of more employments”, substitute “one or~more employments”;

($d$) in paragraph~16(2)($b$)(iv)($aa$)  omit “a higher pensioner premium or”, “11 or” and~“respectively”;

($e$) in paragraph~16(2)($b$)(iv)($bb$)  omit “higher pensioner premium or”.
\end{enumerate}

(12) In Schedule 4 (sums to be disregarded in the calculation of income other than earnings)—
\begin{enumerate}\item[]
($a$) for~paragraph~16($b$), substitute “a war widow’s pension or~any corresponding pension payable to a widower or~surviving civil partner;”;

($b$) in paragraph~45—
\begin{enumerate}\item[]
(i) for~sub-paragraph~(1)($a$), substitute—
\begin{quotation}
“($a$) as respects England, under regulation~5, 6 or~11 of the National Health Service (Travel Expenses and~Remission of Charges) Regulations 2003 (travelling expenses and~health service supplies);”;
\end{quotation}

(ii) for~sub-paragraph~(1)($b$), substitute—
\begin{quotation}
“($b$) as respects Wales, under regulation~5, 6 or~10 of the National Health Service (Travelling Expenses and~Remission of Charges) (Wales) Regulations 2007 (travelling expenses and~health service supplies);”; and
\end{quotation}

(iii) after sub-paragraph~(1)($b$), insert—
\begin{quotation}
“($c$) as respects Scotland, under regulation~3, 5 or~11 of the National Health Service (Travelling Expenses and~Remission of Charges) (Scotland) (No.~2) Regulations 2003 (travelling expenses and~health service supplies);”;
\end{quotation}
\end{enumerate}

($c$) in paragraph~46 omit “8,”;

($d$) for~paragraph~48, substitute—
\begin{quotation}
“48.---(1)  Where a claimant’s applicable amount includes an amount by way of family premium, £15 of any payment of maintenance, other than child maintenance, whether under a court order or~not, which is made or~due to be made by the claimant’s former partner, or~the claimant’s partner’s former partner.

(2) For~the purpose of sub-paragraph~(1) where more than one maintenance payment falls to be taken into account in any week, all such payments shall be aggregated and~treated as if they were a single payment.

(3) A payment made by the Secretary of State in lieu of maintenance shall, for~the purpose of sub-paragraph~(1), be treated as a payment of maintenance made by a person specified in sub-paragraph~(1).

\medskip

48A.---(1)  Any payment of child maintenance which is made by the parent of the child except where the person making the payment is the claimant or~the claimant’s partner.

(2) In this paragraph, “child maintenance” means any payment towards the maintenance of a child or~young person, including any payment made voluntarily and~payments made through or~under—
\begin{enumerate}\item[]
($a$) the Child Support Act 1991;

($b$) the Child Support (Northern Ireland) Order 1991;

($c$) a court order (including a consent order);

($d$) a minute of agreement as registered for~execution in the Books of Council Session or~the sheriff court books,
\end{enumerate}
and~for~this purpose a “young person” is a person referred to in regulation~9 (persons of a prescribed description for~the definition of family in section 137(1) of the Act).

(3) For~the purpose of sub-paragraph~(1) where more than one maintenance payment falls to be taken into account in any week, all such payments shall be aggregated and~treated as if they were a single payment.

(4) A payment made by the Secretary of State in lieu of maintenance shall, for~the purpose of sub-paragraph~(1), be treated as a payment of maintenance made by a person specified in sub-paragraph~(1).”; and
\end{quotation}

($e$) omit paragraph~64.
\end{enumerate}

(13) In Schedule 5 (capital to be disregarded)—
\begin{enumerate}\item[]
($a$) in paragraph~40(1)($a$)  for~“or~12” substitute “or~11” and~after “Regulations”, insert “2003”;

($b$) in paragraph~40(1)($b$)  for~“3, 5 or~8” substitute “5, 6 or~10” and~for~“National Health Service (Travelling Expenses and~Remission of Charges) Regulations 1988” substitute “National Health Service (Travelling Expenses and~Remission of Charges) (Wales) Regulations 2007”;

($c$) in paragraph~40(1)($c$)  for~“or~8” substitute “or~11”, and~after “(Scotland)” insert “(No.~2)”;

($d$) in paragraph~41 omit “8,”;

($e$) in paragraph~43 after “Disabled Persons (Employment) Act 1944” omit “or”; and

($f$) in paragraph~57(1)($b$)  for~“time”, substitute “date”.
\end{enumerate}

\subsection[6. Amendments to the Council Tax Benefit (State Pension Credit) Regulations]{Amendments to the Council Tax Benefit (State Pension Credit) Regulations}

6.---(1)  The Council Tax Benefit (State Pension Credit) Regulations shall be amended as follows.

(2) In regulation~2 (interpretation) for~the definition of “sandwich course”, substitute—
\begin{quotation}
““sandwich course” has the meaning prescribed in regulation~2(9) of the Education (Student Support) Regulations 2008, regulation~4(2) of the Education (Student Loans)(Scotland) Regulations 2007 or~regulation~2(8) of the Education (Student Support) Regulations (Northern Ireland) 2007, as the case may be;”.
\end{quotation}

(3) In regulation~21(11)($f$)  (treatment of child care charges) for~“sub-paragraph~($c$)  or~($d$)”, substitute “sub-paragraph~($d$)  or~($e$)”.

(4) After regulation~53(12)\footnote{Regulation 53(12) was substituted by S.I.~2007/1331.} (time and~manner in which claims are to be made) insert—
\begin{quotation}
“(12A) Paragraph (12) applies in the case of a person who has attained, or~whose partner has attained, the age of 59 years and~35 weeks.”.
\end{quotation}

(5) In Schedule 3 (amounts to be disregarded in the calculation of income other than earnings)—
\begin{enumerate}\item[]
($a$) for~paragraph~1($b$), substitute “a war widow’s pension or~any corresponding pension payable to a widower or~surviving civil partner;”;

($b$) in paragraph~12(2)($a$)  and~(4) for~“ordinary clothing and~footwear”, substitute “ordinary clothing or~footwear”; and

($c$) after paragraph~24, insert—
\begin{quotation}
“25.  Where the claimant, or~the person who was the partner of the claimant on 31st March 2003, was entitled on that date to income support or~an income-based jobseeker’s allowance but ceased to be so entitled on or~before 5th April 2003 by virtue only of regulation~13 of the Housing Benefit (General) Amendment (No.~3) Regulations 1999 as in force at that date, the whole of his income.”.
\end{quotation}
\end{enumerate}

(6) After paragraph~26 of Schedule 4 (capital to be disregarded), insert—
\begin{quotation}
“26A.---(1)  Subject to sub-paragraph~(2), where a claimant satisfies the conditions in section 131(3) and~(6) of the Act (entitlement to alternative maximum council tax benefit), the whole of his capital.

(2) Sub-paragraph~(1) does not apply, where in addition to satisfying the conditions in section 131(3) and~(6) of the Act the claimant also satisfies the conditions in section 131(4) and~(5) of the Act (entitlement to the maximum council tax benefit).”.
\end{quotation}

\subsection[7. Amendments to the Housing Benefit and~Council Tax Benefit (Consequential Provisions) Regulations]{Amendments to the Housing Benefit and~Council Tax Benefit (Consequential Provisions) Regulations}

7.---(1)  The Housing Benefit and~Council Tax Benefit (Consequential Provisions) Regulations shall be amended as follows.

(2) In paragraph~3(1) of Schedule 3 (transitional and~savings provisions) for~“paragraph~13(1)($a$)(ii)  of Schedule 2 to the 1987 Regulations”, substitute “paragraph~12(1)($a$)(ii)  of Schedule 2 to the 1987 Regulations”.

(3) In paragraph~5(2) of Schedule 3\footnote{Paragraph 5 was substituted by S.I.~2007/2870.}(transitional and~savings provisions), in the paragraph~inserted as paragraph~(4)($b$)  of regulation~13 of both of the Housing Benefit Regulations and~the Housing Benefit (State Pension Credit) Regulations, for~that paragraph~(4)($b$)  substitute—
\begin{quotation}
“($b$) is incapable of work for~the purpose of Part XIIA of the Act; or”
\end{quotation}

(4) In paragraph~9(3)($a$)(ii)  of Schedule 3 (transitional and~savings provisions---care homes), in the paragraph~inserted as paragraph~(1A)($b$)  of regulation~9 of the Housing Benefit (State Pension Credit) Regulations for~“regulation~83(4)”, substitute “regulation~64(5)”.

(5) In paragraph~3(4) of Schedule 4 (transitory modifications), in the paragraph~inserted as paragraph~37 of Schedule 4 to the Council Tax Benefit Regulations for~“regulation~11A”, substitute “regulation~10A”. 

\pagebreak[3]

\bigskip

Signed 
by authority of the 
Secretary of State for~Work and~Pensions.
%I concur
%By authority of the Lord Chancellor

{\raggedleft
\emph{Mike O'Brien}\\*
%Secretary
Minister
%Parliamentary Under-Secretary 
of State,\\*Department 
for~Work and~Pensions

}

7th April 2008

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations amend the Social Security and~Child Support (Decisions and~Appeals) Regulations 1999, the Housing Benefit Regulations 2006, the Housing Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations 2006, the Council Tax Benefit Regulations 2006, the Council Tax Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations 2006 and~the Housing Benefit and~Council Tax Benefit (Consequential Provisions) Regulations 2006.

Regulation 2 amends the Social Security and~Child Support (Decisions and~Appeals) Regulations 1999 so as to correct the structure of regulation~7(2) of those Regulations.

Regulation 3 amends the Housing Benefit Regulations 2006. In particular---
\begin{itemize}
\item
    It omits references to the pensioner and~higher pension premiums, as those who in the past have been in receipt of these premiums will now have their housing benefit calculated under the Housing Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations 2006. It also makes consequential amendments (paragraphs (3)($b$), (4)($a$)  and~($b$), (7)($a$), (10)($b$), ($d$)  to ($f$), (11)($a$), ($b$), ($d$)  and~($e$)).

\item
    Similarly paragraphs (5) and~(12)($b$)  omit provisions relating to income derived from pension schemes or~an annuity as those covered by these provisions will have their housing benefit calculated under the Housing Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations 2006.

\item
    Paragraph (2)($a$)  corrects the definition of concessionary payment and~paragraph~(2)($b$)  omits an obsolete definition.

\item
    Paragraphs (6)($b$)  and~($c$), (7)($b$)  to ($d$)  and~(8) update references to various Student Support and~Student Allowance regulations.

\item
    Paragraphs (12)($g$)  and~(13)($e$)  omit a redundant reference to the Welfare Food Regulations 1996.

\item
    Paragraph (12)($h$)  makes amendments with the effect that the child maintenance disregard is to be increased from £15 per week to the full amount.

\item
    Paragraphs (3)($a$), (6)($a$), (7)($e$), (9), (10)($a$), (11)($c$)  and~($f$), (12)($c$), ($d$)  and~($f$)  and~(13)($a$), ($b$), ($d$), ($f$)  and~($g$)  correct errors which were made in the consolidation of the Housing Benefit Regulations, mainly of a typographical nature. 
\end{itemize}

Regulation 4 amends the Housing Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations 2006. In particular---
\begin{itemize}
\item
    Paragraph (2)($b$)  omits an obsolete definition and~paragraph~(2)($c$)  updates the references to Student Support Regulations in the definition of sandwich course.

\item
    Paragraph (7) amends the list of disregards which enable a higher rate of recovery. This amendment restores the policy intention in place before the regulations for~those over the qualifying age for~state pension credit were separated from those of working age.

\item
    The remainder of regulation~4 corrects errors of a typographical nature that were made in the consolidation of the Housing Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations 2006. 
\end{itemize}

Regulation 5 amends the Council Tax Benefit Regulations 2006. In particular---
\begin{itemize}
\item
    Paragraph (8)($b$)  omits the pensioner and~higher pension premiums as those who in the past have been in receipt of these premiums will now have their housing benefit calculated under the Council Tax Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations 2006 and~paragraphs (2), (8)($a$), ($c$)  to ($e$)  and~(9) make consequential amendments.

\item
    Paragraph (3) and~(10)($d$)  omit provisions relating to income derived from pension schemes or~an annuity as those covered by these provisions will have their housing benefit calculated under the Council Tax Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations 2006.

\item
    Paragraph (4) updates references to the Student Support and~Student Allowance regulations.

\item
    Paragraph (5), (6) and~(7) substitute references to “4 weeks” in regulation~70, 71 and~72, which aligns these regulations with the equivalent regulations in the Housing Benefit Regulations.

\item
    Paragraph (10)($b$)  and~(11)($a$)  omit a redundant reference to the Welfare Food Regulations.

\item
    Paragraph (10)($c$)  makes an equivalent amendment to the child maintenance disregard as regulation~3(12)($f$)  above. 
\end{itemize}

Regulation 6 amends the Council Tax Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations 2006. In particular---

\begin{itemize}
\item
    Paragraph (2) updates the references to Student Support Regulations in the definition of sandwich course.

\item
    Paragraph (4) clarifies that a person who has attained the age of 59 years and~35 weeks and~who makes a claim for~the period following his 60th birthday will be assessed under the Council Tax Benefit (Persons who have attained the qualifying age for~state pension credit) Regulations.

\item
    Paragraph (5)($c$)  ensures that those who ceased to be entitled to Income Support or~Jobseeker’s Allowance as a result of the supporting people’s provisions will still be entitled to full Council Tax Benefit.

\item
    Paragraph (6) clarifies the rules regarding capital when determining alternative maximum Council Tax Benefit. 
\end{itemize}

Regulation 7 amends the Housing Benefit and~Council Tax Benefit (Consequential Provisions) Regulations 2006 so as to correct errors of a typographical nature that were made in the consolidation of the Housing Benefit Regulations 2006 and~Council Tax Benefit Regulations 2006.

An impact assessment has not been produced for~this instrument as it has no impact on the private or~voluntary sectors. 

\end{document}