\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support (Miscellaneous Amendments) Regulations 2011}

\newcommand\regsnumber{2011/1464}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and~Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2011 No.\ 1464}

\date{Made
9th June 2011\\
Laid before Parliament
13th June 2011\\
Coming into~force
4th July 2011
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.61603pt}

%\hbadness=10000

\begin{document}

\maketitle

\noindent
The Secretary of State for Work and Pensions, in exercise of the powers conferred by sections 16(1), 17(3) and (5), 51(1), 52(4), 54, of, and paragraph~11(1) of Schedule 1 to, the Child Support Act 1991\footnote{1991 c.~48. Section 16 was substituted by section 40 of the Social Security Act 1998 (c.~14) (“the 1998 Act”) and further substituted by section 8 of the Child Support, Pensions and Social Security Act 2000 (c.~19) (“the 2000 Act”) in relation to cases other than 1993 scheme cases (a “1993 scheme case” means a case in respect of which the provisions of the 2000 Act have not been brought into force in accordance with article 3 of the Child Support, Pensions and Social Security Act 2000 (Commencement No.~12) Order 2003 (C.~11)). Section 17(3) was substituted by section 41 of the 1998 Act and further substituted by section 9 of the 2000 Act in relation to cases other than 1993 scheme cases. Section 54 is cited for the meaning given to the word “prescribed”.}, makes the following Regulations: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation, commencement and interpretation]{Citation, commencement and interpretation}

1.---(1)  These Regulations may be cited as the Child Support (Miscellaneous Amendments) Regulations 2011 and will come into force on 4th July 2011.

(2) In these Regulations—
\begin{enumerate}\item[]
“the Decisions and Appeals Regulations” means the Social Security and Child Support (Decisions and Appeals) Regulations 1999\footnote{S.I.~1999/991. References to the Secretary of State in these Regulations are treated as references to the Commission by virtue of paragraph~55(3) of Schedule 3 to the Child Maintenance and Other Payments Act 2008 (c.~6) (“the 2008 Act”), as the functions of the Secretary of State were transferred to the Commission by section 13 of that Act.}; and

“the Maintenance Assessment Procedure Regulations” means the Child Support (Maintenance Assessment Procedure) Regulations 1992\footnote{S.I.~1992/1813. References to the Secretary of State in these Regulations are treated as references to the Commission by virtue of paragraph~55(3) of Schedule 3 to the 2008 Act, as the functions of the Secretary of State were transferred to the Commission by section 13 of that Act.}.
\end{enumerate}

\subsection[2. Amendment of the Decisions and Appeals Regulations]{Amendment of the Decisions and Appeals Regulations}

2.---(1)  The Decisions and Appeals Regulations are amended as follows.

(2) In regulation 1(3) (interpretation), after the definition of “referral” insert—
\begin{quotation}
““relevant other child” is to be interpreted by reference to paragraph~10C(2) of Schedule 1 to the Child Support Act;”.
\end{quotation}

(3) In regulation 6B(4) (circumstances in which a child support decision may not be superseded)\footnote{Regulation 6B was inserted by S.I.~2000/3185.}—
\begin{enumerate}\item[]
($a$) omit “or” at the end of sub-paragraph~($d$)\footnote{Sub-paragraph~($d$)  was omitted by S.I.~2009/396.}; and

($b$) after sub-paragraph~($e$), add—
\begin{quotation}
“; or

($f$) a decision is superseded and in relation to that superseding decision a maintenance calculation is made to which paragraph~15 of Schedule 1 to the Child Support Act applies.”.
\end{quotation}
\end{enumerate}

(4) In Schedule 3D (effective dates for supersession of child support decisions)\footnote{Schedule 3D was inserted by S.I.~2009/396.}—
\begin{enumerate}\item[]
($a$) in paragraph~3 (decision backdated to when the change occurred)—
\begin{enumerate}\item[]
(i) after sub-paragraph~($a$), insert—
\begin{quotation}
“($aa$) a relevant other child dies or ceases to be a relevant other child;”,
\end{quotation}

(ii) omit “or” at the end of sub-paragraph~($c$), and

(iii) after sub-paragraph~($d$), add—
\begin{quotation}
“; or

($e$) the non-resident parent begins or ceases to receive a benefit mentioned in regulation 4(1) of the Maintenance Calculations and Special Cases Regulations (flat rate) or begins or ceases to be a person who receives, or whose partner receives, a benefit referred to in regulation 4(2) of those Regulations.”;
\end{quotation}
\end{enumerate}

($b$) after paragraph~3, insert—
\begin{quotation}
“3A.  In paragraph~3, the reference to the day on which a person begins or ceases to receive a benefit is to the day on which entitlement to the benefit commences or ends, as the case may be.”;
\end{quotation}

($c$) omit paragraph~4; and

($d$) in paragraph~8 (series of changes waiting to be actioned), for “the date of that application” substitute “the beginning of the maintenance period in which that application was made”.
\end{enumerate}

\subsection[3. Amendment of the Maintenance Assessment Procedure Regulations]{Amendment of the Maintenance Assessment Procedure Regulations}

3.---(1)  The Maintenance Assessment Procedure Regulations are amended as follows.

(2) For regulation 17(6) (revision of decisions)\footnote{Regulation 17 was substituted by S.I.~1999/1047 and revoked with savings by 2001/157 (as amended by S.I.~2003/328 and 347 and 2004/2415). The relevant amending instruments are S.I.~2000/1596, 2003/328 and 347, 2004/2415 and 2008/2543.}, substitute—
\begin{quotation}
“(6) Paragraph (1) shall not apply in respect of a material change of circumstances which—
\begin{enumerate}\item[]
($a$) occurred since the date on which the decision was made; or

($b$) is expected, according to information or evidence which the Commission has, to occur.”.
\end{enumerate}
\end{quotation}

(3) In regulation 21(5) (circumstances in which a decision may not be superseded)\footnote{Regulation 21 was substituted by S.I.~1999/1047 and revoked with savings by 2001/157 (as amended by S.I.~2003/328 and 347 and 2004/2415).}—
\begin{enumerate}\item[]
($a$) omit “or” at the end of sub-paragraph~($b$); and

($b$) after sub-paragraph~($c$)  add—
\begin{quotation}
“; or

($d$) a decision is superseded and in relation to that superseding decision a maintenance assessment is made to which paragraph~15 of Schedule 1 to the Act applies.”.
\end{quotation}
\end{enumerate}

(4) In regulation 23 (date from which a decision is superseded)\footnote{Regulation 23 was substituted by S.I.~1999/1047 and revoked with savings by 2001/157 (as amended by S.I.~2003/328 and 347 and 2004/2415). The relevant amending instruments are S.I.~2000/1596, 2003/1050, 2005/785, 2008/2543 and 2683 and 2009/2909.}—
\begin{enumerate}\item[]
($a$) for paragraph~(2), substitute—
\begin{quotation}
“(2) Where a superseding decision is made in a case to which regulation 20(2)($a$)  applies and—
\begin{enumerate}\item[]
($a$) the absent parent begins or ceases to receive a benefit mentioned in Schedule 4 to the Maintenance Assessments and Special Cases Regulations (case where child support maintenance is not to be payable); or

($b$) the absent parent or person with care begins or ceases to be a person who receives a benefit referred to in paragraph~5(4) of Schedule 1 to the Act (assessable income),
\end{enumerate}
the decision takes effect from the first day of the maintenance period in which the change occurred.”;
\end{quotation}

($b$) for paragraph~(19), substitute—
\begin{quotation}
“(19) Where a superseding decision is made in a case to which regulation 20(2)($a$)  or (3) applies and the material circumstance is—
\begin{enumerate}\item[]
($a$) a qualifying child dies or ceases to be a qualifying child; or

($b$) a relevant child dies or ceases to be a relevant child,
\end{enumerate}
the decision shall take effect as from the first day of the maintenance period in which the change occurred.”;
\end{quotation}

($c$) after paragraph~(21A), insert—
\begin{quotation}
“(21B) Where—
\begin{enumerate}\item[]
($a$) a superseding decision is made in a case to which regulation 20(3) applies; and

($b$) in relation to that decision, a maintenance assessment is made to which paragraph~15 of Schedule 1 to the Act applies,
\end{enumerate}
the effective date of the assessment or assessments is the first day of the maintenance period in which the change of circumstances to which the assessment relates occurred or is expected to occur and where it occurred before the date of the application for the supersession and was notified after that date, the first day of the maintenance period in which that application was made.”; and
\end{quotation}

($d$) after paragraph~(22), add—
\begin{quotation}
“(23) The reference in paragraph~(2) to when an absent parent begins or ceases to receive a benefit is to the day on which entitlement to the benefit commences or ends, as the case may be.

(24) In paragraph~(19), “relevant child” has the same meaning as in regulation 1(2) of the Maintenance Assessments and Special Cases Regulations.”.
\end{quotation}
\end{enumerate}

\subsection[4. Amendment of the Child Support (Maintenance Calculation Procedure) Regulations 2000]{Amendment of the Child Support (Maintenance Calculation Procedure) Regulations 2000}

4.  In regulation 26 of the Child Support (Maintenance Calculation Procedure) Regulations 2000\footnote{S.I.~2001/157. Relevant amending instruments are S.I.~2002/1204 and 2008/2544. References to the Secretary of State in these Regulations are treated as references to the Commission by virtue of paragraph~55(3) of Schedule 3 to the 2008 Act, as the functions of the Secretary of State were transferred to the Commission by section 13 of that Act.} (effective dates of maintenance calculations—maintenance order and application under section 4 or 7), in sub-paragraph~($c$)  of paragraph~(1) after “maintenance order” insert “or, in Scotland, a maintenance agreement registered for execution in the Books of Council and Session or the sheriff court books,”. 

\bigskip

\pagebreak[3]

Signed 
by authority of the 
Secretary of State for~Work and~Pensions.
%I concur
%By authority of the Lord Chancellor

{\raggedleft
\emph{Maria Miller}\\*
%Secretary
%Minister
Parliamentary Under-Secretary 
of State\\*Department 
for~Work and~Pensions

}

9th June 2011

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations are made under powers in the Child Support Act 1991 (c.~48) (“the 1991 Act”) and come into force on 4th July 2011. They amend the Social Security and Child Support (Decisions and Appeals) Regulation 1999 (“the Decisions and Appeals Regulations”), the Child Support (Maintenance Assessment Procedure) Regulations 1992 (“Maintenance Assessment Procedure Regulations”) and the Child Support (Maintenance Calculation Procedure) Regulations 2000 (“the Maintenance Calculation Procedure Regulations”).

Regulation 2 amends the Decisions and Appeals Regulations. This regulation inserts a new definition into regulation 1(3) of those Regulations, provides that regulation 6B of those Regulations does not apply where a decision is made to which paragraph~15 of Schedule 1 to the 1991 Act applies, prescribes two new categories of case to which the effective date in paragraph~3 of Schedule 3D to those Regulations applies (one for relevant other children and the other for non-resident parent or partner on or off benefit), inserts a new paragraph~3A in Schedule 3D which supplements the new on or off benefit category of case in paragraph~3, consequentially omits paragraph~4 and makes a minor amendment to paragraph~8 of that Schedule.

Regulation 3 amends the Maintenance Assessment Procedure Regulations. This regulation substitutes regulation 17(6) of those Regulations to limit the disapplication of paragraph~(1) to a material change of circumstances. Regulation 21 of those Regulations is amended in the same manner as regulation 6B of the Decisions and Appeals Regulations. Regulation 23 is amended to substitute a new effective date for paragraph~(2) (absent parent and parent with care on or off benefit), substitute paragraph~(19) of that regulation with an effective date which applies to relevant other children as well as qualifying children, insert a new effective date into that regulation for the purposes of decisions made to which paragraph~15 of Schedule 1 of the Act applies, make provision which supplements the substituted effective date in paragraph~(2) and insert a definition for the purposes of new paragraph~(19) of regulation 23.

Regulation 4 amends the Maintenance Calculation Procedure Regulations. Regulation 26 (effective dates of maintenance calculations–maintenance order and application under section 4 or 7) of those Regulations is amended to include maintenance agreements registered for execution in the Books of Council and Session or the sheriff court books within the scope of the effective date provided for by that regulation.

A full impact assessment has not been published for this instrument as it has no impact on the private sector and civil society organisations. 

\end{document}