\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support (Variations) (Modification of Statutory Provisions) Regulations 2000}

\newcommand\regsnumber{2000/3173}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I. 2000 No. 3173}

\date{Made 29th November 2000\\Laid before Parliament 6th December 2000\\Coming into force 31st January 2001}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.57402pt}

\begin{document}

\maketitle

\noindent
The Secretary of State for Social Security, in exercise of the power conferred upon him by section 28G(2) of the Child Support Act 1991\footnote{\frenchspacing 1991 c. 48. Section 28G is substituted by section 7 of the Child Support, Pensions and Social Security Act 2000 c. 19.}, and of all other powers enabling him in that behalf, hereby makes the following Regulations: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation, commencement and interpretation]{Citation, commencement and interpretation}

1.---(1)  These Regulations may be cited as the Child Support (Variations) (Modification of Statutory Provisions) Regulations 2000 and shall come into force on 31st January 2001.

(2) In these Regulations references to “the Act” are to the Child Support Act 1991 and references to sections are to sections of, and to Schedules are to Schedules to, the Act.

\subsection[2. Modification of sections 28A to 28F and Schedules 4A and 4B]{Modification of sections 28A to 28F and Schedules 4A and 4B}

2.  Where an application for a variation is made under section 28G, sections 28A to 28F, and Schedules 4A and 4B, shall apply subject to the modifications provided for in these Regulations\footnote{\frenchspacing Sections 28A, 28B, 28C and 28F and Schedules 4A and 4B are substituted by section 5 of, and Schedule 2 to, the Child Support, Pensions and Social Security Act 2000. Sections 28D and 28E were inserted by the Child Support Act 1995 c. 34 and is amended by section 5 of the Child Support, Pensions and Social Security Act 2000.}.

\subsection[3. Modification of section 28A]{Modification of section 28A}

3.---(1)  Section 28A (application for variation of usual rules for calculating maintenance) shall be modified by the substitution in subsection (1)—
\begin{enumerate}\item[]
($a$) for the words “Where an application for a maintenance calculation is made under section 4 or 7, or treated as made under section 6” by the words “Where a maintenance calculation other than an interim maintenance decision is in force”; and

($b$) for the words “(in the case of an application under” by the words “(where the maintenance calculation was made following an application under”.
\end{enumerate}

(2) Subsection (3) shall be omitted.

\subsection[4. Modification of section 28B]{Modification of section 28B}

4.  Section 28B (preliminary consideration of applications) shall be modified—
\begin{enumerate}\item[]
($a$) by the substitution in subsection (2) for the words “(and proceed to make his decision on the application for a maintenance calculation without any variation)” by the words “(and proceed to revise or supersede a decision under section 16 or 17 respectively without taking the variation into account, or not revise or supersede a decision under section 16 or 17)”; and

($b$) by the omission of paragraph ($b$)  of subsection (2).
\end{enumerate}

\subsection[5. Modification of section 28C]{Modification of section 28C}

5.---(1)  Section 28C (imposition of regular payments condition) shall be modified in accordance with the following paragraphs of this regulation and references to subsections are to subsections of that section.

(2) Subsection (1)($b$)  shall be omitted and in the full-out words “also” shall be omitted.

(3) In subsection (2), for the words “interim maintenance decision” there shall be substituted the words “maintenance calculation in force”.

(4) In subsections (3)($c$)  and (7)($c$), for the words “application for the maintenance calculation was” there shall be substituted the words “maintenance calculation in force was made in response to an application”.

(5) For subsection (4)($a$)  there shall be substituted the following—
\begin{quotation}
“($a$) when in response to the application for a variation the Secretary of State has revised or superseded a decision under section 16 or 17 respectively (whether he agrees to a variation or not) or not revised or superseded a decision under section 16 or 17;”.
\end{quotation}

(6) In subsection (5), for the words from “reach” to the end there shall be substituted “revise or supersede a decision under section 16 or 17 respectively, or not revise or supersede a decision under section 16 or 17, as if the application had failed”.

\subsection[6. Modification of sections 28D and 28E]{Modification of sections 28D and 28E}

6.---(1)  Section 28D (determination of applications) shall be modified by the substitution, in paragraph ($a$)  of subsection (1), for the words “under section 11 or 12(1)” by the words “under section 16 or 17”.

(2) Section 28E (matters to be taken into account) shall be modified by the substitution for paragraph ($b$)  of subsection (3) of the following—
\begin{quotation}
“($b$) where the maintenance calculation in force was made in response to an application under section 7, by either of them or the child concerned.”.
\end{quotation}

\subsection[7. Modification of section 28F]{Modification of section 28F}

7.  Section 28F (agreement to a variation) shall be modified—
\begin{enumerate}\item[]
($a$) by the substitution for subsection (3) of the following—
\begin{quotation}
“(3) The Secretary of State shall not agree to a variation (and shall proceed to revise or supersede a decision under section 16 or 17 respectively without taking the variation into account, or not revise or supersede a decision under section 16 or 17) if he is satisfied that prescribed circumstances apply.”;
\end{quotation}

($b$) by the omission in paragraph ($a$)  of subsection (4) of the words after the word “application,” where it first appears;

($c$) by the substitution for subsection (4)($b$)  of the following—
\begin{quotation}
“($b$) revise or supersede a decision under section 16 or 17 respectively on that basis.”; and
\end{quotation}

($d$) by the omission of subsection (5).
\end{enumerate}

\subsection[8. Modification of Schedules 4A and 4B]{Modification of Schedules 4A and 4B}

8.---(1)  In paragraph 5(1) of Schedule 4A, the words 
%“the application for a” 
“application for a”  % Words substituted (30.4.02) by SI 2002/1204 reg 10
shall be omitted.

(2) In paragraphs 2(3)($a$), ($d$)  and ($e$)  of Schedule 4B, for the words “the application for a maintenance calculation has been made (or treated as made)” there shall be substituted the words “there is a maintenance calculation in force”.

(3) In paragraph 2(3)($c$)  of Schedule 4B, for the words “has been applied for (or treated as having been applied for)” there shall be substituted “is in force”.

(4) In paragraph 3(1)($a$)  of Schedule 4B, for the words “the application for the maintenance calculation” there shall be substituted “the maintenance calculation in force” and for the words “that application was made” there shall be substituted “that maintenance calculation is in force”.

(5) In paragraph 3(3) of Schedule 4B, for the words “the application for a maintenance calculation” there shall be substituted the words “the maintenance calculation in force”. 

\amendment{
Words substituted in reg. 8(1) (30.4.02) by the Child Support (Miscellaneous Amendments) Regulations 2002 reg. 10.
}

\bigskip

Signed 
by authority of the Secretary of State for Social Security.

{\raggedleft
\emph{P.~Hollis}\\*Parliamentary Under-Secretary of State,\\*Department of Social Security

}

29th November 2000

\small

\part{Explanatory Note}

\renewcommand\parthead{--- Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations are made in connection with applications for variations to the rate of child support maintenance payable under the Child Support Act 1991 (c.\ 48) (“the Act”) consequent upon the introduction of changes to the child support system made by the Child Support, Pensions and Social Security Act 2000 (c.\ 19).

The Regulations contain modifications to sections 28A to 28F of, and Schedules 4A and 4B to, the Act for the purpose of variation applications made under section 28G of the Act, as authorised by section 28G(2) of the Act. Variation applications made under section 28G of the Act are made where there is a maintenance calculation in force.

The impact on business of these Regulations was covered in the Regulatory Impact Assessment (RIA) for the Child Support, Pensions and Social Security Act 2000, in accordance with, and in consequence of which, these Regulations are made. A copy of that RIA has been placed in the libraries of both Houses of Parliament and can be obtained from the Department of Social Security, Regulatory Impact Unit, Adelphi, 1--11 John Adam Street, London \textsc{\lowercase{WC2N 6HT}}.  

\end{document}