\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 9) Order 2001}

\newcommand\regsnumber{2001/2295}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2001 No.\ 2295 (C.\ 76)}

\date{Made
22nd June 2001\\
%Laid before Parliament
%10th May 2001\\
%Coming into force
%31st May 2001
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.57402pt}

\begin{document}

\maketitle

\noindent
The Secretary of State for Work and Pensions, in exercise of the powers conferred by section 86(2) and (3)($a$)  of the Child Support, Pensions and Social Security Act 2000\footnote{2000 c.\ 19.} and of all other powers enabling him in that behalf, hereby makes the following Order: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and interpretation]{Citation and interpretation}

1.---(1)  This Order may be cited as the Child Support, Pensions and Social Security Act 2000 (Commencement No.\ 9) Order 2001.

(2) In this Order, unless the context otherwise requires, any reference to a numbered section or Schedule is a reference to the section or, as the case may be, the Schedule bearing that number in the Child Support, Pensions and Social Security Act 2000.

\subsection[2. Appointed days]{Appointed days}

2.  The day appointed for the coming into force of—
\begin{enumerate}\item[]
($a$) section 55 (prohibition on occupational pension schemes having different rules for overseas residents, etc.), is 23rd July 2001;

%($b$) Part II of Schedule 5 (alternative to anti-franking rules), so far as not already brought into force, and section 56 so far as it relates to that Part, is 6th April 2002;

($c$) section 70 (grants towards cost of discretionary housing payments)—
\begin{enumerate}\item[]
(i) for the purpose of authorising the making of an order under that section, is 26th June 2001, and

(ii) for all other purposes, is 2nd July 2001; and
\end{enumerate}

($d$) section 71 (recovery of housing benefit), so far as not already brought into force, is 1st October 2001.
\end{enumerate}

\amendment{
Art. 2(b) omitted (27.2.02) by the Child Support, Pensions and Social Security Act 2000 (Commencement No. 11) Order 2002 art. 2.
}

\bigskip

Signed 
by authority of the Secretary of State for Work and Pensions.

{\raggedleft
\emph{Malcolm Wicks}\\*Parliamentary Under-Secretary of State,\\*Department of Work and Pensions

}

%Dated
22nd June 2001

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Order)}

This Order brings into force further provisions of the Child Support, Pensions and Social Security Act 2000.

Section 55 (prohibition on occupational pension schemes having different rules for overseas residents, etc.) is brought into force on 23rd July 2001 (article 2($a$)), and Part II of Schedule 5 (which provides for an alternative to the anti-franking rules relating to salary related contracted-out occupational pension schemes) is brought fully into force on 6th April 2002 (article 2($b$)).

Section 70 (grants towards cost of discretionary housing payments) is brought into force on 26th June 2001 (for the purpose of making an order) and on 2nd July 2001 (for all other purposes), and section 71 (recovery of housing benefit) is brought fully into force on 1st October 2001 (article 2($c$)  and ($d$)).

The impact on business of provisions in the Child Support, Pensions and Social Security Act 2000 is detailed in the Regulatory Impact Assessment relating to the Child Support, Pensions and Social Security Bill (which was introduced in the House of Commons on 1st December 1999). A copy of that Assessment has been placed in the libraries of both Houses of Parliament and can be obtained from the Department for Work and Pensions, Regulatory Impact Unit, 3rd Floor, The Adelphi, 1--11 John Adam Street, London \textsc{\lowercase{WC2N 6HT}}. 

\end{document}