\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Maintenance and~Other Payments Act 2008 (Commencement No.~5) Order 2009}

\newcommand\regsnumber{2009/1314}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and~Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2009 No.\ 1314 (C.~72)}

\date{Made
%18th March 2009\\
%Laid before Parliament
%4th March 2009\\
%Coming into~force
28th May 2009
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.61603pt}

%\hbadness=10000

\begin{document}

\maketitle

\noindent
The Secretary of State, in exercise of the power conferred by section 62(3) of the Child Maintenance and~Other Payments Act 2008\footnote{2008 c.~6.}, makes the following Order: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and~interpretation]{Citation and~interpretation}

1.---(1)  This Order may be cited as the Child Maintenance and~Other Payments Act 2008 (Commencement No.~5) Order 2009.

(2) In this Order, except where otherwise stated, any reference to a numbered section or Schedule is a reference to a section of, or Schedule to, the Child Maintenance and~Other Payments Act 2008.

\subsection[2. Appointed days]{Appointed days}

2.---(1)  The following provisions come into force on 1st June 2009 for the purpose of making regulations and~on 3rd August 2009 for all other purposes—
\begin{enumerate}\item[]
($a$) section 22 (orders for regular deductions from accounts);

($b$) section 23 (lump sum deduction orders);

($c$) section 57(1) (minor and~consequential amendments), so far as relating to paragraph 1(22)($a$)  of Schedule 7; and

($d$) paragraph 1(22)($a$)  of Schedule 7 (minor and~consequential amendments).
\end{enumerate}

(2) The following provisions, in so far as not already in force, come into force on 1st June 2009—
\begin{enumerate}\item[]
($a$) sections 57(1) and~58 (repeals), so far as relating to the paragraphs and~entries referred to in sub-paragraphs ($b$)  and~($c$)  below;

($b$) the following paragraphs of Schedule 7—
\begin{enumerate}\item[]
(i) paragraphs 1(7), (9), (10), (26), (32) and~(34), 2(3) to (6) and~4, and

(ii) paragraph 1(25)($a$), except in relation to the definition of “curfew order”; and
\end{enumerate}

($c$) in Schedule 8 (repeals), the entries relating to—
\begin{enumerate}\item[]
(i) the repeal of sections 6 and~36(2) of the Child Support Act 1991\footnote{1991 c.~48. Section 6 ceased to have effect and~was repealed, except in relation to existing cases, on 14th July 2008, see article 2(3) of the Child Maintenance and~Other Payments Act 2008 (Commencement) Order 2008 (S.I.~2008/1476) (C.~67). Section 6 ceased to have effect in relation to all cases on 27th October 2008, \emph{see} article 3($a$)  of the Child Maintenance and~Other Payments Act 2008 (Commencement No.~3 and~Transitional and~Savings Provisions) Order 2008 (S.I.~2008/2548) (C.~110).} and~the repeals in section 7(1) of that Act, and

(ii) the repeal of paragraph 9 of Schedule 3 to the Child Support Act 1995\footnote{1995 c.~34.}.
\end{enumerate}
\end{enumerate}

\bigskip

\pagebreak[3]

Signed 
by authority of the 
Secretary of State for~Work and~Pensions.
%I concur
%By authority of the Lord Chancellor

{\raggedleft
\emph{William D.~McKenzie}\\*
%Secretary
%Minister
Parliamentary Under-Secretary 
of State\\*Department 
for~Work and~Pensions

}

28th May 2009

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

This Order brings into force provisions of the Child Maintenance and~Other Payments Act 2008 (c.~6) (“the 2008 Act”) as follows:

Article 2(1) brings into force various provisions, including sections 22 and~23, on 1st June 2009 for the purpose of making regulations and~on 3rd August 2009 for all other purposes. Those sections insert provisions into the Child Support Act 1991 (c.~48) for the making of regular and~lump sum deduction orders by the Child Maintenance and~Enforcement Commission.

Article 2(2) brings various other provisions of the 2008 Act into force on 1st June 2009. The provisions are in Schedules 7 and~8 of that Act, which contain minor and~consequential amendments and~repeals. 

\end{document}