\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Tax Credits (Decisions and Appeals) (Amendment) Regulations 2000}

\newcommand\regsnumber{2000/127}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I. 2000 No. 127}

\date{Made
21st January 2000\\
Laid before Parliament
24th January 2000\\
Coming into force
14th February 2000
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.57402pt}

\begin{document}

\maketitle

\amendment{
This Statutory Instrument has been made in consequence of a defect in S.I.\ 1999 No.\ 2570 and is being issued free of charge to all known recipients of that Statutory Instrument. 
}

\medskip

\noindent
The Commissioners of Inland Revenue, in exercise of the powers set out in the Schedule to this instrument, and after consultation with the Council on Tribunals in accordance with section 8 of the Tribunals and Inquiries Act 1992\footnote{\frenchspacing 1992 c. 53; the Tribunals and Inquiries Act 1992 was relevantly amended by paragraph 121 of Schedule 7 to the Social Security Act 1998 (c. 14).}, hereby make the following Regulations: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

1.---(1)  These Regulations may be cited as the Tax Credits (Decisions and Appeals) (Amendment) Regulations 2000 and shall come into force on 14th February 2000.

(2) These Regulations have effect—
\begin{enumerate}\item[]
($a$) with respect only to working families' tax credit and disabled person’s tax credit, and

($b$) with respect to award periods of working families' tax credit or disabled person’s tax credit commencing on or after 5th October 1999.
\end{enumerate}

\medskip

2.  Regulation 5($b$)  of the Tax Credits (Decisions and Appeals) (Amendment) Regulations 1999\footnote{S.I.\ 1999/2570.} (“regulation 5($b$)”) and regulation 2($b$)  of the Social Security and Child Support (Decisions and Appeals) Regulations 1999\footnote{S.I.\ 1999/991.} (“regulation 2($b$)”) shall have effect as if—
\begin{enumerate}\item[]
($a$) in regulation 5($b$)  before sub-paragraph (ii) there were inserted the following sub-paragraph—
\begin{quotation}
“(i) after the words “Secretary of State”, where those words first occur, there shall be inserted the words “or of an officer of the Board”;”; and
\end{quotation}

($b$) regulation 2($b$)  were amended accordingly.
\end{enumerate}

\bigskip

%Signed 
%by authority of the Secretary of State for Social Security.

{\raggedleft
%\emph{Stephen C.\ Timms
%}\\*Minister of State,\\*Department of Social Security

\emph{Nick Montagu\\*Tim Flesher}\\*Two of the Commissioners of Inland Revenue

}

21st January 2000

\small

\part[Schedule --- Provisions conferring powers exercised in making these Regulations]{Schedule\\*Provisions conferring powers exercised in making these Regulations}

{\footnotesize

%\begin{tabulary}{\linewidth}{JJ}
\begin{longtable}{p{181.44629pt}p{162.9498pt}}
\hline
\endhead
\hline
\endlastfoot
Social Security Administration Act 1992\footnote{\frenchspacing 1992 c. 5; section 5(1) was amended by section 74 of the Social Security Act 1998 (c. 14).}	&Section 5(1)($hh$).\\
Social Security Act 1998	&Section 9(1), (4) and (6)\\
&	Section 10(3) and (6)\\
&	Section 11(1)\\
&	Section 12(3), (6) and (7)\\
&	Section 14(10)($a$)  and (11)\\
&	Section 16(1) and Schedule 5\\
&	Sections 20 to 24\\
&	Section 25(3)($b$)  and (5)($c$) \\
&	Section 26(6)($c$) \\
&	Section 79(4) to (6)\\
&	Section 84\\
&	Schedule 3 paragraph 9.\\
Tax Credits Act 1999\footnote{\frenchspacing 1999 c. 10.}	&Section 2(1)($c$) \\
&	Section 19(1)\\
&	Schedule 1 paragraph 3($a$) \\
&	Schedule 2 paragraphs 7($b$)  and 8($a$).\\
%\end{tabulary}
\end{longtable}

}

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations correct an error in the Tax Credits (Decisions and Appeals) (Amendment) Regulations 1999 (S.I.\ 1999/2570). The latter Regulations made amendments, for the purposes of working families' tax credit and disabled person’s tax credit (“tax credits”) only, to the Social Security and Child Support (Decisions and Appeals) Regulations 1999 (S.I.\ 1999/991).

The completed copy of S.I.\ 1999/2570 omitted regulation 5($b$)(i), which amended regulation 2($b$)  of S.I.\ 1999/991, for tax credits purposes. These Regulations correct the omission, with effect from the coming into force of these Regulations. 

\end{document}