\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Tribunals, Courts and~Enforcement Act 2007 (Transitional and~Consequential Provisions) Order 2008}

\newcommand\regsnumber{2008/2683}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and~Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2008 No.\ 2683}

\date{Made
9th October 2008\\
Laid before Parliament
15th October 2008\\
Coming into~force
3rd November 2008
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{42.11603pt}

%\hbadness=10000

\begin{document}

\maketitle

\noindent
The Lord Chancellor makes the following Order in exercise of the powers conferred by sections 31(9) and~145 of, and~paragraph~30 of Schedule~5 to, the Tribunals, Courts and~Enforcement Act 2007\footnote{2007 c.~15.}. 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1--4. Citation, commencement and~extent]{Citation, commencement and~extent}

1.  This Order may be cited as the Tribunals, Courts and~Enforcement Act 2007 (Transitional and~Consequential Provisions) Order 2008 and~comes into~force on 3rd November 2008.

\medskip

2.  Except as provided by articles 3 and~4, an amendment or revocation of any enactment by any provision of Schedules 1 and~2 extends to~any part of the United Kingdom to~which the enactment extends.

\medskip

3.---(1)  For the purposes of article~4 the following amendments and~revocations made by Schedules 1 and~2 do not extend to~Scotland—

(2) In Schedule~1—
\begin{enumerate}\item[]
($a$) paragraph~96($a$), ($c$), ($d$)  and~($e$)(i), (iii), (iv)  and~(vi)  to~(ix) ;

($b$) paragraph~124 in so far as it relates to~regulations~35, 36(1), (2)($a$), (5) and~(8), 37 and~38;

($c$) paragraph~126 in so far as it relates to~regulations~39, 40, 42, 43, 46, 47, 49, 51 and~53 to~58;

($d$) paragraphs~128, 133($a$)  and~134; and

($e$) paragraph~136 in so far as it relates to~regulations~16 to~28 and~30 to~33.
\end{enumerate}

(3) In Schedule~2 the entries relating to—
\begin{enumerate}\item[]
($a$) the Social Security and~Child Support (Decisions and~Appeals) (Amendment) Regulations~1999\footnote{S.I.~1999/1466.} in so far as the entry relates to~regulation~2($b$);

($b$) the Social Security and~Child Support (Decisions and~Appeals), Vaccine Damage Payments and~Jobseeker’s Allowance Amendment Regulations~1999\footnote{S.I.~1999/2677.} in so far as the entry relates to~regulation~10;

($c$) the Social Security and~Child Support (Miscellaneous Amendments) Regulations~2000\footnote{S.I.~2000/1596.} in so far as the entry relates to~regulations~24($a$)  to~($c$), ($e$)  and~($h$), 25, 29 and~31;

($d$) the Social Security and~Child Support (Decisions and~Appeals) (Miscellaneous Amendments) Regulations~2002\footnote{S.I.~2002/1379.} in so far as the entry relates to~regulations~13 to~18 and~20;

($e$) the Social Security and~Child Support (Decisions and~Appeals) (Miscellaneous Amendments) Regulations~2003\footnote{S.I.\ 2003/1050.};

($f$) the Social Security, Child Support and~Tax Credits (Decisions and~Appeals) Amendment Regulations~2004\footnote{S.I.~2004/3368.} in so far as the entry relates to~regulation~2(4) to~(7);

($g$) the Social Security, Child Support and~Tax Credits (Miscellaneous Amendments) Regulations~2005\footnote{S.I.~2005/337.} in so far as the entry relates to~regulation~2(9) to~(14), (18) and~(20);

($h$) the Social Security and~Child Support Commissioners (Procedure) (Amendment) Regulations~2005\footnote{S.I.~2005/870.} in so far as the entry relates to~regulation~2; and

($i$) the Social Security and~Child Support (Decisions and~Appeals) (Amendment) Regulations~2008\footnote{S.I.~2008/1957.}.
\end{enumerate}

\medskip

4.  The purposes referred to~in article~3(1) are—
\begin{enumerate}\item[]
($a$) the determination by an appeal tribunal constituted under Chapter~I of Part I of the Social Security Act 1998\footnote{1998 c.~14.} of an appeal which is referred to~such a tribunal by the Scottish Ministers, or the Secretary of State on their behalf, pursuant to~section~158 (appeal tribunals) of the Health and~Social Care (Community Health and~Standards) Act 2003\footnote{2003 c.~43. The function of Scottish Ministers in relation to~section~158 can be exercised by the Secretary of State pursuant to~the Scotland~Act 1998 (Agency Arrangements) (Specifications) (No.~3) Order 2006 (S.I.~2006/3338).}; and

($b$) the determination by a Social Security Commissioner of an appeal made under section~159 (appeal to~social security commissioner) of that Act against a decision falling within sub-paragraph~($a$).
\end{enumerate}

\subsection[5. Transitional provision]{Transitional provision}

5.  Where an appeal lies to~the High Court under regulation~12 of the Road Traffic (NHS Charges) (Reviews and~Appeals) Regulations~1999\footnote{S.I.~1999/786.} (appeals to~the High Court) from any decision made by the appeal tribunal constituted under Chapter~I of Part I of the Social Security Act 1998, and~that appeal has not been commenced before 3rd November 2008, section~11 of the Tribunals Courts and~Enforcement Act 2007 shall apply as if the decision were a decision made on or after the 3rd November 2008 by the First-tier Tribunal.

\subsection[6. Consequential Amendments and~Revocations]{Consequential Amendments and~Revocations}

6.---(1)  Schedule~1 contains consequential amendments.

(2) Schedule~2 contains revocations. The instruments listed in column (1) of the table in Schedule~2 (which have the references listed in column (2)) are revoked to~the extent indicated in column (3). 

\bigskip

%Signed 
%by authority of the 
%Secretary of State for~Work and~Pensions.
%I concur
By authority of the Lord Chancellor

{\raggedleft
\emph{Bridget Prentice}\\*
%Secretary
%Minister
Parliamentary Under-Secretary 
of State\\%*Department 
%for~Work and~Pensions
Ministry of Justice

}

9th October 2008

\small

\part[Schedule~1 --- Consequential amendments]{Schedule~1\\*Consequential amendments}

\renewcommand\parthead{--- Schedule~1}

\section*{\itshape War Pensions (Mercantile Marine) Scheme 1964}

1.  Schedule~7 to~the War Pensions (Mercantile Marine) Scheme 1964\footnote{S.I.~1964/2058.} is amended as follows—
\begin{enumerate}\item[]
($a$) in paragraph~4—
\begin{enumerate}\item[]
(i) after “decision of the President of the Pensions Appeal Tribunals” insert “or the First-tier Tribunal, as the case may be,”;

(ii) for “the decision of a Pensions Appeal” substitute “the decision of the”; and

(iii) in paragraph~($b$)  after “Pensions Appeal Tribunals” insert “or the First-tier Tribunal, as the case may be,”; and
\end{enumerate}

($b$) in paragraph~8—
\begin{enumerate}\item[]
(i) after “decision of the President of the Pensions Appeal Tribunals” insert “or the First-tier Tribunal, as the case may be,”;

(ii) for “the decision of a Pensions Appeal”, in both places, substitute “the decision of the”; and

(iii) after “application to~the President of the Pensions Appeal Tribunals” insert “or the First-tier Tribunal, as the case may be,”.
\end{enumerate}
\end{enumerate}

\section*{\itshape Rent Assessment Committees (England and Wales) Regulations 1971}

2.  In regulation~3(1) of the Rent Assessment Committees (England~and~Wales) Regulations~1971\footnote{S.I.~1971/1065.} (hearings) omit “; but nothing in these regulations~shall prevent a member of the Council on Tribunals in that capacity from attending any hearing”.

\section*{\itshape\sloppy Plant Varieties and~Seeds Tribunal Rules 1974}

3.  In rule 10 of the Plant Varieties and~Seeds Tribunal Rules 1974\footnote{S.I.~1974/1136.} (tribunal to~sit in public) omit paragraph~(2).

\section*{\itshape Industrial Training (Levy Exemption References) Regulations~1974}

4.  In paragraph~6(1) of the Schedule~to~the Industrial Training (Levy Exemption References) Regulations~1974\footnote{S.I.~1974/1335.} (the hearing) omit “, but a member of the Council on Tribunals or of the Scottish Committee of the Council shall be entitled to~attend the hearing of any reference in private in his capacity as such member”.

\section*{\itshape Health and~Safety Inquiries (Procedure) Regulations~1975}

5.  In regulation~8 of the Health and~Safety Inquiries (Procedure) Regulations~1975\footnote{S.I.~1975/335.} (procedure at inquiry) omit paragraph~(3)($b$)(i)  (and~the following “and” and~“(ii)”).

\section*{\itshape Rehabilitation of Offenders Act 1974 (Exceptions) Order 1975}

6.  In Schedule~3 of the Rehabilitation of Offenders Act 1974 (Exceptions) Order 1975\footnote{S.I.~1975/1023. The Order was revoked in relation to~Scotland~by article~6($a$) of the Rehabilitation of Offenders Act 1974 (Exclusions and~Exceptions) (Scotland) Order 2003 (S.S.I.~2003/231).} (excepted proceedings) for paragraph~5 substitute—
\begin{quotation}
“5.  Proceedings under the Mental Health Act 1983 before any tribunal.”.
\end{quotation}

\section*{\itshape Social Security Benefit (Dependency) Regulations~1977}

7.  In regulation~1(2) of the Social Benefit (Dependency) Regulations~1977\footnote{S.I.~1977/343. In regulation~1(2) the definition of “the determining authority” was substituted by paragraph~1 of Schedule~2 to~the Social Security Act 1998 (Commencement No.~12 and~Consequential and~Transitional Provisions) Order 1999 (S.I.~1999/3178).} (citation, commencement and~interpretation) in the definition of “determining authority” for the words from “an appeal tribunal” to~the end substitute “the First-tier Tribunal or the Upper Tribunal;”.

\section*{\itshape Social Security (Widow’s Benefit and~Retirement Pensions) Regulations~1979}

8.  In regulation~1(2) of the Social Security (Widow’s Benefit and~Retirement Pensions) Regulations~1979\footnote{S.I.~1979/462. In regulation~1(2) the definition of “the determining authority” was substituted by paragraph~1($a$) of Schedule~3 to~the Social Security Act 1998 (Commencement No.~9, and~Savings and~Consequential and~Transitional Provisions) Order 1999 (S.I.~1999/2422).} (citation, commencement and~interpretation) in the definition of “the determining authority” for the words “an appeal tribunal” to~the end substitute “the First-tier Tribunal or the Upper Tribunal;”.

\section*{\itshape Pensions Appeals Tribunals (Posthumous Appeals) Order 1980}

9.  The Pensions Appeals Tribunals (Posthumous Appeals) Order 1980\footnote{S.I.~1980/1082. In article~1 the definition of “Commissioner” was inserted by article~2 of the Pensions Appeals Tribunals (Posthumous Appeals) Amendment Order 2005 (S.I.~2005/245). Article 4(1) and~(2) and~(6) were amended by articles 5, 6($a$) and~($b$), and~9($a$) and~($b$) of the 2005 Order. Article 5A was inserted by article~8 of the 2005 Order.} is amended as follows.

\medskip

10.  In article~1(2) (interpretation)—
\begin{enumerate}\item[]
($a$) in the definition of “Commissioner” for sub-paragraphs~($a$)  and~($b$)  substitute “the Social Security Administration (Northern Ireland) Act 1992\footnote{1992 c.~8.}”; and

($b$) in the definition of “the President of the Pensions Appeal Tribunals”—
\begin{enumerate}\item[]
(i) omit “by the Lord Chancellor”; and

(ii) at the end insert “for Scotland~or Northern Ireland”.
\end{enumerate}
\end{enumerate}

\medskip

11.  In article~3 (posthumous notification of, and~appeals to~Pensions Appeals Tribunals against, decisions of the Secretary of State)—
\begin{enumerate}\item[]
($a$) in the heading for “Pensions Appeals Tribunals” substitute “the appropriate tribunal”;

($b$) in paragraph~(1) for “Pensions Appeal Tribunals” substitute “the appropriate tribunal; and

($c$) after paragraph~(5) insert—
\begin{quotation}
“(6) For appeals to~the First-tier Tribunal, Tribunal Procedure Rules apply in respect of the time limits and~extension to~those time limits by the Secretary of State.”.
\end{quotation}
\end{enumerate}

\medskip

12.  In article~4 (initiation of posthumous appeals to~a Commissioner)—
\begin{enumerate}\item[]
($a$) in the heading after “Commissioner” insert “or the Upper Tribunal”;

($b$) in paragraph~(1)—
\begin{enumerate}\item[]
(i) for “the Pensions Appeal Tribunal” substitute “an appropriate tribunal”;

(ii) after “to~a Commissioner” insert “or the Upper Tribunal”; and

(iii) after “Act” insert “or to~the Upper Tribunal under section~11 of the Tribunals, Courts and~Enforcement Act 2007\footnote{2007 c.~15.}, as the case may be”;
\end{enumerate}

($c$) in paragraph~(2)—
\begin{enumerate}\item[]
(i) for “the Pensions Appeal Tribunal” substitute “an appropriate tribunal”;

(ii) after “to~a Commissioner” insert “or the Upper Tribunal”; and

(iii) after “6A” insert “of the Act, or to~the Upper Tribunal under section~11 of the Tribunals, Courts and~Enforcement Act 2007, as the case may be”; and
\end{enumerate}

($d$) in paragraph~(3)($b$)  for “a Pensions Appeal Tribunal” substitute “the appropriate tribunal”.
\end{enumerate}

\medskip

13.  In article~5 (continuation of appeals after death of claimant) for “or, as the case may be, 6A of the Act” substitute “or 6A of the Act or section~11 of the Tribunals, Courts and~Enforcement Act 2007, as the case may be”.

\medskip

14.  In article~5A (posthumous appeals from a Commissioner)—
\begin{enumerate}\item[]
($a$) in the heading, after “a Commissioner” insert “or the Upper Tribunal”; and

($b$) at the end insert “or where the appeal was brought or continued in the Upper Tribunal, the designated person may appeal from the Upper Tribunal in accordance with section~13 of the Tribunals, Courts and~Enforcement Act 2007”.
\end{enumerate}

\medskip

15.  In article~6 (directions in relation to~appeals) after “President or a Commissioner” insert “or the First-tier Tribunal or the Upper Tribunal, as the case may be,”.

\medskip

16.  In article~9(3) (application of order and~time for appealing) after “of the Act” insert “or the Tribunals, Courts and~Enforcement Act 2007”.

\section*{\itshape Rent Assessment Committees (England and Wales) (Rent Tribunal) Regulations 1980}

17.  In regulation~7(1) of the Rent Assessment Committees (England~and~Wales) (Rent Tribunal) Regulations~1980\footnote{S.I.~1980/1700.} omit “; but nothing in these regulations~shall prevent a member of the Council on Tribunals in that capacity from attending any hearing”.

\section*{\itshape\sloppy\hbadness=1072 Statutory Sick Pay (General) Regulations 1982}

18.  In regulation~9A(3) of the Statutory Sick Pay (General) Regulations~1982\footnote{S.I.~1982/894. Regulation~9A was inserted by regulation~2 of the Statutory Sick Pay (General) (Amendment) Regulations~1987 (S.I.~1987/372).} (liability of the Commissioners of Inland~Revenue for payments of statutory sick pay) for the words “a Social Security Appeal Tribunal” to~the end substitute “the First-tier Tribunal or the Upper Tribunal.”.

\section*{\itshape War Pensions (Commencing Dates of Past Awards) Order 1982}

19.  The War Pensions (Commencing Dates of Past Awards) Order 1982\footnote{S.I.~1982/1046.} is amended as follows.

\medskip

20.  In article~1 (interpretation)—
\begin{enumerate}\item[]
($a$) before the definition of “instruments” insert—
\begin{quotation}
““appropriate tribunal” means the appropriate tribunal as defined in section~12(1) of the 1943 Act;”;
\end{quotation}

($b$) omit the definition of “Pensions Appeal Tribunal”; and

($c$) in the definition of “the rules” after “1943 Act” insert “or Tribunal Procedure Rules”.
\end{enumerate}

\medskip

21.  In article~4 (limitation on arrears)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($a$)—
\begin{enumerate}\item[]
(i) after “under the rules” insert “or by the Upper Tribunal”; and

(ii) for “a Pensions Appeal Tribunal” substitute “an appropriate tribunal”;
\end{enumerate}

($b$) in sub-paragraph~($b$)  for “a Pensions Appeal Tribunal” substitute “an appropriate tribunal”; and

($c$) in sub-paragraph~($c$)—
\begin{enumerate}\item[]
(i) for “from Pensions Appeal Tribunal” substitute “from the appropriate tribunal”; and

(ii) for “a Pensions Appeal Tribunal” substitute “an appropriate tribunal”.
\end{enumerate}
\end{enumerate}

\medskip

22.  In items 4 and~5 of Schedule~2 (commencing dates of past awards)—
\begin{enumerate}\item[]
($a$) in column 2—
\begin{enumerate}\item[]
(i) in paragraph~($a$)  after “under the rules” insert “or by the Upper Tribunal”; and

(ii) in paragraph~($b$)  for “a Pensions Appeal Tribunal” substitute “an appropriate tribunal”; and
\end{enumerate}

($b$) in column 3 for “Pensions Appeal Tribunal” substitute “appropriate tribunal”.
\end{enumerate}

\section*{\itshape Social Security (General Benefit) Regulations 1982}

23.  The Social Security (General Benefit) Regulations~1982\footnote{S.I.~1982/1408. In regulation~1(2) the definition of “determining authority” was substituted by paragraph~1 of Schedule~3 to~the Social Security Act 1998 (Commencement No.~12 and~Consequential and~Transitional Provisions) Order 1999 (S.I.~1999/3178). Regulation~11(7) and~(8) was amended by paragraph~2 of Schedule~3 to~that Order.} are amended as follows.

\medskip

24.  In regulation~1(2) (citation, commencement and~interpretation) in the definition of “determining authority” for the words from “an appeal tribunal” to~the end substitute “the First-tier Tribunal or the Upper Tribunal;”.

\medskip

25.  In regulation~11(7) and~(8) (further definition of the principles of assessment of disablement and~prescribed degrees of disablement) for “an appeal tribunal” substitute “the First-tier Tribunal”.

\section*{\itshape Workmen’s Compensation (Supplementation) Scheme 1982}

26.  The Workmen’s Compensation (Supplementation) Scheme 1982\footnote{S.I.~1982/1489. In article~1(2) the definition of “the appropriate determining authority” was inserted by paragraph~1($b$) of Schedule~6 to~the Social Security Act 1998 (Commencement No.~8, Savings and~Consequential and~Transitional Provisions) Order 1999 (S.I.~1999/1958). Article 12 was substituted by paragraph~3 of Schedule~6 to~that Order.} is amended as follows.

\medskip

27.  In article~1(2) (citation, commencement and~interpretation) in the definition of “the appropriate determining authority” for the words “an appeal tribunal” to~the end substitute “the First-tier Tribunal or the Upper Tribunal;”.

\medskip

28.  In article~12 (determination of claims and~applications for revision and~supersession arising under the scheme) omit “and~the Social Security Commissioners (Procedure) Regulations~1999”.

\medskip

29.  In Schedule~2 (provisions of the 1998 Act or regulations~applicable (with the necessary modifications) to~this scheme) omit the entries relating to—
\begin{enumerate}\item[]
($a$) regulations~35 to~38, 39 to~47 and~49 to~58 of the Social Security and~Child Support (Decisions and~Appeals) Regulations~1999; and

($b$) the Social Security Commissioners (Procedure) Regulations~1999.
\end{enumerate}

\section*{\itshape\sloppy\hbadness=1199 Pneumoconiosis, Byssinosis and Miscellaneous Diseases Benefit Scheme 1983}

30.  The Pneumoconiosis, Byssinosis and~Miscellaneous Diseases Benefit Scheme 1983\footnote{S.I.~1983/136. In article~1(2) the definition of “the appropriate determining authority” was inserted by paragraph~1($b$) of Schedule~7 to~the Social Security Act 1998 (Commencement No.~8, Savings and~Consequential and~Transitional provisions) Order 1999 (S.I.~1999/1958). Article 12 was substituted by paragraph~4 of Schedule~7 to~that Order.} is amended as follows.

\medskip

31.  In article~1(2) (citation, commencement and~interpretation) in the definition of “the appropriate determining authority” for the words “an appeal tribunal” to~the end substitute “the First-tier Tribunal or the Upper Tribunal;”.

\medskip

32.  In article~12 (questions arising under the scheme) omit the entry relating to~“the Social Security Commissioners (Procedure) Regulations~1999”.

\medskip

33.  In Schedule~3 (provisions of the Social Security Act or regulations~applicable (with the necessary modifications) to~this scheme) omit the entries relating to—
\begin{enumerate}\item[]
($a$) regulations~35 to~38, 39 to~47 and~49 to~58 of the Social Security and~Child Support (Decisions and~Appeals) Regulations~1999; and

($b$) the Social Security Commissioners (Procedure) Regulations~1999.
\end{enumerate}

\section*{\itshape Personal Injuries (Civilians) Scheme 1983}

34.  The Personal Injuries (Civilians) Scheme 1983\footnote{S.I.~1983/686.} is amended as follows.

\medskip

35.  In article~56($a$)  (determination of medical questions) after “1949” insert “or, as the case may be, the First-tier Tribunal”.

\medskip

36.  In Schedule~5 (commencing dates of awards of pension)—
\begin{enumerate}\item[]
($a$) in paragraph~4—
\begin{enumerate}\item[]
(i) after “decision of the President of the Pensions Appeal Tribunals” insert “or the First-tier Tribunal, as the case may be,”;

(ii) for “the decision of a Pensions Appeal” substitute “the decision of the”; and

(iii) in paragraph~($b$)  after “Pensions Appeal Tribunals” insert “or the First-tier Tribunal as the case may be”; and
\end{enumerate}

($b$) in paragraph~8—
\begin{enumerate}\item[]
(i) after “decision of the President of the Pensions Appeal Tribunals” insert “or the First-tier Tribunal, as the case may be,”;

(ii) for “the decision of a Pensions Appeal”, in both places, substitute “the decision”; and

(iii) after “application to~the President of the Pensions Appeal Tribunals” insert “or the First-tier Tribunal, as the case may be,”.
\end{enumerate}
\end{enumerate}

\section*{\itshape\sloppy\hbadness=2460 Social Security (Unemployment, Sickness and Invalidity Benefit) Regulations 1983}

37.  In regulation~1(2) of the Social Security (Unemployment, Sickness and~Invalidity Benefit) Regulations~1983\footnote{S.I.~1983/1598. In regulation~1(2) the definition of “the determining authority” was amended by paragraph~1(3)($a$)(i) of Schedule~8 to~the Health and~Social Services and~Social Security Adjudications Act 1983 (c.~41).} (citation, commencement and~interpretation), in the definition of “determining authority” for the words “a social security appeal tribunal” to~the end substitute “the First-tier Tribunal or the Upper Tribunal;”.

\section*{\itshape Civil Aviation Authority (Economic Regulation~of Airports) Regulations~1986}

38.  In regulation~13(7) of the Civil Aviation Authority (Economic Regulation~of Airports) Regulations~1986\footnote{S.I.~1986/1544.} (enforcement of conditions) omit the words “, but nothing in this regulation~shall prevent a member of the Council on Tribunals or of its Scottish Committee from attending a hearing in his capacity as such”.

\enlargethispage{-4\baselineskip}

\section*{\itshape Public Service Vehicles (Traffic Commissioners: Publication and Inquiries) Regulations 1986}

39.  In regulation~7 of the Public Service Vehicles (Traffic Commissioners: Publication and~Inquiries) Regulations~1986\footnote{S.I.~1986/1629.} (attendance at inquiries) omit “, provided that a member of the Council on Tribunals or its Scottish Committee shall be entitled to~attend notwithstanding that attendance is restricted”.

\section*{\itshape\sloppy Medicines Act 1968 (Hearings by Persons Appointed) Rules 1986}

40.  In rule 6 of the Medicines Act 1968 (Hearings by Persons Appointed) Rules 1986\footnote{S.I.~1986/1761.} (procedure at hearings by persons appointed) omit paragraph~(3).

\section*{\itshape\sloppy Animals (Scientific Procedures) (Procedure for Representations) Rules 1986}

41.  In rule 8 of the Animals (Scientific Procedures) (Procedure for Representations) Rules 1986\footnote{S.I.~1986/1911.} (procedure at hearings of oral representations) omit paragraph~(4).

\section*{\itshape Statutory Maternity Pay (General) Regulations~1986}

42.  In regulation~7(2) of the Statutory Maternity Pay (General) Regulations~1986\footnote{S.I.~1986/1960.} (liability of Commissioners of Inland~Revenue to~pay statutory maternity pay), for the words “a Social Security Appeal Tribunal” to~the end substitute “the First-tier Tribunal or the Upper Tribunal.”.

\enlargethispage{-4\baselineskip}

\section*{\itshape Social Security (Claims and~Payments) Regulations~1987}

43.  In regulation~6(26) and~(33)($c$)  of the Social Security (Claims and~Payments) Regulations~1987\footnote{S.I.~1987/1968. These regulations~have been revoked in so far as they relate to~child benefit or guardian’s allowance by the Child Benefit and~Guardian’s Allowance (Administration) Regulations~2003 (S.I.~2003/492). Regulation~6(33) was inserted by regulation~2(4)($e$) of the Social Security (Miscellaneous Amendments) (No.~2) Regulations~2006 (S.I.~2006/832).} (date of claim) for “an appeal tribunal, a Commissioner” substitute “the First-tier Tribunal, the Upper Tribunal”.

\section*{\itshape Social Security (Payments on account, Overpayments and~Recovery) Regulations~1988}

44.  In regulation~1(2) of the Social Security (Payments on account, Overpayments and~Recovery) Regulations~1988\footnote{S.I.~1988/664. These regulations~have been revoked in so far as they relate to~child benefit or guardian’s allowance by the Child Benefit and~Guardian’s Allowance (Administration) Regulations~2003 (S.I.~2003/492). In regulation~1(2) the definition of “adjudicating authority” was substituted by paragraph~1 of Schedule~9 to~the Social Security Act 1998 (Commencement No.~12 and~Consequential and~Transitional Provisions) Order 1999 (S.I.~1999/3178).} (citation, commencement and~interpretation) in the definition of “adjudicating authority” for the words “an appeal tribunal” to~the end substitute “the First-tier Tribunal or the Upper Tribunal;”.

\section*{\itshape Civil Aviation Authority Regulations~1991}

45.  The Civil Aviation Authority Regulations~1991\footnote{S.I.~1991/1672. Regulation~6(7A) was inserted by regulation~2(7) of the Civil Aviation Authority (Amendment) Regulations~2001 (S.I.~2001/2448). Regulation~31D was inserted by regulation~2(10) of the Civil Aviation Authority (Amendment) Regulations~2001 (S.I.~2001/2448).} are amended as follows.

\medskip

46.  For regulation~6(7A)($b$)  (regulation~of the conduct of the Authority) substitute—
\begin{quotation}
“($b$) Any person which the Authority, with the consent of the parties, permits to~attend the hearing is entitled to~do so, whether or not the hearing is in private.”.
\end{quotation}

\medskip

47.  In regulation~14(5) omit the words “, but nothing in this regulation~shall prevent a member of the Council on Tribunals or of its Scottish Committee from attending a hearing in his capacity as such”.

\medskip

48.  In regulation~26(4) (procedure at hearings) omit the words “, but nothing in this regulation~shall prevent a member of the Council on Tribunals or of its Scottish Committee from attending a hearing in his capacity as such”.

\enlargethispage{-2\baselineskip}

\medskip

49.  In regulation~31D(4) (procedure at hearings)—
\begin{enumerate}\item[]
($a$) omit sub-paragraph~($b$); and

($b$) sub-paragraph~($a$)  shall stand~as paragraph~(4).
\end{enumerate}

\section*{\itshape Social Security (Disability Living Allowance) Regulations~1991}

50.  In regulation~1(2) of the Social Security (Disability Living Allowance) Regulations~1991\footnote{S.I.~1991/2890. In regulation~1(2) the definition of “adjudicating authority” was substituted by paragraph~1($b$) of Schedule~7 to~the Social Security Act 1998 (Commencement No.~11, and~Savings and~Consequential and~Transitional Provisions) Order 1999 (S.I.~1999/2860).} (citation, commencement and~interpretation) in the definition of “adjudicating authority” for “an appeal tribunal” to~the end substitute “the First-tier Tribunal or the Upper Tribunal”.

\section*{\itshape National Health Service (Service Committees and~Tribunal) Regulations~1992}

\enlargethispage{-2\baselineskip}

51.  The National Health Service (Service Committees and~Tribunal) Regulations~1992\footnote{S.I.~1992/664. Regulation~10 was substituted by regulation~4 of the National Health Service (Service Committees and~Tribunal) Amendment Regulations~1996 (S.I.~1996/703).} are amended as follows.

\medskip

52.  In regulation~10(10) (procedure on appeals) for “Council on Tribunals” substitute “Administrative Justice and~Tribunals Council”.

\medskip

53.  In regulation~33 (attendance by member of Council on Tribunals)—
\begin{enumerate}\item[]
($a$) for “Council on Tribunals”, in both places (including the heading), substitute “Administrative Justice and~Tribunals Council”;

($b$) omit sub-paragraph~($a$); and

($c$) for “Tribunal, committee” substitute “committee”.
\end{enumerate}

\medskip

54.  In paragraph~5(1) of Schedule~4 (procedure for investigation by discipline committees) for “Council on Tribunals” substitute “Administrative Justice and~Tribunals Council”.

\medskip

55.  In paragraph~5(1) of Schedule~9 (hearings under Part III) omit “Subject to~regulation~33 (attendance by a member of Council on Tribunals)”.

\section*{\itshape\sloppy\hbadness=5652 Child Support (Maintenance Assessment Procedure) Regulations 1992}

56.  The Child Support (Maintenance Assessment Procedure) Regulations~1992\footnote{S.I.~1992/1813. Revoked with savings for certain purposes by the Child Support (Maintenance Calculation Procedure) Regulations~2000 (S.I.~2001/157). In regulation~1(2) the definition of “official error” was substituted by paragraph~8($b$) of Schedule~6 to~the Social Security (Work-focussed Interviews) Regulations~2000 (S.I.~2000/897). Regulations~20(4A) and~23(20) were inserted by Social Security and~Child Support (Miscellaneous Amendments) Regulations~2003 (S.I.~2003/1050).} are amended as follows.

\medskip

57.  In regulation~1(2) (citation, commencement and~interpretation) in the definition of “official error” for “a Child Support Commissioner” substitute “the Upper Tribunal”.

\medskip

58.  In regulation~10(1) (notifications following certain decisions by child support officers) for “an appeal tribunal” substitute “the First-tier Tribunal”.

\medskip

59.  In regulation~18(6)($b$)  (late applications for a revision) for “a Child Support Commissioner” substitute “the Upper Tribunal”.

\medskip

60.  In regulation~20(4A) (supersession of decisions) for “an appeal tribunal or of a Child Support Commissioner” substitute “the First-tier Tribunal or Upper Tribunal”.

\medskip

61.  In regulation~23 (date from which a decision is superseded)—
\begin{enumerate}\item[]
($a$) in paragraph~(10)—
\begin{enumerate}\item[]
(i) in sub-paragraph~($a$)  for “an appeal tribunal under section~20 of the Act or a Child Support Commissioner” substitute “the First-tier Tribunal under section~20 of the Act or the Upper Tribunal”; and

(ii) for “appeal tribunal or, as the case may be, the Child Support Commissioner” substitute “the First-tier Tribunal or, as the case may be, the Upper Tribunal”; and
\end{enumerate}

($b$) in paragraph~(20)—
\begin{enumerate}\item[]
(i) for “appeal tribunal or the Child Support Commissioner’s” substitute “First-tier Tribunal or the Upper Tribunal’s”; and

(ii) for “Child Support Commissioner” substitute “Upper Tribunal”.
\end{enumerate}
\end{enumerate}

\section*{\itshape Child Support (Arrears, Interest and~Adjustment of Maintenance Assessments) Regulations~1992}

62.  In regulation~14(6)($b$)  of the Child Support (Arrears, Interest and~Adjustment of Maintenance Assessments) Regulations~1992\footnote{S.I.~1992/1816. Regulation~14 was substituted by article~28 of the Social Security Act 1998 (Commencement No.~7 and~Consequential and~Transitional Provisions) Order 1999 (S.I.~1999/1510) and~revoked for certain purposes by regulation~14(1) of the Child Support (Decisions and~Appeals) (Amendment) Regulations~2000 (S.I.~2000/3185).} (late application for revision) for “a Child Support Commissioner” substitute “the Upper Tribunal”.

\section*{\itshape\sloppy Family Proceedings Courts (Child Support Act 1991) Rules 1993}

63.  In rule 5(2)($c$)  of the Family Proceedings Courts (Child Support Act 1991) Rules 1993\footnote{S.I.~1993/627. Paragraph 2 of rule 5 was inserted by Rule 16 of the Family Proceedings Courts (Miscellaneous Amendments) Rules 2007 (S.I.~2007/2188).} (disclosure of information under the Act of 1991) for “an appeal tribunal” substitute “the First-tier Tribunal”.

\section*{\itshape\sloppy Road Traffic (Parking Adjudicators) (London) Regulations 1993}

64.  For regulation~9(4) of the Road Traffic (Parking Adjudicators) (London) Regulations~1993\footnote{S.I.~1993/1202.} (procedure at a hearing) substitute—
\begin{quotation}
“(4) Any adjudicator appointed under section~73(3)($a$)  of the Act shall be entitled to~attend the hearing of an appeal whether or not it is in private.”.
\end{quotation}

\section*{\itshape Social Security (Incapacity Benefit) Regulations~1994}

65.  In regulation~4A(3) of the Social Security (Incapacity Benefit) Regulations~1994\footnote{S.I.~1994/2946. Regulation~4A was inserted by regulation~2(4) of the Social Security (Incapacity Benefit) Miscellaneous Amendments Regulations~2000 (S.I.~2000/3120) and~paragraph~(3) was inserted by regulation~6(3) of the Social Security (Miscellaneous Amendments) (No.~5) Regulations~2007 (S.I.~2007/2618).} (days to~be treated as days of incapacity for work)—
\begin{enumerate}\item[]
($a$) omit the definition of “Commissioner”; and

($b$) in the definition of “official error” for “a Commissioner” substitute “the Upper Tribunal”.
\end{enumerate}

\section*{\itshape Social Security (Incapacity for Work) (General) Regulations~1995}

66.  For regulation~17(7)($b$)  of the Social Security (Incapacity for Work) (General) Regulations~1995\footnote{S.I.~1995/311. Regulation~17 was substituted by regulation~4 of the Social Security (Incapacity for Work) Amendment Regulations~2006 (S.I.~2006/757).} (exempt work) substitute—
\begin{quotation}
“($b$) a member of the First-tier Tribunal where the member is eligible for appointment to~be such a member in accordance with article~2(3) of the Qualifications for Appointment of Members to~the First-tier Tribunal and~Upper Tribunal Order 2008\footnote{S.I.~2008/2692.}.”.
\end{quotation}

\section*{\itshape\sloppy Personal and Occupational Pension Schemes (Pensions Ombudsman) (Procedure) Rules 1995}

67.  In rule 12 of the Personal and~Occupational Pension Schemes (Pensions Ombudsman) (Procedure) Rules 1995\footnote{S.I.~1995/1053.} (hearings to~be in public subject to~exceptions) omit paragraph~(2).

\section*{\itshape Civil Aviation Authority (Economic Regulation~of Airports) (Northern Ireland) Regulations~1995}

68.  In regulation~13(9) of the Civil Aviation Authority (Economic Regulation~of Airports) (Northern Ireland) Regulations~1995\footnote{S.I.~1995/2294.} (enforcement of conditions) omit “but nothing in this regulation~shall prevent a member of the Council on Tribunals from attending a hearing in his capacity as such”.

\section*{\itshape Local Government Changes for England~(Education) (Miscellaneous Provisions) Regulations~1996}

69.  The Local Government Changes for England~(Education) (Miscellaneous Provisions) Regulations~1996\footnote{S.I.~1996/710.} are amended as follows.

\medskip

70.  In regulation~13($b$)  for “Special Educational Needs” substitute “First-tier”.

\medskip

71.  Omit regulation~16 (appeals to~Special Educational Needs Tribunal).

\section*{\itshape Deregulation~(Model Appeal Provisions) Order 1996}

72.  The Schedule~to~the Deregulation~(Model Appeal Provisions) Order 1996\footnote{S.I.~1996/1678.} (model rules for appeals) is amended as follows—
\begin{enumerate}\item[]
($a$) in paragraph~6(9) (appointment of tribunal) for “Council on Tribunals” substitute “Administrative Justice and~Tribunals Council”;

($b$) omit paragraph~25(2) (hearing to~be in public);

($c$) in the heading of paragraph~37 for “Council on Tribunals” substitute “Administrative Justice and~Tribunals Council”; and

($d$) in paragraph~37 (supervision by the Council on Tribunals) for “Council on Tribunals as if they were tribunals specified in Schedule~l to~the Tribunals and~Inquiries Act 1992” substitute “Administrative Justice and~Tribunals Council as if they were a listed tribunal within the meaning given in paragraph~25 of Schedule~7 to~the Tribunals, Courts and~Enforcement Act 2007\footnote{2007 c.~15.}”.\looseness=1
\end{enumerate}

\section*{\itshape Employment Protection (Recoupment of Jobseeker’s Allowance and~Income Support) Regulations~1996}

73.  In regulation~10(2B) of the Employment Protection (Recoupment of Jobseeker’s Allowance and~Income Support) Regulations~1996\footnote{S.I.~1996/2349. Regulation~10(2B) was inserted by paragraph~2 of Schedule~14 to~the Social Security Act 1998 (Commencement No.~12 and~Consequential and~Transitional Provisions) Order 1999 (S.I.~1999/3178).} (provisions relating to~determination of amount paid by way of or paid as on account of benefit) for “an appeal tribunal constituted under Chapter~I of Part I of the 1998 Act” substitute “the First-tier Tribunal”.

\section*{\itshape Child Support Departure Direction and~Consequential Amendments Regulations~1996}

74.  The Child Support Departure Direction and~Consequential Amendments Regulations~1996\footnote{S.I.~1996/2907. Revoked with savings for certain purposes by the Child Support (Variations) Regulations~2000 (S.I.~2001/156) as amended by the Child Support (Transitional Provision) (Miscellaneous Amendments) Regulations~2003 (S.I.~2003/347). In regulation~1(2) the definition of “official error” was amended by regulation~10 of the Social Security and~Child Support (Miscellaneous Amendments) Regulations~2000 (S.I.~2000/1596). Regulations~32A, 32B and~32E were inserted, and~regulation~34A(3) amended, by regulations~44 and~46 of the Child Support (Miscellaneous Amendments) (No.~2) Regulations~1999 (S.I.~1999/1047). Regulation~34A was inserted by regulation~19 of the Child Support (Miscellaneous Amendments) Regulations~1998 (S.I.~1998/58).} are amended as follows.

\medskip

75.  In regulation~1(2) (citation, commencement and~interpretation) in the definition of “official error” for “a Child Support Commissioner” substitute “the Upper Tribunal”.

\medskip

76.  In regulation~32A(1) (revision of decisions) for “an appeal tribunal” substitute “the First-tier Tribunal”.

\medskip

77.  In regulation~32B(6)($b$)  (late applications for a revision) for “a Child Support Commissioner” substitute “the Upper Tribunal”.

\medskip

78.  In regulation~32E(6)($a$)  (date from which a superseding decision takes effect) for “an appeal tribunal” substitute “the First-tier Tribunal”.

\medskip

79.  In regulation~34A(3) (correction of accidental errors in departure directions) for the words “in regulation~31(1)” to~“Regulations~1999” substitute “under Tribunal Procedure Rules”.

\section*{\itshape Occupational and~Personal Pension Schemes (Contracting-out etc: Review of Determinations) Regulations~1997}

80.  In regulation~4 of the Occupational and~Personal Pension Schemes (Contracting-out etc: Review of Determinations) Regulations~1997\footnote{S.I.~1997/358.} (formal hearings in connection with reviews) omit paragraph~(5).

\section*{\itshape Occupational Pensions Regulatory Authority (Determinations and~Review Procedure) Regulations~1997}

81.  In regulation~13 of the Occupational Pensions Regulatory Authority (Determinations and~Review Procedure) Regulations~1997\footnote{S.I.~1997/794.} (oral hearings) omit paragraph~(2)($d$).

\section*{\itshape Airports (Groundhandling) Regulations~1997}

82.  The Airports (Groundhandling) Regulations~1997\footnote{S.I.~1997/2389. Paragraph 5 of Schedule~2 was substituted by regulation~10($b$) of the Airports (Groundhandling) (Amendment) Regulations~1998 (S.I.~1998/2918).} are amended as follows.

\medskip

83.  In paragraph~13(4) of Schedule~1 (procedure for a determination by the CAA under regulations~9, 10, 11, 14 and~15) omit the words “, but nothing in this sub-paragraph~shall prevent a member of the Council on Tribunals or of its Scottish Committee from attending a hearing in his capacity as such”.

\medskip

84.  In paragraph~5(3) of Schedule~2 (appeals to~the CAA) omit the words “, but nothing in this sub-paragraph~shall prevent a member of the Council on Tribunals or of its Scottish Committee from attending a hearing in his capacity as such”.

\section*{\itshape Plant Breeders’ Rights Regulations~1998}

85.  In regulation~8 of the Plant Breeders’ Rights Regulations~1998\footnote{S.I.~1998/1027.} (hearings of oral representations) omit paragraph~(9).

\section*{\itshape\sloppy National Lottery (Imposition of Penalties and Revocation of Licences) Procedure Regulations 1999}

86.  The National Lottery (Imposition of Penalties and~Revocation of Licences) Procedure Regulations~1999\footnote{S.I.~1999/137.} are amended as follows.

\medskip

87.  In regulation~7 (admission to~a hearing) omit paragraph~(4).

\medskip

88.  In regulation~14 (admission to~a hearing) omit paragraph~(4).

\section*{\itshape Education (Registered Inspectors of Schools Appeal Tribunal and~Registered Nursery Education Inspectors Appeal Tribunal) (Procedure) Regulations~1999}

89.  For regulation~24(3) of the Education (Registered Inspectors of Schools Appeal Tribunal and~Registered Nursery Education Inspectors Appeal Tribunal) (Procedure) Regulations~1999\footnote{S.I.~1999/265.} (hearings to~be in public: exceptions) substitute—
\begin{quotation}
“(3) A person may, with the leave of the Tribunal and~the consent of the parties present, attend the hearing of an appeal notwithstanding that it is in private.”.
\end{quotation}

\section*{\itshape Road Traffic (NHS Charges) (Reviews and Appeals) Regulations 1999}

90.  The Road Traffic (NHS Charges) (Reviews and~Appeals) Regulations~1999\footnote{S.I.~1999/786.} are amended as follows.

\medskip

91.  In regulation~1 (interpretation)—
\begin{enumerate}\item[]
($a$) in paragraph~(2)—
\begin{enumerate}\item[]
(i) in the definition of “appeal” omit “, except in regulation~12,”; and

(ii) for the definition of “tribunal” substitute—
\begin{quotation}
““tribunal” means the First-tier Tribunal;”;
\end{quotation}
\end{enumerate}

($b$) in paragraph~(4) omit—
\begin{enumerate}\item[]
(i) “or the clerk to~or a chairman of a tribunal,”; and

(ii) “or of the clerk to~the tribunal, as appropriate”; and
\end{enumerate}

($c$) omit paragraph~(5).
\end{enumerate}

\medskip

92.  In regulation~3 (manner of making appeals and~time limits)—
\begin{enumerate}\item[]
($a$) for paragraph~(1) substitute—
\begin{quotation}
“(1) An appeal against a certificate made in accordance with Tribunal Procedure Rules must be made on a form approved by the Secretary of State and~sent to~the Compensation Recovery Unit.”;
\end{quotation}

($b$) omit paragraphs~(2) to~(9);

($c$) in paragraphs~(10) and~(11) for “under paragraph~(9)” substitute “by Tribunal Procedure Rules”;

($d$) in paragraph~(12) for “this regulation” substitute “Tribunal Procedure Rules”; and

($e$) omit paragraphs~(15) and~(16).
\end{enumerate}

\medskip

93.  Omit regulations~4 to~12 (tribunal procedure).

\section*{\itshape Police Appeals Tribunal Rules 1999}

94.  In rule 9 of the Police Appeals Tribunal Rules 1999\footnote{S.I.~1999/818.} (hearing to~be in private) omit paragraph~(3).

\vfill

\section*{\itshape Social Security and~Child Support (Decisions and~Appeals) Regulations~1999}

95.  The Social Security and~Child Support (Decisions and~Appeals) Regulations~1999\footnote{S.I.~1999/991. In regulation~1 the definition of “out of jurisdiction appeal” was substituted by regulation~3(1) of the Social Security and~Child Support (Miscellaneous Amendments) Regulations~2003 (S.I.~2003/1050). The definition of “official error” in regulation~1 and~regulations~3(4A) and~(5A), 9A and~31(1)($a$), ($b$) and~($c$) were inserted, and~regulations~32, 33 and~38A were amended, by the Social Security and~Child Support (Decisions and~Appeals) (Miscellaneous Amendments) Regulations~2002 (S.I.~2002/1379). The definition of “party to~the proceedings” was amended by regulation~4($b$) of the Tax Credits (Decisions and~Appeals) (Amendment) Regulations~1999 (S.I.~1999/2570), regulation~2($c$) of the Child Support (Decisions and~Appeals) (Amendment) Regulations~2000 (S.I.~2000/3185) and~regulation~15(1) of the Social Security (Jobcentre Plus Interviews for Partners) Regulations~2003 (S.I.~2003/1886). The definition of “referral” was amended by regulation~2($d$) of the Child Support (Decisions and~Appeals) (Amendment) Regulations~2000 (S.I.~2000/3185). Regulations~2, 16(3)($b$)(ii), 30, 31 and~33 were amended by regulations~5, 21, 22 and~23 of the Tax Credits (Decisions and~Appeals) (Amendment) Regulations~1999 (S.I.~1999/2570). Regulations~3A, 6A, 6B, 7B and~30A were inserted, and~regulations~4(6)($b$) and~30 were amended, by regulations~5, 6($e$), 8, 11 and~12 of the Child Support (Decisions and~Appeals) (Amendment) Regulations~2000 (S.I.~2000/3185). Regulation 3A(3) and~(5A) were substituted by regulation~2($b$) and~($c$) of the Child Support (Miscellaneous Amendments) Regulations~2002 (S.I.~2002/1204). Regulations~6(2)($c$),~6A(4A), 7(33) and~7B(22A) were inserted by the Child Support (Decisions and~Appeals) (Amendment) Regulations~2000 (S.I.~2000/3185). Regulations~6(2)($n$) and~58A were inserted, and~regulation~31 was amended, by regulation~2(4)($c$), (8) and~(19) of the Social Security, Child Support and~Tax Credits (Miscellaneous Amendments) Regulations~2005 (S.I.~2005/337). Regulations~7(5),~16(4) and~20(2) and~(3) were substituted by the Social Security and~Child Support (Miscellaneous Amendments) Regulations~2000 (S.I.~2000/1596). Regulation 38A was inserted by regulation~2(4) of the Social Security and~Child Support (Decisions and~Appeals) Amendment (No.~3) Regulations~1999 (S.I.~1999/1670). Regulation 9ZA was inserted, and~regulations~29 and~31 were amended, by Schedule~2 of the Social Security (Recovery of Benefits) (Lump Sum Payments) Regulations~2008 (S.I.~2008/1596). Regulation 33(1) was amended by regulation~9 of the Social Security and~Child Support (Decisions and~Appeals), Vaccine Damage Payments and~Jobseeker’s Allowance (Amendment) Regulations~1999 (S.I.~1999/2677) and~by regulation~4 of the Child Support (Consequential Amendments and~Transitional Provisions) Regulations~2001 (S.I.~2001/158). Regulations~3, 3A, 4, 6, 6A, 6B, 7, 7B, 8, 9A, 16,~20,~25 to~27 and~29 to~33 were revoked by the Child Benefit and~Guardian’s Allowance (Decisions and~Appeals) Regulations~2003 (S.I.~2003/916) so far as relating to~child benefit or guardian’s allowance under the Social Security Contribution and~Benefits Act 1992 (c.~4).} are amended as follows.

\medskip

96.  In regulation~1(3) (citation, commencement and~interpretation)—
\begin{enumerate}\item[]
($a$) in the definition of “appeal” for “an appeal tribunal” substitute “the First-tier Tribunal”;

($b$) in the definition of “official error” for “a Commissioner” substitute “the Upper Tribunal”;

($c$) in the definition of “party to~the proceedings” for “an appeal tribunal” substitute “the First-tier Tribunal”;

($d$) in the definition of “referral” for “an appeal tribunal” substitute “the First-tier Tribunal”; and

($e$) omit the definitions of—
\begin{enumerate}\item[]
(i) “clerk to~the appeal tribunal”;

(ii) “financially qualified panel member”;

(iii) “legally qualified panel member”;

(iv) “medically qualified panel member”;

(v) “out of jurisdiction appeal”;

(vi) “panel”;

(vii) “panel member”;

(viii) “panel member with a disability qualification”; and

(ix) “President”.
\end{enumerate}
\end{enumerate}

\medskip

97.  In regulation~2 (service of notices or documents)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($a$)  omit—
\begin{enumerate}\item[]
(i) “to~the clerk to~the appeal tribunal or”; and

(ii) “by the clerk to~the appeal tribunal or”; and
\end{enumerate}

($b$) in sub-paragraph~($b$)  omit “the clerk to~the appeal tribunal or”.
\end{enumerate}

\medskip

98.  In regulation~3 (revision of decisions)—
\begin{enumerate}\item[]
($a$) in paragraph~(4A) for “in regulation~31, or in a case to~which regulation~32 applies within the time prescribed by that regulation,” substitute “by Tribunal Procedure Rules”; and

($b$) in paragraph~(5A)($b$)  for “an appeal tribunal” substitute “the First-tier Tribunal”.
\end{enumerate}

\medskip

99.  In regulation~3A (revision of child support decisions)—
\begin{enumerate}\item[]
($a$) in paragraph~(1)($cc$)  for “in regulation~31, or in a case to~which regulation~32 applies within the time prescribed by that regulation,” substitute “by Tribunal Procedure Rules”; and

($b$) in paragraphs~(3), (5A)($b$)  and~(6) for “an appeal tribunal” substitute “the First-tier Tribunal”.
\end{enumerate}

\medskip

100.  In regulation~4(6)($b$)  (late application for a revision) for “a Commissioner, a Child Support Commissioner” substitute “the Upper Tribunal”.

\medskip

101.  In regulation~6 (supersession of decisions)—
\begin{enumerate}\item[]
($a$) in paragraph~(2)($c$), for “an appeal tribunal or of a Commissioner” substitute “the First-tier Tribunal or of the Upper Tribunal”; and

($b$) in paragraph~(2)($n$)—
\begin{enumerate}\item[]
(i) for “an appeal tribunal” substitute “the First-tier Tribunal”; and

(ii) for “appeal tribunal” substitute “decision of the First-tier Tribunal”.
\end{enumerate}
\end{enumerate}

\medskip

102.  In regulation~6A(4A) (supersession of child support decisions) for “an appeal tribunal or of a Commissioner” substitute “the First-tier Tribunal or of the Upper Tribunal”.

\medskip

103.  In regulation~6B(1) (circumstances in which a child support decision may not be superseded) for “appeal tribunal or Child Support Commissioner” substitute “the First-tier Tribunal or the Upper Tribunal”.

\medskip

104.  In regulation~7 (date from which a decision superseded under section~10 takes effect)—
\begin{enumerate}\item[]
($a$) in paragraph~(5)—
\begin{enumerate}\item[]
(i) for “an appeal tribunal or a Commissioner” substitute “the First-tier Tribunal or the Upper Tribunal”; and

(ii) for “the appeal tribunal or the Commissioner” substitute “the First-tier Tribunal or the Upper Tribunal”; and
\end{enumerate}

($b$) in paragraph~(33)—
\begin{enumerate}\item[]
(i) for “appeal tribunal or the Commissioner’s” substitute “First-tier Tribunal or the Upper Tribunal’s”; and

(ii) for “Commissioner” substitute “Upper Tribunal”.
\end{enumerate}
\end{enumerate}

\medskip

105.  In regulation~7B (date from which a decision superseded under section~17 of the Child Support Act takes effect)—
\begin{enumerate}\item[]
($a$) in paragraph~(9)—
\begin{enumerate}\item[]
(i) in sub-paragraph~($a$)  for “an appeal tribunal or by a Child Support Commissioner” substitute “the First-tier Tribunal or the Upper Tribunal”;

(ii) for “the appeal tribunal” substitute “the First-tier Tribunal”; and

(iii) for “the Child Support Commissioner” substitute “the Upper Tribunal”; and
\end{enumerate}

($b$) in paragraph~(22A)—
\begin{enumerate}\item[]
(i) for “appeal tribunal or the Commissioner’s” substitute “First-tier Tribunal or the Upper Tribunal’s”; and

(ii) for “of the Commissioner” substitute “of the Upper Tribunal”.
\end{enumerate}
\end{enumerate}

\medskip

106.  In regulation~8(6)($b$)  (effective date for late notifications of change of circumstances) for “a Commissioner” substitute “the Upper Tribunal”.

\medskip

107.  In regulation~9ZA(2) (review of certificates) for “29, 31, 33, 36(2)($a$)(ii)  and~58(1)” substitute “29 and~33”.

\medskip

108.  In regulation~9A(3) (correction of accidental errors) omit “, or the time within which an appeal may be brought under regulation~31(1),”.

\medskip

109.---(1)  Regulation~16 (suspension in prescribed cases) is amended as follows.

(2) In paragraph~(3)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($b$)(i)  for “an appeal tribunal, a Commissioner” substitute “the First-tier Tribunal, the Upper Tribunal”; and

($b$) in sub-paragraph~($b$)(ii)  for “a Commissioner” substitute “the Upper Tribunal”.
\end{enumerate}

(3) In paragraph~(4)—
\begin{enumerate}\item[]
($a$) for “an appeal tribunal, a Commissioner” substitute “the First-tier Tribunal, the Upper Tribunal”;

($b$) in sub-paragraph~($a$)  for “an appeal tribunal decision” substitute “a decision of the First-tier Tribunal”; and

($c$) in sub-paragraph~($b$)—
\begin{enumerate}\item[]
(i) for “an appeal tribunal decision” substitute “a decision of the First-tier Tribunal”; and

(ii) for “leave” in both places substitute “permission”.
\end{enumerate}
\end{enumerate}

\medskip

110.---(1)  Regulation~20 (making of payments which have been suspended) is amended as follows.

(2) In paragraph~(2)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($a$)—
\begin{enumerate}\item[]
(i) for “an appeal tribunal” substitute “the First-tier Tribunal”; and

(ii) for “of one month specified in regulation~53(4)” substitute “specified under Tribunal Procedure Rules”;
\end{enumerate}

($b$) in sub-paragraph~($b$)—
\begin{enumerate}\item[]
(i) for “an appeal tribunal, a Commissioner” substitute “the First-tier Tribunal, the Upper Tribunal”; and

(ii) for “leave” in both places, substitute “permission”; and
\end{enumerate}

($c$) in sub-paragraphs~($c$)  and~($d$)  for “leave”, in each place, substitute “permission”.
\end{enumerate}

(3) In paragraph~(3)—
\begin{enumerate}\item[]
($a$) for “a Commissioner” substitute “the Upper Tribunal”; and

($b$) for “leave”, in each place” substitute “permission”.
\end{enumerate}

\medskip

111.  In regulation~21(4) (decisions involving issues that arise on appeal in other cases) for “leave” substitute “permission”.

\medskip

112.  In regulation~22 (appeals involving issues that arise in other cases) for “leave” substitute “permission”.

\medskip

113.  In regulation~23(4) (child support decisions involving issues that arise on appeal in other cases) for “leave” substitute “permission”.

\medskip

114.  In regulation~24 (child support appeals involving issues that arise in other cases) for “leave” substitute “permission”.

\medskip

115.  In regulation~25 (other persons with a right of appeal) for “an appeal tribunal” substitute “the First-tier Tribunal”.

\medskip

116.  In regulation~26 (decisions against which an appeal lies) for “an appeal tribunal” substitute “the First-tier Tribunal”.

\medskip

117.  In regulation~27 (decisions against which no appeal lies)—
\begin{enumerate}\item[]
($a$) in paragraph~(1) for “an appeal tribunal” substitute “the First-tier Tribunal”; and

($b$) omit paragraph~(3).
\end{enumerate}

\medskip

118.  In regulation~29 (further particulars required relating to~certificate of recoverable benefits or, as the case may be, recoverable lump sum payments appeals or applications)—
\begin{enumerate}\item[]
($a$) in the heading omit “or applications”;

($b$) omit paragraphs~(1) and~(2);

($c$) for paragraph~(3) substitute—
\begin{quotation}
“(3) Where it appears to~the Secretary of State that a notice of appeal in respect of an appeal under the 1997 Act relating to~a certificate of recoverable benefits or, as the case may be, recoverable lump sum payments does not contain the particulars required, the Secretary of State may direct the appellant to~provide such particulars.”;
\end{quotation}

($d$) in paragraph~(4) omit “or application”; and

($e$) in paragraph~(5) omit “or a written statement or summary”.
\end{enumerate}

\medskip

119.  In regulation~30(5) (appeal against a decision which has been replaced or revised) for “appeal tribunal” substitute “First-tier Tribunal”.

\medskip

120.  In regulation~30A (appeals to~appeal tribunals in child support cases) in the heading, for “appeal tribunals” substitute “the First-tier Tribunal”.

\medskip

121.  Omit regulation~31 (time within which an appeal is to~be brought).

\medskip

122.  In regulation~32 (late appeals)—
\begin{enumerate}\item[]
($a$) for paragraphs~(1) to~(3) substitute—
\begin{quotation}
“(1) Where a dispute arises as to~whether an appeal was brought within the time specified under Tribunal Procedure Rules the dispute shall be referred to, and~determined by, the First-tier Tribunal.

(2) The Secretary of State, the Commission or the Board, as the case may be, may treat a late appeal as made in time in accordance with Tribunal Procedure Rules if the conditions in paragraphs~(4) to~(8) are satisfied.”;
\end{quotation}

($b$) for paragraph~(4) substitute—
\begin{quotation}
“(4) An appeal may be treated as made in time if the Secretary of State, the Commission or the Board, as the case may be, is satisfied that it is in the interests of justice.”;
\end{quotation}

($c$) in paragraph~(5)—
\begin{enumerate}\item[]
(i) for “grant an application unless the panel member” substitute “treat the appeal as made in time unless”;

(ii) in sub-paragraphs~($a$)  and~($b$)  omit “to~the application”; and

(iii) for “regulation~31” substitute “Tribunal Procedure Rules”;
\end{enumerate}

($d$) in paragraph~(6), in each place, for “applicant” substitute “appellant”;

($e$) in paragraph~(7)—
\begin{enumerate}\item[]
(i) for “grant the application” substitute “treat the appeal as made in time”; and

(ii) for the words “within which” to~the end, substitute “limit under Tribunal Procedure Rules and~the submission of the notice of appeal, the more compelling should be the special circumstances.”;
\end{enumerate}

($f$) in paragraph~(8)—
\begin{enumerate}\item[]
(i) for “grant an application” substitute “treat the appeal as made in time”;

(ii) in sub-paragraph~($a$)  for “these Regulations” substitute “Tribunal Procedure Rules”; and

(iii) in sub-paragraph~($b$)  for “a Commissioner” substitute “the Upper Tribunal”; and
\end{enumerate}

($g$) omit paragraphs~(9) to~(11).
\end{enumerate}

\medskip

123.---(1)  Regulation~33 (making appeals and~applications) is amended as follows.

(2) For the heading substitute “Notice of Appeal”.

(3) Omit paragraph~(1).

(4) In paragraph~(2) for “In this regulation, “an appropriate office” means” substitute “A notice of appeal made in accordance with Tribunal Procedure Rules and~on a form approved by the Secretary of State, the Commission or the Board, as the case may be, or in such other format as the Secretary of State, the Commission or the Board, as the case may be, accepts, is to~be sent or delivered to~the following appropriate office”.

(5) For paragraph~(3) substitute—
\begin{quotation}
“(3) Except where paragraph~(4) applies, where a form does not contain the information required under Tribunal Procedure Rules the form may be returned by the Secretary of State, the Commission or the Board to~the sender for completion in accordance with the Tribunal Procedure Rules.”.
\end{quotation}

(6) In paragraph~(4)—
\begin{enumerate}\item[]
($a$) omit “or application”; and

($b$) for “paragraph~(1)” substitute “Tribunal Procedure Rules”.
\end{enumerate}

\enlargethispage{-3\baselineskip}

(7) In paragraph~(5)—
\begin{enumerate}\item[]
($a$) for “an appeal or application” substitute “a notice of appeal”;

($b$) after “the appeal” omit “or application”; and

($c$) for “paragraph~(1)” substitute “Tribunal Procedure Rules”.
\end{enumerate}

(8) In paragraph~(6) omit “or application”.

(9) In paragraph~(8)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($a$)  for “a legally qualified panel member” substitute “the First-tier Tribunal”; and

($b$) in sub-paragraph~($b$)—
\begin{enumerate}\item[]
(i) for “panel member” substitute “First-tier Tribunal”; and

(ii) for the words “paragraph~(1)” to~the end, substitute “Tribunal Procedure Rules.”.
\end{enumerate}
\end{enumerate}

(10) In paragraph~(9) for “legally qualified panel member who” substitute “First-tier Tribunal which”.

(11) In paragraph~(10)—
\begin{enumerate}\item[]
($a$) after “where the” insert “notice of”; and

($b$) for “clerk to~an appeal tribunal or to~a legally qualified panel member” substitute “First-tier Tribunal”.
\end{enumerate}

\medskip

124.  Omit regulations~35 to~38 (the panel and~appeal tribunals, and~consideration and~determination of appeals)\footnote{Regulation 36 was amended by: regulation~2 of the Social Security and~Child Support (Decisions and~Appeals) (Amendment) Regulations~1999 (S.I.~1999/1466), regulation~24 of the Social Security and~Child Support (Miscellaneous Amendments) Regulations~2000 (S.I.~2000/1596), regulation~2(4) of the Social Security, Child Support and~Tax Credits (Decisions and~Appeals) Amendment Regulations~2004 (S.I.~2004/3368) and~regulation~2 of the Health and~Social Care (Community Health and~Standards) Act 2003 Consequential Provisions (Recovery of NHS Charges) Order 2007 (S.I.~2007/917).}.

\medskip

125.  In regulation~38A (appeals raising issues for decision by officers of Inland~Revenue)\footnote{Regulation 38A was inserted by regulation~2(4) of the Social Security and~Child Support (Decisions and~Appeals) Amendment No.~3 Regulations~1999 (S.I.~1999/1670) and~amended by the Social Security and~Child Support (Decisions and~Appeals) (Miscellaneous Amendments) Regulations~2002 (S.I.~2002/1379).}—
\begin{enumerate}\item[]
($a$) in paragraph~(1)—
\begin{enumerate}\item[]
(i) for “an appeal tribunal and~it appears to~the appeal tribunal, or legally qualified panel member” substitute “the First-tier Tribunal and~it appears to~the First-tier Tribunal,”; and

(ii) omit “or legally qualified panel member, as the case may be,”; and
\end{enumerate}

\enlargethispage{-3\baselineskip}

($b$) in paragraph~(3)($b$)  for “appeal tribunal” substitute “First-tier Tribunal”.
\end{enumerate}

\medskip

126.  Omit regulations~39 to~47 and~49 to~58 (tribunal procedure)\footnote{Regulations~39, 46 and~47 were amended by regulations~2(5), (6) and~(7) of the Social Security, Child Support and~Tax Credits (Decisions and~Appeals) Amendment Regulations~2004 (S.I.~2004/3368). Regulations~40, 41 and~58 were amended by regulations~25,~26 and~27 of the Tax Credits (Decisions and~Appeals) (Amendment) Regulations~1999 (S.I.~1999/2570). Regulation 41 was also amended by regulation~2(5) of the Social Security and~Child Support (Decisions and~Appeals) Amendment (No 3) Regulations~1999 (S.I.~1999/1670). Regulations~42, 54, 56, 57 and~57A were amended by regulations~25 and~29 to~32 of the Social Security and~Child Support (Miscellaneous Amendments) Regulations~2000 (S.I.~2000/1596). Regulation 44 was amended by regulation~4(2) and~(5) of the Child Support (Consequential Amendments and~Transitional Provisions) Regulations~2001 (S.I.~2001/158). Regulation 45 was substituted by regulation~13 of the Child Support (Decisions and~Appeals) (Amendment) Regulations~2000 (S.I.~2000/3185). Regulations~47,~49, 51, 53, 54, 57, 57A and~58 were amended by regulations~13 to~20 of the Social Security and~Child Support (Decisions and~Appeals) (Miscellaneous Amendments) Regulations~2002 (S.I.~2002/1379). Regulations~49 and~53 to~58 were amended by regulation~2(9) to~(18) of the Social Security, Child Support and~Tax Credits (Miscellaneous Amendments) Regulations~2005 (S.I.~2005/337). Regulation 53 was amended by regulation~10 of the Social Security and~Child Support (Decisions and~Appeals), Vaccine Damage Payments and~Jobseeker’s Allowance (Amendment) Regulations~1999 (S.I.~1999/2677).}.

\medskip

127.  In regulation~58A and~the heading (appeal to~a Commissioner by a partner)—
\begin{enumerate}\item[]
($a$) for “a Commissioner”, in each place, substitute “the Upper Tribunal”; and

($b$) for “an appeal tribunal” substitute “the First-tier Tribunal”.
\end{enumerate}

\medskip

128.  Omit Schedule~3 (qualifications of persons appointed to~the panel)\footnote{Schedule~3 was amended by regulation 2(20) of the Social Security, Child Support and Tax Credits (Miscellaneous Amendments) Regulations 2005 (S.I.~2005/337), regulation 22 of the Social Security and Child Support (Decisions and Appeals) (Miscellaneous Amendments) Regulations 2002 (S.I.~2002/1379) and regulation 2 of the Social Security and Child Support (Decisions and Appeals) (Amendment) Regulations 2008 (S.I.~2008/1957).}.

\section*{\itshape Scotland~Act 1998 (Cross-Border Public Authorities) (Specification) Order 1999}

129.  In the Schedule~to~the Scotland~Act 1998 (Cross-Border Public Authorities) (Specification) Order 1999\footnote{S.I.~1999/1319.}—
\begin{enumerate}\item[]
($a$) omit the entry relating to~“Council on Tribunals”; and

($b$) in the appropriate place in the first column insert “Administrative Justice and~Tribunals Council” and~in the corresponding second column insert; “Section 44 of the Tribunals, Courts and~Enforcement Act (c.~15)”.
\end{enumerate}

\section*{\itshape\sloppy Social Security Commissioners (Procedure) Regulations 1999}

130.  The Social Security Commissioners (Procedure) Regulations~1999\footnote{S.I.~1999/1495 was amended by the Social Security Commissioners (Procedure) (Amendment) Regulations 2000 (S.I.~2000/2854), the Social Security Commissioners (Procedure) (Amendment) Regulations 2001 (S.I.~2001/1095), the Social Security and Child Support Commissioners (Procedure) (Amendment) Regulations 2005 (S.I.~2005/207), the Social Security Commissioners (Procedure) (Amendment) Regulations 2005 (S.I.~2005/870) and paragraph 15 of Schedule~2 to the Housing Benefit and Council Tax Benefit (Consequential Provisions) Regulations 2006 (S.I.~2006/217).} may be cited as the Forfeiture Regulations~1999 and~are amended as follows.

\medskip

131.  In the title to~the Regulations~and~in regulation~1 (citation) for “Social Security Commissioners (Procedure)” substitute “Forfeiture”.

\medskip

132.  Omit regulations~2 (revocation) and~3 (transitional provisions).

\medskip

133.  In regulation~4 (interpretation)—
\begin{enumerate}\item[]
($a$) in paragraph~(1) omit all definitions except for the definition of “the 1998 Act”; and

($b$) omit paragraphs~(2) and~(3).
\end{enumerate}

\medskip

134.  Omit regulations~5 to~13 (general provisions and~applications for leave to~appeal, appeals and~references).

\medskip

135.  In regulation~14 (references under the Forfeiture Act 1982) omit paragraphs~(2) and~(3).

\medskip

136.  Omit regulations~15 to~33 (applications for leave to~appeal, appeals and~references, procedure and~decisions).

\section*{\itshape Scotland~Act 1998 (Cross-Border Public Authorities) (Adaptation of Functions etc) Order 1999}

137.  In Schedule~1 to~the Scotland~Act 1998 (Cross-Border Public Authorities) (Adaptation of Functions etc) Order 1999\footnote{S.I.~1999/1747.} (Cross-Border Public Authorities)—
\begin{enumerate}\item[]
($a$) omit the entry relating to~“Council on Tribunals”;

($b$) in the appropriate place insert “Administrative Justice and~Tribunals Council”; and

($c$) for “Scottish Committee of the Council on Tribunals” substitute “Scottish Committee of the Administrative Justice and~Tribunals Council”.
\end{enumerate}

\section*{\itshape\sloppy Road Traffic (Parking Adjudicators) (England and Wales) Regulations~1999}

138.  For regulation~9(4) of the Road Traffic (Parking Adjudicators) (England and Wales) Regulations~1999\footnote{S.I.~1999/1918.} (procedure at a hearing) substitute—
\begin{quotation}
“(4) Any other adjudicator shall be entitled to~attend the hearing of an appeal whether or not it is in private.”.
\end{quotation}

\section*{\itshape Tax Credits (Payments on Account, Overpayments and~Recovery) (Amendment) Regulations~1999}

139.  In regulation~3($a$)  of the Tax Credits (Payments on Account, Overpayments and~Recovery) (Amendment) Regulations~1999\footnote{S.I.~1999/2571.} (amendments to~the principal regulations) in the definition of “adjudicating authority” for the words “an appeal tribunal” to~the end substitute “the First-tier Tribunal or the Upper Tribunal;”.

\section*{\itshape\sloppy Social Security (Work-focused Interviews for Lone Parents) and Miscellaneous Amendments Regulations 2000}

140.  In regulation~9(3) of the Social Security (Work-focused Interviews for Lone Parents) and~Miscellaneous Amendment Regulations~2000\footnote{S.I.~2000/1926.} (appeals) for “(appeal to~appeal tribunal) to~an appeal tribunal” substitute “(appeal to~First-tier Tribunal) to~the First-tier Tribunal”.

\section*{\itshape\sloppy\hbadness=3758 Child Support (Temporary Compensation Payment Scheme) Regulations 2000}

141.  In regulation~2(1)($c$)  of the Child Support (Temporary Compensation Payment Scheme) Regulations~2000\footnote{S.I.~2000/3174.} (application of the regulations) for “a child support appeal tribunal” substitute “the First-tier Tribunal”.

\section*{\itshape Special Educational Needs Tribunal Regulations~2001}

142.  The Special Educational Needs Tribunal Regulations~2001\footnote{S.I.~2001/600. Regulations 2, 30 and 48 were amended by regulations~2, 3, 19 and 22 of the Special Educational Needs Tribunal (Amendment) Regulations 2002 (S.I.~2002/2787).} are amended as follows.

\medskip

143.  In regulation~2(1) (interpretation) for the definition of “the tribunal” substitute—
\begin{quotation}
““the tribunal” or “the Tribunal” means {\selectlanguage{welsh}Tribiwnlys Anghenion Addysgol Arbennig Cymru} or the Special Educational Needs Tribunal for Wales.”.
\end{quotation}

144.  Omit regulation~30(2)($f$)  (right of a member of the Council on Tribunals to~attend a hearing held in private).

\medskip

145.  After regulation~39 (review of the President’s decision) insert—
\begin{quotation}
\subsection*{“Application for permission to~appeal to~the Upper Tribunal}

39A.---(1)  A party seeking permission to~appeal on a point of law under section~336ZB of the Education Act 1996 (appeal to~the Upper Tribunal) must make a written application to~the tribunal for permission to~appeal.

(2) An application under paragraph~(1) must be sent or delivered to~the Secretary of the Tribunal no later than 28 days after the latest of the dates that the Secretary of the Tribunal sent to~the party making the application—
\begin{enumerate}\item[]
($a$) notification of the decision;

($b$) notification that an application for the decision to~be reviewed has been unsuccessful; or

($c$) notification that the decision has been varied following a review.
\end{enumerate}

(3) An application under paragraph~(1) must—
\begin{enumerate}\item[]
($a$) identify the decision to~which it relates;

($b$) identify the alleged error or errors of law in the decision; and

($c$) state the result the party making the application is seeking.
\end{enumerate}

(4) The tribunal may give directions in relation to~the determination of the application, and~may make its decision on the application with or without a hearing.

(5) The Secretary of the Tribunal must send written notification of the tribunal’s decision on the application to~the parties as soon as practicable.

(6) If the tribunal has refused the application the notification under paragraph~(4) must also include—
\begin{enumerate}\item[]
($a$) the reasons for such refusal; and

($b$) notification of the right to~make an application to~the Upper Tribunal for permission to~appeal and~the time within which, and~the method by which, such application must be made.
\end{enumerate}

(7) The tribunal may give permission to~appeal on limited grounds, but must comply with paragraph~(6) in relation to~any grounds on which it has refused permission.”.
\end{quotation}

\medskip

146.  In regulation~48(1), (2) and~(3) (orders of the court), and~in the title of that regulation, for “Court” substitute “Upper Tribunal or the Court”.

\section*{\itshape Social Security (Crediting and~Treatment of Contributions, and~National Insurance Numbers) Regulations~2001}

\enlargethispage{-3\baselineskip}

147.  In regulation~1 of the Social Security (Crediting and~Treatment of Contributions, and~National Insurance Numbers) Regulations~2001\footnote{S.I.~2001/769. Regulations 1(3) and (4) were inserted by regulation 4(2) of the Social Security (National Insurance Credits) Amendment Regulations 2007 (S.I.~2007/2582).} (citation, commencement and~interpretation)—
\begin{enumerate}\item[]
($a$) in paragraph~(3) for “a Commissioner” substitute “the Upper Tribunal”; and

($b$) in paragraph~(4) omit the entry relating to~“Commissioner”.
\end{enumerate}

\section*{\itshape Housing and~Council Tax Benefit (Decisions and~Appeals) Regulations~2001}

148.  The Housing and~Council Tax Benefit (Decisions and~Appeals) Regulations~2001\footnote{S.I.~2001/1002. Regulation 7(2)($d$) was substituted, and regulation 8(11) was inserted, by regulation 4 of the Social Security and Child Support (Miscellaneous Amendments) Regulations 2003 (S.I.~2003/1050). Regulations 1, 19 and 23 were amended, and regulations~10A and 18 were inserted, by regulations~23, 25 to 28 of the Social Security and Child Support (Decisions and Appeals) (Miscellaneous Amendments) Regulations 2002 (S.I.~2002/1379). Regulation 20(1) was amended by paragraph 8(e) of Schedule~2 to the Social Security (Jobcentre Plus Interviews) Regulations 2002 (S.I.~2002/1703). Regulations 22 and 23 were amended by regulation 3(2) and (3) of the Social Security, Child Support and Tax Credits (Decisions and Appeals) Amendment Regulations 2004 (S.I.~2004/3368) and regulation 23 was amended by regulation 9(3) of the Social Security (Civil Partnership) (Consequential Amendments) Regulations 2005 (S.I.~2005/2878).} are amended as follows.

\medskip

149.  In regulation~1 (citation, commencement and~interpretation)—
\begin{enumerate}\item[]
($a$) in the definition of “appeal” for “an appeal tribunal” substitute “the First-tier Tribunal”;

\enlargethispage{-3\baselineskip}

($b$) in the definition of “official error” for “a Commissioner (construed in accordance with paragraph~23(1) of Schedule~7 to~the Act)” substitute “the Upper Tribunal”; and

($c$) omit the definitions of—
\begin{enumerate}\item[]
(i) “clerk to~an appeal tribunal”;

(ii) “financially qualified panel member”;

(iii) “legally qualified panel member”;

(iv) “panel member”; and

(v) “President”.
\end{enumerate}
\end{enumerate}

\medskip

150.  In regulation~2 (service of notices or documents)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($a$)  omit—
\begin{enumerate}\item[]
(i) “the clerk to~an appeal tribunal,”; and

(ii) “the clerk to~the appeal tribunal,”; and
\end{enumerate}

($b$) in sub-paragraph~($b$)  omit “the clerk to~an appeal tribunal,”.
\end{enumerate}

\medskip

151.  In regulation~4 (revision of decisions)—
\begin{enumerate}\item[]
($a$) in paragraph~(1)($c$)  for “in regulation~18, or in a case to~which regulation~19 applies the time prescribed in that regulation,” substitute “by Tribunal Procedure Rules”; and

($b$) in paragraph~(7)($a$)  for “an appeal tribunal, Commissioner” substitute “the First-tier Tribunal, Upper Tribunal”.
\end{enumerate}

\medskip

152.  In regulation~5(5)($b$)  (late application for a revision) for “a Commissioner” substitute “the Upper Tribunal”.

\medskip

153.  In regulation~7(2)($d$)  (decisions superseding earlier decisions) for “an appeal tribunal or of a Commissioner” substitute “the First-tier Tribunal or of the Upper Tribunal”.

\medskip

154.  In regulation~8 (date from which a decision superseding an earlier decision takes effect)—
\begin{enumerate}\item[]
($a$) in paragraph~(7) for “an appeal tribunal or of a Commissioner” substitute “the First-tier Tribunal or of the Upper Tribunal”; and

($b$) in paragraph~(11)—
\begin{enumerate}\item[]
(i) for “appeal tribunal or the Commissioner’s” substitute “First-tier Tribunal or the Upper Tribunal’s”; and

(ii) for “Commissioner” substitute “Upper Tribunal”.
\end{enumerate}
\end{enumerate}

\medskip

155.  In regulation~9(5)($b$)  (effective date for late notification of change of circumstances) for “a Commissioner” substitute “the Upper Tribunal”.

\medskip

156.  In regulation~10A(3) (correction of accidental errors) omit “, or the time within which an appeal may be brought under regulation~18(1),”.

\medskip

157.  In regulation~11(2) (cases where a relevant authority may suspend)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($b$)(i)  for “an appeal tribunal, a Commissioner” substitute “the First-tier Tribunal, the Upper Tribunal”; and

($b$) in sub-paragraph~($b$)(ii)  for “a Commissioner” substitute “the Upper Tribunal”.
\end{enumerate}

\medskip

158.  In regulation~16 (decisions against which no appeal lies) omit paragraph~(2).

\medskip

159.  In regulation~17(5) (appeal against a decision which has been revised) for “appeal tribunal” substitute “First-tier Tribunal”.

\medskip

160.  Omit regulation~18 (time within which an appeal is brought).

\medskip

161.  In regulation~19 (late appeals)—
\begin{enumerate}\item[]
($a$) omit paragraphs~(1) to~(4);

($b$) for paragraph~(5) substitute—
\begin{quotation}
“(5) Where a dispute arises as to~whether an appeal was brought within the time specified under Tribunal Procedure Rules the dispute shall be referred to, and~determined by, the First-tier Tribunal.

(5A) The relevant authority may treat a late appeal as made in time in accordance with Tribunal Procedure Rules if the relevant authority is satisfied that it is in the interests of justice.”;
\end{quotation}

($c$) in paragraph~(6)—
\begin{enumerate}\item[]
(i) for “(5)($b$)” substitute “(5)”;

(ii) for “grant an application unless the panel member or the relevant authority, as the case may be” substitute “treat the appeal as made in time unless the relevant authority”;

(iii) in sub-paragraphs~($a$)  and~($b$)  omit “to~the application”; and

(iv) for “appeal to~be made” to~the end substitute “appeal notice to~be submitted in accordance with Tribunal Procedure Rules.”;
\end{enumerate}

($d$) in paragraph~(7) for “applicant”, in each place, substitute “appellant”;

($e$) in paragraph~(8)—
\begin{enumerate}\item[]
(i) for “grant the application” substitute “treat the appeal as made in time”; and

(ii) for the words “within which” to~the end, substitute “limit under Tribunal Procedure Rules and~the submission of the notice of appeal, the more compelling should be the special circumstances.”;
\end{enumerate}

($f$) in paragraph~(9)—
\begin{enumerate}\item[]
(i) for “grant an application” substitute “treat the appeal as made in time”;

(ii) in sub-paragraph~($a$)  for “these Regulations” substitute “Tribunal Procedure Rules”; and

(iii) in sub-paragraph~($b$)  for “a Commissioner” substitute “the Upper Tribunal”; and
\end{enumerate}

($g$) omit paragraphs~(10) to~(12).
\end{enumerate}

\medskip

162.---(1)  Regulation~20 (making of appeals and~applications) is amended as follows.

(2) For the heading substitute “Notice of Appeal”.

(3) For paragraph~(1) substitute—
\begin{quotation}
“(1) A notice of appeal made in accordance with Tribunal Procedure Rules must be made on a form approved by the relevant authority, or in such other format as the relevant authority may accept, and~sent or delivered to~the relevant authority.”.
\end{quotation}

(4) For paragraph~(2) substitute—
\begin{quotation}
“(2) Except where paragraph~(3) applies, where a form does not contain the information required under Tribunal Procedure Rules the form may be returned by the relevant authority to~the sender for completion in accordance with the Tribunal Procedure Rules.”.
\end{quotation}

(5) In paragraph~(3)—
\begin{enumerate}\item[]
($a$) omit “or application”; and

($b$) for “paragraph~(1)” substitute “Tribunal Procedure Rules”.
\end{enumerate}

(6) In paragraph~(4)—
\begin{enumerate}\item[]
($a$) for “an appeal or application” substitute “a notice of appeal”;

($b$) after “the appeal” omit “or application”; and

($c$) for “paragraph~(1)” substitute “Tribunal Procedure Rules”.
\end{enumerate}

(7) In paragraph~(5) omit “or application”.

(8) In paragraph~(7)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($a$)  for “a legally qualified panel member” substitute “the First-tier Tribunal”; and

($b$) in sub-paragraph~($b$)—
\begin{enumerate}\item[]
(i) for “panel member” substitute “First-tier Tribunal”; and

(ii) for the words “paragraph~(1)” to~the end, substitute “Tribunal Procedure Rules.”.
\end{enumerate}
\end{enumerate}

(9) In paragraph~(8) for “legally qualified panel member who” substitute “First-tier Tribunal which”.

(10) In paragraph~(9)—
\begin{enumerate}\item[]
($a$) for “the appeal” substitute “the notice of appeal”; and

($b$) for “clerk to~an appeal tribunal or to~a legally qualified panel member” substitute “First-tier Tribunal”.
\end{enumerate}

\medskip

163.  Omit regulations~22 (composition of appeal tribunals) and~23 (procedure in connection with appeals).

\section*{\itshape Social Security (Contributions) Regulations 2001}

164.  In regulation~1(2) of the Social Security (Contributions) Regulations~2001\footnote{S.I.~2001/1004. The definition “the Commissioner” was inserted by regulation 3(2) of the Social Security (Contributions) (Amendment No.~8) Regulations 2007 (S.I.~2007/2520).} (citation, commencement and~interpretation)—
\begin{enumerate}\item[]
($a$) omit the definition of “the Commissioner”; and

($b$) in the definition of “official error” for “a Commissioner” substitute “the Upper Tribunal”.
\end{enumerate}

\section*{\itshape Road User Charging (Enforcement and~Adjudication) (London) Regulations~2001}

165.  In the Schedule~to~the Road User Charging (Enforcement and~Adjudication) (London) Regulations~2001\footnote{S.I.~2001/2313.} omit paragraph~8(4) (admission to~a hearing).

\section*{\itshape Education (Special Educational Needs) (England) (Consolidation) Regulations~2001}

166.  The Education (Special Educational Needs) (England) (Consolidation) Regulations~2001\footnote{S.I.~2001/3455 Regulations 2(1), 16($f$) and 26 were amended, and Parts A and B substituted, by regulations~2, 3 and 14 to 17 of the Education (Special Educational Needs) (England) (Consolidation) (Amendment) Regulations 2006 (S.I.~2006/3346).} are amended as follows.

\medskip

167.  In regulation~2(1) (interpretation) omit the definition of “Tribunal”.

\medskip

168.  In regulation~12(2)($b$)  and~(4)($b$)  (time limits and~prescribed information) for “Tribunal”, in each place, substitute “First-tier Tribunal”.

\medskip

169.  In regulation~16($e$)(iii)  and~($f$)(iii)  (statement of special educational needs) for “Tribunal” substitute “First-tier Tribunal”.

\medskip

170.  In regulation~17 (time limits and~prescribed information) for “Tribunal”, in each place, substitute “First-tier Tribunal”.

\medskip

171.  In regulation~25(1) (compliance with tribunal orders) for “Tribunal” substitute “First-tier Tribunal”.

\medskip

172.  In regulation~26(1) and~(2) (compliance with parents’ requests when an authority concedes an appeal to~the Tribunal) and~in the heading of that regulation, for “Tribunal” substitute “First-tier Tribunal”.

\medskip

173.  In Parts A and~B of Schedule~1—
\begin{enumerate}\item[]
($a$) for the first occurrence in each Part of “Special Educational Needs and~Disability” substitute “First-tier”; and

($b$) in the paragraph~in each Part starting “When you receive”—
\begin{enumerate}\item[]
(i) in the first sentence for “Special Educational Needs and~Disability Tribunal” substitute “First-tier Tribunal, which hears appeals in relation to~decisions on assessments and~statements of special educational needs”;

(ii) for “within two months of getting the final statement” substitute “[\emph{insert here the time limit for appealing to~the First-tier Tribunal}]”;

(iii) for “SENDIST, 2nd Floor Old Hall, Mowden Hall, Staindrop Road \textsc{\lowercase{DL3 9BG}}” substitute “[\emph{insert here the address of the First-tier Tribunal}]”;

(iv) for “0870 241 2555” substitute “[\emph{insert here the telephone number of the First-tier Tribunal}]”; and

(v) for “\url{http://www.sendist.gov.uk/}” substitute “[\emph{insert here the address of the First-tier Tribunal’s website}]”.
\end{enumerate}
\end{enumerate}

\section*{\itshape Race Relations Act 1976 (General Statutory Duty) Order 2001}

174.  In the Schedule~to~the Race Relations Act 1976 (General Statutory Duty) Order 2001\footnote{S.I.~2001/3457.} (bodies and~other persons added after commencement of general statutory duty)—
\begin{enumerate}\item[]
($a$) omit the entry relating to~“Council on Tribunals”; and

($b$) in the appropriate place under the title “Regulatory, audit and~inspection” insert “Administrative Justice and~Tribunals Council”.
\end{enumerate}

\section*{\itshape Race Relations Act 1976 (Statutory Duties) Order 2001}

175.  In Schedule~3 to~the Race Relations Act 1976 (Statutory Duties) Order 2001\footnote{S.I.~2001/3458.} (bodies and~other persons excepted by article~5(5)($b$)) for “Council on Tribunals” substitute “Administrative Justice and~Tribunals Council”.

\section*{\itshape Seeds (National Lists of Varieties) Regulations~2001}

176.  In regulation~16(4)($c$)(ii)  of the Seeds (National Lists of Varieties) Regulations~2001\footnote{S.I.~2001/3510.} (representations and~hearings) for “Council on Tribunals” substitute “Administrative Justice and~Tribunals Council”.

\section*{\itshape Goods Vehicles (Enforcement Powers) Regulations~2001}

177.  In regulation~11 of the Goods Vehicles (Enforcement Powers) Regulations~2001\footnote{S.I.~2001/3981.} (hearings) omit paragraph~(7).

\section*{\itshape\sloppy Social Security (Jobcentre Plus Interviews) Regulations 2002}

178.  In regulation~15(3) of the Social Security (Jobcentre Plus Interviews) Regulations~2002\footnote{S.I.~2002/1703.} (appeals) for “an appeal tribunal” substitute “the First-tier Tribunal”.

\section*{\itshape\sloppy\hbadness=10000 Child Support Appeals (Jurisdiction of Courts) Order 2002}

179.  The Child Support Appeals (Jurisdiction of Courts) Order 2002\footnote{S.I.~2002/1915.} is amended as follows.

\medskip

180.  In article~3 for “an appeal tribunal” substitute “the First-tier Tribunal”.

\medskip

181.  For article~5 substitute—
\begin{quotation}
“5.  Regulation~32 of Regulations~and~Rule 23 of the Tribunal Procedure (First-tier Tribunal) (Social Entitlement Chamber) Rules 2008 apply to~appeals brought under this Order as if the word “Tribunal” is read as “court”.”.
\end{quotation}

\section*{\itshape\sloppy\hbadness=1924 Special Educational Needs and Disability Tribunal (General Provisions and Disability Claims Procedure) Regulations 2002}

182.  The Special Educational Needs and~Disability Tribunal (General Provisions and~Disability Claims Procedure) Regulations~2002\footnote{S.I.~2002/1985.} are amended as follows.

\medskip

183.  In regulation~1(2) and~(3) (application) for “Special Educational Needs and~Disability Tribunal” substitute “tribunal”.

\medskip

184.  In regulation~2 (interpretation) for the definition of “the tribunal” substitute—
\begin{quotation}
““the tribunal” means {\selectlanguage{welsh}Tribiwnlys Anghenion Addysgol Arbennig Cymru} or the Special Educational Needs Tribunal for Wales referred to~in section~333(1ZA) of the 1996 Act (constitution of Welsh tribunal);”.
\end{quotation}

\medskip

185.  In regulation~3 (members of lay panel) for “the Secretary of State as respects England, or the National Assembly for Wales as respects Wales, is” substitute “the Welsh Ministers are”.

\medskip

186.  In regulation~4 (establishment of tribunals) for “Special Educational Needs and~Disability Tribunal” substitute “tribunal”.

\medskip

187.  In regulation~30 (right of a member of the Council on Tribunals to~attend a hearing held in private) omit paragraph~(2)($f$).

\medskip

188.  After regulation~39 (review of the President’s decision) insert—
\begin{quotation}
\subsection*{“Application for permission to~appeal to~the Upper Tribunal}

39A.---(1)  A party seeking permission to~appeal on a point of law under section~336ZB of the Education Act 1996 (appeal to~the Upper Tribunal) must make a written application to~the tribunal for permission to~appeal.

(2) An application under paragraph~(1) must be sent or delivered to~the Secretary of the Tribunal no later than 28 days after the latest of the dates that the Secretary of the Tribunal sent to~the party making the application—
\begin{enumerate}\item[]
($a$) notification of the decision;

($b$) notification that an application for the decision to~be reviewed has been unsuccessful; or

($c$) notification that the decision has been varied following a review.
\end{enumerate}

(3) An application under paragraph~(1) must—
\begin{enumerate}\item[]
($a$) identify the decision to~which it relates;

($b$) identify the alleged error or errors of law in the decision; and

($c$) state the result the party making the application is seeking.
\end{enumerate}

(4) The tribunal may give directions in relation to~the determination of the application, and~may make its decision on the application with or without a hearing.

(5) The Secretary of the Tribunal must send written notification of the tribunal’s decision on the application to~the parties as soon as practicable.

(6) If the tribunal has refused the application the notification under paragraph~(4) must also include—
\begin{enumerate}\item[]
($a$) the reasons for such refusal; and

($b$) notification of the right to~make an application to~the Upper Tribunal for permission to~appeal and~the time within which, and~the method by which, such application must be made.
\end{enumerate}

(7) The tribunal may give permission to~appeal on limited grounds, but must comply with paragraph~(6) in relation to~any grounds on which it has refused permission.”.
\end{quotation}

\medskip

189.  In regulation~48(1), (2) and~(3) (orders of the court), and~in the title of that regulation, for “Court” substitute “Upper Tribunal or the Court”.

\section*{\itshape Tax Credits (Payments by the Commissioners) Regulations~2002}

190.  In regulation~11 of the Tax Credits (Payments by the Commissioners) Regulations~2002 (postponement of payment)\footnote{S.I.~2002/2173.}—
\begin{enumerate}\item[]
($a$) in paragraphs~(2) and~(4), for “an appeal tribunal, a” substitute “the appropriate tribunal, the Upper Tribunal, the Northern Ireland”;

($b$) in paragraph~(4)($b$), for “an appeal tribunal” substitute “the appropriate tribunal”;

($c$) in paragraph~(5) for “Appeal tribunal” substitute “Appropriate tribunal”; and

($d$) in paragraph~(6) for “Social” substitute “Northern Ireland~Social”.
\end{enumerate}

\section*{\itshape Tax Credits (Appeals) Regulations~2002}

191.  The Tax Credits (Appeals) Regulations~2002\footnote{S.I.~2002/2926.} are amended as follows.

\medskip

192.  In regulation~2 (interpretation)—
\begin{enumerate}\item[]
($a$) in the definition of “appeal tribunal” omit sub-paragraph~($a$)  (and~the following “or” and~“($b$)”); and

($b$) in the definition of “Social Security Commissioner” omit sub-paragraph~($a$)  (and~the following “and” and~“($b$)”).
\end{enumerate}

\medskip

193.  In regulation~3 (application of section~54 of the Taxes Management Act 1970)—
\begin{enumerate}\item[]
($a$) in paragraphs~(1) and~(2) after “appeal tribunal” insert “or the First-tier Tribunal”; and

($b$) in paragraph~(8), in the inserted subsection~(6), omit sub-paragraph~($a$)  (and~the following “and” and~“($b$)”).
\end{enumerate}

\medskip

194.  In regulation~4 (application of section~12 of the 1998 Act and~article~13 of the 1998 Order)—
\begin{enumerate}\item[]
($a$) in paragraph~(1) after “appeal tribunal”, in both places, insert “or the First-tier Tribunal”; and

($b$) in paragraph~(2), in the substituted paragraph~(1), for “an appeal tribunal” substitute “the First-tier Tribunal”.
\end{enumerate}

\medskip

195.  In regulation~5(1) (application of section~13 of the 1998 Act and~article~14 of the 1998 Order) after “appeal tribunal” insert “or the First-tier Tribunal”.

\medskip

196.  In regulation~6 (application of section~14 of the 1998 Act and~article~15 of the 1998 Order)—
\begin{enumerate}\item[]
($a$) in paragraph~(1)—
\begin{enumerate}\item[]
(i) for “14(1) to~(10)” substitute “14(2) to~(6)”; and

(ii) after “appeal tribunal” insert “or the First-tier Tribunal”; and
\end{enumerate}

($b$) omit paragraph~(2)($a$).
\end{enumerate}

\medskip

197.  In regulation~7—
\begin{enumerate}\item[]
($a$) in paragraph~(1) omit “Section 14(11) and~(12) of, and~Schedule~4 to, the 1998 Act and”; and

($b$) in paragraph~(2) omit “in subsection~(11) of that section~and”.
\end{enumerate}

\medskip

198.  In regulation~8 (application of section~15 of the Social Security Act 1998)—
\begin{enumerate}\item[]
($a$) for “appeal from Commissioner on a point of law” substitute “applications for permission to~appeal against a decision of the Upper Tribunal”; and

($b$) for “a Social Security Commissioner” substitute “the Upper Tribunal”.
\end{enumerate}

\medskip

199.  For regulation~9(2) (application of section~16 of the 1998 Act or Article 16 of the 1998 Order) substitute—
\begin{quotation}
“(2) Omit subsection~(3) of section~16.”.
\end{quotation}

\medskip

200.  In regulation~10 (application of section~17 of the 1998 Act or article~17 of the 1998 Order)—
\begin{enumerate}\item[]
($a$) in paragraph~(1) after “appeal tribunal” insert “the First-tier Tribunal, the Upper Tribunal”; and

($b$) in paragraph~(2), in the substituted subsection~(1)—
\begin{enumerate}\item[]
(i) after sub-paragraph~($b$)  insert—
\begin{quotation}
“($c$) any provision made by or under Chapter~II of Part I of the Tribunals, Courts and~Enforcement Act 2007,”; and
\end{quotation}

(ii) for “an appeal tribunal or lies to~a Commissioner” substitute “the First-tier Tribunal or lies to~the Upper Tribunal”.
\end{enumerate}
\end{enumerate}

\medskip

201.  In regulation~11 (application of section~28 of the 1998 Act and~article~28 of the 1998 Order)—
\begin{enumerate}\item[]
($a$) in the heading omit “section~28 of the 1998 Act and”;

($b$) in paragraph~(1) omit “Section 28 of the 1998 Act and”;

($c$) omit paragraph~(2); and

($d$) in paragraph~(4) omit “subsection~(1A) of that section~and”.
\end{enumerate}

\medskip

202.  In regulation~12(2)($a$)  (applications of section~39 of the 1998 Act and~article~39 of the 1998 Order) for “after the definition of “appeal tribunal”” substitute “in the appropriate place”.

\section*{\itshape\sloppy Education (Pupil Exclusions and Appeals) (Maintained Schools) (England) Regulations 2002}

203.  For paragraph~11 of the Schedule~to~the Education (Pupil Exclusions and~Appeals) (Maintained Schools) (England) Regulations~2002\footnote{S.I.~2002/3178.} (procedure on an appeal) substitute—
\begin{quotation}
“11.  Appeals shall be heard in private except when the local education authority direct otherwise; but if the panel so direct, one member of the local education authority may attend, as an observer, any hearing of an appeal by an appeal panel.”.
\end{quotation}

\section*{\itshape\sloppy Tax Credits (Appeals) (No.~2) Regulations 2002}

204.  The Tax Credits (Appeals) (No.~2) Regulations~2002\footnote{S.I.~2002/3196. Regulation 9 was amended by paragraph 36(3) of Schedule 3 to the Civil Partnership (Pensions, Social Security and Child Support) (Consequential, etc.\ Provisions) Order 2005 (S.I.~2005/2877). Regulations 12, 16 and 17 were amended by regulation 6 of the Social Security, Child Support and Tax Credits (Decisions and Appeals) Amendment Regulations 2004 (S.I.~2004/3368). Regulations 18 and 21 to 27 were amended, and regulation 26A was inserted, by regulation 4(3) to (11) of the Social Security, Child Support and Tax Credits (Miscellaneous Amendments) Regulations 2005 (S.I.~2005/337).} are amended as follows.

\medskip

205.  In regulation~1(3) (citation, commencement, duration and~interpretation) omit the definitions of—
\begin{enumerate}\item[]
($a$) “a case”;

($b$) “clerk to~the appeal tribunal”;

($c$) “the date of notification”;

($d$) “decision”;

($e$) “financially qualified panel member”;

($f$) “legally qualified panel member”;

($g$) “medically qualified panel member”;

($h$) “panel”;

($i$) “panel member”;

($j$) “panel member with a disability qualification”;

($k$) “penalty determination”;

($l$) “penalty proceedings”; and

($m$) “President”.
\end{enumerate}

\medskip

206.  In regulation~2 (service of notices or documents)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($a$)  omit—
\begin{enumerate}\item[]
(i) “to~the clerk to~the appeal tribunal or”; and

(ii) “by the clerk of the appeal tribunal or”; and
\end{enumerate}

($b$) in sub-paragraph~($b$)  omit “the clerk to~the appeal tribunal or”.
\end{enumerate}

\medskip

207.  In regulation~3 (other persons with a right of appeal or a right to~make an application for a direction) for “an appeal tribunal” substitute “the First-tier Tribunal”.

\medskip

208.  In regulation~4 (time within which appeal is to~be brought) for “a legally qualified panel member” substitute “the First-tier Tribunal”.

\medskip

209.  In regulation~5 (late appeals)—
\begin{enumerate}\item[]
($a$) in paragraph~(1)—
\begin{enumerate}\item[]
(i) for “The time within which an appeal must be brought may be extended” substitute “The Board may treat a late appeal as made in time”; and

(ii) for “(2)” substitute “(4)”;
\end{enumerate}

($b$) omit paragraphs~(2) and~(3);

($c$) for paragraph~(4) substitute—
\begin{quotation}
“(4) An appeal may be treated as made in time if the Board is satisfied that it is in the interests of justice.”;
\end{quotation}

($d$) in paragraph~(5)—
\begin{enumerate}\item[]
(i) for “grant the application unless the panel member is, or the Board are, as the case may be,” substitute “treat the appeal as made in time unless the Board are”; and

(ii) in sub-paragraphs~($a$)  and~($b$)  omit “to~the application”;
\end{enumerate}

($e$) in paragraph~(6) for “applicant” substitute “appellant”;

($f$) in paragraph~(7)—
\begin{enumerate}\item[]
(i) for “grant an application” substitute “treat the appeal as made in time”; and

(ii) for the words “making of the application” to~the end substitute “submission of the notice of appeal, the more compelling should be the special circumstances.”;
\end{enumerate}

($g$) in paragraph~(8)—
\begin{enumerate}\item[]
(i) for “grant an application” substitute “treat the appeal as made in time”; and

(ii) in sub-paragraph~($b$)  for “a Commissioner” substitute “the Upper Tribunal”; and
\end{enumerate}

($h$) omit paragraphs~(9) to~(11).
\end{enumerate}

\medskip

210.  Omit regulations~6, 7 and~9 to~27 (procedure on appeal).

\section*{\itshape Child Benefit and~Guardian’s Allowance Administration Regulations~2003}

211.  In regulation~2 of the Child Benefit and~Guardian’s Allowance Administration Regulations~2003\footnote{S.I.~2003/492.} (interpretation) in the definition of “adjudicating authority”—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($b$)  omit “Chapter~I of Part I of the Social Security Act 1998 or”;

($b$) in sub-paragraph~($c$)  omit “within the meaning of section~39(1) of that Act or”; and

($c$) after sub-paragraph~($c$)  insert—
\begin{quotation}
“($d$) the First-tier Tribunal or the Upper Tribunal;”.
\end{quotation}
\end{enumerate}

\section*{\itshape Child Benefit and~Guardian’s Allowance (Decisions and~Appeals) Regulations~2003}

212.  The Child Benefit and~Guardian’s Allowance (Decisions and~Appeals) Regulations~2003\footnote{S.I.~2003/916. Regulation 13(2) was amended, and paragraph 9A of regulation 16 was inserted, by the Child Benefit and Guardian’s Allowance (Miscellaneous Amendments) Regulations 2005 (S.I.~2005/343).} are amended as follows.

\medskip

213.  In regulation~2(1) (interpretation)—
\begin{enumerate}\item[]
($a$) in the definition of “appeal tribunal” omit sub-paragraph~($a$)  (and~the following “($b$)”);

($b$) in the definition of “clerk to~the appeal tribunal” omit sub-paragraph~($a$)  (and~the following “($b$)”);

($c$) in the definition of “Commissioner” omit sub-paragraph~($a$)  (and~the following “($b$)”);

($d$) in the definition of “legally qualified panel member” omit sub-\hspace{0pt}paragraph~($a$)  (and~the following “($b$)”); and

($e$) in the definition of “panel” omit “section~6 or”.
\end{enumerate}

\medskip

214.  In regulation~6(6)($b$)  (late application for revision of decisions) after “a Commissioner” insert “, the Upper Tribunal”.

\medskip

215.  In regulation~8 (Revision of decisions against which there has been an appeal)—
\begin{enumerate}\item[]
($a$) in paragraph~(2)—
\begin{enumerate}\item[]
(i) after “an appeal tribunal” insert “or the First-tier Tribunal”; and

(ii) for “regulation~29 applies within the time prescribed by that regulation” substitute “regulations~29 and~29A apply within the time prescribed by those regulations”; and
\end{enumerate}

($b$) in paragraph~(3)($b$), ($c$)  and~($d$)  after “an appeal tribunal” insert “or the First-tier Tribunal”.
\end{enumerate}

\medskip

216.  In regulation~10(3) (revision of decisions arising from official error etc) after “a Commissioner” insert “, the Upper Tribunal”.

\medskip

217.  In regulation~13(2)($c$)  (cases and~circumstances in which superseding decisions may be made) after “an appeal tribunal” insert “the First-tier Tribunal, the Upper Tribunal”.

\medskip

218.  In regulation~16 (date as from which superseding decisions take effect)—
\begin{enumerate}\item[]
($a$) in paragraphs~(7) and~(8) after “an appeal tribunal”, in each place, insert “the First-tier Tribunal, the Upper Tribunal”;

($b$) in paragraph~(8) after “determination of” insert “the Upper Tribunal,”; and

($c$) in paragraph~(9A) after “a Commissioner” insert “, the Upper Tribunal”.
\end{enumerate}

\medskip

219.  In regulation~17(6)($b$)  (effective date for late notifications of change of circumstances) after “a Commissioner” insert “, the Upper Tribunal”.

\medskip

220.  In regulation~18 (suspension in prescribed cases)—
\begin{enumerate}\item[]
($a$) in paragraph~(3)—
\begin{enumerate}\item[]
(i) in sub-paragraph~($a$)  after “an appeal tribunal,” insert “the First-tier Tribunal, the Upper Tribunal,”; and

(ii) in sub-paragraph~($b$)  after “a Commissioner” insert “, the Upper Tribunal”;
\end{enumerate}

($b$) in paragraph~(4)—
\begin{enumerate}\item[]
(i) after “where an appeal tribunal,” insert “the First-tier Tribunal, the Upper Tribunal,”;

(ii) in sub-paragraphs~($a$), ($b$)  and~($c$)  after “appeal tribunal” insert “or First-tier Tribunal”; and

(iii) in sub-paragraph~($c$)  after “leave”, in both places, insert “or permission”; and
\end{enumerate}

($c$) in paragraph~(5)—
\begin{enumerate}\item[]
(i) in sub-paragraph~($a$)  after “appeal tribunal” insert “or First-tier Tribunal”; and

(ii) in sub-paragraph~($b$)  after “leave” insert “or permission”.
\end{enumerate}
\end{enumerate}

\medskip

221.  In regulation~21 (making of payments which have been suspended)—
\begin{enumerate}\item[]
($a$) in paragraph~(3)—
\begin{enumerate}\item[]
(i) in sub-paragraph~($a$)  after “an appeal tribunal” insert “or the First-tier Tribunal”;

(ii) in sub-paragraph~($b$)  after “an appeal tribunal,” insert “the First-tier Tribunal, the Upper Tribunal”; and

(iii) in sub-paragraphs~($b$)  to~($d$)  after “leave”, in each place, insert “or permission”; and
\end{enumerate}

($b$) in paragraph~(4)—
\begin{enumerate}\item[]
(i) after “Commissioner” insert “, the Upper Tribunal”; and

(ii) after “leave”, in each place, insert “or permission”.
\end{enumerate}
\end{enumerate}

\medskip

222.  In regulation~23 (appeals involving issues that arise on appeal in other cases) after “leave” insert “or permission”.

\medskip

223.  In regulation~25(1) (decisions against which no appeal lies) after “appeal tribunal” insert “or to~the First-tier Tribunal”.

\medskip

224.  In regulation~28—
\begin{enumerate}\item[]
($a$) in paragraph~(1) after “appeal tribunal” insert “or the First-tier Tribunal”;

($b$) in paragraph~(3) after “member” insert “or, as the case may be, the First-tier Tribunal”; and

($c$) in paragraph~(4) after “29” insert “or, as the case may be, regulation~29A”.
\end{enumerate}

\medskip

225.  In regulation~29 (late appeals)—
\begin{enumerate}\item[]
($a$) in the heading after “appeals” insert “to~the appeal tribunal”; and

($b$) in paragraph~(1) after “brought” insert “to~an appeal tribunal”.
\end{enumerate}

\medskip

226.  After regulation~29 (late appeals to~an appeal tribunal) insert—
\begin{quotation}
\subsection*{“Late appeals to~the First-tier Tribunal}

29A.    In respect of an appeal to~the First-tier Tribunal, the Board may treat a late appeal as made in time in accordance with Tribunal Procedure Rules if the Board is satisfied that it is in the interests of justice, but no appeal shall in any event be brought more than one year after the expiration of the last day for appealing under regulation~28.”. 
\end{quotation}

\medskip

227.  In regulation~30 (interests of justice)—
\begin{enumerate}\item[]
($a$) in paragraph~(1)—
\begin{enumerate}\item[]
(i) after “29” insert “and~regulation~29A”;

(ii) after “grant an application” substitute “or, as the case may be, treat the appeal as made in time”;

(iii) omit “under that regulation”; and

(iv) in sub-paragraphs~($a$)  and~($b$)  omit “to~the application”.
\end{enumerate}

($b$) in paragraph~(4)—
\begin{enumerate}\item[]
(i) after “29” insert “or, as the case may be, treat the appeal as made in time under regulation~29A”; and

(ii) after “making of the application” insert “or, as the case may be, submission of a notice of appeal”; and
\end{enumerate}

($c$) in paragraph~(5)—
\begin{enumerate}\item[]
(i) after “29” insert “or, as the case may be, treat the appeal as made in time under regulation~29A”; and

(ii) in sub-paragraph~($b$)  after “a Commissioner” insert “, the Upper Tribunal”.
\end{enumerate}
\end{enumerate}

\medskip

228.  In regulation~31 (making of appeals or applications)—
\begin{enumerate}\item[]
($a$) after paragraph~(1) insert—
\begin{quotation}
“(1A) A notice of appeal to~the First-tier Tribunal made in accordance with Tribunal Procedure Rules must be made on a form approved by the Board, or in such other format as the Board may accept.

(1B) Except where paragraph~(3) applies, in respect of an appeal to~the First-tier Tribunal, where a form does not contain the information required under Tribunal Procedure Rules the form may be returned by the Board to~the sender for completion in accordance with the Tribunal Procedure Rules.”.
\end{quotation}

($b$) in paragraph~(2) for “An Approved” substitute “In respect of an appeal to~the appeal tribunal an approved”;

($c$) in paragraphs~(3) and~(4) after “paragraph~(1)” insert “or, as the case may be, Tribunal Procedure Rules”;

($d$) in paragraph~(7)—
\begin{enumerate}\item[]
(i) after “panel member who” insert “, or, as the case may be, the First-tier Tribunal which,”; and

(ii) in sub-paragraph~($a$)  after “paragraph~(1)” insert “or, as the case may be, Tribunal Procedure Rules”; and
\end{enumerate}

($e$) in paragraph~(8) after “panel member who” insert “, or, as the case may be, First-tier Tribunal which,”.
\end{enumerate}

\medskip

229.  In regulation~32 (discontinuing action on appeals)—
\begin{enumerate}\item[]
($a$) after “appeal to~an appeal tribunal” insert “or to~the First-tier Tribunal”; and

($b$) in sub-paragraph~($a$)  after “panel member” insert “or, as the case may be, the First-tier Tribunal”.
\end{enumerate}

\section*{\itshape\sloppy\hbadness=1881 Education (Prohibition from Teaching or Working with Children) Regulations~2003}

230.  The Education (Prohibition from Teaching or Working with Children) Regulations~2003\footnote{S.I.~2003/1184. Regulation 10A was inserted by regulation 10 of the Education (Prohibition from Teaching or Working with Children) Regulations 2007 (S.I.~2007/195).} are amended as follows.

\medskip

231.  In regulation~2 (interpretation) omit the definition of “Tribunal”.

\medskip

232.  In regulation~10(1), (2) and~(3) (review by the tribunal), and~in the title of that regulation, for “Tribunal” substitute “First-tier Tribunal”.

\medskip

233.  In regulation~10A(2) and~(3) for “Tribunal” substitute “First-tier Tribunal”.

\medskip

234.  In regulation~11(1) and~(5) for “Tribunal” substitute “First-tier Tribunal”.

\medskip

235.  In regulation~12(1) (appeals) for “Tribunal” substitute “First-tier Tribunal”.

\medskip

236.  In regulation~13(1) and~(2) (the tribunal’s powers), and~in the title of that regulation, for “Tribunal” substitute “First-tier Tribunal”.

\section*{\itshape\sloppy Social Security (Jobcentre Plus Interviews for Partners) Regulations~2003}

237.  In regulation~14(3) of the Social Security (Jobcentre Plus Interviews for Partners) Regulations~2003\footnote{S.I.~2003/1886.} (appeals) for “an appeal tribunal” substitute “the First-tier Tribunal”.

\section*{\itshape\sloppy\hbadness=1107 Leasehold Valuation Tribunals (Procedure) (England) Regulations~2003}

238.  For regulation~21 of the Leasehold Valuation Tribunals (Procedure) (England) Regulations~2003\footnote{S.I.~2003/2099.} (attendance by member of Council on Tribunals) substitute—
\begin{quotation}
\subsection*{“Attendance by member of Administrative Justice and~Tribunals Council}

21.  A member of the Administrative Justice and~Tribunals Council, who is acting in that capacity, may attend any inspection for which any necessary consent has been obtained.”.
\end{quotation}

\section*{\itshape\sloppy Social Security (Incapacity Benefit Work-\hspace{0pt}focused Interviews) Regulations 2003}

239.  In regulation~12(3) of the Social Security (Incapacity Benefit Work-focused Interviews) Regulations~2003\footnote{S.I.~2003/2439.} (appeals) for “(appeal to~appeal tribunal) to~an appeal tribunal” substitute “(appeal to~First-tier Tribunal) to~the First-tier Tribunal”.

\vfill

\section*{\itshape\sloppy\hbadness=3525 Employment Tribunals (Constitution and Rules of Procedure) Regulations 2004}

240.  The Employment Tribunals (Constitution and~Rules of Procedure) Regulations~2004\footnote{S.I.~2004/1861. Regulation 2 was amended by article~2 of and paragraphs 73, 74(1) to (4) of Schedule 1 to the Lord Chancellor (Transfer of Functions and Supplementary Provisions) Order 2006 (S.I.~2006/680). Regulations 3(1) and (3) and 15(1), and paragraphs 8(2) and 48(6) of Schedule 1 were substituted, and Schedule 6 was inserted, by regulations~2(1),~(4),~(5), (6)($a$), (9)($a$) and ($d$) and (11) of the Employment Tribunals (Constitution and Rules of Procedure) (Amendment) Regulations 2004 (S.I.~2004/2351). Paragraphs 38(2), 39(1) and 43(1) of Schedule 1 were amended by regulation 2(4)($i$) of the Employment Tribunals (Constitution and Rules of Procedure) (Amendment) (No.~2) Regulations 2005 (S.I.~2005/1865).} are amended as follows.

\medskip

241.  In regulation~2(1) (interpretation)—
\begin{enumerate}\item[]
($a$) omit the definition of “chairman”;

($b$) after the definition of “Employment Act” insert—
\begin{quotation}
““Employment Judge” has the meaning given in section~3A of the Employment Tribunals Act;”;
\end{quotation}

($c$) in the definitions of “Employment Tribunal Office”, “Regional Chairman”, and~“tribunal” for “chairman”, in each place, substitute “Employment Judge”;

($d$) in the definition of “hearing”—
\begin{enumerate}\item[]
(i) for “a chairman” substitute “an Employment Judge; and

(ii) for “the chairman” substitute “the Employment Judge”; and
\end{enumerate}

($e$) in the definitions of “panel of chairmen” and~“Regional Chairman” for “chairmen” substitute “Employment Judges”.
\end{enumerate}

\medskip

242.  In regulation~3 (overriding objective)—
\begin{enumerate}\item[]
($a$) in paragraph~(1) for “chairmen” substitute “Employment Judges”; and

($b$) in paragraphs~(3) and~(4) for “chairman” substitute “Employment Judge”.
\end{enumerate}

\medskip

243.  In regulation~4(1) and~(2) (President of employment tribunals) for “chairmen” substitute “Employment Judges”.

\medskip

244.  In regulation~5(2) (establishment of employment tribunals)—
\begin{enumerate}\item[]
($a$) for “Chairman” substitute “Employment Judge”; and

($b$) for “chairmen” substitute “Employment Judges”.
\end{enumerate}

\medskip

245.  In regulation~6 (regional chairmen)—
\begin{enumerate}\item[]
($a$) for “chairmen”, in each place (including the heading), substitute “Employment Judges”; and

($b$) for “chairman”, in each place, substitute “Employment Judge”.
\end{enumerate}

\medskip

246.  In regulation~7 (Vice President) for “chairmen”, in each place, substitute “Employment Judges”.

\medskip

247.  In regulation~8(3)($a$), (4) and~(5) (panels of members of tribunals---general) for “chairmen” substitute “Employment Judges”.

\medskip

248.  In regulation~9 (composition of tribunals---general)—
\begin{enumerate}\item[]
($a$) in paragraph~(1) for “chairmen” substitute “Employment Judges”;

($b$) in paragraphs~(1) and~(2) for “a chairman” substitute “an Employment Judge”; and

($c$) in paragraphs~(1) to~(4) for “chairman” in each place, substitute “Employment Judge”.
\end{enumerate}

\medskip

249.  In regulation~10($a$)  (panels of members of tribunals---national security proceedings) for “chairmen”, in both places, substitute “Employment Judges”.

\medskip

250.  In regulation~11 (composition of tribunals---national security proceedings)—
\begin{enumerate}\item[]
($a$) for “Chairman”, in each place, substitute “Employment Judge”; and

($b$) for “a chairman”, in each place, substitute “an Employment Judge”.
\end{enumerate}

\medskip

251.  In regulation~13 (practice directions) for “chairmen” substitute “Employment Judges”.

\medskip

252.  In regulation~15(1) and~(4) (calculation of time) for “a chairman” substitute “an Employment Judge”.

\medskip

253.  In regulation~16(2) (application of Schedules 1 to 5 to~proceedings) for “a chairman” substitute “an Employment Judge”.

\medskip

254.  In regulation~17(2) (register) for “chairman” substitute “Employment Judge”.

\medskip

255.  In Schedule~1 (the employment tribunal rules of procedure)—
\begin{enumerate}\item[]
($a$) in the headings of rules 12 and~31 for “chairman” substitute “Employment Judge”;

($b$) in rules 1(8), 3(3), (7) and~(8), 6(3) and~(6), 7(2), 8(1),(2)($b$)  and~(4), 10(1), 11(2) and~(6), 12, 13(1), 14(1), 17(1), 18(1), (3), (4) and~(7), 19(1), 20(1) and~(4), 22(8), 23(2), 25(5), 27(7), 28(2), 30(5), 33(1), (3) and~(5), 34(1), 35(1), 36(3), 46(2), 50(1) and~(3), 52($b$), 60(2) and~61(1) for “a chairman”, in each place, substitute “an Employment Judge”;

($c$) in rules 3(3), (4), (5) and~(9), 4(4), 6(3) to~(5), 8(3), 10(1), (2)($f$),~($k$)  and~($r$)  and~(8), 11(2) and~(3), 14(2), (3) and~(6), 15(1), 16, 18(2), (5),~(7)($f$)  and~(9), 19(1), 20(1) to~(3) and~(4)($b$), 23(2), 27(1), 28(3) and~(4), 29(1), 30(1), (2), (4) and~(6)($a$), 31, 32(2), 33(4), (6) and~(7), 34(5), 35(3) and~(4), 36, 37(1), 38(1), (2), (7), (9) and~(10), 39(1), 40(1), (2) and~(4), 41(2), 42(1), (5), (7) and~(8), 43(1), 44(1), (2) and~(4), 45(1), (2) and~(3), 46, 47(1) and~(2)($b$), 48(1), (2), (6), (7) and~(9), 49, 50(2), (6) to~(10), 52, 54, 55(1), 57(1) and~(3), 58, 60(1) and~61(4)($h$)(ii)  and~(6) for “chairman”, in each place, substitute “Employment Judge”;

($d$) in rules 13(3) and~28(1) for “Chairmen” substitute “Employment Judges”; and

($e$) in rule 16(2) omit the words from “A member of the Council on Tribunals” to~the end.
\end{enumerate}

\medskip

256.  In Schedule~2 (the employment tribunal (national security) rules of procedure)—
\begin{enumerate}\item[]
($a$) in rules 6(1) and~10(3) for “a chairman”, in each place, substitute “an Employment Judge”;

($b$) in rules 3(1)($b$), (2) and~(3), 4(2), 6, 8(1), (3) to~(5) and~(7), 9 and~10(1),~(3) and~(4) for “chairman”, in each place, substitute “Employment Judge”; and

($c$) in rule 9(2) for “Council on Tribunals” substitute “Administrative Justice and~Tribunals Council”.
\end{enumerate}

\medskip

257.  In rule 8(1) of Schedule~3 (the employment tribunals (levy appeals) rules of procedure)—
\begin{enumerate}\item[]
($a$) for “a chairman” substitute “an Employment Judge”; and

($b$) for “the chairman” substitute “the Employment Judge”.
\end{enumerate}

\medskip

258.  In Schedule~4 (the employment tribunals (health and~safety---appeals against improvement and~prohibition notices) rules of procedure)—
\begin{enumerate}\item[]
($a$) in rule 7(1) for “a chairman” substitute “an Employment Judge”; and

($b$) in rules 6(3) and~(4), 7, 8, 9(3) and~10(1) and~(4) for “chairman”, in each place, substitute “Employment Judge”.
\end{enumerate}

\medskip

259.  In Schedule~6 (the employment tribunals (equal value) rules of procedure)—
\begin{enumerate}\item[]
($a$) in rules 6(3)($d$), 10(2)($b$)  and~($e$), 11(5) and~13(3) for “a chairman”, in each place, substitute “an Employment Judge”; and

($b$) in rules 3(1), 5(1)($c$), 6(2) and~(3), 10(2)($d$)  and~12(2) for “chairman”, in each place, substitute “Employment Judge”.
\end{enumerate}

\section*{\itshape Child Trust Funds (Non-tax Appeals) Regulations~2005}

260.  The Child Trust Funds (Non-tax Appeals) Regulations~2005\footnote{S.I.~2005/191.} are amended as follows.

\medskip

261.  In regulation~2 (interpretation)—
\begin{enumerate}\item[]
($a$) in the definition of “appeal tribunal” omit ($a$)  (and~the following “($b$)”);

($b$) in the definition of “child trust fund appeal” after “Commissioner” insert “or to~the First-tier Tribunal or lies to~the Upper Tribunal”; and

($c$) in the definition of “Social Security Commissioner” omit sub-paragraph~($a$)  (and~the following “($b$)”).
\end{enumerate}

\medskip

262.  In regulation~3(1) (prescribed manner of notice of appeal) after “notice of appeal” insert “, in respect of an appeal to~an appeal tribunal,”.

\medskip

263.  In regulation~4 (application of section~54 of the Taxes Management Act 1970)—
\begin{enumerate}\item[]
($a$) in paragraphs~(1) and~(2) after “appeal tribunal” insert “or the First-tier Tribunal”; and

($b$) in paragraph~(6), in the inserted subsection~(6), omit paragraph~($a$)  (and~the following “($b$)”).
\end{enumerate}

\medskip

264.  In regulation~5 (application of sections 5 to~7 of and~Schedule~1 to~the 1998 Act or articles 6 to~8 of and~Schedule~1 to~the 1998 Order)—
\begin{enumerate}\item[]
($a$) in the heading omit “sections 5 to~7 and~Schedule~1 to~the 1998 Act or”;

($b$) in paragraph~(1) omit “Sections 5 to~7 and~paragraphs~7, 11 and~12 of Schedule~1 to~the 1998 Act or, in Northern Ireland,”; and

($c$) omit paragraph~(2).
\end{enumerate}

\medskip

265.  In regulation~6(1) (application of section~12 of the 1998 Act or article~13 of the 1998 Order) after “an appeal tribunal”, in both places, insert “or the First-tier Tribunal”.

\medskip

266.  In regulation~7 (application of section~13 of the 1998 Act or article~14 of the 1998 Order) after “appeal tribunal” insert “or the First-tier Tribunal”.

\medskip

267.  In regulation~8 (application of section~14 of the 1998 Act or article~15 of the 1998 Order)—
\begin{enumerate}\item[]
($a$) in paragraph~(1)—
\begin{enumerate}\item[]
(i) for “14(1) to~(10)” substitute “14(2) and~(3)”;

(ii) after “Commissioner” insert “or the Upper Tribunal”; and

(iii) after “an appeal tribunal” insert “or the First-tier Tribunal”; and
\end{enumerate}

($b$) in paragraph~(2)—
\begin{enumerate}\item[]
(i) in sub-paragraph~($a$)  for “(1)” substitute “(3)”;

(ii) at the end of sub-paragraph~($c$)  insert “and”;

(iii) for sub-paragraph~($d$)  substitute—
\begin{quotation}
“($d$) omit subsections (3)($c$)  and~($d$).”; and
\end{quotation}

(iv) omit sub-paragraph~($e$).
\end{enumerate}
\end{enumerate}

\medskip

268.  In regulation~9 (application of section~14(11) and~(12) of and~Schedule~4 to~the 1998 Act or article~15(11) to~(13) of the 1998 Order)—
\begin{enumerate}\item[]
($a$) in the heading omit “section~14(11) and~(12) of and~Schedule~4 to~the 1998 Act or”;

($b$) in paragraph~(1) omit “Section 14(11) and~(12) of, and~Schedule~4 to, the 1998 Act, or, in Northern Ireland,”; and

($c$) in paragraph~(2) omit “section~21(9) of the Act as modified by section~24(2) of the Act in subsection~11 of section~14 and”.
\end{enumerate}

\medskip

269.  In regulation~10 (application of section~15 of the 1998 Act)—
\begin{enumerate}\item[]
($a$) for “appeal from Commissioner on point of law” substitute “Applications for permission to~appeal against a decision of the Upper Tribunal”; and

($b$) for “a Social Security Commissioner” substitute “the Upper Tribunal”.
\end{enumerate}

\medskip

270.  For regulation~11(2) (application of section~16 of the 1998 Act or article~16 of the 1998 Order) substitute—
\begin{quotation}
“(2) Omit subsection~(3) of section~16.”.
\end{quotation}

\medskip

271.  In regulation~12 (application of section~17 of the 1998 Act or article~17 of the 1998 Order)—
\begin{enumerate}\item[]
($a$) in paragraph~(1) after “appeal tribunal” insert “, the First-tier Tribunal, the Upper Tribunal”;

($b$) in paragraph~(2), in the substituted section~17(1)—
\begin{enumerate}\item[]
(i) at the end of sub-paragraph~($a$)  omit “and”;

(ii) at the end of sub-paragraph~($b$)  insert “and”;

(iii) after sub-paragraph~($b$)  insert—
\begin{quotation}
“($c$) any provisions made by or under Chapter~II of Part I of the Tribunals, Courts and~Enforcement Act 2007 (c.~15)”; and
\end{quotation}

(iv) for “an appeal tribunal or lies to~a Commissioner” substitute “the First-tier Tribunal or lies to~the Upper Tribunal”.
\end{enumerate}
\end{enumerate}

\medskip

272.  In regulation~13 (application of section~28 of the 1998 Act or article~28 of the 1998 Order)—
\begin{enumerate}\item[]
($a$) in the heading omit “section~28 of the 1998 Act or”;

($b$) in paragraph~(1) omit “Section 28 of the 1998 Act (“section~28”) or, in Northern Ireland,”;

($c$) in paragraph~(2) omit “subsection~(1A) of section~28 and”; and

($d$) omit paragraph~(3).
\end{enumerate}

\medskip

273.  In regulation~14(2) (application of section~39 of the 1998 Act or article~39 of the 1998 Order) in the definition of “child trust fund appeal” inserted into~section~39 for “an appeal tribunal or lies to~a Social Security Commissioner” substitute “the First-tier Tribunal or lies to~the Upper Tribunal”.

\medskip

274.  Omit regulation~15(2)($a$)  (application of sections 79, 80 and~84 of the 1998 Act or Articles 74 and~75 of the 1998 Order).

\section*{\itshape\sloppy Asylum and~Immigration Tribunal (Procedure) Rules 2005}

275.  In rule 54 of the Asylum and~Immigration Tribunal (Procedure) Rules 2005\footnote{S.I.~2005/230.} (admission of public to~hearings) omit paragraph~(5).

\section*{\itshape Armed Forces and~Reserve Forces (Compensation Scheme) Order 2005}

276.  The Armed Forces and~Reserve Forces (Compensation Scheme) Order 2005\footnote{S.I.~2005/439. The definition of “additional multiple injury lump sum” and article~15B were inserted by the Armed Forces and Reserve Forces (Compensation Scheme) (Amendment) Order 2008 (S.I.~2008/39).} is amended as follows.

\medskip

277.  In article~2 (interpretation) after the definition of “additional multiple injury lump sum” insert—
\begin{quotation}
““appropriate tribunal” means the appropriate tribunal as defined in section~12(1) of the Pensions Appeal Tribunals Act 1943;”.
\end{quotation}

\medskip

278.  In article~13($b$)(iv)  (interpretation of Part III) after “Commissioner” insert “, the First-tier Tribunal, the Upper Tribunal”.

\medskip

279.  In article~15B(6)($d$)  (additional multiple injury lump sum) after “Commissioner” insert “, the First-tier Tribunal, the Upper Tribunal”.

\medskip

280.  In article~43(3)($b$)  (decisions) for “a Pension Appeal Tribunal” substitute “the appropriate tribunal”.

\medskip

281.  In article~45 (reconsideration)—
\begin{enumerate}\item[]
($a$) in paragraph~(4) for “a Pension Appeal Tribunal” substitute “the appropriate tribunal”;

($b$) in paragraph~(5) for “a Pensions Appeal Tribunal” substitute “an appropriate tribunal”; and

($c$) in paragraph~(6) for “Pensions Appeal Tribunal” substitute “appropriate tribunal”.
\end{enumerate}

\medskip

282.  In article~47(3)($b$)  (review on discharge on medical grounds) for “a Pensions Appeal Tribunal” substitute “the appropriate tribunal”.

\medskip

283.  In article~48(6)($b$)  (review---exceptional circumstances) for “a Pensions Appeal Tribunal” substitute “the appropriate tribunal”.

\medskip

284.  In article~49(4)($b$)  (review---ignorance or mistake) for “a Pensions Appeal Tribunal” substitute “the appropriate tribunal”.

\medskip

285.  In article~54(3)($d$)  (date on which awards of benefit become payable) after “Commissioner” insert “, the First-tier Tribunal, the Upper Tribunal”.

\medskip

286.  In article~56 (suspension---Pensions Appeal Tribunal)—
\begin{enumerate}\item[]
($a$) in the heading omit “Pensions Appeal Tribunal” substitute “an appropriate tribunal”;

($b$) in paragraphs~(1), (4) and~(5) for “a Pensions Appeal Tribunal”, in each place, substitute “an appropriate tribunal”;

($c$) in paragraph~(5) for “the Pensions Appeal Tribunal” substitute “the appropriate tribunal”;

($d$) in paragraph~(6)—
\begin{enumerate}\item[]
(i) for “a Pensions Appeal Tribunal”, in both places, substitute “an appropriate tribunal”; and

(ii) for “an appropriate Commissioner” substitute “a Commissioner or the Upper Tribunal, as the case may be”; and
\end{enumerate}

($e$) in paragraph~(7)($b$)  after “that Act” insert “or section~11 of the Tribunals, Courts and~Enforcement Act 2007”.
\end{enumerate}

\medskip

287.---(1)  Article 57 (suspension---Social Security Commissioner) is amended as follows.

(2) In the heading after “Commissioner” insert “and~Upper Tribunal”.

(3) In paragraph~(1)—
\begin{enumerate}\item[]
($a$) for “an appropriate” substitute “a”; and

($b$) after “1943” insert “or, as the case may be, the Upper Tribunal under section~13 of the Tribunals Courts and~Enforcement Act 2007 (c.~15)”.
\end{enumerate}

(4) In paragraph~(5)—
\begin{enumerate}\item[]
($a$) for “an appropriate” substitute “a”; and

($b$) after “1943” insert “or, as the case may be, the Upper Tribunal under section~13 of the Tribunals Courts and~Enforcement Act (c.~15)”.
\end{enumerate}

(5) In paragraph~(6)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($a$)  after “1943” insert “or, as the case may be, section~13 of the Tribunals Courts and~Enforcement Act (c.~15)”;

($b$) in sub-paragraph~($b$)  for “that Act” substitute “the 1943 Act or an application for permission to~appeal under section~13(4) of the 2007 Act”; and

($c$) in sub-paragraph~($e$)—
\begin{enumerate}\item[]
(i) for “an appropriate” substitute “a”; and

(ii) omit “a Great Britain Social Security Commissioner or”.
\end{enumerate}
\end{enumerate}

\section*{\itshape\sloppy Pension Protection Fund (Review and Reconsideration of Reviewable Matters) Regulations 2005}

288.  In regulation~27 of the Pension Protection Fund (Review and~Reconsideration of Reviewable Matters) Regulations~2005\footnote{S.I.~2005/669.} (meetings of the Reconsideration Committee) for “Council on Tribunals”, in both places, substitute “Administrative Justice and~Tribunals Council”.

\section*{\itshape Pension Protection Fund (PPF Ombudsman) Order 2005}

289.  In article~7(2)($k$)  of Pension Protection Fund (PPF Ombudsman) Order 2005\footnote{S.I.~2005/824. Article 7(2)($k$) was inserted by article 2($b$)(iii) of the Pension Protection Fund (PPF Ombudsman) Amendment Order 2005 (S.I.~2005/2023).} (restrictions on the disclosure of information) for “Council on Tribunals”, in both places, substitute “Administrative Justice and~Tribunals Council”.

\section*{\itshape\sloppy\hbadness=2384 Child Trust Funds (Appeals) Regulations 2005}

290.  The Child Trust Funds (Appeals) Regulations~2005\footnote{S.I.~2005/990.} are amended as follows.

\medskip

291.---(1)  Regulation~1 (citation, commencement, duration and~interpretation) is amended as follows.

(2) In paragraph~(3)—
\begin{enumerate}\item[]
($a$) in the definition of “appeal” for “an appeal tribunal” substitute “the First-tier Tribunal”; and

($b$) omit the definitions of—
\begin{enumerate}\item[]
(i) “clerk to~the appeal tribunal”;

(ii) “decision notice”;

(iii) “financially qualified panel member”;

(iv) “legally qualified panel member”; and

(v) “the President”.
\end{enumerate}
\end{enumerate}

(3) Omit paragraph~(4).

\medskip

292.  In regulation~2 (service of notices or documents)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($a$)  omit—
\begin{enumerate}\item[]
(i) “the clerk to~the appeal tribunal or to”; and

(ii) “the clerk to~the appeal tribunal or by”; and
\end{enumerate}

($b$) in sub-paragraph~($b$)  omit “the clerk to~the appeal tribunal or”.
\end{enumerate}

\medskip

293.  In regulation~3 (disputes about notices of appeal) for “a legally qualified panel member” substitute “the First-tier Tribunal”.

\medskip

294.  In regulation~4 (late appeals)—
\begin{enumerate}\item[]
($a$) in paragraph~(1) for “(2) to~(8) are satisfied, an appeal may be” substitute “(4) to~(8) are satisfied, the Board may treat an appeal as made in time where an appeal is”;

($b$) omit paragraphs~(2) and~(3);

($c$) for paragraph~(4) substitute—
\begin{quotation}
“(4) The Board must not treat the appeal as made in time unless the Board is satisfied that it is in the interests of justice.”;
\end{quotation}

($d$) in paragraph~(5)—
\begin{enumerate}\item[]
(i) for “grant an application unless the panel member is, or the Board are, as the case may be,” substitute “treat the appeal as made in time unless the Board are”; and

(ii) in sub-paragraphs~($a$)  and~($b$)  omit “to~the application”;
\end{enumerate}

($e$) in paragraph~(6) for “applicant”, in each place, substitute “appellant”;

($f$) in paragraph~(7)—
\begin{enumerate}\item[]
(i) for “grant the application” substitute “treat the appeal as made in time”; and

(ii) for the words “making of the application” to~the end substitute “submission of the notice of appeal, the more compelling should be the special circumstances.”;
\end{enumerate}

($g$) in paragraph~(8)—
\begin{enumerate}\item[]
(i) for “grant an application” substitute “treat the appeal as made in time”;

(ii) in sub-paragraph~($a$)  for “applicant” substitute “appellant”; and

(iii) in sub-paragraph~($b$)  for “a Social Security Commissioner” substitute “the Upper Tribunal”; and
\end{enumerate}

($h$) omit paragraphs~(9) and~(10).
\end{enumerate}

\medskip

295.  Omit regulations~6 to~25.

\section*{\itshape Residential Property Tribunal (Right to~Buy Determinations) Procedure (England) Regulations~2005}

296.  The Residential Property Tribunal (Right to~Buy Determinations) Procedure (England) Regulations~2005\footnote{S.I.~2005/1509.} are amended as follows.

\medskip

297.  In regulation~12(2)($b$)  (inspection of property and~neighbourhood), for “Council on Tribunals” substitute “Administrative Justice and~Tribunals Council”.

\medskip

298.  In regulation~26 (persons entitled to~be present at a hearing held in private) omit paragraph~(1)($b$).

\section*{\itshape Pension Protection Fund (Reference of Reviewable Matters to~the PPF Ombudsman) Regulations~2005}

299.  In regulation~14 of the Pension Protection Fund (Reference of Reviewable Matters to~the PPF Ombudsman) Regulations~2005\footnote{S.I.~2005/2024.} (Council on Tribunals) for “Council on Tribunals” in each place (including the heading) substitute “Administrative Justice and~Tribunals Council”.

\section*{\itshape\sloppy\hbadness=1742 Bus Lane Contraventions (Penalty charges, Adjudication and Enforcement) (England) Regulations 2005}

300.  In regulation~20(4) of the Bus Lane Contraventions (Penalty charges, Adjudication and~Enforcement) (England) Regulations~2005\footnote{S.I.~2005/2757.} (procedure at a hearing) substitute—
\begin{quotation}
“(4) Any other adjudicator shall be entitled to~attend the hearing of an appeal whether or not it is in private.”.
\end{quotation}

\section*{\itshape Financial Assistance Scheme (Appeals) Regulations~2005}

301.  The Financial Assistance Scheme (Appeals) Regulations~2005\footnote{S.I.~2005/3273.} are amended as follows.

\medskip

302.  In regulation~21 (Council on Tribunals) for “Council on Tribunals”, in each place (including the heading), substitute “Administrative Justice and~Tribunals Council”.

\medskip

303.  In regulation~28 paragraph~(3)($l$)  (restriction on use of documents and~information provided for investigations) for “Council on Tribunals” in both places, substitute “Administrative Justice and~Tribunals Council”.

\section*{\itshape\sloppy\hbadness=2705 Victims of Violent Intentional Crime (Arrangements for Compensation) (European Communities) Regulations 2005}

304.  The Victims of Intentional Crime (Arrangements for Compensation) (European Communities) Regulations~2005\footnote{S.I.~2005/3396.} are amended as follows.

\medskip

305.  For regulation~4(1)($b$)  (designation of deciding authorities) for “Criminal Injuries Compensation Appeals Panel” substitute “First-tier Tribunal”.

\medskip

306.  In regulation~11(2) (hearing of the applicant for compensation)—
\begin{enumerate}\item[]
($a$) for “Criminal Injuries Compensation Appeals Panel”, in both places, substitute “First-tier Tribunal”; and

($b$) for “Criminal Injuries Compensation Scheme 2001”, in both places, substitute “Tribunal Procedure Rules”.
\end{enumerate}

\section*{\itshape Public Contracts Regulations~2006}

307.  In Schedule~1 to~the Public Contracts Regulations~2006\footnote{S.I.~2006/5.} (GPA annex~1 contracting authorities) omit the first entry relating to~the Pensions Appeal Tribunals.

\section*{\itshape Child Benefit (General) Regulations~2006}

308.  In regulation~38 of the Child Benefit (General) Regulations~2006\footnote{S.I.~2006/223.} (exception to~rules preventing duplicate payment)—
\begin{enumerate}\item[]
($a$) in paragraph~(2)($b$)  omit “section~7 of the Social Security Act 1998 or”;

($b$) in paragraph~(2)($c$)  omit “section~16(7) of the Social Security Act 1998 or”; and

($c$) after paragraph~(2)($c$)  insert—
\begin{quotation}
“($d$) the First-tier Tribunal;

($e$) the Upper Tribunal.”.
\end{quotation}
\end{enumerate}

\section*{\itshape\sloppy Naval, Military and Air Forces etc.\ (Disablement and Death) Service Pensions Order 2006}

309.  The Naval, Military and~Air Forces etc.\ (Disablement and~Death) Service Pensions Order 2006\footnote{S.I.~2006/606. Paragraph 3 of Schedule 3 was amended by paragraph 9($b$) of Schedule 1 to the Naval, Military and Air Forces etc (Disablement and Death) Service Pensions Order 2008 (S.I.~2008/606).} is amended as follows.

\medskip

310.  In article~43($a$)  (certification) after “1943” insert “or established under the Tribunals, Courts and~Enforcement Act 2007 (c.~15)”.

\medskip

311.  In article~44(3) (review of decisions, assessments and~awards) after “1943” insert “or the First-tier Tribunal”.

\medskip

312.---(1)  Article 61 (suspension in individual cases---pensions appeal tribunal) is amended as follows.

(2) In the heading, omit “Pensions Appeal”.

(3) In paragraphs~(1), (4) and~(5) for “a Pensions Appeal Tribunal”, in each place, substitute “an appropriate tribunal”.

(4) In paragraph~(5) for “the Pensions Appeal Tribunal” substitute “the appropriate tribunal”.

(5) In paragraph~(6)—
\begin{enumerate}\item[]
($a$) for “a Pensions Appeal Tribunal”, in both places, substitute “an appropriate tribunal”; and

($b$) for “an appropriate Commissioner” substitute “a Commissioner or the Upper Tribunal, as the case may be”.
\end{enumerate}

(6) In paragraph~(8)—
\begin{enumerate}\item[]
($a$) in sub-paragraph~($a$)  after “1943” insert “or, as the case may be, section~13 of the Tribunals, Courts and~Enforcement Act 2007 (c.~15);

($b$) in sub-paragraph~($b$)  for “leave to~appeal under Part LII” substitute “permission to~appeal in accordance with Tribunal Procedure Rules or under Part LII”;

($c$) after sub-paragraph~($b$)  insert—
\begin{quotation}
“($ba$) “appropriate tribunal” means the appropriate tribunal as defined in section~12(1) of the Pensions Appeal Tribunals Act 1943;” and
\end{quotation}

($d$) in sub-paragraph~($c$)—
\begin{enumerate}\item[]
(i) for “an appropriate” substitute “a”; and

(ii) omit “a Great Britain Social Security Commissioner or”.
\end{enumerate}
\end{enumerate}

\medskip

313.  In article~62 (suspension---Social Security Commissioner)—
\begin{enumerate}\item[]
($a$) in the heading after “Commissioner” insert “and~Upper Tribunal”;

($b$) in paragraphs~(1) and~(5)—
\begin{enumerate}\item[]
(i) for “an appropriate” substitute “a”; and

(ii) after “1943” insert “or, as the case may be, the Upper Tribunal under section~13 of the Tribunals, Courts and~Enforcement Act 2007 (c.~15)”; and
\end{enumerate}

($c$) in paragraph~(6)—
\begin{enumerate}\item[]
(i) in sub-paragraph~($a$)  after “1943” insert “or, as the case may be, section~13 of the Tribunals, Courts and~Enforcement Act 2007 (c.~15)”;

(ii) in sub-paragraph~($b$)  for “that Act” substitute “the Pensions Appeal Tribunals Act 1943 or an application for permission to~appeal under section~13(4) of the Tribunals, Courts and~Enforcement Act 2007 (c.~15)”; and

(iii) in sub-paragraph~($e$)  for “an appropriate” substitute “a”.
\end{enumerate}
\end{enumerate}

\medskip

314.  In Schedule~3 (commencing dates of awards)—
\begin{enumerate}\item[]
($a$) in paragraph~3 after “Commissioners”, in each place, insert “or the Upper Tribunal”; and

($b$) after paragraph~11 insert—
\begin{quotation}
“(12) Paragraphs 4 and~8 apply to~a decision of the First-tier Tribunal that a decision made by it be treated as set aside as they apply to~a decision of the President of the Pensions Appeals Tribunal that the decision of a Pensions Appeal Tribunal be treated as set aside.”.
\end{quotation}
\end{enumerate}

\section*{\itshape\sloppy\hbadness=7740 Residential Property Tribunal Procedure (England) Regulations 2006}

315.  The Residential Property Tribunal Procedure (England) Regulations~2006\footnote{S.I.~2006/831.} are amended as follows.

\medskip

316.  In regulation~21(2)($b$)  (inspection of premises and~neighbourhood), for “Council on Tribunals” substitute “Administrative Justice and~Tribunals Council”.

\medskip

317.  In regulation~29 (persons entitled to~be present at a hearing held in private) omit paragraph~(1)($b$).

\section*{\itshape Registered Design Rules 2006}

318.  In rule 20 of the Registered Design Rules 2006\footnote{S.I.~2006/1975.} (hearings in public) omit paragraph~(6).

\section*{\itshape Health and~Social Care (Community Health and~Standards) Act 2003 (Commencement) (No.~11) Order 2006}

319.  In article~4 of the Health and~Social Care (Community Health and~Standards) Act 2003 (Commencement) (No.~11) Order 2006\footnote{S.I.~2006/3397.} (saving provisions)—
\begin{enumerate}\item[]
($a$) in paragraph~(1) after “28th January 2007” insert “subject to~paragraph~(3)”; and

($b$) after paragraph~(2) insert—
\begin{quotation}
“(3) The reference in section~8(6)($a$)  to~an appeal tribunal constituted under Chapter~I of Part I of the Social Security Act 1998 is to~be read as a reference to~the First-tier Tribunal.”.
\end{quotation}
\end{enumerate}

\section*{\itshape\sloppy\hbadness=7704 Personal Injuries (NHS Charges) (Reviews and Appeals) and Road Traffic (NHS Charges) (Reviews and Appeals) (Amendment) Regulations 2006}

320.  The Personal Injuries (NHS Charges) (Reviews and~Appeals) and~Road Traffic (NHS Charges) (Reviews and~Appeals) (Amendment) Regulations~2006\footnote{S.I.~2006/3398. Regulation 6 was amended by regulation 2 of the Personal Injuries (NHS Charges) (Reviews and Appeals) Amendment Regulations 2007 (S.I.~2007/1613).} are amended as follows.

\medskip

321.  In regulation~1(3) (citation, commencement, application and~interpretation) omit the definitions of—
\begin{enumerate}\item[]
($a$) “appeal tribunal”;

($b$) “clerk to~the appeal tribunal”;

($c$) “Commissioner”;

($d$) “legally qualified panel member”; and

($e$) “medically qualified panel member”.
\end{enumerate}

\medskip

322.  In regulation~4 (waiver applications and~appeals)—
\begin{enumerate}\item[]
($a$) for paragraph~(4) substitute—
\begin{quotation}
“(4) An appeal against a waiver decision made in accordance with Tribunal Procedure Rules must be made on a form approved by the Secretary of State and~sent to~the Compensation Recovery Unit.”; and
\end{quotation}

($b$) omit paragraph~(5).
\end{enumerate}

\medskip

323.  In regulation~5 (appeals against certificates)—
\begin{enumerate}\item[]
($a$) for paragraph~(1) substitute—
\begin{quotation}
“(1) An appeal against a certificate made in accordance with Tribunal Procedure Rules must be made on a form approved by the Secretary of State and~sent to~the Compensation Recovery Unit.”; and
\end{quotation}

($b$) omit paragraph~(4).
\end{enumerate}

\medskip

324.  In regulation~6 (appeals general)—
\begin{enumerate}\item[]
($a$) in paragraphs~(1) and~(2) for “under regulations~4(5) or 5(4), as the case may be” substitute “by Tribunal Procedure Rules”;

($b$) in paragraph~(3) for “regulations~4(4) or 5(1), as the case may be” substitute “Tribunal Procedure Rules”;

($c$) in paragraph~(5)($a$)  for “a legally qualified panel member” substitute “the First-tier Tribunal”;

($d$) in paragraph~(5)($b$)—
\begin{enumerate}\item[]
(i) for “that panel member” substitute “the First-tier Tribunal”; and

(ii) omit “, and~shall inform the appellant, and~the Secretary of State of his decision”; and
\end{enumerate}

($e$) omit paragraph~(6).
\end{enumerate}

\medskip

325.---(1)  Regulation~7 (extension of time for appealing) is amended as follows.

(2) For paragraphs~(1) to~(3) substitute—
\begin{quotation}
“(1) The Secretary of State may treat an appeal as made in time, even though the time prescribed by Tribunal Procedure Rules has expired, if the Secretary of State is satisfied that it is in the interests of justice.”.
\end{quotation}

(3) In paragraph~(4)—
\begin{enumerate}\item[]
($a$) for “(3)” substitute “(1)”;

($b$) for “grant an application unless the person determining the application is satisfied that” substitute “treat the appeal as made in time unless”;

($c$) in sub-paragraph~($b$)—
\begin{enumerate}\item[]
(i) for “, as the case may be, by regulation~4 or 5” substitute “by Tribunal Procedure Rules”; and

(ii) for “application for extension of time” substitute “notice of appeal is submitted”; and
\end{enumerate}

($d$) in sub-paragraph~($c$)  for “applicant’s” substitute “appellant’s”.
\end{enumerate}

(4) In paragraph~(5)—
\begin{enumerate}\item[]
($a$) for “for granting an application for an extension of time for making an appeal under paragraph~(1) the person determining the application shall have regard” substitute “to~treat the appeal as made in time under paragraph~(1) regard shall be had”; and

($b$) for “making of the application” to~the end substitute “submission of the notice of appeal, the more cogent should be the special reasons.”.
\end{enumerate}

(5) In paragraph~(6)—
\begin{enumerate}\item[]
($a$) for “for granting an application for an extension of time for making an appeal” substitute “to~treat the appeal as made in time”;

($b$) in sub-paragraph~($a$)—
\begin{enumerate}\item[]
(i) for “applicant” substitute “appellant”; and

(ii) for “regulations~4 or 5” substitute “Tribunal Procedure Rules”; and
\end{enumerate}

($c$) in sub-paragraph~($b$)  for “a Commissioner” substitute “the Upper Tribunal”.
\end{enumerate}

(6) Omit paragraphs~(7) and~(8).

(7) For paragraph~(9) substitute—
\begin{quotation}
“(9) An appellant shall be notified of a decision made under this regulation.”.
\end{quotation}

(8) Omit paragraphs~(10) to~(12).

\medskip

326.  For regulation~8 (general provisions relating to~the procedure for appeals) substitute—
\begin{quotation}
\subsection*{“General provision relating to~the procedure for appeals}

8.  Regulation~34 of the Social Security Regulations~shall apply in relation to~an appeal as it applies to~an appeal to~the First-tier Tribunal under section~12 of the Social Security Act 1998, except that a reference to~a party to~the proceedings means the person to~whom the certificate was issued.”.
\end{quotation}

\medskip

327.  Omit regulation~9 (consolidation of appeals).

\section*{\itshape Scottish Parliament (Disqualification) Order 2007}

328.  In Part I of the Schedule~to~the Scottish Parliament (Disqualification) Order 2007\footnote{S.I.~2007/285.} (office-holders disqualified from being a member of the Scottish Parliament)—
\begin{enumerate}\item[]
($a$) omit the entries for—
\begin{enumerate}\item[]
(i) “Any member of the Council on Tribunals”;

(ii) “Any member of the Scottish Committee of the Council of Tribunals”;

(iii) “Adjudicator appointed under section~5 of the Criminal Injuries Compensation Act 1995”; and

(iv) “Chief Asylum Support Adjudicator, Deputy Chief Asylum Support Adjudicator and~any other adjudicator appointed under paragraph~1 of Schedule~10 to~the Immigration and~Asylum Act 1999”; and
\end{enumerate}

($b$) after the entry for Accounts Commission for Scotland~insert “Any member of the Administrative Justice and~Tribunals Council or the Scottish Committee of the Administrative Justice and~Tribunals Council”.
\end{enumerate}

\section*{\itshape Tax Credits (Child Care Providers) (Miscellaneous Revocation and~Transitional Provisions) (England) Scheme 2007}

329.  Article 4 of the Tax Credits (Child Care Providers) (Miscellaneous Revocation and~Transitional Provisions) (England) Scheme 2007\footnote{S.I.~2007/2481.} (revocation of the 2005 Scheme and~transitional provision) is amended as follows—
\begin{enumerate}\item[]
($a$) in paragraph~(2) after “effect” insert “, with the modifications in paragraph~(3),”; and

($b$) after paragraph~(2) insert—
\begin{quotation}
“(3) For the purposes of paragraph~(2) the 2005 Scheme is amended as follows—
\begin{enumerate}\item[]
($a$) in article~2 omit the definitions of “the Tribunal” and~“the Tribunal Regulations”;

($b$) in article~11—
\begin{enumerate}\item[]
(i) in paragraphs~(1) and~(5) for “Tribunal” substitute “First-tier Tribunal”;

(ii) for paragraph~(2) substitute—
\begin{quotation}
“(2) Tribunal Procedure Rules shall apply to~an appeal under paragraph~(1) as they apply to~an appeal under section~79M of the 1989 Act.”; and
\end{quotation}
\end{enumerate}

($c$) omit paragraphs~(3) and~(4).”.
\end{enumerate}
\end{quotation}
\end{enumerate}

\section*{\itshape European Communities (Recognition of Professional Qualifications) Regulations~2007}

330.  In Schedule~5 to~the European Communities (Recognition of Professional Qualifications) Regulations~2007\footnote{S.I.~2007/2781.} (appeal bodies) for “Care Standards Tribunal”, in each place, substitute “First-tier Tribunal”.

\section*{\itshape Administrative Justice and~Tribunals Council (Listed Tribunals) Order 2007}

331.  In article~2 of the Administrative Justice and~Tribunals Council (Listed Tribunals) Order 2007\footnote{S.I.~2007/2951.} (list of tribunals)—
\begin{enumerate}\item[]
($a$) omit the following entries—
\begin{enumerate}\item[]
(i) Adjudicators under section~5 of the Criminal Injuries Compensation Act 1995;

(ii) Asylum Support Adjudicators;

(iii) Pensions Appeal Tribunals for England~and~Wales;

(iv) Special Educational Needs and~Disability Tribunal; and

(v) Tribunal under section~9 of the Protection of Children Act 1999; and
\end{enumerate}

($b$) for “Mental Health Review Tribunals for England~and~Wales” substitute “Mental Health Review Tribunal for Wales”.
\end{enumerate}

\section*{\itshape\sloppy Safeguarding Vulnerable Groups Act 2006 (Transitional Provisions) Order 2008}

332.  The Safeguarding Vulnerable Groups Act 2006 (Transitional Provisions) Order 2008\footnote{S.I.~2008/473.} is amended as follows.

\medskip

333.  In article~1(2) (citation, commencement and~interpretation) omit the definition of “Tribunal”.

\medskip

334.  In article~2(5) and~(6) (inclusion in the children’s barred list: persons disqualified from working with children) for “Tribunal”, in each place, substitute “Upper Tribunal”.

\medskip

335.  In article~4(5) and~(6) (inclusion in the adults’ barred list: persons considered unsuitable to~work with vulnerable adults) for “Tribunal”, in each place, substitute “Upper Tribunal”.

\section*{\itshape\sloppy Safeguarding Vulnerable Groups Act 2006 (Barring Procedure) Regulations~2008}

336.  The Safeguarding Vulnerable Groups Act 2006 (Barring Procedure) Regulations~2008\footnote{S.I.~2008/474.} are amended as follows.

\medskip

337.  In regulation~1 (citation, commencement and~interpretation) omit the definition of “Tribunal”.

\medskip

338.  In regulation~4(2)($b$)  (the minimum barred period: persons included in the list maintained under section~1 of the Protection of Children Act 1999) for “Tribunal” substitute “Upper Tribunal”.

\medskip

339.  In regulation~5(2)($b$)  (the minimum barred period: persons subject to~disqualification orders) for “Tribunal” substitute “Upper Tribunal”.

\medskip

340.  In regulation~6(2)($b$)  (the minimum barred period: persons subject to~directions made under section~142(1) of the Education Act 2002) for “Tribunal” substitute “Upper Tribunal”.

\medskip

341.  In regulation~8(4)($b$)  (the minimum barred period: persons subject to~previous restrictions (adults’ barred list)) for “Tribunal” substitute “Upper Tribunal”.

\section*{\itshape Employment and~Support Allowance Regulations~2008}

342.  For regulation~40(2)($b$)(ii)  of the Employment and~Support Allowance Regulations~2008\footnote{S.I.~2008/794.} (a claimant who works to~be treated as not entitled to~an employment support allowance) substitute—
\begin{quotation}
“(ii) a member of the First-tier Tribunal where the member is eligible for appointment to~be such a member in accordance with article~2(3) of the Qualifications for Appointment of Members to~the First-tier Tribunal and~Upper Tribunal Order 2008\footnote{S.I.~2008/2692.}.”.
\end{quotation}

\section*{\itshape Childcare (Early Years and~General Childcare Registers) (Common Provisions) Regulations~2008}

343.  In regulation~12 of the Childcare (Early Years and~General Childcare Registers) (Common Provisions) Regulations~2008\footnote{S.I.~2008/976.} (appeal against suspensions) for “Tribunal”, in each place, substitute “First-tier Tribunal”.

\section*{\itshape Social Security (Recovery of Benefits) (Lump Sum Payments) Regulations~2008}

344.  Schedule~1 of the Social Security (Recovery of Benefits) (Lump Sum Payments) Regulations~2008\footnote{S.I.~2008/1596.} (modification of certain provisions of the Act) is amended as follows—
\begin{enumerate}\item[]
($a$) in paragraph~5—
\begin{enumerate}\item[]
(i) for “medical appeal tribunal” substitute “First-tier Tribunal”; and

(ii) omit sub-paragraph~($a$); and
\end{enumerate}

($b$) in paragraph~6 for “Social Security Commissioner” substitute “Upper Tribunal”.
\end{enumerate}

\section*{\itshape Trade Marks Rules 2008}

345.  In rule 66 of the Trade Marks Rules 2008\footnote{S.I.\ 2008/1797.} (hearings before registrar to~be in public) omit paragraph~(2).

\section*{\itshape Child Support Information Regulations~2008}

346.  In regulation~12(1)($c$)  and~(2) of the Child Support Information Regulations~2008\footnote{S.I.~2008/2551.} (disclosure of information to~a court or tribunal) for “an appeal tribunal” substitute “the First-tier Tribunal”.

\part[Schedule 2 --- Revocations]{Schedule 2\\*Revocations}

\renewcommand\parthead{--- Schedule 2}

{\noindent\footnotesize
%\begin{tabulary}{\linewidth}{JlJ}
\begin{longtable}{p{154.60547pt}lp{131.7065pt}}
\hline
Column 1&
Column 2&
Column 3\\
\itshape 
Instrument revoked
	&
\itshape 
Reference
	&
\itshape 
Extent of revocation\\
\hline
\endhead
\hline
\endlastfoot
\hbadness=2401 The Pensions Appeal Tribunals (England and Wales) Regulations 1926	&S.I.~1926/129	&The whole of the Regulations.\\
The Pensions Appeals Tribunals (England~and~Wales) Rules 1980	&S.I.~1980/1120	&The whole of the Rules.\\
The Pensions Appeals Tribunals (England~and~Wales) (Amendment) Rules 1986	&S.I.~1986/366	&The whole of the Rules.\\
The Pensions Appeals Tribunals (England~and~Wales) (Amendment) Rules 1998	&S.I.~1998/1201	&The whole of the Rules.\\
The Child Support (Miscellaneous Amendments) (No.~2) Regulations 1999	&S.I.~1999/1047	&Regulation~46.\\
The Child Support Commissioners (Procedure) Regulations~1999	&S.I.~1999/1305	&The whole of the Regulations.\\
\hbadness=2772 The Social Security and Child Support (Decisions and Appeals) (Amendment) Regulations 1999	&S.I.~1999/1466	&Regulation~2.\\
\hbadness=2772 The Social Security and Child Support (Decisions and Appeals) Amendment No.~3 Regulations 1999	&S.I.~1999/1670	&Regulation~2(5).\\
The Tax Credits (Decisions and Appeals) (Amendment) Regulations 1999	&S.I.~1999/2570	&Regulations~22, 23(2), 25, 26 and~27.\\
\hbadness=3178 The Social Security and~Child Support (Decisions and Appeals), Vaccine Damage Payments and Jobseeker’s Allowance (Amendment) Regulations 1999	&S.I.~1999/2677	&Regulations~9 and~10.\\
The Asylum Support Appeals (Procedure) Rules 2000	&S.I.~2000/541	&The whole of the Rules.\\
The Social Security and~Child Support (Miscellaneous Amendments) Regulations~2000	&S.I.~2000/1596	&Regulations~24, 25 and~29 to~32.\\
The Social Security Commissioners (Procedure) (Amendment) Regulations~2000	&S.I.~2000/2854	&The whole of the Regulations.\\
The Child Support (Decisions and Appeals) (Amendment) Regulations 2000	&S.I.~2000/3185	&Regulation~13.\\
The Child Support (Consequential Amendments and~Transitional Provisions) Regulations~2001	&S.I.~2001/158	&Regulation~4(2) (in so far as it applies to~regulation~44 of the Social Security and~Child Support (Decisions and~Appeals) Regulations~1999) and~(5).\\
The Pensions Appeals Tribunals (England~and~Wales) (Amendment) Rules 2001&	S.I.~2001/257	&The whole of the Rules.\\
The Social Security Commissioners (Procedure) (Amendment) Regulations~2001	&S.I.~2001/1095	&Regulations~2, 3($c$)  to~($k$), 4, 5($b$)  and~($c$)  and~6 to~14.\\
The Pensions Appeals Tribunals (England~and~Wales) (Amendment No.~2) Rules 2001	&S.I.~2001/1183	&The whole of the Rules.\\
The Protection of Children and~Vulnerable Adults and~Care Standards Tribunal Regulations~2002	&S.I.~2002/816	&The whole of the Regulations.\\
\hbadness=1515 The Social Security and Child Support (Decisions and Appeals) (Miscellaneous Amendments) Regulations 2002	&S.I.~2002/1379	&Regulations~9, 10($a$), 13 to~20, 22, 27($a$)  and~28.\\
The Social Security Commissioners (Procedure) (Tax Credits Appeals) Regulations~2002	&S.I.~2002/3237	&The whole of the Regulations.\\
The Protection of Children and Vulnerable Adults and Care Standards Tribunal (Amendment) Regulations 2003	&S.I.~2003/626	&The whole of the Regulations.\\
\hbadness=1515 The Social Security and Child Support (Decisions and Appeals) (Miscellaneous Amendments) Regulations 2003	&S.I.~2003/1050	&Regulation~3(1).\\
The Protection of Children and~Vulnerable Adults and~Care Standards Tribunal (Amendment No.~2) Regulations~2003	&S.I.~2003/1060	&The whole of the Regulations.\\
The Asylum Support Appeals (Procedure) (Amendment) Rules 2004	&S.I.~2003/1735	&The whole of the Rules.\\
The Protection of Children and~Vulnerable Adults and~Care Standards Tribunal (Amendment No.~3) Regulations~2003	&S.I.~2003/2043	&The whole of the Regulations.\\
\hbadness=1259 The Mental Health Review Tribunals (Regions) Order 2003	&S.I.~2003/2251	&The whole Order.\\
\hbadness=1048 The Health and Social Care (Community Health and Standards) Act 2003 (Commission for Healthcare Audit and Inspection and Commission for Social Care Inspection) (Transitional and Consequential Provisions) Order 2004	&S.I.~2004/664	&Paragraph 7 of Schedule~1.\\
The Protection of Children and Vulnerable Adults and Care Standards Tribunal (Amendment) Regulations 2004	&S.I.~2004/2073	&The whole of the Regulations.\\
The Protection of Children and~Vulnerable Adults and~Care Standards Tribunal (Amendment No.~2) Regulations~2004	&S.I.~2004/3354	&The whole of the Regulations.\\
The Social Security, Child Support and Tax Credits (Decisions and~Appeals) (Amendment) Regulations 2004	&S.I.~2004/3368	&Regulations~2(4) to~(7), 3(2) and~(3) and~6.\\
\hbadness=2707 The Social Security and Child Support Commissioners (Procedure) (Amendment) Regulations 2005	&S.I.~2005/207	&The whole of the Regulations.\\
\hbadness=1127 The Social Security, Child Support and Tax Credits (Miscellaneous Amendments) Regulations 2005	&S.I.~2005/337	&Regulations~2(8) to~(18) and (20) and~4(3) to~(11).\\
The Social Security Commissioners (Procedure) (Amendment) Regulations~2005	&S.I.~2005/870	&The whole of the Regulations.\\
The Social Security Commissioners (Procedure) (Child Trust Funds) Regulations~2005	&S.I.~2005/1031	&The whole of the Regulations.\\
The Civil Partnership (Pensions, Social Security and~Child Support) (Consequential, etc.\ Provisions) Order 2005	&S.I.~2005/2877	&Paragraph 36(3) of Schedule~3.\\
The Social Security (Civil Partnership) (Consequential Amendments) Regulations~2005	&S.I.~2005/2878	&Regulation~9(3).\\
The Adoption and~Children Act 2002 (Consequential Amendments) Order 2005	&S.I.~2005/3504	&Article 6.\\
The Pensions Appeals Tribunals (England~and~Wales) (Amendment) Rules 2005	&S.I.~2005/7009	&The whole of the Rules.\\
The Housing Benefit and~Council Tax Benefit (Consequential Provisions) Regulations~2006	&S.I.~2006/217	&Paragraph 15 of Schedule~2.\\
The Protection of Children and Vulnerable Adults and Care Standards Tribunal (Amendment) Regulations 2006	&S.I.~2006/1930	&The whole of the Regulations.\\
The Transfer of Functions (Asylum Support Adjudicators) Order 2007	&S.I.~2007/275	&Article 6(2).\\
The Education and~Inspections Act 2006 (Consequential Amendments) Regulations~2007	&S.I.~2007/603	&Regulation~11.\\
The Health and~Social Care (Community Health and~Standards) Act 2003 Consequential Provisions (Recovery of NHS Charges) Order 2007	&S.I.~2007/917	&The whole Order.\\
The Protection of Children and Vulnerable Adults and Care Standards Tribunal (Amendment) Regulations 2007	&S.I.~2007/1684	&The whole of the Regulations.\\
The Protection of Children and~Vulnerable Adults and~Care Standards Tribunal (Review of Inclusion in the PoCA List and~Review of Section 142 Directions) Regulations~2007	&S.I.~2007/2620	&The whole of the Regulations.\\
The Secretaries of State for Children, Schools and~Families, for Innovation, Universities and~Skills and~for Business, Enterprise and~Regulatory Reform Order 2007	&S.I.~2007/3224	&Paragraph 32 of the Schedule.\\
The Protection of Children and~Vulnerable Adults and~Care Standards Tribunal (Children’s and~Adults’ Barred Lists) (Transitional Provisions) Regulations~2008	&S.I.~2008/1497	&The whole of the Regulations.\\
The Protection of Children and Vulnerable Adults and Care Standards Tribunal (Amendment) Regulations 2008	&S.I.~2008/1802	&The whole of the Regulations.\\
The Child Support Commissioners (Procedure) (Amendment) Regulations~2008	&S.I.~2008/1955	&The whole of the Regulations.\\
\hbadness=2772 The Social Security and Child Support (Decisions and Appeals) (Amendment) Regulations 2008	&S.I.~2008/1957	&The whole of the Regulations.\\
%\end{tabulary}
\end{longtable}

}

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Order)}

This Order makes consequential amendments and~transitional provisions in respect of the transfer of functions of tribunals on 3rd November 2008 to~the First-Tier Tribunal and~Upper Tribunal, which are established with the coming into~force of Part I of the Tribunals, Courts and~Enforcement Act 2007 (“the Act”).

\section*{Consequential amendments and~revocations}

The Schedules to~the Order make consequential amendments to, and~revocations of, secondary legislation in respect of the functions of tribunals transferring to~the First-tier Tribunal and~Upper Tribunal on 3rd November 2008.

This Order also makes consequential amendments to~secondary legislation in respect of the abolition of the Council of Tribunals and~changes to~the name of chairmen of employment tribunals.

\section*{Extent}

The extent provisions in articles 3 and~4 preserve the current position in Scotland~for appeals to~the appeal tribunal constituted under Chapter~I of Part I of the Social Security Act 1998 (and~appeals from that tribunal to~the Social Security Commissioners) in relation to~appeals under sections 157 and~159 of the Health and~Social Care (Community Health and~Standards) Act 2003. These functions are not transferred under the Transfer of Tribunal Functions Order 2008.

\section*{Transitional Provisions}

Article 5 redirects potential appeals from the appeal tribunal (constituted under Chapter~I of Part I of the Social Security Act 1998) against its decisions on appeals under section~8 of the Road Traffic Act 1999, from the High Court to~the Upper Tribunal, where those decisions were made prior to~the transfer of the tribunal, and~the appeal right to~the High Court has not been initiated. 

\end{document}