\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Maintenance and Other Payments Act 2008 (Commencement No.~6) Order 2009}

\newcommand\regsnumber{2009/3072}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and~Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.I.\ 2009 No.\ 3072 (C.~134)}

\date{Made
%2nd November 2009\\
%Laid before Parliament
%9th November 2009\\
%Coming into~force
23rd November 2009
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{27.61603pt}

%\hbadness=10000

\begin{document}

\maketitle

\noindent
The Secretary of State for Work and Pensions, in exercise of the powers conferred by sections 62(3) of the Child Maintenance and Other Payments Act 2008\footnote{2008 c.~6.}, makes the following Order: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and interpretation]{Citation and interpretation}

1.---(1)  This Order may be cited as the Child Maintenance and Other Payments Act 2008 (Commencement No.~6) Order 2009.

(2) In this Order, any reference to a numbered section is a reference to a section of the Child Maintenance and Other Payments Act 2008.

\subsection[2. Appointed day]{Appointed day}

2.---(1)  Section 31 (power to treat liability as satisfied) comes into force on 26th November 2009 for the purpose of making regulations and on 25th January 2010 for all other purposes.

(2) Section 38 (recovery of arrears from deceased’s estate) comes into force on 26th November 2009. 

\bigskip

\pagebreak[3]

Signed 
by authority of the 
Secretary of State for~Work and~Pensions.
%I concur
%By authority of the Lord Chancellor

{\raggedleft
\emph{Helen Goodman}\\*
%Secretary
%Minister
Parliamentary Under-Secretary 
of State\\*Department 
for~Work and~Pensions

}

23rd November 2009

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Order)}

This Order brings into force provisions of the Child Maintenance and Other Payments Act 2008 (c.~6).

Article 2(1) brings into force section 31 (power to treat liability as satisfied) on 26th November 2009 for the purpose of making regulations and on 25th January 2010 for all other purposes.

Article 2(2) brings into force section 38 (recovery of arrears from deceased’s estate) on 26th November 2009. 

\end{document}