\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support and Claims and Payments (Miscellaneous Amendments and Change to the Minimum Amount of Liability) Regulations 2013}

\newcommand\regsnumber{2013/1654}

\title{\regstitle}

\author{S.I.\ 2013 No.\ 1654}

\date{Made
3rd July 2013\\
%Laid before Parliament
%27th June 2013\\
Coming into force
in accordance with regulation 1
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\setlength\headheight{42.11603pt}

%\hbadness=10000

\begin{document}

\maketitle

\enlargethispage{\baselineskip}

\noindent
The Secretary of State makes the following Regulations in exercise of the powers conferred by sections 14(1), 43 and 52(4) of, and paragraphs 3(2) and 10A(1)($b$)  of Schedule 1 and paragraphs 4(1) and 5 of Schedule 4B to, the Child Support Act 1991\footnote{1991 c.~48. Section 43 was inserted by the Child Support, Pensions and Social Security Act 2000 (c.~19) (“the 2000 Act”), section 21. Section 54(1) is cited for the meaning of prescribed. Schedule 1 was substituted by the 2000 Act, section 1(3); paragraph 10A(1) was amended by the Child Maintenance and Other Payments Act 2008 (c.~6) (“the 2008 Act”), Schedule 7, paragraph 1(30). Schedule 4B was substituted by section 6(2) of, and Schedule 2 to, the 2000 Act.} and section 5(1)($p$)  of the Social Security Administration Act 1992\footnote{1992 c.~5.}.

The Social Security Advisory Committee has agreed that the proposals in respect of these Regulations, so far as made under that section 5(1)($p$), should not be referred to it\footnote{See sections 172(1) and 173(1)($b$)  of the Social Security Administration Act 1992 (c.~5).}.

A draft of this instrument was laid before and approved by a resolution of each House of Parliament in accordance with section 52(2)\footnote{Section 52(2) was substituted by the Child Support, Pensions and Social Security Act 2000 (c.~19), section 25.} of the Child Support Act 1991. 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation and commencement]{Citation and commencement}

1.---(1)  These Regulations may be cited as the Child Support and Claims and Payments (Miscellaneous Amendments and Change to the Minimum Amount of Liability) Regulations 2013.

(2) These Regulations come into force in relation to a case to which the new calculation rules apply on the day on which paragraph 2 of Schedule~4 to the Child Maintenance and Other Payments Act 2008 (calculation by reference to gross weekly income)\footnote{2008 c.~6.} comes into force for all purposes.

(3) In paragraph (2), “a case to which the new calculation rules apply” means a case in which liability to pay child support maintenance is calculated in accordance with Part~I of Schedule 1 to the Child Support Act 1991 as amended by paragraph 2 of Schedule 4 to the Child Maintenance and Other Payments Act 2008.

\subsection[2. Amendment to Schedule 1 to the Child Support Act 1991]{Amendment to Schedule 1 to the Child Support Act 1991}

2.  In Schedule 1 to the Child Support Act 1991 (calculation of weekly amount of child support maintenance)\footnote{1991 c.~48.}, paragraph 5A(2)\footnote{Paragraph 5A was inserted by the 2008 Act, Schedule 4, paragraph 5 and subsequently amended by S.I.~2012/2678.} shall have effect as if for “£5” in that paragraph there is substituted “£7”.

\subsection[3. Amendment to the Social Security (Claims and Payments) Regulations 1987]{Amendment to the Social Security (Claims and Payments) Regulations 1987}

3.  In paragraphs 5(2) and 6(2) of Schedule 9B to the Social Security (Claims and Payments) Regulations 1987 (deductions from benefit in respect of child support maintenance and payment to persons with care)\footnote{S.I.~1987/1968. Schedule 9B was inserted by S.I.~2001/18, regulation 2($b$), Schedule.}—
\begin{enumerate}\item[]
($a$) for “£5” substitute “the flat rate of maintenance”; and

($b$) after the references to “regulation 4(3) of the Child Support (Maintenance Calculations and Special Cases) Regulations 2000”, insert “or regulation 44(3) of the Child Support Maintenance Calculation Regulations 2012\footnote{S.I.~2012/2677.}”.
\end{enumerate}

\subsection[4. Amendment to the Child Support Information Regulations 2008]{Amendment to the Child Support Information Regulations 2008}

4.  In regulation 9A(9) of the Child Support Information Regulations 2008 (duty to notify increase in current income)\footnote{S.I.~2008/2551. Reg.~9A was inserted by S.I.~2012/2785, reg.~8(4).}, for “£5” substitute “£7”.

\subsection[5. Amendment to the Child Support Maintenance Calculation Regulations 2012]{Amendment to the Child Support Maintenance Calculation Regulations 2012}

5.---(1)  The Child Support Maintenance Calculation Regulations 2012 are amended as follows.

(2) For the Table in regulation 43 (reduced rate), substitute the following table—\looseness=-1
	
\noindent
%\begin{tabulary}{\linewidth}{JJJ}
\begin{longtable}{p{155.22916pt}p{167.40198pt}p{31.36664pt}}
\hline
	&\itshape ``Number of relevant other children of the non-resident parent	&$T$ (\%)\\
\hline
\endhead
\hline
\endlastfoot
1 qualifying child of the non-resident parent	&0\newline 1	&17$.$0\newline 14$.$1\\
&2	&13$.$2\\
&3 or more&	12$.$4\\
\hline
2 qualifying children of the non-resident parent&0\newline 1	&25$.$0\newline 21$.$2\\
&2	&19$.$9\\
&3 or more	&18$.$9\\
\hline
3 or more qualifying children of the non-resident parent	&0\newline 1	&31$.$0\newline 26$.$4\\
&2	&24$.$9\\
&3 or more	&23$.$8''\\
%\end{tabulary}
\end{longtable}

(3) In regulation 69 (non-resident parent with unearned income)—
\begin{enumerate}\item[]
($a$) in paragraph (5), after sub-paragraph ($b$)  insert—
\begin{quotation}
“or

($c$) the Secretary of State is unable, for whatever reason, to request or obtain the information from HMRC,”;
\end{quotation}

($b$) after paragraph (7) insert—
\begin{quotation}
“(8) Subject to paragraph (9), where the non-resident parent makes relievable pension contributions, which have not been otherwise taken into account for the purposes of the maintenance calculation, there is to be deducted from the additional weekly income calculated in accordance with paragraph (7) an amount determined by the Secretary of State as representing the weekly average of those contributions.

(9) An amount must only be deducted in accordance with paragraph (8) where the relievable pension contributions referred to in that paragraph relate to the same tax year that has been used for the purposes of determining the additional weekly income.”.
\end{quotation}
\end{enumerate}

(4) In paragraph (1)($c$)  of regulation 70 (non-resident parent on a flat or nil rate with gross weekly income), omit “equal to or”.

(5) In regulation 74 (effect on maintenance calculation---general), after paragraph (1) insert—
\begin{quotation}
“(1A) Where the application of a variation agreed to (or of the aggregate of variations agreed to) would decrease the amount of child support maintenance payable by the non-resident parent to less than the figure equivalent to the flat rate referred to in paragraph 4(1) of Schedule 1 to the 1991 Act (or in that sub-paragraph as modified by regulations under paragraph 10A of that Schedule), the non-resident parent is instead liable to pay child support maintenance at a rate equivalent to that flat rate apportioned if appropriate as provided in paragraph 6 of Schedule~1 to that Act.”.
\end{quotation}

\bigskip

\pagebreak[3]

Signed 
by authority of the 
Secretary of State for~Work and~Pensions.
%I concur
%By authority of the Lord Chancellor

{\raggedleft
\emph{Steve Webb}\\*
%Secretary
Minister
%Parliamentary Under-Secretary 
of State\\*Department 
for~Work and~Pensions

}

3rd July 2013

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Regulations)}

These Regulations make a consequential amendment to Schedule 1 to the Child Support Act 1991 (c.~48) (“the 1991 Act”) arising from the increase to the flat rate of child support maintenance from £5 to £7 for cases in which liability for child support maintenance is calculated under Part~I of Schedule 1 to the 1991 Act as amended by paragraph 2 of Schedule 4 to the Child Maintenance and Other Payments Act 2008 (c.~6) (the “2012 scheme rules”). The flat rate of child support maintenance was increased from £5 to £7 by paragraph 4 of Schedule 4 and paragraph 1(28) of Schedule 7 to the Child Maintenance and Other Payments Act 2008for cases subject to the 2012 scheme rules. These Regulations also make other consequential amendments to certain secondary legislation as a result of the increase to the flat rate for those cases and make miscellaneous amendments to the Child Support Maintenance Calculation Regulations (S.I.~2012/2677) (“the 2012 Regulations”) in relation to the reduced rate of child support maintenance and in relation to variations. The reduced rate of child support maintenance is payable if neither the flat or nil rate applies and the non-resident parent has income of less than £200 but more than £100. Variations allow for deviations from the usual rules for calculating maintenance in certain limited circumstances.

Regulation 5 amends provisions of the 2012 Regulations as they relate to the reduced rate provisions and variations. Paragraph (2) substitutes the table contained in regulation 43 concerning the calculation of the reduced rate of child support maintenance as a consequence of the increase to the flat rate from £5 to £7. Paragraph (3)($a$)  amends regulation 69 so that, in cases where the Secretary of State is unable to request or obtain information from HMRC, the Secretary of State can determine the amount of the non-resident parent’s unearned income by reference to the most recent tax year, based, as far as possible, on information that would be required to be provided in a self-assessment tax return. Paragraph (3)($b$)  amends regulation 69 so that relievable pension contributions can be taken account of for the purposes of calculating unearned income. Paragraph (4) amends regulation 70 so that a case can be subject to a variation in circumstances where the nil rate or the flat rate apply and the non-resident parent has a gross weekly income of more than £100 per week. Paragraph (5) amends regulation 74 so that, where the application of a variation would otherwise decrease the amount payable to less than the flat rate, the non-resident parent will be liable to pay child support maintenance at a rate equal to the flat rate.

A full impact assessment has not been published for this instrument as it has no impact on the private sector or civil society organisations. 

\end{document}