\documentclass[12pt,a4paper]{article}

\newcommand\regstitle{The Child Support Appeals (Jurisdiction of Courts) (Scotland) Order 2003}

\newcommand\regsnumber{2003/96}

%\opt{newrules}{
\title{\regstitle}
%}

%\opt{2012rules}{
%\title{Child Maintenance and Other Payments Act 2008\\(2012 scheme version)}
%}

\author{S.S.I.\ 2003 No.\ 96}

\date{Made
18th February 2003\\
%Laid before Parliament
%26th March 2002\\
Coming into force
in accordance with article 1(2)
}

%\opt{oldrules}{\newcommand\versionyear{1993}}
%\opt{newrules}{\newcommand\versionyear{2003}}
%\opt{2012rules}{\newcommand\versionyear{2012}}

\usepackage{csa-regs}

\renewcommand\siprefix{S.S.I.~}

\setlength\headheight{27.57402pt}

\begin{document}

\maketitle

\noindent
The Scottish Ministers, in exercise of the powers conferred by sections 45(1) and (7) and 58(7) of the Child Support Act 1991\footnote{1991 c.\ 48. Section 45(1) was amended by the Social Security Act 1998 (c.\ 14), Schedule 7, paragraph 42. The functions of the Lord Advocate were transferred to the Secretary of State by the Transfer of Functions (Lord Advocate and Secretary of State) Order 1999 (S.I.\ 1999/678), article 2(1) and the Schedule, and the functions of the Secretary of State were transferred to the Scottish Ministers by the Scotland Act 1998 (Transfer of Functions to the Scottish Ministers etc.)\ Order 1999 (S.I.\ 1999/1750), article 2 and Schedule 1.} and of all other powers enabling them in that behalf, hereby make the following Order, a draft of which has, in accordance with section 52(2) of that Act, been laid before and approved by resolution of the Scottish Parliament: 

{\sloppy

\tableofcontents

}

\bigskip

\setcounter{secnumdepth}{-2}

\subsection[1. Citation, commencement, interpretation and extent]{Citation, commencement, interpretation and extent}

1.---(1)  This Order may be cited as the Child Support Appeals (Jurisdiction of Courts) (Scotland) Order 2003.

(2) This Order shall come into force in relation to a particular type of case on the date on which section 10 of the Child Support, Pensions and Social Security Act 2000\footnote{2000 c.\ 19.} comes into force for the purposes of that type of case.

(3) In this Order–
\begin{enumerate}\item[]
($a$) “the Act” means the Child Support Act 1991; and

($b$) “the Regulations” means the Social Security and Child Support (Decisions and Appeals) Regulations 1999\footnote{S.I.\ 1999/991.}.
\end{enumerate}

(4) This Order extends to Scotland only.

\subsection[2--4. Parentage appeals to be made to courts]{Parentage appeals to be made to courts}

2.  An appeal under section 20\footnote{1991 c.\ 48. Section 20 was substituted by section 10 of the Child Support, Pensions and Social Security Act 2000 (c.\ 19).} of the Act shall be made to a court instead of to an appeal tribunal in the circumstances mentioned in article 3.

\medskip

3.  The circumstances are that–
\begin{enumerate}\item[]
($a$) the appeal will be an appeal under section 20(1)($a$)  or ($b$)  of the Act;

($b$) the decision by the Secretary of State against which the appeal is brought was made on the basis that a particular person (whether the applicant or some other person) either was, or was not, a parent of the qualifying child in question (“a parentage determination”); and

($c$) the ground of appeal will be that, the parentage determination being unfounded in fact, the decision should not have been made on that basis.
\end{enumerate}

\medskip

4.---(1)  For the purposes of article 2, an appeal may be made to a court in Scotland if–
\begin{enumerate}\item[]
($a$) the child in question was born in Scotland; or

($b$) the child, the non-resident parent or the person with care of the child is domiciled in Scotland on the date when the appeal is made or is habitually resident in Scotland on that date.
\end{enumerate}

(2) Where an appeal to a court in Scotland is to be made to the sheriff, it shall be to the sheriff of the sheriffdom where–
\begin{enumerate}\item[]
($a$) the child in question was born; or

($b$) the child, the non-resident parent or the person with care of the child is habitually resident on the date when the appeal is made.
\end{enumerate}

\subsection[5. Modifications to the Social Security and Child Support (Decisions and Appeals) Regulations 1999]{Modifications to the Social Security and Child Support (Decisions and Appeals) Regulations 1999}

5.  Regulations 31 and 32 of the Regulations shall apply to appeals brought under this Order with the following modifications–
\begin{enumerate}\item[]
($a$) in regulation 31(1), for “an appeal tribunal” substitute “a court”;

($b$) wherever they appear, for “legally qualified panel member” or “panel member” substitute “the court”;

($c$) in regulation 32(10) for “such written form as has been approved by the President” substitute “written form”.
\end{enumerate}

\subsection[6. Revocation]{Revocation}

6.  The Child Support Appeals (Jurisdiction of Courts) Order 1993\footnote{S.I.\ 1993/961.}, to the extent that it applies to Scotland, is revoked.

\subsection[7. Amendment of the Law Reform (Parent and Child) (Scotland) Act 1986]{Amendment of the Law Reform (Parent and Child) (Scotland) Act 1986}

7.  In section 8 (Interpretation) of the Law Reform (Parent and Child) (Scotland) Act 1986\footnote{1986 c.\ 9. Section 8 of that Act was amended by article 8 of the Child Support Appeals (Jurisdiction of Courts) Order 1993 (S.I.\ 1993/961), which is repealed by article 6 of this Order.} at the end of the definition of “action for declarator” there shall be inserted the words “but does not include an appeal under section 20(1)($a$)  or ($b$)  (Appeals) of the Child Support Act 1991 made to the court by virtue of an order made under section 45 (jurisdiction of the courts in certain proceedings) of that Act:”. 

\bigskip

%Signed 
%by authority of the Secretary of State for Work and Pensions.

{\raggedleft
\emph{Hugh Henry}\\*A member of the Scottish Executive%Parliamentary Under-Secretary of State,\\*Department of Work and Pensions

}

St Andrew's House, Edinburgh

%Dated
18th February 2003

\small

\part{Explanatory Note}

\renewcommand\parthead{— Explanatory Note}

\subsection*{(This note is not part of the Order)}

This Order revokes and replaces (as regards Scotland) the Child Support Appeals (Jurisdiction of Courts) Order 1993, which provides for child support appeals to be made to a court instead of to an appeal tribunal where the issue in the appeal is parentage of the qualifying child in relation to whom an application for a maintenance calculation has been made under the Child Support Act 1991.

This Order is designed to take account of the changes made to section 20 of the Child Support Act 1991 (which deals with child support appeals) effected by section 10 of the Child Support, Pensions and Social Security Act 2000. This Order also makes provision for the application (with modifications) of regulations 31 and 32 of the Social Security and Child Support (Decision and Appeals) Regulations 1999 in relation to the appeals to which this Order applies. Article 8 of the Child Support Appeals (Jurisdiction of Courts) Order 1993 (which amended the Law Reform (Parent and Child) (Scotland) Act 1986 consequential on that Order) is re-enacted as article 7 of this Order with necessary amendment to reflect the terms of this Order.  

\end{document}